### 2016-03-14 journal-draft/bare_jrnl_comsoc.tex
erwin's input

\documentclass[10pt,journal,compsoc]{IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal,comsoc]{../sty/IEEEtran}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% copied from thesis
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Packages für Formeln %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[colorlinks,
            linkcolor=red,
            anchorcolor=blue,
            citecolor=green
            ]{hyperref}
\usepackage{amsmath}
\usepackage{amsthm}
%\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{booktabs}
\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}

%% Packages
%\usepackage{tikz}
%\usetikzlibrary{shapes,arrows}
%\usetikzlibrary{positioning}
\usepackage{graphicx}
\usepackage{kantlipsum} %<- For dummy text
\usepackage{mwe} %<- For dummy images
\usepackage{multirow}
\usepackage{multicol}
%\usepackage{colortbl}
%\usepackage{todonotes}	
\newcounter{todocounter}
\newcommand{\todonum}[2][]
{\stepcounter{todocounter}\todo[inline,backgroundcolor=blue!10!white, #1]{\thetodocounter: #2}}

%% Zeilenabstand %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{setspace}
%\singlespacing        %% 1-zeilig (Standard)
%\onehalfspacing       %% 1,5-zeilig
%\doublespacing        %% 2-zeilig

%% Andere Packages %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage{a4wide} %%Kleinere Seitenränder = mehr Text pro Zeile.
\usepackage{fancyhdr} %%Fancy Kopf- und Fußzeilen
%\usepackage{longtable} %%Für Tabellen, die eine Seite überschreiten
\usepackage{lscape}
\usepackage{rotating} 
%\usepackage[htt]{hyphenat} %Trennung von Typewriter-Schriften
%\usepackage{listings}
%\usepackage{pstricks-add} --> This package generates problems with booktabs (toprule, etc.)
\usepackage[autostyle]{csquotes}
\usepackage{amsmath,bm}
\usepackage{array}
% Tabellen mit Center und left
\usepackage{tabularx,colortbl} % colored table background
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
% Table spacings
\newcommand\T{\rule{0pt}{2.5ex}\rule[-1.0ex]{0pt}{0pt}}
\newcommand\B{\rule[-1.0ex]{0pt}{0pt}}

\definecolor{slightgray}{gray}{.90} 
\usepackage{rotating}
\usepackage{hhline}

\newtheoremstyle{mytheoremstyle} % name
        {\topsep}                    % Space above
        {\topsep}                    % Space below
        {\itshape\fontfamily{ptm}\selectfont}                   % Body font, ptm is times new roma
        {}                           % Indent amount
        {\fontfamily{ptm}\selectfont\scshape\color{black}\bfseries}                   % Theorem head font
        {:}                          % Punctuation after theorem head
        {.5em}                       % Space after theorem head
        {}  % Theorem head spec (can be left empty, meaning ‘normal’)

\theoremstyle{mytheoremstyle}
\newtheorem{theorem}{Theorem}[section]

\theoremstyle{mytheoremstyle}
\newtheorem{corollary}{Corollary}[section]

\theoremstyle{mytheoremstyle}
\newtheorem{lemma}{Lemma}[section]

%\theoremstyle{mytheoremstyle}
%\let\definition\relax
\newtheorem{mydef}{Definition}%[section]

%%%%%%
%%%%%% Proof
    \makeatletter
    \renewenvironment{proof}[1][\proofname]{%
      \par\pushQED{\qed}\fontfamily{ptm}\selectfont%
      \topsep6\p@\@plus6\p@\relax
      \trivlist\item[\hskip\labelsep\bfseries#1\@addpunct{.}]%
      \ignorespaces
    }{%
      \popQED\endtrivlist\@endpefalse
    }
    \makeatother 
%%%%%%%%%%%%%%%%%

\newcommand{\eg}{e.g., }
\newcommand{\ie}{i.e., }
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
%\usepackage{algorithmic}
\usepackage{times}
%\usepackage{mathptmx}
\usepackage{mathtools}
\usepackage[draft,nomargin,marginclue,footnote,silent]{fixme}
\setcounter{tocdepth}{2}

\makeatother
\usepackage{comment}
\newcommand{\Tau}{\mathrm{T}}
\usepackage[colorinlistoftodos]{todonotes}
\DeclareMathOperator*{\Max}{Max}
\DeclareMathOperator*{\Min}{Min}

\newcommand{\bigO}{\ensuremath{\mathcal{O}}}% big-O notation/symbol
\usepackage{subfigure}
\usepackage{adjustbox}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{lipsum}
\setlist[itemize]{leftmargin=*}
%%%%%%%%%%%%%%%%%%%%%%%%%% copied from thesis
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage[T1]{fontenc}% optional T1 font encoding

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
% Do NOT use the amsbsy package under comsoc mode as that feature is
% already built into the Times Math font (newtxmath, mathtime, etc.).
% 
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% Select a Times math font under comsoc mode or else one will automatically
% be selected for you at the document start. This is required as Communications
% Society journals use a Times, not Computer Modern, math font.
%\usepackage[cmintegrals]{newtxmath}
\usepackage{txfonts}
% The freely available newtxmath package was written by Michael Sharpe and
% provides a feature rich Times math font. The cmintegrals option, which is
% the default under IEEEtran, is needed to get the correct style integral
% symbols used in Communications Society journals. Version 1.451, July 28,
% 2015 or later is recommended. Also, do *not* load the newtxtext.sty package
% as doing so would alter the main text font.
% http://www.ctan.org/pkg/newtx
%
% Alternatively, you can use the MathTime commercial fonts if you have them
% installed on your system:
%\usepackage{mtpro2}
%\usepackage{mt11p}
%\usepackage{mathtime}

%\usepackage{bm}
% The bm.sty package was written by David Carlisle and Frank Mittelbach.
% This package provides a \bm{} to produce bold math symbols.
% http://www.ctan.org/pkg/bm

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Versatile Robust Clustering of Ad Hoc Cognitive Radio Network}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{Di~Li,~\IEEEmembership{Member,~IEEE,}
        Erwin~Fang,
        and James~Gross,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
\thanks{D. Li was with RWTH Aachen university, Germany.}% <-this % stops a space
\thanks{Erwin. Fang is with ETH, Switzerland.}% <-this % stops a space
\thanks{J. Gross is with KTH Royal Institute of Technology, Sweden.}% <-this % stops a space
\thanks{Manuscript received xxxx xx, 20xx; revised xxxx xx, 20xx.}}

% note the % following the last \IEEEmembership and also \thanks - 
% these prevent an unwanted space from occurring between the last author name
% and the end of the author line. i.e., if you had this:
% 
% \author{....lastname \thanks{...} \thanks{...} }
%                     ^------------^------------^----Do not want these spaces!
%
% a space would be appended to the last name and could cause every name on that
% line to be shifted left slightly. This is one of those "LaTeX things". For
% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
% "AB" then you have to do: "\textbf{A}\textbf{B}"
% \thanks is no different in this regard, so shield the last } of each \thanks
% that ends a line with a % and do not let a space in before the next \thanks.
% Spaces after \IEEEmembership other than the last one are OK (and needed) as
% you are supposed to have spaces between the names. For what it is worth,
% this is a minor point as most people would not even notice if the said evil
% space somehow managed to creep in.

% The paper headers
\markboth{Journal of xxxxx,~Vol.~xx, No.~x, xxxx~20xx}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Communications Society Journals}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark.

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
Cluster structure in CRN facilitates cooperative spectrum sensing, routing and other functionalities.
The availability of unlicensed channels which are available for every member in a cluster decides the survival of that cluster from licensed users' influence.
Thus in order to be robust against licensed users, there should be more unlicensed channels in the clusters.
In the process of forming clusters, every secondary user needs to decide with whom to form a cluster, or which cluster to join.
Congestion game model is adopted to analyse this process, which not only contributes the algorithm design directly, but also provides guarantee of convergence into Nash Equilibrium and convergence speed.
%
Our proposed distributed clustering scheme outperforms the comparison scheme in terms of robustness against primary users, convergence speed and volume of control messages.
Furthermore, the proposed clustering solution is versatile to fulfil other requirements such like fast convergence and cluster size control.
Besides, we prove the clustering problem to be NP-hard, and also propose the centralized solution.
The extensive simulation supports our claims.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Cognitive Radio, Cluster, Robust, game theory, congestion game, distributed, centralised, size control.
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\graphicspath{
{../figures/04_clutering/}
}

\section{Introduction}
\label{intro}
%CR concept
\IEEEPARstart{C}{ognitive} radio (CR) is a promising technology to solve the spectrum scarcity problem~\cite{Mitola}.
Unlicensed users access the spectrum allocated to them whenever there is information to be transmitted.
In contrast, unlicensed users can only access the licensed spectrum after validating the channel is unoccupied by licensed users.
This refers to the process of sensing a particular channel and verifying (with a previously specified probability of error) that it is not used by a primary user currently.
In this hierarchical spectrum access model~\cite{zhao_survey_DSA_2007}, the licensed users are also called primary users (PU), and the CR users are known as secondary users and constitute the cognitive radio networks (CRN).

%cluster
As to the operation of CRN, efficient spectrum sensing is identified to be critical to the success of cognitive radio networks~\cite{Sahai_FundamentalDesignTradeoffs2006}.
Cooperative spectrum sensing is able to effectively cope with noise uncertainty and channel fading, thus remarkably improves the sensing accuracy~\cite{coorperativeSensing_Akyildiz11}.
Collaborative sensing relies on the consensus of CR users within certain area, and decreases considerably the false sensing reports caused by fading and shadowing of reporting channel.
In this regard, clustering is regarded as an effective method in cooperative spectrum sensing~\cite{Sun07_clustering_spectrum_secsing, Zhao07}, as a cluster forms adjacent secondary users as a collectivity to perform spectrum sensing together.
%As a result, more accurate sensing result can be obtained by collaborative sensing, and the improvement on spectrum sensing decreases the interference originating from CR users to primary users, which is highly desirable.
%Also,  prevents CR users from using channels that are occupied by primary users. 
Clustering is also efficient to enable all CR devices within the same cluster to stop payload transmission on the operating channel and initiate the sensing process, so that all the CR users\footnote{User and node are used interchangeably in this paper, in particular, user is used when its networking or cognitive ability are discussed or stressed, and node is used when the network topology is discussed.} within the one cluster are able to vacate the channel swiftly when primary users are detected by at least one CR node residing in the cluster~\cite{willkomm08}.
With cluster structure, as CR users can be notified by cluster head (CH) or other cluster members about the possible collision, the possibility for them to interfere neighbouring clusters is reduced~\cite{centralizedSharing80222}. 
Clustering algorithm has also proposed to support routing in cognitive ad-hoc networks~\cite{Abbasi_survey_07}.

%%[crn for clustering] 
%%due to attenuation of signal propagation, primary users can only be detected by CR users when they locate closely to CR users.
%In cognitive radio networks, secondary users which locate closely with each other are possibly affected by the same group of primary users, so that the availability of licensed spectrum is similar to them, \ie certain channels are available on each of them.
%The similarity of available spectrum on a group of neighbouring CR nodes, along with the benefit of collaborative decision among multiple nodes, leads to clustering as an effective approach for many applications.

%[robustness issue for clustering]
The communication within a cluster is conducted in the spectrum which is available for every member in that cluster.
Usually there are multiple unlicensed channels available for all the members in a cluster, which are referred as \textit{common control channels} (CCC).
When one or several members can not use one certain CCC because primary users are detected to appear on that channel, this channel will be excluded from the set of CCCs, in particular, if this channel is the working channel, then all the cluster members switch to another channel in the set of CCCs.
In the context of CRN, as the activity of primary users is controlled by licensed operators which are generally not known to CR users, the availability of CCCs for the formed clusters  is totally decided by primary users' activity.
In other words, the availability of CCCs for clusters is passive and can not guaranteed.
%
In CRN, one cluster survives the influence of primary users when at least one CCC is available for that cluster.
As the channel occupation by primary users is assumed to be uncontrollable to the CR users, a cluster formed with more CCCs will survive with higher probability.
Thus the number of CCCs in one cluster indicates robustness of it when facing ungovernable influence from primary users.
%It is easy to see that forming clusters with different neighbours leads to different amount of CCCs in the clusters.
As a result, how to form the clusters plays an important role on the robustness of clusters in CRN.

%Furthermore, the clustering algorithm also determines the connectivity between several clusters which ultimately determines the robustness of the entire network on the respect of connectivity.

To solely pursue cluster robustness against the primary users' activity, \ie to achieve more common channels within clusters, the ultimately best clustering strategy is ironically that each node constitutes one single node clusters.
%In that case, the common channels within cluster are the available channels available at that node's place.
Apparently this contradicts our motivation of proposing cluster in cognitive radio network.
This contradiction indicates that, the robustness discussed in terms of number of common channels carries little meaning when the sizes of formed clusters are not given consideration.
Besides, cluster size plays import roles in certain aspects.
For instance, cluster size is one decisive factor in power preservation~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}, and it also influences the accuracy of cooperative spectrum sensing~\cite{Consensus_based_clustering12}.
Hence, cluster size should be given consideration when discussing cluster robustness against primary users.

In this paper, a decentralized clustering approach ROSS (RObust Spectrum Sharing) is proposed to cover the issues of robustness and size control of clusters in CRN.
ROSS is able to form clusters with desired sizes, and the generated clusters are more robust than other clustering scheme which has claims on cluster robustness, \ie more secondary users residing in clusters against increasing influence from primary users.
Compared with previous work, ROSS involves much less control messages, and the generated clusters are significantly more robust.
%ROSS selects cluster head through coordination within its neighborhood, and then cluster membership is decided locally and its fast convergence is proved under game theoretic framework. 
%For our scheme we can prove convergence in cluster formation phase and resolve ambiguities with respect to cluster membership in a game-theoretic setting. 
We also propose the light weighted versions of ROSS, which involve less overheads and thus are more suitable for mobile networks.
Throughout this paper, we refer the clustering schemes on the basis of ROSS as \textit{variants of ROSS}, \ie the fast versions, or that with size control feature.

The rest of paper is organized as follows. 
After reviewing related work in section~\ref{related_work}, we present our system model in Section~\ref{sec:model}. 
Then we introduce our clustering scheme ROSS and its variants in section~\ref{ross}.
The clustering problem is given through analysis and a centralized scheme is proposed in section~\ref{centralized_scheme}.
Extensive performance evaluation is in section~\ref{performance}.
Finally, we conclude our work and point out direction future research in section~\ref{conclusion}.

\section{Related Work}
\label{related_work}

Prior to the emergence of open spectrum access, as an important method to manage network, clustering has been proposed in for ad hoc networks~\cite{Kawadia03,Lin97adaptiveclustering,Basagni99}, wireless mesh networks and sensor networks~\cite{Abbasi_survey_07}. 
In ad hoc and mesh networks, the major focus of clustering is to preserve connectivity (under static channel conditions) or to improve routing.
In sensor networks, the emphasis of clustering has been on longevity and coverage.
Overhead generated by clustering in ad hoc network is analysed in~\cite{clusterRoutingOverhead02infocom, clusterRoutingOverhead_wcnc04}.

As to cognitive radio networks, clustering schemes are also proposed, which target different aspects.
Work~\cite{Consensus_based_clustering12} improves spectrum sensing ability by grouping the CR users
with potentially best detection performance into the same cluster.
Clustering scheme~\cite{clustering_globecom11} obtains the best cluster size which minimizes power consumption caused by communication within and among clusters.
\cite{clustering_globecom11} proposes clustering strategy in cognitive radio network, which looks into the relationship between cluster size and power consumption and accordingly controlling the cluster size to decrease power consumption.
%The works~\cite{} introduced in Introduction section don't provide solution that how are the clusters formed.
%There have been several clustering schemes tailored for CRNs. 
Cogmesh is proposed in~\cite{Chen07} to construct clusters by the neighbour nodes which share local common channels, and by interacting with neighbour clusters, a mesh network in the context of open spectrum sharing is formed.
Robustness issue is not considered by this clustering approach.
\cite{TWC2012_cooperative_communication} targets on the QoS poisoning and energy efficiency. 
This approach first decides on the relay nodes which minimize transmission power consumption, then the chosen nodes become cluster heads and clusters are formed in a dynamic coalition process.
This work emphasis on power efficiency and doesn't take into account the channel availability and the issue of robustness of the formed clusters.
In~\cite{Zhao07, Affinity_clustering_09icccn}, the channel available to the largest set of one-hop neighbours is selected as common channel which yields a partition of the CRN into clusters. 
This approach minimizes the set of distinct frequency bands (and hence, the set of clusters) used as common channels within the CRN.
However, bigger cluster sizes generally lead to less options within one cluster to switch to if the common channel is reclaimed by a primary node. 
Hence, this scheme does not provide robustness to formed clusters. 
\cite{cluster_EW10} deploys cluster structure in order to implement common channel control, medium access  with multiple channel and channel allocation. 
The node with the maximum number of common channels within its k-hop neighborhood is chosen as cluster head, but how to avoid one node appearing in multiple clusters is not given consideration.

Clustering robustness is considered in~\cite{Lazos09, LIU_TMC11_2}.
The authors propose a distributed scheme where the metric is the product of cluster size and the number of common control channels.
This scheme involves both cluster size and number of CCCs, but it is inherently flawed.
With the metric, cluster could be formed only due to one factor of the two, e.g. a spectrum rich node will exclude its neighbour to form a cluster by itself.
%emphasis on improving the numbers of common channels within clusters, in order to strengthening robustness of clusters, but the perused metric is not examined or proved to be able to maintain cluster structure under vigorous intensity of primary users’ activities.
%The authors consider the balance between the number of idle common channels within cluster and cluster size and propose an algorithm that increases the number of common channels within clusters. 
%However, this work neglects the issue of connectivity between clusters. 
%One drawback of this scheme is, in order to increase the number of common channels within clusters, the scheme excludes certain CR nodes from the formed clusters, so that isolated nodes have to form clusters themselves. 
Besides, this scheme leads to a high variance on the size of clusters, which is not desired in certain applications as discussed in~\cite{clustering_globecom11, cluster_EW10}.

\section{System Model}
\label{sec:model}
%Let us consider a two dimensional area where primary and secondary users coexist together.
%They share the licensed channels according to the spectrum overlay model, where secondary transmitters are only allowed to transmit when the primary users are detected as being idle, and they should vacate the working channel when the presence of primary user is detected.
%The set of primary users and secondary users are presented by $\mathcal{P}$ and $\mathcal{N}$ separately, there are $|\mathcal{P}| = P$ and $|\mathcal{N}| = N$.
%Cognitive radio ad hoc network is constituted by all the secondary users in $\mathcal{N}$.
%The collection of non-overlapping licensed frequency bands is denoted as $\mathcal{F}$ with $|\mathcal{F}| =F$, which is shared by the the primary and secondary users.
%We assume that primary users have a relatively low variation in activity (periods of activity and inactivity in the range of seconds or minutes).
%%
%Primary users access the allocated channels in $\mathcal{F}$ according to its need without sending any explicit notification to secondary users.

We consider wireless sensor nodes distributed on a two-dimensional Euclidean plane. We denote the set of these nodes as $V$ which is partitioned into sets of primary users $V_P$ and secondary users $V_N$, i.e., $V~=~V_P~\dot\cup~V_N$. These users share a number of non-overlapping licenced channels according to the spectrum overlay model. The set of these licenced channels is denoted as $\mathcal{C}$. Secondary users are allowed to transmit on a channel $c \in \mathcal{C}$ only if every primary user $p \in V_P$ that has access to channel $c$ is idle. Further, we consider a \textit{cognitive radio ad-hoc network} which consists of all secondary users and does not contain any primary user.

%Secondary users conduct spectrum sensing independently, and every secondary user conducts spectrum sensing on all licensed channels sequentially.
%The sensing duration and frequency on one channel is a technical problem~\cite{sensing_survey_2009}, but we assume that every node can to certain extend accurately and agilely detect the presence of primary user on each channel. \footnote{The spectrum availability can be validated with a certain probability of detection. Spectrum sensing/validation is out of the scope of this paper.}
%The available channels sensed on secondary user $i$ is denoted by $V_i$ and there is $\vert V_i \vert \leq F$. % indicating the total number of 
%%Each secondary user notifies its neighbours of the sensing result about the available channels.

Secondary users conduct spectrum sensing independently and sequentially on all licenced channels. In our system model, we assume that a secondary node $n$ is able to detect for each channel $c$ whether any primary user utilizes $c$. We denote $C_n \subseteq \mathcal{C}$ as the set of available channels for $n$.

%One dedicated control channel is assumed to be available for all the secondary nodes to exchange control messages with neighbours in the process of cluster formation.
%The control channel could be in ISM band or other reserved spectrum which is exclusively used for transmitting control messages.
%Note that the assumption of dedicated control channel is to simplify the discussion so that we can focus on the kernel of this paper, the robustness of clusters.
%Actually, the control messages involved in the clustering process can be conveyed on available licensed channels through rendezvous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}. 
%Over the control channel, secondary users exchange their spectrum sensing results $V_{i}$ with one hop neighbours. 
%Secondary users have the same transmission range on both licensed and control channel, and the communication links are reciprocal.

In addition to the licenced channels there is one dedicated control channel. It is available for any secondary node $n$ to exchange control messages with any other node in its proximity (or neighborhood) $N(n)$ during the cluster formation phase. $N(n)$ is simply defined as the set of nodes located within the transmission range of $n$. Control messages involved in the clustering process can be transmitted on available licenced channels through a rendez-vous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}. \textcolor{red}{(The rendez-vous should be briefly explained! TODO)} Over the control channel, a secondary user $n$ can exchange its spectrum sensing result $C_n$ to any $n' \in N(n)$.

%Primary users also have fixed transmission range on the licensed channels\footnote{This assumption is made to simplify the discussion, and doesn't affect the effectiveness of the proposed scheme}.

\textcolor{red}{As to a pair of secondary users, when the distance between them is smaller than secondary users' transmission range, we assume the pair is able to communicate on both control channel and licensed channel, and the both are considered to be neighbours of each other. DEFINE DISTANCE! TODO for Di!}

If a secondary user $n$ is not in the transmission range of a primary user $u$, $n$ can certainly not detect the presence of $u$.
As the transmission range of primary users is limited and secondary users are located at different locations, different secondary users may have different views of the spectrum availability, i.e., for any $n, n' \in \mathcal{N}$, $C_n = C_{n'}$ does not necessarily hold.	
%
%Neighbourhood establishment and maintenance with control channel and according to a neighborhood discovery protocol which is out of scope of our work.
%While primary users are assumed to be fixed, secondary users can be mobile.
%Validation refers to the process of ensuring that no primary transmission is actually taking place on the respective channel.
%All $N$ secondary users constitute an ad-hoc network in which data can be transmitted from one certain node to any other node should available c.hannels are available on the source node, destination node and other intermediate nodes.
%Communication on licensed channels is possible only when nodes $i, j$ are both located in each other's transmission range and both share a validated licensed channel.
As the assumed $0/1$ state \textcolor{red}{(What is that?? Define! Fix it TODO)} of connectivity is solely based on the distance between secondary users,
%CRN can be represented by a graph $\mathcal{G}(I,\mathcal{E})$, where $\mathcal{E}=\lbrace(i,j,v) \vert i, j \in \mathcal{N} \wedge v\in V_i \wedge v\in V_j \rbrace$ is wireless link between any secondary node $i$ and its neighbour $j$ with licensed channel $v$.
%Due to relatively low primary user dynamics, time index is omitted here.
%%In order to perform clustering, CR users first need to establish their neighborhood.
%For secondary node $i$, its neighborhood $Nb_i$ consists of all the secondary users locating within its transmission range, regardless whether common licensed channels exist or not. 
%% and have at least one common channel with node $i$ each, i.e. $ j\in Nb_i \Rightarrow V_i\cap V_j\neq \emptyset$.
%%The clustering phase is initialized during which any control message is again conveyed by the control channel.
%In the rest of this paper, \textit{channel} only refers to the licensed common control channel unless the dedicated control channel is particularly mentioned.

A cognitive readio network (CRN) can be represented as an undirected graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{n_1,n_2\} \in E$  if, and only if, there exists a channel $c \in \mathcal{C}$ with $c \in C_{n_1} \cap C_{n_2}$. Note that we consider the channel availability only for \textit{one} snapshot of time. For the rest of this paper the word channel is referred to licensed channel, if the control channel is not explicitly mentioned.

\subsection{Clustering}
\label{def_cluster}
%We give the description of cluster in the context of CRN, all the clusters discussed in this paper comply with it.
%A cluster $C$ is composed with one cluster head and cluster members, which satisfies the following conditions:
%\begin{itemize}
%\item Cluster head $H_C$ is able to communicate with any cluster member \textit{directly}, \ie for any cluster member $i\in C$, there is $i\in \texttt{Nb}_{H_C}$.
%\item There exists as least one common control channel in the cluster, \ie $\cap_{i\in C} V_i \neq \emptyset$.
%\end{itemize}
In this section, we describe what a cluster in the context of CRNs means. A cluster $\textsf{Cl} \subseteq \mathcal{N}$ is a set of secondary nodes consisting of a cluster head $h_{\textsf{Cl}}$ and a number of cluster members. The cluster head is able to communicate with any cluster member directly. In other terms, for any cluster member $m \in \textsf{Cl}$, $m \in N \left( h_{\textsf{Cl}} \right)$ holds.

A cluster head coordinates the activities of cluster members, \ie it notifies all the members to vacate a channel if a primary user's presence is detected by one cluster member. Further it also notifies the members to use a different common control channel for payload communication. (\textcolor{red}{(Not clear what the meaning of payload communication is. Why not omitting payload here?)}

----------- No modifications from here on ... -------------

Cluster is denoted as $C_i$, the subscript $i$ represents the cluster head.
%, for the sake of concision, $C_i$ is also named as cluster $i$ in the following part of this paper.
We denote the set of common control channels for cluster $C$ with set $K_C$.
$ K_C = \cap_{i\in C_i} V_i$, and $k_C = |K_C|$ is the number of common control channels for cluster $C$.
Clustering is performed periodicity, as secondary users may move with certain velocity, or the most current clusters can not maintain due to lack of CCCs when primary users' operation is intense.

%We propose distributed scheme ROSS to form clusters to generate robust clusters, and in the same time clusters have preferred sizes, \ie fewer number of singleton clusters (the cluster which consist with only one CR node) compared with state of art.

%Besides, cluster size is also considered in to clustering solution.
%Size preference can be met after minor modifications on ROSS.

%The metric is summation of the number of channels available to be used for each node when they reside in a certain cluster, together with a cost for not following the desired cluster size, \ie when the desired cluster size is $\delta$ and the other cluster sizes are denoted as $\delta'$, the metric is, 
%\begin{equation}
%\label{metric}
%\sum_{i=1}^{N}(ICC_i)
%\end{equation}
%$N$ is the number of CR nodes in the network.

%Also, we refer to the common channels between neighbouring clusters by the term \textit{outward common channels} (OCC). We define the set of OCCs of cluster $C$ to be the set of available common channels between any member of $C$ and any other CR user of a neighbouring cluster:
%\begin{equation}
%\label{numocc}
%R_{C}=\bigcup_{j\in C, k\in N_j, k\notin C}(V_{j}\cap V_{k})
%\end{equation}

%In the process of clustering, when there is no restriction on cluster size, the metric will only be the summation of the number of channels for each node when they reside in a certain cluster.
%When we try to maximize the summation of ICCs, an obvious correlation between cluster size and number of ICCs is encountered, \ie when each node constitutes one cluster, the aforementioned metric will be maximized.
%The goal of the proposed clustering scheme is to let as more CR nodes as possible to form clusters, meanwhile the clusters have more common channels and preferred cluster size.

\begin{table}[h!]
\caption{Notations in robust clustering problem}
\label{tab1}
\centering
\begin{tabular}{llr}
\toprule
%\multicolumn{2}{c}{Item} \\
%\cmidrule(r){1-2}
Symbol & Description \\
\midrule
$\mathcal{P}$, $\mathcal{N}$  & collection of primary and secondary users\\
$P$, $N$ & the number of primary users and secondary users\\
%$J$ & set of primary uesrs in the scenario\\
$\mathcal{F}$ & set of non-overlapping channels in the scenario\\
$\texttt{Nb}_i$ & node $i$' neighborhood     \\
$C$ & a cluster \\
$C_i$ & a cluster whose cluster head is $i$ \\
& (in Section~\ref{centralized_scheme}, $C_i$ is the $i$th cluster \\
& among the legitimate clusters.)\\
$V_i$   & set of available channels at CR node $i$  \\
$V_C$   & set of available CCCs of cluster $C$  \\
$V_{C_i}$   & set of available CCCs of cluster $C_i$\\
%$\phi_i$ & the number of available channels for cluster $i$\\ 
%		& note it is different than $|V_i|$\\
%$p_i$   & number of available channels on CR node $i$  \\
$H_C$ & cluster head of a cluster $C$\\
$\delta$ & desired cluster size\\
%$C_i$ & a cluster with CR node $i$ as cluster head \\
%$V_{C_i}$   & set of common channels within cluster $C_i$  \\
%$V_{OC_i}$   & set of common channels among cluster $C_i$ and neighbor clusters  \\
%$CH_i$ & cluster head of node $i$ \\
%$CHS_i$ & set of cluster heads of node $i$ after phase I\\
$S_i$ & set of claiming clusters, each of which includes \\
& debatable node $i$ after phase I\\
$K_{C_i}$ & set of CCCs within cluster $C_i$\\
$k_{C_i}$ & num. of CCCs of cluster $C_i$, $k_{C_i} = |K_{C_i}|$\\
%$m_{ij}$ & number of common channels between CR node \\
%& $i$ and $j$\\
\bottomrule
\end{tabular}
\end{table}

\section{Distributed Coordination Framework: Clustering Algorithm}
\label{ross}

In this section, we present the clustering scheme ROSS.
ROSS utilizes the proximity of the available spectrum within a local area to form clusters.
%is based on the spectrum sensing results in its neighbours , then
ROSS consists of two cascaded phases: \textit{cluster formation} and \textit{membership clarification}.
We will describe them sequentially.

\subsection{Phase I - Cluster Formation}
\label{phaseI}
After conducting spectrum sensing and communication with neighbours, every CR node is aware of the available channels at itself and all its neighbours.
For each CR user, two metrics are proposed to characterize the spectrum proximity between the CR user and its neighborhood.
As to CR node $i$, there are,
%\newtheorem{def1}{Definition}
%\label{def1}
%\begin{def1}
%Connection vector $\left\{D_i,G_i\right\}$ of CR node $i$:
%spectrum connectivity degree: 
%\begin{equation}
%\label{D_i}
%D_i=\sum_{j\in N_i}\vert V_i\cap V_j\vert
%\end{equation}
%Social Connection degree:
%\begin{equation}
%\label{G_i}
%G_i=|\bigcap_{j\in N_i}V_j|
%\end{equation}
%\end{def1}
\begin{itemize}

\item \textit{Individual connectivity degree} $D_i$: $D_i=\sum_{j\in \texttt{Nb}_i}\vert V_i\cap V_j\vert$, which denotes the sum of the pairwise common channels of node $i$. 
It is an indicator of node $i$'s adhesive property to the CRN.

\item \textit{Social connectivity degree} $G_i$: $G_i=|\bigcap_{j\in \texttt{Nb}_i\cup i}V_j|$, which is the number of common channels of CR node $i$ and its neighbours.
$G_i$ represents the ability of $i$ to form a robust cluster with its neighborhood.
\end{itemize}
Individual connectivity degree $D_i$ and social connectivity degree $G_i$ together form the \textit{connectivity vector}.
Figure~\ref{fig1} illustrates an example CRN where each node's connectivity vector is calculated and shown.	
\begin{figure}[ht!]
  \centering
\includegraphics[width=0.7\linewidth]{figure1.pdf}
% \includegraphics{figure1.pdf}
	\caption{Connectivity graph and the connectivity vector $\{D_i, G_i\}$ on each node. The available channels sensed by each CR node are: $V_A=\{1,2,3,4,5,6,10\}, V_B=\{1,2,3,5,7\}, V_C=\{1,3,4,10\}, V_D=\{1,2,3,5\}, V_E=\{2,3,5,7\}, V_F=\{2,4,5,6,7\}, V_G=\{1,2,3,4,8\}, V_H=\{1,2,5,8\}$. Dashed lines indicates two end nodes are within transmission range of each other. Each edge is labelled by the number of common channels between the two ends.}
	\label{fig1}
\end{figure}

After introducing connectivity vector, we proceed to introduce the first phase of algorithm ROSS.
At first, cluster heads are determined, then clusters are formed on the basis of the cluster heads' neighbourhoods.

\subsubsection{Determining Cluster Heads and Form the Initial Clusters}
In this phase, each CR node decides whether it is cluster head by comparing its connectivity vector with its neighbours.
When CR node $i$ has bigger individual connectivity degree than any neighbours except for those which have already become cluster heads (the appearance of cluster heads will be explained in next subsubsection), then node $i$ becomes clusters head.
%In other words, CR node $i$ becomes cluster head if $D_i > D_k, \forall k\in \texttt{Nb}_i\setminus CHs$ ($CHs$ donate the cluster heads existing in $\texttt{Nb}_i$).
If there is another CR node $j$ in its neighborhood, which has the same individual connectivity degree with $i$, \ie $D_j = D_i$ and $D_j > D_{k}, \forall k\in Nb_j\setminus \{CHs\cup i\}$, then the node out of $\{i, j\}$ with higher social connectivity degree becomes cluster head, and the other one becomes one member of it. 
If $G_i = G_j$ as well, node ID is used to break the tie, \ie the one with smaller node ID takes precedence and becomes cluster head.
%
The node which becomes cluster head broadcasts a message on its eligibility of being cluster head to notify its neighbours, and claims its neighbourhood as its cluster.
The pseudo code for deciding cluster head and forming initial clusters is in Algorithm~\ref{alg0} in appendix.

After receiving the notification from a cluster head, a CR node, \eg $i$, is aware that it becomes one member of a cluster, then $i$ sets its individual connectivity degree to zero. %, which is smaller than all the possible individual connectivity degrees in the CR network.
Then node $i$ broadcasts its new individual connectivity degree to all its neighbours. 
%wrong:
%Note that there is no cluster head which receives the notification on cluster head eligibility, and there is a Lemma on this.
%\begin{theorem}{lemma}
%There is no cluster head receiving the notification message on cluster head eligibility, which is sent from a node which newly becomes a cluster head.
%\end{theorem}
%\begin{proof}
%We use contradiction to prove. 
%Assume a CR node $j$ is cluster head, and receives a notification on cluster head eligibility form CR node $i$. 
%According to the assumption on the reciprocal communication link, $i$ should have received the notification message from $j$ when $j$ becomes cluster head.
%Then CR node $i$ will set its individual connectivity degree to zero, and has no possibility to become a cluster head.
%\end{proof}
When a CR node $i$ is associated to multiple clusters \ie $i$ receives multiple notifications on cluster head eligibility from different CR nodes, $D_i$ is still set to zero. %Note here that connectivity degree on cluster head will still be the actual value.% The value will expire after some duration and is changed later on back to the original value. 
%
%
The purpose of this temporary manipulation on individual connectivity degree is to let the CR nodes out side of the cluster be possible to become cluster heads, so that every CR node either becomes cluster head or a member of at least one cluster.
%In other words, with this manipulation on its individual connectivity degree, every CR node in the network will be involved in the clustering process, the proof will be given later.
%Every CR user is involved in the clustering process and becomes either cluster head or member is described in theorem~\ref{clustering:theorem}.
We have the following theorem to show that as long as a secondary user's connectivity the CRN is not zero, the secondary user will always be integrated into a certain cluster.
\begin{theorem}
\label{clustering:theorem}
Given a CRN, every secondary user is included into at least one cluster within $N$ steps.
\end{theorem}
The Proof is in Appendix~\ref{proof_clustering:theorem}.
According to Theorem~\ref{clustering:theorem}, we can assign reasonable amount of time for phase I to complete.

%This judgement is conducted periodically, and phase I ends after every node ascertains it is cluster head or not.
Let us apply Algorithm~\ref{alg0} to the example shown in Figure~\ref{fig1}.
Node $B$ and $H$ have same individual connectivity degree, $D_B=D_H$, but as $G_H=2>G_B=1$, node $H$ becomes cluster head.
Cluster $C_H$ is $\{H, B, A, G\}$.

\subsubsection{Guarantee Availability of Common Control Channel}
After deciding itself being cluster head, CR node broadcasts to notify its neighbours on the dedicated control channel, meanwhile, $i$'s initial cluster is formed immediately, which is $i$'s neighborhood except for those nodes which have become cluster heads, \ie $C_i=(\texttt{Nb}_i\setminus CHs)\cup i$.
Note this is the initial cluster, as it is possible for the formed cluster to pose no common control channels.
This problem can be solved with the following method.

As smaller cluster size increases the number of CCCs within the cluster, certain nodes are eliminated until there is at least one common control channel.
The elimination of nodes is performed according to an ascending list of nodes which are sorted by their number of common channels with the cluster head. 
In other words, the cluster member which has the least number of common channels with the cluster head is excluded first.
If there are nodes having the same number of common channels with cluster head, the node whose elimination brings in more common channels will be excluded.
If this criterion meets a tie, the tie will be broken by deleting the node with smaller ID.
It is possible that the cluster head excludes all its neighbours and resulting into a singleton cluster composed by itself.
%At the end of this procedure every formed cluster has at least one common channel.
The pseudo code for cluster head to obtain at least one common channel is shown in Algorithm~\ref{alg_size_control_available_CCC}.
As to the nodes eliminated in this procedure, they restore their original individual connectivity degrees, and become either cluster heads or get included into other clusters later on according to Theorem~\ref{clustering:theorem}.

\subsubsection{Cluster Size Control in Dense CRN}
\label{cluster_pruning}

In the introduction section, we have stated that cluster size should be given consideration to justify the concept of robustness of clusters, \ie without specifying requirement on cluster sizes, small clusters will be generated to obtain more CCCs.
Except for cooperative sensing, clusters need to conduct some other functionalities.
When cluster size is large, there will be substantial burden on cluster heads to manage the cluster members, which is a challenge for resource limited cluster heads, thus the cluster size should fall in a desired range~\cite{Chen04clusteringalgorithms, capacity_cluster_06}.
Here we illustrate the pressing necessity to control cluster size when CRN becomes dense via theoretical analysis and simulation.

Assuming the CR and primary users are evenly distributed and primary users occupy the licensed channels randomly, then both CR nodes density and channel availability in the CRN can be seen as homogeneous.
Based on Algorithm~\ref{alg0}, cluster heads are the CR nodes which possess the biggest individual connectivity degrees in their neighborhood respectively, and they are surrounded by CR nodes.
%In contrast, CR nodes residing on edge are unlikely to become cluster heads as their neighbourhoods are only half the nodes locating away from edge.
The formed clusters are the neighborhood of cluster heads, which is decided by the transmission range and network density.

When the CRN is extremely dense, consider a cluster with cluster head of CR node $i$, based on the rule for cluster head selection Algorithm~\ref{alg0}, the nearest cluster head could locate just outside node $i$'s transmission range.
An instance of this situation is shown in Figure~\ref{clusters_denseNetwork}.
%
In the figure, black dots represent cluster heads, the circles denotes the transmission ranges of those cluster heads.
Cluster members are not shown in the figure.
%Circles represent the transmission range of cluster head, within which CR nodes are absorbed in cluster.
\begin{figure}[h!]
  \centering
  \includegraphics[width=0.4\linewidth]{clusters_denseNetwork_2.pdf}
  \caption{Clusters formation in extremely dense CRN. Black dots are cluster heads, other cluster members are not drawn.}
  \label{clusters_denseNetwork}
\end{figure}
Let $l$ be the length of side of simulation plan square, and $r$ be CR's transmission radius.
Based on the aforementioned analysis and geometry illustration as shown in Figure~\ref{clusters_denseNetwork}, we can give an estimate on the maximum number of generated clusters, which is the product of the number of cluster heads in row and line, $l/r * l/r = l^2/r^2$.

Now we verify the estimation with simulation.
We distribute CR and primary users randomly on a square plain, $r$=10 and $l$=50.
Network density is increased by adding more CR users.
%We now have a look at how does the network density affect the cluster size when the transmission range is constant.
%This implicates when the cluster size is decided by the density of the network.
%As to SOC, the membership of one cluster is decided after a complex process, and the cluster size is roughly the same with one neighborhood.xxxx
%We can see from the example that although two neighbouring clusters can overlap greatly with each other, no cluster head will be covered by other clusters.
The number of formed clusters is shown in Figure~\ref{number_clusters_scale}.
With the increase of CR users in the network, network density increases linearly (the Y axis label is the number of neighbours), and the number of formed clusters also increases and approaches to the the upper bound of 25 which complies with the estimation.
For each network scale, simulation is run for 50 times and the confidence interval is 95\%.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{number_clusters_upperBound.pdf}
  \caption{The correlation between the number of formed clusters and network density. Note that the number of neighbours denotes the network density.}
  \label{number_clusters_scale}
\end{figure}

Both the analysis and simulation show that when applying ROSS, the cluster size increases with the increase of network density.
As a result, certain measures are needed to prevent the network size from increasing with the increasing network density.
This task falls to the cluster heads.
To control cluster size, cluster heads prune their cluster members.
The desired size $\delta$ is decided based on the capability of the CR users and the tasks to be conveyed.
Given desired size as $\delta$, cluster head excludes members sequentially, whose absence leads to the maximum increase of common channels within the cluster.

Note that ROSS generates clusters on based of cluster heads' neighbourhood, thus the $\delta$ is smaller than the average neighbourhood size.
As there are extensive overlaps between clusters, the threshold that the cluster size satisfies requirement should be larger than $\delta$.
%In practise, we set this threshold as $5*\delta/2$.
%This process ends when the size of resultant cluster is at most $5*\delta/2$ and at least one CCC is available.
This process ends when the size of resultant cluster is at most $\delta$ and at least one CCC is available.
This procedure is similar with that to guarantee CCCs in cluster, thus the algorithm can reuse Algorithm~\ref{alg_size_control_available_CCC}.

%Figure~\ref{fig2} shows the clusters formed in the example in Figure~\ref{fig1} when the desired cluster size is 3.

%Especially, it forster the connectivity between the clusters. It can do so, as the nodes with larger connectivity degree are not cluster heads but members. 
%As basin nodes have smaller $d_i$ compared with its cluster members, and many of the cluster members locate between the basin node and neighbor clusters,  %the bigger $d_i$ with bigger robustness of Social Connection, i.e, with bigger $d$ are located around cluster heads, 
%After clusters are formed, with aid of \textit{control channel rotation scheme} proposed in \cite{Lazos09}, intra and inter cluster communication is conducted and for each debable node (XXX Debatable nodes are not defined yet), the membership and channel availablity of the clusters concluding it is known.

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.6\linewidth]{figure2.pdf}
  \caption{Clusters formation after the first phase of ROSS. There are some nodes being debatable nodes, \ie belonging to more than one cluster.}
  \label{fig2}
\end{figure}

\subsection{Phase II - Membership Clarification}
%\subsubsection*{Problem Description}
After applying phase I of ROSS to the example in Figure~\ref{fig1}, the resulted clusters are shown in Figure~\ref{fig2}.
We notice nodes $A, B, D$ are included in more than one cluster. 
We refer these nodes as \textit{debatable nodes} as their cluster affiliations are not clear, and the clusters which include debatable node $i$ are called \textit{claiming clusters} of node $i$, and are represented as $S_i$.  
Actually, debatable nodes extensively exist in CRN with larger scale.
Figure~\ref{percentage_overlapping_node} shows the percentage of debatable nodes increases when the CRN network scales up.

Debatable nodes should be exclusively associated with only one cluster and removed from the other claiming clusters, this procedure is called cluster membership clarification.
We will introduce the solution for cluster membership clarification in the following.

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.7\linewidth]{percentage_overlapping_node.pdf}
  \caption{The percentage of debatable nodes after phase I of ROSS.}\label{percentage_overlapping_node}
\end{figure}

%In the second phase of ROSS, debatable nodes will chose only one cluster to reside.

%In particular, the un-affiliation of one debatable nodes from a cluster increasing the set $K_C$ of ICCs of cluster $C$ (at the cost of potentially decreasing $R_C$, the set of OCCs).

%\newtheorem{observation}{Observation}
%\label{observation}
%\begin{observation}
%If the number of nodes within a cluster decreases, the number of common channels will increase or keep constant.
%\end{observation}
%
%\begin{proof}
%Contradiction, To be continued
%\end{proof}
%From observation 1 we know that the procedure of membership clarification will increase the set of common channels for some clusters and accordingly strengthen the robustness of intra connectivity.

% % % % %	dependancy!
%An debatable node belongs to multiple clusters, and in the same time, it is possible that several debatable CR nodes locate within one same cluster. %Each debatable node tries to increase the sum of ICC of the clusters which it belong to. More specifically, 
%For a debatable node $i\in S_i$ after phase I, as to clarify its membership, it will choose one cluster $C\in S_i$ to stay and withdraw from the other clusters in $S_i$ with the consideration of increasing ICCs within $S_i$ by the largest margin.

\subsubsection{Distributed Greedy Algorithm}
%Debatable node $i$ is aware of all its claiming clusters in $S_i$. 
After Phase I, debatable nodes, \eg $i$ needs to decide which cluster $C\in S_i$ to stay, and thereafter leaves the rest others in $S_i$.
The principle for debatable node $i$ to choose one claiming cluster is to result in the greatest increase of common channels in all its claiming clusters.
%The set of available channels of one cluster are known by the debatable nodes which locate in that cluster. %this is finished 
Node $i$ communicates with all the cluster heads whose clusters of its claiming clusters, and is aware of the vector of common channels of the claiming clusters, then $i$ is able to know how many more common control channels will be in one certain claiming cluster if $i$ leaves that cluster.
Based on this calculation, $i$ decides on one claiming cluster to stay and leaves the other claiming clusters.
If there exists one cluster $C\in S_i$, if $i$ leaves this cluster brings the least increased common control channels than leaving any other claiming clusters, then $i$ chooses to stay in cluster $C$.
When there comes a tie in terms of the increase of common channels among multiple claiming clusters, $i$ chooses to stay in the cluster whose cluster head shares more common channels with $i$.
In case there are multiple claiming clusters demonstrating the same on the aforementioned metrics, node $i$ chooses to stay in the claiming cluster with smallest size.
IDs of cluster heads will be used to break tie if the previous rule could not decide on the unique cluster to stay.

Algorithm for debatable node $i$ to decide which claiming cluster to stay is described as Algorithm~\ref{alg4}.
To conduct Algorithm~\ref{alg4}, debatable node $i$ needs to know the necessary information about its claiming clusters, \ie $V_C$ (the set of available channels in $C$), $V_{H_C}$ (the set of available channels on $C$'s cluster head $H_C$) and $|C|, C\in S_i$ (sizes of $i$'s claiming clusters).
After deciding which cluster to stay based on Algorithm~\ref{alg4}, node $i$ notifies all its claiming clusters, and retrieves the updated information of the necessary information $V_C$, $V_{H_C}$, $|C|$, where $C\in S_i$.

This procedure raises the concern on the infinite chain effect that debatable nodes update their choices based on other debatable nodes' choices, and this process never ceases.
Consider the following example, where debatable node $i$ locates in cluster $C\in S_i$, and $C$ has more than one debatable node except for $i$.
Assuming that $i$ makes decision on which cluster to stay, which is followed by the other debatable nodes $j$ to decides its affiliation, and there is $j\in C\in S_i$.
The choice of $j$ may change $C$'s members, \ie $j$ leaves cluster $C$, which could possibly triggers node $i$ to alter its previous decision.
%To maximize the increase of common channel in clusters in $S_j$, $j$ either stays in $C$, or leaves cluster $C$ and stay another cluster in $S_j$.
%$j$'s decision changes $C$'s membership, which will affect $i$'s decision.
%Assume $i$ makes decision before $j$ and chooses to stay in $C$, as which brings the most common channels in $i$' claiming clusters, and then it is $j$' turn to choose cluster.
%If $j$ leaves $C$, the smaller cluster $C$ will possibly make $i$ to leave it and join another cluster.
%and the choice of $j$ to stay in $C$ or not possibly changes $C$'s membership and  which potentially further triggers node $i$ to alter its previous decision. 
Thence, we must answer this question raised when implementing ROSS-DGA.
%, and if it converges, how good such a distributed scheme performs. 
In the following we show that the process of membership clarification can be formulated into a singleton congestion game, and a equilibrium is reached after a finite number of best response updates.

\subsubsection{Bridging ROSS-DGA with Congestion Game}
\label{clustering:phaseII:game}
%In this part, we illustrate that when debatable nodes decide on the exclusive clusters to stay, in particular, the 
To formulate the problem of membership clarification for the debatable nodes in the context of a game, we observe this process from a different (or opposite) perspective. 
From the new perspective, the debatable nodes are regarded as isolated and don't belong to any cluster, which means their claiming clusters become their neighbouring clusters. 
Then for debatable nodes, the previous problem of deciding which clusters to leave becomes a new problem that which cluster to join.
In this new problem, debatable node $i$ (note now $i\notin S_i$) chooses one cluster $C$ out of $S_i$ to join if the decrement of common channels in cluster $C$ is the smallest in $S_i$, and the decrement of CCCs in cluster $C$ is $\sum_{C\in S_i}\Delta\vert K_C \vert=\sum_{C\in S_i}({\vert K_{C} \vert-\vert K_{C\cup i} \vert})$.
The relation between debatable nodes and claiming clusters is shown in Figure~\ref{debatable_nodes_claiming_cluster}.
The concern on convergence appears again as we have discussed in the previous subsubsection.
We will give proof on convergence under game theoretic framework.
\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.25\linewidth]{singletongame_png.png}
  \caption{Debatable nodes and claiming clusters}
  \label{debatable_nodes_claiming_cluster}
\end{figure}

Game theory is a powerful mathematical tool for studying, modelling and analysing the interactions among individuals.
A game consists of three elements: a set of players, a selfish utility for each player, and a set of feasible strategy space for each player. In a game, the players are rational and intelligent decision makers, which are related with one explicit formalized incentive expression (the utility or cost).
Game theory provides standard procedures to study its equilibriums~\cite{game_for_communication_01}.
In the past few years, game theory has been extensively applied to problems in communication and networking~\cite{Neel06analysisand, Wang_gtc_crn_survey_2010}.
Congestion game is an attractive game model which describes the problem where participants compete for limited resources in a non-cooperative manner, it has good property that Nash equilibrium can be achieved after finite steps of best response dynamic, \ie each player choose strategy to maximizes/minimizes its utility/cost with respect to the other players' strategies.
Congestion game has been used to model certain problems in internet-centric applications or cloud computing, where self-interested clients compete for the centralized resources and meanwhile interact with each other.
For example, server selection is involved in distributed computing platforms~\cite{Cloud_Computing_2010}, or users downloading files from cloud, etc.
In the following we will introduce an \textit{server matching}~\cite{kothari:congestion_serverMatching} problem to illustrate congestion game's application in communication systems.

In the following, we show that the decision of debatable nodes to clarify their membership can be mapped to the behaviour of the players in a \textit{player-specific singleton congestion game} when proper cost function is given.

The game to be constructed can be represented by a 4-tuple $\Gamma=(\mathcal{P},\mathcal{R},(\sum_i)_{i \in \mathcal{N}},\Delta\vert K^i_C \vert)$, where the elements in $\Gamma$ are given below,
%To make the model of this game more clear, we make some change to our original problem. Previously, the nodes in overlapping areas belong to more than one cluster, and our scheme is to remove them out of some clusters to increase the set of common channels within the cluster form which the mode leave. In the new model, we assume all the nodes in overlapping nodes don't belong any cluster and the problem become into how do these nodes decide which cluster to join.

%The components of the game are listed as follows,

\begin{itemize}
%	\item $\mathcal{D}=\left\{1,\ldots,n\right\}$, the set of players (debatable nodes).
	\item $\mathcal{P}$, the set of players of the game, which are the debatable nodes after phase I in our clustering problem.
%	\item $\mathcal{R}=\left\{1,\ldots,m\right\}$, the set of resources which player can choose, which are all the clusters in our model.
	\item $\mathcal{R} = \cup S_i, i\in \mathcal{P}$, denotes the set of resources for players to choose, $S_i$ is the set of claiming clusters of node $i$. $\mathcal{R}$ is the set of claiming clusters after phase I in our clustering problem.
	\item As to the strategy space $\sum_i$ of player $i\in \mathcal{N}$, there is $\sum_i \subseteq 2^{\left[S_i\right]}$. As one debatable node is supposed to choose one claiming cluster in our problem, thus only one resource is allocated for $i$, accordingly this congestion game is a singleton game.
	%when $i$ makes decision, only one resource (one claiming cluster) from the allowed resources is allocated.

	%\item We denote by $\mathcal{S}=\left(\mathcal{S}_1,\ldots,\mathcal{S}_n\right)\in \sum_1\times \cdots\times\sum_n$ the state of game where player $i$ plays strategy $\mathcal{S}_i\in \Sigma_i$.

	\item %For the clusters which are possible destination of debatable nodes, the decrement of common channels caused by different debatable node' join can be different because of the heterogeneity of channel availability within itself and on the debatable nodes. %furthermore, the sequence of debatable node's join can also alter the decrement. 
	The utility (cost) function $f(C)$ of resource $C\in \mathcal{R}$, (or to say $f(r)$ of resource $r \in \mathcal{R}$) is $\Delta\vert K^i_C \vert$ which represents the decrement of CCCs in cluster $C$ caused by debatable node $i$' joining in it.
	As to cluster $C\in S_i$, the decrement of CCCs caused by the enrolment of debatable nodes is $\sum_{i:C\in S_i, i\rightarrow C} \Delta\vert K^i_C \vert$. 
$i\rightarrow C$ means $i$ joins in cluster $C$.
Obviously this function is non-decreasing with respect to the number of nodes joining in cluster $C$.

The utility function is not purely decided by the number of players (debatable nodes) as that in a canonical congestion game, because in this game the channel availability on debatable nodes is different.
Given two same sized groups of debatable nodes, when the nodes are not completely the same (neither are the channel availabilities on these nodes), the cost happened on one claiming cluster could be different if the two groups of debatable nodes join in that cluster respectively.
%In a canonical congestion game, the cost (or pay off) is function of only the number of players occupying the resource, and is mono-
%In this new game, the cost function 
Hence, this game is called player specific.
In this game, every player greedily updates its strategy (choosing one claiming cluster to join) if joining in a different claiming cluster minimizes the decrement of CCCs $\sum_{i:C\in S_i} \Delta\vert K^i_C \vert$, player's strategy in the game is exactly the same with the behaviour of debatable node in membership clarification phase, as described by Algorithm~\ref{alg4}.

%	\item The Rosenthal's potential function \cite{Rosenthal} of this congestion game is given by:
%	\begin{equation*}
%	\phi(S)=\sum_{C\in\mathcal{R}} \sum_{i:C\in S_i} \Delta\vert K^i_C \vert   	
%   	%\sum_{i=1}^N \Delta^{i}_{p}(S)=\sum_{i=1}^N \sum_{r\in S_i}\Delta^{i}_{r}(t)	
%  	% \Delta =\sum_{i=1}^N w_i (x_i - \bar{x})^2 .
%	\end{equation*}
%All the players in this game greedily update their strategy to minimize the potential function (congestion), this process is exactly the same with the network behaviour under \textit{Distributed Greedy Algorithm}.

%	\item It is an asymmetric game because the sets of strategies shared by different players are different.
%	\item The total cost is: 
%\begin{equation*}
%   \sum_{i=1}^N \Delta^{i}_{p}(S)=\sum_{i=1}^N \sum_{p\in s_i} \Delta^{i}_{p}(n_p(S))
%  % \Delta =\sum_{i=1}^N w_i (x_i - \bar{x})^2 .
%\end{equation*}

%This is the global objective we want to minimize.
\end{itemize}

%Singleton congestion game is a special type of matroid game~\cite{Milchtaich1996111,}. 
%It is known that player-specific matroid congestion game admit pure equilibrium,

As to singleton congestion game, there exists pure equilibria which can be reached with best response update, and the upper bound of number of steps before convergence is $n^2*m$~\cite{Ackermann06purenash}, where $n$ is the number of players, and $m$ is the number of resources.
In our problem, the players are the debatable nodes, and the resources are the claiming clusters (or clusters heads).
Thus the upper bound of the number of steps can be expressed as $\mathcal{O}(N^3)$.
In fact, the actual number of steps is much smaller than $N^3$ as both $n$ and $m$ are considerably smaller than $N$.
The amount of debatable nodes is illustrated in Figure~\ref{fig2}, which is between 10\% to 80\% of the total number of CR nodes in the network.
The number of clusters heads, as discussed in the part of cluster size in Section~\ref{phaseI}, is decided by the network density and the CR node's transmission range.
Only a small part of the CR nodes become cluster heads, as in the example shown in Figure~\ref{number_clusters_scale}, the number of clusters is only 3.4\% to 20\% of the total number of CR nodes.

%and the number of steps towards \textit{Nash Equilibrium} is upper-bounded\footnote{Here we present this with modifying the original conclusion in \cite{Ackermann06purenash} according to our model.} by $ n^2\cdot m $. In our context, $n$ is the number of debatable nodes, $m$ is number of clusters in CRN, %$rk(\Gamma)$ of the matroid  is the cardinality of the maximal independent sets, which is 1 in the case of singleton game, 
%so the total time complexity to achieve the \textit{Nash Equilibrium} using greedy approach is 	.
%%(XXX Just mention after this complexity result the relationship to the system mdeol XX)
%This is upper-bounded (in the worst case) by $O(\vert I\vert^3)$. 
%Based on above model and analysis, phase II converges is Algorithm~\ref{alg4} is run by debatable nodes. 
%Although the game version of DGA can achieve \textit{Nash Equilibrium}, the whole scheme can possibly obtain sub-optimal result.    %, furthermore,this stable state is a local minimum of the global decrement function.
%\todo[inline]{The number of steps, or the upper bound of steps in convergence needs a formal proof}

\subsubsection{Distributed Fast Algorithm (DFA)}
%The convergence speed of DGA is large recalling that the number of steps is of $\mathcal{O}(N^3)$.
We propose a faster version of ROSS, which is ROSS-DFA, which is especially suitable for CRN where channel availability change dynamically and re-clustering is necessary.
In DFA, debatable nodes regard their claiming clusters includes all their debatable nodes, thus the membership of claiming clusters is static and debatable nodes can make decisions simultaneously without considering the change of membership of their claiming clusters.
To run ROSS-DFA, debatable node executes only one loop in Algorithm~\ref{alg4}.

Now we apply the two versions of ROSS to the toy network in Figure \ref{fig2}, which has finished cluster head selection.
In the network, node $A$'s claiming clusters are cluster $C_C, C_H\in S_A$, their members are $\{A,B,C,D\}$ and $\{A,B,H,G\}$ respectively. 
The two possible strategies of node $A$'s clarification is illustrated in Figure \ref{fig3}.
In Figure \ref{AinC}, node $A$ staying in $C_C$ and leaving $C_H$ brings 2 more CCC into $S_A$, which is more than that brought by another strategy showed in \ref{AinH}.
After the decisions made similarly by the other debatable nodes $B$ and $D$, the final clusters formed are shown in Figure~\ref{fig4}.

%Using DFA in phase II, the time complexity is decreased drastically to 1. Thus, the total complexity of ROSS-DFA is $|I|$, while, ROSS-DGA's complexity is $|I|^3$ in the worst case.

\begin{figure}[h]
\centering
\subfigure[Node A stays in cluster $C_C$, quits $C_H$, $\Delta\vert K_{C_C}\vert+\Delta\vert K_{C_H}\vert=2$]{
\includegraphics[width=0.435\linewidth]{figure4AinC.pdf}
\label{AinC}
}
\hspace{.15 in}
\subfigure[Node A stays in cluster $C_H$, quits $C_C$, $\Delta\vert K_{C_C}\vert+\Delta\vert K_{C_H}\vert=1$]{
\includegraphics[width=0.435\linewidth]{figure4AinH.pdf}
\label{AinH}
}
\caption[]{Membership clarification: possible cluster formations decided by node A's different choices} %\subref{node A in $C_C$}, \subref{node A in $C_H$}}
\label{fig3}
\end{figure}

\begin{comment}
As an example, when node A comes to decide which cluster to stay, the memberships of relevant clusters, like $C_C$ and $C_H$, are $\{C,B,D,A\}$ and $\{H,B,G,A\}$ respectively. Before the other two debatable nodes B and D making their belonging clear, cluster $C_C$ and $C_H$ have them in the same time. So node A can decide which cluster to belong to without considering other debatable nodes' action. There are two strategies for node A, which is illustrated in Figure \ref{fig3}. Because staying in cluster $C_C$ brings in more common channels within relevant clusters, node A finally choose cluster $C_C$ to stay and caveat from cluster $C_H$. The membership of $C_H$ is updated in the same time. Node B and D undertake the same process and the clusters are formed finally as Figure \ref{fig4} shows.

Because debatable nodes can conduct membership clarification abased on static membership information of relevant clusters, thus no iteration happens in this process. The time complexity of this algorithm is only decided by the number of debatable nodes, which is maximal $O(\vert I\vert)$.

As an example, when node A comes to decide which cluster to stay, the memberships of relevant clusters, like $C_C$ and $C_H$, are $\{C,B,D,A\}$ and $\{H,B,G,A\}$ respectively. Before the other two debatable nodes B and D making their belonging clear, cluster $C_C$ and $C_H$ have them in the same time. So node A can decide which cluster to belong to without considering other debatable nodes' action. Figure \ref{AinC}. Because staying in cluster $C_C$ brings in more common channels within relevant clusters, node A finally choose cluster $C_C$ to stay and retreat from cluster $C_H$. The membership of $C_H$ is updated in the same time. Node B and D undertake the same process and the clusters are formed finally as Figure \ref{fig4} shows.
\end{comment}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.5\linewidth]{final_clustering_ross.pdf}
  \caption{Final formation of clusters, CCCs for each cluster is shown.}
  \label{fig4}
\end{figure}

\section{Centralized Clustering Scheme}
\label{centralized_scheme}

%paper given by james is useful which provides a survey from the perspective of wsn!

%\todo[inline]{check}
The centralized clustering scheme aims to form clusters with desired sizes, meanwhile the total number of common control channels of all clusters is maximized.
In the following, we refer this problem as \textit{centralized clustering}, and the problem definition is as follows,

\begin{mydef}
\label{def_centralized_clustering}
\textit{Centralized clustering in CRN.}

Given a cognitive radio network $\mathcal{N}$ where nodes are indexed from 1 to $N$ sequentially.
Based on certain correlation, certain secondary users constitute one cluster $C$.
$1\leq |C| \leqslant k$ where $|C|$ is the size of cluster $C$ and $k$ is a positive integer.
We name the collection of such clusters as $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$ (the subscript $i$ is the unique index of cluster in $\mathcal{S}$, not the ID of cluster head of that cluster), $\mathcal{S}$ satisfies the following properties: $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$ and $V_{C_i}\neq \emptyset$ for any $i$ which satisfies $1\leq i \leq |\mathcal{S}|$.

Following condition distinguishes the centralized clustering problem discussed in this paper.
The number of common control channels is $|V_{C}|$ if $|V_{C}|>1$, and is zero when $|V_{C}|=1$.
We use $f$ to denoted this new number of CCCs. 
The question of this problem is to find a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, so that $\bigcup_{C_j\in \mathcal{S}'} C_j = N$, and $C_j'\cap C_j =\emptyset$ for $C_j', C_j\in \mathcal{S}'$, so that $\sum_{C\in \mathcal{S}'} f$ is maximized.
% when $|C|>1$, and $f(\cdot)=0$ when $|C|=1$.
%As to $f(\cdot):z\rightarrow z$, under this problem setting, if only number of common channels are given consideration, only singleton clusters will be preferred, which contradicts to our goal of clustering CR nodes together, thus we choose $f(\cdot)= |V_{C}|\cdot |C|$, the product of number of common channels and cluster size.
The decision version of centralized clustering in CRN is to ask whether exist $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C\in \mathcal{S}'} f \geqslant \lambda$ where $\lambda$ is a real number.% in stead of to maximize $\sum_{C\in \mathcal{S}'} f$.
\end{mydef}

%The decision version of \textit{weighted exact cover problem}: 
%Given an universe $U$, and collection $S=\{s_1, s_2, \ldots, s_m\}$ where each subset $s_i\subseteq U$ and is given a weight $w_i$, whether there exists a collection of subsets $\mathcal{C}$ and constant number $\lambda$, so that the union of $\mathcal{C}$ equals to $U$, $s_j\cap s_{j'} = \emptyset$ for different $j$ and $j'\in \{1,2,\ldots, m\}$, and $\sum_{i\in J} w_i \geq \lambda$.
\subsection{Complexity of Clustering Problem}
In the following part of this section, we will discuss the complexity of centralized clustering problem and provide a centralized solution for it.

\begin{theorem}
\label{theorem1}
CRN clustering problem is NP-hard, when the maximum size of clusters $k\geqslant 3$.
%Assume a CRN can be represented by a connected graph, and there is at least one common channel between any pair of neighbours, then forming at least two CR nodes into one cluster is NP-complete.
\end{theorem}
The proof is in Appendix~\ref{proof_theorem1}.

\subsection{Centralized Optimization}
\label{centralized_opt}
%Exact cover problem can be solved with Knuth's Algorithm X~\cite{dancingLinks_Knuth} as it finds out all the instances of exact cover, then we can choose the one with the biggest sum of weights. 
As there is no efficient algorithm to solve clustering problem in CRN, we propose a centralized optimization where the objective function and the constraints are heuristic, then we adopt binary linear programming to solve the problem.
%Note that binary linear programming is in NP-complete.

%This example indicates the chose of $\mathcal{C}$ plays an important role on the resultant clustering strategy.
%Meanwhile, it provide a chance to constrain the cluster size by putting groups with desired sizes into $\mathcal{C}$.

%the maximum size of $S$ is the \textit{Bell number} of $N$, and $S$ contains the conditions cluster .
%In this case, the resultant $\mathcal{C}$ is composed with all the singleton clusters, \ie, the cluster which contains one node, and the objective is -38.

%it is possible that there doesn't exist combination of clusters with the same cluster size.
%We thus list all possible clusters whose sizes are from 2 to one certain number \footnote{this number of decided by the density of CR network, along with the occupation of PUs. We set this number as cluster size of the biggest cluster ever appears when conducting distributed schemes.}, and check each combination of clusters to find the best covering of network on the aspect of number of ICCs per cluster.
%The complexity of computation is thus \bigO$(N^\delta)$, $\delta$ is the preferred cluster size.

%The global optimal clustering scheme with respect to the number of common channels is investigated to show the gap with the distributed schemes.

%We apply this centralized scheme on a network with network size $N$ and cluster size $\delta$.
%There is $N\mod \delta=0$, and the expected number of clusters is $C = N/\delta$.
%These tailored parameters don't harm the validity of the performance gap between the two schemes.

Given a CRN $\mathcal{N}$ and desired cluster size $\delta$, we obtain a collection of clusters $\mathcal{G}$ which contains all the \textit{legitimate} clusters, and the sizes of these clusters are $1,2,\ldots,\delta$.
Legitimate clusters are the clusters which satisfy the conditions in Section~\ref{def_cluster}. 
Note that the legitimate clusters include the singleton ones, which guarantees the partition of any network is feasible.

With $N=|\mathcal{N}|, G=|\mathcal{G}|$, we construct a constant $G\times N$ matrix $Q_{G\text{x}N}$. 
The element of matrix $Q$ is $q_{ij}$, where the subscript $i$ denotes a legitimate cluster, and $j$ denotes a CR node, which can be seen as the node ID. 
Note that $C_i$ means $i$th cluster in the collection $\mathcal{G}$, doesn't denote the cluster where cluster head is $i$, this notation is only valid in this subsection.
There are $i\in \{1,2,\cdots,G-1, G\}$, and $j\in \{1,2,\cdots,N-1, N\}$.
Element $q_{ij}= k_{C_i}$ if node $j\in C_i$, and $q_{ij}= 0$ if $j\notin C_i$.
In other words, each non-zero element $q_{ij}$ denotes the number of CCCs of the cluster $i$ where node $j$ resides.

\begin{figure}[ht!]
\centering
Q = \bordermatrix{~ 		& 1 	& 2 	& 3 	& \cdots & j & \cdots	& N-1 	& N	\cr
                  1 	& k_{C_1} 	& k_{C_1} 	& 0 	& \cdots & \cdots &\cdots	& 0 	& 0	\cr
                  2 	& k_{C_2} 	& 0 	& k_{C_2} 	& \cdots & \cdots & \cdots 	& 0 	& 0	\cr
				\vdots  	&\vdots & 	 	& 		&  \vdots		& 		& \vdots \cr
				i 	& 0 	& k_{C_i} 	& 0 	& \cdots  & \cdots & \cdots 	& k_{C_i} 	& 0	\cr
				\vdots  	&\vdots & 	 	& 		&  \vdots & \cdots & \cdots 		& 		& \vdots \cr
				\vdots 	& \vdots  	& 0 	& 0 	& \cdots & \cdots & \cdots 	& k_{C_i'} 	& 0	\cr
				G  	& k_{C_G} & \cdots	 	& 		&  \vdots	& \cdots & \cdots& 		& \vdots \cr}	
\caption{An example of Matrix Q, its rows correspond to all legitimate clusters, and columns correspond to the CR nodes in the CRN.}
\label{xx}
\end{figure}

We build a $G\times N$ binary variable matrix $X$, which illustrates the clustering strategy.
The element of matrix $X$ is binary variable $x_{ij}, i=1, \ldots, G, j=1, \ldots, N$.
$x_{ij}=1$ denotes cluster $i$ is one partition in the clustering solution, $x_{ij}=0$ means this partition is not adopted.
%Note that matrix $Q$ contains only constant elements, and matrix $X$ contains only binary variables.
Now, we can formulate the optimization problem as follows,

\begin{equation}
\begin{aligned}
     &\min\limits_{x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^G (-x_{ij}q_{ij} + (1-w_i)*p) \\
     &\text{subject to}   && \Sigma_{i=1}^G x_{ij} = 1, for \forall j=1, \ldots, N \\
   &&& \Sigma_{j=1}^N x_{ij} = |C_i|*(1-w_i), for \forall i=1, \ldots, G \\
   &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
   &&& i\in \{1,2, \cdots G\}, \hspace{0.3cm} j\in \{1,2,\cdots N\}
\notag
\end{aligned}
\end{equation}
The objective is the sum of two parts, the first part is the sum of products of cluster size and the corresponding number of CCCs.
We notice that the first part is the metric adopted by the scheme SOC~\cite{Lazos09}.
The second part is the \textit{punishment} for choosing the clusters whose sizes are not $\delta$.
In fact, the second part is particularly designed to eliminates the drawbacks of SOC, \ie a large number of singleton clusters, or a few very large clusters which access affluent unlicensed spectrum.
In practical computation, we minimize the opposite of the sum of the products of cluster size and the corresponding number of CCCs, thus the punishment is positive.

The first constraint restricts each node $j$ to reside in exactly one cluster.
The second constraint regulates that when $i$th legitimate cluster $C_i$ chosen, the number of elements which equal to 1 in the $i$th row is $|C_i|$.

Now we explain how does the mechanism of the punishment in the objective work. 
$w_i$ is an auxiliary binary variable, which denotes whether cluster $C_i$ is chosen by the solution, in particular, 
$$
w_i = \left\{ \begin{array}{rl}
0 &\mbox{if $i$th legitimate cluster $C_i$ is chosen} \\
1 &\mbox{if $i$th legitimate cluster $C_i$ is not chosen} \\
\end{array} \right.
$$
%$w_i=0$ denotes $i$th legitimate cluster $C_i$ is chosen in the solution, and $w_i=1$ means $i$th legitimate cluster is not chosen.
and $p$ is defined as follows,
%$\texttt{cost($\delta$)}$
$$
p = \left\{ \begin{array}{rl}
0 &\mbox{ if $|C_i|=\delta$} \\
\alpha_1 &\mbox{if $|C_i|=\delta-1$} \\
\alpha_2 &\mbox{if $|C_i|=\delta-2$} \\
\dots
\end{array} \right.
$$
where $\alpha_i>0$ and increases when $|C_i|$ diverges from $\delta$.
Because of $w_i$, any chosen cluster brings certain \textit{punishment}.
Function $p$ denotes that when the chosen cluster's size is desired size $\delta$, the punishment is zero.
When the chosen cluster's size diverges from $\delta$, the objective function suffers \textit{loss}.
%
Choice of $\alpha_i$ affects the resultant clusters.

%\begin{figure}[ht!]
%\centering
%\includegraphics[width=0.45\linewidth]{example.JPG}
%\caption{Example of Matrix Q in a 6-node network, cluster size is set as 2}
%\label{xx}
%\end{figure}

%\begin{figure}[ht!]
%  \centering
%  \includegraphics[width=0.5\linewidth]{figure5final.pdf}
%  \caption{Final cluster formation.}
%  \label{fig4}
%\end{figure}

This is a integer linear optimization problem, which is solved by function $bintprog$ provided in MATLAB.
Note that the proposed centralized solution is heuristic.
There are two reasons for pursuing the heuristic scheme, first, the problem of centralized clustering is NP hard, and there is no efficient solution to solve it.
The second reason is, the collection of legitimate clusters is dependant on the network topology and spectrum availability in the network, thus to each specific CRN, the space of solution is different.

\subsubsection{Example of the Centralized Optimization}
We look into how it the centralized scheme perform in the toy example of the CRN in Figure~\ref{fig1}.

We let the cluster size $\delta$ to be 3.
A collection of clusters $\mathcal{G}$ is obtained, which contains all the clusters satisfying the conditions of cluster in Section~\ref{def_cluster} and the sizes of clusters are 1, 2 or 3. 
$\mathcal{G}=\{\{A\}, \{B\},\dots,\{B,C\},\{B,A\},\{B,H\},\cdots,\{B,A,C\},$\\$\{B,H,C\}, \{A,D,C\},\cdots\}$, $G = |\mathcal{G}|=38$.
$\alpha_1$ and $\alpha_1$ are set as 0.2 and 0.8. 
The clustering result of centralized programming is shown in Figure~\ref{fig:final_clustering_LP}.

The formed clusters are $\{\{D,E,F\},\{A,C,G\},\{H,G\}\}$, the numbers of CCCs are 2, 3, 3.
The resulted clustering solutions from ROSS-DGA/DFA and SOC are shown in  Figure~\ref{fig4} and Figure~\ref{fig:final_clustering_soc} respectively.%, clusters are $\{A,B,C,D,G\},\{E,F\},\{H\}$, and the numbers of CCCs are 2, 3, 4.
%The solution resulted from ROSS-DGA is $\{\{B,H,G\},\{C,A\},\{D,E,F\}\}$ (in Figure~\ref{fig4}), the numbers of CCCs are 2, 4, 2.
%ROSS-DFA generates the same result with ROSS-DGA in this example.	
As to the average number of CCCs, the results of ROSS, centralized and SOC are 2.66, 2.66, and 3 respectively. 
Note there is one singleton cluster $C_H$ generated by SOC, which is not preferred.
When the singleton cluster $\{E\}$ is excluded, the average number of common channels of SOC drops to 2.5. 
\begin{figure}[ht]
\begin{center}
\subfigure[Resulted from SOC]{\includegraphics[width=0.435\linewidth]{final_clustering_soc}\label{fig:final_clustering_soc}}
\hspace{0.15 in}
\subfigure[Resulted from Centralized Optimization]{\includegraphics[width=0.435\linewidth]{final_clustering_LP}\label{fig:final_clustering_LP}}
\end{center}
\caption{Final clusters formed in the example CRN network from Figure~\ref{fig1}}
\label{fig:final_clustering}
\end{figure}

\section{Performance Evaluation}
\label{performance}
In this section, we evaluate the performances of all the variants of ROSS, \ie ROSS-DGA and ROSS-DFA, and that with cluster size control features.
The latter is referred as ROSS-x-DGA/ROSS-x-DFA, where x is the desired cluster size.
We choose SOC as comparison scheme.
To the best of our knowledge, SOC~\cite{Lazos09} is the only work emphasizing on the robustness of clustering structure from all previous work on clustering in CRN. The authors of~\cite{Lazos09} compared SOC with other schemes based on the average number of common channels within each cluster, on which SOC outperforms other schemes by 50\%-100\%. This is because the schemes except for SOC are designed either for ad hoc network without consideration of channel availability~\cite{Basagni99}, or for CRN  but just considering basic connection among CR nodes~\cite{Zhao07}. Hence, we only compare the two versions of our scheme ROSS-DGA and ROSS-DFA with SOC to show the merits of ROSS, and also compare with the centralized scheme to see the gap with the global optima. 
In particular, we will investigate the following metrics,
\begin{itemize}
\item \textit{Average number of common channels per non-singleton cluster.} 
This metric shows the robustness of the current non-singleton clusters.
Non-singleton cluster refers the cluster whose cluster size is larger than 1, and can also be seen as unclustered node.
Note that this metric along is biased and misleading, because the CR nodes with more channels could be formulated as singleton clusters.
This happens in SOC solution, whose objective is to improve the average number of common channel over \textit{all} clusters, \ie including the singleton clusters, thus many CR nodes with more channels are turned into clusters.
%As we try to look into the robustness of clusters of CRs, we exclude those singleton clusters.

\item \textit{Number of unclustered CRs with moderate and vigorous intensity of primary users' activities.}
This is a straight forward metric which reflects the robustness of clusters, as this metric directly shows how many nodes can make use of the cluster structure.
With this metric, we investigate the performance of different schemes under different availability of spectrum in the CRN.
When we vary the intensity of primary users' activity, \eg from low to medium level by increasing the number of primary users, this metric is the antonym of \textit{survival rate}, \ie, how many nodes are still within a certain cluster when some clusters have collapsed due to the newly added primary users.

\item \textit{Cluster sizes.}
Specific clusters size is pursued in many applications due to energy preservation and the system design ~\cite{clustering_globecom11}.
We will present the distribution of CRs residing in the formed clusters, and the number of generated clusters through multiple simulations.

\item \textit{Amount of control messages involved.}

\end{itemize}

The simulation is conducted with C++. 
Certain number of CRs and PUs are deployed in a 2-dimensional Euclidean space.
We adopt the unit disk model~\cite{unitDiskModel}, and both CR users and PU have fixed transmission ranges respectively.
Complying with the system model, the CR node residing within another CR node's transmission range is seen as neighbour of that CR node.
If CR node locating within one PU's transmission range, the CR node is not allowed to use the channel which is being used by that PU.
The number of licensed channels is 10, each PU is operating on each channel with probability of 50\%.
All primary and CR users are assumed to be static during the process of clustering.

Simulation is divided into two parts, in the first part, we investigate the performance of centralized scheme, and the gap between the distributed schemes with the centralized scheme.
The simulation of this part is conducted in a small network, as there is no polynomial time solution available to solve the centralized problem.
In the second part, we investigate the performance of the proposed distributed schemes thoroughly in the networks with different scales and densities.

\subsection{Centralized Schemes vs. Decentralized Schemes}
10 primary users and 20 CR users are dropped randomly (with uniform distribution) within a square area of size $A^{2}$, where we set the transmission ranges of primary and CR users to $A/3$.
There are 10 available channels. 
With this setting, the average number of neighbours of one CR user is 4.8.
Each primary user randomly occupies one channel, and CR users are assumed to be able to sense the existence of primary users and identify available channels.
When clustering scheme is executed, around 7 channels are available on each CR node.
The desired cluster size is 3, the parameters used in the \textit{punishment} for choosing the clusters with undesired sizes are set as follows, $\alpha_1 =  0.4$, $\alpha_2 =  0.6$.
Performance results are averaged over 50 randomly generated topologies with equal parameters.
The confidence interval shown in figure corresponds to 95\% confidence level.

\subsubsection{Number of Common Control Channels in Non-singleton Clusters}
\label{ccc_20}
%We first have a look at the average number of common channels per non-singleton cluster.
Figure~\ref{ccc_per_nonsingleton} shows the average number of common channel of non-singleton clusters, as the singleton clusters (in other words unclustered nodes) don't execute any functionalities of clusters, which are has be discussed in Section~\ref{intro}.
From Figure~\ref{ccc_per_nonsingleton}, we can see centralized schemes outperform distributed schemes.
SOC achieves the most number of CCC than all the variants of ROSS.
The reason is, SOC is liable to group the neighbouring CRs which share the most abundant spectrum together, no matter how many of them are, thus the number of CCC of the formed clusters is higher.
But this method leaves considerable number of CRs which have less spectrum not in any clusters.
As to the variants of ROSS, the procedure of debatable nodes greedily looking for better affiliation improves the number of CCC, thus ROSS-DGA with and without size control outperform ROSS-DFA and its size control version respectively.
We also notice that, the size control feature doesn't affect the number of CCC for both ROSS-DGA and ROSS-DFA.
This is because the desired cluster size happens to be the average size of clusters generated by ROSS-DGA and ROSS-DFA, then the size control functionality doesn't play effect to increase the number of CCCs.

\subsubsection{Survival Rate of Clusters with Increasing Primary Users}
With the number of PUs in CRN increases, or their operation becomes more intensive, some CCCs will no longer be available.
If there is no common control channels available any more because of the new added PRs, the cluster is regarded as destroyed and the former cluster member CRs become unclustered CRs or in other words singleton clusters.

We investigate the robustness of the formed clusters when they co-exist with primary users whose intensity of activities are varying.
After the clusters are formed under the influence of the initial 10 PUs, extra 100 PUs are added sequentially to the network.
%The transmission range and channel occupancy of the new PU is the same with the previous ones, \ie transmission range is $A/3$, and one channel out of 10 is randomly chosen to operate.
Figure~\ref{singleton_clusters} shows the number of unclustered CRs with the increasing number of PUs.%, which indicates the vulnerability of clusters under varying availability of licensed spectrum.
%
We draw three conclusions corresponding to three comparisons shown in this figure,
\begin{itemize}
\item Centralized scheme with cluster size of 2 generates the most robust clusters, and SOC results in the most vulnerable clusters.
When the desired cluster size is 3, the centralized scheme performs similarly with the variants of ROSS.
The reason that centralized scheme with cluster size of 3 does not completely excel variants of ROSS is due to the favourable achievement of it: the uniformly sized clusters.
As distributed schemes, variants of ROSS generate considerable amount of smaller clusters which are more likely to survive when PUs' activities become intense.
The comparison on cluster sizes will be given in details in~\ref{cluster_size}.
% when the number of PRs is 10$\sim$30, when number of PUs is 30$\sim$60, same amount of unclustered CRs are generated with variants of ROSS.
%When there are 75 and more new PRs, centralized scheme with cluster size of 3 results in more unclustered CR nodes than variants of ROSS.

\item Greedy algorithm improves survival rate. 
ROSS-DGA improves the survival rate of ROSS-DFA, so does ROSS-x-DGA against ROSS-x-DFA.
This complies with the observation in Figure~\ref{ccc_per_nonsingleton}.
As the debatable CRs greedily update their affiliation with claiming clusters, and the metric for updating is the maximum increase of CCCs of the demanding clusters, the average number of CCCs in non-singleton clusters is improved. 
%Meanwhile, sizes of more clusters become smaller also contributes more robustness.

\item ROSS with size control is better than the other two distributed schemes.
Conducting size control improves both ROSS-DGA and ROSS-DFA's performance when the number of new PUs is greater than 50.
The size control decreases the clusters size and makes the clusters more robust when against PUs' activity.

\end{itemize}

%\begin{figure}[h!]
%  \centering
%  \includegraphics[width=0.8\linewidth]{ccc_20.pdf}
%  \caption{Number of common channels for non-singleton clusters, the numbers in the names of schemes annotate the desired cluster size.}
%  \label{ccc_per_nonsingleton}
%\end{figure}
%
%
%\begin{figure}[h]
%  \centering
%  \includegraphics[width=0.8\linewidth]{survival_rate_20.pdf}
%  \caption{Number of CRs which are not included in any clusters}
%  \label{singleton_clusters}
%\end{figure}

\subsubsection{Cluster Size Control}
\label{cluster_size}
%\begin{figure}[h]
%  \centering
%  \includegraphics[width=0.8\linewidth]{cdf_clusterSize_20.pdf}
%  \caption{Cumulative distribution of CRs residing in clusters with different sizes.}
%  \label{size_control}
%\end{figure}

\begin{figure*}[t]
\begin{multicols}{3}
    \includegraphics[width=\linewidth]{ccc_20.pdf}\par\caption{Number of common channels for non-singleton clusters}\label{ccc_per_nonsingleton}
    \includegraphics[width=\linewidth]{survival_rate_20.pdf}\par\caption{Number of CRs which are not included in any clusters}\label{singleton_clusters}
    \includegraphics[width=\linewidth]{cdf_clusterSize_20.pdf}\par\caption{Cumulative distribution of CRs residing in clusters with different sizes}\label{size_control}
\end{multicols}
\caption{Comparison between the distributed and centralized clustering schemes in a small network ($N$ = 20)}
\label{compare_dis_centralized}
\end{figure*}

Figure~\ref{size_control} depicts the empirical cumulative distribution of the CRs residing in certain sized clusters in 50 runs.
The centralized schemes are able to form clusters which satisfy the requirement on cluster sizes strictly.
When the desired size is 2, each generated cluster has two members, whereas when the desired size is 3, about 15\% CRs are formed into 2 node clusters.
Both of ROSS-DFG and ROSS-DFA with size control feature also obtain clusters with homogeneous sizes.
%When ROSS-3-DFA is applied, most number of CRs are in 3 node clusters, nevertheless, slightly less nodes are found in 2 node and 4 node clusters, there are also considerable number of singleton clusters.
%ROSS-3-DGA decreases the clusters sizes and results in more 2 node clusters, the second most CRs are found in 3 node clusters.
The sizes of clusters generated by ROSS-DGA and ROSS-DFA are disperse, but appear better than SOC, i.e., the 50\% percentiles for ROSS-DGA, ROSS-DFA and SOC is 4.5, 5, and 5.5, and the 90\% percentiles for the three schemes are 8, 8, and 9.
%Figure~\ref{size_control} shows distributed clustering schemes are not able to control cluster sizes perfectly, but ROSS-DGA and ROSS-DFA eliminate the clusters whose size diverges largely with the desired one, \ie single node clusters and clusters with size of 13 and 14.
Note ROSS-DGA and ROSS-DFA with size control feature generate 10\%-20\% singleton clusters, which is due to the cluster pruning discussed in section~\ref{cluster_pruning}, whereas, without size control, only 3\% nodes are in singleton clusters.
When applying SOC, 10\% of nodes are in singleton clusters.

\subsubsection{Control Signalling Overhead}
%Different from the clustering schemes proposed in ~\cite{LIU_TMC11_2, clustering_globecom11}, 
%There are two phases for any variants of ROSS.
%Clusters are formed in the first phase, in the second phase, cluster membership is decided so that each node only resides in one cluster.
%Control message exchanges between CR nodes are involved in both phases.

In this section we compare the amount of control messages generated in different clustering schemes, \eg centralized scheme, ROC, and the variants of ROSS.

In order to highlight the amount of control signalling only for clustering, we omit the process of neighbourhood discovery, which is premise for all clustering schemes.
According to~\cite{complexity_aggregation_2011}, the message complexity is defined as the number of messages used by all nodes.
To have the same criterion to compare the overhead of signalling, we count \textit{the number of transmissions of control messages}, without distinguishing they are sent with broadcast or unicast.
This metric is Synonymous with \textit{the number of updates} discussed in Section~\ref{ross}.

As to ROSS, the control messages are generated in both phases.
In the first phase, %every CR node decides whether it is cluster head by comparing its spectrum robustness with its neighbours.
When a CR node decides itself to be the cluster head, it forms one cluster with its neighbourhood, 
each cluster head broadcasts one message containing its ID, cluster members and the set of CCCs in its cluster.
%As to ROSS with size control feature, there are same amount of cluster heads with ROSS without enabling size control feature, and the cluster head broadcasts the available channels of the pruned cluster.
In the second phase, %membership clarification of debatable nodes is conducted.
debatable node informs its claiming clusters by broadcasting its affiliation, and the claiming cluster's cluster head broadcasts message about its new cluster if its cluster's members are changed.
The total number of times for all CR nodes to send control messages, \ie the total number of decisions related with clustering functionality, has been analysed in the part of convergence speed in Theorem~\ref{clustering:theorem} and Section~\ref{clustering:phaseII:game} respectively.

Comparison scheme SOC involves three rounds of execution. 
In the first two rounds, every CR node maintains its own cluster and seek to integrate neighbouring clusters, or join in one of them.
The final clusters are obtained in the third round. 
In each round, every CR node is involved in comparisons and cluster mergers.
%Comparing with the second phase of ROSS, only debatable nodes to communicate with cluster heads to clarify their membership.
%The signalling overhead for centralized scheme comes from two processes, the the process of collecting information to the centralized controller, and the process that the controller spreads the clustering result to all the CR nodes.

As to the centralized scheme, except for the calculation in the centralized control device, it also involves two phases of control message transmission.
The first phase is information aggregation, in which every CR node's channel availability and neighbourhood is sent to the centralized controller.
The second phase is broadcasting, where the final clustering solution is disseminated over the network to every CR node.
%As basic communication primitive for wireless networks, 
We adopt the algorithm proposed in~\cite{Efficient_broadcasting_gathering_adhoc} to broadcast and gather information as the algorithm is simple and self-stabilizing.
This scheme needs building a backbone structure to support the communication, we use our generated cluster heads as the backbone and the debatable nodes as the gateway nodes between the backbone nodes.
As the backbone is built once and can support transmission for multiple times, the messages involved in the clustering process are not included.
Every CR node can be informed if the cluster heads broadcast the message sent from the controller or other cluster heads, then the number of transmission is $h+m$.
As to information gathering, we assume that every cluster member sends the spectrum availability and its ID to its cluster head, which further forwards or the message to the controller.
The number of transmission for information gathering is $N$.
%As we adopt a simplified communication model, node's transmission is not influenced by collision or interference, 
%Our simulation doesn't consider the behaviour in the physical layer, 
The number of transmission is depicted in Figure~\ref{control_msg}.
Note that the curve for the centralized scheme is from theoretical analysis, which is $h+m+N$ as discussed beforehand.
Note the overhead involved to construct the backbone (clusters) is not included.
%Assume we use OSPF~\cite{BCJ10} to aggregate and disseminate information, then the best and worst complexity for is $\mathcal{O}(E)$, where $E$ is the number of edges in the graph which corresponds to the network.
%The minimum number of edges is $n-1$ when the nodes form a line and each node has at more two neighbours, and the maximum number is $N*(N-1)/2$ when the nodes form a complete graph.
%Thus the best message complexity of the centralized scheme is $\mathcal{O}{(N)}$ and the worst is $\mathcal{O}{(N^2)}$.

%1. update membership to form X1, 
%2. broadcast new X1, form new X2
%3. broadcast X3

%The complexity parameters are the number of nodes $n$ in network, number of clusters $h$.
The message complexity, quantitative analysis of the number of messages, and the size of control messages are shown in Table \ref{tab_overhead}.
Some notations are written as follows,  $h$: number of cluster heads, $m$: number of debatable nodes, $d$: number of demanding clusters, $D(s)$: the maximum distance between centralized controller and CR users.

%\begin{table}[hc]
%\centering
%\caption{Singalling overhead. Notations: $n$-number of CR nodes in CRN, $h$-number of cluster heads, $m$-number of debatable nodes, $c$-number of demanding clusters.}\label{tab_overhead}
%\begin{tabular}{|p{2.2 cm}|p{1.5 cm}|p{3.7 cm}|}
%\hline
% Scheme 					&   Number of transmissions 					& Content of message \\ \hline
% ROSS-DGA, ROSS-x-DGA 		&   $h+2*m^2c$ (upper bound)
%				& $ID_{H_C}$ and $V_C$ for $h+m^2c$ times, notification to join in one cluster for $m^2c$ times					\\ \hline
% ROSS-DFA, ROSS-x-DFA 		&   $h+ 2m$	 (upper bound) 						& $ID_{H_C}$ and $V_C$ for $h+m$ times, notification to join in one cluster for $m$ times	 					\\ \hline
% SOC 						&   $3*n$					& $\{V_i\}, i\in M\subseteq \texttt{Nb}_i$						\\ \hline
% Centralized				&	$n$						& $\{C\}$         	\\ 
% \hline
%\end{tabular}
%\end{table}

\begin{center}
\begin{table*}[ht]
\caption{Singalling overhead.}\label{tab_overhead}
{\small
\hfill{}
\begin{tabular}{|L{2.2 cm}|C{2.8 cm}|C{3.15 cm}|C{6.6 cm}|}
\hline
 Scheme 				&Message Complexity 	&   Quantitative number of messages 		& Content of message 									\\ \hline
 ROSS-DGA, ROSS-x-DGA 	&$\mathcal{O}(N^3)$ (worst case)		&   $h+2*m^2d$ (upper bound)  				&   \multirow{2}{*}{\parbox{6.4cm}{Phase I: notification from cluster head (1 byte), new individual connectivity degree (1 byte);  Phase II: update of debatable nodes' affiliation (1 byte), claiming clusters' new membership ($|C_i|$ bytes)}}								\\ \cline{1-3}
 ROSS-DFA, ROSS-x-DFA 	&$\mathcal{O}(N)$ (worst case)		&   $h + 2m$	 (upper bound) 					& 	      												\\ \hline
 SOC 					&$\mathcal{O}(N)$		&   $3*N$									& $C_i$ ($|C_i|$ bytes), $V_i$ ($P$ bytes), $i\in \mathcal{N}$						\\ \hline
 Centralized			&$\mathcal{O}(N)$			&	$h + m + N$ (upper bound)~\cite{Efficient_broadcasting_gathering_adhoc}		& $\{C\}$ ($|C_i|*N$ bytes)        					\\ \hline
\end{tabular}
}
\hfill{}
\end{table*}
\end{center}
% centralized: $\mathcal{O}(D(s)+log N)$ + $\mathcal{O}(1+D(s)+log N)$

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.7\linewidth]{number_controlMsg.pdf}
  \caption{Number of control messages, note the curves for ROSS-DGA and ROSS-DFA are the upper bounds of the number of messages, the curve of centralized scheme reflects an ideal situation.}
  \label{control_msg}
\end{figure}

\subsection{Comparison between Distributed Schemes}
In this section we investigate the performances of distributed clustering schemes in CRN with different network scales and densities.
The transmission range of CR is $A/10$, PR's transmission range is $A/5$.
The number of PU is 30.
%The number of CR is 100, 200 and 300, and the average number of neighbours of each CR is 9.5, 20, and 31.
We list some parameters of the simulation in the Table~\ref{Simulation_para}.

\begin{table}[ht]
\caption{}
\label{Simulation_para}
{\small
\hfill{}
\begin{tabular}{|L{3.7 cm}|C{1 cm}|C{1 cm}|C{1 cm}|}
\hline
Number of CRs			& 100 	&  200 					& 300 \\ \hline
Average num. of neighbours 	&9.5	&   20		& 31  \\ \hline
Desired size $\delta$ 	& 6	&   12 						& 20      \\ \hline
\end{tabular}
}
\hfill{}
\end{table}

\subsubsection{Number of CCCs per Non-singleton Clusters}

\begin{figure}[ht!]
  \centering
  \includegraphics[width=1\linewidth]{ccc_large_scale_color.pdf}
  \caption{Number of common channels of non-singleton clusters.}
  \label{ccc_large_scale}
\end{figure}

Figure~\ref{ccc_large_scale} illustrates the average number of CCCs of the non-singleton clusters.
It shows when $N=100$, variants of ROSS have 30\% less CCCs than SOC, but this gap is decreased significantly when $N$ is 200 and 300, \ie when $N=300$, number of CCCs achieved by ROSS variants (except for ROSS-x-DFA) is almost the same with that resulted from SOC.

This means SOC performs better in terms of the average number of CCCs per non-singleton clusters when network is sparse.
this is also observed in the evaluation in Section \ref{ccc_20} where $N=20$.
When the network becomes denser, even this metric favours SOC as discussed in the beginning of Section~\ref{performance}, ROSS-DGA achieves even more CCCs than SOC, and ROSS-DFA and ROSS-x-DGA increase the number of CCCs visibly.

\subsubsection{Survival Rate of Clusters with Increasing Primary Users}

In this part of simulation, we investigate the robustness of clusters by increasing the PUs working on certain channels.

Figure~\ref{singleton_clusters_100} illustrates the increasing trend of singleton clusters with the increase of PUs.
SOC generates around 10 more singleton clusters than the variants of ROSS, which accounts for 10\% of the total CR nodes.
We only show the average values of the variants of ROSS as their confidence intervals overlap.
%It can be seen that greedy algorithms result in slightly less singleton clusters than their counterparts.
%
Figure ~\ref{singleton_clusters_300} depicts a denser CRN where $N=300$.
SOC noticeably causes more singleton clusters than ROSS variants, except that ROSS-20-DFA results in more singleton clusters when PUs are few.
The reason is ROSS-20-DFA conducts cluster membership clarification for only once, which causes large number of singleton clusters.
ROSS-20-DGA increases the size of smaller clusters through debatable nodes' repeated updates thus drastically decreases the number of singleton clusters.

\begin{figure}[!h]
  \centering
  \includegraphics[width=0.8\linewidth]{survival_rate_100.pdf}
  \caption{Percentage of CRs which are not included in any clusters with the increasing number of primary users, $N=100$}
  \label{singleton_clusters_100}
\end{figure}

  \begin{figure}[!h]
    \centering
   \includegraphics[width=0.8\linewidth]{survival_rate_300.pdf}
  \caption{Percentage of CRs which are not included in any clusters with the increasing number of primary users, $N=300$}
  \label{singleton_clusters_300}
\end{figure}

From the Figure~\ref{singleton_clusters_100} and \ref{singleton_clusters_300}, we can conclude that the greedy versions of ROSS are slightly more robust than their counterpart variants of ROSS, and the clusters obtained from variants of ROSS are clearly more robust than SOC. 
%When the network is denser, the improvement on cluster sizes and robustness by the greedy search in the membership clarification phase is more obvious.

\subsubsection{Cluster Size Control}

The number of formed clusters is shown in Fig.~\ref{nClusters_largeNetwork}.
When the network scales up, the number of formed clusters by ROSS increases by smaller margin.
This result coincides with the analysis in Section~\ref{cluster_pruning}, that with ROSS, the number of formed clusters saturates when the network scales.
When the network becomes denser, more clusters are generated by SOC compared with ROSS variants.
To better understand the distribution of the sizes of formed clusters, we depict the cluster sizes with cumulative distribution.
In this group of evaluation, the number of PRs is 30.

\begin{figure}[!h]
  \centering
   \includegraphics[width=1\linewidth]{nClusters_largeNetwork.pdf}
  \caption{The number of formed clusters.}
  %, there are $x=6$ when $N=100$, $x=12$ when $N=200$, $x=21$ when $N=300$, which is around $2/3$ of the number of average neighbours.
  \label{nClusters_largeNetwork}
\end{figure}

%\begin{figure}[ht]
%\begin{center}
%%\centering
%\subfigure[100 CRs, 30 PRs]{\label{result1:1}\includegraphics[width=0.48\linewidth]{cdf_clusterSize_100.pdf}}
%\subfigure[300 CRns, 30 PRns]{\label{result1:2}\includegraphics[width=0.48\linewidth]{cdf_clusterSize_300.pdf}}
%\end{center} 
%\caption[Cluster sizes]{Distribution of CRs in clusters with different sizes} %{\subref{a}, \subref{b}, \subref{c}, \subref{d}}
%\label{result1}
%\end{figure}

Figures~\ref{cdf_clusterSize_100}~\ref{cdf_clusterSize_200}~\ref{cdf_clusterSize_300} illustrate the empirical cumulative distribution of CR nodes which reside in clusters with certain sizes in CRNs with different densities.
%The desired cluster sizes are 5, 8 and 13, which are around 45\% of the average number of neighbours in respective CRNs. 
When the variants of ROSS with size control feature are applied, the sizes of the most generated clusters are below $\delta$, and most of them are around the 50\% percentile.
%This means the size control feature effectively restricts the size of clusters, which is able to prevent the clusters from ungovernable growing with the increase of network density.
The sizes of clusters generated by ROSS-DGA and ROSS-DFA span a wider range than that with feature control feature.
We find that average number of neighbours is roughly equal with the 95\% percentile of the ROSS-DGA curve.
%But the range where most of the CRs (80\% which exclude the CR nodes residing in small and big clusters) resides centres a value, which is roughly the half of the average number of neighbours.
As to SOC, the 95\% percentiles are 36, 30, and 40.
Overviewing the three Figures, we can see ROSS-DGA and ROSS-DFA show similar behaviour on cluster sizes.
The clusters generated from SOC demonstrate strong divergence on cluster sizes.

\begin{figure*}[t]
\begin{multicols}{3}
    \includegraphics[width=\linewidth]{cdf_clusterSize_100.pdf}\par\caption{100 CRs, 30 PRs in network}\label{cdf_clusterSize_100}
    \includegraphics[width=\linewidth]{cdf_clusterSize_200.pdf}\par\caption{200 CRs, 30 PRs in network}\label{cdf_clusterSize_200}
    \includegraphics[width=\linewidth]{cdf_clusterSize_300.pdf}\par\caption{300 CRs, 30 PRs in network}\label{cdf_clusterSize_300}
\end{multicols}
\caption{Cumulative distribution of CRs residing in clusters with different sizes}
\label{cdf_100_200_300}
\end{figure*}

\section{Conclusion}
\label{conclusion}
In this paper we design a distributed clustering scheme with the singleton congestion model, which forms robust clusters against primary users' effect.
Through simulation and theoretical analysis, we find that distributed scheme achieves similar performance with centralized optimization in terms of cluster survival ratio and number of control messages.
%, which is important to form clusters which maintains unbroken to the greatest extent possible under primary users' activity.
This paper investigates the robust clustering problem in CRN extensively, and proves the NP hardness of this problem.
A Light weighted clustering scheme ROSS is proposed, on the basis of which, we propose the fast version scheme and the scheme which generate clusters with desired sizes.
These schemes outperform other distributed clustering scheme in terms of both cluster survival ratio and control overhead.

%The clusters resulted from ROSS-DGA and its faster version ROSS-DFA are less vulnerable compared with other distributed clustering schemes, and demonstrates similar survival rate with centralized scheme under primary users' influence.
%An light weighted cluster size control mechanism is contained in both ROSS-DGA and ROSS-DFA, which is advantageous for cooperative sensing and network operation with clusters.
%Furthermore, considerable less control messages are generated when compared with other clustering schemes.

The shortage of ROSS scheme is it doesn't generate big clusters whose sizes exceed the cluster head's neighbourhood.
This problem is attributed to fact that ROSS forms clusters on the basis of cluster head's neighbourhood, and doesn't involve interaction with the nodes outside its neighbourhood.
In the other way around, forming big cluster which extends out side of cluster head's neighbourhood has very limited applications, because multiple hop communication and coordination are required mange this kind of big clusters.

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%

\appendices
%\section{Algorithm~\ref{alg0}}
\section*{}
\begin{algorithm}              % enter the algorithm environment
\caption{ROSS phase I: cluster head determination and initial cluster formation for Unclustered CR node $i$}          % give the algorithm a caption
\label{alg0} 
\DontPrintSemicolon
\SetAlgoLined
\KwIn{$D_j, G_j, j\in \texttt{Nb}_i\setminus CHs$. Empty sets $\tau_1,\tau_2$}
\KwResult{1 means $i$ is cluster head, then $D_j, j\in \texttt{Nb}_i\setminus CHs$ is changed as a big positive value $M$. 0 means $i$ is not.}

\If{$\nexists j\in \texttt{Nb}_i\setminus CHs$, such that $D_i \leq D_j$}{
	return 1;
	}
\eIf{$\exists j\in \texttt{Nb}_i\setminus CHs$, such that $D_i < D_j$}{
	return 0;}{
	\If{$\nexists j\in \texttt{Nb}_i\setminus CHs$, such that $D_j == D_i$}{
	$\tau_1 \leftarrow j$
	}
}
\If{$\nexists j\in \tau_1$, such that $G_i \leq G_j$}{
	return 1;
	}
\eIf{$\exists j\in \tau_1$, such that $G_i < G_j$}{
	return 0;
	}
	{\If{$\nexists j\in \tau_1$, such that $G_j == G_i$}{
		$\tau_2\leftarrow j$
		}
	}
\If{$\texttt{ID}_i$ is smaller than any $\texttt{ID}_j$, $j\in \tau_2\setminus i$}{
	return 1;
	}
	{return 0;
	}
\end{algorithm}

% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
%\section*{Algorithm~\ref{alg_size_control_available_CCC}}
\section*{}
\begin{algorithm}               % enter the algorithm environment
\caption{ROSS phase I: cluster head guarantees the availability of CCC (use line 1) / cluster size control (use line 2)}          % give the algorithm a caption
\label{alg_size_control_available_CCC}
\DontPrintSemicolon
\SetAlgoLined
\KwIn{Cluster C, empty sets $\tau_1, \tau_2$}
\KwOut{Cluster C has at least one CCC, or satisfies the requirement on cluster size}
%\tcc*[r]{When to guarantee available CCCs, execute from line 1, when to control cluster size, execute from line 2}
\textbf{while} $V_C =\emptyset$ \textbf{do}\\
\While{$|C|> \delta$}{
	%calculate $\lambda = \min_{i\in C, i\neq H_C}(|K_{H_C}\cap K_i|)$;\\
	\eIf{$\exists$ only one $i\in C\setminus H_C$, $i = \argmin(|K_{H_C}\cap K_i|)$}{
			$C=C\setminus i$;
		}{
				$\exists$ multiple $i$ which satisfies $i = \argmin(|K_{H_C}\cap K_i|)$;\\ $\tau_1\leftarrow i$;		
		}

	\eIf{$\exists$ only one $i\in \tau_1$, $i = \argmax(|\cap_{j\in C\setminus i} V_j|-|\cap_{j\in C} V_j|)$}{
		$C=C\setminus i$;
		}{
			%$\exists$ multiple $i$ which satisfies $i = \argmax(|\cap_{j\in C\setminus i} V_j|-|\cap_{j\in C} V_j|)$;\\
			$C=C\setminus i$, where $i = \argmin_{i\in \tau_1} \texttt{ID}_i $
			%$\texttt{ID}_i$ is smaller than any $\texttt{ID}_j$, $j\in \tau_2\setminus i$;
	}
}
\end{algorithm}

\section*{}
\begin{algorithm}               % enter the algorithm environment
\caption{Debatable node $i$ decides its affiliation in phase II of ROSS}
%, chooses one claiming cluster to stay and leaves all the other claiming clusters}          % give the algorithm a caption,  cluster to settle
\label{alg4}
\DontPrintSemicolon
\SetAlgoLined
\KwIn{all claiming clusters $C\in S_i$}
\KwOut{one cluster $C\in S_i$, node $i$ notifies all its claiming clusters in $S_i$ about its affiliation decision.
}
\While{$i$ has not chosen the cluster, or $i$ has joined cluster $\tilde{C}$, but $\exists C'\in S_i, C'\neq \tilde{C}$, which has $|K_{C'\setminus i}|-|K_{C'}|<|K_{C\setminus i}|-|K_{C}|$}{
	\eIf{$\exists$ only one $C\in S_i$, $C = \argmin(|K_{C\setminus i}| - |K_C|)$}{
			return $C$;
		}{
				$\exists$ multiple $C\in S_i$ which satisfies $C = \argmin(|K_{C\setminus i}| - |K_C|)$;\\ 
				$\tau_1\leftarrow C$;		
		}
	\eIf{$\exists$ only one $C\in \tau_1$, $C = \argmax(V_{H_C}\cap V_i)$}{
			return $C$;
		}{
				$\exists$ multiple $C\in S_i$ which satisfies $C = \argmax(V_{H_C}\cap V_i)$;\\ 
				$\tau_2\leftarrow C$;		
		}
	\eIf{$\exists$ only one $C\in \tau_2$, $C = \argmin|C|)$}{
			return $C$;
		}{
				return $\argmin_{C\in \tau_2}\texttt{ID}_{H_C}$;\\
		}
		}
\end{algorithm}

% use section* for acknowledgment

\section*{Proof of Theorem~\ref{clustering:theorem}}
\label{proof_clustering:theorem}
\begin{proof}
Note the formed cluster can be a singleton cluster, \ie cluster size is 1.
To simplify the proof, we assume secondary users have unique individual connectivity degrees.
This is fair as there are other metrics to break the tie according to Algorithm~\ref{alg0}, \ie the social connectivity degrees and node ID.
Assuming there are some secondary users which are not assigned to any cluster and node $\alpha$ is one of them.
As node $\alpha$ is not contained in any cluster, there must be at least one node $\beta\in Nb_\alpha$, with $D_{\alpha} < D_{\beta}$.
Otherwise, node $\alpha$ is eligible to form a cluster.
Then, as node $\beta$ form a cluster and include node $\alpha$, we can repeat the analysis on node $\alpha$, and deduce that node $\beta$ has at least one neighbouring node $\gamma$ with $D_{\gamma}>D_{\beta}$, and this series of nodes with monotonically increasing $D_i$ might continue to grow and ceases finally because both of the individual connectivity degree 
and the total number of nodes are limited.
The formed node series is shown as Figure~\ref{lemma1}.

\begin{figure}[ht!]
  \centering
\includegraphics[width=0.6\linewidth]{lemma1.pdf}
% \includegraphics{figure1.pdf}
	\caption{The node series discussed in the proof for Theorem~\ref{clustering:theorem}, the deduction begins from node $\alpha$}
	\label{lemma1}
\end{figure}

Now we find the node $\omega$ is in the end of this series.
As $\omega$ is the end node and does not have neighbouring nodes with bigger individual connectivity degree $D$, $\omega$ becomes cluster head and incorporate all its one-hop neighbours, including the node before it in the node series (here we assume that every new formed cluster has common channels).
After that, the node recruited into cluster will set its connection degree $D$ to zero, which enables the node further down in the list to become a cluster head.
In this way, all the nodes in the series are included in at least one cluster in an inverse sequence.
This result contradicts the initial assumption and proves the claim stated above.
Meanwhile, through this proof, we know that within at most $N$ steps, all nodes will become a part of certain clusters.
\end{proof}

%
\section*{Proof of Theorem~\ref{theorem1}}
\label{proof_theorem1}
\begin{proof}
We put the definition of weighted k-set packing problem here as it will be used in the analysis on the complexity of our problem.

\begin{mydef}
\label{def_kset_packing}
\textit{Weighted k-set packing.}

Given a set $\mathcal{G}$ which contains finite number of positive integers, and a collection of set $\mathcal{Q}=\{s_1,s_2,\cdots,s_m\}$, where for each element $s_r, 1\leq r \leq m$, there is $s_r\subseteq \mathcal{G}$, $ 1\leq|s_r| \leq k$, and $s_r$ has an associated weight which is positive real number.
The question is whether exists a collection $\mathcal{S}\subseteq \mathcal{Q}$, where $\mathcal{S}$ contains only disjoint sets and the total weight of sets in $\mathcal{S}$ is greater than $\lambda$.
Weighted k-set packing is NP-hard when $k\geqslant 3$.~\cite{Computers_a_Intractability}
\end{mydef}

To prove the centralized clustering problem is of NP-hard, we reduce the NP-hard problem \textit{weighted k-set packing} to it to prove the former is as hard as the later.
%, which means centralized clustering in CRN problem is as hard as weighted k-set packing to be solved.
To complete the reduction, we need to conduct following two steps:
\begin{itemize}
\item step 1: Show there exists a polynomial algorithm $\sigma$, by which any instance $\mathcal{S}$ of a weighted k-set packing can be transformed to a clustering solution $\sigma(\mathcal{S})$ which complies with Definition~\ref{def_centralized_clustering}.
\item step 2: Show that $\mathcal{S}$ is a \textit{yes} instance of weighted k-set packing if and only if $\sigma(\mathcal{S})$ is a \textit{yes} instance for CRN clustering problem.
\end{itemize}

We continue to use the notation adopted in the problem definition in Section~\ref{centralized_opt}.
Let set $\mathcal{G}$ contain $N$ natural numbers which are from 1 to $N$.
$\mathcal{Q}$ is a collection of sets $\{s_1, s_2,\cdots s_m\}$, each set is composed with certain elements in $\mathcal{G}$.
Assume $\mathcal{S}\subseteq \mathcal{Q}$ is one instance of weighted k-set packing, and the sets in $\mathcal{S}$ are disjoint.
$\omega$ indicates the weight for each set $s$, $\omega:\mathcal{S}\rightarrow \mathbb{Z}^{+}$.
%As the number of common channel of clusters is always integer
%give new weight to them in following way

The polynomial algorithm $\sigma$ consists of three transformations.

\begin{itemize}
\item Given a collection $\mathcal{Q}$, on basis of which we construct a CRN.
We prepare $N$ CR nodes who are labelled from 1 to $N$.
We put the CR users on a 2 dimension space, and deem a pair of them can communicate if they appear in the same set in $\mathcal{Q}$.
We regard each set in $\mathcal{Q}$ is a cluster, whose number of CCCs equals to the weight of that set.

%There is one situation deserving extra explanation in the second transformation, we adopt one example to discuss it.
Assuming two sets in $\mathcal{Q}$ are $s_1=\{1,2\}$ and $s_2=\{1,2,3\}$, then their weights are 3 and 5 respectively.
%Their dummy sets are $s_1'=\{1,1,2,2\}$ and $s_2'=\{1,1,2,2,3,3,4,4\}$ and their new weights are 3 and 5 as before.
We find it is impossible to map the sets into clusters in the same time, because the number of CCCs of the cluster which bases on $s_1$ should be no less than the cluster which bases on $s_2$, as the latter has one extra node compared with the former cluster.
%When $s_1'$ and $s_2'$ are mapped to CRN respectively, there is contradiction between them, because the number of common channels of CR node group $\{1,1,2,2\}$ is smaller than that of $\{1,1,2,2,3,3,4,4\}$.
But as to any instance of the solution to the weighted k-set packing problem, this contradiction doesn't happen because the instance $\mathcal{S}$ contains only disjoint sets, thus at most only one set of $s_1$ and $s_2$ appears in $\mathcal{S}$.%, then we can safely delete the connections based on the deleted set from the CRN, and the contradiction is eliminated.

\item In the second step, we transform the instance $\mathcal{S}$ to $\mathcal{S'}$ by adding dummy elements into each set in $\mathcal{S}$.
For each set $s_i\in \mathcal{S}$, the elements in $s_i$ are duplicated, for instance, given $s_i=\{1, 4, 6\}$, the dummy set $s_i'$ is $\{1,1,4,4,6,6\}$.
%By doing this, we obtain the dummy sets and constitute the dummy instance $\mathcal{S}'$ based on $\mathcal{S}$.
The purpose of this transformation is to eliminate the set in $\mathcal{S}$, which has single element.
The weight of set is unchanged after this transformation, \ie $\omega(s_i)=\omega(s_i')$.
%After this transmission, there is no set with only one element.
This transformation requires $\sum_{s_i \in \mathcal{S}} |s_i|$ steps.

\item In this step, we transform the instance $\mathcal{S'}$ to a clustering solution for CRN.
We prepare a second pool of CR nodes which are identical with the CR nodes prepared in step 1, i.e., identical IDs and channel availabilities on them, we call these CR nodes as dummy nodes.
We locate these CR nodes besides the CR nodes with the sane IDs in the CRN built in step 1, and there is connection between the CR node and its dummy node (the one CR node and its dummy node can be seen as two transceivers at one node).
Because of the dummy nodes, the clustering solution which corresponds to $\mathcal{S'}$ doesn't have singleton cluster.
This transformation requires $2\cdot\sum_{s_i \in \mathcal{S}} |s_i|$ steps.
%
Afterwards, the CR node whose ID doesn't appear in any set in $\mathcal{S}$ becomes single node clusters, according to the definition of clustering problem in CRN, the number of CCCs in these single node clusters is 0.
These singleton clusters and the clusters in $\mathcal{S}$ constitute a clustering solution, and finding the singleton clusters requires at most $N$ steps.
%We deliberately locate them so that at least one CR node can communicate with the rest of them.
%map every element in $\mathcal{S}$ into one CR node, \ie each integer corresponds to one CR node, in particular, that integer becomes the CR node's ID.
%As $s'$ is dummy set which has duplicated elements, we also deploy the the same CR node twice.

An example is shown in Table~\ref{no_hard_proof_instance}.
\begin{table}[h!]
     \begin{center}
     \begin{tabular}{ p{3cm}  p{4.5cm} }
     \toprule
      $\mathcal{N}$  & $\{1,2,3,4,5\}$\\ 
    \cmidrule(r){1-1}\cmidrule(lr){2-2}     
      $\mathcal{Q}$  & $\{(1),(1, 5),(1,2,4),(2,3), (4)\}$\\ 
    \cmidrule(r){1-1}\cmidrule(lr){2-2}     
      Instance for Weighted k-set packing  & $\{(1),(2,3), (4)\}$\\ 
    \cmidrule(r){1-1}\cmidrule(lr){2-2}
      Instance with dummy elements
      & 
		$\{(1,1),(2,2,3,3), (4,4)\}$
      \\    \cmidrule(r){1-1}\cmidrule(lr){2-2}
	Instance for clustering solution (dashed circles are dummy nodes)
	  &
	  %\raisebox{-\totalheight}{\includegraphics[width=0.8\linewidth]{np_hard_proof_dummy.pdf}}      
	  \begin{minipage}{.3\textwidth}
      \includegraphics[width=0.8\linewidth]{np_hard_proof_dummy.pdf}
    \end{minipage}
	  \\       \bottomrule
      \end{tabular}
      \caption{}
      \label{no_hard_proof_instance}
      \end{center}
      \end{table}

%As to duplicated elements, we also map them into a CR node, thus there exist CR nodes with identical ID.
%As a result, these CR nodes constitute a collection of CR nodes, and they can not be called as a CRN yet as there are not communication links drawn between them.
%Connections in CRN under this context is decided by physical conditions, which means to have a communication link, the two CR nodes should have common channels and locate within each other's transmission range.
%We further assume that all CR nodes locate in a way that any two pair of nodes has potential to be connected if their IDs are in the same set in $\mathcal{S}$, the instance for weighted k-set packing.
%\item Mere isolated nodes don't constitute network, thus we add connections in CRN based on the sets in $\mathcal{S}'$ sequentially.
%For each set $s'\in \mathcal{S}'$, we add connection between two CR nodes if their IDs can be found in $s'$.
%No connection exists between two CR nodes if their IDs don't appear in the same set in $\mathcal{S}$.

%We complete the polynomial algorithm $\sigma$ for the the transformation so far.
%The number of common channels of cluster $f$ is non-increasing function of cluster size, while, the weight of set in weighted k-set packing problem doesn't have this property.
%In weighted k-set packing, the weight of a set with smaller size could be larger than a set with more elements.
%But this difference doesn't hinder the transformation because an instance of weighted k-set packing contains only disjoint sets in $\mathcal{G}$.

\end{itemize}

We have crossed the hurdle of finding one polynomial algorithm $\sigma$ to transform instance of weighted k-set packing to an instance for clustering in CRN.
Now we look into the step 2 in reduction.

As to an instance $\mathcal{S}$ for weighted k-set packing, the sum weights is identical to the sum of CCCs in the CRN mapped from $\mathcal{S'}$, even $\mathcal{S}$ contains set which only has one element.
Thus, when the instance $\mathcal{S}$ is one solution and its sum weights is greater than $\lambda$, in the CRN which is mapped from $\mathcal{S'}$, the summed number of CCCs of the clusters is greater than $\lambda$.
%
When there is no solution out of set $\mathcal{G}$ for weighted k-set packing,
%let's assume the maximum sum of weights of all instances is $\sum_{s_i\in \mathcal{S}}\omega(s_i)=\delta < \lambda$. 
%The dummy set of each $s_i\in \mathcal{S}$ is mapped to cluster of CR nodes.
%Definition of CRN clustering regulates that the number of common channels is 0 when the cluster has only one node.
%As to $|s_i|=1$, the mapped cluster has two nodes, with one of them is the dummy CR node.
%Then number of common channels is on longer 0 but equals to the weight of corresponding set $s_i$.
%%Meanwhile, the number of common channels of all the other single node cluster is 0.
the summed number of CCCs of the clusters in the mapped CRN is also smaller than $\lambda$.

Thus, weighted k-set packing can be reduced to centralized clustering problem in CRN, and we can say the latter problem is of NP-hard.
\end{proof}

\section*{Acknowledgment}

The authors would like to thank xxxx

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)

% biography section
% 
% If you have an EPS/PDF photo (graphicx package needed) extra braces are
% needed around the contents of the optional argument to biography to prevent
% the LaTeX parser from getting confused when it sees the complicated
% \includegraphics command within an optional argument. (You could create
% your own custom macro containing the \includegraphics command to make things
% simpler here.)
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
% or if you just want to reserve a space for a photo:

\begin{IEEEbiographynophoto}{Di Li}
received BE and MS degrees in control engineering from Zhejiang University and Shaanxi University of Science and Technology respectively in China.
He worked with James Gross for his PhD in RWTH Aachen University since 2010.
\end{IEEEbiographynophoto}

% if you will not have a photo at all:
\begin{IEEEbiography}{Erwin Fang}
Biography text here.
Biography text here.
Biography text here.
Biography text here.
Biography text here.
Biography text here.
Biography text here.
Biography text here.
Biography text here.
Biography text here.
\end{IEEEbiography}

% insert where needed to balance the two columns on the last page with
% biographies
%\newpage

\begin{IEEEbiography}{James Gross}
Biography text here.
Biography text here.
Biography text here.
Biography text here.
Biography text here.
Biography text here.
Biography text here.
Biography text here.
Biography text here.
\end{IEEEbiography}

% You can push biographies down or up by placing
% a \vfill before or after them. The appropriate
% use of \vfill depends on what kind of text is
% on the last page and whether or not the columns
% are being equalized.

%\vfill

% Can be used to pull up biographies so that the bottom of the last one
% is flush with the other column.
%\enlargethispage{-5in}

\bibliographystyle{IEEEtran}
\bibliography{../backmatter/myrefs}

\end{document}

### 2016-03-15 journal-draft/bare_jrnl_comsoc.tex
licensed->licensed

@@
 We denote the set of these nodes as $V$ which is partitioned into sets of primary users $V_P$ and secondary users $V_N$, i.e., $V~=~V_P~\dot\cup~V_N$.
-These users share a number of non-overlapping licenced channels according to the spectrum overlay model.
-The set of these licenced channels is denoted as $\mathcal{C}$.
+These users share a number of non-overlapping licensed channels according to the spectrum overlay model.
+The set of these licensed channels is denoted as $\mathcal{C}$.
 Secondary users are allowed to transmit on a channel $c \in \mathcal{C}$ only if every primary user $p \in V_P$ that has access to channel $c$ is idle.
@@
 
-Secondary users conduct spectrum sensing independently and sequentially on all licenced channels.
+Secondary users conduct spectrum sensing independently and sequentially on all licensed channels.
 In our system model, we assume that a secondary node $n$ is able to detect for each channel $c$ whether any primary user utilizes $c$.
@@
 
-In addition to the licenced channels there is one dedicated control channel.
+In addition to the licensed channels there is one dedicated control channel.
 It is available for any secondary node $n$ to exchange control messages with any other node in its proximity (or neighborhood) $N(n)$ during the cluster formation phase.
 $N(n)$ is simply defined as the set of nodes located within the transmission range of $n$.
-Control messages involved in the clustering process can be transmitted on available licenced channels through a rendez-vous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}.
+Control messages involved in the clustering process can be transmitted on available licensed channels through a rendezvous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}, i.e., .
 \textcolor{red}{(The rendez-vous should be briefly explained!

### 2016-03-15 journal-draft/bare_jrnl_comsoc.tex
Di's answers to Erwin's initial modidication in the section of system model

@@
 $N(n)$ is simply defined as the set of nodes located within the transmission range of $n$.
-Control messages involved in the clustering process can be transmitted on available licensed channels through a rendezvous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}, i.e., .
-\textcolor{red}{(The rendez-vous should be briefly explained!
-TODO)} Over the control channel, a secondary user $n$ can exchange its spectrum sensing result $C_n$ to any $n' \in N(n)$.
+%To establish the communications with neighbours, 
+Control messages involved in the clustering process can be transmitted on available licensed channels through a rendezvous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}, i.e., two neighbouring nodes establish communication on the same channel.
+\textcolor{brown}{rendezvous, done} Over the control channel, a secondary user $n$ can exchange its spectrum sensing result $C_n$ to any $n' \in N(n)$.
 
@@
 
-\textcolor{red}{As to a pair of secondary users, when the distance between them is smaller than secondary users' transmission range, we assume the pair is able to communicate on both control channel and licensed channel, and the both are considered to be neighbours of each other.
+As to a pair of secondary users, when the Euclidean distance between them is smaller than secondary users' transmission range, we assume the pair is able to communicate on both control channel and licensed channel, and the both are considered to be neighbours of each other.
 DEFINE DISTANCE!
-TODO for Di!}
-
+\textcolor{brown}{distance, done}
+%
 If a secondary user $n$ is not in the transmission range of a primary user $u$, $n$ can certainly not detect the presence of $u$.
@@
 %Communication on licensed channels is possible only when nodes $i, j$ are both located in each other's transmission range and both share a validated licensed channel.
-As the assumed $0/1$ state \textcolor{red}{(What is that?? Define! Fix it TODO)} of connectivity is solely based on the distance between secondary users,
+As the assumed $0/1$ state \textcolor{red}{(What is that??
+Define!
+Fix it TODO)}\textcolor{brown}{Di: 0/1 means the connectivity is either available or not} of connectivity is solely based on the Euclidean distance between secondary users,
 %CRN can be represented by a graph $\mathcal{G}(I,\mathcal{E})$, where $\mathcal{E}=\lbrace(i,j,v) \vert i, j \in \mathcal{N} \wedge v\in V_i \wedge v\in V_j \rbrace$ is wireless link between any secondary node $i$ and its neighbour $j$ with licensed channel $v$.
@@
 
-A cognitive readio network (CRN) can be represented as an undirected graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{n_1,n_2\} \in E$  if, and only if, there exists a channel $c \in \mathcal{C}$ with $c \in C_{n_1} \cap C_{n_2}$.
+A cognitive radio network (CRN) can be represented as an undirected graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{n_1,n_2\} \in E$  if, and only if, there exists a channel $c \in \mathcal{C}$ with $c \in C_{n_1} \cap C_{n_2}$.
 Note that we consider the channel availability only for \textit{one} snapshot of time.
@@
 (\textcolor{red}{(Not clear what the meaning of payload communication is.
-Why not omitting payload here?)}
+Why not omitting payload here?)} \textcolor{brown}{payload communication happens when the clusters are formed, and start to support network functionalities, e.g.
+routing.
+Thus I think it is necessary to leave it here.}
 

### 2016-03-16 journal-draft/bare_jrnl_comsoc.tex
notation for secondary users

@@
 If a secondary user $n$ is not in the transmission range of a primary user $u$, $n$ can certainly not detect the presence of $u$.
-As the transmission range of primary users is limited and secondary users are located at different locations, different secondary users may have different views of the spectrum availability, i.e., for any $n, n' \in \mathcal{N}$, $C_n = C_{n'}$ does not necessarily hold.
+As the transmission range of primary users is limited and secondary users are located at different locations, different secondary users may have different views of the spectrum availability, i.e., for any $n, n' \in V_N$, $C_n = C_{n'}$ does not necessarily hold.
 %
@@
 
-A cognitive radio network (CRN) can be represented as an undirected graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{n_1,n_2\} \in E$  if, and only if, there exists a channel $c \in \mathcal{C}$ with $c \in C_{n_1} \cap C_{n_2}$.
+A cognitive radio network (CRN) can be represented as an undirected graph $G = (V_N, E)$, where $E \subseteq V_N \times V_N$ such that $\{n_1,n_2\} \in E$  if, and only if, there exists a channel $c \in \mathcal{C}$ with $c \in C_{n_1} \cap C_{n_2}$.
 Note that we consider the channel availability only for \textit{one} snapshot of time.
@@
 In this section, we describe what a cluster in the context of CRNs means.
-A cluster $\textsf{Cl} \subseteq \mathcal{N}$ is a set of secondary nodes consisting of a cluster head $h_{\textsf{Cl}}$ and a number of cluster members.
+A cluster $\textsf{Cl} \subseteq V_N$ is a set of secondary nodes consisting of a cluster head $h_{\textsf{Cl}}$ and a number of cluster members.
 The cluster head is able to communicate with any cluster member directly.
@@
 $\mathcal{P}$, $\mathcal{N}$  & collection of primary and secondary users\\
-$P$, $N$ & the number of primary users and secondary users\\
-%$J$ & set of primary uesrs in the scenario\\
 $\mathcal{F}$ & set of non-overlapping channels in the scenario\\
-$\texttt{Nb}_i$ & node $i$' neighborhood     \\
-$C$ & a cluster \\
-$C_i$ & a cluster whose cluster head is $i$ \\
+$N(n)$ & neighborhood of node $n$    \\
+$C$ & a cluster -- remove ? \\
+$C_i$ & a cluster whose cluster head is $i$ -- remove ? \\
 & (in Section~\ref{centralized_scheme}, $C_i$ is the $i$th cluster \\
-& among the legitimate clusters.)\\
-$V_i$   & set of available channels at CR node $i$  \\
-$V_C$   & set of available CCCs of cluster $C$  \\
-$V_{C_i}$   & set of available CCCs of cluster $C_i$\\
+& among the legitimate clusters.) -- remove ?\\
+$V_i$   & set of available channels at CR node $i$ --$V$ is usually a set of vertices \\
+$V_C$   & set of available CCCs of cluster $C$ --$V$ is usually a set of vertices \\
+$V_{C_i}$   & set of available CCCs of cluster $C_i$ --$V$ is usually a set of vertices\\
 %$\phi_i$ & the number of available channels for cluster $i$\\ 
@@
 \end{table}
+
+\textcolor{red}{The notation is not well chosen.
+Does it make sense to have only one letter for a potential cluster?
+What happens if we have two clusters?
+Find some comments next to your proposed notation.}
 

### 2016-03-16 journal-draft/bare_jrnl_comsoc.tex
notation
some comments on the notation

@@
 If a secondary user $n$ is not in the transmission range of a primary user $u$, $n$ can certainly not detect the presence of $u$.
-As the transmission range of primary users is limited and secondary users are located at different locations, different secondary users may have different views of the spectrum availability, i.e., for any $n, n' \in V_N$, $C_n = C_{n'}$ does not necessarily hold.
+As the transmission range of primary users is limited and secondary users are located at different locations, different secondary users may have different views of the spectrum availability, i.e., for any $n, n' \in \mathcal{N}$, $C_n = C_{n'}$ does not necessarily hold.
 %
@@
 
-A cognitive radio network (CRN) can be represented as an undirected graph $G = (V_N, E)$, where $E \subseteq V_N \times V_N$ such that $\{n_1,n_2\} \in E$  if, and only if, there exists a channel $c \in \mathcal{C}$ with $c \in C_{n_1} \cap C_{n_2}$.
+A cognitive radio network (CRN) can be represented as an undirected graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{n_1,n_2\} \in E$  if, and only if, there exists a channel $c \in \mathcal{C}$ with $c \in C_{n_1} \cap C_{n_2}$.
 Note that we consider the channel availability only for \textit{one} snapshot of time.
@@
 In this section, we describe what a cluster in the context of CRNs means.
-A cluster $\textsf{Cl} \subseteq V_N$ is a set of secondary nodes consisting of a cluster head $h_{\textsf{Cl}}$ and a number of cluster members.
+A cluster $\textsf{Cl} \subseteq \mathcal{N}$ is a set of secondary nodes consisting of a cluster head $h_{\textsf{Cl}}$ and a number of cluster members.
 The cluster head is able to communicate with any cluster member directly.

### 2016-03-16 journal-draft/bare_jrnl_comsoc.tex
put all the notations there, need cleaning

--- 2016-03-16 journal-draft/bare_jrnl_comsoc.tex
@@
 
+xxxxxx
+
+\begin{table}[h!]
+\caption{Notations in robust clustering problem}
+\label{tab1}
+\centering
+\begin{tabular}{llr}
+\toprule
+%\multicolumn{2}{c}{Item} \\
+%\cmidrule(r){1-2}
+Symbol & Description \\
+\midrule
+$\mathcal{N}$  & collection of secondary users\\
+$N(i)$ & neighborhood of node $i$    \\
+$K(i)$ & a cluster whose cluster head is $i$  \\
+$C(i)$   & set of available channels at CR node $i$  \\
+$C(K)$   & set of available CCCs of cluster $K$ \\
+$C(K(i))$   & set of available CCCs of cluster $K(i)$ \\
+$C_{K_i}$   & set of available CCCs of cluster $K(i)$ \\
+$h(K)$ & cluster head of a cluster $K$\\
+$h_K$ & cluster head of a cluster $K$\\
+$\delta$ & desired cluster size\\
+$S(i)$ & set of claiming clusters, each of which includes \\
+& debatable node $i$ after phase I\\
+
+$\mathcal{N}$  & collection of secondary users\\
+$N_i$ & neighborhood of node $i$    \\
+$C_i$ & a cluster whose cluster head is $i$  \\
+$K_i$   & set of available channels at CR node $i$  \\
+$K_C$   & set of available CCCs of cluster $C$ \\
+$K_{C_i}$   & set of available CCCs of cluster $C_i$ \\
+$h_C$ & cluster head of a cluster $C$\\
+$\delta$ & desired cluster size\\
+$S_i$ & set of claiming clusters, each of which includes \\
+& debatable node $i$ after phase I\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+xxxxx
+
 \section{Distributed Coordination Framework: Clustering Algorithm}
@@
 % \includegraphics{figure1.pdf}
-	\caption{Connectivity graph and the connectivity vector $\{D_i, G_i\}$ on each node.
-The available channels sensed by each CR node are: $V_A=\{1,2,3,4,5,6,10\}, V_B=\{1,2,3,5,7\}, V_C=\{1,3,4,10\}, V_D=\{1,2,3,5\}, V_E=\{2,3,5,7\}, V_F=\{2,4,5,6,7\}, V_G=\{1,2,3,4,8\}, V_H=\{1,2,5,8\}$.
+	\caption{Connectivity graph and the connectivity vector $(D_i, G_i)$ on each node.
+The available channels sensed by each CR node are: $K_A=\{1,2,3,4,5,6,10\}, K_B=\{1,2,3,5,7\}, K_C=\{1,3,4,10\}, K_D=\{1,2,3,5\}, K_E=\{2,3,5,7\}, K_F=\{2,4,5,6,7\}, K_G=\{1,2,3,4,8\}, K_H=\{1,2,5,8\}$.
 Dashed lines indicates two end nodes are within transmission range of each other.
@@
 Algorithm for debatable node $i$ to decide which claiming cluster to stay is described as Algorithm~\ref{alg4}.
-To conduct Algorithm~\ref{alg4}, debatable node $i$ needs to know the necessary information about its claiming clusters, \ie $V_C$ (the set of available channels in $C$), $V_{H_C}$ (the set of available channels on $C$'s cluster head $H_C$) and $|C|, C\in S_i$ (sizes of $i$'s claiming clusters).
-After deciding which cluster to stay based on Algorithm~\ref{alg4}, node $i$ notifies all its claiming clusters, and retrieves the updated information of the necessary information $V_C$, $V_{H_C}$, $|C|$, where $C\in S_i$.
+To conduct Algorithm~\ref{alg4}, debatable node $i$ needs to know the necessary information about its claiming clusters, \ie $K_C$ (the set of available channels in $C$), $K_{H_C}$ (the set of available channels on $C$'s cluster head $H_C$) and $|C|, C\in S_i$ (sizes of $i$'s claiming clusters).
+After deciding which cluster to stay based on Algorithm~\ref{alg4}, node $i$ notifies all its claiming clusters, and retrieves the updated information of the necessary information $K_C$, $K_{H_C}$, $|C|$, where $C\in S_i$.
 
@@
 $1\leq |C| \leqslant k$ where $|C|$ is the size of cluster $C$ and $k$ is a positive integer.
-We name the collection of such clusters as $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$ (the subscript $i$ is the unique index of cluster in $\mathcal{S}$, not the ID of cluster head of that cluster), $\mathcal{S}$ satisfies the following properties: $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$ and $V_{C_i}\neq \emptyset$ for any $i$ which satisfies $1\leq i \leq |\mathcal{S}|$.
+We name the collection of such clusters as $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$ (the subscript $i$ is the unique index of cluster in $\mathcal{S}$, not the ID of cluster head of that cluster), $\mathcal{S}$ satisfies the following properties: $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$ and $K_{C_i}\neq \emptyset$ for any $i$ which satisfies $1\leq i \leq |\mathcal{S}|$.
 
 Following condition distinguishes the centralized clustering problem discussed in this paper.
-The number of common control channels is $|V_{C}|$ if $|V_{C}|>1$, and is zero when $|V_{C}|=1$.
+The number of common control channels is $|K_{C}|$ if $|K_{C}|>1$, and is zero when $|K_{C}|=1$.
 We use $f$ to denoted this new number of CCCs. 
@@
 % when $|C|>1$, and $f(\cdot)=0$ when $|C|=1$.
-%As to $f(\cdot):z\rightarrow z$, under this problem setting, if only number of common channels are given consideration, only singleton clusters will be preferred, which contradicts to our goal of clustering CR nodes together, thus we choose $f(\cdot)= |V_{C}|\cdot |C|$, the product of number of common channels and cluster size.
+%As to $f(\cdot):z\rightarrow z$, under this problem setting, if only number of common channels are given consideration, only singleton clusters will be preferred, which contradicts to our goal of clustering CR nodes together, thus we choose $f(\cdot)= |K_{C}|\cdot |C|$, the product of number of common channels and cluster size.
 The decision version of centralized clustering in CRN is to ask whether exist $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C\in \mathcal{S}'} f \geqslant \lambda$ where $\lambda$ is a real number.% in stead of to maximize $\sum_{C\in \mathcal{S}'} f$.
@@
 % ROSS-DGA, ROSS-x-DGA 		&   $h+2*m^2c$ (upper bound)
-%				& $ID_{H_C}$ and $V_C$ for $h+m^2c$ times, notification to join in one cluster for $m^2c$ times					\\ \hline
-% ROSS-DFA, ROSS-x-DFA 		&   $h+ 2m$	 (upper bound) 						& $ID_{H_C}$ and $V_C$ for $h+m$ times, notification to join in one cluster for $m$ times	 					\\ \hline
-% SOC 						&   $3*n$					& $\{V_i\}, i\in M\subseteq \texttt{Nb}_i$						\\ \hline
+%				& $ID_{H_C}$ and $K_C$ for $h+m^2c$ times, notification to join in one cluster for $m^2c$ times					\\ \hline
+% ROSS-DFA, ROSS-x-DFA 		&   $h+ 2m$	 (upper bound) 						& $ID_{H_C}$ and $K_C$ for $h+m$ times, notification to join in one cluster for $m$ times	 					\\ \hline
+% SOC 						&   $3*n$					& $\{K_i\}, i\in M\subseteq \texttt{Nb}_i$						\\ \hline
 % Centralized				&	$n$						& $\{C\}$         	\\ 
@@
  ROSS-DFA, ROSS-x-DFA 	&$\mathcal{O}(N)$ (worst case)		&   $h + 2m$	 (upper bound) 					& 	      												\\ \hline
- SOC 					&$\mathcal{O}(N)$		&   $3*N$									& $C_i$ ($|C_i|$ bytes), $V_i$ ($P$ bytes), $i\in \mathcal{N}$						\\ \hline
+ SOC 					&$\mathcal{O}(N)$		&   $3*N$									& $C_i$ ($|C_i|$ bytes), $K_i$ ($P$ bytes), $i\in \mathcal{N}$						\\ \hline
  Centralized			&$\mathcal{O}(N)$			&	$h + m + N$ (upper bound)~\cite{Efficient_broadcasting_gathering_adhoc}		& $\{C\}$ ($|C_i|*N$ bytes)        					\\ \hline
@@
 %\tcc*[r]{When to guarantee available CCCs, execute from line 1, when to control cluster size, execute from line 2}
-\textbf{while} $V_C =\emptyset$ \textbf{do}\\
+\textbf{while} $K_C =\emptyset$ \textbf{do}\\
 \While{$|C|> \delta$}{
@@
 
-	\eIf{$\exists$ only one $i\in \tau_1$, $i = \argmax(|\cap_{j\in C\setminus i} V_j|-|\cap_{j\in C} V_j|)$}{
+	\eIf{$\exists$ only one $i\in \tau_1$, $i = \argmax(|\cap_{j\in C\setminus i} K_j|-|\cap_{j\in C} K_j|)$}{
 		$C=C\setminus i$;
 		}{
-			%$\exists$ multiple $i$ which satisfies $i = \argmax(|\cap_{j\in C\setminus i} V_j|-|\cap_{j\in C} V_j|)$;\\
+			%$\exists$ multiple $i$ which satisfies $i = \argmax(|\cap_{j\in C\setminus i} K_j|-|\cap_{j\in C} K_j|)$;\\
 			$C=C\setminus i$, where $i = \argmin_{i\in \tau_1} \texttt{ID}_i $
@@
 		}
-	\eIf{$\exists$ only one $C\in \tau_1$, $C = \argmax(V_{H_C}\cap V_i)$}{
+	\eIf{$\exists$ only one $C\in \tau_1$, $C = \argmax(K_{H_C}\cap K_i)$}{
 			return $C$;
 		}{
-				$\exists$ multiple $C\in S_i$ which satisfies $C = \argmax(V_{H_C}\cap V_i)$;\\ 
+				$\exists$ multiple $C\in S_i$ which satisfies $C = \argmax(K_{H_C}\cap K_i)$;\\ 
 				$\tau_2\leftarrow C$;		

### 2016-03-17 journal-draft/bare_jrnl_comsoc.tex
renew the notations, not done

@@
 \begin{abstract}
-Cluster structure in CRN facilitates cooperative spectrum sensing, routing and other functionalities.
+Cluster structure in cognitive radio networks facilitates cooperative spectrum sensing, routing and other functionalities.
 The availability of unlicensed channels which are available for every member in a cluster decides the survival of that cluster from licensed users' influence.
@@
 %Also,  prevents CR users from using channels that are occupied by primary users. 
-Clustering is also efficient to enable all CR devices within the same cluster to stop payload transmission on the operating channel and initiate the sensing process, so that all the CR users\footnote{User and node are used interchangeably in this paper, in particular, user is used when its networking or cognitive ability are discussed or stressed, and node is used when the network topology is discussed.} within the one cluster are able to vacate the channel swiftly when primary users are detected by at least one CR node residing in the cluster~\cite{willkomm08}.
+Clustering is also efficient to enable all CR devices within the same cluster to stop payload transmission on the operating channel and initiate the sensing process, so that all the CR users\footnote{The term $\textit{user}$ and $\textit{node}$ are used interchangeably in this paper, in particular, user is used when its networking or cognitive ability are discussed or stressed, and node is used when the network topology is discussed.} within the one cluster are able to vacate the channel swiftly when primary users are detected by at least one CR node residing in the cluster~\cite{willkomm08}.
 With cluster structure, as CR users can be notified by cluster head (CH) or other cluster members about the possible collision, the possibility for them to interfere neighbouring clusters is reduced~\cite{centralizedSharing80222}.
@@
 %Let us consider a two dimensional area where primary and secondary users coexist together.
-%They share the licensed channels according to the spectrum overlay model, where secondary transmitters are only allowed to transmit when the primary users are detected as being idle, and they should vacate the working channel when the presence of primary user is detected.
+%They share the licensed channels according to the spectrum overlay model, where secondary transmitters are only allowed to transmit when the prifcan exchange its spectrum sensing resulmary users are detected as being idle, and they should vacate the working channel when the presence of primary user is detected.
 %The set of primary users and secondary users are presented by $\mathcal{P}$ and $\mathcal{N}$ separately, there are $|\mathcal{P}| = P$ and $|\mathcal{N}| = N$.
@@
 
-We consider wireless sensor nodes distributed on a two-dimensional Euclidean plane.
-We denote the set of these nodes as $V$ which is partitioned into sets of primary users $V_P$ and secondary users $V_N$, i.e., $V~=~V_P~\dot\cup~V_N$.
+We consider a set of cognitive radio users $\mathcal{N}$ and a set of primary users distributed on a two-dimensional Euclidean plane.
+%We denote the set of these nodes as $V$ which is partitioned into sets of primary users $V_P$ and secondary users $V_N$, i.e., $V~=~V_P~\dot\cup~V_N$. 
 These users share a number of non-overlapping licensed channels according to the spectrum overlay model. 
-The set of these licensed channels is denoted as $\mathcal{C}$.
-Secondary users are allowed to transmit on a channel $c \in \mathcal{C}$ only if every primary user $p \in V_P$ that has access to channel $c$ is idle.
+The set of these licensed channels is denoted as $\mathcal{K}$. 
+As secondary users, the CR users are allowed to transmit on a channel $k \in \mathcal{K}$ only if no primary user is detected being accessing channel $k$ in the secondary users' neighbourhoods. 
 Further, we consider a \textit{cognitive radio ad-hoc network} which consists of all secondary users and does not contain any primary user.
 
-%Secondary users conduct spectrum sensing independently, and every secondary user conducts spectrum sensing on all licensed channels sequentially.
-%The sensing duration and frequency on one channel is a technical problem~\cite{sensing_survey_2009}, but we assume that every node can to certain extend accurately and agilely detect the presence of primary user on each channel.
+%The available channels sensed on secondary user $i$ is denoted by $V_i$ and there is $\vert V_i \vert \leq F$. % indicating the total number of 
+%%Each secondary user notifies its neighbours of the sensing result about the available channels.
+
+Secondary users conduct spectrum sensing independently and sequentially on all licensed channels.
+The sensing duration and frequency on one channel is a research topic~\cite{sensing_survey_2009}, and we assume that every node can detect the presence of primary user on each channel with certain accuracy.
 \footnote{The spectrum availability can be validated with a certain probability of detection.
 Spectrum sensing/validation is out of the scope of this paper.}
-%The available channels sensed on secondary user $i$ is denoted by $V_i$ and there is $\vert V_i \vert \leq F$. % indicating the total number of 
-%%Each secondary user notifies its neighbours of the sensing result about the available channels.
-
-Secondary users conduct spectrum sensing independently and sequentially on all licensed channels.
-In our system model, we assume that a secondary node $n$ is able to detect for each channel $c$ whether any primary user utilizes $c$.
-We denote $C_n \subseteq \mathcal{C}$ as the set of available channels for $n$.
+%In our system model, we assume that a secondary node $n$ is able to detect for each channel $c$ whether any primary user utilizes $c$.
+We denote $K_i \subseteq \mathcal{K}$ as the set of available channels for $i$.
 
 %One dedicated control channel is assumed to be available for all the secondary nodes to exchange control messages with neighbours in the process of cluster formation.
-%The control channel could be in ISM band or other reserved spectrum which is exclusively used for transmitting control messages.
 %Note that the assumption of dedicated control channel is to simplify the discussion so that we can focus on the kernel of this paper, the robustness of clusters.
@@
 
-In addition to the licensed channels there is one dedicated control channel.
-It is available for any secondary node $n$ to exchange control messages with any other node in its proximity (or neighborhood) $N(n)$ during the cluster formation phase.
-$N(n)$ is simply defined as the set of nodes located within the transmission range of $n$.
-%To establish the communications with neighbours, 
-Control messages involved in the clustering process can be transmitted on available licensed channels through a rendezvous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}, i.e., two neighbouring nodes establish communication on the same channel.
-\textcolor{brown}{rendezvous, done} Over the control channel, a secondary user $n$ can exchange its spectrum sensing result $C_n$ to any $n' \in N(n)$.
+We adopt the unit disk model~\cite{unitDiskModel} for the transmission of both primary and CR users.
+Both primary users and CR users have fixed transmission ranges respectively, and the all the channels are regarded to be identical in terms of signal propagation.
+If a CR node locates within the transmission range of primary user $p$, that CR node is not allowed to use the channel $k(p)$.
+
+We assume that in addition to the licensed channels, there is one dedicated control channel.
+This control channel could be in ISM band or other reserved spectrum which is exclusively used for transmitting control messages.
+Actually, the control messages involved in the clustering process can be transmitted on available licensed channels through a rendezvous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}, i.e., two neighbouring nodes establish communication on the same channel.
+Over the control channel, a secondary user $i$ can exchange its spectrum sensing result $K_i$ to any $i' \in \text{Nb}(i)$.
+It is available for any secondary node $i$ to exchange control messages with any other node in its proximity (or neighborhood) $\text{Nb}(i)$ during the cluster formation phase.
+$\text{Nb}(i)$ is simply defined as the set of nodes located within the transmission range of $i$.
 
@@
 
-As to a pair of secondary users, when the Euclidean distance between them is smaller than secondary users' transmission range, we assume the pair is able to communicate on both control channel and licensed channel, and the both are considered to be neighbours of each other.
+%As to a pair of secondary users, when the Euclidean distance between them is smaller than secondary users' transmission range, we assume the pair is able to communicate on both control channel and licensed channel, and the both are considered to be neighbours of each other.
 DEFINE DISTANCE!
@@
 %
-If a secondary user $n$ is not in the transmission range of a primary user $u$, $n$ can certainly not detect the presence of $u$.
-As the transmission range of primary users is limited and secondary users are located at different locations, different secondary users may have different views of the spectrum availability, i.e., for any $n, n' \in V_N$, $C_n = C_{n'}$ does not necessarily hold.
+If a secondary user $i$ is not in the transmission range of a primary user $p$, $i$ can certainly not detect the presence of $p$.
+As the transmission range of primary users is limited and secondary users are located at different locations, different secondary users may have different views of the spectrum availability, i.e., for any $i, i' \in \mathcal{N}$, $K_i = K_{i'}$ does not necessarily hold.
 %
@@
 %Communication on licensed channels is possible only when nodes $i, j$ are both located in each other's transmission range and both share a validated licensed channel.
-As the assumed $0/1$ state \textcolor{red}{(What is that??
-Define!
-Fix it TODO)}\textcolor{brown}{Di: 0/1 means the connectivity is either available or not} of connectivity is solely based on the Euclidean distance between secondary users,
+As the assumed $0/1$ state of connectivity is solely based on the Euclidean distance between secondary users,
 %CRN can be represented by a graph $\mathcal{G}(I,\mathcal{E})$, where $\mathcal{E}=\lbrace(i,j,v) \vert i, j \in \mathcal{N} \wedge v\in V_i \wedge v\in V_j \rbrace$ is wireless link between any secondary node $i$ and its neighbour $j$ with licensed channel $v$.
@@
 
-A cognitive radio network (CRN) can be represented as an undirected graph $G = (V_N, E)$, where $E \subseteq V_N \times V_N$ such that $\{n_1,n_2\} \in E$  if, and only if, there exists a channel $c \in \mathcal{C}$ with $c \in C_{n_1} \cap C_{n_2}$.
+A cognitive radio network (CRN) can be represented as an undirected graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{i, i'\} \in E$  if, and only if, there exists a channel $k \in \mathcal{K}$ with $k \in K_{i} \cap K_{i'}$.
 Note that we consider the channel availability only for \textit{one} snapshot of time.
@@
 In this section, we describe what a cluster in the context of CRNs means.
-A cluster $\textsf{Cl} \subseteq V_N$ is a set of secondary nodes consisting of a cluster head $h_{\textsf{Cl}}$ and a number of cluster members.
+A cluster $\textsf{C} \subseteq \mathcal{N}$ is a set of secondary nodes consisting of a cluster head $h_{\textsf{C}}$ and a number of cluster members.
 The cluster head is able to communicate with any cluster member directly.
-In other terms, for any cluster member $m \in \textsf{Cl}$, $m \in N \left( h_{\textsf{Cl}} \right)$ holds.
+In other terms, for any cluster member $i \in \textsf{C}$, $i \in \text{Nb} (h_{\textsf{C}}) $ holds.
 
@@
 
-Cluster is denoted as $C_i$, the subscript $i$ represents the cluster head.
+Cluster is denoted as $C_i$ when its cluster head is $i$.
 %, for the sake of concision, $C_i$ is also named as cluster $i$ in the following part of this paper.
 We denote the set of common control channels for cluster $C$ with set $K_C$.
-$ K_C = \cap_{i\in C_i} V_i$, and $k_C = |K_C|$ is the number of common control channels for cluster $C$.
-Clustering is performed periodicity, as secondary users may move with certain velocity, or the most current clusters can not maintain due to lack of CCCs when primary users' operation is intense.
+$ K_C = \cap_{i\in C} K_i$ is the set of common control channels for cluster $C$.
+Clustering is performed periodicity, as secondary users are mobile and primary users change their working channels or move.%, or the most current clusters can not maintain due to lack of CCCs when primary users' operation is intense.
 
@@
 
-\begin{table}[h!]
-\caption{Notations in robust clustering problem}
-\label{tab1}
-\centering
-\begin{tabular}{llr}
-\toprule
-%\multicolumn{2}{c}{Item} \\
-%\cmidrule(r){1-2}
-Symbol & Description \\
-\midrule
-$\mathcal{P}$, $\mathcal{N}$  & collection of primary and secondary users\\
-$\mathcal{F}$ & set of non-overlapping channels in the scenario\\
-$N(n)$ & neighborhood of node $n$    \\
-$C$ & a cluster -- remove ? \\
-$C_i$ & a cluster whose cluster head is $i$ -- remove ? \\
-& (in Section~\ref{centralized_scheme}, $C_i$ is the $i$th cluster \\
-& among the legitimate clusters.) -- remove ?\\
-$V_i$   & set of available channels at CR node $i$ --$V$ is usually a set of vertices \\
-$V_C$   & set of available CCCs of cluster $C$ --$V$ is usually a set of vertices \\
-$V_{C_i}$   & set of available CCCs of cluster $C_i$ --$V$ is usually a set of vertices\\
-%$\phi_i$ & the number of available channels for cluster $i$\\ 
-%		& note it is different than $|V_i|$\\
-%$p_i$   & number of available channels on CR node $i$  \\
-$H_C$ & cluster head of a cluster $C$\\
-$\delta$ & desired cluster size\\
-%$C_i$ & a cluster with CR node $i$ as cluster head \\
-%$V_{C_i}$   & set of common channels within cluster $C_i$  \\
-%$V_{OC_i}$   & set of common channels among cluster $C_i$ and neighbor clusters  \\
-%$CH_i$ & cluster head of node $i$ \\
-%$CHS_i$ & set of cluster heads of node $i$ after phase I\\
-$S_i$ & set of claiming clusters, each of which includes \\
-& debatable node $i$ after phase I\\
-$K_{C_i}$ & set of CCCs within cluster $C_i$\\
-$k_{C_i}$ & num. of CCCs of cluster $C_i$, $k_{C_i} = |K_{C_i}|$\\
-%$m_{ij}$ & number of common channels between CR node \\
-%& $i$ and $j$\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\textcolor{red}{The notation is not well chosen.
+%\textcolor{red}{The notation is not well chosen.
 Does it make sense to have only one letter for a potential cluster?
@@
 Find some comments next to your proposed notation.}
-
-xxxxxx
 
@@
 $\mathcal{N}$  & collection of secondary users\\
-$N(i)$ & neighborhood of node $i$    \\
-$K(i)$ & a cluster whose cluster head is $i$  \\
-$C(i)$   & set of available channels at CR node $i$  \\
-$C(K)$   & set of available CCCs of cluster $K$ \\
-$C(K(i))$   & set of available CCCs of cluster $K(i)$ \\
-$C_{K_i}$   & set of available CCCs of cluster $K(i)$ \\
-$h(K)$ & cluster head of a cluster $K$\\
-$h_K$ & cluster head of a cluster $K$\\
-$\delta$ & desired cluster size\\
-$S(i)$ & set of claiming clusters, each of which includes \\
-& debatable node $i$ after phase I\\
-
-$\mathcal{N}$  & collection of secondary users\\
-$N_i$ & neighborhood of node $i$    \\
-$C_i$ & a cluster whose cluster head is $i$  \\
+$k(i)$ & working channel of user $i$\\
+$\text{Nb}(i)$ & neighborhood of CR node $i$    \\
+$C(i)$ & a cluster whose cluster head is $i$  \\
+%$K(i)$   & set of available channels at CR node $i$  \\
 $K_i$   & set of available channels at CR node $i$  \\
-$K_C$   & set of available CCCs of cluster $C$ \\
-$K_{C_i}$   & set of available CCCs of cluster $C_i$ \\
+$K_{C(i)}$   & set of available CCCs of cluster $C(i)$ \\
+%$h(C)$ & cluster head of a cluster $C$\\
 $h_C$ & cluster head of a cluster $C$\\
+%$\text{CH}$ & cluster head\\
 $\delta$ & desired cluster size\\
@@
 & debatable node $i$ after phase I\\
+$D_i$  & Individual connectivity degree \\
+$G_i$  & Social connectivity degree \\
 \bottomrule
@@
 \end{table}
-
-xxxxx
 
@@
 
-\item \textit{Individual connectivity degree} $D_i$: $D_i=\sum_{j\in \texttt{Nb}_i}\vert V_i\cap V_j\vert$, which denotes the sum of the pairwise common channels of node $i$. 
+\item \textit{Individual connectivity degree} $D_i$: $D_i=\sum_{j\in \text{Nb}(i)}\vert K_i\cap K_j\vert$, which denotes the sum of the pairwise common channels of node $i$. 
 It is an indicator of node $i$'s adhesive property to the CRN.
 
-\item \textit{Social connectivity degree} $G_i$: $G_i=|\bigcap_{j\in \texttt{Nb}_i\cup i}V_j|$, which is the number of common channels of CR node $i$ and its neighbours.
+\item \textit{Social connectivity degree} $G_i$: $G_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$, which is the number of common channels of CR node $i$ and its neighbours.
 $G_i$ represents the ability of $i$ to form a robust cluster with its neighborhood.
@@
 In this phase, each CR node decides whether it is cluster head by comparing its connectivity vector with its neighbours.
-When CR node $i$ has bigger individual connectivity degree than any neighbours except for those which have already become cluster heads (the appearance of cluster heads will be explained in next subsubsection), then node $i$ becomes clusters head.
+When CR node $i$ has bigger individual connectivity degree than any neighbours except for those which have already become cluster heads (the appearance of cluster heads will be explained in next subsubsection, they are denoted as $\text{CHs}$), then node $i$ becomes clusters head.
 %In other words, CR node $i$ becomes cluster head if $D_i > D_k, \forall k\in \texttt{Nb}_i\setminus CHs$ ($CHs$ donate the cluster heads existing in $\texttt{Nb}_i$).
-If there is another CR node $j$ in its neighborhood, which has the same individual connectivity degree with $i$, \ie $D_j = D_i$ and $D_j > D_{k}, \forall k\in Nb_j\setminus \{CHs\cup i\}$, then the node out of $\{i, j\}$ with higher social connectivity degree becomes cluster head, and the other one becomes one member of it.
+If there is another CR node $j$ in its neighborhood, which has the same individual connectivity degree with $i$, \ie $D_j = D_i$ and $D_j > D_{k}, \forall k\in \text{Nb}(j)\setminus \{\text{CHs}\cup i\}$, then the node out of $\{i, j\}$ with higher social connectivity degree becomes cluster head, and the other one becomes one member of it.
 If $G_i = G_j$ as well, node ID is used to break the tie, \ie the one with smaller node ID takes precedence and becomes cluster head.
@@
 Let us apply Algorithm~\ref{alg0} to the example shown in Figure~\ref{fig1}.
-Node $B$ and $H$ have same individual connectivity degree, $D_B=D_H$, but as $G_H=2>G_B=1$, node $H$ becomes cluster head.
+Node $B$ and $H$ have the same individual connectivity degree, $D_B=D_H$, but as $G_H=2>G_B=1$, node $H$ becomes cluster head.
 Cluster $C_H$ is $\{H, B, A, G\}$.
@@
 \subsubsection{Guarantee Availability of Common Control Channel}
-After deciding itself being cluster head, CR node broadcasts to notify its neighbours on the dedicated control channel, meanwhile, $i$'s initial cluster is formed immediately, which is $i$'s neighborhood except for those nodes which have become cluster heads, \ie $C_i=(\texttt{Nb}_i\setminus CHs)\cup i$.
+After deciding itself being cluster head, CR node broadcasts to notify its neighbours on the dedicated control channel, meanwhile, $i$'s initial cluster is formed immediately, which is $i$'s neighborhood except for those nodes which have become cluster heads, \ie $C_i=(\text{Nb}_i\setminus \text{CHs})\cup i$.
 Note this is the initial cluster, as it is possible for the formed cluster to pose no common control channels.
@@
 Algorithm for debatable node $i$ to decide which claiming cluster to stay is described as Algorithm~\ref{alg4}.
-To conduct Algorithm~\ref{alg4}, debatable node $i$ needs to know the necessary information about its claiming clusters, \ie $K_C$ (the set of available channels in $C$), $K_{H_C}$ (the set of available channels on $C$'s cluster head $H_C$) and $|C|, C\in S_i$ (sizes of $i$'s claiming clusters).
+To conduct Algorithm~\ref{alg4}, debatable node $i$ needs to know the necessary information about its claiming clusters, \ie $K_C$ (the set of available channels in $C$), $K_{h_C}$ (the set of available channels on $C$'s cluster head $h_C$) and $|C|, C\in S_i$ (sizes of $i$'s claiming clusters).
 After deciding which cluster to stay based on Algorithm~\ref{alg4}, node $i$ notifies all its claiming clusters, and retrieves the updated information of the necessary information $K_C$, $K_{H_C}$, $|C|$, where $C\in S_i$.
@@
 %	\item $\mathcal{D}=\left\{1,\ldots,n\right\}$, the set of players (debatable nodes).
-	\item $\mathcal{P}$, the set of players of the game, which are the debatable nodes after phase I in our clustering problem.
+	\item $\mathcal{P}$, the set of players of the game, which are the debatable nodes after phase I of ROSS.
 %	\item $\mathcal{R}=\left\{1,\ldots,m\right\}$, the set of resources which player can choose, which are all the clusters in our model.
@@
 Certain number of CRs and PUs are deployed in a 2-dimensional Euclidean space.
-We adopt the unit disk model~\cite{unitDiskModel}, and both CR users and PU have fixed transmission ranges respectively.
-Complying with the system model, the CR node residing within another CR node's transmission range is seen as neighbour of that CR node.
-If CR node locating within one PU's transmission range, the CR node is not allowed to use the channel which is being used by that PU.
+%Complying with the system model, the CR node residing within another CR node's transmission range is seen as neighbour of that CR node.
 The number of licensed channels is 10, each PU is operating on each channel with probability of 50\%.

### 2016-03-17 journal-draft/bare_jrnl_comsoc.tex
renew the notations

@@
 The set of these licensed channels is denoted as $\mathcal{K}$. 
-As secondary users, the CR users are allowed to transmit on a channel $k \in \mathcal{K}$ only if no primary user is detected being accessing channel $k$ in the secondary users' neighbourhoods. 
+As secondary users, the CR users are allowed to transmit on a channel $k \in \mathcal{K}$ only if no primary user is detected being accessing channel $k$. 
 Further, we consider a \textit{cognitive radio ad-hoc network} which consists of all secondary users and does not contain any primary user.
@@
 In this section, we describe what a cluster in the context of CRNs means.
-A cluster $\textsf{C} \subseteq \mathcal{N}$ is a set of secondary nodes consisting of a cluster head $h_{\textsf{C}}$ and a number of cluster members.
+A cluster $C \subseteq \mathcal{N}$ is a set of secondary nodes consisting of a cluster head $h_{\textsf{C}}$ and a number of cluster members.
 The cluster head is able to communicate with any cluster member directly.
-In other terms, for any cluster member $i \in \textsf{C}$, $i \in \text{Nb} (h_{\textsf{C}}) $ holds.
-
-A cluster head coordinates the activities of cluster members, \ie it notifies all the members to vacate a channel if a primary user's presence is detected by one cluster member.
+In other terms, for any cluster member $i \in C$, $i \in \text{Nb} (h_C) $ holds.
+
+%A cluster head coordinates the activities of cluster members, \ie it notifies all the members to vacate a channel if a primary user's presence is detected by one cluster member.
 Further it also notifies the members to use a different common control channel for payload communication.
-(\textcolor{red}{(Not clear what the meaning of payload communication is.
+%(\textcolor{red}{(Not clear what the meaning of payload communication is.
 Why not omitting payload here?)} \textcolor{brown}{payload communication happens when the clusters are formed, and start to support network functionalities, e.g.
@@
 
-The game to be constructed can be represented by a 4-tuple $\Gamma=(\mathcal{P},\mathcal{R},(\sum_i)_{i \in \mathcal{N}},\Delta\vert K^i_C \vert)$, where the elements in $\Gamma$ are given below,
+The game to be constructed can be represented by a 4-tuple $\Gamma=(\mathcal{P},\mathcal{R},\sum_{i, i \in \mathcal{P}}, f)$, and the elements in $\Gamma$ are explained below,
 %To make the model of this game more clear, we make some change to our original problem.
@@
 	$\mathcal{R}$ is the set of claiming clusters after phase I in our clustering problem.
-	\item As to the strategy space $\sum_i$ of player $i\in \mathcal{N}$, there is $\sum_i \subseteq 2^{\left[S_i\right]}$.
-As one debatable node is supposed to choose one claiming cluster in our problem, thus only one resource is allocated for $i$, accordingly this congestion game is a singleton game.
+	\item Strategy space $\sum_i, i \in \mathcal{P}$ is the set of claiming clusters $S_i$.
+	As debatable node $i$ is supposed to choose one claiming cluster in our problem, only one piece of resource is allocated for $i$.%, accordingly this congestion game is a singleton game.
 	%when $i$ makes decision, only one resource (one claiming cluster) from the allowed resources is allocated.
@@
 %furthermore, the sequence of debatable node's join can also alter the decrement.
-	The utility (cost) function $f(C)$ of resource $C\in \mathcal{R}$, (or to say $f(r)$ of resource $r \in \mathcal{R}$) is $\Delta\vert K^i_C \vert$ which represents the decrement of CCCs in cluster $C$ caused by debatable node $i$' joining in it.
+	The utility (cost) function $f$ as to resource $C\in \mathcal{R}$ is $\Delta\vert K^i_C \vert$, which represents the decrement of CCCs in cluster $C$ when debatable node $i$' joins in it.
 	As to cluster $C\in S_i$, the decrement of CCCs caused by the enrolment of debatable nodes is $\sum_{i:C\in S_i, i\rightarrow C} \Delta\vert K^i_C \vert$. 
@@
 Now we apply the two versions of ROSS to the toy network in Figure \ref{fig2}, which has finished cluster head selection.
-In the network, node $A$'s claiming clusters are cluster $C_C, C_H\in S_A$, their members are $\{A,B,C,D\}$ and $\{A,B,H,G\}$ respectively. 
+In the network, node $A$'s claiming clusters are cluster $C(C), C(H)\in S_A$, their members are $\{A,B,C,D\}$ and $\{A,B,H,G\}$ respectively. 
 The two possible strategies of node $A$'s clarification is illustrated in Figure \ref{fig3}.
-In Figure \ref{AinC}, node $A$ staying in $C_C$ and leaving $C_H$ brings 2 more CCC into $S_A$, which is more than that brought by another strategy showed in \ref{AinH}.
+In Figure \ref{AinC}, node $A$ staying in $C(C)$ and leaving $C(H)$ brings 2 more CCC into $S_A$, which is more than that brought by another strategy showed in \ref{AinH}.
 After the decisions made similarly by the other debatable nodes $B$ and $D$, the final clusters formed are shown in Figure~\ref{fig4}.
@@
 \centering
-\subfigure[Node A stays in cluster $C_C$, quits $C_H$, $\Delta\vert K_{C_C}\vert+\Delta\vert K_{C_H}\vert=2$]{
+\subfigure[Node A stays in cluster $C(C)$, quits $C(H)$, $\Delta\vert K_{C(C)}\vert+\Delta\vert K_{C(H)}\vert=2$]{
 \includegraphics[width=0.435\linewidth]{figure4AinC.pdf}
@@
 \hspace{.15 in}
-\subfigure[Node A stays in cluster $C_H$, quits $C_C$, $\Delta\vert K_{C_C}\vert+\Delta\vert K_{C_H}\vert=1$]{
+\subfigure[Node A stays in cluster $C(H)$, quits $C(C)$, $\Delta\vert K_{C(C)}\vert+\Delta\vert K_{C(H)}\vert=1$]{
 \includegraphics[width=0.435\linewidth]{figure4AinH.pdf}

### 2016-03-24 journal-draft/bare_jrnl_comsoc.tex
modiy notations, and proof 1

@@
 \begin{table}[h!]
-\caption{Notations in robust clustering problem}
+\caption{Notations in robust clustering problem (*when sub*)}
 \label{tab1}
@@
 $\mathcal{N}$  & collection of secondary users\\
-$k(i)$ & working channel of user $i$\\
-$\text{Nb}(i)$ & neighborhood of CR node $i$    \\
+$k_i$ & the working channel of user $i$\\
+$\text{Nb}(i)$ & the neighborhood of CR node $i$    \\
 $C(i)$ & a cluster whose cluster head is $i$  \\
-%$K(i)$   & set of available channels at CR node $i$  \\
-$K_i$   & set of available channels at CR node $i$  \\
-$K_{C(i)}$   & set of available CCCs of cluster $C(i)$ \\
+%$k_i$   & set of available channels at CR node $i$  \\
+$K_i$   & the set of available channels at CR node $i$  \\
+$K(C(i))$   & the set of available CCCs of cluster $C(i)$ \\
 %$h(C)$ & cluster head of a cluster $C$\\
-$h_C$ & cluster head of a cluster $C$\\
+$h_C$ & the cluster head of a cluster $C$\\
 %$\text{CH}$ & cluster head\\
 $\delta$ & desired cluster size\\
-$S_i$ & set of claiming clusters, each of which includes \\
+$S_i$ & a set of claiming clusters, each of which includes \\
 & debatable node $i$ after phase I\\
-$D_i$  & Individual connectivity degree \\
-$G_i$  & Social connectivity degree \\
+$d_i$  & individual connectivity degree of CR node $i$\\
+$g_i$  & social connectivity degree of CR node $i$\\
 \bottomrule
@@
 %\begin{def1}
-%Connection vector $\left\{D_i,G_i\right\}$ of CR node $i$:
+%Connection vector $\left\{d_i,g_i\right\}$ of CR node $i$:
 %spectrum connectivity degree: 
 %\begin{equation}
-%\label{D_i}
-%D_i=\sum_{j\in N_i}\vert V_i\cap V_j\vert
+%\label{d_i}
+%d_i=\sum_{j\in N_i}\vert V_i\cap V_j\vert
 %\end{equation}
@@
 %\begin{equation}
-%\label{G_i}
-%G_i=|\bigcap_{j\in N_i}V_j|
+%\label{g_i}
+%g_i=|\bigcap_{j\in N_i}V_j|
 %\end{equation}
@@
 
-\item \textit{Individual connectivity degree} $D_i$: $D_i=\sum_{j\in \text{Nb}(i)}\vert K_i\cap K_j\vert$, which denotes the sum of the pairwise common channels of node $i$. 
+\item \textit{Individual connectivity degree} $d_i$: $d_i=\sum_{j\in \text{Nb}(i)}\vert K_i\cap K_j\vert$, which denotes the sum of the pairwise common channels of node $i$. 
 It is an indicator of node $i$'s adhesive property to the CRN.
 
-\item \textit{Social connectivity degree} $G_i$: $G_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$, which is the number of common channels of CR node $i$ and its neighbours.
-$G_i$ represents the ability of $i$ to form a robust cluster with its neighborhood.
+\item \textit{Social connectivity degree} $g_i$: $g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$, which is the number of common channels of CR node $i$ and its neighbours.
+$g_i$ represents the ability of $i$ to form a robust cluster with its neighborhood.
 \end{itemize}
-Individual connectivity degree $D_i$ and social connectivity degree $G_i$ together form the \textit{connectivity vector}.
+Individual connectivity degree $d_i$ and social connectivity degree $g_i$ together form the \textit{connectivity vector}.
 Figure~\ref{fig1} illustrates an example CRN where each node's connectivity vector is calculated and shown.	
@@
 % \includegraphics{figure1.pdf}
-	\caption{Connectivity graph and the connectivity vector $(D_i, G_i)$ on each node.
+	\caption{Connectivity graph and the connectivity vector $(d_i, g_i)$ at each node.
 The available channels sensed by each CR node are: $K_A=\{1,2,3,4,5,6,10\}, K_B=\{1,2,3,5,7\}, K_C=\{1,3,4,10\}, K_D=\{1,2,3,5\}, K_E=\{2,3,5,7\}, K_F=\{2,4,5,6,7\}, K_G=\{1,2,3,4,8\}, K_H=\{1,2,5,8\}$.
@@
 When CR node $i$ has bigger individual connectivity degree than any neighbours except for those which have already become cluster heads (the appearance of cluster heads will be explained in next subsubsection, they are denoted as $\text{CHs}$), then node $i$ becomes clusters head.
-%In other words, CR node $i$ becomes cluster head if $D_i > D_k, \forall k\in \texttt{Nb}_i\setminus CHs$ ($CHs$ donate the cluster heads existing in $\texttt{Nb}_i$).
-If there is another CR node $j$ in its neighborhood, which has the same individual connectivity degree with $i$, \ie $D_j = D_i$ and $D_j > D_{k}, \forall k\in \text{Nb}(j)\setminus \{\text{CHs}\cup i\}$, then the node out of $\{i, j\}$ with higher social connectivity degree becomes cluster head, and the other one becomes one member of it.
-If $G_i = G_j$ as well, node ID is used to break the tie, \ie the one with smaller node ID takes precedence and becomes cluster head.
+%In other words, CR node $i$ becomes cluster head if $d_i > d_k, \forall k\in \texttt{Nb}_i\setminus CHs$ ($CHs$ donate the cluster heads existing in $\texttt{Nb}_i$).
+If there is another CR node $j$ in its neighborhood, which has the same individual connectivity degree with $i$, \ie $d_j = d_i$ and $d_j > d_{k}, \forall k\in \text{Nb}(j)\setminus \{\text{CHs}\cup i\}$, then the node out of $\{i, j\}$ with higher social connectivity degree becomes cluster head, and the other one becomes one member of it.
+If $g_i = g_j$ as well, node ID is used to break the tie, \ie the one with smaller node ID takes precedence and becomes cluster head.
 %
@@
 %\end{proof}
-When a CR node $i$ is associated to multiple clusters \ie $i$ receives multiple notifications on cluster head eligibility from different CR nodes, $D_i$ is still set to zero.
+When a CR node $i$ is associated to multiple clusters \ie $i$ receives multiple notifications on cluster head eligibility from different CR nodes, $d_i$ is still set to zero.
 %Note here that connectivity degree on cluster head will still be the actual value.% The value will expire after some duration and is changed later on back to the original value.
@@
 %
-The purpose of this temporary manipulation on individual connectivity degree is to let the CR nodes out side of the cluster be possible to become cluster heads, so that every CR node either becomes cluster head or a member of at least one cluster.
+We manipulate the individual connectivity degree of the CR nodes, so that those locating outside of the cluster are possible to become cluster heads, then every CR node becomes either cluster head or one member of at least one cluster.
 %In other words, with this manipulation on its individual connectivity degree, every CR node in the network will be involved in the clustering process, the proof will be given later.
@@
 Let us apply Algorithm~\ref{alg0} to the example shown in Figure~\ref{fig1}.
-Node $B$ and $H$ have the same individual connectivity degree, $D_B=D_H$, but as $G_H=2>G_B=1$, node $H$ becomes cluster head.
+Node $B$ and $H$ have the same individual connectivity degree, $d_B=d_H$, but as $g_H=2>g_B=1$, node $H$ becomes cluster head.
 Cluster $C_H$ is $\{H, B, A, G\}$.
@@
 To conduct Algorithm~\ref{alg4}, debatable node $i$ needs to know the necessary information about its claiming clusters, \ie $K_C$ (the set of available channels in $C$), $K_{h_C}$ (the set of available channels on $C$'s cluster head $h_C$) and $|C|, C\in S_i$ (sizes of $i$'s claiming clusters).
-After deciding which cluster to stay based on Algorithm~\ref{alg4}, node $i$ notifies all its claiming clusters, and retrieves the updated information of the necessary information $K_C$, $K_{H_C}$, $|C|$, where $C\in S_i$.
+After deciding which cluster to stay based on Algorithm~\ref{alg4}, node $i$ notifies all its claiming clusters, and retrieves the updated information of the necessary information $K_C$, $K_{h_C}$, $|C|$, where $C\in S_i$.
 
@@
 \SetAlgoLined
-\KwIn{$D_j, G_j, j\in \texttt{Nb}_i\setminus CHs$. Empty sets $\tau_1,\tau_2$}
-\KwResult{1 means $i$ is cluster head, then $D_j, j\in \texttt{Nb}_i\setminus CHs$ is changed as a big positive value $M$. 0 means $i$ is not.}
-
-\If{$\nexists j\in \texttt{Nb}_i\setminus CHs$, such that $D_i \leq D_j$}{
+\KwIn{$d_j, g_j, j\in \texttt{Nb}_i\setminus CHs$. Empty sets $\tau_1,\tau_2$}
+\KwResult{1 means $i$ is cluster head, then $d_j, j\in \texttt{Nb}_i\setminus CHs$ is changed as a big positive value $M$. 0 means $i$ is not.}
+
+\If{$\nexists j\in \texttt{Nb}_i\setminus CHs$, such that $d_i \leq d_j$}{
 	return 1;
 	}
-\eIf{$\exists j\in \texttt{Nb}_i\setminus CHs$, such that $D_i < D_j$}{
+\eIf{$\exists j\in \texttt{Nb}_i\setminus CHs$, such that $d_i < d_j$}{
 	return 0;}{
-	\If{$\nexists j\in \texttt{Nb}_i\setminus CHs$, such that $D_j == D_i$}{
+	\If{$\nexists j\in \texttt{Nb}_i\setminus CHs$, such that $d_j == d_i$}{
 	$\tau_1 \leftarrow j$
@@
 }
-\If{$\nexists j\in \tau_1$, such that $G_i \leq G_j$}{
+\If{$\nexists j\in \tau_1$, such that $g_i \leq g_j$}{
 	return 1;
 	}
-\eIf{$\exists j\in \tau_1$, such that $G_i < G_j$}{
+\eIf{$\exists j\in \tau_1$, such that $g_i < g_j$}{
 	return 0;
 	}
-	{\If{$\nexists j\in \tau_1$, such that $G_j == G_i$}{
+	{\If{$\nexists j\in \tau_1$, such that $g_j == g_i$}{
 		$\tau_2\leftarrow j$
@@
 Note the formed cluster can be a singleton cluster, \ie cluster size is 1.
-To simplify the proof, we assume secondary users have unique individual connectivity degrees.
-This is fair as there are other metrics to break the tie according to Algorithm~\ref{alg0}, \ie the social connectivity degrees and node ID.
-Assuming there are some secondary users which are not assigned to any cluster and node $\alpha$ is one of them.
-As node $\alpha$ is not contained in any cluster, there must be at least one node $\beta\in Nb_\alpha$, with $D_{\alpha} < D_{\beta}$.
+To simplify the discussion, we assume the secondary users have unique individual connectivity degrees, and they have identical ID and social connectivity degrees.
+This assumption is fair as the social connectivity degrees and node ID are used to break ties as shown in Algorithm~\ref{alg0}, when the individual connectivity degrees are unique, it is not necessary to use the former two metrics to break ties.
+
+We assume every node has at least one neighbour.
+It is further assumed that there exist some secondary users which are not included into any cluster and node $\alpha$ is of this kind.
+As node $\alpha$ is not contained in any cluster, there must be at least one node $\beta\in \text{Nb}_\alpha$, with $d_{\alpha} < d_{\beta}$.
 Otherwise, node $\alpha$ is eligible to form a cluster.
-Then, as node $\beta$ form a cluster and include node $\alpha$, we can repeat the analysis on node $\alpha$, and deduce that node $\beta$ has at least one neighbouring node $\gamma$ with $D_{\gamma}>D_{\beta}$, and this series of nodes with monotonically increasing $D_i$ might continue to grow and ceases finally because both of the individual connectivity degree
-and the total number of nodes are limited.
+If node $\beta$ becomes cluster head, node $\alpha$ is included.
+If node node $\beta$ is not cluster head, i.e., $\beta$ is not in any cluster, we can repeat the previous analysis made on node $\alpha$, and deduce that node $\beta$ has at least one neighbouring node $\gamma$ with $d_{\gamma}>d_{\beta}$.
+When no cluster head appears, this series of nodes with monotonically increasing $d_i$ might continue to grow, and only ceases because both of the individual connectivity degree and the total number of nodes are limited.
 The formed node series is shown as Figure~\ref{lemma1}.

### 2016-03-25 journal-draft/bare_jrnl_comsoc.tex
has polished the part before 4.1.3

@@
 
-Cluster is denoted as $C_i$ when its cluster head is $i$.
+Cluster is denoted as $C(i)$ when its cluster head is $i$.
 %, for the sake of concision, $C_i$ is also named as cluster $i$ in the following part of this paper.
-We denote the set of common control channels for cluster $C$ with set $K_C$.
-$ K_C = \cap_{i\in C} K_i$ is the set of common control channels for cluster $C$.
-Clustering is performed periodicity, as secondary users are mobile and primary users change their working channels or move.%, or the most current clusters can not maintain due to lack of CCCs when primary users' operation is intense.
+$ K(C) = \cap_{i\in C} K_i$, $K(C)$ denotes the set of common control channels in cluster $C$.
+Clustering is performed periodicity, as secondary users are mobile and the channel availability on secondary users are changing as primary users change their operation state.%, or the most current clusters can not maintain due to lack of CCCs when primary users' operation is intense.
 
@@
 \begin{table}[h!]
-\caption{Notations in robust clustering problem (*when sub*)}
+\caption{Notations in robust clustering problem}
 \label{tab1}
@@
 
-In this section, we present the clustering scheme ROSS.
-ROSS utilizes the proximity of the available spectrum within a local area to form clusters.
+In this section, we introduce the distributed clustering scheme ROSS which leads to robust clusters against primary users' influence.
+ROSS consists of two cascaded phases: \textit{cluster formation} and \textit{membership clarification}.
+With ROSS, CR nodes form clusters on the basis of the proximity of the available spectrum in their neighbourhood, and then some CR nodes finalize their cluster membership, i.e., belonging to one certain cluster, by interacting with certain neighbours.
 %is based on the spectrum sensing results in its neighbours , then
-ROSS consists of two cascaded phases: \textit{cluster formation} and \textit{membership clarification}.
-We will describe them sequentially.
 
@@
 After conducting spectrum sensing and communication with neighbours, every CR node is aware of the available channels at itself and all its neighbours.
-For each CR user, two metrics are proposed to characterize the spectrum proximity between the CR user and its neighborhood.
+For each CR user, two metrics are proposed to characterize the spectrum proximity between that CR user and its neighbourhood.
 As to CR node $i$, there are,
@@
 
-\item \textit{Individual connectivity degree} $d_i$: $d_i=\sum_{j\in \text{Nb}(i)}\vert K_i\cap K_j\vert$, which denotes the sum of the pairwise common channels of node $i$. 
+\item \textit{Individual connectivity degree} $d_i$: $d_i=\sum_{j\in \text{Nb}(i)}\vert K_i\cap K_j\vert$, denotes the sum of the numbers of common controls channels between node $i$ and every neighbour.
 It is an indicator of node $i$'s adhesive property to the CRN.
 
-\item \textit{Social connectivity degree} $g_i$: $g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$, which is the number of common channels of CR node $i$ and its neighbours.
-$g_i$ represents the ability of $i$ to form a robust cluster with its neighborhood.
+\item \textit{Social connectivity degree} $g_i$: $g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$, which is the number of common channels which are available to CR node $i$ and all its neighbours.
+$g_i$ represents the ability of $i$ to form a robust cluster with its neighbours.
 \end{itemize}
@@
 Dashed lines indicates two end nodes are within transmission range of each other.
-Each edge is labelled by the number of common channels between the two ends.}
+The number of common channels between the two nodes is put along with the edge.}
 	\label{fig1}
@@
 
-After introducing connectivity vector, we proceed to introduce the first phase of algorithm ROSS.
-At first, cluster heads are determined, then clusters are formed on the basis of the cluster heads' neighbourhoods.
+After introducing the connectivity vector, we proceed to introduce the first phase of algorithm ROSS.
+To put it briefly, in this phase cluster heads are determined at first, then clusters are formed on the basis of the cluster heads' neighbourhoods.
 
@@
 In this phase, each CR node decides whether it is cluster head by comparing its connectivity vector with its neighbours.
-When CR node $i$ has bigger individual connectivity degree than any neighbours except for those which have already become cluster heads (the appearance of cluster heads will be explained in next subsubsection, they are denoted as $\text{CHs}$), then node $i$ becomes clusters head.
+When CR node $i$ has larger individual connectivity degree than any neighbours except for those which have already become cluster heads (the appearance of cluster heads will be explained in next subsubsection), then node $i$ becomes clusters head.
 %In other words, CR node $i$ becomes cluster head if $d_i > d_k, \forall k\in \texttt{Nb}_i\setminus CHs$ ($CHs$ donate the cluster heads existing in $\texttt{Nb}_i$).
-If there is another CR node $j$ in its neighborhood, which has the same individual connectivity degree with $i$, \ie $d_j = d_i$ and $d_j > d_{k}, \forall k\in \text{Nb}(j)\setminus \{\text{CHs}\cup i\}$, then the node out of $\{i, j\}$ with higher social connectivity degree becomes cluster head, and the other one becomes one member of it.
+If there is another CR node $j$ in its neighbourhood, which has the same individual connectivity degree with $i$, \ie $d_j = d_i$ and $d_j > d_{k}, \forall k\in \text{Nb}(j)\setminus \{\text{CHs}\cup i\}$, then the node out of $\{i, j\}$ with higher social connectivity degree becomes cluster head, and the other one becomes one member of it.
 If $g_i = g_j$ as well, node ID is used to break the tie, \ie the one with smaller node ID takes precedence and becomes cluster head.
 %
-The node which becomes cluster head broadcasts a message on its eligibility of being cluster head to notify its neighbours, and claims its neighbourhood as its cluster.
+The node which becomes cluster head broadcasts a message of its eligibility of being cluster head to notify its neighbours, and claims its neighbourhood as its cluster.
 The pseudo code for deciding cluster head and forming initial clusters is in Algorithm~\ref{alg0} in appendix.
@@
 %\end{proof}
-When a CR node $i$ is associated to multiple clusters \ie $i$ receives multiple notifications on cluster head eligibility from different CR nodes, $d_i$ is still set to zero.
-%Note here that connectivity degree on cluster head will still be the actual value.% The value will expire after some duration and is changed later on back to the original value.
-%
-%
-We manipulate the individual connectivity degree of the CR nodes, so that those locating outside of the cluster are possible to become cluster heads, then every CR node becomes either cluster head or one member of at least one cluster.
+When a CR node $i$ is associated to multiple clusters, \ie $i$ has received multiple notifications of cluster head eligibility from different CR nodes, $d_i$ is still set to zero.
+We manipulate the individual connectivity degree of the CR nodes, so that the nodes which locate outside of the a formed cluster can possibly become cluster heads, or be included into other clusters.
+%Then every CR node becomes either cluster head or one member of at least one cluster.
 %In other words, with this manipulation on its individual connectivity degree, every CR node in the network will be involved in the clustering process, the proof will be given later.
 %Every CR user is involved in the clustering process and becomes either cluster head or member is described in theorem~\ref{clustering:theorem}.
-We have the following theorem to show that as long as a secondary user's connectivity the CRN is not zero, the secondary user will always be integrated into a certain cluster.
+We have the following theorem to show that as long as a secondary user's individual connectivity degree is not zero, that secondary user will be integrated into a certain cluster, or become a cluster head.
 \begin{theorem}
@@
 \end{theorem}
+Here, \textit{Step} means a secondary user conducts Algorithm~\ref{clustering:theorem} once.
 The Proof is in Appendix~\ref{proof_clustering:theorem}.
@@
 Let us apply Algorithm~\ref{alg0} to the example shown in Figure~\ref{fig1}.
-Node $B$ and $H$ have the same individual connectivity degree, $d_B=d_H$, but as $g_H=2>g_B=1$, node $H$ becomes cluster head.
-Cluster $C_H$ is $\{H, B, A, G\}$.
+Node $B$ and $H$ have the same individual connectivity degree, $d_B=d_H$, but as $g_H=2>g_B=1$, node $H$ becomes the cluster head and cluster $C_H$ is $\{H, B, A, G\}$.
 
 \subsubsection{Guarantee Availability of Common Control Channel}
-After deciding itself being cluster head, CR node broadcasts to notify its neighbours on the dedicated control channel, meanwhile, $i$'s initial cluster is formed immediately, which is $i$'s neighborhood except for those nodes which have become cluster heads, \ie $C_i=(\text{Nb}_i\setminus \text{CHs})\cup i$.
-Note this is the initial cluster, as it is possible for the formed cluster to pose no common control channels.
-This problem can be solved with the following method.
-
-As smaller cluster size increases the number of CCCs within the cluster, certain nodes are eliminated until there is at least one common control channel.
-The elimination of nodes is performed according to an ascending list of nodes which are sorted by their number of common channels with the cluster head. 
+%After deciding itself being cluster head, CR node broadcasts to notify its neighbours on the dedicated control channel, meanwhile, $i$'s initial cluster is formed immediately, which is $i$'s neighbourhood except for those nodes which have become cluster heads, \ie $C_i=(\text{Nb}_i\setminus \text{CHs})\cup i$.
+After executing phase I of ROSS, there are some secondary users which become cluster heads.
+The cluster head and its neighbourhood (except for the CHs) become a cluster.
+It is possible that there is no CCCs for some formed clusters, and we solve this problem with the following method.
+
+As decreasing cluster size increases the number of CCCs within the cluster, to have at least one CCC, certain nodes are eliminated.
+The sequence of elimination is performed according to an ascending list of nodes which are sorted by the number of common channels between the nodes and the cluster head. 
 In other words, the cluster member which has the least number of common channels with the cluster head is excluded first.
-If there are nodes having the same number of common channels with cluster head, the node whose elimination brings in more common channels will be excluded.
-If this criterion meets a tie, the tie will be broken by deleting the node with smaller ID.
-It is possible that the cluster head excludes all its neighbours and resulting into a singleton cluster composed by itself.
+If there are multiple nodes having the same number of common channels with the cluster head, the node whose elimination brings in more common channels will be excluded.
+If this criterion meets a tie, the tie will be broken by deleting the node with smaller node ID.
+It is possible that the cluster head excludes all its neighbours and resulting in a \textit{singleton cluster} which is composed by itself.
 %At the end of this procedure every formed cluster has at least one common channel.
 The pseudo code for cluster head to obtain at least one common channel is shown in Algorithm~\ref{alg_size_control_available_CCC}.
-As to the nodes eliminated in this procedure, they restore their original individual connectivity degrees, and become either cluster heads or get included into other clusters later on according to Theorem~\ref{clustering:theorem}.
+As to the nodes eliminated in this procedure, they restore their original individual connectivity degrees, and become either cluster heads or get included into other clusters afterwards according to Theorem~\ref{clustering:theorem}.
 
@@
 \SetAlgoLined
-\KwIn{$d_j, g_j, j\in \texttt{Nb}_i\setminus CHs$. Empty sets $\tau_1,\tau_2$}
-\KwResult{1 means $i$ is cluster head, then $d_j, j\in \texttt{Nb}_i\setminus CHs$ is changed as a big positive value $M$. 0 means $i$ is not.}
-
-\If{$\nexists j\in \texttt{Nb}_i\setminus CHs$, such that $d_i \leq d_j$}{
+\KwIn{$d_j, g_j, j\in \text{Nb}_i\setminus \text{CHs}$. Empty sets $\tau_1,\tau_2$}
+\KwResult{Returning 1 means $i$ is cluster head, then $d_j$ is set to 0, $j\in \text{Nb}_i\setminus \text{CHs}$. returning 0 means $i$ is not CH.}
+
+\If{$\nexists j\in \text{Nb}_i\setminus \text{CHs}$, such that $d_i \leq d_j$}{
 	return 1;
 	}
-\eIf{$\exists j\in \texttt{Nb}_i\setminus CHs$, such that $d_i < d_j$}{
+\eIf{$\exists j\in \text{Nb}_i\setminus CHs$, such that $d_i < d_j$}{
 	return 0;}{
-	\If{$\nexists j\in \texttt{Nb}_i\setminus CHs$, such that $d_j == d_i$}{
+	\If{$\nexists j\in \text{Nb}_i\setminus CHs$, such that $d_j == d_i$}{
 	$\tau_1 \leftarrow j$
@@
 \begin{proof}
-Note the formed cluster can be a singleton cluster, \ie cluster size is 1.
+Note that the formed cluster can be a singleton cluster, \ie cluster size is 1.
 To simplify the discussion, we assume the secondary users have unique individual connectivity degrees, and they have identical ID and social connectivity degrees.

### 2016-03-25 journal-draft/bare_jrnl_comsoc.tex
has polished the part 4.1.3

@@
 When cluster size is large, there will be substantial burden on cluster heads to manage the cluster members, which is a challenge for resource limited cluster heads, thus the cluster size should fall in a desired range~\cite{Chen04clusteringalgorithms, capacity_cluster_06}.
-Here we illustrate the pressing necessity to control cluster size when CRN becomes dense via theoretical analysis and simulation.
-
-Assuming the CR and primary users are evenly distributed and primary users occupy the licensed channels randomly, then both CR nodes density and channel availability in the CRN can be seen as homogeneous.
-Based on Algorithm~\ref{alg0}, cluster heads are the CR nodes which possess the biggest individual connectivity degrees in their neighborhood respectively, and they are surrounded by CR nodes.
+
+In the following we illustrate the pressing necessity to control the cluster size when CRN becomes dense via both theoretical analysis and simulation.
+Assuming the secondary and primary users are evenly distributed and primary users occupy the licensed channels randomly, then both CR nodes density and channel availability in the CRN can be seen to be spatially homogeneous.
+%Based on Algorithm~\ref{alg0}, cluster heads are the CR nodes which possess the biggest individual connectivity degrees in their neighborhood respectively, and they are surrounded by CR nodes.
 %In contrast, CR nodes residing on edge are unlikely to become cluster heads as their neighbourhoods are only half the nodes locating away from edge.
-The formed clusters are the neighborhood of cluster heads, which is decided by the transmission range and network density.
-
-When the CRN is extremely dense, consider a cluster with cluster head of CR node $i$, based on the rule for cluster head selection Algorithm~\ref{alg0}, the nearest cluster head could locate just outside node $i$'s transmission range.
+The formed clusters are the neighbourhoods of cluster heads, and the neighbourhood is decided by the transmission range and network density.
+%
+We consider a cluster $C(i)$ where $i$ is CH in a dense CRN. 
+When we don't consider the CHs which could appear within $i$'s neighbourhood in the procedure of guaranteeing CCCs, according to Algorithm~\ref{alg0}, the nearest cluster heads could locate just outside node $i$'s transmission range.
 An instance of this situation is shown in Figure~\ref{clusters_denseNetwork}.
 %
-In the figure, black dots represent cluster heads, the circles denotes the transmission ranges of those cluster heads.
+In the figure, black dots represent cluster heads, the circles denotes the transmission ranges of cluster heads.
 Cluster members are not shown in the figure.
@@
 Let $l$ be the length of side of simulation plan square, and $r$ be CR's transmission radius.
-Based on the aforementioned analysis and geometry illustration as shown in Figure~\ref{clusters_denseNetwork}, we can give an estimate on the maximum number of generated clusters, which is the product of the number of cluster heads in row and line, $l/r * l/r = l^2/r^2$.
-
-Now we verify the estimation with simulation.
-We distribute CR and primary users randomly on a square plain, $r$=10 and $l$=50.
-Network density is increased by adding more CR users.
+Based on the aforementioned analysis and geometry illustration as shown in Figure~\ref{clusters_denseNetwork}, we give an estimate on the maximum number of generated clusters, which is the product of the number of cluster heads in one row and that number in one line, $l/r * l/r = l^2/r^2$.
+%Now we verify the estimation with simulation.
+%We distribute CR and primary users randomly on a square plain, $r$=10 and $l$=50.
+%Network density is increased by adding more CR users.
 %We now have a look at how does the network density affect the cluster size when the transmission range is constant.
@@
 %We can see from the example that although two neighbouring clusters can overlap greatly with each other, no cluster head will be covered by other clusters.
-The number of formed clusters is shown in Figure~\ref{number_clusters_scale}.
-With the increase of CR users in the network, network density increases linearly (the Y axis label is the number of neighbours), and the number of formed clusters also increases and approaches to the the upper bound of 25 which complies with the estimation.
-For each network scale, simulation is run for 50 times and the confidence interval is 95\%.
+Given $r$=10 and $l$=50, the number of formed clusters is shown in Figure~\ref{number_clusters_scale}.
+With the increase of CR users in the network, network density increases linearly (the Y axis label is the average number of neighbours), and the number of formed clusters also increases and approaches to the the upper bound of 25 which complies with the estimation.
 
@@
   \includegraphics[width=0.8\linewidth]{number_clusters_upperBound.pdf}
-  \caption{The correlation between the number of formed clusters and network density. Note that the number of neighbours denotes the network density.}
+  \caption{The correlation between the number of formed clusters and network density.
+Note that the number of neighbours denotes the network density.
+Simulation is run for 50 times and the confidence interval is 95\%.}
   \label{number_clusters_scale}
@@
 
-Both the analysis and simulation show that when applying ROSS, the cluster size increases with the increase of network density.
-As a result, certain measures are needed to prevent the network size from increasing with the increasing network density.
+Both the analysis and simulation show that when applying ROSS, after the number of clusters saturates with the increase of network density, the cluster size increases almost linearly with the network density, thus certain measures are needed to curb this problem.
 This task falls to the cluster heads.
-To control cluster size, cluster heads prune their cluster members.
+
+To control the cluster size, cluster heads prune their cluster members to achieve the desired cluster size.
 The desired size $\delta$ is decided based on the capability of the CR users and the tasks to be conveyed.
-Given desired size as $\delta$, cluster head excludes members sequentially, whose absence leads to the maximum increase of common channels within the cluster.
-
-Note that ROSS generates clusters on based of cluster heads' neighbourhood, thus the $\delta$ is smaller than the average neighbourhood size.
-As there are extensive overlaps between clusters, the threshold that the cluster size satisfies requirement should be larger than $\delta$.
+Given the desired size $\delta$, a cluster head excludes members sequentially according to the following principle, the absence of one cluster member leads to the maximum increase of common channels within the cluster.
+This process ends when the size of resultant cluster is $\delta$ and at least one CCC is available.
+This procedure is similar with that to guarantee CCCs in cluster, thus the algorithm can reuse Algorithm~\ref{alg_size_control_available_CCC}.
+
+%Note that ROSS generates clusters on basis of cluster heads' neighbourhood, thus the $\delta$ is smaller than the average neighbourhood size.
+%As there are extensive overlaps between clusters, the threshold that the cluster size satisfies requirement should be larger than $\delta$.
 %In practise, we set this threshold as $5*\delta/2$.
 %This process ends when the size of resultant cluster is at most $5*\delta/2$ and at least one CCC is available.
-This process ends when the size of resultant cluster is at most $\delta$ and at least one CCC is available.
-This procedure is similar with that to guarantee CCCs in cluster, thus the algorithm can reuse Algorithm~\ref{alg_size_control_available_CCC}.
 

### 2016-03-25 journal-draft/bare_jrnl_comsoc.tex
has polished the part 4.2.2

@@
 We notice nodes $A, B, D$ are included in more than one cluster. 
-We refer these nodes as \textit{debatable nodes} as their cluster affiliations are not clear, and the clusters which include debatable node $i$ are called \textit{claiming clusters} of node $i$, and are represented as $S_i$.
+We refer these nodes as \textit{debatable nodes} as their cluster affiliations are not clear, and the clusters which include the debatable node $i$ are called \textit{claiming clusters} of node $i$, and are denoted as $S_i$.
 Actually, debatable nodes extensively exist in CRN with larger scale.
-Figure~\ref{percentage_overlapping_node} shows the percentage of debatable nodes increases when the CRN network scales up.
-
-Debatable nodes should be exclusively associated with only one cluster and removed from the other claiming clusters, this procedure is called cluster membership clarification.
+Figure~\ref{percentage_overlapping_node} shows the percentage of debatable nodes increases when the CRN network becomes denser.
+Debatable nodes should be exclusively associated with only one cluster and be removed from the other claiming clusters, this procedure is called \textit{cluster membership clarification}.
 We will introduce the solution for cluster membership clarification in the following.
@@
 %Debatable node $i$ is aware of all its claiming clusters in $S_i$. 
-After Phase I, debatable nodes, \eg $i$ needs to decide which cluster $C\in S_i$ to stay, and thereafter leaves the rest others in $S_i$.
-The principle for debatable node $i$ to choose one claiming cluster is to result in the greatest increase of common channels in all its claiming clusters.
+After Phase I, debatable nodes, \eg $i$ needs to decide one cluster $C\in S_i$ to stay, and thereafter leaves the rest others in $S_i$.
+The principle for debatable node $i$ to choose one claiming cluster is that its decision can result in the greatest increase of common channels in all its claiming clusters.
 %The set of available channels of one cluster are known by the debatable nodes which locate in that cluster. %this is finished 
-Node $i$ communicates with all the cluster heads whose clusters of its claiming clusters, and is aware of the vector of common channels of the claiming clusters, then $i$ is able to know how many more common control channels will be in one certain claiming cluster if $i$ leaves that cluster.
-Based on this calculation, $i$ decides on one claiming cluster to stay and leaves the other claiming clusters.
-If there exists one cluster $C\in S_i$, if $i$ leaves this cluster brings the least increased common control channels than leaving any other claiming clusters, then $i$ chooses to stay in cluster $C$.
-When there comes a tie in terms of the increase of common channels among multiple claiming clusters, $i$ chooses to stay in the cluster whose cluster head shares more common channels with $i$.
-In case there are multiple claiming clusters demonstrating the same on the aforementioned metrics, node $i$ chooses to stay in the claiming cluster with smallest size.
-IDs of cluster heads will be used to break tie if the previous rule could not decide on the unique cluster to stay.
-
-Algorithm for debatable node $i$ to decide which claiming cluster to stay is described as Algorithm~\ref{alg4}.
-To conduct Algorithm~\ref{alg4}, debatable node $i$ needs to know the necessary information about its claiming clusters, \ie $K_C$ (the set of available channels in $C$), $K_{h_C}$ (the set of available channels on $C$'s cluster head $h_C$) and $|C|, C\in S_i$ (sizes of $i$'s claiming clusters).
-After deciding which cluster to stay based on Algorithm~\ref{alg4}, node $i$ notifies all its claiming clusters, and retrieves the updated information of the necessary information $K_C$, $K_{h_C}$, $|C|$, where $C\in S_i$.
-
-This procedure raises the concern on the infinite chain effect that debatable nodes update their choices based on other debatable nodes' choices, and this process never ceases.
-Consider the following example, where debatable node $i$ locates in cluster $C\in S_i$, and $C$ has more than one debatable node except for $i$.
-Assuming that $i$ makes decision on which cluster to stay, which is followed by the other debatable nodes $j$ to decides its affiliation, and there is $j\in C\in S_i$.
-The choice of $j$ may change $C$'s members, \ie $j$ leaves cluster $C$, which could possibly triggers node $i$ to alter its previous decision.
+Since node $i$ is a neighbour of all the cluster heads in $S_i$, node $i$ is aware of the channel availability on these claiming cluster heads, and the common control channels in these claiming clusters.
+With these information, node $i$ is able to calculate how how many more CCCs will be produced in one claiming cluster if $i$ leaves that cluster.
+%Based on this calculation, $i$ decides on one claiming cluster to stay and leaves the other claiming clusters.
+If there exists one cluster $C\in S_i$, when $i$ leaves this cluster brings the least increased CCCs than leaving any other claiming clusters, then $i$ chooses to stay in cluster $C$.
+When there comes a tie, among the relevant claiming clusters, $i$ chooses to stay in the cluster whose cluster head shares the most CCCs with $i$.
+In case there are multiple claiming clusters demonstrating the same on the aforementioned criteria, node $i$ chooses to stay in the claiming cluster which has the smallest size.
+Node IDs of cluster heads will be used to break tie if the previous rules could not decide on the unique claiming cluster to stay.
+The pseudo code of this algorithm is described as Algorithm~\ref{alg4}.
+%To conduct Algorithm~\ref{alg4}, debatable node $i$ needs to know the necessary information about its claiming clusters, \ie $K(C)$ (the set of available channels in cluster $C$), $K(h_C)$ (the set of available channels on $C$'s cluster head $h_C$) and $|C|, C\in S_i$ (sizes of $i$'s claiming clusters).
+After deciding its membership, debatable node $i$ notifies all its claiming clusters, and retrieves the updated information of the claiming clusters, \eg $K(C)$, $K_{h_C}$, $|C|$, where $C\in S_i$.
+
+This procedure raises a concern that the debatable nodes may never stop changing their affiliations, as debatable nodes' choices seem to be dependent on each other, and the infinite chain effect never ceases.
+%  update their choices based on other debatable nodes' choices, and this process 
+For example, assuming one debatable node $i$ locates in cluster $C\in S_i$, and $C$ has more than one debatable node except for $i$.
+Assuming node $i$ makes decision to stay in the claiming cluster $C$, afterwards one another debatable nodes $j$ decides its affiliation, and there is $j\in C\in S_i$.
+When $j$ leaves cluster $C$, which decrease cluster $C$'s cluster size, and could possibly trigger node $i$ to alter its previous decision to leave $C$, as $C$'s size is smaller now and leaving it may result in more increase of CCCs in $S_i$.
+At this point of time, debatable node $j$ may rejoin cluster $C$ duo to the changes in $S_j$, then both node $i$ and $j$ are facing the \textit{same}\footnote{Actually it is not totally same as before, as there are some new changes within $S_j$.} situation again.
 %To maximize the increase of common channel in clusters in $S_j$, $j$ either stays in $C$, or leaves cluster $C$ and stay another cluster in $S_j$.
@@
 %and the choice of $j$ to stay in $C$ or not possibly changes $C$'s membership and  which potentially further triggers node $i$ to alter its previous decision. 
-Thence, we must answer this question raised when implementing ROSS-DGA.
+Thence, we must answer this concern raised when implementing ROSS-DGA.
 %, and if it converges, how good such a distributed scheme performs. 
-In the following we show that the process of membership clarification can be formulated into a singleton congestion game, and a equilibrium is reached after a finite number of best response updates.
+In the following we show that the process of membership clarification can be formulated into a singleton congestion game, and a equilibrium is reached after a finite number of best response updates made by the debatable nodes.
 
@@
 \label{clustering:phaseII:game}
-%In this part, we illustrate that when debatable nodes decide on the exclusive clusters to stay, in particular, the 
-To formulate the problem of membership clarification for the debatable nodes in the context of a game, we observe this process from a different (or opposite) perspective. 
-From the new perspective, the debatable nodes are regarded as isolated and don't belong to any cluster, which means their claiming clusters become their neighbouring clusters. 
-Then for debatable nodes, the previous problem of deciding which clusters to leave becomes a new problem that which cluster to join.
-In this new problem, debatable node $i$ (note now $i\notin S_i$) chooses one cluster $C$ out of $S_i$ to join if the decrement of common channels in cluster $C$ is the smallest in $S_i$, and the decrement of CCCs in cluster $C$ is $\sum_{C\in S_i}\Delta\vert K_C \vert=\sum_{C\in S_i}({\vert K_{C} \vert-\vert K_{C\cup i} \vert})$.
-The relation between debatable nodes and claiming clusters is shown in Figure~\ref{debatable_nodes_claiming_cluster}.
-The concern on convergence appears again as we have discussed in the previous subsubsection.
-We will give proof on convergence under game theoretic framework.
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[width=0.25\linewidth]{singletongame_png.png}
-  \caption{Debatable nodes and claiming clusters}
-  \label{debatable_nodes_claiming_cluster}
-\end{figure}
-
 Game theory is a powerful mathematical tool for studying, modelling and analysing the interactions among individuals.
@@
 For example, server selection is involved in distributed computing platforms~\cite{Cloud_Computing_2010}, or users downloading files from cloud, etc.
-In the following we will introduce an \textit{server matching}~\cite{kothari:congestion_serverMatching} problem to illustrate congestion game's application in communication systems.
+
+To formulate the debatable nodes' membership clarification into the desired congestion game, we observe this process from a different (or opposite) perspective. 
+From the new perspective, the debatable nodes are regarded to be isolated and don't belong to any cluster, in other words, their claiming clusters become clusters which are beside them. 
+Now for the debatable nodes, the previous problem of deciding which clusters to leave becomes a new problem that which cluster to join.
+In the new problem, debatable node $i$ chooses one cluster $C$ out of $S_i$ to join if the decrease of CCCs in cluster $C$ is the smallest in $S_i$, and the decrease of CCCs in cluster $C$ is $\sum_{C\in S_i}\Delta\vert K(C) \vert=\sum_{C\in S_i}({\vert K(C) \vert-\vert K(C\cup i) \vert})$.
+The interaction between the debatable nodes and the claiming clusters is shown in Figure~\ref{debatable_nodes_claiming_cluster}.
+%The concern on convergence appears again as we have discussed in the previous subsubsection.
+We give proof on convergence under game theoretic framework.
+\begin{figure}[ht!]
+  \centering
+  \includegraphics[width=0.25\linewidth]{singletongame_png.png}
+  \caption{Debatable nodes and claiming clusters}
+  \label{debatable_nodes_claiming_cluster}
+\end{figure}
+
+%In the following we will introduce an \textit{server matching}~\cite{kothari:congestion_serverMatching} problem to illustrate congestion game's application in communication systems.
 
 In the following, we show that the decision of debatable nodes to clarify their membership can be mapped to the behaviour of the players in a \textit{player-specific singleton congestion game} when proper cost function is given.
-
-The game to be constructed can be represented by a 4-tuple $\Gamma=(\mathcal{P},\mathcal{R},\sum_{i, i \in \mathcal{P}}, f)$, and the elements in $\Gamma$ are explained below,
+The game to be constructed is represented with a 4-tuple $\Gamma=(\mathcal{P},\mathcal{R},\sum_{i, i \in \mathcal{P}}, f)$, and the elements in $\Gamma$ are explained below,
 %To make the model of this game more clear, we make some change to our original problem.
@@
 %	\item $\mathcal{D}=\left\{1,\ldots,n\right\}$, the set of players (debatable nodes).
-	\item $\mathcal{P}$, the set of players of the game, which are the debatable nodes after phase I of ROSS.
+	\item $\mathcal{P}$, the set of players in the game, which are the debatable nodes in our problem.
 %	\item $\mathcal{R}=\left\{1,\ldots,m\right\}$, the set of resources which player can choose, which are all the clusters in our model.
-	\item $\mathcal{R} = \cup S_i, i\in \mathcal{P}$, denotes the set of resources for players to choose, $S_i$ is the set of claiming clusters of node $i$. 
-	$\mathcal{R}$ is the set of claiming clusters after phase I in our clustering problem.
+	\item $\mathcal{R} = \cup S_i, i\in \mathcal{P}$, denotes the set of resources for players to choose, in our problem, $S_i$ is the set of claiming clusters of node $i$, and $\mathcal{R}$ is the set of all claiming clusters.
 	\item Strategy space $\sum_i, i \in \mathcal{P}$ is the set of claiming clusters $S_i$.
-	As debatable node $i$ is supposed to choose one claiming cluster in our problem, only one piece of resource is allocated for $i$.%, accordingly this congestion game is a singleton game.
+	As debatable node $i$ is supposed to choose only one claiming cluster, then only one piece of resource will be allocated to $i$.%, accordingly this congestion game is a singleton game.
 	%when $i$ makes decision, only one resource (one claiming cluster) from the allowed resources is allocated.
@@
 
-	\item %For the clusters which are possible destination of debatable nodes, the decrement of common channels caused by different debatable node' join can be different because of the heterogeneity of channel availability within itself and on the debatable nodes.
-%furthermore, the sequence of debatable node's join can also alter the decrement.
-	The utility (cost) function $f$ as to resource $C\in \mathcal{R}$ is $\Delta\vert K^i_C \vert$, which represents the decrement of CCCs in cluster $C$ when debatable node $i$' joins in it.
-	As to cluster $C\in S_i$, the decrement of CCCs caused by the enrolment of debatable nodes is $\sum_{i:C\in S_i, i\rightarrow C} \Delta\vert K^i_C \vert$. 
-$i\rightarrow C$ means $i$ joins in cluster $C$.
-Obviously this function is non-decreasing with respect to the number of nodes joining in cluster $C$.
-
-The utility function is not purely decided by the number of players (debatable nodes) as that in a canonical congestion game, because in this game the channel availability on debatable nodes is different.
-Given two same sized groups of debatable nodes, when the nodes are not completely the same (neither are the channel availabilities on these nodes), the cost happened on one claiming cluster could be different if the two groups of debatable nodes join in that cluster respectively.
+	\item %For the clusters which are possible destination of debatable nodes, the decrease of common channels caused by different debatable node' join can be different because of the heterogeneity of channel availability within itself and on the debatable nodes.
+%furthermore, the sequence of debatable node's join can also alter the decrease.
+	The utility (cost) function $f(C)$ as to a resource $C$. 
+	$f(C) = \Delta\vert K^i(C)|, C\in S_i$, which represents the decrease of CCCs in cluster $C$ when debatable node $i$ joins $C$.
+	As to cluster $C\in S_i$, the decrease of CCCs caused by the enrolment of debatable nodes is $\sum_{i:C\in S_i, i\rightarrow C} \Delta\vert K^i(C) \vert$. 
+$i\rightarrow C$ means $i$ joins cluster $C$.
+Obviously this function is non-decreasing with respect to the number of nodes joining cluster $C$.
+
+The utility function $f$ is not purely decided by the number of players accessing the resource (debatable nodes join claiming clusters), which happens in a canonical congestion game.
+The reason is in this game the channel availability on debatable nodes is different.
+Given two same groups of debatable nodes and their sizes are the same, when the nodes are not completely the same (neither are the channel availabilities on these nodes), the cost happened on one claiming cluster could be different if the two groups of debatable nodes join that cluster respectively.
 %In a canonical congestion game, the cost (or pay off) is function of only the number of players occupying the resource, and is mono-
 %In this new game, the cost function 
-Hence, this game is called player specific.
-In this game, every player greedily updates its strategy (choosing one claiming cluster to join) if joining in a different claiming cluster minimizes the decrement of CCCs $\sum_{i:C\in S_i} \Delta\vert K^i_C \vert$, player's strategy in the game is exactly the same with the behaviour of debatable node in membership clarification phase, as described by Algorithm~\ref{alg4}.
+Hence, this congestion game is player specific~\cite{Ackermann06purenash}.
+In this game, every player greedily updates its strategy (choosing one claiming cluster to join) if joining a different claiming cluster minimizes the decrease of CCCs $\sum_{i:C\in S_i} \Delta\vert K^i(C) \vert$, and a player's strategy in the game is exactly the same with the behaviour of a debatable node in the membership clarification phas.
 
@@
 As to singleton congestion game, there exists pure equilibria which can be reached with best response update, and the upper bound of number of steps before convergence is $n^2*m$~\cite{Ackermann06purenash}, where $n$ is the number of players, and $m$ is the number of resources.
-In our problem, the players are the debatable nodes, and the resources are the claiming clusters (or clusters heads).
+In our problem, the players are the debatable nodes, and the resources are the claiming clusters.
 Thus the upper bound of the number of steps can be expressed as $\mathcal{O}(N^3)$.
-In fact, the actual number of steps is much smaller than $N^3$ as both $n$ and $m$ are considerably smaller than $N$.
+In fact, the number of steps which are actually involved in this process is much smaller than $N^3$, as both $n$ and $m$ are considerably smaller than $N$.
 The amount of debatable nodes is illustrated in Figure~\ref{fig2}, which is between 10\% to 80\% of the total number of CR nodes in the network.
@@
 %Although the game version of DGA can achieve \textit{Nash Equilibrium}, the whole scheme can possibly obtain sub-optimal result.
-%, furthermore,this stable state is a local minimum of the global decrement function.
+%, furthermore,this stable state is a local minimum of the global decrease function.
 %\todo[inline]{The number of steps, or the upper bound of steps in convergence needs a formal proof}
@@
 Comparison scheme SOC involves three rounds of execution. 
-In the first two rounds, every CR node maintains its own cluster and seek to integrate neighbouring clusters, or join in one of them.
+In the first two rounds, every CR node maintains its own cluster and seek to integrate neighbouring clusters, or joins one of them.
 The final clusters are obtained in the third round. 
@@
 % ROSS-DGA, ROSS-x-DGA 		&   $h+2*m^2c$ (upper bound)
-%				& $ID_{H_C}$ and $K_C$ for $h+m^2c$ times, notification to join in one cluster for $m^2c$ times					\\ \hline
-% ROSS-DFA, ROSS-x-DFA 		&   $h+ 2m$	 (upper bound) 						& $ID_{H_C}$ and $K_C$ for $h+m$ times, notification to join in one cluster for $m$ times	 					\\ \hline
+%				& $ID_{H_C}$ and $K_C$ for $h+m^2c$ times, notification to join one cluster for $m^2c$ times					\\ \hline
+% ROSS-DFA, ROSS-x-DFA 		&   $h+ 2m$	 (upper bound) 						& $ID_{H_C}$ and $K_C$ for $h+m$ times, notification to join one cluster for $m$ times	 					\\ \hline
 % SOC 						&   $3*n$					& $\{K_i\}, i\in M\subseteq \texttt{Nb}_i$						\\ \hline

### 2016-03-26 journal-draft/bare_jrnl_comsoc.tex
polished section 5

@@
 Cluster is denoted as $C(i)$ when its cluster head is $i$.
+Cluster size of $C(i)$ is written as $|C(i)|$.
 %, for the sake of concision, $C_i$ is also named as cluster $i$ in the following part of this paper.
@@
 $\mathcal{N}$  & collection of secondary users\\
-$k_i$ & the working channel of user $i$\\
+%$k_i$ & the working channel of user $i$\\
 $\text{Nb}(i)$ & the neighborhood of CR node $i$    \\
@@
 $g_i$  & social connectivity degree of CR node $i$\\
+$C_i$  & the $i$th legitimate cluster (only adopted in Section~\ref{centralized_opt})\\
 \bottomrule
@@
 
-\subsubsection{Distributed Greedy Algorithm}
+\subsubsection{Distributed Greedy Algorithm (DGA)}
 %Debatable node $i$ is aware of all its claiming clusters in $S_i$. 
@@
 %The convergence speed of DGA is large recalling that the number of steps is of $\mathcal{O}(N^3)$.
-We propose a faster version of ROSS, which is ROSS-DFA, which is especially suitable for CRN where channel availability change dynamically and re-clustering is necessary.
-In DFA, debatable nodes regard their claiming clusters includes all their debatable nodes, thus the membership of claiming clusters is static and debatable nodes can make decisions simultaneously without considering the change of membership of their claiming clusters.
+We propose a faster version of ROSS, ROSS-DFA, which differs from ROSS-DGA in the second phase.
+With ROSS-DFA, debatable nodes decide their respective cluster heads once.
+The debatable nodes consider their claiming clusters to include all their debatable nodes, thus the membership of claiming clusters is static and all the debatable nodes can make decision simultaneously without considering the change of membership of their claiming clusters.
+As ROSS-DFA is quicker than ROSS-DGA, the former is especially suitable for the CRN where the channel availability changes dynamically and re-clustering is necessary.
 To run ROSS-DFA, debatable node executes only one loop in Algorithm~\ref{alg4}.
 
-Now we apply the two versions of ROSS to the toy network in Figure \ref{fig2}, which has finished cluster head selection.
+Now we apply both ROSS-DGA and ROSS-DFA to the toy network in Figure~\ref{fig2} which has been applied the phase I of ROSS.
 In the network, node $A$'s claiming clusters are cluster $C(C), C(H)\in S_A$, their members are $\{A,B,C,D\}$ and $\{A,B,H,G\}$ respectively. 
-The two possible strategies of node $A$'s clarification is illustrated in Figure \ref{fig3}.
-In Figure \ref{AinC}, node $A$ staying in $C(C)$ and leaving $C(H)$ brings 2 more CCC into $S_A$, which is more than that brought by another strategy showed in \ref{AinH}.
-After the decisions made similarly by the other debatable nodes $B$ and $D$, the final clusters formed are shown in Figure~\ref{fig4}.
+The two possible strategies of node $A$ is illustrated in Figure \ref{fig3}.
+In Figure \ref{AinC}, node $A$ staying in $C(C)$ and leaving $C(H)$ brings 2 more CCCs to $S_A$, which is more than that brought by another strategy showed in \ref{AinH}.
+After the decisions made similarly by the other debatable nodes $B$ and $D$, the final clusters are formed as shown in Figure~\ref{fig4}.
 
@@
 }
-\caption[]{Membership clarification: possible cluster formations decided by node A's different choices} %\subref{node A in $C_C$}, \subref{node A in $C_H$}}
+\caption[]{Membership clarification: possible cluster formations caused by node A's different choices} %\subref{node A in $C_C$}, \subref{node A in $C_H$}}
 \label{fig3}
@@
 The centralized clustering scheme aims to form clusters with desired sizes, meanwhile the total number of common control channels of all clusters is maximized.
-In the following, we refer this problem as \textit{centralized clustering}, and the problem definition is as follows,
+In the following, we refer this problem as \textit{centralized clustering}, and give the formal problem definition.
 
@@
 
-Following condition distinguishes the centralized clustering problem discussed in this paper.
-The number of common control channels is $|K_{C}|$ if $|K_{C}|>1$, and is zero when $|K_{C}|=1$.
-We use $f$ to denoted this new number of CCCs. 
-The question of this problem is to find a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, so that $\bigcup_{C_j\in \mathcal{S}'} C_j = N$, and $C_j'\cap C_j =\emptyset$ for $C_j', C_j\in \mathcal{S}'$, so that $\sum_{C\in \mathcal{S}'} f$ is maximized.
+We give a new definition of the number of CCCs, which distinguishes the centralized clustering problem discussed in this paper.
+In this problem, the number of common control channels is $|K(C)|$ if $|C|>1$, and is zero when $|C|=1$.
+We use $f(C)$ to denote this new definition of the number of CCCs of a cluster $C$.
+The question of centralized clustering problem is to find a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, so that $\bigcup_{C_j\in \mathcal{S}'} C_j = N$, and $C_{j'}\cap C_j =\emptyset$ for $C_{j'}, C_j\in \mathcal{S}'$ and $j'\neq j$, so that $\sum_{C\in \mathcal{S}'} f$ is maximized.
 % when $|C|>1$, and $f(\cdot)=0$ when $|C|=1$.
 %As to $f(\cdot):z\rightarrow z$, under this problem setting, if only number of common channels are given consideration, only singleton clusters will be preferred, which contradicts to our goal of clustering CR nodes together, thus we choose $f(\cdot)= |K_{C}|\cdot |C|$, the product of number of common channels and cluster size.
-The decision version of centralized clustering in CRN is to ask whether exist $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C\in \mathcal{S}'} f \geqslant \lambda$ where $\lambda$ is a real number.% in stead of to maximize $\sum_{C\in \mathcal{S}'} f$.
+The decision version of centralized clustering in CRN is to ask whether there exists no-empty $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C\in \mathcal{S}'} f \geqslant \lambda$ where $\lambda$ is a real number.% in stead of to maximize $\sum_{C\in \mathcal{S}'} f$.
 \end{mydef}
@@
 \subsection{Complexity of Clustering Problem}
-In the following part of this section, we will discuss the complexity of centralized clustering problem and provide a centralized solution for it.
+In this section we investigate the complexity of centralized clustering problem.
+Theorem~\ref{theorem1} tells centralized clustering problem in CRN is one NP-hard problem.
 
@@
 Legitimate clusters are the clusters which satisfy the conditions in Section~\ref{def_cluster}. 
-Note that the legitimate clusters include the singleton ones, which guarantees the partition of any network is feasible.
+Note that the legitimate clusters include the singleton ones, so that we can guarantee the partition of any network is always feasible.
 
 With $N=|\mathcal{N}|, G=|\mathcal{G}|$, we construct a constant $G\times N$ matrix $Q_{G\text{x}N}$. 
-The element of matrix $Q$ is $q_{ij}$, where the subscript $i$ denotes a legitimate cluster, and $j$ denotes a CR node, which can be seen as the node ID. 
-Note that $C_i$ means $i$th cluster in the collection $\mathcal{G}$, doesn't denote the cluster where cluster head is $i$, this notation is only valid in this subsection.
+The element of matrix $Q$ is $q_{ij}$, where the subscript $i$ is the index of legitimate cluster, and $j$ is the node ID of one CR node.
+%Note that $C_i$ means $i$th cluster in the collection $\mathcal{G}$, doesn't denote the cluster where cluster head is $i$, this notation is only valid in this subsection.
 There are $i\in \{1,2,\cdots,G-1, G\}$, and $j\in \{1,2,\cdots,N-1, N\}$.
-Element $q_{ij}= k_{C_i}$ if node $j\in C_i$, and $q_{ij}= 0$ if $j\notin C_i$.
+Element $q_{ij}= |K(C_i)|$ if node $j\in C_i$, and $q_{ij}= 0$ if $j\notin C_i$.
 In other words, each non-zero element $q_{ij}$ denotes the number of CCCs of the cluster $i$ where node $j$ resides.
@@
 \centering
-Q = \bordermatrix{~ 		& 1 	& 2 	& 3 	& \cdots & j & \cdots	& N-1 	& N	\cr
-                  1 	& k_{C_1} 	& k_{C_1} 	& 0 	& \cdots & \cdots &\cdots	& 0 	& 0	\cr
-                  2 	& k_{C_2} 	& 0 	& k_{C_2} 	& \cdots & \cdots & \cdots 	& 0 	& 0	\cr
+\bordermatrix{~ 		& 1 	& 2 	& 3 	& \cdots & j & \cdots	& N-1 	& N	\cr
+                  1 	& |K(C_1)| 	& |K(C_1)| 	& 0 	& \cdots & \cdots &\cdots	& 0 	& 0	\cr
+                  2 	& |K(C_2)| 	& 0 	& |K(C_2)| 	& \cdots & \cdots & \cdots 	& 0 	& 0	\cr
 				\vdots  	&\vdots & 	 	& 		&  \vdots		& 		& \vdots \cr
-				i 	& 0 	& k_{C_i} 	& 0 	& \cdots  & \cdots & \cdots 	& k_{C_i} 	& 0	\cr
+				i 	& 0 	& |K(C_i)| 	& 0 	& \cdots  & \cdots & \cdots 	& |K(C_i)| 	& 0	\cr
 				\vdots  	&\vdots & 	 	& 		&  \vdots & \cdots & \cdots 		& 		& \vdots \cr
-				\vdots 	& \vdots  	& 0 	& 0 	& \cdots & \cdots & \cdots 	& k_{C_i'} 	& 0	\cr
-				G  	& k_{C_G} & \cdots	 	& 		&  \vdots	& \cdots & \cdots& 		& \vdots \cr}	
-\caption{An example of Matrix Q, its rows correspond to all legitimate clusters, and columns correspond to the CR nodes in the CRN.}
+				\vdots 	& \vdots  	& 0 	& 0 	& \cdots & \cdots & \cdots 	& |K(C_i')| 	& 0	\cr
+				G  	& |K(C_G)| & \cdots	 	& 		&  \vdots	& \cdots & \cdots& 		& \vdots \cr}	
+\caption{An example of Matrix $Q$, its rows correspond to all legitimate clusters, and columns correspond to the CR nodes in the CRN.}
 \label{xx}
@@
 
-We build a $G\times N$ binary variable matrix $X$, which illustrates the clustering strategy.
+We build a $G\times N$ binary variable matrix $X$, which illustrates the clustering solution.
 The element of matrix $X$ is binary variable $x_{ij}, i=1, \ldots, G, j=1, \ldots, N$.
@@
 \end{equation}
-The objective is the sum of two parts, the first part is the sum of products of cluster size and the corresponding number of CCCs.
-We notice that the first part is the metric adopted by the scheme SOC~\cite{Lazos09}.
+
+The objective is a sum of two parts, the first part is the sum of products of cluster size and the corresponding number of CCCs.
+The first part is the only metric adopted by the scheme SOC~\cite{Lazos09}.
 The second part is the \textit{punishment} for choosing the clusters whose sizes are not $\delta$.
-In fact, the second part is particularly designed to eliminates the drawbacks of SOC, \ie a large number of singleton clusters, or a few very large clusters which access affluent unlicensed spectrum.
-In practical computation, we minimize the opposite of the sum of the products of cluster size and the corresponding number of CCCs, thus the punishment is positive.
+In fact, the second part is particularly designed to eliminates the drawbacks of SOC, \ie SOC produces a large number of singleton clusters and a few very large clusters which access affluent unlicensed spectrum.
+In practical computation, we minimize the opposite of the first part, then the punishment is a positive value.
 
 The first constraint restricts each node $j$ to reside in exactly one cluster.
-The second constraint regulates that when $i$th legitimate cluster $C_i$ chosen, the number of elements which equal to 1 in the $i$th row is $|C_i|$.
-
-Now we explain how does the mechanism of the punishment in the objective work. 
-$w_i$ is an auxiliary binary variable, which denotes whether cluster $C_i$ is chosen by the solution, in particular, 
+In the second constraint, $w_i$ is an auxiliary binary variable, which denotes whether cluster $C_i$ is chosen by the solution, in particular, 
 $$
@@
 $$
-%$w_i=0$ denotes $i$th legitimate cluster $C_i$ is chosen in the solution, and $w_i=1$ means $i$th legitimate cluster is not chosen.
-and $p$ is defined as follows,
-%$\texttt{cost($\delta$)}$
+The second constraint regulates that when the $i$th legitimate cluster $C_i$ is chosen, then  there are $|C_i|$ elements in $i$th row in matrix $X$, which are 1.
+%
+Now we explain how does the mechanism of the punishment in the objective work. 
+The parameter $p$ is defined as follows,
 $$
@@
 where $\alpha_i>0$ and increases when $|C_i|$ diverges from $\delta$.
-Because of $w_i$, any chosen cluster brings certain \textit{punishment}.
-Function $p$ denotes that when the chosen cluster's size is desired size $\delta$, the punishment is zero.
-When the chosen cluster's size diverges from $\delta$, the objective function suffers \textit{loss}.
-%
+Because of $w_i$, any chosen cluster ($w=0$) brings certain \textit{punishment}.
+When the chosen cluster's size is desired size $\delta$, the punishment is zero.
+In contrary, when the chosen cluster's size diverges from $\delta$, the objective function suffers \textit{loss}.
+In particular, when $w_i=0$ and $|C_i|=1$, the punishment is the most severe.
+This design doesn't follow the definition of $f(C)$ in Definition~\ref{def_centralized_clustering} strictly, where $f(C_i)=0$ when $|C_i|=1$, but our design echoes the definition by exerting the most severe punishment on the singleton clusters in the clustering solution.
 Choice of $\alpha_i$ affects the resultant clusters.
@@
 
-This is a integer linear optimization problem, which is solved by function $bintprog$ provided in MATLAB.
+The optimization formulation is an integer linear optimization problem, which is solved by the function $bintprog$ provided in MATLAB.
 Note that the proposed centralized solution is heuristic.
-There are two reasons for pursuing the heuristic scheme, first, the problem of centralized clustering is NP hard, and there is no efficient solution to solve it.
+We reiterate the reasons for pursuing the heuristic scheme, first, the problem of centralized clustering is NP hard, and there is no efficient solution to solve it.
 The second reason is, the collection of legitimate clusters is dependant on the network topology and spectrum availability in the network, thus to each specific CRN, the space of solution is different.
@@
 \subsubsection{Example of the Centralized Optimization}
-We look into how it the centralized scheme perform in the toy example of the CRN in Figure~\ref{fig1}.
-
-We let the cluster size $\delta$ to be 3.
+We look into how does the centralized scheme perform in the toy example of the CRN in Figure~\ref{fig1}.
+%
+We let the desired cluster size $\delta$ be 3.
 A collection of clusters $\mathcal{G}$ is obtained, which contains all the clusters satisfying the conditions of cluster in Section~\ref{def_cluster} and the sizes of clusters are 1, 2 or 3. 
 $\mathcal{G}=\{\{A\}, \{B\},\dots,\{B,C\},\{B,A\},\{B,H\},\cdots,\{B,A,C\},$\\$\{B,H,C\}, \{A,D,C\},\cdots\}$, $G = |\mathcal{G}|=38$.
-$\alpha_1$ and $\alpha_1$ are set as 0.2 and 0.8. 
-The clustering result of centralized programming is shown in Figure~\ref{fig:final_clustering_LP}.
-
-The formed clusters are $\{\{D,E,F\},\{A,C,G\},\{H,G\}\}$, the numbers of CCCs are 2, 3, 3.
+
+When $\alpha_1$ and $\alpha_1$ are set as 0.2 and 0.8, the formed clusters are shown in Figure~\ref{fig:final_clustering_LP}.
+%$\{\{D,E,F\},\{A,C,G\},\{H,G\}\}$, the numbers of CCCs are 2, 3, 3.
 The resulted clustering solutions from ROSS-DGA/DFA and SOC are shown in Figure~\ref{fig4} and Figure~\ref{fig:final_clustering_soc} respectively.%, clusters are $\{A,B,C,D,G\},\{E,F\},\{H\}$, and the numbers of CCCs are 2, 3, 4.
@@
 %ROSS-DFA generates the same result with ROSS-DGA in this example.
-As to the average number of CCCs, the results of ROSS, centralized and SOC are 2.66, 2.66, and 3 respectively. 
+
+As to the average number of CCCs, the results of ROSS (including both ROSS-DGA and ROSS-DFA), centralized and SOC are 2.66, 2.66, and 3 respectively. 
 Note there is one singleton cluster $C_H$ generated by SOC, which is not preferred.
-When the singleton cluster $\{E\}$ is excluded, the average number of common channels of SOC drops to 2.5. 
+When we take no account of the singleton clusters, the average number of common channels of SOC drops to 2.5. 
 \begin{figure}[ht]

### 2016-03-26 journal-draft/bare_jrnl_comsoc.tex
polished section 6, not done

@@
 Actually, debatable nodes extensively exist in CRN with larger scale.
-Figure~\ref{percentage_overlapping_node} shows the percentage of debatable nodes increases when the CRN network becomes denser.
 Debatable nodes should be exclusively associated with only one cluster and be removed from the other claiming clusters, this procedure is called \textit{cluster membership clarification}.
 We will introduce the solution for cluster membership clarification in the following.
-
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[width=0.7\linewidth]{percentage_overlapping_node.pdf}
-  \caption{The percentage of debatable nodes after phase I of ROSS.}\label{percentage_overlapping_node}
-\end{figure}
 
@@
 To have the same criterion to compare the overhead of signalling, we count \textit{the number of transmissions of control messages}, without distinguishing they are sent with broadcast or unicast.
-This metric is Synonymous with \textit{the number of updates} discussed in Section~\ref{ross}.
+This metric is synonymous with \textit{the number of updates} discussed in Section~\ref{ross}.
 
@@
 %Our simulation doesn't consider the behaviour in the physical layer,
-The number of transmission is depicted in Figure~\ref{control_msg}.
-Note that the curve for the centralized scheme is from theoretical analysis, which is $h+m+N$ as discussed beforehand.
-Note the overhead involved to construct the backbone (clusters) is not included.
+
 %Assume we use OSPF~\cite{BCJ10} to aggregate and disseminate information, then the best and worst complexity for is $\mathcal{O}(E)$, where $E$ is the number of edges in the graph which corresponds to the network.
@@
 Some notations are written as follows,  $h$: number of cluster heads, $m$: number of debatable nodes, $d$: number of demanding clusters, $D(s)$: the maximum distance between centralized controller and CR users.
+
+Figure~\ref{percentage_overlapping_node} shows the percentage of debatable nodes increases when the CRN network becomes denser, from which we can obtain the value of $m$.
+\begin{figure}[ht!]
+  \centering
+  \includegraphics[width=0.7\linewidth]{percentage_overlapping_node.pdf}
+  \caption{The percentage of debatable nodes after phase I of ROSS.}\label{percentage_overlapping_node}
+\end{figure}
+
+Figure~\ref{control_msg} shows the number of transmissions of SOC, the upper bound of the number of transmissions for ROSS, and the analytical number of transmissions of the centralised scheme. 
+Note that the curve for the centralized scheme is from theoretical analysis, which is $h+m+N$ as discussed beforehand.
+Note the overhead involved to construct the backbone (clusters) is not included.
 

### 2016-03-29 journal-draft/bare_jrnl_comsoc.tex
add todo at the start
replot Fig 1, 4
minor changes

@@
 %CR concept
+\todo[inline]{todo: polish section 6}
 \IEEEPARstart{C}{ognitive} radio (CR) is a promising technology to solve the spectrum scarcity problem~\cite{Mitola}.
@@
 $g_i$  & social connectivity degree of CR node $i$\\
-$C_i$  & the $i$th legitimate cluster (only adopted in Section~\ref{centralized_opt})\\
+$C_i$  & the $i$th legitimate cluster (only appear in Sec.~\ref{centralized_opt})\\
 \bottomrule
@@
 The available channels sensed by each CR node are: $K_A=\{1,2,3,4,5,6,10\}, K_B=\{1,2,3,5,7\}, K_C=\{1,3,4,10\}, K_D=\{1,2,3,5\}, K_E=\{2,3,5,7\}, K_F=\{2,4,5,6,7\}, K_G=\{1,2,3,4,8\}, K_H=\{1,2,5,8\}$.
-Dashed lines indicates two end nodes are within transmission range of each other.
-The number of common channels between the two nodes is put along with the edge.}
+The dashed edge indicates the end nodes are within each other's transmission range.
+The number of common channels between the two nodes is shown by the edge.}
 	\label{fig1}
@@
 \centering
-\subfigure[Node A stays in cluster $C(C)$, quits $C(H)$, $\Delta\vert K_{C(C)}\vert+\Delta\vert K_{C(H)}\vert=2$]{
+\subfigure[Node A stays in cluster $C(C)$, quits $C(H)$, $\Delta\vert K(C(C))\vert+\Delta\vert K(C(H))\vert=2$]{
 \includegraphics[width=0.435\linewidth]{figure4AinC.pdf}
@@
 \hspace{.15 in}
-\subfigure[Node A stays in cluster $C(H)$, quits $C(C)$, $\Delta\vert K_{C(C)}\vert+\Delta\vert K_{C(H)}\vert=1$]{
+\subfigure[Node A stays in cluster $C(H)$, quits $C(C)$, $\Delta\vert K(C(C))\vert+\Delta\vert K(C(H))\vert=1$]{
 \includegraphics[width=0.435\linewidth]{figure4AinH.pdf}
@@
   \includegraphics[width=0.5\linewidth]{final_clustering_ross.pdf}
-  \caption{Final formation of clusters, CCCs for each cluster is shown.}
+  \caption{Final formation of clusters, CCCs for each cluster is shown. $K(C(C)),K(C(E)),K(C(H))$ are shown beside corresponding clusters.}
   \label{fig4}
@@
 \hspace{0.15 in}
-\subfigure[Resulted from Centralized Optimization]{\includegraphics[width=0.435\linewidth]{final_clustering_LP}\label{fig:final_clustering_LP}}
+\subfigure[Resulted from the centralized clustering scheme]{\includegraphics[width=0.435\linewidth]{final_clustering_LP}\label{fig:final_clustering_LP}}
 \end{center}
-\caption{Final clusters formed in the example CRN network from Figure~\ref{fig1}}
+\caption{Final clusters formed in the example network when being applied with SOC and the centralized clustering scheme.}
 \label{fig:final_clustering}

### 2016-03-29 journal-draft/bare_jrnl_comsoc.tex
minor changes

@@
 $\mathcal{N}$  & collection of secondary users\\
-%$k_i$ & the working channel of user $i$\\
+$k(i)$ & the working channel of user $i$\\
 $\text{Nb}(i)$ & the neighborhood of CR node $i$    \\
@@
 \end{theorem}
-Here, \textit{Step} means a secondary user conducts Algorithm~\ref{clustering:theorem} once.
+Here, \textit{Step} means one secondary user conducts Algorithm~\ref{clustering:theorem} once.
 The Proof is in Appendix~\ref{proof_clustering:theorem}.
@@
 
-\subsubsection{Guarantee Availability of Common Control Channel}
+\subsubsection{Guarantee the Availability of Common Control Channel}
 %After deciding itself being cluster head, CR node broadcasts to notify its neighbours on the dedicated control channel, meanwhile, $i$'s initial cluster is formed immediately, which is $i$'s neighbourhood except for those nodes which have become cluster heads, \ie $C_i=(\text{Nb}_i\setminus \text{CHs})\cup i$.
@@
 $1\leq |C| \leqslant k$ where $|C|$ is the size of cluster $C$ and $k$ is a positive integer.
-We name the collection of such clusters as $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$ (the subscript $i$ is the unique index of cluster in $\mathcal{S}$, not the ID of cluster head of that cluster), $\mathcal{S}$ satisfies the following properties: $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$ and $K_{C_i}\neq \emptyset$ for any $i$ which satisfies $1\leq i \leq |\mathcal{S}|$.
-
-We give a new definition of the number of CCCs, which distinguishes the centralized clustering problem discussed in this paper.
-In this problem, the number of common control channels is $|K(C)|$ if $|C|>1$, and is zero when $|C|=1$.
-We use $f(C)$ to denote this new definition of the number of CCCs of a cluster $C$.
-The question of centralized clustering problem is to find a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, so that $\bigcup_{C_j\in \mathcal{S}'} C_j = N$, and $C_{j'}\cap C_j =\emptyset$ for $C_{j'}, C_j\in \mathcal{S}'$ and $j'\neq j$, so that $\sum_{C\in \mathcal{S}'} f$ is maximized.
+We name the collection of such clusters as $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$, where $\mathcal{S}$ satisfies the following properties: $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$ and $K(C(i))\neq \emptyset$ for any $i$ which satisfies $1\leq i \leq |\mathcal{S}|$.
+
+%, which distinguishes the centralized clustering problem discussed in this paper.
+We give a new definition of the number of CCCs, where the number of common control channels is $|K(C)|$ if $|C|>1$, and is zero when $|C|=1$.
+We use $f(C)$ to denote the number of CCCs of a cluster $C$ in the new definition.
+
+The centralized clustering problem is to find a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, so that $\bigcup_{C_j\in \mathcal{S}'} C_j = N$, and $C_{j'}\cap C_j =\emptyset$ for $C_{j'}, C_j\in \mathcal{S}'$ and $j'\neq j$, so that $\sum_{C\in \mathcal{S}'} f(C)$ is maximized.
 % when $|C|>1$, and $f(\cdot)=0$ when $|C|=1$.
 %As to $f(\cdot):z\rightarrow z$, under this problem setting, if only number of common channels are given consideration, only singleton clusters will be preferred, which contradicts to our goal of clustering CR nodes together, thus we choose $f(\cdot)= |K_{C}|\cdot |C|$, the product of number of common channels and cluster size.
-The decision version of centralized clustering in CRN is to ask whether there exists no-empty $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C\in \mathcal{S}'} f \geqslant \lambda$ where $\lambda$ is a real number.% in stead of to maximize $\sum_{C\in \mathcal{S}'} f$.
+The decision version of centralized clustering in CRN is to ask whether there exists a no-empty $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C\in \mathcal{S}'} f \geqslant \lambda$ where $\lambda$ is a real number.% in stead of to maximize $\sum_{C\in \mathcal{S}'} f$.
 \end{mydef}

### 2016-03-31 journal-draft/bare_jrnl_comsoc.tex
minor changes before processing section 6

@@
 
-A cognitive radio network (CRN) can be represented as an undirected graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{i, i'\} \in E$  if, and only if, there exists a channel $k \in \mathcal{K}$ with $k \in K_{i} \cap K_{i'}$.
+A cognitive radio network can be represented as an undirected graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{i, i'\} \in E$  if, and only if, there exists a channel $k \in \mathcal{K}$ with $k \in K_{i} \cap K_{i'}$.
 Note that we consider the channel availability only for \textit{one} snapshot of time.
@@
 \midrule
-$\mathcal{N}$  & collection of secondary users\\
+$\mathcal{N}$  & collection of secondary users, $N=|\mathcal{N}|$\\
+$\mathcal{K}$	& set of licensed channels\\
 $k(i)$ & the working channel of user $i$\\
@@
 In this phase, each CR node decides whether it is cluster head by comparing its connectivity vector with its neighbours.
-When CR node $i$ has larger individual connectivity degree than any neighbours except for those which have already become cluster heads (the appearance of cluster heads will be explained in next subsubsection), then node $i$ becomes clusters head.
+When CR node $i$ has lower individual connectivity degree than any neighbours except for those which have already become cluster heads (the appearance of cluster heads will be explained in next subsubsection), then node $i$ becomes clusters head.
 %In other words, CR node $i$ becomes cluster head if $d_i > d_k, \forall k\in \texttt{Nb}_i\setminus CHs$ ($CHs$ donate the cluster heads existing in $\texttt{Nb}_i$).
-If there is another CR node $j$ in its neighbourhood, which has the same individual connectivity degree with $i$, \ie $d_j = d_i$ and $d_j > d_{k}, \forall k\in \text{Nb}(j)\setminus \{\text{CHs}\cup i\}$, then the node out of $\{i, j\}$ with higher social connectivity degree becomes cluster head, and the other one becomes one member of it.
+If there is another CR node $j$ in its neighbourhood, which has the same individual connectivity degree with $i$, \ie $d_j = d_i$ and $d_j < d_{k}, \forall k\in \text{Nb}(j)\setminus \{\text{CHs}\cup i\}$, then the node out of $\{i, j\}$ with higher social connectivity degree becomes cluster head, and the other one becomes one member of it.
 If $g_i = g_j$ as well, node ID is used to break the tie, \ie the one with smaller node ID takes precedence and becomes cluster head.
@@
 
-After receiving the notification from a cluster head, a CR node, \eg $i$, is aware that it becomes one member of a cluster, then $i$ sets its individual connectivity degree to zero.
+After receiving the notification from a cluster head, a CR node, \eg $i$, is aware that it becomes one member of a cluster, then $i$ sets its individual connectivity degree to a positive number $M$, where $M > |\mathcal{K}|*N$.
 %, which is smaller than all the possible individual connectivity degrees in the CR network.
@@
 %\end{proof}
-When a CR node $i$ is associated to multiple clusters, \ie $i$ has received multiple notifications of cluster head eligibility from different CR nodes, $d_i$ is still set to zero.
-We manipulate the individual connectivity degree of the CR nodes, so that the nodes which locate outside of the a formed cluster can possibly become cluster heads, or be included into other clusters.
+We manipulate the individual connectivity degree of the CR nodes which are included into certain clusters, so that the nodes which locate outside of the a formed cluster can possibly become cluster heads, or be included into other clusters.
+When a CR node $i$ is associated to multiple clusters, \ie $i$ has received multiple notifications of cluster head eligibility from different CR nodes, $d_i$ is still set to $M$.
 %Then every CR node becomes either cluster head or one member of at least one cluster.
@@
 
-As to singleton congestion game, there exists pure equilibria which can be reached with best response update, and the upper bound of number of steps before convergence is $n^2*m$~\cite{Ackermann06purenash}, where $n$ is the number of players, and $m$ is the number of resources.
+As to singleton congestion game, there exists a pure equilibria which can be reached with the best response update, and the upper bound of number of steps before convergence is $n^2*m$~\cite{Ackermann06purenash}, where $n$ is the number of players, and $m$ is the number of resources.
 In our problem, the players are the debatable nodes, and the resources are the claiming clusters.
 Thus the upper bound of the number of steps can be expressed as $\mathcal{O}(N^3)$.
+
 In fact, the number of steps which are actually involved in this process is much smaller than $N^3$, as both $n$ and $m$ are considerably smaller than $N$.
-The amount of debatable nodes is illustrated in Figure~\ref{fig2}, which is between 10\% to 80\% of the total number of CR nodes in the network.
-The number of clusters heads, as discussed in the part of cluster size in Section~\ref{phaseI}, is decided by the network density and the CR node's transmission range.
-Only a small part of the CR nodes become cluster heads, as in the example shown in Figure~\ref{number_clusters_scale}, the number of clusters is only 3.4\% to 20\% of the total number of CR nodes.
+The percentage of debatable nodes in $\mathcal{N}$ is illustrated in Figure~\ref{percentage_overlapping_node}, which is between 10\% to 60\% of the total number of CR nodes in the network.
+The number of clusters heads, as discussed in Section~\ref{phaseI}, is dependent on the network density and the CR node's transmission range.
+As shown in Figure~\ref{number_clusters_scale}, the cluster heads take up only 3.4\% to 20\% of the total number of CR nodes.
 
@@
 The element of matrix $X$ is binary variable $x_{ij}, i=1, \ldots, G, j=1, \ldots, N$.
-$x_{ij}=1$ denotes cluster $i$ is one partition in the clustering solution, $x_{ij}=0$ means this partition is not adopted.
+%$x_{ij}=1$ denotes node $i$ is in the $j$th legitimate cluster, and the cluster is chosen in the solution, $x_{ij}=0$ means the $j$th legitimate cluster is not adopted by the partition.
 %Note that matrix $Q$ contains only constant elements, and matrix $X$ contains only binary variables.
@@
 As to the average number of CCCs, the results of ROSS (including both ROSS-DGA and ROSS-DFA), centralized and SOC are 2.66, 2.66, and 3 respectively. 
-Note there is one singleton cluster $C_H$ generated by SOC, which is not preferred.
-When we take no account of the singleton clusters, the average number of common channels of SOC drops to 2.5. 
+Note there is one singleton cluster $C(H)$ generated by SOC, which is not preferred.
+When we take no account of the singleton clusters, then the average number of common channels of SOC drops to 2.5. 
 \begin{figure}[ht]
@@
 
-\If{$\nexists j\in \text{Nb}_i\setminus \text{CHs}$, such that $d_i \leq d_j$}{
+\If{$\nexists j\in \text{Nb}_i\setminus \text{CHs}$, such that $d_i \geq d_j$}{
 	return 1;
 	}
-\eIf{$\exists j\in \text{Nb}_i\setminus CHs$, such that $d_i < d_j$}{
+\eIf{$\exists j\in \text{Nb}_i\setminus CHs$, such that $d_i > d_j$}{
 	return 0;}{
@@
 \begin{proof}
-Note that the formed cluster can be a singleton cluster, \ie cluster size is 1.
+%Note that the formed cluster can be a singleton cluster, \ie cluster size is 1.
+We consider a CRN which can be represented as a connected graph.
 To simplify the discussion, we assume the secondary users have unique individual connectivity degrees, and they have identical ID and social connectivity degrees.
@@
 
-We assume every node has at least one neighbour.
-It is further assumed that there exist some secondary users which are not included into any cluster and node $\alpha$ is of this kind.
-As node $\alpha$ is not contained in any cluster, there must be at least one node $\beta\in \text{Nb}_\alpha$, with $d_{\alpha} < d_{\beta}$.
+%we assume every node has at least one neighbour.
+Assuming there exist some secondary users which are not included into any cluster, and node $\alpha$ is of this kind.
+As node $\alpha$ is not contained in any cluster, there must be at least one node $\beta\in \text{Nb}_\alpha$, with $d_{\alpha} > d_{\beta}$.
 Otherwise, node $\alpha$ is eligible to form a cluster.
 If node $\beta$ becomes cluster head, node $\alpha$ is included.
-If node node $\beta$ is not cluster head, i.e., $\beta$ is not in any cluster, we can repeat the previous analysis made on node $\alpha$, and deduce that node $\beta$ has at least one neighbouring node $\gamma$ with $d_{\gamma}>d_{\beta}$.
-When no cluster head appears, this series of nodes with monotonically increasing $d_i$ might continue to grow, and only ceases because both of the individual connectivity degree and the total number of nodes are limited.
-The formed node series is shown as Figure~\ref{lemma1}.
+If node node $\beta$ is not cluster head, i.e., $\beta$ is not in any cluster, we can repeat the previous analysis made on node $\alpha$, and deduce that node $\beta$ has at least one neighbouring node $\gamma$ with $d_{\gamma} < d_{\beta}$.
+When no cluster head appears, this series of nodes with monotonically decreasing $d_i$ might continue to grow, and finally ceases when the individual connectivity degree is zero, or all secondary nodes are already in the series of nodes.
+An example of the formed node series is shown as Figure~\ref{lemma1}.
 

### 2016-03-31 journal-draft/bare_jrnl_comsoc.tex
polishing before section 6.1.2

@@
 To the best of our knowledge, SOC~\cite{Lazos09} is the only work emphasizing on the robustness of clustering structure from all previous work on clustering in CRN. 
-The authors of~\cite{Lazos09} compared SOC with other schemes based on the average number of common channels within each cluster, on which SOC outperforms other schemes by 50\%-100\%.
-This is because the schemes except for SOC are designed either for ad hoc network without consideration of channel availability~\cite{Basagni99}, or for CRN  but just considering basic connection among CR nodes~\cite{Zhao07}.
-Hence, we only compare the two versions of our scheme ROSS-DGA and ROSS-DFA with SOC to show the merits of ROSS, and also compare with the centralized scheme to see the gap with the global optima.
-In particular, we will investigate the following metrics,
+The authors of~\cite{Lazos09} compared SOC with other schemes in terms of the average number of CCCs of the formed cluster, on which SOC outperforms other schemes by 50\%-100\%. 
+SOC's comparison schemes are designed either for ad hoc network without consideration of channel availability~\cite{Basagni99}, or for CRN but just considering connection among CR nodes~\cite{Zhao07}.
+Hence, we only compare the our proposed schemes with SOC to show the ROSS's merits, besides, we compare the variants of ROSS with the centralized scheme to examine the gap with the global optima.
+In particular, we investigate the following metrics,
+
 \begin{itemize}
-\item \textit{Average number of common channels per non-singleton cluster.} 
+\item \textit{Average number of CCCs per non-singleton cluster.}
 This metric shows the robustness of the current non-singleton clusters.
-Non-singleton cluster refers the cluster whose cluster size is larger than 1, and can also be seen as unclustered node.
-Note that this metric along is biased and misleading, because the CR nodes with more channels could be formulated as singleton clusters.
-This happens in SOC solution, whose objective is to improve the average number of common channel over \textit{all} clusters, \ie including the singleton clusters, thus many CR nodes with more channels are turned into clusters.
+Non-singleton cluster refers the cluster whose cluster size is larger than 1.
+SOC~\cite{Lazos09} compares the average number of CCCs per cluster without distinguishing singleton clusters, which is biased as singleton clusters don't contribute to the cluster structure.
+%the CR nodes with more channels could be formulated as singleton clusters.
+%This happens in SOC solution, whose objective is to improve the average number of common channel over \textit{all} clusters, \ie including the singleton clusters, thus many CR nodes with more channels are turned into clusters.
 %As we try to look into the robustness of clusters of CRs, we exclude those singleton clusters.
 
-\item \textit{Number of unclustered CRs with moderate and vigorous intensity of primary users' activities.}
-This is a straight forward metric which reflects the robustness of clusters, as this metric directly shows how many nodes can make use of the cluster structure.
-With this metric, we investigate the performance of different schemes under different availability of spectrum in the CRN.
-When we vary the intensity of primary users' activity, \eg from low to medium level by increasing the number of primary users, this metric is the antonym of \textit{survival rate}, \ie, how many nodes are still within a certain cluster when some clusters have collapsed due to the newly added primary users.
+\item \textit{Number of singleton clusters.}
+This is a straight forward metric which reflects the effectiveness of clustering scheme.
+The less resulted singleton clusters means more secondary users are benefited from cluster structure.
+%robustness of clusters, as this metric directly shows how many nodes can make use of the cluster structure.
+When we investigate the performance with moderate and vigorous intensity of primary users' activities, this metric is the antonym of \textit{survival rate}, \ie, how many nodes are still within a certain cluster when some clusters have collapsed due to the newly added primary users.
+%When we vary the intensity of primary users' activity, \eg from low to medium level by increasing the number of primary users,
 
@@
 \item \textit{Amount of control messages involved.}
+We investigate the number of control messages involved in the clustering process.
 
@@
 The simulation is conducted with C++. 
-Certain number of CRs and PUs are deployed in a 2-dimensional Euclidean space.
+Certain number of CRs and PUs are deployed on a two-dimensional Euclidean plane.
 %Complying with the system model, the CR node residing within another CR node's transmission range is seen as neighbour of that CR node.
@@
 Simulation is divided into two parts, in the first part, we investigate the performance of centralized scheme, and the gap between the distributed schemes with the centralized scheme.
-The simulation of this part is conducted in a small network, as there is no polynomial time solution available to solve the centralized problem.
+This part of simulation is conducted in a small network, as there is no polynomial time solution available to solve the centralized problem.
 In the second part, we investigate the performance of the proposed distributed schemes thoroughly in the networks with different scales and densities.
@@
 10 primary users and 20 CR users are dropped randomly (with uniform distribution) within a square area of size $A^{2}$, where we set the transmission ranges of primary and CR users to $A/3$.
-There are 10 available channels. 
+%There are 10 available channels. 
 With this setting, the average number of neighbours of one CR user is 4.8.
-Each primary user randomly occupies one channel, and CR users are assumed to be able to sense the existence of primary users and identify available channels.
+%Each primary user randomly occupies one channel, and 
+CR users are assumed to be able to sense the existence of primary users and identify available channels.
 When clustering scheme is executed, around 7 channels are available on each CR node.
-The desired cluster size is 3, the parameters used in the \textit{punishment} for choosing the clusters with undesired sizes are set as follows, $\alpha_1 =  0.4$, $\alpha_2 =  0.6$.
-Performance results are averaged over 50 randomly generated topologies with equal parameters.
-The confidence interval shown in figure corresponds to 95\% confidence level.
-
-\subsubsection{Number of Common Control Channels in Non-singleton Clusters}
+
+The desired cluster size $\delta$ is 3, the parameters used in the \textit{punishment} for choosing the clusters with undesired sizes are set as follows, $\alpha_1 =  0.4$, $\alpha_2 =  0.6$.
+Performance results are averaged over 50 randomly generated topologies, and the confidence interval corresponds to 95\% confidence level.
+
+\subsubsection{Number of CCCs in Non-singleton Clusters}
 \label{ccc_20}
 %We first have a look at the average number of common channels per non-singleton cluster.
-Figure~\ref{ccc_per_nonsingleton} shows the average number of common channel of non-singleton clusters, as the singleton clusters (in other words unclustered nodes) don't execute any functionalities of clusters, which are has be discussed in Section~\ref{intro}.
-From Figure~\ref{ccc_per_nonsingleton}, we can see centralized schemes outperform distributed schemes.
-SOC achieves the most number of CCC than all the variants of ROSS.
+Figure~\ref{ccc_per_nonsingleton} shows the average number of common channel of non-singleton clusters,
+%as the singleton clusters (in other words unclustered nodes) don't execute any functionalities of clusters, which are has be discussed in Section~\ref{intro}.
+from which we can see the centralized schemes outperform distributed counterparts.
+As to the distributed schemes, SOC achieves the largest number of CCCs than all the variants of ROSS.
 The reason is, SOC is liable to group the neighbouring CRs which share the most abundant spectrum together, no matter how many of them are, thus the number of CCC of the formed clusters is higher.
-But this method leaves considerable number of CRs which have less spectrum not in any clusters.
-As to the variants of ROSS, the procedure of debatable nodes greedily looking for better affiliation improves the number of CCC, thus ROSS-DGA with and without size control outperform ROSS-DFA and its size control version respectively.
-We also notice that, the size control feature doesn't affect the number of CCC for both ROSS-DGA and ROSS-DFA.
+But this method leaves considerable number of CRs to form singleton clusters.
+
+As to the variants of ROSS, ROSS-DGA with and without size control outperform ROSS-DFA and its size control version respectively, this is due to the procedure that debatable nodes greedily look for better affiliation to improve the number of CCCs.
+We also notice that, the size control feature doesn't affect the number of CCCs for both ROSS-DGA and ROSS-DFA.
 This is because the desired cluster size happens to be the average size of clusters generated by ROSS-DGA and ROSS-DFA, then the size control functionality doesn't play effect to increase the number of CCCs.
 
-\subsubsection{Survival Rate of Clusters with Increasing Primary Users}
-With the number of PUs in CRN increases, or their operation becomes more intensive, some CCCs will no longer be available.
-If there is no common control channels available any more because of the new added PRs, the cluster is regarded as destroyed and the former cluster member CRs become unclustered CRs or in other words singleton clusters.
-
-We investigate the robustness of the formed clusters when they co-exist with primary users whose intensity of activities are varying.
+\subsubsection{Number of Singleton Clusters}
+When the number of PUs in CRN increases, or their operation becomes more intensive, some clusters don't seize any CCCs any more, so that the cluster members and the cluster heads become unclustered, or singleton clusters.
+%If there is no common control channels available any more because of the new added PRs, the cluster is regarded as destroyed and the former cluster member CRs become unclustered CRs or in other words singleton clusters.
+We investigate the number of singleton clusters with primary users whose intensity of activities are varying.
 After the clusters are formed under the influence of the initial 10 PUs, extra 100 PUs are added sequentially to the network.

### 2016-04-04 journal-draft/bare_jrnl_comsoc.tex
minor changes in Section 4 (theorem not included)

@@
 ROSS consists of two cascaded phases: \textit{cluster formation} and \textit{membership clarification}.
-With ROSS, CR nodes form clusters on the basis of the proximity of the available spectrum in their neighbourhood, and then some CR nodes finalize their cluster membership, i.e., belonging to one certain cluster, by interacting with certain neighbours.
+With ROSS, CR nodes form clusters on the basis of the proximity of the available spectrum in their neighbourhood.
+Afterwards, CR nodes belong to one certain cluster.
+%by interacting with certain neighbours.
 %is based on the spectrum sensing results in its neighbours , then
@@
 \label{phaseI}
-After conducting spectrum sensing and communication with neighbours, every CR node is aware of the available channels at itself and all its neighbours.
-For each CR user, two metrics are proposed to characterize the spectrum proximity between that CR user and its neighbourhood.
-As to CR node $i$, there are,
+After conducting spectrum sensing and communication with neighbours, every CR node is aware of the available channels available for themselves as well as for all its neighbors.
+For each CR user $i$, two metrics are proposed to characterize the spectrum proximity between $u$ and its neighborhood:
 %\newtheorem{def1}{Definition}
@@
 
-\item \textit{Individual connectivity degree} $d_i$: $d_i=\sum_{j\in \text{Nb}(i)}\vert K_i\cap K_j\vert$, denotes the sum of the numbers of common controls channels between node $i$ and every neighbour.
+\item \textit{Individual connectivity degree} $d_i$: $d_i=\sum_{j\in \text{Nb}(i)}\vert K_i\cap K_j\vert$.
+It denotes the sum of the numbers of common controls channels between node $i$ and every neighbour.
 It is an indicator of node $i$'s adhesive property to the CRN.
 
-\item \textit{Social connectivity degree} $g_i$: $g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$, which is the number of common channels which are available to CR node $i$ and all its neighbours.
+\item \textit{Social connectivity degree} $g_i$: $g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$. It is the number of common channels available to$i$ and all its neighbors.
 $g_i$ represents the ability of $i$ to form a robust cluster with its neighbours.
@@
 After introducing the connectivity vector, we proceed to introduce the first phase of algorithm ROSS.
-To put it briefly, in this phase cluster heads are determined at first, then clusters are formed on the basis of the cluster heads' neighbourhoods.
+To put it briefly, in this phase cluster heads are determined in the beginning. Then clusters are formed on the basis of the cluster heads' neighborhoods.
 
 \subsubsection{Determining Cluster Heads and Form the Initial Clusters}
-In this phase, each CR node decides whether it is cluster head by comparing its connectivity vector with its neighbours.
-When CR node $i$ has lower individual connectivity degree than any neighbours except for those which have already become cluster heads (the appearance of cluster heads will be explained in next subsubsection), then node $i$ becomes clusters head.
+In this phase, each CR node decides whether it is a cluster head by comparing its connectivity vector with its neighbors.
+When CR node $i$ has lower individual connectivity degree than any neighbors except for those which have already become cluster heads (the appearance of cluster heads will be explained in Section~...), then node $i$ becomes clusters head.
 %In other words, CR node $i$ becomes cluster head if $d_i > d_k, \forall k\in \texttt{Nb}_i\setminus CHs$ ($CHs$ donate the cluster heads existing in $\texttt{Nb}_i$).
-If there is another CR node $j$ in its neighbourhood, which has the same individual connectivity degree with $i$, \ie $d_j = d_i$ and $d_j < d_{k}, \forall k\in \text{Nb}(j)\setminus \{\text{CHs}\cup i\}$, then the node out of $\{i, j\}$ with higher social connectivity degree becomes cluster head, and the other one becomes one member of it.
-If $g_i = g_j$ as well, node ID is used to break the tie, \ie the one with smaller node ID takes precedence and becomes cluster head.
+If there is another CR node $j$ in its neighborhood which has the same individual connectivity degree as $i$, \ie $d_j = d_i$ and $d_j < d_{k}, \forall k\in \text{Nb}(j)\setminus \{\text{CHs}\cup i\}$, then the node out of $\{i, j\}$ with higher social connectivity degree becomes cluster head.
+The other nodes become a member of that cluster.
+If $g_i = g_j$ as well, the node ID is used to break the tie, \ie the one with smaller node ID becomes the cluster's head.
 %
 The node which becomes cluster head broadcasts a message of its eligibility of being cluster head to notify its neighbours, and claims its neighbourhood as its cluster.
-The pseudo code for deciding cluster head and forming initial clusters is in Algorithm~\ref{alg0} in appendix.
-
-After receiving the notification from a cluster head, a CR node, \eg $i$, is aware that it becomes one member of a cluster, then $i$ sets its individual connectivity degree to a positive number $M$, where $M > |\mathcal{K}|*N$.
+The pseudo code for the cluster head decision and the initial cluster formation is shown in Algorithm~\ref{alg0} in the appendix.
+
+After receiving the notification from a cluster head, a CR node $i$ is aware that it becomes a member of a cluster.
+Consequently, $i$ sets its individual connectivity degree to a positive number $M > |\mathcal{K}| \cdot N$.
 %, which is smaller than all the possible individual connectivity degrees in the CR network.
-Then node $i$ broadcasts its new individual connectivity degree to all its neighbours. 
+Then $i$ broadcasts its new individual connectivity degree to all its neighbors. 
 %wrong:
@@
 %\end{proof}
-We manipulate the individual connectivity degree of the CR nodes which are included into certain clusters, so that the nodes which locate outside of the a formed cluster can possibly become cluster heads, or be included into other clusters.
+We manipulate the individual connectivity degree of the CR nodes which are included in certain clusters.
+Hence, nodes located outside of the a formed cluster can possibly become cluster heads or can also be included into other clusters.
 When a CR node $i$ is associated to multiple clusters, \ie $i$ has received multiple notifications of cluster head eligibility from different CR nodes, $d_i$ is still set to $M$.
@@
 %Every CR user is involved in the clustering process and becomes either cluster head or member is described in theorem~\ref{clustering:theorem}.
-We have the following theorem to show that as long as a secondary user's individual connectivity degree is not zero, that secondary user will be integrated into a certain cluster, or become a cluster head.
+We have the following theorem to show that as long as a secondary user's individual connectivity degree is greater than zero, that secondary user will eventually be integrated into a certain cluster, or it eventually becomes a cluster head.
 \begin{theorem}

### 2016-04-05 journal-draft/bare_jrnl_comsoc.tex
finished 6.1

@@
 In this section, we evaluate the performances of all the variants of ROSS, \ie ROSS-DGA and ROSS-DFA, and that with cluster size control features.
-The latter is referred as ROSS-x-DGA/ROSS-x-DFA, where x is the desired cluster size.
+The latter is referred as ROSS-$\delta$-DGA/ROSS-$\delta$-DFA, where x is the desired cluster size.
 We choose SOC as comparison scheme.
@@
 %robustness of clusters, as this metric directly shows how many nodes can make use of the cluster structure.
-When we investigate the performance with moderate and vigorous intensity of primary users' activities, this metric is the antonym of \textit{survival rate}, \ie, how many nodes are still within a certain cluster when some clusters have collapsed due to the newly added primary users.
+When we investigate the performance with moderate and vigorous intensity of primary users' activities, this metric is the antonym of \textit{survival rate}, \ie, the percentage of nodes which are still within certain clusters.
 %When we vary the intensity of primary users' activity, \eg from low to medium level by increasing the number of primary users,
@@
 \subsubsection{Number of Singleton Clusters}
-When the number of PUs in CRN increases, or their operation becomes more intensive, some clusters don't seize any CCCs any more, so that the cluster members and the cluster heads become unclustered, or singleton clusters.
+%When the number of PUs in CRN increases, or their operation becomes more intensive, some clusters don't seize any CCCs any more, so that the cluster members and the cluster heads become unclustered, or singleton clusters.
 %If there is no common control channels available any more because of the new added PRs, the cluster is regarded as destroyed and the former cluster member CRs become unclustered CRs or in other words singleton clusters.
-We investigate the number of singleton clusters with primary users whose intensity of activities are varying.
-After the clusters are formed under the influence of the initial 10 PUs, extra 100 PUs are added sequentially to the network.
+%We investigate the number of singleton clusters with primary users whose intensity of activities are varying.
+Initially, clusters are formed with the presence of 10 PUs. 
+Afterwards, extra 20 batches of PUs are added to the network sequentially, and each batch includes 5 PUs. 
 %The transmission range and channel occupancy of the new PU is the same with the previous ones, \ie transmission range is $A/3$, and one channel out of 10 is randomly chosen to operate.
-Figure~\ref{singleton_clusters} shows the number of unclustered CRs with the increasing number of PUs.%, which indicates the vulnerability of clusters under varying availability of licensed spectrum.
-%
-We draw three conclusions corresponding to three comparisons shown in this figure,
+Figure~\ref{singleton_clusters} shows the number of unclustered CRs with the increasing number of PUs, from which two conclusions are drawn.
+%, which indicates the vulnerability of clusters under varying availability of licensed spectrum.
+%
+
 \begin{itemize}
-\item Centralized scheme with cluster size of 2 generates the most robust clusters, and SOC results in the most vulnerable clusters.
-When the desired cluster size is 3, the centralized scheme performs similarly with the variants of ROSS.
-The reason that centralized scheme with cluster size of 3 does not completely excel variants of ROSS is due to the favourable achievement of it: the uniformly sized clusters.
-As distributed schemes, variants of ROSS generate considerable amount of smaller clusters which are more likely to survive when PUs' activities become intense.
-The comparison on cluster sizes will be given in details in~\ref{cluster_size}.
+\item The centralized scheme with desired size of 2 generates the most robust clusters, and SOC results in the most vulnerable clusters.
+The centralized scheme with desired size of 3 doesn't surpass the variants of ROSS.
+The reason lies in the the uniformly sized clusters, whereas the variants of ROSS generate considerable amount of smaller clusters which are more likely to survive when PUs' activities become intense.
+%The comparison on cluster sizes will be given in Section~\ref{cluster_size}.
 % when the number of PRs is 10$\sim$30, when number of PUs is 30$\sim$60, same amount of unclustered CRs are generated with variants of ROSS.
@@
 
+ROSS with size control distinguishes itself as the size control avoid the appearance of the clusters with large size.
+
 \item Greedy algorithm improves survival rate. 
-ROSS-DGA improves the survival rate of ROSS-DFA, so does ROSS-x-DGA against ROSS-x-DFA.
-This complies with the observation in Figure~\ref{ccc_per_nonsingleton}.
-As the debatable CRs greedily update their affiliation with claiming clusters, and the metric for updating is the maximum increase of CCCs of the demanding clusters, the average number of CCCs in non-singleton clusters is improved.
+Greedy strategy adopted in the second phase of ROSS improves the robustness of clusters, i.e. ROSS-DGA exceeds ROSS-DFA, and ROSS-$\delta$-DGA surpasses ROSS-$\delta$-DFA.
+When the debatable CRs greedily update their affiliation with the claiming clusters, one of the metrics is the maximum increase of CCCs of the demanding clusters. 
+This observation complies with the result shown in Figure~\ref{ccc_per_nonsingleton}.
+
 %Meanwhile, sizes of more clusters become smaller also contributes more robustness.
-
-\item ROSS with size control is better than the other two distributed schemes.
-Conducting size control improves both ROSS-DGA and ROSS-DFA's performance when the number of new PUs is greater than 50.
-The size control decreases the clusters size and makes the clusters more robust when against PUs' activity.
 
@@
 
-\begin{figure*}[t]
+\begin{figure*}[th]
 \begin{multicols}{3}
@@
 
-Figure~\ref{size_control} depicts the empirical cumulative distribution of the CRs residing in certain sized clusters in 50 runs.
-The centralized schemes are able to form clusters which satisfy the requirement on cluster sizes strictly.
-When the desired size is 2, each generated cluster has two members, whereas when the desired size is 3, about 15\% CRs are formed into 2 node clusters.
-Both of ROSS-DFG and ROSS-DFA with size control feature also obtain clusters with homogeneous sizes.
+Figure~\ref{size_control} depicts the empirical cumulative distribution of the CRs residing in certain sized clusters which are generated in 50 runs.
+The centralized schemes form clusters which satisfy the requirement on cluster size strictly.
+%When the desired size is 2, each generated cluster has two members, whereas when the desired size is 3, about 15\% CRs are formed into 2 node clusters.
+As to ROSS-DFG and ROSS-DFA with size control mechanism, CR nodes averagely distributes in clusters whose sizes are 2, 3 and 4.
 %When ROSS-3-DFA is applied, most number of CRs are in 3 node clusters, nevertheless, slightly less nodes are found in 2 node and 4 node clusters, there are also considerable number of singleton clusters.
 %ROSS-3-DGA decreases the clusters sizes and results in more 2 node clusters, the second most CRs are found in 3 node clusters.
-The sizes of clusters generated by ROSS-DGA and ROSS-DFA are disperse, but appear better than SOC, i.e., the 50\% percentiles for ROSS-DGA, ROSS-DFA and SOC is 4.5, 5, and 5.5, and the 90\% percentiles for the three schemes are 8, 8, and 9.
+The sizes of clusters resulted from ROSS-DGA and ROSS-DFA are disperse, but appear to be better than SOC, i.e., the 50\% percentiles for ROSS-DGA, ROSS-DFA and SOC is 4.5, 5, and 5.5, and the 90\% percentiles for the three schemes are 8, 8, and 9.
 %Figure~\ref{size_control} shows distributed clustering schemes are not able to control cluster sizes perfectly, but ROSS-DGA and ROSS-DFA eliminate the clusters whose size diverges largely with the desired one, \ie single node clusters and clusters with size of 13 and 14.
+
 Note ROSS-DGA and ROSS-DFA with size control feature generate 10\%-20\% singleton clusters, which is due to the cluster pruning discussed in section~\ref{cluster_pruning}, whereas, without size control, only 3\% nodes are in singleton clusters.
@@
 
-In this section we compare the amount of control messages generated in different clustering schemes, \eg centralized scheme, ROC, and the variants of ROSS.
-
-In order to highlight the amount of control signalling only for clustering, we omit the process of neighbourhood discovery, which is premise for all clustering schemes.
+In this section we compare the amount of control messages involved in different clustering schemes, \ie centralized scheme, ROC, and the variants of ROSS.
+%In order to highlight the amount of control signalling only for clustering, 
+We omit the control messaged involved in the process of neighbourhood discovery, which is the premise for the clustering schemes.
 According to~\cite{complexity_aggregation_2011}, the message complexity is defined as the number of messages used by all nodes.
@@
 As to ROSS, the control messages are generated in both phases.
-In the first phase, %every CR node decides whether it is cluster head by comparing its spectrum robustness with its neighbours.
-When a CR node decides itself to be the cluster head, it forms one cluster with its neighbourhood, 
-each cluster head broadcasts one message containing its ID, cluster members and the set of CCCs in its cluster.
+In the first phase, when a CR node decides itself to be the cluster head, it broadcasts a message containing its ID, cluster members and the set of CCCs in its cluster.
 %As to ROSS with size control feature, there are same amount of cluster heads with ROSS without enabling size control feature, and the cluster head broadcasts the available channels of the pruned cluster.
-In the second phase, %membership clarification of debatable nodes is conducted.
-debatable node informs its claiming clusters by broadcasting its affiliation, and the claiming cluster's cluster head broadcasts message about its new cluster if its cluster's members are changed.
-The total number of times for all CR nodes to send control messages, \ie the total number of decisions related with clustering functionality, has been analysed in the part of convergence speed in Theorem~\ref{clustering:theorem} and Section~\ref{clustering:phaseII:game} respectively.
+In the second phase, a debatable node broadcasts its affiliation to inform its claiming clusters, then the $\text{CH}$s of the claiming clusters  broadcast message about the new cluster members if they are changed due to the debatable node's decision.
+The total number of the decisions involved in cluster formation has been analysed in Theorem~\ref{clustering:theorem} and Section~\ref{clustering:phaseII:game} respectively.
 
@@
 
-As to the centralized scheme, except for the calculation in the centralized control device, it also involves two phases of control message transmission.
-The first phase is information aggregation, in which every CR node's channel availability and neighbourhood is sent to the centralized controller.
+The centralized scheme is conducted at the centralized control device, but it involves two phases of control message transmission.
+The first phase is information aggregation, in which every CR node's channel availability and neighborhood is transmitted to the centralized controller.
 The second phase is broadcasting, where the final clustering solution is disseminated over the network to every CR node.
-%As basic communication primitive for wireless networks, 
+
 We adopt the algorithm proposed in~\cite{Efficient_broadcasting_gathering_adhoc} to broadcast and gather information as the algorithm is simple and self-stabilizing.
 This scheme needs building a backbone structure to support the communication, we use our generated cluster heads as the backbone and the debatable nodes as the gateway nodes between the backbone nodes.
-As the backbone is built once and can support transmission for multiple times, the messages involved in the clustering process are not included.
-Every CR node can be informed if the cluster heads broadcast the message sent from the controller or other cluster heads, then the number of transmission is $h+m$.
-As to information gathering, we assume that every cluster member sends the spectrum availability and its ID to its cluster head, which further forwards or the message to the controller.
+As the backbone is built once and can support transmission for multiple times, the messages involved in the clustering process are not counted.
+As to the process of information gathering, we assume that every cluster member sends the spectrum availability and its ID to its cluster head, which further forwards or the message to the controller.
 The number of transmission for information gathering is $N$.
-%As we adopt a simplified communication model, node's transmission is not influenced by collision or interference, 
-%Our simulation doesn't consider the behaviour in the physical layer,
-
-%Assume we use OSPF~\cite{BCJ10} to aggregate and disseminate information, then the best and worst complexity for is $\mathcal{O}(E)$, where $E$ is the number of edges in the graph which corresponds to the network.
-%The minimum number of edges is $n-1$ when the nodes form a line and each node has at more two neighbours, and the maximum number is $N*(N-1)/2$ when the nodes form a complete graph.
-%Thus the best message complexity of the centralized scheme is $\mathcal{O}{(N)}$ and the worst is $\mathcal{O}{(N^2)}$.
-
-%1. update membership to form X1, 
-%2. broadcast new X1, form new X2
-%3. broadcast X3
-
-%The complexity parameters are the number of nodes $n$ in network, number of clusters $h$.
-The message complexity, quantitative analysis of the number of messages, and the size of control messages are shown in Table \ref{tab_overhead}.
-Some notations are written as follows,  $h$: number of cluster heads, $m$: number of debatable nodes, $d$: number of demanding clusters, $D(s)$: the maximum distance between centralized controller and CR users.
-
-Figure~\ref{percentage_overlapping_node} shows the percentage of debatable nodes increases when the CRN network becomes denser, from which we can obtain the value of $m$.
+As to the process of dissemination, in an extreme situation where all the gateway nodes and the backbone nodes broadcast, the number of transmission will be $h + m$, where $h$ is the number of cluster heads, $m$ is number of debatable nodes, $d$ is the average number of demanding clusters for each debatable node.
+
+The number of control messages which are involved in both ROSS and the centralized scheme is related with the number of debatable nodes.
+Figure~\ref{percentage_overlapping_node} shows the percentage of debatable nodes when the CRN network becomes denser, from which we can obtain the value of $m$.
 \begin{figure}[ht!]
@@
 
+%As we adopt a simplified communication model, node's transmission is not influenced by collision or interference, 
+%Our simulation doesn't consider the behaviour in the physical layer,
+
+%Assume we use OSPF~\cite{BCJ10} to aggregate and disseminate information, then the best and worst complexity for is $\mathcal{O}(E)$, where $E$ is the number of edges in the graph which corresponds to the network.
+%The minimum number of edges is $n-1$ when the nodes form a line and each node has at more two neighbours, and the maximum number is $N*(N-1)/2$ when the nodes form a complete graph.
+%Thus the best message complexity of the centralized scheme is $\mathcal{O}{(N)}$ and the worst is $\mathcal{O}{(N^2)}$.
+
+%1. update membership to form X1, 
+%2. broadcast new X1, form new X2
+%3. broadcast X3
+
+%The complexity parameters are the number of nodes $n$ in network, number of clusters $h$.
+The message complexity, quantitative analysis of the number of control messages involved in clustering, and the size of control messages are shown in Table \ref{tab_overhead}.
+%$D(s)$: the maximum distance between centralized controller and CR users.
+%
 Figure~\ref{control_msg} shows the number of transmissions of SOC, the upper bound of the number of transmissions for ROSS, and the analytical number of transmissions of the centralised scheme. 
-Note that the curve for the centralized scheme is from theoretical analysis, which is $h+m+N$ as discussed beforehand.
-Note the overhead involved to construct the backbone (clusters) is not included.
+%Note that the curve for the centralized scheme is from theoretical analysis, which is $h+m+N$ as discussed beforehand.
+%Note the overhead involved to construct the backbone (clusters) is not included.
 
@@
 % Scheme 					&   Number of transmissions 					& Content of message \\ \hline
-% ROSS-DGA, ROSS-x-DGA 		&   $h+2*m^2c$ (upper bound)
+% ROSS-DGA, ROSS-$\delta$-DGA 		&   $h+2*m^2c$ (upper bound)
 %				& $ID_{H_C}$ and $K_C$ for $h+m^2c$ times, notification to join one cluster for $m^2c$ times					\\ \hline
-% ROSS-DFA, ROSS-x-DFA 		&   $h+ 2m$	 (upper bound) 						& $ID_{H_C}$ and $K_C$ for $h+m$ times, notification to join one cluster for $m$ times	 					\\ \hline
+% ROSS-DFA, ROSS-$\delta$-DFA 		&   $h+ 2m$	 (upper bound) 						& $ID_{H_C}$ and $K_C$ for $h+m$ times, notification to join one cluster for $m$ times	 					\\ \hline
 % SOC 						&   $3*n$					& $\{K_i\}, i\in M\subseteq \texttt{Nb}_i$						\\ \hline
@@
 \hline
- Scheme 				&Message Complexity 	&   Quantitative number of messages 		& Content of message 									\\ \hline
- ROSS-DGA, ROSS-x-DGA 	&$\mathcal{O}(N^3)$ (worst case)		&   $h+2*m^2d$ (upper bound)  				&   \multirow{2}{*}{\parbox{6.4cm}{Phase I: notification from cluster head (1 byte), new individual connectivity degree (1 byte);  Phase II: update of debatable nodes' affiliation (1 byte), claiming clusters' new membership ($|C_i|$ bytes)}}								\\ \cline{1-3}
- ROSS-DFA, ROSS-x-DFA 	&$\mathcal{O}(N)$ (worst case)		&   $h + 2m$	 (upper bound) 					& 	      												\\ \hline
- SOC 					&$\mathcal{O}(N)$		&   $3*N$									& $C_i$ ($|C_i|$ bytes), $K_i$ ($P$ bytes), $i\in \mathcal{N}$						\\ \hline
+ Scheme 				&Message Complexity 	&   Quantitative number of messages 		& Content of message (size of message) 									\\ \hline
+ ROSS-DGA, ROSS-$\delta$-DGA 	&$\mathcal{O}(N^3)$ (worst case)		&   $h+2*m^2d$ (upper bound)  				&   \multirow{2}{*}{\parbox{6.4cm}{Phase I: notification from cluster head (1 byte), new individual connectivity degree (1 byte);  Phase II: update of debatable nodes' affiliation (1 byte), claiming cluster$i$' new membership ($|C(i)|$ bytes)}}								\\ \cline{1-3}
+ ROSS-DFA, ROSS-$\delta$-DFA 	&$\mathcal{O}(N)$ (worst case)		&   $h + 2m$	 (upper bound) 					& 	      												\\ \hline
+ SOC 					&$\mathcal{O}(N)$		&   $3*N$									& $C(i)$ ($|C(i)|$ bytes), $K(C(i))$ ($|\mathcal{P}|$ bytes), $i\in \mathcal{N}$						\\ \hline
  Centralized			&$\mathcal{O}(N)$			&	$h + m + N$ (upper bound)~\cite{Efficient_broadcasting_gathering_adhoc}		& $\{C\}$ ($|C_i|*N$ bytes)        					\\ \hline
@@
   \includegraphics[width=0.7\linewidth]{number_controlMsg.pdf}
-  \caption{Number of control messages, note the curves for ROSS-DGA and ROSS-DFA are the upper bounds of the number of messages, the curve of centralized scheme reflects an ideal situation.}
+  \caption{Number of control messages. Note the curves for ROSS-DGA and ROSS-DFA are the upper bounds of the number of messages, the curve of centralized scheme reflects an extreme situation.}
   \label{control_msg}
@@
 Figure~\ref{ccc_large_scale} illustrates the average number of CCCs of the non-singleton clusters.
-It shows when $N=100$, variants of ROSS have 30\% less CCCs than SOC, but this gap is decreased significantly when $N$ is 200 and 300, \ie when $N=300$, number of CCCs achieved by ROSS variants (except for ROSS-x-DFA) is almost the same with that resulted from SOC.
+It shows when $N=100$, variants of ROSS have 30\% less CCCs than SOC, but this gap is decreased significantly when $N$ is 200 and 300, \ie when $N=300$, number of CCCs achieved by ROSS variants (except for ROSS-$\delta$-DFA) is almost the same with that resulted from SOC.
 
@@
 this is also observed in the evaluation in Section \ref{ccc_20} where $N=20$.
-When the network becomes denser, even this metric favours SOC as discussed in the beginning of Section~\ref{performance}, ROSS-DGA achieves even more CCCs than SOC, and ROSS-DFA and ROSS-x-DGA increase the number of CCCs visibly.
+When the network becomes denser, even this metric favours SOC as discussed in the beginning of Section~\ref{performance}, ROSS-DGA achieves even more CCCs than SOC, and ROSS-DFA and ROSS-$\delta$-DGA increase the number of CCCs visibly.
 

### 2016-04-05 journal-draft/bare_jrnl_comsoc.tex
finished 6, and randomly proofread to shorten the pages, now 14 pages!

@@
 \usepackage{graphicx}
+\usepackage{sidecap}
 \usepackage{kantlipsum} %<- For dummy text
@@
 Cluster structure in cognitive radio networks facilitates cooperative spectrum sensing, routing and other functionalities.
-The availability of unlicensed channels which are available for every member in a cluster decides the survival of that cluster from licensed users' influence.
-Thus in order to be robust against licensed users, there should be more unlicensed channels in the clusters.
-In the process of forming clusters, every secondary user needs to decide with whom to form a cluster, or which cluster to join.
+The availability of unlicensed channels which are available for every member in a cluster decides the robustness of that cluster against the licensed users' influence.
+Thus there should be more unlicensed channels in the clusters.
+In the process of forming clusters, every secondary user decides with whom to form a cluster, or which cluster to join.
 Congestion game model is adopted to analyse this process, which not only contributes the algorithm design directly, but also provides guarantee of convergence into Nash Equilibrium and convergence speed.
 %
-Our proposed distributed clustering scheme outperforms the comparison scheme in terms of robustness against primary users, convergence speed and volume of control messages.
+Our proposed distributed clustering scheme outperforms the comparison scheme in terms of cluster robustness against the primary users, convergence speed and volume of control messages.
 Furthermore, the proposed clustering solution is versatile to fulfil other requirements such like fast convergence and cluster size control.
-Besides, we prove the clustering problem to be NP-hard, and also propose the centralized solution.
+Besides, we prove the clustering problem is NP-hard, and also propose the centralized solution.
 The extensive simulation supports our claims.
@@
 %CR concept
-\todo[inline]{todo: polish section 6}
 \IEEEPARstart{C}{ognitive} radio (CR) is a promising technology to solve the spectrum scarcity problem~\cite{Mitola}.
@@
 In contrast, unlicensed users can only access the licensed spectrum after validating the channel is unoccupied by licensed users.
-This refers to the process of sensing a particular channel and verifying (with a previously specified probability of error) that it is not used by a primary user currently.
+This refers to the process of sensing a particular channel and verifying (with a previously specified probability of error) it is not used by a primary user currently.
 In this hierarchical spectrum access model~\cite{zhao_survey_DSA_2007}, the licensed users are also called primary users (PU), and the CR users are known as secondary users and constitute the cognitive radio networks (CRN).
@@
 Secondary users conduct spectrum sensing independently and sequentially on all licensed channels.
-The sensing duration and frequency on one channel is a research topic~\cite{sensing_survey_2009}, and we assume that every node can detect the presence of primary user on each channel with certain accuracy.
+%The sensing duration and frequency on one channel is a research topic~\cite{sensing_survey_2009}, and 
+We assume that every node can detect the presence of primary user on each channel with certain accuracy.
 \footnote{The spectrum availability can be validated with a certain probability of detection.
@@
 We denote $K_i \subseteq \mathcal{K}$ as the set of available channels for $i$.
-
+%
 %One dedicated control channel is assumed to be available for all the secondary nodes to exchange control messages with neighbours in the process of cluster formation.
@@
 %Secondary users have the same transmission range on both licensed and control channel, and the communication links are reciprocal.
-
+%
 We adopt the unit disk model~\cite{unitDiskModel} for the transmission of both primary and CR users.
-Both primary users and CR users have fixed transmission ranges respectively, and the all the channels are regarded to be identical in terms of signal propagation.
+Both primary users and CR users have fixed transmission ranges respectively, and all the channels are regarded to be identical in terms of signal propagation.
 If a CR node locates within the transmission range of primary user $p$, that CR node is not allowed to use the channel $k(p)$.
@@
 Over the control channel, a secondary user $i$ can exchange its spectrum sensing result $K_i$ to any $i' \in \text{Nb}(i)$.
-It is available for any secondary node $i$ to exchange control messages with any other node in its proximity (or neighborhood) $\text{Nb}(i)$ during the cluster formation phase.
+It is available for any secondary node $i$ to exchange control messages with any other node in its neighborhood $\text{Nb}(i)$ during the cluster formation phase.
 $\text{Nb}(i)$ is simply defined as the set of nodes located within the transmission range of $i$.
@@
 Thus I think it is necessary to leave it here.}
-
------------ No modifications from here on ... -------------
 
@@
 
-\section{Distributed Coordination Framework: Clustering Algorithm}
+\section{Clustering Algorithm: ROSS}
 \label{ross}
 
-In this section, we introduce the distributed clustering scheme ROSS which leads to robust clusters against primary users' influence.
+In this section we introduce the distributed clustering scheme ROSS which leads to robust clusters against PU' influence.
 ROSS consists of two cascaded phases: \textit{cluster formation} and \textit{membership clarification}.
@@
 
-\item \textit{Social connectivity degree} $g_i$: $g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$. It is the number of common channels available to$i$ and all its neighbors.
+\item \textit{Social connectivity degree} $g_i$: $g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$. It is the number of common channels available to $i$ and all its neighbors.
 $g_i$ represents the ability of $i$ to form a robust cluster with its neighbours.
@@
 % \includegraphics{figure1.pdf}
-	\caption{Connectivity graph and the connectivity vector $(d_i, g_i)$ at each node.
-The available channels sensed by each CR node are: $K_A=\{1,2,3,4,5,6,10\}, K_B=\{1,2,3,5,7\}, K_C=\{1,3,4,10\}, K_D=\{1,2,3,5\}, K_E=\{2,3,5,7\}, K_F=\{2,4,5,6,7\}, K_G=\{1,2,3,4,8\}, K_H=\{1,2,5,8\}$.
-The dashed edge indicates the end nodes are within each other's transmission range.
-The number of common channels between the two nodes is shown by the edge.}
+	\caption{Connectivity graph and the connectivity vector $(d_i, g_i)$ for each node.
+The available channels sensed by each node are: $K_A=\{1,2,3,4,5,6,10\}, K_B=\{1,2,3,5,7\}, K_C=\{1,3,4,10\}, K_D=\{1,2,3,5\}, K_E=\{2,3,5,7\}, K_F=\{2,4,5,6,7\}, K_G=\{1,2,3,4,8\}, K_H=\{1,2,5,8\}$.
+Dashed edge indicates the end nodes are within each other's transmission range.
+The number of common channels between two nodes is shown by the edge.}
 	\label{fig1}
@@
 In this phase, each CR node decides whether it is a cluster head by comparing its connectivity vector with its neighbors.
-When CR node $i$ has lower individual connectivity degree than any neighbors except for those which have already become cluster heads (the appearance of cluster heads will be explained in Section~...), then node $i$ becomes clusters head.
+When CR node $i$ has lower individual connectivity degree than any neighbors except for those which have already become cluster heads (the appearance of cluster heads will be explained in Section~\ref{membershipClarification}), then node $i$ becomes clusters head.
 %In other words, CR node $i$ becomes cluster head if $d_i > d_k, \forall k\in \texttt{Nb}_i\setminus CHs$ ($CHs$ donate the cluster heads existing in $\texttt{Nb}_i$).
@@
 After executing phase I of ROSS, there are some secondary users which become cluster heads.
-The cluster head and its neighbourhood (except for the CHs) become a cluster.
-It is possible that there is no CCCs for some formed clusters, and we solve this problem with the following method.
+The cluster head and its neighbourhood (except for the CHs) form a cluster.
+It is possible that certain formed clusters don't own CCCs, then we solve this problem with the following method.
 
@@
   \centering
-  \includegraphics[width=0.4\linewidth]{clusters_denseNetwork_2.pdf}
+  \includegraphics[width=0.3\linewidth]{clusters_denseNetwork_2.pdf}
   \caption{Clusters formation in extremely dense CRN. Black dots are cluster heads, other cluster members are not drawn.}
@@
 Given $r$=10 and $l$=50, the number of formed clusters is shown in Figure~\ref{number_clusters_scale}.
-With the increase of CR users in the network, network density increases linearly (the Y axis label is the average number of neighbours), and the number of formed clusters also increases and approaches to the the upper bound of 25 which complies with the estimation.
+With the increase of CR users, network density increases linearly (the Y axis label is the average number of neighbours), and the number of formed clusters also increases and approaches to the the upper bound of 25 which complies with the estimation.
 
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{number_clusters_upperBound.pdf}
+  \includegraphics[width=0.7\linewidth]{number_clusters_upperBound.pdf}
   \caption{The correlation between the number of formed clusters and network density.
@@
   \centering
-  \includegraphics[width=0.6\linewidth]{figure2.pdf}
+  \includegraphics[width=0.5\linewidth]{figure2.pdf}
   \caption{Clusters formation after the first phase of ROSS. There are some nodes being debatable nodes, \ie belonging to more than one cluster.}
@@
 \subsection{Phase II - Membership Clarification}
+\label{membershipClarification}
 %\subsubsection*{Problem Description}
@@
 
-This procedure raises a concern that the debatable nodes may never stop changing their affiliations, as debatable nodes' choices seem to be dependent on each other, and the infinite chain effect never ceases.
+This procedure raises a concern that the debatable nodes may never stop changing their affiliations, as debatable nodes' choices seem to be dependent on each other, thus the infinite chain effect never ceases.
 %  update their choices based on other debatable nodes' choices, and this process 
@@
 When $j$ leaves cluster $C$, which decrease cluster $C$'s cluster size, and could possibly trigger node $i$ to alter its previous decision to leave $C$, as $C$'s size is smaller now and leaving it may result in more increase of CCCs in $S_i$.
-At this point of time, debatable node $j$ may rejoin cluster $C$ duo to the changes in $S_j$, then both node $i$ and $j$ are facing the \textit{same}\footnote{Actually it is not totally same as before, as there are some new changes within $S_j$.} situation again.
+At this point of time, debatable node $j$ may rejoin cluster $C$ due to the changes in $S_j$, then both node $i$ and $j$ face the \textit{same}\footnote{Actually it is not totally same as before, as there are some new changes within $S_j$.} situation again.
 %To maximize the increase of common channel in clusters in $S_j$, $j$ either stays in $C$, or leaves cluster $C$ and stay another cluster in $S_j$.
@@
 %and the choice of $j$ to stay in $C$ or not possibly changes $C$'s membership and  which potentially further triggers node $i$ to alter its previous decision. 
-Thence, we must answer this concern raised when implementing ROSS-DGA.
+Thence, we need to answer this concern before implementing ROSS-DGA.
 %, and if it converges, how good such a distributed scheme performs. 
-In the following we show that the process of membership clarification can be formulated into a singleton congestion game, and a equilibrium is reached after a finite number of best response updates made by the debatable nodes.
+In the following we show that the process of membership clarification can be formulated into a game, and a equilibrium is reached after a finite number of best response updates made by the debatable nodes.
 
@@
 %The concern on convergence appears again as we have discussed in the previous subsubsection.
-We give proof on convergence under game theoretic framework.
+%We give proof on convergence under game theoretic framework.
 \begin{figure}[ht!]
@@
 %\todo[inline]{check}
-The centralized clustering scheme aims to form clusters with desired sizes, meanwhile the total number of common control channels of all clusters is maximized.
+The centralized clustering scheme aims to form clusters with desired sizes, meanwhile the total number of CCCs of all clusters is maximized.
 In the following, we refer this problem as \textit{centralized clustering}, and give the formal problem definition.
@@
 
-The objective is a sum of two parts, the first part is the sum of products of cluster size and the corresponding number of CCCs.
-The first part is the only metric adopted by the scheme SOC~\cite{Lazos09}.
+The objective is a sum of two parts, the first part is the sum of products of cluster size and the corresponding number of CCCs, which is the sole metric adopted by the scheme SOC~\cite{Lazos09}.
 The second part is the \textit{punishment} for choosing the clusters whose sizes are not $\delta$.
-In fact, the second part is particularly designed to eliminates the drawbacks of SOC, \ie SOC produces a large number of singleton clusters and a few very large clusters which access affluent unlicensed spectrum.
-In practical computation, we minimize the opposite of the first part, then the punishment is a positive value.
-
+In fact, the second part is particularly designed to eliminates the drawbacks of SOC, \ie SOC produces a large number of singleton clusters and a few large clusters.
+In practical computation, we minimize the opposite of the first part, and the punishment is a positive value.
+%
 The first constraint restricts each node $j$ to reside in exactly one cluster.
-In the second constraint, $w_i$ is an auxiliary binary variable, which denotes whether cluster $C_i$ is chosen by the solution, in particular, 
+In the second constraint, $w_i$ is an auxiliary binary variable which denotes whether cluster $C_i$ is chosen by the solution, in particular, 
 $$
@@
 $$
-The second constraint regulates that when the $i$th legitimate cluster $C_i$ is chosen, then  there are $|C_i|$ elements in $i$th row in matrix $X$, which are 1.
+The second constraint regulates when the $i$th legitimate cluster $C_i$ is chosen, the number of elements which are 1 in the $i$th row of the matrix $X$ is $|C_i|$.
 %
@@
 A collection of clusters $\mathcal{G}$ is obtained, which contains all the clusters satisfying the conditions of cluster in Section~\ref{def_cluster} and the sizes of clusters are 1, 2 or 3. 
-$\mathcal{G}=\{\{A\}, \{B\},\dots,\{B,C\},\{B,A\},\{B,H\},\cdots,\{B,A,C\},$\\$\{B,H,C\}, \{A,D,C\},\cdots\}$, $G = |\mathcal{G}|=38$.
-
-When $\alpha_1$ and $\alpha_1$ are set as 0.2 and 0.8, the formed clusters are shown in Figure~\ref{fig:final_clustering_LP}.
+$\mathcal{G}=\{\{A\}, \{B\},\dots,\{B,C\},\{B,A\},\{B,H\},\cdots,\{B,A,C\},$\\$\{B,H,C\}, \{A,D,C\},\cdots\}$, and $G = |\mathcal{G}|=38$.
+
+When $\alpha_1$ and $\alpha_1$ are set as 0.2 and 0.8, the formed clusters are shown in Fig.~\ref{fig:final_clustering_LP}.
 %$\{\{D,E,F\},\{A,C,G\},\{H,G\}\}$, the numbers of CCCs are 2, 3, 3.
-The resulted clustering solutions from ROSS-DGA/DFA and SOC are shown in Figure~\ref{fig4} and Figure~\ref{fig:final_clustering_soc} respectively.%, clusters are $\{A,B,C,D,G\},\{E,F\},\{H\}$, and the numbers of CCCs are 2, 3, 4.
+The resulted clustering solutions from ROSS-DGA/DFA and SOC are shown in Fig.~\ref{fig4} and Fig.~\ref{fig:final_clustering_soc} respectively.%, clusters are $\{A,B,C,D,G\},\{E,F\},\{H\}$, and the numbers of CCCs are 2, 3, 4.
 %The solution resulted from ROSS-DGA is $\{\{B,H,G\},\{C,A\},\{D,E,F\}\}$ (in Figure~\ref{fig4}), the numbers of CCCs are 2, 4, 2.
@@
 SOC's comparison schemes are designed either for ad hoc network without consideration of channel availability~\cite{Basagni99}, or for CRN but just considering connection among CR nodes~\cite{Zhao07}.
-Hence, we only compare the our proposed schemes with SOC to show the ROSS's merits, besides, we compare the variants of ROSS with the centralized scheme to examine the gap with the global optima.
-In particular, we investigate the following metrics,
+Hence, we only compare our proposed schemes with SOC  to show the ROSS's merits as a distributed scheme, and compare with the centralized scheme to examine the gap with the global optima.
+In particular, we investigate the following metrics.
 
@@
 Specific clusters size is pursued in many applications due to energy preservation and the system design ~\cite{clustering_globecom11}.
-We will present the distribution of CRs residing in the formed clusters, and the number of generated clusters through multiple simulations.
+We will present the distribution of CRs residing in the formed clusters with different sizes.
 
@@
 
-The simulation is conducted with C++. 
+The simulation is written in C++. 
 Certain number of CRs and PUs are deployed on a two-dimensional Euclidean plane.
@@
 All primary and CR users are assumed to be static during the process of clustering.
-
-Simulation is divided into two parts, in the first part, we investigate the performance of centralized scheme, and the gap between the distributed schemes with the centralized scheme.
-This part of simulation is conducted in a small network, as there is no polynomial time solution available to solve the centralized problem.
-In the second part, we investigate the performance of the proposed distributed schemes thoroughly in the networks with different scales and densities.
+%
+Simulation consists of two parts, in the first part, we investigate the performance of centralized scheme, and the gap between the distributed schemes and the centralized scheme.
+This part is conducted in a small network, as there is no polynomial time solution available to solve the centralized problem.
+In the second part, we investigate the performance of the proposed distributed schemes in the CRN with different scales and densities.
 
@@
 %We first have a look at the average number of common channels per non-singleton cluster.
-Figure~\ref{ccc_per_nonsingleton} shows the average number of common channel of non-singleton clusters,
+Figure~\ref{ccc_per_nonsingleton} shows the average number of the CCCs of non-singleton clusters,
 %as the singleton clusters (in other words unclustered nodes) don't execute any functionalities of clusters, which are has be discussed in Section~\ref{intro}.
-from which we can see the centralized schemes outperform distributed counterparts.
+from which we can see the centralized schemes outperform the distributed schemes.
 As to the distributed schemes, SOC achieves the largest number of CCCs than all the variants of ROSS.
@@
 
-As to the variants of ROSS, ROSS-DGA with and without size control outperform ROSS-DFA and its size control version respectively, this is due to the procedure that debatable nodes greedily look for better affiliation to improve the number of CCCs.
-We also notice that, the size control feature doesn't affect the number of CCCs for both ROSS-DGA and ROSS-DFA.
-This is because the desired cluster size happens to be the average size of clusters generated by ROSS-DGA and ROSS-DFA, then the size control functionality doesn't play effect to increase the number of CCCs.
+As to the variants of ROSS, greedy mechanism increases CCCs in non-singleton clusters significantly.
+%, this is due to the procedure that debatable nodes greedily look for better affiliation to improve the number of CCCs.
+We also notice that the size control feature doesn't affect the number of CCCs for both ROSS-DGA and ROSS-DFA.
+Size control mechanism converts the large clusters into small ones, but meanwhile clusters with the desired sizes have to be made when forming smaller clusters is possible.
+%, which can also be observed in the large scale CRN in Section~\ref{largeScaleCRN}.
+
+%This is because the desired cluster size happens to be the average size of clusters generated by ROSS-DGA and ROSS-DFA, then the size control functionality doesn't play effect to increase the number of CCCs.
 
@@
 \begin{itemize}
-\item The centralized scheme with desired size of 2 generates the most robust clusters, and SOC results in the most vulnerable clusters.
+\item The centralized scheme with desired size of two generates the most robust clusters, and SOC results in the most vulnerable clusters.
 The centralized scheme with desired size of 3 doesn't surpass the variants of ROSS.
@@
 
-\item Greedy algorithm improves survival rate. 
+\item Greedy algorithm improves the survival rate. 
 Greedy strategy adopted in the second phase of ROSS improves the robustness of clusters, i.e. ROSS-DGA exceeds ROSS-DFA, and ROSS-$\delta$-DGA surpasses ROSS-$\delta$-DFA.
-When the debatable CRs greedily update their affiliation with the claiming clusters, one of the metrics is the maximum increase of CCCs of the demanding clusters. 
+When the debatable CRs greedily update their affiliations, one of the metrics is the maximum increase of CCCs of the demanding clusters. 
 This observation complies with the result shown in Figure~\ref{ccc_per_nonsingleton}.
@@
 %In order to highlight the amount of control signalling only for clustering, 
-We omit the control messaged involved in the process of neighbourhood discovery, which is the premise for the clustering schemes.
+We omit the control messaged involved in the process of neighbourhood discovery, which is the premise for any clustering scheme.
 According to~\cite{complexity_aggregation_2011}, the message complexity is defined as the number of messages used by all nodes.
@@
 The first phase is information aggregation, in which every CR node's channel availability and neighborhood is transmitted to the centralized controller.
-The second phase is broadcasting, where the final clustering solution is disseminated over the network to every CR node.
+The second phase is broadcasting, where the clustering solution is disseminated to every CR node.
 
@@
 As the backbone is built once and can support transmission for multiple times, the messages involved in the clustering process are not counted.
-As to the process of information gathering, we assume that every cluster member sends the spectrum availability and its ID to its cluster head, which further forwards or the message to the controller.
-The number of transmission for information gathering is $N$.
-As to the process of dissemination, in an extreme situation where all the gateway nodes and the backbone nodes broadcast, the number of transmission will be $h + m$, where $h$ is the number of cluster heads, $m$ is number of debatable nodes, $d$ is the average number of demanding clusters for each debatable node.
+As to the process of information gathering, we assume that every cluster member sends the spectrum availability and its ID to its cluster head, which further forwards or the message to the controller, thus the number of transmission is $N$.
+As to the process of dissemination, in an extreme situation where all the gateway and the backbone nodes broadcast, the number of transmission will be $h + m$, where $h$ is the number of cluster heads, $m$ is number of debatable nodes, $d$ is the average number of demanding clusters for each debatable node.
 
@@
 \begin{center}
-\begin{table*}[ht]
-\caption{Singalling overhead.}\label{tab_overhead}
+\begin{table*}[!htb]
+\caption{Singalling overhead}\label{tab_overhead}
 {\small
@@
  Scheme 				&Message Complexity 	&   Quantitative number of messages 		& Content of message (size of message) 									\\ \hline
- ROSS-DGA, ROSS-$\delta$-DGA 	&$\mathcal{O}(N^3)$ (worst case)		&   $h+2*m^2d$ (upper bound)  				&   \multirow{2}{*}{\parbox{6.4cm}{Phase I: notification from cluster head (1 byte), new individual connectivity degree (1 byte);  Phase II: update of debatable nodes' affiliation (1 byte), claiming cluster$i$' new membership ($|C(i)|$ bytes)}}								\\ \cline{1-3}
+ ROSS-DGA, ROSS-$\delta$-DGA 	&$\mathcal{O}(N^3)$ (worst case)		&   $h+2*m^2d$ (upper bound)  				&   \multirow{2}{*}{\parbox{6.4cm}{Phase I: notification from cluster head (1 byte), new individual connectivity degree (1 byte);  Phase II: update of debatable nodes' affiliation (1 byte), claiming cluster $i$' new membership ($|C(i)|$ bytes)}}								\\ \cline{1-3}
  ROSS-DFA, ROSS-$\delta$-DFA 	&$\mathcal{O}(N)$ (worst case)		&   $h + 2m$	 (upper bound) 					& 	      												\\ \hline
@@
 \subsection{Comparison between Distributed Schemes}
+\label{largeScaleCRN}
 In this section we investigate the performances of distributed clustering schemes in CRN with different network scales and densities.
 The transmission range of CR is $A/10$, PR's transmission range is $A/5$.
-The number of PU is 30.
+The initial number of PU is 30.
 %The number of CR is 100, 200 and 300, and the average number of neighbours of each CR is 9.5, 20, and 31.
-We list some parameters of the simulation in the Table~\ref{Simulation_para}.
+The desired sizes adopted are listed in the Table~\ref{Simulation_para}.
 
@@
   \centering
-  \includegraphics[width=1\linewidth]{ccc_large_scale_color.pdf}
+  \includegraphics[width=.8\linewidth]{ccc_large_scale_color.pdf}
   \caption{Number of common channels of non-singleton clusters.}
@@
 Figure~\ref{ccc_large_scale} illustrates the average number of CCCs of the non-singleton clusters.
-It shows when $N=100$, variants of ROSS have 30\% less CCCs than SOC, but this gap is decreased significantly when $N$ is 200 and 300, \ie when $N=300$, number of CCCs achieved by ROSS variants (except for ROSS-$\delta$-DFA) is almost the same with that resulted from SOC.
-
-This means SOC performs better in terms of the average number of CCCs per non-singleton clusters when network is sparse.
+When $N=100$, variants of ROSS have 30\% less CCCs than SOC, but this gap is decreased significantly when $N$ is 200 and 300, \ie when $N=300$, the number of CCCs achieved by ROSS variants (except for ROSS-$\delta$-DFA) is almost the same as that resulted from SOC.
+This means SOC out performs in terms of the average number of CCCs per non-singleton cluster when network is sparse.
+
 this is also observed in the evaluation in Section \ref{ccc_20} where $N=20$.
@@
 
-\subsubsection{Survival Rate of Clusters with Increasing Primary Users}
-
-In this part of simulation, we investigate the robustness of clusters by increasing the PUs working on certain channels.
-
-Figure~\ref{singleton_clusters_100} illustrates the increasing trend of singleton clusters with the increase of PUs.
+\subsubsection{Number of Singleton Clusters}
+
+%In this part of simulation, we investigate the robustness of clusters by increasing the PUs working on certain channels.
+
+Figure~\ref{singleton_clusters_100} illustrates the increasing trend of singleton clusters with the increase of PUs, when $N=100$.
 SOC generates around 10 more singleton clusters than the variants of ROSS, which accounts for 10\% of the total CR nodes.
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{survival_rate_100.pdf}
+  \includegraphics[width=0.7\linewidth]{survival_rate_100.pdf}
   \caption{Percentage of CRs which are not included in any clusters with the increasing number of primary users, $N=100$}
@@
     \centering
-   \includegraphics[width=0.8\linewidth]{survival_rate_300.pdf}
+   \includegraphics[width=0.7\linewidth]{survival_rate_300.pdf}
   \caption{Percentage of CRs which are not included in any clusters with the increasing number of primary users, $N=300$}
@@
 
-From the Figure~\ref{singleton_clusters_100} and \ref{singleton_clusters_300}, we can conclude that the greedy versions of ROSS are slightly more robust than their counterpart variants of ROSS, and the clusters obtained from variants of ROSS are clearly more robust than SOC.
+From the Figure~\ref{singleton_clusters_100} and \ref{singleton_clusters_300}, we can conclude that the clusters obtained from the variants of ROSS are more robust than SOC.
+Besides, the greedy mechanism moderately strengthens the robustness of the clusters.
 %When the network is denser, the improvement on cluster sizes and robustness by the greedy search in the membership clarification phase is more obvious.
@@
 \subsubsection{Cluster Size Control}
-
-The number of formed clusters is shown in Fig.~\ref{nClusters_largeNetwork}.
-When the network scales up, the number of formed clusters by ROSS increases by smaller margin.
-This result coincides with the analysis in Section~\ref{cluster_pruning}, that with ROSS, the number of formed clusters saturates when the network scales.
+As Fig.~\ref{nClusters_largeNetwork} shows, when the network scales up, the number of formed clusters by ROSS increases by smaller margin.
+This result coincides with the analysis in Section~\ref{cluster_pruning}, that the number of formed clusters saturates when the network scales.
 When the network becomes denser, more clusters are generated by SOC compared with ROSS variants.
 To better understand the distribution of the sizes of formed clusters, we depict the cluster sizes with cumulative distribution.
-In this group of evaluation, the number of PRs is 30.
+%In this group of evaluation, the number of PRs is 30.
 
@@
   \centering
-   \includegraphics[width=1\linewidth]{nClusters_largeNetwork.pdf}
+   \includegraphics[width=0.85\linewidth]{nClusters_largeNetwork.pdf}
   \caption{The number of formed clusters.}
@@
 Overviewing the three Figures, we can see ROSS-DGA and ROSS-DFA show similar behaviour on cluster sizes.
-The clusters generated from SOC demonstrate strong divergence on cluster sizes.
+In contrary, the clusters generated from SOC demonstrate strong divergence on cluster sizes.
 
@@
 This problem is attributed to fact that ROSS forms clusters on the basis of cluster head's neighbourhood, and doesn't involve interaction with the nodes outside its neighbourhood.
-In the other way around, forming big cluster which extends out side of cluster head's neighbourhood has very limited applications, because multiple hop communication and coordination are required mange this kind of big clusters.
+In the other way around, forming big cluster which extends a cluster head's neighbourhood has limited applications, as multiple hop communication and coordination are required within such clusters.
 
@@
 \begin{algorithm}               % enter the algorithm environment
-\caption{ROSS phase I: cluster head guarantees the availability of CCC (use line 1) / cluster size control (use line 2)}          % give the algorithm a caption
+\caption{ROSS phase I: cluster head guarantees the availability of CCC (start from line 1) / cluster size control (start from line 2)}          % give the algorithm a caption
 \label{alg_size_control_available_CCC}
@@
 }
-\While{$i$ has not chosen the cluster, or $i$ has joined cluster $\tilde{C}$, but $\exists C'\in S_i, C'\neq \tilde{C}$, which has $|K_{C'\setminus i}|-|K_{C'}|<|K_{C\setminus i}|-|K_{C}|$}{
-	\eIf{$\exists$ only one $C\in S_i$, $C = \argmin(|K_{C\setminus i}| - |K_C|)$}{
+\While{$i$ has not chosen the cluster, or $i$ has joined cluster $\tilde{C}$, but $\exists C'\in S_i, C'\neq \tilde{C}$, which has $|K(C'\setminus i)|-|K(C')|<|K(C\setminus i)|-|K(C)|$}{
+	\eIf{$\exists$ only one $C\in S_i$, $C = \argmin(|K(C\setminus i)| - |K(C)|)$}{
 			return $C$;
 		}{
-				$\exists$ multiple $C\in S_i$ which satisfies $C = \argmin(|K_{C\setminus i}| - |K_C|)$;\\ 
+				$\exists$ multiple $C\in S_i$ which satisfies $C = \argmin(|K(C\setminus i)| - |K(C)|)$;\\ 
 				$\tau_1\leftarrow C$;		
 		}
-	\eIf{$\exists$ only one $C\in \tau_1$, $C = \argmax(K_{H_C}\cap K_i)$}{
+	\eIf{$\exists$ only one $C\in \tau_1$, $C = \argmax(K_{h_C}\cap K_i)$}{
 			return $C$;
 		}{
-				$\exists$ multiple $C\in S_i$ which satisfies $C = \argmax(K_{H_C}\cap K_i)$;\\ 
+				$\exists$ multiple $C\in S_i$ which satisfies $C = \argmax(K_{h_C}\cap K_i)$;\\ 
 				$\tau_2\leftarrow C$;		
@@
 		}{
-				return $\argmin_{C\in \tau_2}\texttt{ID}_{H_C}$;\\
+				return $\argmin_{C\in \tau_2}h_C$;\\
 		}
@@
 To simplify the discussion, we assume the secondary users have unique individual connectivity degrees, and they have identical ID and social connectivity degrees.
-This assumption is fair as the social connectivity degrees and node ID are used to break ties as shown in Algorithm~\ref{alg0}, when the individual connectivity degrees are unique, it is not necessary to use the former two metrics to break ties.
+This assumption is fair as the social connectivity degrees and node ID are used to break ties in Algorithm~\ref{alg0}, when the individual connectivity degrees are unique, it is not necessary to use the former two metrics.
 
@@
 If node node $\beta$ is not cluster head, i.e., $\beta$ is not in any cluster, we can repeat the previous analysis made on node $\alpha$, and deduce that node $\beta$ has at least one neighbouring node $\gamma$ with $d_{\gamma} < d_{\beta}$.
-When no cluster head appears, this series of nodes with monotonically decreasing $d_i$ might continue to grow, and finally ceases when the individual connectivity degree is zero, or all secondary nodes are already in the series of nodes.
+When no cluster head appears, this series of nodes with monotonically decreasing $d_i$ might continue to grow, but finally ceases when either the individual connectivity degree is zero, or every secondary node has already been in the series of nodes.
 An example of the formed node series is shown as Figure~\ref{lemma1}.
@@
 % \includegraphics{figure1.pdf}
-	\caption{The node series discussed in the proof for Theorem~\ref{clustering:theorem}, the deduction begins from node $\alpha$}
+	\caption{The node series discussed in the proof of Theorem~\ref{clustering:theorem}, the deduction begins from node $\alpha$}
 	\label{lemma1}
@@
 Now we find the node $\omega$ is in the end of this series.
-As $\omega$ is the end node and does not have neighbouring nodes with bigger individual connectivity degree $D$, $\omega$ becomes cluster head and incorporate all its one-hop neighbours, including the node before it in the node series (here we assume that every new formed cluster has common channels).
-After that, the node recruited into cluster will set its connection degree $D$ to zero, which enables the node further down in the list to become a cluster head.
-In this way, all the nodes in the series are included in at least one cluster in an inverse sequence.
+As $\omega$ is the end node and does not have neighbouring nodes with lower individual connectivity degree $D$, $\omega$ becomes cluster head and incorporate all its one-hop neighbours, including the node before it in the series (here we assume that every new formed cluster has common channels).
+After that, the node recruited into cluster will set its connection degree $D$ to $M$, which enables the node further down in the list to become a cluster head.
+In this way, all the nodes in the series are in at least one cluster in the inverse sequence.
 This result contradicts the initial assumption and proves the claim stated above.
-Meanwhile, through this proof, we know that within at most $N$ steps, all nodes will become a part of certain clusters.
+Meanwhile, through this proof, we know that within at most $N$ steps, all the nodes belong to certain clusters.
 \end{proof}
@@
 \begin{proof}
-We put the definition of weighted k-set packing problem here as it will be used in the analysis on the complexity of our problem.
+We put the definition of weighted k-set packing problem here as it to be used in the analysis on the complexity of the centralised clustering problem.
 
@@
 \item Given a collection $\mathcal{Q}$, on basis of which we construct a CRN.
-We prepare $N$ CR nodes who are labelled from 1 to $N$.
-We put the CR users on a 2 dimension space, and deem a pair of them can communicate if they appear in the same set in $\mathcal{Q}$.
+We prepare $N$ CR nodes who are labelled from 1 to $N$, put them on a 2 dimension space, and deem a pair of them can communicate if they appear in one same set in $\mathcal{Q}$.
 We regard each set in $\mathcal{Q}$ is a cluster, whose number of CCCs equals to the weight of that set.
@@
 %As $s'$ is dummy set which has duplicated elements, we also deploy the the same CR node twice.
-
+%
 An example is shown in Table~\ref{no_hard_proof_instance}.
@@
 
-We have crossed the hurdle of finding one polynomial algorithm $\sigma$ to transform instance of weighted k-set packing to an instance for clustering in CRN.
-Now we look into the step 2 in reduction.
-
+We have crossed the hurdle of finding one polynomial algorithm $\sigma$ which transforms an instance of weighted k-set packing to an instance of the clustering problem in CRN.
+Now we look into the step 2 in the reduction.
 As to an instance $\mathcal{S}$ for weighted k-set packing, the sum weights is identical to the sum of CCCs in the CRN mapped from $\mathcal{S'}$, even $\mathcal{S}$ contains set which only has one element.
@@
 
-Thus, weighted k-set packing can be reduced to centralized clustering problem in CRN, and we can say the latter problem is of NP-hard.
+Thus, weighted k-set packing can be reduced to clustering problem in CRN, then the latter problem is of NP-hard.
 \end{proof}
@@
 
+% You can push biographies down or up by placing
+% a \vfill before or after them. The appropriate
+% use of \vfill depends on what kind of text is
+% on the last page and whether or not the columns
+% are being equalized.
+
+%\vfill
+
+% Can be used to pull up biographies so that the bottom of the last one
+% is flush with the other column.
+%\enlargethispage{-5in}
+\bibliographystyle{IEEEtran}
+\bibliography{../backmatter/myrefs}
+
 % biography section
@@
 % or if you just want to reserve a space for a photo:
-
-\begin{IEEEbiographynophoto}{Di Li}
+%IEEEbiographynophoto
+\begin{IEEEbiography}{Di Li}
 received BE and MS degrees in control engineering from Zhejiang University and Shaanxi University of Science and Technology respectively in China.
 He worked with James Gross for his PhD in RWTH Aachen University since 2010.
-\end{IEEEbiographynophoto}
+\end{IEEEbiography}
 
@@
 Biography text here.
-Biography text here.
-Biography text here.
-Biography text here.
-Biography text here.
+
 \end{IEEEbiography}
-
+%\vspace{-50 mm}
 % insert where needed to balance the two columns on the last page with
@@
 Biography text here.
-Biography text here.
-Biography text here.
+
 \end{IEEEbiography}
 
-% You can push biographies down or up by placing
-% a \vfill before or after them. The appropriate
-% use of \vfill depends on what kind of text is
-% on the last page and whether or not the columns
-% are being equalized.
-
-%\vfill
-
-% Can be used to pull up biographies so that the bottom of the last one
-% is flush with the other column.
-%\enlargethispage{-5in}
-
-\bibliographystyle{IEEEtran}
-\bibliography{../backmatter/myrefs}
-
 \end{document}

### 2016-04-06 journal-draft/bare_jrnl_comsoc.tex
Erwin looked briefly into the first proof and started to correct the second proof.

@@
 \label{clustering:theorem}
-Given a CRN, every secondary user is included into at least one cluster within $N$ steps.
+Given a CRN, every secondary user is included into at least one cluster within $N$ steps. (COMMENT: $N$ has to be defined within the theorem!!)
 \end{theorem}
-Here, \textit{Step} means one secondary user conducts Algorithm~\ref{clustering:theorem} once.
+Here, by \textit{step} we mean one application of Algorithm~\ref{clustering:theorem} by a secondary user.
 The Proof is in Appendix~\ref{proof_clustering:theorem}.
-According to Theorem~\ref{clustering:theorem}, we can assign reasonable amount of time for phase I to complete.
+According to Theorem~\ref{clustering:theorem}, Phase I completes within a reasonable amount of time.
 
@@
 Let us apply Algorithm~\ref{alg0} to the example shown in Figure~\ref{fig1}.
-Node $B$ and $H$ have the same individual connectivity degree, $d_B=d_H$, but as $g_H=2>g_B=1$, node $H$ becomes the cluster head and cluster $C_H$ is $\{H, B, A, G\}$.
+Node $B$ and $H$ have the same individual connectivity degree, i.e., $d_B=d_H$. As $g_H=2>g_B=1$, node $H$ becomes the cluster head and cluster $C_H$ is $\{H, B, A, G\}$.
 
@@
 %Note that the formed cluster can be a singleton cluster, \ie cluster size is 1.
-We consider a CRN which can be represented as a connected graph.
-To simplify the discussion, we assume the secondary users have unique individual connectivity degrees, and they have identical ID and social connectivity degrees.
+We consider a CRN which can be represented as a connected graph. (COMMENT: Why is it necessarily connected? No special case where the graph has two components?)
+To simplify the discussion, we assume the secondary users have unique individual connectivity degrees. Each user has an identical ID and a social connectivity degree.
 This assumption is fair as the social connectivity degrees and node ID are used to break ties in Algorithm~\ref{alg0}, when the individual connectivity degrees are unique, it is not necessary to use the former two metrics.
+(COMMENT: What do you mean by breaking ties??
+I don't see why your argument holds.)
 
 %we assume every node has at least one neighbour.
-Assuming there exist some secondary users which are not included into any cluster, and node $\alpha$ is of this kind.
-As node $\alpha$ is not contained in any cluster, there must be at least one node $\beta\in \text{Nb}_\alpha$, with $d_{\alpha} > d_{\beta}$.
-Otherwise, node $\alpha$ is eligible to form a cluster.
-If node $\beta$ becomes cluster head, node $\alpha$ is included.
-If node node $\beta$ is not cluster head, i.e., $\beta$ is not in any cluster, we can repeat the previous analysis made on node $\alpha$, and deduce that node $\beta$ has at least one neighbouring node $\gamma$ with $d_{\gamma} < d_{\beta}$.
-When no cluster head appears, this series of nodes with monotonically decreasing $d_i$ might continue to grow, but finally ceases when either the individual connectivity degree is zero, or every secondary node has already been in the series of nodes.
+For the sake of contradiction, let us assume there exist some secondary user $\alpha$ which is not included into any cluster.
+Then there is at least one node $\beta\in \text{Nb}_\alpha$ such that $d_{\alpha} > d_{\beta}$. Now, we distinguish between two cases: 
+%Otherwise, node $\alpha$ is eligible to form a cluster. COMMENT: unnecessary sentence!
+If $\beta$ becomes cluster head, node $\alpha$ is included.
+If $\beta$ is not a cluster head, i.e., $\beta$ is not in any cluster (COMMENT: $\beta$ not being a cluster head and $\beta$ not belonging to any cluster is not the same statement!!!), we can repeat the previous analysis made on node $\alpha$, and deduce that node $\beta$ has at least one neighbouring node $\gamma$ with $d_{\gamma} < d_{\beta}$.
+When no cluster head appears, this series (COMMENT: what is that?
+sequence?) of nodes with monotonically decreasing connectivity degrees might continue to grow.
+Finally, it ceases (COMMENT: not a good/suitable word!!) when either the individual connectivity degree is zero, or every secondary node has already been in the series (COMMENT: sequence?) of nodes.
 An example of the formed node series is shown as Figure~\ref{lemma1}.
@@
 
-Now we find the node $\omega$ is in the end of this series.
-As $\omega$ is the end node and does not have neighbouring nodes with lower individual connectivity degree $D$, $\omega$ becomes cluster head and incorporate all its one-hop neighbours, including the node before it in the series (here we assume that every new formed cluster has common channels).
-After that, the node recruited into cluster will set its connection degree $D$ to $M$, which enables the node further down in the list to become a cluster head.
-In this way, all the nodes in the series are in at least one cluster in the inverse sequence.
-This result contradicts the initial assumption and proves the claim stated above.
-Meanwhile, through this proof, we know that within at most $N$ steps, all the nodes belong to certain clusters.
+Now, we can see that the node $\omega$ is the last element of this sequence.
+As $\omega$ does not have neighboring nodes with lower individual connectivity degree $D$, $\omega$ becomes the cluster head and incorporate all its one-hop neighbours, including the node before (COMMENT: you mean $\alpha$?) it in the series (here we assume that every newly formed cluster has common channels).
+After that, the node that joined a cluster will set its connection degree $D$ to $M$, which enables the node further down in the list (WHAT ???
+What is further down and which list???
+I cannot follow.) to become a cluster head.
+In this way, all the nodes in the series are in at least one cluster in the inverse sequence (? inverse of?), which contradicts the assumption.
+Meanwhile, through this proof, we know that within at most $N$ steps, all the nodes belong to certain clusters. (COMMENT: No, we don't! Where was that shown?)
 \end{proof}
@@
 
-Given a set $\mathcal{G}$ which contains finite number of positive integers, and a collection of set $\mathcal{Q}=\{s_1,s_2,\cdots,s_m\}$, where for each element $s_r, 1\leq r \leq m$, there is $s_r\subseteq \mathcal{G}$, $ 1\leq|s_r| \leq k$, and $s_r$ has an associated weight which is positive real number.
-The question is whether exists a collection $\mathcal{S}\subseteq \mathcal{Q}$, where $\mathcal{S}$ contains only disjoint sets and the total weight of sets in $\mathcal{S}$ is greater than $\lambda$.
+Given a finite set $\mathcal{G} = \{ g_1, \ldots , g_N \} \subsetneq \mathbb{N}$ of non-negative integers and a collection of sets $\mathcal{Q}=\{S_1,S_2,\cdots,S_m\}$ such that $S_i \subseteq \mathcal{G}$ for every $1 \leq i \leq N$.
+Each set $S \in \mathcal{Q}$ is associated with a weight $w(S) \in \mathbb{R}$.
+Further, we are given a threshold value $\lambda \in \mathbb{N}$.\\
+The question is whether there exists a collection $\mathcal{S} \subseteq \mathcal{Q}$ such that $\mathcal{S}$ contains only pairwise disjoint sets, i.e., for all $S, S' \in \mathcal{S}$ with $S \neq S'$ it holds that $S \cap S' = \emptyset$, and the total weight of the sets in $\mathcal{S}$ is greater than $\lambda$, i.e., $\sum_{S \in \mathcal{S}} w(S) > \lambda$.
+\end{mydef}
+
 Weighted k-set packing is NP-hard when $k\geqslant 3$.~\cite{Computers_a_Intractability}
-\end{mydef}
-
-To prove the centralized clustering problem is of NP-hard, we reduce the NP-hard problem \textit{weighted k-set packing} to it to prove the former is as hard as the later.
+
+To prove that the centralized clustering problem is NP-hard, we reduce the NP-hard problem \textit{weighted k-set packing} to it to prove the former is at least as hard as the latter.
 %, which means centralized clustering in CRN problem is as hard as weighted k-set packing to be solved.
-To complete the reduction, we need to conduct following two steps:
-\begin{itemize}
-\item step 1: Show there exists a polynomial algorithm $\sigma$, by which any instance $\mathcal{S}$ of a weighted k-set packing can be transformed to a clustering solution $\sigma(\mathcal{S})$ which complies with Definition~\ref{def_centralized_clustering}.
-\item step 2: Show that $\mathcal{S}$ is a \textit{yes} instance of weighted k-set packing if and only if $\sigma(\mathcal{S})$ is a \textit{yes} instance for CRN clustering problem.
-\end{itemize}
-
-We continue to use the notation adopted in the problem definition in Section~\ref{centralized_opt}.
-Let set $\mathcal{G}$ contain $N$ natural numbers which are from 1 to $N$.
-$\mathcal{Q}$ is a collection of sets $\{s_1, s_2,\cdots s_m\}$, each set is composed with certain elements in $\mathcal{G}$.
-Assume $\mathcal{S}\subseteq \mathcal{Q}$ is one instance of weighted k-set packing, and the sets in $\mathcal{S}$ are disjoint.
-$\omega$ indicates the weight for each set $s$, $\omega:\mathcal{S}\rightarrow \mathbb{Z}^{+}$.
+%To complete the reduction, we need to conduct following two steps:
+%\begin{itemize}
+%\item Step 1: We show the existence a polynomial algorithm $\sigma$, by which any instance $\mathcal{S}$ of a weighted k-set packing can be transformed to a clustering solution $\sigma(\mathcal{S})$ which complies with Definition~\ref{def_centralized_clustering}.
+%\item Step 2: Show that $\mathcal{S}$ is a \textit{yes} instance of weighted k-set packing if and only if $\sigma(\mathcal{S})$ is a \textit{yes} instance for CRN clustering problem.
+%\end{itemize}
+We show the existence of a polynomial-time algorithm $\sigma$ that transforms any instance $\mathcal{S}$ (COMMENT: be careful - there is an overloading of $\mathcal{S}$ of a weighted $k$-set packing into an instance $\sigma(\mathcal{S})$) of centralized clustering such that ...
+(to be completed - Erwin can do that)
+
+%We continue to use the notation adopted in the problem definition in Section~\ref{centralized_opt}.
+W.l.o.g. let set $\mathcal{G} = \{ 1, \ldots , N \}$.
+%$\mathcal{Q}$ is a collection of sets $\{s_1, s_2,\cdots s_m\}$, each set is composed with certain elements in $\mathcal{G}$. REPEATING THE DEF??
+%Assume $\mathcal{S}\subseteq \mathcal{Q}$ is one instance of weighted k-set packing, and the sets in $\mathcal{S}$ are disjoint.
+%$\omega$ indicates the weight for each set $s$, $\omega:\mathcal{S}\rightarrow \mathbb{Z}^{+}$. COMMENT: again unnecessary. Already contained in the definition!
 %As the number of common channel of clusters is always integer
 %give new weight to them in following way
+
+ERWIN FINISHED HERE FOR THE MOMENT ---
 

### 2016-04-07 journal-draft/bare_jrnl_comsoc.tex
corrections in the appendix

@@
 \begin{itemize}
-\item Given a collection $\mathcal{Q}$, on basis of which we construct a CRN.
-We prepare $N$ CR nodes who are labelled from 1 to $N$, put them on a 2 dimension space, and deem a pair of them can communicate if they appear in one same set in $\mathcal{Q}$.
-We regard each set in $\mathcal{Q}$ is a cluster, whose number of CCCs equals to the weight of that set.
+\item Given a collection $\mathcal{Q}$, on basis of which we construct a CRN. (I DON'T UNDERSTAND THAT. What do you mean?)
+%We prepare $N$ CR nodes who are labelled from 1 to $N$, put them on a 2 dimension space, and deem a pair of them can communicate if they appear in one same set in $\mathcal{Q}$.
+We define a set of CR nodes $\mathcal{N} = \{ 1, \ldots , N \}$
+We regard each set in $\mathcal{Q}$ as a cluster, whose number of CCCs is equal to the weight of that set.
 
 %There is one situation deserving extra explanation in the second transformation, we adopt one example to discuss it.
-Assuming two sets in $\mathcal{Q}$ are $s_1=\{1,2\}$ and $s_2=\{1,2,3\}$, then their weights are 3 and 5 respectively.
+Assuming two sets in $\mathcal{Q}$ are $s_1=\{1,2\}$ and $s_2=\{1,2,3\}$, then their weights are 3 and 5 respectively. (THAT'S TOO HAND-WAVY.)
 %Their dummy sets are $s_1'=\{1,1,2,2\}$ and $s_2'=\{1,1,2,2,3,3,4,4\}$ and their new weights are 3 and 5 as before.
-We find it is impossible to map the sets into clusters in the same time, because the number of CCCs of the cluster which bases on $s_1$ should be no less than the cluster which bases on $s_2$, as the latter has one extra node compared with the former cluster.
+We find it is impossible to map the sets into clusters in the same time (SORRY, which sets??
+The sets you mentioned before are already clusters, isn't it?), because the number of CCCs of the cluster which bases on $s_1$ should be no less than the cluster which bases on $s_2$, as the latter has one extra node compared with the former cluster.
 %When $s_1'$ and $s_2'$ are mapped to CRN respectively, there is contradiction between them, because the number of common channels of CR node group $\{1,1,2,2\}$ is smaller than that of $\{1,1,2,2,3,3,4,4\}$.
 But as to any instance of the solution to the weighted k-set packing problem, this contradiction doesn't happen because the instance $\mathcal{S}$ contains only disjoint sets, thus at most only one set of $s_1$ and $s_2$ appears in $\mathcal{S}$.%, then we can safely delete the connections based on the deleted set from the CRN, and the contradiction is eliminated.
+(THIS PARAGRAPH IS TOO DIFFICULT FOR ME TO UNDERSTAND.)
 
 \item In the second step, we transform the instance $\mathcal{S}$ to $\mathcal{S'}$ by adding dummy elements into each set in $\mathcal{S}$.
-For each set $s_i\in \mathcal{S}$, the elements in $s_i$ are duplicated, for instance, given $s_i=\{1, 4, 6\}$, the dummy set $s_i'$ is $\{1,1,4,4,6,6\}$.
+Formally, for each set $s_i\in \mathcal{S}$, we create $s_i' = s_i \times \{ 1,2\}$. %for instance, given $s_i=\{1, 4, 6\}$, the dummy set $s_i'$ is $\{1,1',4,4',6,6' \}$.
 %By doing this, we obtain the dummy sets and constitute the dummy instance $\mathcal{S}'$ based on $\mathcal{S}$.
 The purpose of this transformation is to eliminate the set in $\mathcal{S}$, which has single element.
-The weight of set is unchanged after this transformation, \ie $\omega(s_i)=\omega(s_i')$.
+The weight of these sets remain unchanged, \ie $\omega(s_i)=\omega(s_i')$.
 %After this transmission, there is no set with only one element.
-This transformation requires $\sum_{s_i \in \mathcal{S}} |s_i|$ steps.
+%This transformation requires $\sum_{s_i \in \mathcal{S}} |s_i|$ steps.
 
 \item In this step, we transform the instance $\mathcal{S'}$ to a clustering solution for CRN.
-We prepare a second pool of CR nodes which are identical with the CR nodes prepared in step 1, i.e., identical IDs and channel availabilities on them, we call these CR nodes as dummy nodes.
-We locate these CR nodes besides the CR nodes with the sane IDs in the CRN built in step 1, and there is connection between the CR node and its dummy node (the one CR node and its dummy node can be seen as two transceivers at one node).
+We prepare a second pool of CR nodes which are identical with the CR nodes prepared in step 1, i.e., identical IDs and channel availabilities on them, we call these CR nodes dummy nodes.
+We locate these CR nodes besides the CR nodes with the same IDs (THAT DOESN'T MAKE SENSE.
+THEN THE ID IS NOT UNIQUE ANYMORE.) in the CRN built in step 1, and there is connection between the CR node and its dummy node (the one CR node and its dummy node can be seen as two transceivers at one node).
+(YOU DON'T NEED TO GIVE PRACTICAL MOTIVATION IN A HARDNESS-PROOF.)
 Because of the dummy nodes, the clustering solution which corresponds to $\mathcal{S'}$ doesn't have singleton cluster.
@@
     \cmidrule(r){1-1}\cmidrule(lr){2-2}     
-      $\mathcal{Q}$  & $\{(1),(1, 5),(1,2,4),(2,3), (4)\}$\\ 
+      $\mathcal{Q}$  & $\{ \{1\}, \{1, 5\}, \{1,2,4\}, \{2,3\}, \{4\} \}$\\ 
     \cmidrule(r){1-1}\cmidrule(lr){2-2}     
-      Instance for Weighted k-set packing  & $\{(1),(2,3), (4)\}$\\ 
+      Instance for Weighted k-set packing  & $\{ \{1\}, \{2,3\}, \{4\} \}$\\ 
     \cmidrule(r){1-1}\cmidrule(lr){2-2}
@@
       & 
-		$\{(1,1),(2,2,3,3), (4,4)\}$
+		$\{ \, \{(1,1),(1,2)\},\{(2,1),(2,2),$ \\ &$(3,1),(3,2) \}, \{ (4,1), (4,2) \} \, \}$
       \\    \cmidrule(r){1-1}\cmidrule(lr){2-2}

### 2016-04-08 journal-draft/bare_jrnl_comsoc.tex
modified proof of theorem 1, and answered Erwin's questions in the tex file

@@
 %Note that the formed cluster can be a singleton cluster, \ie cluster size is 1.
-We consider a CRN which can be represented as a connected graph. (COMMENT: Why is it necessarily connected? No special case where the graph has two components?)
-To simplify the discussion, we assume the secondary users have unique individual connectivity degrees. Each user has an identical ID and a social connectivity degree.
+We consider a CRN which can be represented as a connected graph.
+% (COMMENT: Why is it necessarily connected?
+No special case where the graph has two components?
+ANSWER(Di): It is possible for the graph to have two components.
+My point it, when theorem works in one component, it works in the complete graph.)
+To simplify the discussion, we assume the secondary users have unique individual connectivity degrees. 
+Each user has an identical ID and a social connectivity degree.
 This assumption is fair as the social connectivity degrees and node ID are used to break ties in Algorithm~\ref{alg0}, when the individual connectivity degrees are unique, it is not necessary to use the former two metrics.
-(COMMENT: What do you mean by breaking ties??
-I don't see why your argument holds.)
+%(COMMENT: What do you mean by breaking ties??
+I don't see why your argument holds.
+ANSWER(DI): according to Algorithm 1, to decide whether node $i$ is a cluster head, the comparision on $i$'s certain degrees with its neighbors needs to be made.
+It is possible that $i$ has the same degree with some neighbors, then we need ID to decide whether $i$ is cluster head.)
 
@@
 For the sake of contradiction, let us assume there exist some secondary user $\alpha$ which is not included into any cluster.
-Then there is at least one node $\beta\in \text{Nb}_\alpha$ such that $d_{\alpha} > d_{\beta}$. Now, we distinguish between two cases: 
+Then there is at least one node $\beta\in \text{Nb}_\alpha$ such that $d_{\alpha} > d_{\beta}$. 
+According to Algorithm~\ref{alg0}, $\delta$ is not included in any clusters, because otherwise $d_{\beta} = M$, a large positive integer.
+Now, we distinguish between two cases: 
 %Otherwise, node $\alpha$ is eligible to form a cluster. COMMENT: unnecessary sentence!
-If $\beta$ becomes cluster head, node $\alpha$ is included.
-If $\beta$ is not a cluster head, i.e., $\beta$ is not in any cluster (COMMENT: $\beta$ not being a cluster head and $\beta$ not belonging to any cluster is not the same statement!!!), we can repeat the previous analysis made on node $\alpha$, and deduce that node $\beta$ has at least one neighbouring node $\gamma$ with $d_{\gamma} < d_{\beta}$.
-When no cluster head appears, this series (COMMENT: what is that?
-sequence?) of nodes with monotonically decreasing connectivity degrees might continue to grow.
-Finally, it ceases (COMMENT: not a good/suitable word!!) when either the individual connectivity degree is zero, or every secondary node has already been in the series (COMMENT: sequence?) of nodes.
+If $\beta$ becomes cluster head, node $\alpha$ is included, the assumption is not true.
+If $\beta$ is not a cluster head, then $\beta$ is not in any cluster, we can repeat the previous analysis made on node $\alpha$, and deduce that node $\beta$ has at least one neighbouring node $\gamma$ with $d_{\gamma} < d_{\beta}$.
+% (COMMENT: $\beta$ not being a cluster head and $\beta$ not belonging to any cluster is not the same statement!!! ANSWER(Di): I add some more words)
+Till now, when there is no cluster head identified, the unclustered nodes, \ie $\alpha$, $\bata$ form a linked list, where their connectivity degrees monotonically decrease.
+But this list will not continue to grow, because the minimum individual connectivity degree is zero, and the length of this list is upper bounded by the total number of nodes in the CRN.
 An example of the formed node series is shown as Figure~\ref{lemma1}.
@@
 
-Now, we can see that the node $\omega$ is the last element of this sequence.
-As $\omega$ does not have neighboring nodes with lower individual connectivity degree $D$, $\omega$ becomes the cluster head and incorporate all its one-hop neighbours, including the node before (COMMENT: you mean $\alpha$?) it in the series (here we assume that every newly formed cluster has common channels).
-After that, the node that joined a cluster will set its connection degree $D$ to $M$, which enables the node further down in the list (WHAT ???
-What is further down and which list???
-I cannot follow.) to become a cluster head.
-In this way, all the nodes in the series are in at least one cluster in the inverse sequence (? inverse of?), which contradicts the assumption.
-Meanwhile, through this proof, we know that within at most $N$ steps, all the nodes belong to certain clusters. (COMMENT: No, we don't! Where was that shown?)
+In this example, node $\omega$ is at the tail of the list.
+As $\omega$ does not have neighboring nodes with lower individual connectivity degree, $\omega$ becomes a cluster head.
+Then $\omega$ incorporates all its one-hop neighbours (here we assume that every newly formed cluster has common channels), including the nodes which precede $\omega$ in the list.
+The nodes which join a cluster set their individual connection degrees to $M$, which enables the node immediately precede in the listto become a cluster head.
+In this way, cluster heads are generated from the tail of list to the head of the list, and all the nodes in the list are in at least one cluster, which contradicts the assumption that $\alpha$ is not included in any cluster.
+
+(This paragraph should be moved out of the proof.)
+The procedure of this proof also illustrates the time needed to complete phase I. 
+Consider an extreme scenario, where all the secondary nodes sequentially execute Algorithm~\ref{alg0}, and constitute one list as that in the above example.
+If we see a secondary user \textit{becoming a cluster head}, or \textit{becoming a cluster member} as one step, then there are $N$ steps for this scenario to complete phase I.
+If one step can be finished within certain time, we can give the maximum time needed to conduct the phase I of ROSS.
+In other scenarios, as Algorithm~\ref{alg0} can be executed concurrently by secondary users which locate in different places, the needed time can be considerably reduced.
+%we know that within at most $N$ steps, all the nodes belong to certain clusters. (COMMENT: No, we don't! Where was that shown?)
 \end{proof}

### 2016-04-08 journal-draft/bare_jrnl_comsoc.tex
minor changes

@@
 % (COMMENT: $\beta$ not being a cluster head and $\beta$ not belonging to any cluster is not the same statement!!! ANSWER(Di): I add some more words)
-Till now, when there is no cluster head identified, the unclustered nodes, \ie $\alpha$, $\bata$ form a linked list, where their connectivity degrees monotonically decrease.
+Till now, when there is no cluster head identified, the unclustered nodes, \ie $\alpha$, $\beta$ form a linked list, where their connectivity degrees monotonically decrease.
 But this list will not continue to grow, because the minimum individual connectivity degree is zero, and the length of this list is upper bounded by the total number of nodes in the CRN.

### 2016-04-09 journal-draft/bare_jrnl_comsoc.tex
modified proof for T5.1

@@
 Given a finite set $\mathcal{G} = \{ g_1, \ldots , g_N \} \subsetneq \mathbb{N}$ of non-negative integers and a collection of sets $\mathcal{Q}=\{S_1,S_2,\cdots,S_m\}$ such that $S_i \subseteq \mathcal{G}$ for every $1 \leq i \leq N$.
-Each set $S \in \mathcal{Q}$ is associated with a weight $w(S) \in \mathbb{R}$.
+Each set $S \in \mathcal{Q}$ is associated with a weight $\omega(S) \in \mathbb{R}$.
 Further, we are given a threshold value $\lambda \in \mathbb{N}$.\\
-The question is whether there exists a collection $\mathcal{S} \subseteq \mathcal{Q}$ such that $\mathcal{S}$ contains only pairwise disjoint sets, i.e., for all $S, S' \in \mathcal{S}$ with $S \neq S'$ it holds that $S \cap S' = \emptyset$, and the total weight of the sets in $\mathcal{S}$ is greater than $\lambda$, i.e., $\sum_{S \in \mathcal{S}} w(S) > \lambda$.
+The question is whether there exists a collection $\mathcal{S} \subseteq \mathcal{Q}$ such that $\mathcal{S}$ contains only pairwise disjoint sets, i.e., for all $S, S' \in \mathcal{S}$ with $S \neq S'$ it holds that $S \cap S' = \emptyset$, and the total weight of the sets in $\mathcal{S}$ is greater than $\lambda$, i.e., $\sum_{S \in \mathcal{S}} \omega(S) > \lambda$.
 \end{mydef}
@@
 %\end{itemize}
-We show the existence of a polynomial-time algorithm $\sigma$ that transforms any instance $\mathcal{S}$ (COMMENT: be careful - there is an overloading of $\mathcal{S}$ of a weighted $k$-set packing into an instance $\sigma(\mathcal{S})$) of centralized clustering such that ...
-(to be completed - Erwin can do that)
+We show the existence of a polynomial-time algorithm $\sigma$ that transforms any instance $\mathcal{I}$ of a weighted $k$-set packing into an instance $\sigma(\mathcal{S})$) of centralized clustering problem.
 
@@
 %give new weight to them in following way
-
-ERWIN FINISHED HERE FOR THE MOMENT ---
-
-The polynomial algorithm $\sigma$ consists of three transformations.
+The polynomial algorithm $\sigma$ consists of three steps.
 
 \begin{itemize}
-\item Given a collection $\mathcal{Q}$, on basis of which we construct a CRN. (I DON'T UNDERSTAND THAT. What do you mean?)
-%We prepare $N$ CR nodes who are labelled from 1 to $N$, put them on a 2 dimension space, and deem a pair of them can communicate if they appear in one same set in $\mathcal{Q}$.
-We define a set of CR nodes $\mathcal{N} = \{ 1, \ldots , N \}$
-We regard each set in $\mathcal{Q}$ as a cluster, whose number of CCCs is equal to the weight of that set.
-
-%There is one situation deserving extra explanation in the second transformation, we adopt one example to discuss it.
-Assuming two sets in $\mathcal{Q}$ are $s_1=\{1,2\}$ and $s_2=\{1,2,3\}$, then their weights are 3 and 5 respectively. (THAT'S TOO HAND-WAVY.)
-%Their dummy sets are $s_1'=\{1,1,2,2\}$ and $s_2'=\{1,1,2,2,3,3,4,4\}$ and their new weights are 3 and 5 as before.
-We find it is impossible to map the sets into clusters in the same time (SORRY, which sets??
-The sets you mentioned before are already clusters, isn't it?), because the number of CCCs of the cluster which bases on $s_1$ should be no less than the cluster which bases on $s_2$, as the latter has one extra node compared with the former cluster.
-%When $s_1'$ and $s_2'$ are mapped to CRN respectively, there is contradiction between them, because the number of common channels of CR node group $\{1,1,2,2\}$ is smaller than that of $\{1,1,2,2,3,3,4,4\}$.
-But as to any instance of the solution to the weighted k-set packing problem, this contradiction doesn't happen because the instance $\mathcal{S}$ contains only disjoint sets, thus at most only one set of $s_1$ and $s_2$ appears in $\mathcal{S}$.%, then we can safely delete the connections based on the deleted set from the CRN, and the contradiction is eliminated.
-(THIS PARAGRAPH IS TOO DIFFICULT FOR ME TO UNDERSTAND.)
-
-\item In the second step, we transform the instance $\mathcal{S}$ to $\mathcal{S'}$ by adding dummy elements into each set in $\mathcal{S}$.
-Formally, for each set $s_i\in \mathcal{S}$, we create $s_i' = s_i \times \{ 1,2\}$. %for instance, given $s_i=\{1, 4, 6\}$, the dummy set $s_i'$ is $\{1,1',4,4',6,6' \}$.
+
+\item In the first step, we transform the instance $\mathcal{I}$ to $\mathcal{I'}$ by adding dummy elements into each set in $\mathcal{I}$.
+Formally, for each set $s_i\in \mathcal{I}$, we create $s_i' = s_i \times \{ 1,2\}$.
+Then we change the dummy elements by adding $N$ on them.
+ %for instance, given $s_i=\{1, 4, 6\}$, the dummy set $s_i'$ is $\{1,1',4,4',6,6' \}$.
 %By doing this, we obtain the dummy sets and constitute the dummy instance $\mathcal{S}'$ based on $\mathcal{S}$.
-The purpose of this transformation is to eliminate the set in $\mathcal{S}$, which has single element.
-The weight of these sets remain unchanged, \ie $\omega(s_i)=\omega(s_i')$.
+The purpose of this transformation is to eliminate the set in $\mathcal{I}$, which has single element.
+The weight of these sets remain unchanged, \ie $\omega(s_i') = \omega(s_i)$.
 %After this transmission, there is no set with only one element.
@@
 
-\item In this step, we transform the instance $\mathcal{S'}$ to a clustering solution for CRN.
-We prepare a second pool of CR nodes which are identical with the CR nodes prepared in step 1, i.e., identical IDs and channel availabilities on them, we call these CR nodes dummy nodes.
-We locate these CR nodes besides the CR nodes with the same IDs (THAT DOESN'T MAKE SENSE.
+\item Mapping the elements in $\mathcal{I'}$ to CR nodes, and mapping the sets in $\mathcal{I'}$ to clusters.
+There is a bijection between the union of sets in $\mathcal{I'}$ to the CRN which consists of the CR nodes, in particular, each element one-to-one corresponds to the CR node whose node ID equals to the element.
+%Given a collection $\mathcal{Q}$, on basis of which we construct a CRN. (I DON'T UNDERSTAND THAT. What do you mean?)
+%We prepare $N$ CR nodes who are labelled from 1 to $N$, put them on a 2 dimension space, and deem a pair of them can communicate if they appear in one same set in $\mathcal{Q}$.
+%We define a set of CR nodes $\mathcal{N} = \{ 1, \ldots , N \}$
+We further regulate that, each set in $\mathcal{I}$ as a corresponding cluster, \ie there is a bijection between a set in $\mathcal{I}$ and a set of node IDs in a cluster, besides, the number of CCCs is equal to the weight of the corresponding set.
+
+%%There is one situation deserving extra explanation in the second transformation, we adopt one example to discuss it.
+%Assuming two sets in $\mathcal{Q}$ are $s_1=\{1,2\}$ and $s_2=\{1,2,3\}$, then their weights are 3 and 5 respectively. (THAT'S TOO HAND-WAVY.)
+%%Their dummy sets are $s_1'=\{1,1,2,2\}$ and $s_2'=\{1,1,2,2,3,3,4,4\}$ and their new weights are 3 and 5 as before.
+%We find it is impossible to map the sets into clusters in the same time (SORRY, which sets??
+The sets you mentioned before are already clusters, isn't it?), because the number of CCCs of the cluster which bases on $s_1$ should be no less than the cluster which bases on $s_2$, as the latter has one extra node compared with the former cluster.
+%%When $s_1'$ and $s_2'$ are mapped to CRN respectively, there is contradiction between them, because the number of common channels of CR node group $\{1,1,2,2\}$ is smaller than that of $\{1,1,2,2,3,3,4,4\}$.
+%But as to any instance of the solution to the weighted k-set packing problem, this contradiction doesn't happen because the instance $\mathcal{S}$ contains only disjoint sets, thus at most only one set of $s_1$ and $s_2$ appears in $\mathcal{S}$.%, then we can safely delete the connections based on the deleted set from the CRN, and the contradiction is eliminated.
+%(THIS PARAGRAPH IS TOO DIFFICULT FOR ME TO UNDERSTAND.)
+
+\item In this step, we transform the instance $\mathcal{I'}$ to a clustering proposal for CRN.
+%We prepare a second pool of CR nodes which are identical with the CR nodes prepared in step 1, i.e., identical IDs and channel availabilities on them, we call these CR nodes dummy nodes.
+We adjust the locations of the CR nodes which are mapped from the dummy elements in the instance $\mathcal{I'}$, to let them beside the CR nodes whose ID is $N$ smaller.
+% (THAT DOESN'T MAKE SENSE.
 THEN THE ID IS NOT UNIQUE ANYMORE.) in the CRN built in step 1, and there is connection between the CR node and its dummy node (the one CR node and its dummy node can be seen as two transceivers at one node).
@@
 %
-Afterwards, the CR node whose ID doesn't appear in any set in $\mathcal{S}$ becomes single node clusters, according to the definition of clustering problem in CRN, the number of CCCs in these single node clusters is 0.
-These singleton clusters and the clusters in $\mathcal{S}$ constitute a clustering solution, and finding the singleton clusters requires at most $N$ steps.
+Afterwards, the CR node whose ID is smaller than $N$ and doesn't appear in any set in $\mathcal{S}$ becomes single node clusters, according to the definition of clustering problem in CRN, the number of CCCs in these single node clusters is 0.
+These singleton clusters and the clusters in $\mathcal{S}$ constitute a clustering proposal, and finding these singleton clusters requires at most $N$ steps.
 %We deliberately locate them so that at least one CR node can communicate with the rest of them.
@@
      \toprule
-      $\mathcal{N}$  & $\{1,2,3,4,5\}$\\ 
+      $\mathcal{N}$  & $\{0, 1,2,3,4,5,6, 7, 8, 9\}$\\ 
     \cmidrule(r){1-1}\cmidrule(lr){2-2}     
@@
       & 
-		$\{ \, \{(1,1),(1,2)\},\{(2,1),(2,2),$ \\ &$(3,1),(3,2) \}, \{ (4,1), (4,2) \} \, \}$
+		$\{ \, \{1,11\},\{2,12, 3, 13\}, \{ 4,14\} \, \}$
       \\    \cmidrule(r){1-1}\cmidrule(lr){2-2}
@@
 We have crossed the hurdle of finding one polynomial algorithm $\sigma$ which transforms an instance of weighted k-set packing to an instance of the clustering problem in CRN.
-Now we look into the step 2 in the reduction.
-As to an instance $\mathcal{S}$ for weighted k-set packing, the sum weights is identical to the sum of CCCs in the CRN mapped from $\mathcal{S'}$, even $\mathcal{S}$ contains set which only has one element.
+%Now we look into the step 2 in the reduction.
+As to an instance $\mathcal{I}$ for weighted k-set packing, the sum weights is identical to the sum of CCCs in the CRN mapped from $\mathcal{I'}$, even $\mathcal{I}$ contains set which only has one element.
 Thus, when the instance $\mathcal{S}$ is one solution and its sum weights is greater than $\lambda$, in the CRN which is mapped from $\mathcal{S'}$, the summed number of CCCs of the clusters is greater than $\lambda$.
-%
 When there is no solution out of set $\mathcal{G}$ for weighted k-set packing,
@@
 the summed number of CCCs of the clusters in the mapped CRN is also smaller than $\lambda$.
+
+When an instance $\mathcal{I}$ contains joint sets, there will be overlapped clusters among the mapped clusters, then neither is solution to their corresponding problem.
 

### 2016-04-09 journal-draft/bare_jrnl_comsoc.tex
modified proof of 5.1, polish some triviral things

@@
 \midrule
-$\mathcal{N}$  & collection of secondary users, $N=|\mathcal{N}|$\\
+$\mathcal{N}$  & collection of CR users in a CRN\\
+$N$ & number of CR users in a CRN, $N=|\mathcal{N}|$\\
 $\mathcal{K}$	& set of licensed channels\\
@@
 \label{clustering:theorem}
-Given a CRN, every secondary user is included into at least one cluster within $N$ steps. (COMMENT: $N$ has to be defined within the theorem!!)
+Given a CRN, it takes at most $N$ steps that every secondary user either becomes cluster head, or gets included into at least one cluster.
 \end{theorem}
-Here, by \textit{step} we mean one application of Algorithm~\ref{clustering:theorem} by a secondary user.
+Here, by \textit{step} we mean one secondary user executing Algorithm~\ref{clustering:theorem} for one time.
 The Proof is in Appendix~\ref{proof_clustering:theorem}.
-According to Theorem~\ref{clustering:theorem}, Phase I completes within a reasonable amount of time.
+
+The procedure of the proof also illustrates the time needed to conduct Algorithm~\ref{clustering:theorem}. 
+Consider an extreme scenario, where all the secondary nodes sequentially execute Algorithm~\ref{alg0}, \ie they constitute one list as discussed in the example in the proof.
+%
+If one step can be finished within certain time $T$, then the total time needed for the network to conduct Algorithm~\ref{clustering:theorem} is $N*T$.
+In other scenarios, as Algorithm~\ref{alg0} can be executed concurrently by secondary users which locate in different places, the needed time can be considerably reduced.
+%According to Theorem~\ref{clustering:theorem}, Phase I completes within a reasonable amount of time.
 
@@
 Then $\omega$ incorporates all its one-hop neighbours (here we assume that every newly formed cluster has common channels), including the nodes which precede $\omega$ in the list.
-The nodes which join a cluster set their individual connection degrees to $M$, which enables the node immediately precede in the listto become a cluster head.
+The nodes which join a cluster set their individual connection degrees to $M$, which enables the node immediately precede in the list to become a cluster head.
 In this way, cluster heads are generated from the tail of list to the head of the list, and all the nodes in the list are in at least one cluster, which contradicts the assumption that $\alpha$ is not included in any cluster.
 
-(This paragraph should be moved out of the proof.)
-The procedure of this proof also illustrates the time needed to complete phase I. 
-Consider an extreme scenario, where all the secondary nodes sequentially execute Algorithm~\ref{alg0}, and constitute one list as that in the above example.
-If we see a secondary user \textit{becoming a cluster head}, or \textit{becoming a cluster member} as one step, then there are $N$ steps for this scenario to complete phase I.
-If one step can be finished within certain time, we can give the maximum time needed to conduct the phase I of ROSS.
-In other scenarios, as Algorithm~\ref{alg0} can be executed concurrently by secondary users which locate in different places, the needed time can be considerably reduced.
+If we see a secondary user \textit{becoming a cluster head}, or \textit{becoming a cluster member} as one step, as the length of the list of secondary users is not larger than $N$, there are $N$ steps for this scenario to form the initial clusters.
+
 %we know that within at most $N$ steps, all the nodes belong to certain clusters. (COMMENT: No, we don't! Where was that shown?)
@@
 %\end{itemize}
-We show the existence of a polynomial-time algorithm $\sigma$ that transforms any instance $\mathcal{I}$ of a weighted $k$-set packing into an instance $\sigma(\mathcal{S})$) of centralized clustering problem.
+We show the existence of a polynomial-time algorithm $\sigma$ that transforms any instance $\mathcal{I}$ of a weighted $k$-set packing into an instance $\sigma(\mathcal{I})$) of centralized clustering problem.
 
@@
 
-\item Mapping the elements in $\mathcal{I'}$ to CR nodes, and mapping the sets in $\mathcal{I'}$ to clusters.
+\item Mapping the elements in $\mathcal{I'}$ to CR nodes on a two-dimensional Euclidean plane, and mapping the sets in $\mathcal{I'}$ to clusters.
 There is a bijection between the union of sets in $\mathcal{I'}$ to the CRN which consists of the CR nodes, in particular, each element one-to-one corresponds to the CR node whose node ID equals to the element.
@@
 %We define a set of CR nodes $\mathcal{N} = \{ 1, \ldots , N \}$
-We further regulate that, each set in $\mathcal{I}$ as a corresponding cluster, \ie there is a bijection between a set in $\mathcal{I}$ and a set of node IDs in a cluster, besides, the number of CCCs is equal to the weight of the corresponding set.
+We further regulate that, each set in $\mathcal{I'}$ has a corresponding cluster, \ie there is a bijection between a set in $\mathcal{I'}$ and a set of node IDs in a cluster, besides, the number of CCCs is equal to the weight of the corresponding set.
 
@@
 %We prepare a second pool of CR nodes which are identical with the CR nodes prepared in step 1, i.e., identical IDs and channel availabilities on them, we call these CR nodes dummy nodes.
-We adjust the locations of the CR nodes which are mapped from the dummy elements in the instance $\mathcal{I'}$, to let them beside the CR nodes whose ID is $N$ smaller.
+We adjust the locations of the CR nodes which are mapped from the dummy elements in the instance $\mathcal{I'}$, and let them beside the CR nodes whose ID is exact $N$ smaller.
 % (THAT DOESN'T MAKE SENSE.
@@
 (YOU DON'T NEED TO GIVE PRACTICAL MOTIVATION IN A HARDNESS-PROOF.)
-Because of the dummy nodes, the clustering solution which corresponds to $\mathcal{S'}$ doesn't have singleton cluster.
-This transformation requires $2\cdot\sum_{s_i \in \mathcal{S}} |s_i|$ steps.
-%
-Afterwards, the CR node whose ID is smaller than $N$ and doesn't appear in any set in $\mathcal{S}$ becomes single node clusters, according to the definition of clustering problem in CRN, the number of CCCs in these single node clusters is 0.
-These singleton clusters and the clusters in $\mathcal{S}$ constitute a clustering proposal, and finding these singleton clusters requires at most $N$ steps.
+Because of the dummy nodes, the clustering solution which corresponds to $\mathcal{I'}$ doesn't have singleton cluster.
+This transformation requires $2\cdot\sum_{s_i \in \mathcal{I'}} |s_i|$ steps.
+%
+Now we look back to the elements in $\mathcal{G}$, which don't appear in $\mathcal{I'}$. 
+We one-to-one map these elements to CR nodes, and arbitrarily put these CR nodes in the plane, and these CR nodes become single node clusters.
+According to the definition of clustering problem in CRN, the number of CCCs in these single node clusters is 0.
+These singleton clusters and the clusters mapped from $\mathcal{I'}$ constitute a clustering proposal, and finding these singleton clusters requires at most $N$ steps.
 %We deliberately locate them so that at least one CR node can communicate with the rest of them.
@@
 %Now we look into the step 2 in the reduction.
-As to an instance $\mathcal{I}$ for weighted k-set packing, the sum weights is identical to the sum of CCCs in the CRN mapped from $\mathcal{I'}$, even $\mathcal{I}$ contains set which only has one element.
-Thus, when the instance $\mathcal{S}$ is one solution and its sum weights is greater than $\lambda$, in the CRN which is mapped from $\mathcal{S'}$, the summed number of CCCs of the clusters is greater than $\lambda$.
+When $\mathcal{I}$ is not an instance for weighted k-set packing problem due to the existence of joint sets, then the corresponding cluster strategy is not a solution for the centralized clustering problem, as there are overlapped clusters.
+
+When there are only disjoint sets in an instance $\mathcal{I}$ for weighted k-set packing, the sum weights is identical to the sum of CCCs in the CRN mapped from $\mathcal{I'}$, even $\mathcal{I}$ contains set which only has one element.
+Thus, when a instance $\mathcal{I}$ is one solution and its sum weights is greater than $\lambda$, in the CRN which is mapped from $\mathcal{I'}$, the summed number of CCCs of the clusters is greater than $\lambda$.
 When there is no solution out of set $\mathcal{G}$ for weighted k-set packing,
@@
 %%Meanwhile, the number of common channels of all the other single node cluster is 0.
-the summed number of CCCs of the clusters in the mapped CRN is also smaller than $\lambda$.
-
-When an instance $\mathcal{I}$ contains joint sets, there will be overlapped clusters among the mapped clusters, then neither is solution to their corresponding problem.
+the summed number of CCCs of the clusters in the mapped CRN is always smaller than $\lambda$.
+
+%When an instance $\mathcal{I}$ contains joint sets, there will be overlapped clusters among the mapped clusters, then neither is solution to their corresponding problem.
 

### 2016-04-09 journal-draft/bare_jrnl_comsoc.tex
polished proof of 5.1

@@
 
-When there are only disjoint sets in an instance $\mathcal{I}$ for weighted k-set packing, the sum weights is identical to the sum of CCCs in the CRN mapped from $\mathcal{I'}$, even $\mathcal{I}$ contains set which only has one element.
-Thus, when a instance $\mathcal{I}$ is one solution and its sum weights is greater than $\lambda$, in the CRN which is mapped from $\mathcal{I'}$, the summed number of CCCs of the clusters is greater than $\lambda$.
-When there is no solution out of set $\mathcal{G}$ for weighted k-set packing,
+When there are only disjoint sets in an instance $\mathcal{I}$ for weighted k-set packing, the sum weight is identical to the sum number of CCCs in the CRN mapped from $\mathcal{I'}$, even $\mathcal{I}$ contains sets which only have one element.
+Thus, when a instance $\mathcal{I}$ for k-set packing problem is true, \ie the sum of weights is greater than $\lambda$, then in the CRN which is mapped from $\mathcal{I'}$, the summed number of CCCs of the clusters is greater than $\lambda$.
+In the other way around, when an instance if false for weighted k-set packing problem,
 %let's assume the maximum sum of weights of all instances is $\sum_{s_i\in \mathcal{S}}\omega(s_i)=\delta < \lambda$. 
@@
 %%Meanwhile, the number of common channels of all the other single node cluster is 0.
-the summed number of CCCs of the clusters in the mapped CRN is always smaller than $\lambda$.
+the summed number of CCCs of the clusters in the mapped CRN is smaller than $\lambda$, and there is no clustering solution satisfying the centralized clustering problem.
 

### 2016-07-24 journal-draft/bare_jrnl_comsoc.tex
change one plot, and minor changes
the version before sending to James in July

@@
 \usepackage{hhline}
+\usepackage{float}
+\usepackage{caption}% http://ctan.org/pkg/caption
+\captionsetup[table]{format=plain,labelformat=simple,labelsep=period}%
 
@@
 \usepackage[draft,nomargin,marginclue,footnote,silent]{fixme}
-\setcounter{tocdepth}{2}
+\setcounter{tocdepth}{2} %table of contents
 
@@
 Cluster structure in cognitive radio networks facilitates cooperative spectrum sensing, routing and other functionalities.
-The availability of unlicensed channels which are available for every member in a cluster decides the robustness of that cluster against the licensed users' influence.
-Thus there should be more unlicensed channels in the clusters.
-In the process of forming clusters, every secondary user decides with whom to form a cluster, or which cluster to join.
-Congestion game model is adopted to analyse this process, which not only contributes the algorithm design directly, but also provides guarantee of convergence into Nash Equilibrium and convergence speed.
-%
-Our proposed distributed clustering scheme outperforms the comparison scheme in terms of cluster robustness against the primary users, convergence speed and volume of control messages.
-Furthermore, the proposed clustering solution is versatile to fulfil other requirements such like fast convergence and cluster size control.
-Besides, we prove the clustering problem is NP-hard, and also propose the centralized solution.
+The unlicensed channels, which are available for every member of a group of cognitive radio users, consolidate the group into a cluster, and the availability of unlicensed channels decides the robustness of that cluster against the licensed users' influence.
+%Thus there should be more unlicensed channels in the clusters.
+This paper analyses the problem that how to form robust clusters in cognitive radio network, so that more cognitive radio users can get benefits from cluster structure even when the primary users' operation are intense.
+%In the process of forming clusters, every secondary user decides with whom to form a cluster, or which cluster to join.
+We provide a formal description of robust clustering problem, prove it to be NP-hard and propose a centralized solution, besides, a distributed solution is proposed to suit the dynamics in the ad hoc cognitive radio network.
+Congestion game model is adopted to analyse the process of cluster formation, which not only contributes designing the distributed clustering scheme directly, but also provides the guarantee of convergence into Nash Equilibrium and convergence speed.
+Our proposed clustering solution is versatile to fulfil some other requirements such as faster convergence and cluster size control.
+The proposed distributed clustering scheme outperforms the related work in terms of cluster robustness, convergence speed and overhead.
+%Besides, we prove the clustering problem is NP-hard, and also propose the centralized solution.
 The extensive simulation supports our claims.
@@
 \begin{IEEEkeywords}
-Cognitive Radio, Cluster, Robust, game theory, congestion game, distributed, centralised, size control.
+cognitive radio, robust cluster, game theory, congestion game, distributed, centralised, cluster size control.
 \end{IEEEkeywords}
@@
 \IEEEPARstart{C}{ognitive} radio (CR) is a promising technology to solve the spectrum scarcity problem~\cite{Mitola}.
-Unlicensed users access the spectrum allocated to them whenever there is information to be transmitted.
-In contrast, unlicensed users can only access the licensed spectrum after validating the channel is unoccupied by licensed users.
-This refers to the process of sensing a particular channel and verifying (with a previously specified probability of error) it is not used by a primary user currently.
+Licensed users access the spectrum allocated to them whenever there is information to be transmitted.
+In contrast, unlicensed users can only access the licensed spectrum after validating the channel is unoccupied by licensed users, where spectrum sensing~\cite{sensing_survey_2009} plays an important role in this process.
+%This refers to the process of sensing a particular channel and verifying (with a previously specified probability of error) it is not used by a primary user currently.
 In this hierarchical spectrum access model~\cite{zhao_survey_DSA_2007}, the licensed users are also called primary users (PU), and the CR users are known as secondary users and constitute the cognitive radio networks (CRN).
-
+%
 %cluster
 As to the operation of CRN, efficient spectrum sensing is identified to be critical to the success of cognitive radio networks~\cite{Sahai_FundamentalDesignTradeoffs2006}.
-Cooperative spectrum sensing is able to effectively cope with noise uncertainty and channel fading, thus remarkably improves the sensing accuracy~\cite{coorperativeSensing_Akyildiz11}.
-Collaborative sensing relies on the consensus of CR users within certain area, and decreases considerably the false sensing reports caused by fading and shadowing of reporting channel.
+Cooperative spectrum sensing is able to effectively cope with noise uncertainty and channel fading, thus remarkably improving the sensing accuracy~\cite{coorperativeSensing_Akyildiz11}.
+Collaborative sensing relies on the consensus of CR users within certain area, and decreases considerably the negative probability due to the random channel effects like fading and shadowing.
 In this regard, clustering is regarded as an effective method in cooperative spectrum sensing~\cite{Sun07_clustering_spectrum_secsing, Zhao07}, as a cluster forms adjacent secondary users as a collectivity to perform spectrum sensing together.
@@
 %
-In CRN, one cluster survives the influence of primary users when at least one CCC is available for that cluster.
-As the channel occupation by primary users is assumed to be uncontrollable to the CR users, a cluster formed with more CCCs will survive with higher probability.
-Thus the number of CCCs in one cluster indicates robustness of it when facing ungovernable influence from primary users.
+In CRN, one cluster survives the influence of primary users when at least one CCC is available in that cluster.
+As the primary users' operation is assumed to be unknown to the CR users, a cluster formed with more CCCs will survive with higher probability.
+Thus the number of CCCs in one cluster indicates the robustness of it when facing the unpredictable influence from primary users.
 %It is easy to see that forming clusters with different neighbours leads to different amount of CCCs in the clusters.
-As a result, how to form the clusters plays an important role on the robustness of clusters in CRN.
+%As a result, how to form the clusters plays an important role on the robustness of clusters in CRN.
 
@@
 
-To solely pursue cluster robustness against the primary users' activity, \ie to achieve more common channels within clusters, the ultimately best clustering strategy is ironically that each node constitutes one single node clusters.
+To solely pursue cluster robustness against the primary users' activity, \ie to achieve more common channels within clusters, the ultimately best clustering strategy is ironically that every node constitutes one cluster (called as \textit{singleton cluster} in this paper).
 %In that case, the common channels within cluster are the available channels available at that node's place.
-Apparently this contradicts our motivation of proposing cluster in cognitive radio network.
+Apparently this contradicts our motivation of proposing cluster in cognitive radio network to enable cooperative decision making.
 This contradiction indicates that, the robustness discussed in terms of number of common channels carries little meaning when the sizes of formed clusters are not given consideration.
@@
 For instance, cluster size is one decisive factor in power preservation~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}, and it also influences the accuracy of cooperative spectrum sensing~\cite{Consensus_based_clustering12}.
-Hence, cluster size should be given consideration when discussing cluster robustness against primary users.
+%thesis
+%Hence, cluster size should be given consideration when discussing cluster robustness against primary users.
 
 In this paper, a decentralized clustering approach ROSS (RObust Spectrum Sharing) is proposed to cover the issues of robustness and size control of clusters in CRN.
-ROSS is able to form clusters with desired sizes, and the generated clusters are more robust than other clustering scheme which has claims on cluster robustness, \ie more secondary users residing in clusters against increasing influence from primary users.
-Compared with previous work, ROSS involves much less control messages, and the generated clusters are significantly more robust.
+ROSS is able to form clusters with desired sizes, and when compared with previous works, ROSS involves smaller signalling overhead, and the generated clusters are significantly more robust against the primary users which appear after the clusters are formed.
+%thesis
+%and the generated clusters are more robust than the other clustering scheme which has claims on cluster robustness, \ie more secondary users residing in clusters against increasing influence from primary users.
+%
 %ROSS selects cluster head through coordination within its neighborhood, and then cluster membership is decided locally and its fast convergence is proved under game theoretic framework. 
 %For our scheme we can prove convergence in cluster formation phase and resolve ambiguities with respect to cluster membership in a game-theoretic setting. 
-We also propose the light weighted versions of ROSS, which involve less overheads and thus are more suitable for mobile networks.
+We also propose the light weighted versions of ROSS, which involve less overheads and thus are more suitable for fast deployment.
 Throughout this paper, we refer the clustering schemes on the basis of ROSS as \textit{variants of ROSS}, \ie the fast versions, or that with size control feature.
@@
 The rest of paper is organized as follows. 
-After reviewing related work in section~\ref{related_work}, we present our system model in Section~\ref{sec:model}. 
-Then we introduce our clustering scheme ROSS and its variants in section~\ref{ross}.
-The clustering problem is given through analysis and a centralized scheme is proposed in section~\ref{centralized_scheme}.
+After reviewing related work in section~\ref{related_work}, we present the system model in Section~\ref{sec:model}. 
+In Section~\ref{problem}, problem formulation is presented and the problem is thoroughly analysed.
+The centralized clustering scheme and the our proposed clustering scheme ROSS are introduced in Section~\ref{centralized_opt} and \ref{ross} respectively.
+%The clustering problem is given through analysis and a centralized scheme is proposed in section~\ref{centralized_scheme}.
 Extensive performance evaluation is in section~\ref{performance}.
@@
 
-Prior to the emergence of open spectrum access, as an important method to manage network, clustering has been proposed in for ad hoc networks~\cite{Kawadia03,Lin97adaptiveclustering,Basagni99}, wireless mesh networks and sensor networks~\cite{Abbasi_survey_07}.
+Prior to the emergence of cognitive radio, clustering has been proposed as an important method to manage network in ad hoc networks~\cite{Kawadia03,Lin97adaptiveclustering,Basagni99}, wireless mesh networks and sensor networks~\cite{Abbasi_survey_07}.
 In ad hoc and mesh networks, the major focus of clustering is to preserve connectivity (under static channel conditions) or to improve routing.
-In sensor networks, the emphasis of clustering has been on longevity and coverage.
+In sensor networks, the emphasis of clustering is on longevity and coverage.
 Overhead generated by clustering in ad hoc network is analysed in~\cite{clusterRoutingOverhead02infocom, clusterRoutingOverhead_wcnc04}.
@@
 %There have been several clustering schemes tailored for CRNs. 
-Cogmesh is proposed in~\cite{Chen07} to construct clusters by the neighbour nodes which share local common channels, and by interacting with neighbour clusters, a mesh network in the context of open spectrum sharing is formed.
-Robustness issue is not considered by this clustering approach.
+Cogmesh is proposed in~\cite{Chen07} to construct clusters with the neighbouring nodes which share local common channels.
+This method pays attention to the communication among the formed clusters, but cluster robustness is not considered.
 \cite{TWC2012_cooperative_communication} targets on the QoS poisoning and energy efficiency. 
@@
 The node with the maximum number of common channels within its k-hop neighborhood is chosen as cluster head, but how to avoid one node appearing in multiple clusters is not given consideration.
-
-Clustering robustness is considered in~\cite{Lazos09, LIU_TMC11_2}.
-The authors propose a distributed scheme where the metric is the product of cluster size and the number of common control channels.
-This scheme involves both cluster size and number of CCCs, but it is inherently flawed.
+A event-driven clustering scheme is proposed for cognitive radio sensor network in \cite{Ozger_cluster_crsn_13}.
+The cluster heads are selected according to node degree, spectrum availability and the distance to the sink, and the clusters are no longer available after the event ends.
+
+Clustering robustness is considered in~\cite{Lazos09, LIU_TMC11_2, mansoor_15_cluster_robust}.
+The first two propose a distributed scheme where the metric is the product of cluster size and the number of common control channels.
+This scheme involves both cluster size and the number of CCCs, but it is inherently flawed.
 With the metric, cluster could be formed only due to one factor of the two, e.g. a spectrum rich node will exclude its neighbour to form a cluster by itself.
@@
 Besides, this scheme leads to a high variance on the size of clusters, which is not desired in certain applications as discussed in~\cite{clustering_globecom11, cluster_EW10}.
+\cite{mansoor_15_cluster_robust} presents a heuristic method to form clusters, although the authors claim robustness is one goal to achieve, they actually uphold the minimum number of formed clusters.
 
@@
 This control channel could be in ISM band or other reserved spectrum which is exclusively used for transmitting control messages.
-Actually, the control messages involved in the clustering process can be transmitted on available licensed channels through a rendezvous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}, i.e., two neighbouring nodes establish communication on the same channel.
+Actually, the control messages involved in the clustering process can also be transmitted on the available licensed channels through a rendezvous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}, i.e., two neighbouring nodes establish communication on the same channel.
 Over the control channel, a secondary user $i$ can exchange its spectrum sensing result $K_i$ to any $i' \in \text{Nb}(i)$.
@@
 
-\subsection{Clustering}
+\section{Robust Clustering Problem in CRN}
+\label{problem}
+In this section, we describe the definition of cluster in the context of CRNs, and the problem of robust clustering.
+
+\subsection{Cluster in CRN}
 \label{def_cluster}
@@
 %\end{itemize}
-In this section, we describe what a cluster in the context of CRNs means.
-A cluster $C \subseteq \mathcal{N}$ is a set of secondary nodes consisting of a cluster head $h_{\textsf{C}}$ and a number of cluster members.
+A cluster $C \subseteq \mathcal{N}$ is a set of secondary nodes consisting of a cluster head $h_C$ and a number of cluster members.
 The cluster head is able to communicate with any cluster member directly.
@@
 
-\section{Clustering Algorithm: ROSS}
+\subsection{Robust Clustering Problem}
+\label{centralized_scheme}
+
+%paper given by james is useful which provides a survey from the perspective of wsn!
+
+In the introduction section, we have stated that cluster size should be given consideration to justify the concept of robustness of clusters, \ie without specifying requirement on cluster sizes, small clusters will be generated to obtain more CCCs.
+Except for cooperative sensing, clusters need to conduct some other functionalities.
+When cluster size is large, there will be substantial burden on cluster heads to manage the cluster members, which is a challenge for resource limited cluster heads, thus the cluster size should fall in a desired range~\cite{Chen04clusteringalgorithms, capacity_cluster_06}.
+
+The centralized clustering scheme aims to form clusters with desired sizes, meanwhile the total number of CCCs of all clusters is maximized.
+In the following, we refer this problem as \textit{centralized clustering}, and give the formal problem definition.
+
+\begin{mydef}
+\label{def_centralized_clustering}
+\textit{Robust clustering problem in CRN.}
+
+Given a cognitive radio network $\mathcal{N}$ where nodes are indexed from 1 to $N$ sequentially.
+Based on certain correlation, certain secondary users constitute one cluster $C$.
+$1\leq |C| \leqslant k$ where $|C|$ is the size of cluster $C$ and $k$ is a positive integer.
+We name the collection of such clusters as $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$, where $\mathcal{S}$ satisfies the following properties: $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$ and $K(C(i))\neq \emptyset$ for any $i$ which satisfies $1\leq i \leq |\mathcal{S}|$.
+
+%, which distinguishes the centralized clustering problem discussed in this paper.
+We give a new definition of the number of CCCs, where the number of common control channels is $|K(C)|$ if $|C|>1$, and is zero when $|C|=1$.
+We use $f(C)$ to denote the number of CCCs of a cluster $C$ in the new definition.
+
+The centralized clustering problem is to find a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, so that $\bigcup_{C_j\in \mathcal{S}'} C_j = N$, and $C_{j'}\cap C_j =\emptyset$ for $C_{j'}, C_j\in \mathcal{S}'$ and $j'\neq j$, so that $\sum_{C\in \mathcal{S}'} f(C)$ is maximized.
+% when $|C|>1$, and $f(\cdot)=0$ when $|C|=1$.
+%As to $f(\cdot):z\rightarrow z$, under this problem setting, if only number of common channels are given consideration, only singleton clusters will be preferred, which contradicts to our goal of clustering CR nodes together, thus we choose $f(\cdot)= |K_{C}|\cdot |C|$, the product of number of common channels and cluster size.
+The decision version of centralized clustering in CRN is to ask whether there exists a no-empty $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C\in \mathcal{S}'} f \geqslant \lambda$ where $\lambda$ is a real number.% in stead of to maximize $\sum_{C\in \mathcal{S}'} f$.
+\end{mydef}
+
+%The decision version of \textit{weighted exact cover problem}: 
+%Given an universe $U$, and collection $S=\{s_1, s_2, \ldots, s_m\}$ where each subset $s_i\subseteq U$ and is given a weight $w_i$, whether there exists a collection of subsets $\mathcal{C}$ and constant number $\lambda$, so that the union of $\mathcal{C}$ equals to $U$, $s_j\cap s_{j'} = \emptyset$ for different $j$ and $j'\in \{1,2,\ldots, m\}$, and $\sum_{i\in J} w_i \geq \lambda$.
+
+\subsection{Complexity of the Robust Clustering Problem}
+In this section we investigate the complexity of robust clustering problem.
+Theorem~\ref{theorem1} tells centralized clustering problem in CRN is one NP-hard problem.
+
+\begin{theorem}
+\label{theorem1}
+CRN clustering problem is NP-hard, when the maximum size of clusters $k\geqslant 3$.
+%Assume a CRN can be represented by a connected graph, and there is at least one common channel between any pair of neighbours, then forming at least two CR nodes into one cluster is NP-complete.
+\end{theorem}
+The proof is in Appendix~\ref{proof_theorem1}.
+In the following sections, both centralized and distributed solutions will be introduced.
+
+\section{Centralized Solution for Robust Clustering}
+\label{centralized_opt}
+%Exact cover problem can be solved with Knuth's Algorithm X~\cite{dancingLinks_Knuth} as it finds out all the instances of exact cover, then we can choose the one with the biggest sum of weights. 
+As the robust clustering problem in CRN is NP hard, there is no polynomial algorithm to solve the problem, \ie maximizing the sum of CCCs in all non-singleton clusters.
+Thus, we formulate the problem into a binary linear programming problem, where the objective function and the constraints are heuristic, in particular, the objective is different from the object in the Definition~\ref{def_centralized_clustering}.
+%Note that binary linear programming is in NP-complete.
+
+%This example indicates the chose of $\mathcal{C}$ plays an important role on the resultant clustering strategy.
+%Meanwhile, it provide a chance to constrain the cluster size by putting groups with desired sizes into $\mathcal{C}$.
+
+%the maximum size of $S$ is the \textit{Bell number} of $N$, and $S$ contains the conditions cluster .
+%In this case, the resultant $\mathcal{C}$ is composed with all the singleton clusters, \ie, the cluster which contains one node, and the objective is -38.
+
+%it is possible that there doesn't exist combination of clusters with the same cluster size.
+%We thus list all possible clusters whose sizes are from 2 to one certain number \footnote{this number of decided by the density of CR network, along with the occupation of PUs.
+We set this number as cluster size of the biggest cluster ever appears when conducting distributed schemes.}, and check each combination of clusters to find the best covering of network on the aspect of number of ICCs per cluster.
+%The complexity of computation is thus \bigO$(N^\delta)$, $\delta$ is the preferred cluster size.
+
+%The global optimal clustering scheme with respect to the number of common channels is investigated to show the gap with the distributed schemes.
+
+%We apply this centralized scheme on a network with network size $N$ and cluster size $\delta$.
+%There is $N\mod \delta=0$, and the expected number of clusters is $C = N/\delta$.
+%These tailored parameters don't harm the validity of the performance gap between the two schemes.
+
+Given a CRN $\mathcal{N}$ and desired cluster size $\delta$, we obtain a collection of clusters $\mathcal{G}$ which contains all the \textit{legitimate} clusters, and the sizes of these clusters are $1,2,\ldots,\delta$.
+Legitimate clusters are the clusters which satisfy the conditions in Section~\ref{def_cluster}. 
+Note that the legitimate clusters include the \textit{singleton} ones, \ie the cluster which has only one CR node, so that we can guarantee the partition of any network is always feasible.
+%
+With $N=|\mathcal{N}|, G=|\mathcal{G}|$, we construct a constant $G\times N$ matrix $Q_{G\text{x}N}$. 
+The element of matrix $Q$ is $q_{ij}$, where the subscript $i$ is the index of legitimate cluster, and $j$ is the node ID of one CR node.
+%Note that $C_i$ means $i$th cluster in the collection $\mathcal{G}$, doesn't denote the cluster where cluster head is $i$, this notation is only valid in this subsection.
+There are $i\in \{1,2,\cdots,G-1, G\}$, and $j\in \{1,2,\cdots,N-1, N\}$.
+Element $q_{ij}= |K(C_i)|$ if node $j\in C_i$, and $q_{ij}= 0$ if $j\notin C_i$.
+In other words, each non-zero element $q_{ij}$ denotes the number of CCCs of the cluster $i$ where node $j$ resides.
+
+\begin{figure}[ht!]
+\centering
+\bordermatrix{~ 		& 1 	& 2 	& 3 	& \cdots & j & \cdots	& N-1 	& N	\cr
+                  1 	& |K(C_1)| 	& |K(C_1)| 	& 0 	& \cdots & \cdots &\cdots	& 0 	& 0	\cr
+                  2 	& |K(C_2)| 	& 0 	& |K(C_2)| 	& \cdots & \cdots & \cdots 	& 0 	& 0	\cr
+				\vdots  	&\vdots & 	 	& 		&  \vdots		& 		& \vdots \cr
+				i 	& 0 	& |K(C_i)| 	& 0 	& \cdots  & \cdots & \cdots 	& |K(C_i)| 	& 0	\cr
+				\vdots  	&\vdots & 	 	& 		&  \vdots & \cdots & \cdots 		& 		& \vdots \cr
+				\vdots 	& \vdots  	& 0 	& 0 	& \cdots & \cdots & \cdots 	& |K(C_i')| 	& 0	\cr
+				G  	& |K(C_G)| & \cdots	 	& 		&  \vdots	& \cdots & \cdots& 		& \vdots \cr}	
+\caption{An example of Matrix $Q$, its rows correspond to all legitimate clusters, and columns correspond to the CR nodes in the CRN.}
+\label{xx}
+\end{figure}
+
+We build a $G\times N$ binary variable matrix $X$, which illustrates the clustering solution.
+The element of matrix $X$ is binary variable $x_{ij}, i=1, \ldots, G, j=1, \ldots, N$.
+%$x_{ij}=1$ denotes node $i$ is in the $j$th legitimate cluster, and the cluster is chosen in the solution, $x_{ij}=0$ means the $j$th legitimate cluster is not adopted by the partition.
+%Note that matrix $Q$ contains only constant elements, and matrix $X$ contains only binary variables.
+Now, we can formulate the optimization problem as follows,
+
+\begin{equation}
+\begin{aligned}
+     &\min\limits_{x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^G (-x_{ij}q_{ij} + (1-w_i)*p) \\
+     &\text{subject to}   && \Sigma_{i=1}^G x_{ij} = 1, for \forall j=1, \ldots, N \\
+   &&& \Sigma_{j=1}^N x_{ij} = |C_i|*(1-w_i), for \forall i=1, \ldots, G \\
+   &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
+   &&& i\in \{1,2, \cdots G\}, \hspace{0.3cm} j\in \{1,2,\cdots N\}
+\notag
+\end{aligned}
+\end{equation}
+
+The objective is a sum of two components, the first component is the sum of products of cluster size and the corresponding number of CCCs, which is the sole metric adopted by the scheme SOC~\cite{Lazos09}.
+The second component is the \textit{punishment} for choosing the clusters whose sizes are not $\delta$.
+In fact, the second part is particularly designed to eliminates the drawbacks of SOC, \ie SOC produces a large number of singleton clusters and a few large clusters.
+In practical computation, we minimize the opposite of the first part, and the punishment is a positive value.
+%
+The first constraint restricts each node $j$ to reside in exactly one cluster.
+In the second constraint, $w_i$ is an auxiliary binary variable which denotes whether cluster $C_i$ is chosen by the solution, in particular, 
+$$
+w_i = \left\{ \begin{array}{rl}
+0 &\mbox{if $i$th legitimate cluster $C_i$ is chosen} \\
+1 &\mbox{if $i$th legitimate cluster $C_i$ is not chosen} \\
+\end{array} \right.
+$$
+The second constraint regulates that when the $i$th legitimate cluster $C_i$ is chosen, the number of elements which equal to 1 in the $i$th row of the matrix $X$ is $|C_i|$.
+%
+Now we explain how does the mechanism of the punishment in the objective work. 
+The parameter $p$ is defined as follows,
+$$
+p = \left\{ \begin{array}{rl}
+0 &\mbox{ if $|C_i|=\delta$} \\
+\alpha_1 &\mbox{if $|C_i|=\delta-1$} \\
+\alpha_2 &\mbox{if $|C_i|=\delta-2$} \\
+\dots
+\end{array} \right.
+$$
+where $\alpha_i>0$ and increases when $|C_i|$ diverges from $\delta$.
+Because of $w_i$, any chosen cluster ($w=0$) brings certain \textit{punishment}.
+When the chosen cluster's size is desired size $\delta$, the punishment is zero.
+In contrary, when the chosen cluster's size diverges from $\delta$, the objective function suffers \textit{loss}.
+In particular, when $w_i=0$ and $|C_i|=1$, the punishment is the most severe.
+This design doesn't follow the definition of $f(C)$ in Definition~\ref{def_centralized_clustering} strictly, where $f(C_i)=0$ when $|C_i|=1$, but our design echoes the definition by exerting the most severe punishment on the singleton clusters in the clustering solution.
+Choice of $\alpha_i$ affects the resultant clusters.
+
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[width=0.45\linewidth]{example.JPG}
+%\caption{Example of Matrix Q in a 6-node network, cluster size is set as 2}
+%\label{xx}
+%\end{figure}
+
+%\begin{figure}[ht!]
+%  \centering
+%  \includegraphics[width=0.5\linewidth]{figure5final.pdf}
+%  \caption{Final cluster formation.}
+%  \label{fig4}
+%\end{figure}
+
+%Note that the proposed centralized solution is heuristic.
+%We reiterate the reasons for pursuing the heuristic scheme, 
+%Note the collection of legitimate clusters is dependant on the network topology and spectrum availability in the network, thus to each specific CRN, the space of solution is different.
+
+\section{Distributed Clustering Algorithm: ROSS}
 \label{ross}
-
-In this section we introduce the distributed clustering scheme ROSS which leads to robust clusters against PU' influence.
+The cluster formation of one CRN can be obtained by solving the proposed optimization problem, but centralized scheme is inherently not suitable for the CRN which involves dynamics, \eg the mobility of CR users and the variance of the available spectrum due to primary users' operation.
+In this section we introduce the distributed clustering scheme ROSS.
+%
 ROSS consists of two cascaded phases: \textit{cluster formation} and \textit{membership clarification}.
-With ROSS, CR nodes form clusters on the basis of the proximity of the available spectrum in their neighbourhood.
-Afterwards, CR nodes belong to one certain cluster.
-%by interacting with certain neighbours.
+With ROSS, CR nodes form clusters based on the proximity of the available spectrum in their neighbourhood. Afterwards, CR nodes belong to one certain cluster. %by interacting with certain neighbours.
 %is based on the spectrum sensing results in its neighbours , then
@@
 Individual connectivity degree $d_i$ and social connectivity degree $g_i$ together form the \textit{connectivity vector}.
-Figure~\ref{fig1} illustrates an example CRN where each node's connectivity vector is calculated and shown.	
+Figure~\ref{fig1} illustrates an example CRN where each node's connectivity vector is shown.	
 \begin{figure}[ht!]
@@
 % \includegraphics{figure1.pdf}
-	\caption{Connectivity graph and the connectivity vector $(d_i, g_i)$ for each node.
-The available channels sensed by each node are: $K_A=\{1,2,3,4,5,6,10\}, K_B=\{1,2,3,5,7\}, K_C=\{1,3,4,10\}, K_D=\{1,2,3,5\}, K_E=\{2,3,5,7\}, K_F=\{2,4,5,6,7\}, K_G=\{1,2,3,4,8\}, K_H=\{1,2,5,8\}$.
-Dashed edge indicates the end nodes are within each other's transmission range.
-The number of common channels between two nodes is shown by the edge.}
+	\caption{Connectivity graph of the example CRN and the connectivity vector $(d_i, g_i)$ for each node.
+The sets of the indices of the available channels sensed by each node are: $K_A=\{1,2,3,4,5,6,10\}, K_B=\{1,2,3,5,7\}, K_C=\{1,3,4,10\}, K_D=\{1,2,3,5\}, K_E=\{2,3,5,7\}, K_F=\{2,4,5,6,7\}, K_G=\{1,2,3,4,8\}, K_H=\{1,2,5,8\}$.
+Dashed edge indicates the end nodes are within each other's transmission range.}
+	% The number of common channels between two nodes is shown by the edge.
 	\label{fig1}
@@
 %According to Theorem~\ref{clustering:theorem}, Phase I completes within a reasonable amount of time.
-
+%
 %This judgement is conducted periodically, and phase I ends after every node ascertains it is cluster head or not.
@@
 %After deciding itself being cluster head, CR node broadcasts to notify its neighbours on the dedicated control channel, meanwhile, $i$'s initial cluster is formed immediately, which is $i$'s neighbourhood except for those nodes which have become cluster heads, \ie $C_i=(\text{Nb}_i\setminus \text{CHs})\cup i$.
-After executing phase I of ROSS, there are some secondary users which become cluster heads.
-The cluster head and its neighbourhood (except for the CHs) form a cluster.
-It is possible that certain formed clusters don't own CCCs, then we solve this problem with the following method.
-
-As decreasing cluster size increases the number of CCCs within the cluster, to have at least one CCC, certain nodes are eliminated.
+After executing phase I of ROSS, it is possible that certain formed clusters don't own CCCs.
+%We solve this problem with the following method.
+%there are some secondary users which become cluster heads.
+%The cluster head and its neighbourhood (except for the CHs) form a cluster.
+%
+As decreasing cluster size increases the number of CCCs within the cluster, for those clusters having no CCCs, certain nodes need to be eliminated to gain at least one CCC.
 The sequence of elimination is performed according to an ascending list of nodes which are sorted by the number of common channels between the nodes and the cluster head. 
@@
 
-In the introduction section, we have stated that cluster size should be given consideration to justify the concept of robustness of clusters, \ie without specifying requirement on cluster sizes, small clusters will be generated to obtain more CCCs.
-Except for cooperative sensing, clusters need to conduct some other functionalities.
-When cluster size is large, there will be substantial burden on cluster heads to manage the cluster members, which is a challenge for resource limited cluster heads, thus the cluster size should fall in a desired range~\cite{Chen04clusteringalgorithms, capacity_cluster_06}.
-
 In the following we illustrate the pressing necessity to control the cluster size when CRN becomes dense via both theoretical analysis and simulation.
-Assuming the secondary and primary users are evenly distributed and primary users occupy the licensed channels randomly, then both CR nodes density and channel availability in the CRN can be seen to be spatially homogeneous.
+Assuming the CR users and PUs are evenly distributed and PUs occupy the licensed channels randomly, then both CR nodes density and channel availability in the CRN can be seen to be spatially homogeneous.
 %Based on Algorithm~\ref{alg0}, cluster heads are the CR nodes which possess the biggest individual connectivity degrees in their neighborhood respectively, and they are surrounded by CR nodes.
@@
   \includegraphics[width=0.3\linewidth]{clusters_denseNetwork_2.pdf}
-  \caption{Clusters formation in extremely dense CRN. Black dots are cluster heads, other cluster members are not drawn.}
+  \caption{Clusters formation in extremely dense CRN. Black dots are cluster heads, cluster members are not drawn.}
   \label{clusters_denseNetwork}
 \end{figure}
+%\begin{figure}
+%\floatbox[{\capbeside\thisfloatsetup{capbesideposition={left,top},capbesidewidth=4cm}}]{figure}[\FBwidth]
+%{\caption{Clusters formation in extremely dense CRN. Black dots are cluster heads, other cluster members are not drawn.}\label{clusters_denseNetwork}}
+%{\includegraphics[width=0.3\linewidth]{clusters_denseNetwork_2.pdf}}
+%\end{figure}
 Let $l$ be the length of side of simulation plan square, and $r$ be CR's transmission radius.
@@
 %We can see from the example that although two neighbouring clusters can overlap greatly with each other, no cluster head will be covered by other clusters.
-Given $r$=10 and $l$=50, the number of formed clusters is shown in Figure~\ref{number_clusters_scale}.
-With the increase of CR users, network density increases linearly (the Y axis label is the average number of neighbours), and the number of formed clusters also increases and approaches to the the upper bound of 25 which complies with the estimation.
+Given $r$=10 and $l$=50, the maximum number of clusters is 25.
+The number of clusters in the simulation is shown in Figure~\ref{number_clusters_scale}.
+Simulation is run for 50 times and the confidence interval is 95\%.
+With the increase of CR users, network density (the average number of neighbours) increases linearly, and the number of clusters approaches to 25 which complies with the estimation.
 
@@
   \includegraphics[width=0.7\linewidth]{number_clusters_upperBound.pdf}
-  \caption{The correlation between the number of formed clusters and network density.
-Note that the number of neighbours denotes the network density.
-Simulation is run for 50 times and the confidence interval is 95\%.}
+  \caption{The correlation between the number of formed clusters and network density.}
   \label{number_clusters_scale}
@@
 
-Both the analysis and simulation show that when applying ROSS, after the number of clusters saturates with the increase of network density, the cluster size increases almost linearly with the network density, thus certain measures are needed to curb this problem.
+Both analysis and simulation show that when applying ROSS, after the number of clusters saturates with the increase of network density, the cluster size increases linearly with the network density, thus certain measures are needed to curb this problem.
+
 This task falls to the cluster heads.
-
 To control the cluster size, cluster heads prune their cluster members to achieve the desired cluster size.
@@
   \includegraphics[width=0.5\linewidth]{figure2.pdf}
-  \caption{Clusters formation after the first phase of ROSS. There are some nodes being debatable nodes, \ie belonging to more than one cluster.}
+  \caption{Clusters formation after the phase I of ROSS. Some nodes are debatable nodes, \ie belonging to more than one cluster.}
   \label{fig2}
@@
 After deciding its membership, debatable node $i$ notifies all its claiming clusters, and retrieves the updated information of the claiming clusters, \eg $K(C)$, $K_{h_C}$, $|C|$, where $C\in S_i$.
-
-This procedure raises a concern that the debatable nodes may never stop changing their affiliations, as debatable nodes' choices seem to be dependent on each other, thus the infinite chain effect never ceases.
-%  update their choices based on other debatable nodes' choices, and this process 
-For example, assuming one debatable node $i$ locates in cluster $C\in S_i$, and $C$ has more than one debatable node except for $i$.
-Assuming node $i$ makes decision to stay in the claiming cluster $C$, afterwards one another debatable nodes $j$ decides its affiliation, and there is $j\in C\in S_i$.
-When $j$ leaves cluster $C$, which decrease cluster $C$'s cluster size, and could possibly trigger node $i$ to alter its previous decision to leave $C$, as $C$'s size is smaller now and leaving it may result in more increase of CCCs in $S_i$.
-At this point of time, debatable node $j$ may rejoin cluster $C$ due to the changes in $S_j$, then both node $i$ and $j$ face the \textit{same}\footnote{Actually it is not totally same as before, as there are some new changes within $S_j$.} situation again.
-%To maximize the increase of common channel in clusters in $S_j$, $j$ either stays in $C$, or leaves cluster $C$ and stay another cluster in $S_j$.
-%$j$'s decision changes $C$'s membership, which will affect $i$'s decision.
-%Assume $i$ makes decision before $j$ and chooses to stay in $C$, as which brings the most common channels in $i$' claiming clusters, and then it is $j$' turn to choose cluster.
-%If $j$ leaves $C$, the smaller cluster $C$ will possibly make $i$ to leave it and join another cluster.
-%and the choice of $j$ to stay in $C$ or not possibly changes $C$'s membership and  which potentially further triggers node $i$ to alter its previous decision. 
-Thence, we need to answer this concern before implementing ROSS-DGA.
-%, and if it converges, how good such a distributed scheme performs. 
+%
+%This procedure raises a concern that the debatable nodes may never stop changing their affiliations, because a debatable nodes' choice is based on the members of its claiming clusters, and the members are changed by other debatable nodes' choices.
+%In a word, debatable nodes' choices on cluster affiliation are dependent on each other, thus there could be an infinite chain effect in the process of membership clarification.
+%%  update their choices based on other debatable nodes' choices, and this process 
+%%%thesis needs1
+%For example, assuming one debatable node $i$ locates in cluster $C\in S_i$, and $C$ has more than one debatable node except for $i$.
+%Assuming node $i$ decides to stay in cluster $C$, then one another debatable nodes $j$ decides its affiliation, and there is $j\in C\in S_i$.
+%$j$'s move decreases cluster $C$'s size, and could possibly trigger node $i$ to alter its previous decision to leave $C$, as $C$'s size is smaller now and leaving it may result in more increase of CCCs in $S_i$.
+%At this point of time, debatable node $j$ may rejoin cluster $C$ due to the changes in $S_j$, then both node $i$ and $j$ face the \textit{same} situation again.
+%%\footnote{Actually it is not totally same as before, as there are some new changes within $S_j$.}
+%%To maximize the increase of common channel in clusters in $S_j$, $j$ either stays in $C$, or leaves cluster $C$ and stay another cluster in $S_j$.
+%%$j$'s decision changes $C$'s membership, which will affect $i$'s decision.
+%%Assume $i$ makes decision before $j$ and chooses to stay in $C$, as which brings the most common channels in $i$' claiming clusters, and then it is $j$' turn to choose cluster.
+%%If $j$ leaves $C$, the smaller cluster $C$ will possibly make $i$ to leave it and join another cluster.
+%%and the choice of $j$ to stay in $C$ or not possibly changes $C$'s membership and  which potentially further triggers node $i$ to alter its previous decision. 
+%Thence, we need to answer this concern before implementing ROSS-DGA.
+%%, and if it converges, how good such a distributed scheme performs. 
+%
 In the following we show that the process of membership clarification can be formulated into a game, and a equilibrium is reached after a finite number of best response updates made by the debatable nodes.
@@
 
-As to singleton congestion game, there exists a pure equilibria which can be reached with the best response update, and the upper bound of number of steps before convergence is $n^2*m$~\cite{Ackermann06purenash}, where $n$ is the number of players, and $m$ is the number of resources.
+As to singleton congestion game, there exists a pure equilibria which can be reached with the best response update, and the upper bound for the number of steps before convergence is $n^2*m$~\cite{Ackermann06purenash}, where $n$ is the number of players, and $m$ is the number of resources.
 In our problem, the players are the debatable nodes, and the resources are the claiming clusters.
@@
 In Figure \ref{AinC}, node $A$ staying in $C(C)$ and leaving $C(H)$ brings 2 more CCCs to $S_A$, which is more than that brought by another strategy showed in \ref{AinH}.
-After the decisions made similarly by the other debatable nodes $B$ and $D$, the final clusters are formed as shown in Figure~\ref{fig4}.
+After the decisions made similarly by the other debatable nodes $B$ and $D$, the final clusters are formed as shown in Figure~\ref{final_clustering_ross}.
 
@@
 The membership of $C_H$ is updated in the same time.
-Node B and D undertake the same process and the clusters are formed finally as Figure \ref{fig4} shows.
+Node B and D undertake the same process and the clusters are formed finally as Figure \ref{final_clustering_ross} shows.
 \end{comment}
@@
   \includegraphics[width=0.5\linewidth]{final_clustering_ross.pdf}
-  \caption{Final formation of clusters, CCCs for each cluster is shown. $K(C(C)),K(C(E)),K(C(H))$ are shown beside corresponding clusters.}
-  \label{fig4}
+  \caption{Final formation of clusters. $K(C(C)),K(C(E)),K(C(H))$ are shown beside corresponding clusters.}
+  \label{final_clustering_ross}
 \end{figure}
 
-\section{Centralized Clustering Scheme}
-\label{centralized_scheme}
-
-%paper given by james is useful which provides a survey from the perspective of wsn!
-
-%\todo[inline]{check}
-The centralized clustering scheme aims to form clusters with desired sizes, meanwhile the total number of CCCs of all clusters is maximized.
-In the following, we refer this problem as \textit{centralized clustering}, and give the formal problem definition.
-
-\begin{mydef}
-\label{def_centralized_clustering}
-\textit{Centralized clustering in CRN.}
-
-Given a cognitive radio network $\mathcal{N}$ where nodes are indexed from 1 to $N$ sequentially.
-Based on certain correlation, certain secondary users constitute one cluster $C$.
-$1\leq |C| \leqslant k$ where $|C|$ is the size of cluster $C$ and $k$ is a positive integer.
-We name the collection of such clusters as $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$, where $\mathcal{S}$ satisfies the following properties: $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$ and $K(C(i))\neq \emptyset$ for any $i$ which satisfies $1\leq i \leq |\mathcal{S}|$.
-
-%, which distinguishes the centralized clustering problem discussed in this paper.
-We give a new definition of the number of CCCs, where the number of common control channels is $|K(C)|$ if $|C|>1$, and is zero when $|C|=1$.
-We use $f(C)$ to denote the number of CCCs of a cluster $C$ in the new definition.
-
-The centralized clustering problem is to find a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, so that $\bigcup_{C_j\in \mathcal{S}'} C_j = N$, and $C_{j'}\cap C_j =\emptyset$ for $C_{j'}, C_j\in \mathcal{S}'$ and $j'\neq j$, so that $\sum_{C\in \mathcal{S}'} f(C)$ is maximized.
-% when $|C|>1$, and $f(\cdot)=0$ when $|C|=1$.
-%As to $f(\cdot):z\rightarrow z$, under this problem setting, if only number of common channels are given consideration, only singleton clusters will be preferred, which contradicts to our goal of clustering CR nodes together, thus we choose $f(\cdot)= |K_{C}|\cdot |C|$, the product of number of common channels and cluster size.
-The decision version of centralized clustering in CRN is to ask whether there exists a no-empty $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C\in \mathcal{S}'} f \geqslant \lambda$ where $\lambda$ is a real number.% in stead of to maximize $\sum_{C\in \mathcal{S}'} f$.
-\end{mydef}
-
-%The decision version of \textit{weighted exact cover problem}: 
-%Given an universe $U$, and collection $S=\{s_1, s_2, \ldots, s_m\}$ where each subset $s_i\subseteq U$ and is given a weight $w_i$, whether there exists a collection of subsets $\mathcal{C}$ and constant number $\lambda$, so that the union of $\mathcal{C}$ equals to $U$, $s_j\cap s_{j'} = \emptyset$ for different $j$ and $j'\in \{1,2,\ldots, m\}$, and $\sum_{i\in J} w_i \geq \lambda$.
-\subsection{Complexity of Clustering Problem}
-In this section we investigate the complexity of centralized clustering problem.
-Theorem~\ref{theorem1} tells centralized clustering problem in CRN is one NP-hard problem.
-
-\begin{theorem}
-\label{theorem1}
-CRN clustering problem is NP-hard, when the maximum size of clusters $k\geqslant 3$.
-%Assume a CRN can be represented by a connected graph, and there is at least one common channel between any pair of neighbours, then forming at least two CR nodes into one cluster is NP-complete.
-\end{theorem}
-The proof is in Appendix~\ref{proof_theorem1}.
-
-\subsection{Centralized Optimization}
-\label{centralized_opt}
-%Exact cover problem can be solved with Knuth's Algorithm X~\cite{dancingLinks_Knuth} as it finds out all the instances of exact cover, then we can choose the one with the biggest sum of weights. 
-As there is no efficient algorithm to solve clustering problem in CRN, we propose a centralized optimization where the objective function and the constraints are heuristic, then we adopt binary linear programming to solve the problem.
-%Note that binary linear programming is in NP-complete.
-
-%This example indicates the chose of $\mathcal{C}$ plays an important role on the resultant clustering strategy.
-%Meanwhile, it provide a chance to constrain the cluster size by putting groups with desired sizes into $\mathcal{C}$.
-
-%the maximum size of $S$ is the \textit{Bell number} of $N$, and $S$ contains the conditions cluster .
-%In this case, the resultant $\mathcal{C}$ is composed with all the singleton clusters, \ie, the cluster which contains one node, and the objective is -38.
-
-%it is possible that there doesn't exist combination of clusters with the same cluster size.
-%We thus list all possible clusters whose sizes are from 2 to one certain number \footnote{this number of decided by the density of CR network, along with the occupation of PUs.
-We set this number as cluster size of the biggest cluster ever appears when conducting distributed schemes.}, and check each combination of clusters to find the best covering of network on the aspect of number of ICCs per cluster.
-%The complexity of computation is thus \bigO$(N^\delta)$, $\delta$ is the preferred cluster size.
-
-%The global optimal clustering scheme with respect to the number of common channels is investigated to show the gap with the distributed schemes.
-
-%We apply this centralized scheme on a network with network size $N$ and cluster size $\delta$.
-%There is $N\mod \delta=0$, and the expected number of clusters is $C = N/\delta$.
-%These tailored parameters don't harm the validity of the performance gap between the two schemes.
-
-Given a CRN $\mathcal{N}$ and desired cluster size $\delta$, we obtain a collection of clusters $\mathcal{G}$ which contains all the \textit{legitimate} clusters, and the sizes of these clusters are $1,2,\ldots,\delta$.
-Legitimate clusters are the clusters which satisfy the conditions in Section~\ref{def_cluster}. 
-Note that the legitimate clusters include the singleton ones, so that we can guarantee the partition of any network is always feasible.
-
-With $N=|\mathcal{N}|, G=|\mathcal{G}|$, we construct a constant $G\times N$ matrix $Q_{G\text{x}N}$. 
-The element of matrix $Q$ is $q_{ij}$, where the subscript $i$ is the index of legitimate cluster, and $j$ is the node ID of one CR node.
-%Note that $C_i$ means $i$th cluster in the collection $\mathcal{G}$, doesn't denote the cluster where cluster head is $i$, this notation is only valid in this subsection.
-There are $i\in \{1,2,\cdots,G-1, G\}$, and $j\in \{1,2,\cdots,N-1, N\}$.
-Element $q_{ij}= |K(C_i)|$ if node $j\in C_i$, and $q_{ij}= 0$ if $j\notin C_i$.
-In other words, each non-zero element $q_{ij}$ denotes the number of CCCs of the cluster $i$ where node $j$ resides.
-
-\begin{figure}[ht!]
-\centering
-\bordermatrix{~ 		& 1 	& 2 	& 3 	& \cdots & j & \cdots	& N-1 	& N	\cr
-                  1 	& |K(C_1)| 	& |K(C_1)| 	& 0 	& \cdots & \cdots &\cdots	& 0 	& 0	\cr
-                  2 	& |K(C_2)| 	& 0 	& |K(C_2)| 	& \cdots & \cdots & \cdots 	& 0 	& 0	\cr
-				\vdots  	&\vdots & 	 	& 		&  \vdots		& 		& \vdots \cr
-				i 	& 0 	& |K(C_i)| 	& 0 	& \cdots  & \cdots & \cdots 	& |K(C_i)| 	& 0	\cr
-				\vdots  	&\vdots & 	 	& 		&  \vdots & \cdots & \cdots 		& 		& \vdots \cr
-				\vdots 	& \vdots  	& 0 	& 0 	& \cdots & \cdots & \cdots 	& |K(C_i')| 	& 0	\cr
-				G  	& |K(C_G)| & \cdots	 	& 		&  \vdots	& \cdots & \cdots& 		& \vdots \cr}	
-\caption{An example of Matrix $Q$, its rows correspond to all legitimate clusters, and columns correspond to the CR nodes in the CRN.}
-\label{xx}
-\end{figure}
-
-We build a $G\times N$ binary variable matrix $X$, which illustrates the clustering solution.
-The element of matrix $X$ is binary variable $x_{ij}, i=1, \ldots, G, j=1, \ldots, N$.
-%$x_{ij}=1$ denotes node $i$ is in the $j$th legitimate cluster, and the cluster is chosen in the solution, $x_{ij}=0$ means the $j$th legitimate cluster is not adopted by the partition.
-%Note that matrix $Q$ contains only constant elements, and matrix $X$ contains only binary variables.
-Now, we can formulate the optimization problem as follows,
-
-\begin{equation}
-\begin{aligned}
-     &\min\limits_{x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^G (-x_{ij}q_{ij} + (1-w_i)*p) \\
-     &\text{subject to}   && \Sigma_{i=1}^G x_{ij} = 1, for \forall j=1, \ldots, N \\
-   &&& \Sigma_{j=1}^N x_{ij} = |C_i|*(1-w_i), for \forall i=1, \ldots, G \\
-   &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
-   &&& i\in \{1,2, \cdots G\}, \hspace{0.3cm} j\in \{1,2,\cdots N\}
-\notag
-\end{aligned}
-\end{equation}
-
-The objective is a sum of two parts, the first part is the sum of products of cluster size and the corresponding number of CCCs, which is the sole metric adopted by the scheme SOC~\cite{Lazos09}.
-The second part is the \textit{punishment} for choosing the clusters whose sizes are not $\delta$.
-In fact, the second part is particularly designed to eliminates the drawbacks of SOC, \ie SOC produces a large number of singleton clusters and a few large clusters.
-In practical computation, we minimize the opposite of the first part, and the punishment is a positive value.
-%
-The first constraint restricts each node $j$ to reside in exactly one cluster.
-In the second constraint, $w_i$ is an auxiliary binary variable which denotes whether cluster $C_i$ is chosen by the solution, in particular, 
-$$
-w_i = \left\{ \begin{array}{rl}
-0 &\mbox{if $i$th legitimate cluster $C_i$ is chosen} \\
-1 &\mbox{if $i$th legitimate cluster $C_i$ is not chosen} \\
-\end{array} \right.
-$$
-The second constraint regulates when the $i$th legitimate cluster $C_i$ is chosen, the number of elements which are 1 in the $i$th row of the matrix $X$ is $|C_i|$.
-%
-Now we explain how does the mechanism of the punishment in the objective work. 
-The parameter $p$ is defined as follows,
-$$
-p = \left\{ \begin{array}{rl}
-0 &\mbox{ if $|C_i|=\delta$} \\
-\alpha_1 &\mbox{if $|C_i|=\delta-1$} \\
-\alpha_2 &\mbox{if $|C_i|=\delta-2$} \\
-\dots
-\end{array} \right.
-$$
-where $\alpha_i>0$ and increases when $|C_i|$ diverges from $\delta$.
-Because of $w_i$, any chosen cluster ($w=0$) brings certain \textit{punishment}.
-When the chosen cluster's size is desired size $\delta$, the punishment is zero.
-In contrary, when the chosen cluster's size diverges from $\delta$, the objective function suffers \textit{loss}.
-In particular, when $w_i=0$ and $|C_i|=1$, the punishment is the most severe.
-This design doesn't follow the definition of $f(C)$ in Definition~\ref{def_centralized_clustering} strictly, where $f(C_i)=0$ when $|C_i|=1$, but our design echoes the definition by exerting the most severe punishment on the singleton clusters in the clustering solution.
-Choice of $\alpha_i$ affects the resultant clusters.
-
-%\begin{figure}[ht!]
-%\centering
-%\includegraphics[width=0.45\linewidth]{example.JPG}
-%\caption{Example of Matrix Q in a 6-node network, cluster size is set as 2}
-%\label{xx}
-%\end{figure}
-
-%\begin{figure}[ht!]
-%  \centering
-%  \includegraphics[width=0.5\linewidth]{figure5final.pdf}
-%  \caption{Final cluster formation.}
-%  \label{fig4}
-%\end{figure}
-
-The optimization formulation is an integer linear optimization problem, which is solved by the function $bintprog$ provided in MATLAB.
-Note that the proposed centralized solution is heuristic.
-We reiterate the reasons for pursuing the heuristic scheme, first, the problem of centralized clustering is NP hard, and there is no efficient solution to solve it.
-The second reason is, the collection of legitimate clusters is dependant on the network topology and spectrum availability in the network, thus to each specific CRN, the space of solution is different.
-
-\subsubsection{Example of the Centralized Optimization}
-We look into how does the centralized scheme perform in the toy example of the CRN in Figure~\ref{fig1}.
-%
-We let the desired cluster size $\delta$ be 3.
+\subsection{Apply the Centralized and Comparison Distributed Schemes in the Example CRN}
+After introducing the resulted clusters from ROSS in Fig.~\ref{final_clustering_ross}, we apply the other robust clustering schemes in the same example CRN in Figure~\ref{fig1}.
+%We look into how does the centralized scheme perform in the toy example of the CRN in Figure~\ref{fig1}.
+%
+As to the centralized robust clustering scheme, we let the desired cluster size $\delta$ be 3.
 A collection of clusters $\mathcal{G}$ is obtained, which contains all the clusters satisfying the conditions of cluster in Section~\ref{def_cluster} and the sizes of clusters are 1, 2 or 3. 
 $\mathcal{G}=\{\{A\}, \{B\},\dots,\{B,C\},\{B,A\},\{B,H\},\cdots,\{B,A,C\},$\\$\{B,H,C\}, \{A,D,C\},\cdots\}$, and $G = |\mathcal{G}|=38$.
-
+%
 When $\alpha_1$ and $\alpha_1$ are set as 0.2 and 0.8, the formed clusters are shown in Fig.~\ref{fig:final_clustering_LP}.
 %$\{\{D,E,F\},\{A,C,G\},\{H,G\}\}$, the numbers of CCCs are 2, 3, 3.
-The resulted clustering solutions from ROSS-DGA/DFA and SOC are shown in Fig.~\ref{fig4} and Fig.~\ref{fig:final_clustering_soc} respectively.%, clusters are $\{A,B,C,D,G\},\{E,F\},\{H\}$, and the numbers of CCCs are 2, 3, 4.
+The resulted clustering solutions from SOC is shown in Fig.~\ref{fig:final_clustering_soc}.%, clusters are $\{A,B,C,D,G\},\{E,F\},\{H\}$, and the numbers of CCCs are 2, 3, 4.
 %The solution resulted from ROSS-DGA is $\{\{B,H,G\},\{C,A\},\{D,E,F\}\}$ (in Figure~\ref{fig4}), the numbers of CCCs are 2, 4, 2.
@@
 \label{performance}
-In this section, we evaluate the performances of all the variants of ROSS, \ie ROSS-DGA and ROSS-DFA, and that with cluster size control features.
-The latter is referred as ROSS-$\delta$-DGA/ROSS-$\delta$-DFA, where x is the desired cluster size.
-We choose SOC as comparison scheme.
-To the best of our knowledge, SOC~\cite{Lazos09} is the only work emphasizing on the robustness of clustering structure from all previous work on clustering in CRN. 
+%In this section, we evaluate the performances of ROSS.
+The schemes involved in the simulation are listed as follows,
+\begin{itemize}
+\item ROSS without size control, \ie ROSS-DGA and ROSS-DFA.
+\item ROSS-$\delta$-DGA and ROSS-$\delta$-DFA, which are the variants of ROSS with the size control feature.
+$\delta$ is the desired cluster size.
+\item SOC~\cite{Lazos09}, one distributed clustering scheme pursuing cluster robustness.
+To the best of our knowledge, SOC is the only work emphasizing on the robustness of clustering structure among the related works.
+\item Centralized robust clustering scheme. 
+The formulated optimization is an integer linear optimization problem, which is solved by the function $bintprog$ provided in MATLAB.
+\end{itemize}
 The authors of~\cite{Lazos09} compared SOC with other schemes in terms of the average number of CCCs of the formed cluster, on which SOC outperforms other schemes by 50\%-100\%. 
 SOC's comparison schemes are designed either for ad hoc network without consideration of channel availability~\cite{Basagni99}, or for CRN but just considering connection among CR nodes~\cite{Zhao07}.
-Hence, we only compare our proposed schemes with SOC  to show the ROSS's merits as a distributed scheme, and compare with the centralized scheme to examine the gap with the global optima.
-In particular, we investigate the following metrics.
+Thus SOC is chosen to be the only distributed scheme as comparison, besides, we also compare ROSS with the centralized scheme.
+%
+We investigate the schemes with the following metrics.
 
 \begin{itemize}
-\item \textit{Average number of CCCs per non-singleton cluster.}
-This metric shows the robustness of the current non-singleton clusters.
+\item \textbf{Average number of CCCs per non-singleton cluster.}
 Non-singleton cluster refers the cluster whose cluster size is larger than 1.
-SOC~\cite{Lazos09} compares the average number of CCCs per cluster without distinguishing singleton clusters, which is biased as singleton clusters don't contribute to the cluster structure.
+%This metric denotes the robustness of the formed non-singleton clusters.
+Comparing with the metric adopted by SOC~\cite{Lazos09}, which is the average number of CCCs per cluster without excluding the singleton clusters, this metric provides an more accurate description of the robustness of the non-singleton cluster.
+The larger number of CCCs per non-singleton clusters means these clusters have higher probability to survive when the primary users' operation becomes more intense.
+%which is biased as the singleton clusters (isolated CR users) don't get benefits from the cluster structure.
+Although this metric doesn't disclose the information about the CR nodes which are not included in any non-singleton clusters, we still examine this metric as the number of CCCs is involved in the utility which is adopted by all robust clustering schemes.
+%, thus it fails to give an overview of how many CR nodes can benefit from non-singleton clusters.
+
 %the CR nodes with more channels could be formulated as singleton clusters.
@@
 
-\item \textit{Number of singleton clusters.}
-This is a straight forward metric which reflects the effectiveness of clustering scheme.
-The less resulted singleton clusters means more secondary users are benefited from cluster structure.
+\item \textbf{Cluster sizes.}
+%Specific clusters size is pursued in many applications due to energy preservation and the system design ~\cite{clustering_globecom11}.
+The distribution of CRs residing in the formed clusters with different sizes is presented.
+
+\item \textbf{Robustness of the clusters against newly added PUs.}
+We increase the number of PUs to challenge the clusters, and count the number of \textit{unclustered} CR nodes which are the CR nodes which are not included in any non-singleton clusters.
+This metric indicates the robustness of clusters from a more practical point of view, \ie as to the clusters formed for a given CRN and spectrum availability, how many CR nodes can still make use of the clusters when the spectrum availability decreases.
 %robustness of clusters, as this metric directly shows how many nodes can make use of the cluster structure.
-When we investigate the performance with moderate and vigorous intensity of primary users' activities, this metric is the antonym of \textit{survival rate}, \ie, the percentage of nodes which are still within certain clusters.
+%When we investigate the performance with moderate and vigorous intensity of primary users' activities, 
+%All the robust clustering schemes are proposed for a given CRN, when the available spectrum becomes scarce when the primary users' operation becomes more intense, the metric can illustrate the robustness of clusters by showing the unclustered CR nodes.
+%This metric is closely related with cluster robustness, \ie the less CR nodes which are not  nodes means more CR nodes are included into non-singleton clusters which survive the primary users' influence.
 %When we vary the intensity of primary users' activity, \eg from low to medium level by increasing the number of primary users, 
-
-\item \textit{Cluster sizes.}
-Specific clusters size is pursued in many applications due to energy preservation and the system design ~\cite{clustering_globecom11}.
-We will present the distribution of CRs residing in the formed clusters with different sizes.
-
-\item \textit{Amount of control messages involved.}
+%The drawback of this metric is, it doesn't indicate the robustness of the non-singleton clusters when the primary users conquer more spectrum.
+
+\item \textbf{Amount of control messages involved.}
 We investigate the number of control messages involved in the clustering process.
@@
 
-The simulation is written in C++. 
-Certain number of CRs and PUs are deployed on a two-dimensional Euclidean plane.
-%Complying with the system model, the CR node residing within another CR node's transmission range is seen as neighbour of that CR node.
-The number of licensed channels is 10, each PU is operating on each channel with probability of 50\%.
-All primary and CR users are assumed to be static during the process of clustering.
-%
 Simulation consists of two parts, in the first part, we investigate the performance of centralized scheme, and the gap between the distributed schemes and the centralized scheme.
@@
 
+We give a brief introduction to the settings which are common for both simulation parts.
+CRs and PUs are deployed on a two-dimensional Euclidean plane.
+%Complying with the system model, the CR node residing within another CR node's transmission range is seen as neighbour of that CR node.
+The number of licensed channels is 10, each PU is operating on each channel with probability of 50\%.
+CR users are assumed to be able to sense the existence of primary users and identify available channels.
+All primary and CR users are assumed to be static during the process of clustering.
+The simulation is written in C++, and the performance results are averaged over 50 randomly generated topologies, and the confidence interval corresponds to 95\% confidence level.
+
 \subsection{Centralized Schemes vs. Decentralized Schemes}
-10 primary users and 20 CR users are dropped randomly (with uniform distribution) within a square area of size $A^{2}$, where we set the transmission ranges of primary and CR users to $A/3$.
+There are 10 primary users and 20 CR users are dropped randomly (with uniform distribution) within a square area of size $A^{2}$, where we set the transmission ranges of primary and CR users to $A/3$.
 %There are 10 available channels. 
-With this setting, the average number of neighbours of one CR user is 4.8.
+%With this setting, the average number of neighbours of one CR user is 4.8.
 %Each primary user randomly occupies one channel, and 
-CR users are assumed to be able to sense the existence of primary users and identify available channels.
 When clustering scheme is executed, around 7 channels are available on each CR node.
-
 The desired cluster size $\delta$ is 3, the parameters used in the \textit{punishment} for choosing the clusters with undesired sizes are set as follows, $\alpha_1 =  0.4$, $\alpha_2 =  0.6$.
-Performance results are averaged over 50 randomly generated topologies, and the confidence interval corresponds to 95\% confidence level.
 
@@
 %We first have a look at the average number of common channels per non-singleton cluster.
-Figure~\ref{ccc_per_nonsingleton} shows the average number of the CCCs of non-singleton clusters,
+% shows the average number of the CCCs of non-singleton clusters,
 %as the singleton clusters (in other words unclustered nodes) don't execute any functionalities of clusters, which are has be discussed in Section~\ref{intro}.
-from which we can see the centralized schemes outperform the distributed schemes.
-As to the distributed schemes, SOC achieves the largest number of CCCs than all the variants of ROSS.
+From Figure~\ref{ccc_per_nonsingleton}, we can see the centralized schemes outperform the distributed schemes.
+As to the distributed schemes, SOC achieves the best than all the variants of ROSS.
 The reason is, SOC is liable to group the neighbouring CRs which share the most abundant spectrum together, no matter how many of them are, thus the number of CCC of the formed clusters is higher.
-But this method leaves considerable number of CRs to form singleton clusters.
-
-As to the variants of ROSS, greedy mechanism increases CCCs in non-singleton clusters significantly.
+We have discussed the flaw of this metric as it doesn't convey the number of unclustered CR nodes, in fact, SOC generates the most unclustered CRs, which can be seen when we discuss the performance on the number of unclustered CR nodes.
+As to the variants of ROSS, we notice that the greedy mechanism increases CCCs in non-singleton clusters significantly.
 %, this is due to the procedure that debatable nodes greedily look for better affiliation to improve the number of CCCs.
-We also notice that the size control feature doesn't affect the number of CCCs for both ROSS-DGA and ROSS-DFA.
-Size control mechanism converts the large clusters into small ones, but meanwhile clusters with the desired sizes have to be made when forming smaller clusters is possible.
+%We also notice that the size control feature doesn't affect the number of CCCs for both ROSS-DGA and ROSS-DFA.
+%Size control mechanism converts the large clusters into small ones, but meanwhile clusters with the desired sizes have to be made when forming smaller clusters is possible.
 %, which can also be observed in the large scale CRN in Section~\ref{largeScaleCRN}.
@@
 
-\subsubsection{Number of Singleton Clusters}
-%When the number of PUs in CRN increases, or their operation becomes more intensive, some clusters don't seize any CCCs any more, so that the cluster members and the cluster heads become unclustered, or singleton clusters.
-%If there is no common control channels available any more because of the new added PRs, the cluster is regarded as destroyed and the former cluster member CRs become unclustered CRs or in other words singleton clusters.
-%We investigate the number of singleton clusters with primary users whose intensity of activities are varying.
-Initially, clusters are formed with the presence of 10 PUs. 
-Afterwards, extra 20 batches of PUs are added to the network sequentially, and each batch includes 5 PUs. 
-%The transmission range and channel occupancy of the new PU is the same with the previous ones, \ie transmission range is $A/3$, and one channel out of 10 is randomly chosen to operate.
-Figure~\ref{singleton_clusters} shows the number of unclustered CRs with the increasing number of PUs, from which two conclusions are drawn.
-%, which indicates the vulnerability of clusters under varying availability of licensed spectrum.
-%
-
-\begin{itemize}
-\item The centralized scheme with desired size of two generates the most robust clusters, and SOC results in the most vulnerable clusters.
-The centralized scheme with desired size of 3 doesn't surpass the variants of ROSS.
-The reason lies in the the uniformly sized clusters, whereas the variants of ROSS generate considerable amount of smaller clusters which are more likely to survive when PUs' activities become intense.
-%The comparison on cluster sizes will be given in Section~\ref{cluster_size}.
-% when the number of PRs is 10$\sim$30, when number of PUs is 30$\sim$60, same amount of unclustered CRs are generated with variants of ROSS.
-%When there are 75 and more new PRs, centralized scheme with cluster size of 3 results in more unclustered CR nodes than variants of ROSS.
-
-ROSS with size control distinguishes itself as the size control avoid the appearance of the clusters with large size.
-
-\item Greedy algorithm improves the survival rate. 
-Greedy strategy adopted in the second phase of ROSS improves the robustness of clusters, i.e. ROSS-DGA exceeds ROSS-DFA, and ROSS-$\delta$-DGA surpasses ROSS-$\delta$-DFA.
-When the debatable CRs greedily update their affiliations, one of the metrics is the maximum increase of CCCs of the demanding clusters. 
-This observation complies with the result shown in Figure~\ref{ccc_per_nonsingleton}.
-
-%Meanwhile, sizes of more clusters become smaller also contributes more robustness.
-
-\end{itemize}
-
-%\begin{figure}[h!]
-%  \centering
-%  \includegraphics[width=0.8\linewidth]{ccc_20.pdf}
-%  \caption{Number of common channels for non-singleton clusters, the numbers in the names of schemes annotate the desired cluster size.}
-%  \label{ccc_per_nonsingleton}
-%\end{figure}
-%
-%
-%\begin{figure}[h]
-%  \centering
-%  \includegraphics[width=0.8\linewidth]{survival_rate_20.pdf}
-%  \caption{Number of CRs which are not included in any clusters}
-%  \label{singleton_clusters}
-%\end{figure}
+\begin{figure*}[th]
+\begin{multicols}{3}
+    \includegraphics[width=\linewidth]{ccc_20.pdf}\par\caption{Number of common channels of non-singleton clusters}\label{ccc_per_nonsingleton}
+    \includegraphics[width=\linewidth]{cdf_clusterSize_20.pdf}\par\caption{Cumulative distribution of CRs residing in clusters with different sizes}\label{size_control}    
+    \includegraphics[width=\linewidth]{survival_rate_20.pdf}\par\caption{Number of unclustered CRs with decreasing spectrum availability}\label{singleton_clusters}
+\end{multicols}
+\caption{Comparison between the distributed and centralized clustering schemes ($N$ = 20)}
+\label{compare_dis_centralized}
+\end{figure*}
 
@@
 
-\begin{figure*}[th]
-\begin{multicols}{3}
-    \includegraphics[width=\linewidth]{ccc_20.pdf}\par\caption{Number of common channels for non-singleton clusters}\label{ccc_per_nonsingleton}
-    \includegraphics[width=\linewidth]{survival_rate_20.pdf}\par\caption{Number of CRs which are not included in any clusters}\label{singleton_clusters}
-    \includegraphics[width=\linewidth]{cdf_clusterSize_20.pdf}\par\caption{Cumulative distribution of CRs residing in clusters with different sizes}\label{size_control}
-\end{multicols}
-\caption{Comparison between the distributed and centralized clustering schemes in a small network ($N$ = 20)}
-\label{compare_dis_centralized}
-\end{figure*}
-
-Figure~\ref{size_control} depicts the empirical cumulative distribution of the CRs residing in certain sized clusters which are generated in 50 runs.
-The centralized schemes form clusters which satisfy the requirement on cluster size strictly.
+Figure~\ref{size_control} depicts the empirical cumulative distribution of the CRs residing in certain sized clusters, from which we have two conclusions.
+The first, SOC generates more unclustered CR nodes than other schemes.
+The centralized schemes produce no unclustered CR nodes, ROSS-DGA/DFA generate 3\% unclustered nodes, as comparison, 10\% of nodes are unclustered when applying SOC.
+ROSS-DGA and ROSS-DFA with size control feature generate 5\%-8\% unclustered CR nodes, which is due to the cluster pruning procedure (discussed in section~\ref{cluster_pruning}).
+Second, the centralized schemes and cluster size control mechanism of RPSS generate clusters which satisfy the requirement on cluster size strictly.
 %When the desired size is 2, each generated cluster has two members, whereas when the desired size is 3, about 15\% CRs are formed into 2 node clusters.
-As to ROSS-DFG and ROSS-DFA with size control mechanism, CR nodes averagely distributes in clusters whose sizes are 2, 3 and 4.
+As to ROSS-DFG and ROSS-DFA with size control feature, CR nodes reside averagely in clusters whose sizes are 2, 3 and 4.
 %When ROSS-3-DFA is applied, most number of CRs are in 3 node clusters, nevertheless, slightly less nodes are found in 2 node and 4 node clusters, there are also considerable number of singleton clusters.
 %ROSS-3-DGA decreases the clusters sizes and results in more 2 node clusters, the second most CRs are found in 3 node clusters.
-The sizes of clusters resulted from ROSS-DGA and ROSS-DFA are disperse, but appear to be better than SOC, i.e., the 50\% percentiles for ROSS-DGA, ROSS-DFA and SOC is 4.5, 5, and 5.5, and the 90\% percentiles for the three schemes are 8, 8, and 9.
+The sizes of clusters resulted from ROSS-DGA and ROSS-DFA are disperse, but appear to be better than SOC, i.e., the 50\% percentiles for ROSS-DGA, ROSS-DFA and SOC are 4.5, 5, and 5.5, and the 90\% percentiles for the three schemes are 8, 8, and 9.
 %Figure~\ref{size_control} shows distributed clustering schemes are not able to control cluster sizes perfectly, but ROSS-DGA and ROSS-DFA eliminate the clusters whose size diverges largely with the desired one, \ie single node clusters and clusters with size of 13 and 14.
 
-Note ROSS-DGA and ROSS-DFA with size control feature generate 10\%-20\% singleton clusters, which is due to the cluster pruning discussed in section~\ref{cluster_pruning}, whereas, without size control, only 3\% nodes are in singleton clusters.
-When applying SOC, 10\% of nodes are in singleton clusters.
+\subsubsection{Robustness of the clusters against newly added PUs}
+%When the number of PUs in CRN increases, or their operation becomes more intensive, some clusters don't seize any CCCs any more, so that the cluster members and the cluster heads become unclustered, or singleton clusters.
+%If there is no common control channels available any more because of the new added PRs, the cluster is regarded as destroyed and the former cluster member CRs become unclustered CRs or in other words singleton clusters.
+%We investigate the number of singleton clusters with primary users whose intensity of activities are varying.
+%We will obtain two observations by examining this metric.
+%First, we will know how many CR nodes are unclusterred by applying the robust clustering schemes in a given CRN.
+We add PUs in the CRN to decrease the available spectrum, and observe the number of unclustered CR nodes.
+Clusters are formed with the presence of 10 PUs in the beginning, then extra 20 batches of PUs are added sequentially, where each batch includes 5 PUs. 
+%The transmission range and channel occupancy of the new PU is the same with the previous ones, \ie transmission range is $A/3$, and one channel out of 10 is randomly chosen to operate.
+
+Figure~\ref{singleton_clusters} shows with the increase of PUs, certain clusters disappear and the number of unclustered CR nodes increases.
+Among the robust clustering schemes, the centralized scheme with desired size of two generates the most robust clusters, meanwhile, SOC results in the most vulnerable clusters.
+The centralized scheme with desired size of three doesn't outperform the variants of ROSS, because the centralized scheme peruses clusters with size of 3 at the expenses of sanctifying CCCs.
+In contrary, the variants of ROSS generate some smaller clusters which are more likely to survive when PUs' activities become intense.
+%The comparison on cluster sizes will be given in Section~\ref{cluster_size}.
+% when the number of PRs is 10$\sim$30, when number of PUs is 30$\sim$60, same amount of unclustered CRs are generated with variants of ROSS.
+%When there are 75 and more new PRs, centralized scheme with cluster size of 3 results in more unclustered CR nodes than variants of ROSS.
+%ROSS with size control distinguishes itself as the size control avoid the appearance of the clusters with large size.
+
+%As to the variants of ROSS, the greedy process in ROSS improves the performance.
+
+%Greedy strategy adopted in the second phase of ROSS improves the robustness of clusters, i.e. ROSS-DGA exceeds ROSS-DFA, and ROSS-$\delta$-DGA surpasses ROSS-$\delta$-DFA.
+%When the debatable CRs greedily update their affiliations, one of the metrics is the maximum increase of CCCs of the demanding clusters. 
+%This observation complies with the result shown in Figure~\ref{ccc_per_nonsingleton}.
+%Meanwhile, sizes of more clusters become smaller also contributes more robustness.
+
+%\begin{figure}[h!]
+%  \centering
+%  \includegraphics[width=0.8\linewidth]{ccc_20.pdf}
+%  \caption{Number of common channels for non-singleton clusters, the numbers in the names of schemes annotate the desired cluster size.}
+%  \label{ccc_per_nonsingleton}
+%\end{figure}
+%
+%
+%\begin{figure}[h]
+%  \centering
+%  \includegraphics[width=0.8\linewidth]{survival_rate_20.pdf}
+%  \caption{Number of CRs which are not included in any clusters}
+%  \label{singleton_clusters}
+%\end{figure}
 
@@
 
-In this section we compare the amount of control messages involved in different clustering schemes, \ie centralized scheme, ROC, and the variants of ROSS.
+In this section we compare the overhead of signalling involved in different clustering schemes.
 %In order to highlight the amount of control signalling only for clustering, 
-We omit the control messaged involved in the process of neighbourhood discovery, which is the premise for any clustering scheme.
+We omit the control messaged involved in neighbourhood discovery, which is the premise for any clustering scheme.
 According to~\cite{complexity_aggregation_2011}, the message complexity is defined as the number of messages used by all nodes.
-To have the same criterion to compare the overhead of signalling, we count \textit{the number of transmissions of control messages}, without distinguishing they are sent with broadcast or unicast.
+To have the same criterion to compare, we count \textit{the number of transmissions of control messages}, without distinguishing they are sent with broadcast or unicast.
 This metric is synonymous with \textit{the number of updates} discussed in Section~\ref{ross}.
@@
 The second phase is broadcasting, where the clustering solution is disseminated to every CR node.
-
+%
 We adopt the algorithm proposed in~\cite{Efficient_broadcasting_gathering_adhoc} to broadcast and gather information as the algorithm is simple and self-stabilizing.
-This scheme needs building a backbone structure to support the communication, we use our generated cluster heads as the backbone and the debatable nodes as the gateway nodes between the backbone nodes.
-As the backbone is built once and can support transmission for multiple times, the messages involved in the clustering process are not counted.
+This scheme needs building a backbone structure to support the communication, and we apply ROSS to generate cluster heads which serve as the backbone, besides, the debatable nodes as used as the gateway nodes between the backbone nodes.
+As the backbone is built once and support transmission for multiple times, the messages involved in the clustering process are not counted.
 As to the process of information gathering, we assume that every cluster member sends the spectrum availability and its ID to its cluster head, which further forwards or the message to the controller, thus the number of transmission is $N$.
-As to the process of dissemination, in an extreme situation where all the gateway and the backbone nodes broadcast, the number of transmission will be $h + m$, where $h$ is the number of cluster heads, $m$ is number of debatable nodes, $d$ is the average number of demanding clusters for each debatable node.
+As to the process of dissemination, in an extreme situation where all the gateway and the backbone nodes broadcast, the number of transmission is $h + m$, where $h$ is the number of cluster heads and $m$ is number of debatable nodes.
+%, $d$ is the average number of demanding clusters for each debatable node.
 
@@
   \centering
-  \includegraphics[width=0.7\linewidth]{percentage_overlapping_node.pdf}
+  \includegraphics[width=0.6\linewidth]{percentage_overlapping_node.pdf}
   \caption{The percentage of debatable nodes after phase I of ROSS.}\label{percentage_overlapping_node}
 \end{figure}
-
+%
 %As we adopt a simplified communication model, node's transmission is not influenced by collision or interference, 
 %Our simulation doesn't consider the behaviour in the physical layer, 
-
+%
+%
 %Assume we use OSPF~\cite{BCJ10} to aggregate and disseminate information, then the best and worst complexity for is $\mathcal{O}(E)$, where $E$ is the number of edges in the graph which corresponds to the network.
@@
 %Thus the best message complexity of the centralized scheme is $\mathcal{O}{(N)}$ and the worst is $\mathcal{O}{(N^2)}$.
-
+%
 %1. update membership to form X1, 
@@
 %3. broadcast X3
-
 %The complexity parameters are the number of nodes $n$ in network, number of clusters $h$.
@@
 \begin{table*}[!htb]
-\caption{Singalling overhead}\label{tab_overhead}
+\caption{Signalling overhead}\label{tab_overhead}
 {\small
@@
   \centering
-  \includegraphics[width=0.7\linewidth]{number_controlMsg.pdf}
-  \caption{Number of control messages. Note the curves for ROSS-DGA and ROSS-DFA are the upper bounds of the number of messages, the curve of centralized scheme reflects an extreme situation.}
+  \includegraphics[width=0.6\linewidth]{number_controlMsg.pdf}
+  \caption{Number of control messages. Note the curves of ROSS-DGA and ROSS-DFA are the upper bounds}
   \label{control_msg}
@@
 In this section we investigate the performances of distributed clustering schemes in CRN with different network scales and densities.
-The transmission range of CR is $A/10$, PR's transmission range is $A/5$.
+The transmission range of CR is $A/5$, PR's transmission range is $2A/5$.
 The initial number of PU is 30.
 %The number of CR is 100, 200 and 300, and the average number of neighbours of each CR is 9.5, 20, and 31.
-The desired sizes adopted are listed in the Table~\ref{Simulation_para}.
+The desired sizes adopted are listed in the Table~\ref{Simulation_para}, which is about 60\% of the average number of neighbours.
 
@@
   \centering
-  \includegraphics[width=.8\linewidth]{ccc_large_scale_color.pdf}
+  \includegraphics[width=.7\linewidth]{ccc_large_scale_color.pdf}
   \caption{Number of common channels of non-singleton clusters.}
@@
 
-Figure~\ref{ccc_large_scale} illustrates the average number of CCCs of the non-singleton clusters.
-When $N=100$, variants of ROSS have 30\% less CCCs than SOC, but this gap is decreased significantly when $N$ is 200 and 300, \ie when $N=300$, the number of CCCs achieved by ROSS variants (except for ROSS-$\delta$-DFA) is almost the same as that resulted from SOC.
-This means SOC out performs in terms of the average number of CCCs per non-singleton cluster when network is sparse.
-
-this is also observed in the evaluation in Section \ref{ccc_20} where $N=20$.
-When the network becomes denser, even this metric favours SOC as discussed in the beginning of Section~\ref{performance}, ROSS-DGA achieves even more CCCs than SOC, and ROSS-DFA and ROSS-$\delta$-DGA increase the number of CCCs visibly.
-
-\subsubsection{Number of Singleton Clusters}
-
+Figure~\ref{ccc_large_scale} shows the average number of CCCs of the non-singleton clusters.
+We notice that SOC achieves the most CCCs per non-singleton cluster, although the lead over the variants of ROSS shrinks significantly when $N$ increases.
+%\ie when $N=300$, the number of CCCs achieved by ROSS variants (except for ROSS-$\delta$-DFA) is almost the same as that resulted from SOC.
+%This means SOC out performs in terms of the average number of CCCs per non-singleton cluster when network is sparse.
+%This is also observed in the evaluation in Section \ref{ccc_20} where $N=20$.
+%When the network becomes denser, even this metric favours SOC as discussed in the beginning of Section~\ref{performance}, ROSS-DGA achieves even more CCCs than SOC, and ROSS-DFA and ROSS-$\delta$-DGA increase the number of CCCs visibly.
+
+\subsubsection{Robustness of the clusters against newly added PUs}
+We add extra 20 batches of PUs sequentially in the CRN, where each batch includes 10 PUs. 
 %In this part of simulation, we investigate the robustness of clusters by increasing the PUs working on certain channels.
-
-Figure~\ref{singleton_clusters_100} illustrates the increasing trend of singleton clusters with the increase of PUs, when $N=100$.
-SOC generates around 10 more singleton clusters than the variants of ROSS, which accounts for 10\% of the total CR nodes.
+Figure~\ref{singleton_clusters_100} and \ref{singleton_clusters_200} show that when $N=100$ and 200, more unclustered CR nodes appear in the CRN where SOC is applied.
+When the network becomes denser, ROSS-DGA/DFA generate slightly more unclustered CR nodes than SOC when new PUs are not many, but SOC's performance deteriorates quickly when the number of PUs becomes larger.
 We only show the average values of the variants of ROSS as their confidence intervals overlap.
+%
+When applying ROSS with size control mechanism, significantly less unclustered CR nodes are generated.
+Besides, the greedy mechanism moderately strengthens the robustness of the clusters.
 %It can be seen that greedy algorithms result in slightly less singleton clusters than their counterparts.
 %
-Figure ~\ref{singleton_clusters_300} depicts a denser CRN where $N=300$.
-SOC noticeably causes more singleton clusters than ROSS variants, except that ROSS-20-DFA results in more singleton clusters when PUs are few.
-The reason is ROSS-20-DFA conducts cluster membership clarification for only once, which causes large number of singleton clusters.
-ROSS-20-DGA increases the size of smaller clusters through debatable nodes' repeated updates thus drastically decreases the number of singleton clusters.
+%Figure ~\ref{singleton_clusters_300} depicts a denser CRN where $N=300$.
+%SOC noticeably causes more singleton clusters than ROSS variants, except that ROSS-20-DFA results in more singleton clusters when PUs are few.
+%The reason is ROSS-20-DFA conducts cluster membership clarification for only once, which causes large number of singleton clusters.
+%ROSS-20-DGA increases the size of smaller clusters through debatable nodes' repeated updates thus drastically decreases the number of singleton clusters.
+%\begin{figure}[!h]
+%  \centering
+%  \includegraphics[width=0.7\linewidth]{survival_rate_100_edge50.pdf}
+%  \caption{Percentage of CRs which are not included in any clusters with the increasing number of primary users, $N=100$}
+%  \label{singleton_clusters_100}
+%\end{figure}
+%  
+%  \begin{figure}[!h]
+%    \centering
+%   \includegraphics[width=0.7\linewidth]{survival_rate_300_edge50.pdf}
+%  \caption{Percentage of CRs which are not included in any clusters with the increasing number of primary users, $N=300$}
+%  \label{singleton_clusters_300}
+%\end{figure}
+
+\begin{figure*}[t]
+\begin{multicols}{3}
+    \includegraphics[width=\linewidth]{survival_rate_100_edge50.pdf}\par\caption{100 CRs}\label{singleton_clusters_100}
+    \includegraphics[width=\linewidth]{survival_rate_200_edge50.pdf}\par\caption{200 CRs}\label{singleton_clusters_200}
+    \includegraphics[width=\linewidth]{survival_rate_300_edge50.pdf}\par\caption{300 CRs}\label{singleton_clusters_300}
+\end{multicols}\caption{Percentage of CR nodes which are not included in any non-singleton clusters}
+\label{unclustered_100_200_300}
+\end{figure*}
+
+%When the network is denser, the improvement on cluster sizes and robustness by the greedy search in the membership clarification phase is more obvious.
+
+\begin{figure*}[t]
+\begin{multicols}{3}
+    \includegraphics[width=\linewidth]{cdf_clusterSize_100.pdf}\par\caption{100 CRs, 30 PUs in network}\label{cdf_clusterSize_100}
+    \includegraphics[width=\linewidth]{cdf_clusterSize_200.pdf}\par\caption{200 CRs, 30 PUs in network}\label{cdf_clusterSize_200}
+    \includegraphics[width=\linewidth]{cdf_clusterSize_300.pdf}\par\caption{300 CRs, 30 PUs in network}\label{cdf_clusterSize_300}
+\end{multicols}
+\caption{Cumulative distribution of CRs residing in clusters with different sizes}
+\label{cdf_100_200_300}
+\end{figure*}
+
+\subsubsection{Cluster Size Control}
+Figure~\ref{nClusters_largeNetwork} shows when the network density scales up, the number of formed clusters by ROSS increases by smaller margin, and that generated by SOC increases linearly.
+This result coincides with the analysis in Section~\ref{cluster_pruning}.
+%When the network becomes denser, more clusters are generated by SOC compared with ROSS variants.
+To better understand the distribution of the sizes of formed clusters, we depict the empirical cumulative distribution of CR nodes which reside in clusters with certain sizes in CRNs in Figures~\ref{cdf_clusterSize_100}~\ref{cdf_clusterSize_200}~\ref{cdf_clusterSize_300}.
+
+%In this group of evaluation, the number of PRs is 30.
 
@@
   \centering
-  \includegraphics[width=0.7\linewidth]{survival_rate_100.pdf}
-  \caption{Percentage of CRs which are not included in any clusters with the increasing number of primary users, $N=100$}
-  \label{singleton_clusters_100}
-\end{figure}
-
-  \begin{figure}[!h]
-    \centering
-   \includegraphics[width=0.7\linewidth]{survival_rate_300.pdf}
-  \caption{Percentage of CRs which are not included in any clusters with the increasing number of primary users, $N=300$}
-  \label{singleton_clusters_300}
-\end{figure}
-
-From the Figure~\ref{singleton_clusters_100} and \ref{singleton_clusters_300}, we can conclude that the clusters obtained from the variants of ROSS are more robust than SOC.
-Besides, the greedy mechanism moderately strengthens the robustness of the clusters.
-%When the network is denser, the improvement on cluster sizes and robustness by the greedy search in the membership clarification phase is more obvious.
-
-\subsubsection{Cluster Size Control}
-As Fig.~\ref{nClusters_largeNetwork} shows, when the network scales up, the number of formed clusters by ROSS increases by smaller margin.
-This result coincides with the analysis in Section~\ref{cluster_pruning}, that the number of formed clusters saturates when the network scales.
-When the network becomes denser, more clusters are generated by SOC compared with ROSS variants.
-To better understand the distribution of the sizes of formed clusters, we depict the cluster sizes with cumulative distribution.
-%In this group of evaluation, the number of PRs is 30.
-
-\begin{figure}[!h]
-  \centering
-   \includegraphics[width=0.85\linewidth]{nClusters_largeNetwork.pdf}
+   \includegraphics[width=0.7\linewidth]{nClusters_largeNetwork.pdf}
   \caption{The number of formed clusters.}
@@
 
-Figures~\ref{cdf_clusterSize_100}~\ref{cdf_clusterSize_200}~\ref{cdf_clusterSize_300} illustrate the empirical cumulative distribution of CR nodes which reside in clusters with certain sizes in CRNs with different densities.
+The sizes of clusters generated by ROSS-DGA and ROSS-DFA span a wider range than ROSS with size control feature.
+Most of the generated clusters are smaller than the average number of neighbours, which is roughly equal with the 95\% percentile of the ROSS-DGA curve.
+The 50\% percentile of the ROSS-DGA curve is roughly the desired size $\delta$.
+%
 %The desired cluster sizes are 5, 8 and 13, which are around 45\% of the average number of neighbours in respective CRNs. 
-When the variants of ROSS with size control feature are applied, the sizes of the most generated clusters are below $\delta$, and most of them are around the 50\% percentile.
+When the variants of ROSS with size control feature are applied, the sizes of the most generated clusters are smaller than $\delta$.
 %This means the size control feature effectively restricts the size of clusters, which is able to prevent the clusters from ungovernable growing with the increase of network density.
-The sizes of clusters generated by ROSS-DGA and ROSS-DFA span a wider range than that with feature control feature.
-We find that average number of neighbours is roughly equal with the 95\% percentile of the ROSS-DGA curve.
 %But the range where most of the CRs (80\% which exclude the CR nodes residing in small and big clusters) resides centres a value, which is roughly the half of the average number of neighbours.
-As to SOC, the 95\% percentiles are 36, 30, and 40.
-Overviewing the three Figures, we can see ROSS-DGA and ROSS-DFA show similar behaviour on cluster sizes.
+As to the curves of SOC, the 95\% percentiles are 36, 30, and 40 in respective networks.
+
+Overviewing Figure~\ref{cdf_100_200_300}, we conclude that the sizes of the clusters generated by ROSS are limited by the network density, the sizes of the clusters formed by ROSS with size control feature are restricted by the desired size.
 In contrary, the clusters generated from SOC demonstrate strong divergence on cluster sizes.
 
-\begin{figure*}[t]
-\begin{multicols}{3}
-    \includegraphics[width=\linewidth]{cdf_clusterSize_100.pdf}\par\caption{100 CRs, 30 PRs in network}\label{cdf_clusterSize_100}
-    \includegraphics[width=\linewidth]{cdf_clusterSize_200.pdf}\par\caption{200 CRs, 30 PRs in network}\label{cdf_clusterSize_200}
-    \includegraphics[width=\linewidth]{cdf_clusterSize_300.pdf}\par\caption{300 CRs, 30 PRs in network}\label{cdf_clusterSize_300}
-\end{multicols}
-\caption{Cumulative distribution of CRs residing in clusters with different sizes}
-\label{cdf_100_200_300}
-\end{figure*}
+\subsection{Insights from the Simulation}
+The centralized clustering scheme can form the clusters which satisfy the requirement on cluster size strictly, and the clusters are robust against the newly added PUs, besides, it generates the smallest control overhead in the process of cluster formation.
+
+As distributed schemes, ROSS outperform the comparison scheme SOC considerately on three metrics.
+ROSS generates much less singleton clusters than SOC, and the resulted clusters are robuster than SOC in front of newly added PUs.
+The signalling overhead involved in ROSS is about half of that needed for SOC, and the signalling messages are much shorter that the latter.
+The sizes of the clusters which are generated by ROSS are restricted by the network density, which demonstrate smaller discrepancy than that of SOC.
+%
+Besides, ROSS achieves similar performance to the centralized scheme, \ie the cluster sizes obtained by ROSS with size control feature are limited by the desired size, and the cluster robustness is similar when applying the variants of ROSS and the centralized scheme respectively.
+As to the variants of ROSS, the greedy mechanism in ROSS-DGA helps to improve the performance on cluster size and cluster robustness at the cost of mildly increased signalling overhead.
+
+We also notice that the metric that the number of CCCs per non-singleton cluster doesn't indicate the robustness of clusters as shown in Figure~\ref{singleton_clusters} and \ref{unclustered_100_200_300}, although it is adopted as the metric in the formation of clusters.
 
@@
 \label{conclusion}
-In this paper we design a distributed clustering scheme with the singleton congestion model, which forms robust clusters against primary users' effect.
-Through simulation and theoretical analysis, we find that distributed scheme achieves similar performance with centralized optimization in terms of cluster survival ratio and number of control messages.
+In this paper we investigate the robust clustering problem in CRN extensively, in order to generate robust clusters against primary users' influence, so that more CR users can benefit from operative decision making provided by the clusters.
+We provide the mathematical description of the problem, and propose both centralized and distributed schemes.
+We prove the NP hardness of this problem, and the congestion game model in game theory is used to design the distributed scheme.
+A Light weighted clustering scheme ROSS is also proposed.
+Through simulation and theoretical analysis, we find that distributed schemes achieve similar performance with centralized optimization in terms of cluster robustness, signalling overhead and cluster sizes, and outperform the comparison distributed scheme on the above mentioned metrics.
 %, which is important to form clusters which maintains unbroken to the greatest extent possible under primary users' activity.
-This paper investigates the robust clustering problem in CRN extensively, and proves the NP hardness of this problem.
-A Light weighted clustering scheme ROSS is proposed, on the basis of which, we propose the fast version scheme and the scheme which generate clusters with desired sizes.
-These schemes outperform other distributed clustering scheme in terms of both cluster survival ratio and control overhead.
+%These schemes outperform other distributed clustering scheme in terms of both cluster survival ratio and control overhead.
 
@@
 %\tcc*[r]{When to guarantee available CCCs, execute from line 1, when to control cluster size, execute from line 2}
-\textbf{while} $K_C =\emptyset$ \textbf{do}\\
+\While {$K_C =\emptyset$} {
 \While{$|C|> \delta$}{
@@
 			%$\texttt{ID}_i$ is smaller than any $\texttt{ID}_j$, $j\in \tau_2\setminus i$;
+	}
 }
@@
 %
-Now we look back to the elements in $\mathcal{G}$, which don't appear in $\mathcal{I'}$. 
+Now we look back to the elements in $\mathcal{Q}$, which don't appear in $\mathcal{I'}$. 
 We one-to-one map these elements to CR nodes, and arbitrarily put these CR nodes in the plane, and these CR nodes become single node clusters.
@@
 	  \begin{minipage}{.3\textwidth}
-      \includegraphics[width=0.8\linewidth]{np_hard_proof_dummy.pdf}
+      \includegraphics[width=0.6\linewidth]{np_hard_proof_dummy.pdf}
     \end{minipage}
@@
 %Now we look into the step 2 in the reduction.
-When $\mathcal{I}$ is not an instance for weighted k-set packing problem due to the existence of joint sets, then the corresponding cluster strategy is not a solution for the centralized clustering problem, as there are overlapped clusters.
+When $\mathcal{I}$ is not an instance for weighted k-set packing problem due to the existence of joint sets, the corresponding cluster strategy is not a solution for the centralized clustering problem, as there are overlapped clusters.
 

### 2016-07-31 journal-draft/bare_jrnl_comsoc.tex
modified section 1

@@
 Congestion game model is adopted to analyse the process of cluster formation, which not only contributes designing the distributed clustering scheme directly, but also provides the guarantee of convergence into Nash Equilibrium and convergence speed.
-Our proposed clustering solution is versatile to fulfil some other requirements such as faster convergence and cluster size control.
+Our proposed clustering solution is versatile to fulfill some other requirements such as faster convergence and cluster size control.
 The proposed distributed clustering scheme outperforms the related work in terms of cluster robustness, convergence speed and overhead.
@@
 Licensed users access the spectrum allocated to them whenever there is information to be transmitted.
-In contrast, unlicensed users can only access the licensed spectrum after validating the channel is unoccupied by licensed users, where spectrum sensing~\cite{sensing_survey_2009} plays an important role in this process.
-%This refers to the process of sensing a particular channel and verifying (with a previously specified probability of error) it is not used by a primary user currently.
-In this hierarchical spectrum access model~\cite{zhao_survey_DSA_2007}, the licensed users are also called primary users (PU), and the CR users are known as secondary users and constitute the cognitive radio networks (CRN).
+In contrast, as one way, unlicensed users can access the spectrum via opportunistic spectrum access, \ie they access the licensed spectrum only after validating the channel is unoccupied by licensed users, where spectrum sensing~\cite{sensing_survey_2009} plays an important role in this process.
+%
+In this hierarchical spectrum access model~\cite{zhao_survey_DSA_2007}, the licensed users are also called primary users (PU), while the unlicensed users are referred to as secondary users and constitute the cognitive radio networks (CRN).
 %
 %cluster
-As to the operation of CRN, efficient spectrum sensing is identified to be critical to the success of cognitive radio networks~\cite{Sahai_FundamentalDesignTradeoffs2006}.
-Cooperative spectrum sensing is able to effectively cope with noise uncertainty and channel fading, thus remarkably improving the sensing accuracy~\cite{coorperativeSensing_Akyildiz11}.
-Collaborative sensing relies on the consensus of CR users within certain area, and decreases considerably the negative probability due to the random channel effects like fading and shadowing.
-In this regard, clustering is regarded as an effective method in cooperative spectrum sensing~\cite{Sun07_clustering_spectrum_secsing, Zhao07}, as a cluster forms adjacent secondary users as a collectivity to perform spectrum sensing together.
-%As a result, more accurate sensing result can be obtained by collaborative sensing, and the improvement on spectrum sensing decreases the interference originating from CR users to primary users, which is highly desirable.
-%Also,  prevents CR users from using channels that are occupied by primary users. 
-Clustering is also efficient to enable all CR devices within the same cluster to stop payload transmission on the operating channel and initiate the sensing process, so that all the CR users\footnote{The term $\textit{user}$ and $\textit{node}$ are used interchangeably in this paper, in particular, user is used when its networking or cognitive ability are discussed or stressed, and node is used when the network topology is discussed.} within the one cluster are able to vacate the channel swiftly when primary users are detected by at least one CR node residing in the cluster~\cite{willkomm08}.
-With cluster structure, as CR users can be notified by cluster head (CH) or other cluster members about the possible collision, the possibility for them to interfere neighbouring clusters is reduced~\cite{centralizedSharing80222}.
-Clustering algorithm has also proposed to support routing in cognitive ad-hoc networks~\cite{Abbasi_survey_07}.
+Regarding to the operation of CRN, efficient spectrum sensing is identified to be critical for a smooth operation of a cognitive radio network~\cite{Sahai_FundamentalDesignTradeoffs2006}.
+This can be achieved by cooperative spectrum sensing of multiple secondary users, which has been shown to cope effectively with noise uncertainty and channel fading, thus remarkably improving the sensing accuracy~\cite{coorperativeSensing_Akyildiz11}.
+Collaborative sensing relies on the consensus of CR users\footnote{The terms user and node appear interchangeably in this paper.
+In particular, user is adopted when its networking or cognitive ability are discussed or stressed, while we refer node typicallly in the context of the topology.} within a certain area, in this regard, clustering is regarded as an effective method to realize cooperative spectrum sensing~\cite{Sun07_clustering_spectrum_secsing, Zhao07}.
+% ... decreases considerably the negative probability due to the random channel effects like fading and shadowing.
+%
+Clustering is also efficient to coordinate the channel switch operation when primary users are detected by at least one CR node residing in the cluster.
+The cluster head (CH) can enable all the CR devices within the same cluster to stop payload transmission swiftly on the operating channel and to vacate the channel ~\cite{willkomm08}.
+%
+%As to the coexistence of CR users, they can be notified by cluster head (CH) or other cluster members about the possible collision, the possibility for them to interfere neighbouring clusters is reduced~\cite{centralizedSharing80222}.
+In addition to the collaborate sensing advantage, the use of clusters is beneficial as it reduces the interference between cognitive clusters~\cite{centralizedSharing80222}.
+Clustering algorithm has also been proposed to support routing in cognitive radio networks ~\cite{Abbasi_survey_07}.
 
@@
 %The similarity of available spectrum on a group of neighbouring CR nodes, along with the benefit of collaborative decision among multiple nodes, leads to clustering as an effective approach for many applications.
-
 %[robustness issue for clustering]
-The communication within a cluster is conducted in the spectrum which is available for every member in that cluster.
-Usually there are multiple unlicensed channels available for all the members in a cluster, which are referred as \textit{common control channels} (CCC).
-When one or several members can not use one certain CCC because primary users are detected to appear on that channel, this channel will be excluded from the set of CCCs, in particular, if this channel is the working channel, then all the cluster members switch to another channel in the set of CCCs.
-In the context of CRN, as the activity of primary users is controlled by licensed operators which are generally not known to CR users, the availability of CCCs for the formed clusters  is totally decided by primary users' activity.
-In other words, the availability of CCCs for clusters is passive and can not guaranteed.
-%
-In CRN, one cluster survives the influence of primary users when at least one CCC is available in that cluster.
-As the primary users' operation is assumed to be unknown to the CR users, a cluster formed with more CCCs will survive with higher probability.
-Thus the number of CCCs in one cluster indicates the robustness of it when facing the unpredictable influence from primary users.
+
+Forming clusters is conducted in the very beginning or periodically according to the dynamics of the CRN.
+To form a cluster which is composed by the CR users, there should be channels available for communication within the cluster.
+Usually there are multiple unlicensed channels available for all the CR nodes in the cluster, which are referred to in the following of this paper as \textit{common control channels} (CCC).
+Out of the available CCCs, there are always one or multiple channels which are used for the payload communication.
+%The communication within a cluster is conducted in the spectrum which is available for every member in that cluster.
+When one or several cluster members can not use one certain CCC for example because primary user activity has been detected on that channel, it will be excluded from the set of CCCs.
+If the channel is being used for payload communication, all the cluster members will switch to another channel in the set of available CCCs to achieve seamless transmission.
+As long as there is a CCC available, the corresponding cluster can continue to exchange payload data.
+In the context of CRN, as the activity of primary users is unknown to the secondary users, the availability of CCCs of the formed clusters is totally dependent on primary users' activity.
+Thus, the clusters with more CCCs are in general better as this anticipates a longer time span payload can be exchanged.
+In this paper the robustness of a cluster against primary users is synonymous with the affluence of CCCs which are possessed by that cluster. 
+%In other words, the availability of CCCs of the formed clusters is passive and can not be guaranteed.
+%Thus, the number of CCCs in one formed cluster indicates the robustness of it when facing the unpredictable influence from primary users.
+%In CRN, one cluster survives the influence of primary users when at least one CCC is available in that cluster.
+%As the primary users' operation is assumed to be unknown to the CR users, a cluster formed with more CCCs will survive with higher probability.
+
 %It is easy to see that forming clusters with different neighbours leads to different amount of CCCs in the clusters.
 %As a result, how to form the clusters plays an important role on the robustness of clusters in CRN.
-
 %Furthermore, the clustering algorithm also determines the connectivity between several clusters which ultimately determines the robustness of the entire network on the respect of connectivity. 
-
-To solely pursue cluster robustness against the primary users' activity, \ie to achieve more common channels within clusters, the ultimately best clustering strategy is ironically that every node constitutes one cluster (called as \textit{singleton cluster} in this paper).
-%In that case, the common channels within cluster are the available channels available at that node's place.
-Apparently this contradicts our motivation of proposing cluster in cognitive radio network to enable cooperative decision making.
-This contradiction indicates that, the robustness discussed in terms of number of common channels carries little meaning when the sizes of formed clusters are not given consideration.
-Besides, cluster size plays import roles in certain aspects.
-For instance, cluster size is one decisive factor in power preservation~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}, and it also influences the accuracy of cooperative spectrum sensing~\cite{Consensus_based_clustering12}.
-%thesis
+There is a trade-off between CCCs in the formation process and the collaborative sensing performance, as less members in a cluster yield in general a higher number of CCCs while this reduces the sensing accuracy~\cite{Consensus_based_clustering12}.
+In addition, there are other reasons that motivate clusters with more members.
+For example, instead of less members, the proper cluster size results in smaller power consumption~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
+%
+%To solely pursue cluster robustness against the primary users' activity, \ie to achieve more common channels within clusters, the ultimately best clustering strategy is ironically that every node constitutes one cluster (called as \textit{singleton cluster} in this paper).
+%%In that case, the common channels within cluster are the available channels available at that node's place.
+%Apparently this contradicts our motivation of proposing cluster in cognitive radio network to enable cooperative decision making.
+Thus the cluster robustness discussed in terms of number of CCCs carries little meaning when the sizes of formed clusters are not given consideration.
+
 %Hence, cluster size should be given consideration when discussing cluster robustness against primary users.
@@
 The rest of paper is organized as follows. 
-After reviewing related work in section~\ref{related_work}, we present the system model in Section~\ref{sec:model}. 
-In Section~\ref{problem}, problem formulation is presented and the problem is thoroughly analysed.
-The centralized clustering scheme and the our proposed clustering scheme ROSS are introduced in Section~\ref{centralized_opt} and \ref{ross} respectively.
+After reviewing related work in Section~\ref{related_work}, we present the system model in Section~\ref{sec:model}. 
+Then the formal description of robust clustering problem in CRN and the characteristics of the problem are given in Section~\ref{problem}.
+The centralized and distributed solutions are introduced in Section~\ref{centralized_opt} and \ref{ross} respectively.
 %The clustering problem is given through analysis and a centralized scheme is proposed in section~\ref{centralized_scheme}.
-Extensive performance evaluation is in section~\ref{performance}.
-Finally, we conclude our work and point out direction future research in section~\ref{conclusion}.
+Extensive performance evaluation is presented in Section~\ref{performance}.
+Finally, we conclude our work and point out the direction for the future research in Section~\ref{conclusion}.
 

### 2016-08-28 journal-draft/bare_jrnl_comsoc.tex
merge the Section 2 (related work) to Section 1

@@
 \begin{IEEEkeywords}
-cognitive radio, robust cluster, game theory, congestion game, distributed, centralised, cluster size control.
+cognitive radio, robust cluster, game theory, congestion game, distributed, centralized, cluster size control.
 \end{IEEEkeywords}
@@
 In the context of CRN, as the activity of primary users is unknown to the secondary users, the availability of CCCs of the formed clusters is totally dependent on primary users' activity.
-Thus, the clusters with more CCCs are in general better as this anticipates a longer time span payload can be exchanged.
+Thus, the clusters with more CCCs are in general better as this anticipates a longer time span that payload can be exchanged.
 In this paper the robustness of a cluster against primary users is synonymous with the affluence of CCCs which are possessed by that cluster. 
@@
 
-%Hence, cluster size should be given consideration when discussing cluster robustness against primary users.
+Before mentioning our proposed robust clustering scheme, we will look back briefly on the research about clustering in wireless networks.
+%Prior to the emergence of cognitive radio, clustering has been proposed as an important method to manage network ad-hoc networks~\cite{Kawadia03,Lin97adaptiveclustering,Basagni99}, wireless mesh networks\cite{clustering_mesh_globecom2010} and sensor networks~\cite{Abbasi_survey_07}.
+In ad-hoc and mesh networks, the major goal of clustering is to maximize connectivity or to improve the performance of routes~\cite{Kawadia03, clustering_mesh_globecom2010}.
+The emphasis of clustering in sensor networks is on network lifetime and coverage~\cite{Abbasi_survey_07}..
+%Few works also take the overhead of clustering into account in ad-hoc network~\cite{clusterRoutingOverhead02infocom, clusterRoutingOverhead_wcnc04}.
+Various clustering schemes are proposed to target different aspects in cognitive radio networks.
+%Work~\cite{Consensus_based_clustering12} improves spectrum sensing ability by grouping the CR users with potentially best detection performance into the same cluster.
+%Clustering scheme~\cite{clustering_globecom11} obtains the best cluster size which minimizes power consumption caused by communication within and among clusters.
+%\cite{clustering_globecom11} proposes clustering strategy in cognitive radio network, which looks into the relationship between cluster size and power consumption and accordingly controlling the cluster size to decrease power consumption.
+The clustering schemes proposed in~\cite{Zhao07, Chen07,Affinity_clustering_09icccn} form clusters which meet the basic condition, having CCC in every cluster.
+Clustering scheme~\cite{Consensus_based_clustering12} improves spectrum sensing accuracy.
+%Clustering scheme~\cite{clustering_globecom11} obtains the best cluster size which minimizes power consumption caused by communication within and among clusters.
+\cite{clustering_globecom11, TWC2012_cooperative_communication} target on the QoS poisoning and energy efficiency.
+\cite{cluster_EW10} exploits the multiple CCCs in clusters after forming them.
+A event-driven clustering scheme is proposed for cognitive radio sensor network in \cite{Ozger_cluster_crsn_13}.
+% optimize the sizes of the formed clusters to decrease power consumption.
+%the channel available to the largest set of one-hop neighbours is selected as common channel which yields a partition of the CRN into clusters. 
+%This approach minimizes the set of distinct frequency bands (and hence, the set of clusters) used as common channels within the CRN.
+%However, bigger cluster sizes generally lead to less options within one cluster to switch to if the common channel is reclaimed by a primary node. 
+%This method pays attention to the communication among the formed clusters, but cluster robustness is not considered.
+%\cite{TWC2012_cooperative_communication} targets on the QoS poisoning and energy efficiency. 
+%This approach first decides on the relay nodes which minimize transmission power consumption, then the chosen nodes become cluster heads and clusters are formed in a dynamic coalition process.
+%This work emphasis on power efficiency and doesn't take into account the channel availability and the issue of robustness of the formed clusters.
+%\cite{cluster_EW10} deploys cluster structure in order to implement common channel control, medium access  with multiple channel and channel allocation. 
+%The node with the maximum number of common channels within its k-hop neighborhood is chosen as cluster head, but how to avoid one node appearing in multiple clusters is not given consideration.
+%A event-driven clustering scheme is proposed for cognitive radio sensor network in \cite{Ozger_cluster_crsn_13}.
+%The cluster heads are selected according to node degree, spectrum availability and the distance to the sink, and the clusters are no longer available after the event ends.
+These schemes do not provide robustness to formed clusters against primary users.
+
+%Forming robust clusters is considered in~\cite{LIU_TMC11_2, mansoor_15_cluster_robust}.
+
+A clustering scheme (denoted by SOC) which is commited to generate robust clusters against primary users is proposed in~\cite{LIU_TMC11_2}.
+SOC involves three phases of distributed executions.
+In the first phase, every secondary user forms clusters with some one-hop neighbors, in the second and third phase, each secondary user seeks to either merger other clusters around it, or join one of them.
+The metric adopted by every secondary user in the three phases is the product of the the number of CCCs and cluster size (the number of secondary users in the cluster).
+To the best of our knowledge, SOC is the only work emphasizing on the robustness of clustering structure among the related works. 
+But this robust clustering scheme is inherently flawed.
+Although the adopted metric covers both cluster size and the number of CCCs, the formation of certain clusters may be easily dominated by only one factor, e.g.
+a node which is able to use many channels will exclude its neighbor and form a cluster by itself.
+%emphasis on improving the numbers of common channels within clusters, in order to strengthening robustness of clusters, but the perused metric is not examined or proved to be able to maintain cluster structure under vigorous intensity of primary users’ activities.
+%The authors consider the balance between the number of idle common channels within cluster and cluster size and propose an algorithm that increases the number of common channels within clusters. 
+%However, this work neglects the issue of connectivity between clusters. 
+%One drawback of this scheme is, in order to increase the number of common channels within clusters, the scheme excludes certain CR nodes from the formed clusters, so that isolated nodes have to form clusters themselves.
+In addition, this scheme leads to the high variance of the cluster sizes, which is not desired in certain applications as discussed in~\cite{clustering_globecom11, cluster_EW10}.
+%The first two propose a distributed scheme where the metric is the product of cluster size and the number of common control channels.
+\cite{mansoor_15_cluster_robust} presents a heuristic method to form clusters, although the authors claim robustness is one goal to achieve, they actually uphold the minimum number of formed clusters.
 
@@
 The rest of paper is organized as follows. 
-After reviewing related work in Section~\ref{related_work}, we present the system model in Section~\ref{sec:model}. 
-Then the formal description of robust clustering problem in CRN and the characteristics of the problem are given in Section~\ref{problem}.
+We present the system model in Section~\ref{sec:model}. 
+Then the formal description of robust clustering problem in CRN and the properties of the problem are given in Section~\ref{problem}.
 The centralized and distributed solutions are introduced in Section~\ref{centralized_opt} and \ref{ross} respectively.
@@
 Finally, we conclude our work and point out the direction for the future research in Section~\ref{conclusion}.
-
-\section{Related Work}
-\label{related_work}
-
-Prior to the emergence of cognitive radio, clustering has been proposed as an important method to manage network in ad hoc networks~\cite{Kawadia03,Lin97adaptiveclustering,Basagni99}, wireless mesh networks and sensor networks~\cite{Abbasi_survey_07}.
-In ad hoc and mesh networks, the major focus of clustering is to preserve connectivity (under static channel conditions) or to improve routing.
-In sensor networks, the emphasis of clustering is on longevity and coverage.
-Overhead generated by clustering in ad hoc network is analysed in~\cite{clusterRoutingOverhead02infocom, clusterRoutingOverhead_wcnc04}.
-
-As to cognitive radio networks, clustering schemes are also proposed, which target different aspects.
-Work~\cite{Consensus_based_clustering12} improves spectrum sensing ability by grouping the CR users
-with potentially best detection performance into the same cluster.
-Clustering scheme~\cite{clustering_globecom11} obtains the best cluster size which minimizes power consumption caused by communication within and among clusters.
-\cite{clustering_globecom11} proposes clustering strategy in cognitive radio network, which looks into the relationship between cluster size and power consumption and accordingly controlling the cluster size to decrease power consumption.
-%The works~\cite{} introduced in Introduction section don't provide solution that how are the clusters formed.
-%There have been several clustering schemes tailored for CRNs. 
-Cogmesh is proposed in~\cite{Chen07} to construct clusters with the neighbouring nodes which share local common channels.
-This method pays attention to the communication among the formed clusters, but cluster robustness is not considered.
-\cite{TWC2012_cooperative_communication} targets on the QoS poisoning and energy efficiency. 
-This approach first decides on the relay nodes which minimize transmission power consumption, then the chosen nodes become cluster heads and clusters are formed in a dynamic coalition process.
-This work emphasis on power efficiency and doesn't take into account the channel availability and the issue of robustness of the formed clusters.
-In~\cite{Zhao07, Affinity_clustering_09icccn}, the channel available to the largest set of one-hop neighbours is selected as common channel which yields a partition of the CRN into clusters. 
-This approach minimizes the set of distinct frequency bands (and hence, the set of clusters) used as common channels within the CRN.
-However, bigger cluster sizes generally lead to less options within one cluster to switch to if the common channel is reclaimed by a primary node. 
-Hence, this scheme does not provide robustness to formed clusters. 
-\cite{cluster_EW10} deploys cluster structure in order to implement common channel control, medium access  with multiple channel and channel allocation. 
-The node with the maximum number of common channels within its k-hop neighborhood is chosen as cluster head, but how to avoid one node appearing in multiple clusters is not given consideration.
-A event-driven clustering scheme is proposed for cognitive radio sensor network in \cite{Ozger_cluster_crsn_13}.
-The cluster heads are selected according to node degree, spectrum availability and the distance to the sink, and the clusters are no longer available after the event ends.
-
-Clustering robustness is considered in~\cite{Lazos09, LIU_TMC11_2, mansoor_15_cluster_robust}.
-The first two propose a distributed scheme where the metric is the product of cluster size and the number of common control channels.
-This scheme involves both cluster size and the number of CCCs, but it is inherently flawed.
-With the metric, cluster could be formed only due to one factor of the two, e.g. a spectrum rich node will exclude its neighbour to form a cluster by itself.
-%emphasis on improving the numbers of common channels within clusters, in order to strengthening robustness of clusters, but the perused metric is not examined or proved to be able to maintain cluster structure under vigorous intensity of primary users’ activities.
-%The authors consider the balance between the number of idle common channels within cluster and cluster size and propose an algorithm that increases the number of common channels within clusters. 
-%However, this work neglects the issue of connectivity between clusters. 
-%One drawback of this scheme is, in order to increase the number of common channels within clusters, the scheme excludes certain CR nodes from the formed clusters, so that isolated nodes have to form clusters themselves.
-Besides, this scheme leads to a high variance on the size of clusters, which is not desired in certain applications as discussed in~\cite{clustering_globecom11, cluster_EW10}.
-\cite{mansoor_15_cluster_robust} presents a heuristic method to form clusters, although the authors claim robustness is one goal to achieve, they actually uphold the minimum number of formed clusters.
 
@@
 
-The objective is a sum of two components, the first component is the sum of products of cluster size and the corresponding number of CCCs, which is the sole metric adopted by the scheme SOC~\cite{Lazos09}.
+The objective is a sum of two components, the first component is the sum of products of cluster size and the corresponding number of CCCs, which is the sole metric adopted by the scheme SOC~\cite{LIU_TMC11_2}.
 The second component is the \textit{punishment} for choosing the clusters whose sizes are not $\delta$.
@@
 %As basin nodes have smaller $d_i$ compared with its cluster members, and many of the cluster members locate between the basin node and neighbor clusters,  %the bigger $d_i$ with bigger robustness of Social Connection, i.e, with bigger $d$ are located around cluster heads,
-%After clusters are formed, with aid of \textit{control channel rotation scheme} proposed in \cite{Lazos09}, intra and inter cluster communication is conducted and for each debable node (XXX Debatable nodes are not defined yet), the membership and channel availablity of the clusters concluding it is known.
+%After clusters are formed, with aid of \textit{control channel rotation scheme} proposed in \cite{LIU_TMC11_2}, intra and inter cluster communication is conducted and for each debable node (XXX Debatable nodes are not defined yet), the membership and channel availablity of the clusters concluding it is known.
 
@@
 $\delta$ is the desired cluster size.
-\item SOC~\cite{Lazos09}, one distributed clustering scheme pursuing cluster robustness.
-To the best of our knowledge, SOC is the only work emphasizing on the robustness of clustering structure among the related works.
+\item SOC~\cite{LIU_TMC11_2}, a distributed clustering scheme pursuing cluster robustness.
 \item Centralized robust clustering scheme. 
@@
 \end{itemize}
-The authors of~\cite{Lazos09} compared SOC with other schemes in terms of the average number of CCCs of the formed cluster, on which SOC outperforms other schemes by 50\%-100\%. 
+The authors of~\cite{LIU_TMC11_2} compared SOC with other schemes in terms of the average number of CCCs of the formed cluster, on which SOC outperforms other schemes by 50\%-100\%. 
 SOC's comparison schemes are designed either for ad hoc network without consideration of channel availability~\cite{Basagni99}, or for CRN but just considering connection among CR nodes~\cite{Zhao07}.
@@
 %This metric denotes the robustness of the formed non-singleton clusters.
-Comparing with the metric adopted by SOC~\cite{Lazos09}, which is the average number of CCCs per cluster without excluding the singleton clusters, this metric provides an more accurate description of the robustness of the non-singleton cluster.
+Comparing with the metric adopted by SOC~\cite{LIU_TMC11_2}, which is the average number of CCCs per cluster without excluding the singleton clusters, this metric provides an more accurate description of the robustness of the non-singleton cluster.
 The larger number of CCCs per non-singleton clusters means these clusters have higher probability to survive when the primary users' operation becomes more intense.

### 2016-08-28 journal-draft/bare_jrnl_comsoc.tex
modified section system model

@@
 In ad-hoc and mesh networks, the major goal of clustering is to maximize connectivity or to improve the performance of routes~\cite{Kawadia03, clustering_mesh_globecom2010}.
-The emphasis of clustering in sensor networks is on network lifetime and coverage~\cite{Abbasi_survey_07}..
+The emphasis of clustering in sensor networks is on network lifetime and coverage~\cite{Abbasi_survey_07}.
 %Few works also take the overhead of clustering into account in ad-hoc network~\cite{clusterRoutingOverhead02infocom, clusterRoutingOverhead_wcnc04}.
@@
 
-We consider a set of cognitive radio users $\mathcal{N}$ and a set of primary users distributed on a two-dimensional Euclidean plane.
+We consider a set of cognitive radio users $\mathcal{N}$ and a set of primary users distributed over a given area.
 %We denote the set of these nodes as $V$ which is partitioned into sets of primary users $V_P$ and secondary users $V_N$, i.e., $V~=~V_P~\dot\cup~V_N$. 
-These users share a number of non-overlapping licensed channels according to the spectrum overlay model. 
-The set of these licensed channels is denoted as $\mathcal{K}$. 
-As secondary users, the CR users are allowed to transmit on a channel $k \in \mathcal{K}$ only if no primary user is detected being accessing channel $k$. 
-Further, we consider a \textit{cognitive radio ad-hoc network} which consists of all secondary users and does not contain any primary user.
-
+%These users share a number of non-overlapping licensed channels according to the spectrum overlay model. 
+The CR users opportunistically a set of licensed channels, which is denoted as $\mathcal{K}$. 
+The CR users are allowed to transmit on channel $k \in \mathcal{K}$ only if no primary user is detected on channel $k$. 
 %The available channels sensed on secondary user $i$ is denoted by $V_i$ and there is $\vert V_i \vert \leq F$. % indicating the total number of 
 %%Each secondary user notifies its neighbours of the sensing result about the available channels.
-
-Secondary users conduct spectrum sensing independently and sequentially on all licensed channels.
+CR users conduct spectrum sensing independently and sequentially on all licensed channels.
 %The sensing duration and frequency on one channel is a research topic~\cite{sensing_survey_2009}, and 
@@
 Spectrum sensing/validation is out of the scope of this paper.}
+We adopt the unit disk model~\cite{unitDiskModel} for the transmission of both primary and CR users.
+%Both primary users and CR users have fixed transmission ranges respectively, and all the channels are regarded to be identical in terms of signal propagation.
+If a CR node locates within the transmission range of primary user which is working, that CR node is not allowed to use the channel which is being used by that primary user.
 %In our system model, we assume that a secondary node $n$ is able to detect for each channel $c$ whether any primary user utilizes $c$.
-We denote $K_i \subseteq \mathcal{K}$ as the set of available channels for $i$.
+As the result of spectrum sensing, $K_i \subseteq \mathcal{K}$ denotes the set of licensed channels which can be used by $i$.
 %
@@
 %
-We adopt the unit disk model~\cite{unitDiskModel} for the transmission of both primary and CR users.
-Both primary users and CR users have fixed transmission ranges respectively, and all the channels are regarded to be identical in terms of signal propagation.
-If a CR node locates within the transmission range of primary user $p$, that CR node is not allowed to use the channel $k(p)$.
 
 We assume that in addition to the licensed channels, there is one dedicated control channel.
-This control channel could be in ISM band or other reserved spectrum which is exclusively used for transmitting control messages.
-Actually, the control messages involved in the clustering process can also be transmitted on the available licensed channels through a rendezvous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}, i.e., two neighbouring nodes establish communication on the same channel.
-Over the control channel, a secondary user $i$ can exchange its spectrum sensing result $K_i$ to any $i' \in \text{Nb}(i)$.
-It is available for any secondary node $i$ to exchange control messages with any other node in its neighborhood $\text{Nb}(i)$ during the cluster formation phase.
-$\text{Nb}(i)$ is simply defined as the set of nodes located within the transmission range of $i$.
+This control channel could be one of the ISM bands or other reserved spectrum which is exclusively used for transmitting control messages.
+\footnote{Actually, the control messages involved in the clustering process can also be transmitted on the available licensed channels through a rendezvous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}, i.e., two neighbouring nodes establish communication on the same channel.}
+Over the control channel, a secondary user $i$ can exchange its spectrum sensing result $K_i$ to all its one hop neighbors $\text{Nb}(i)$, where $\text{Nb}(i)$ is the neighbors of $i$, and is simply defined as the set of CR nodes located within the transmission range of $i$.
+%It is available for any secondary node $i$ to exchange control messages with any other node in its neighborhood $\text{Nb}(i)$ during the cluster formation phase.
+In the following, we refer to the word \textit{channel} in general as licensed channel, unless we mention the control channel explicitly.
 
@@
 If a secondary user $i$ is not in the transmission range of a primary user $p$, $i$ can certainly not detect the presence of $p$.
-As the transmission range of primary users is limited and secondary users are located at different locations, different secondary users may have different views of the spectrum availability, i.e., for any $i, i' \in \mathcal{N}$, $K_i = K_{i'}$ does not necessarily hold.
+As the transmission range of primary users is limited and secondary users are located at different locations, different secondary users may have different views of the spectrum availability, i.e., for any $i, j \in \mathcal{N}$, $K_i = K_{j}$ does not necessarily hold.
 %
@@
 %Communication on licensed channels is possible only when nodes $i, j$ are both located in each other's transmission range and both share a validated licensed channel.
-As the assumed $0/1$ state of connectivity is solely based on the Euclidean distance between secondary users,
+%As the assumed $0/1$ state of connectivity is solely based on the Euclidean distance between secondary users,
 %CRN can be represented by a graph $\mathcal{G}(I,\mathcal{E})$, where $\mathcal{E}=\lbrace(i,j,v) \vert i, j \in \mathcal{N} \wedge v\in V_i \wedge v\in V_j \rbrace$ is wireless link between any secondary node $i$ and its neighbour $j$ with licensed channel $v$.
@@
 %In the rest of this paper, \textit{channel} only refers to the licensed common control channel unless the dedicated control channel is particularly mentioned.
-
-A cognitive radio network can be represented as an undirected graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{i, i'\} \in E$  if, and only if, there exists a channel $k \in \mathcal{K}$ with $k \in K_{i} \cap K_{i'}$.
-Note that we consider the channel availability only for \textit{one} snapshot of time.
-For the rest of this paper the word channel is referred to licensed channel, if the control channel is not explicitly mentioned.
+Then, a cognitive radio network can be represented as a graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{i, j\} \in E$  if, and only if, there exists a channel $k \in \mathcal{K}$ with $k \in K_{i} \cap K_{i'}$.
+%Note that the channel availability is that when the clustering process is performed. 
+%For the rest of this paper the word channel is referred to licensed channel, if the control channel is not explicitly mentioned.
 

### 2016-09-04 journal-draft/bare_jrnl_comsoc.tex
modified a lot, to modify the game part

@@
 % ... decreases considerably the negative probability due to the random channel effects like fading and shadowing.
-%
+Clustering is a process of grouping certain users in a proximity into a collective.
 Clustering is also efficient to coordinate the channel switch operation when primary users are detected by at least one CR node residing in the cluster.
@@
 \label{problem}
-In this section, we describe the definition of cluster in the context of CRNs, and the problem of robust clustering.
+In this section, we present the definition of cluster in the context of CRNs, define the clustering problem and discuss its complexity.
 
@@
 \begin{table}[h!]
-\caption{Notations in robust clustering problem}
+\caption{Notations}
 \label{tab1}
@@
 %$h(C)$ & cluster head of a cluster $C$\\
-$h_C$ & the cluster head of a cluster $C$\\
+$h_C$ & the cluster head of a cluster C\\
+$\text{CH}$ & cluster head\\
 %$\text{CH}$ & cluster head\\
-$\delta$ & desired cluster size\\
+$\delta$ & the cluster size which is preferred\\
 $S_i$ & a set of claiming clusters, each of which includes \\
@@
 $d_i$  & individual connectivity degree of CR node $i$\\
-$g_i$  & social connectivity degree of CR node $i$\\
-$C_i$  & the $i$th legitimate cluster (only appear in Sec.~\ref{centralized_opt})\\
+$g_i$  & neighborhood connectivity degree of CR node $i$\\
+$C_i$  & the $i$th potential cluster (only used in Sec.~\ref{centralized_opt})\\
 \bottomrule
@@
 
-In the introduction section, we have stated that cluster size should be given consideration to justify the concept of robustness of clusters, \ie without specifying requirement on cluster sizes, small clusters will be generated to obtain more CCCs.
-Except for cooperative sensing, clusters need to conduct some other functionalities.
-When cluster size is large, there will be substantial burden on cluster heads to manage the cluster members, which is a challenge for resource limited cluster heads, thus the cluster size should fall in a desired range~\cite{Chen04clusteringalgorithms, capacity_cluster_06}.
-
-The centralized clustering scheme aims to form clusters with desired sizes, meanwhile the total number of CCCs of all clusters is maximized.
-In the following, we refer this problem as \textit{centralized clustering}, and give the formal problem definition.
+The clustering scheme we propose in the paper aims to form clusters with preferred sizes, meanwhile maximize the average number of CCCs per cluster.
+%In the following, we refer this problem as \textit{centralized clustering}. 
+%We have mentioned that the sizes of the formed clusters should be given consideration, which is import for the discussion on cluster robustness, \ie 
+when perusing the cluster robustness without specifying the requirement on cluster sizes, a clustering method will be inclined to form small clusters.
+In that case, although more CCCs are obtained per cluster, the benefits brought in by the collective of the cluster members are compromised.
+%Except for cooperative sensing, clusters need to conduct some other functionalities.
+Large clusters are not preferred in some scenarios neither, \eg for the CRN composed with resource limited users, managing the cluster members is a substantial burden. 
+Hence, the cluster size should fall in a desired range~\cite{Chen04clusteringalgorithms, capacity_cluster_06}.
+In the following, we present the formal definition of robust clustering problem.
 
@@
 
-Given a cognitive radio network $\mathcal{N}$ where nodes are indexed from 1 to $N$ sequentially.
-Based on certain correlation, certain secondary users constitute one cluster $C$.
-$1\leq |C| \leqslant k$ where $|C|$ is the size of cluster $C$ and $k$ is a positive integer.
-We name the collection of such clusters as $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$, where $\mathcal{S}$ satisfies the following properties: $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$ and $K(C(i))\neq \emptyset$ for any $i$ which satisfies $1\leq i \leq |\mathcal{S}|$.
+Given a cognitive radio network $\mathcal{N}$ where $|\mathcal{N}|=N$, secondary users are indexed from 1 to $N$.
+A cluster $C$ can be composed with one or multiple secondary users when $|K(C)|>0$, and any two cluster members can communicate either directly, or through other members belonging to the same cluster.
+We use $f(C)$ to denote the number of CCCs of a cluster $C$, and give it a new definition as follows, the number of common control channels is $f(C) = |K(C)|$ if $|C|>1$, and $f(C)=0$ when $|C|=1$.
+The size of cluster $C$ is not bigger than a positive integer $k$.
+The collection of such clusters $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$, satisfies the following condition: $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$ and $1\leq i \leq |\mathcal{S}|$.
 
 %, which distinguishes the centralized clustering problem discussed in this paper.
-We give a new definition of the number of CCCs, where the number of common control channels is $|K(C)|$ if $|C|>1$, and is zero when $|C|=1$.
-We use $f(C)$ to denote the number of CCCs of a cluster $C$ in the new definition.
-
-The centralized clustering problem is to find a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, so that $\bigcup_{C_j\in \mathcal{S}'} C_j = N$, and $C_{j'}\cap C_j =\emptyset$ for $C_{j'}, C_j\in \mathcal{S}'$ and $j'\neq j$, so that $\sum_{C\in \mathcal{S}'} f(C)$ is maximized.
+
+The robust clustering problem is to find a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, so that $\sum_{C\in \mathcal{S}'} f(C)$ is maximized, and $\mathcal{S}'$ satisfies the following conditions, $\bigcup_{C_j\in \mathcal{S}'} C_j = \mathcal{N}$ and $C_{j'}\cap C_j =\emptyset$ where $C_{j'}, C_j\in \mathcal{S}'$ and $j'\neq j$.
 % when $|C|>1$, and $f(\cdot)=0$ when $|C|=1$.
 %As to $f(\cdot):z\rightarrow z$, under this problem setting, if only number of common channels are given consideration, only singleton clusters will be preferred, which contradicts to our goal of clustering CR nodes together, thus we choose $f(\cdot)= |K_{C}|\cdot |C|$, the product of number of common channels and cluster size.
-The decision version of centralized clustering in CRN is to ask whether there exists a no-empty $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C\in \mathcal{S}'} f \geqslant \lambda$ where $\lambda$ is a real number.% in stead of to maximize $\sum_{C\in \mathcal{S}'} f$.
 \end{mydef}
@@
 \subsection{Complexity of the Robust Clustering Problem}
-In this section we investigate the complexity of robust clustering problem.
-Theorem~\ref{theorem1} tells centralized clustering problem in CRN is one NP-hard problem.
+%In this section we investigate the complexity of robust clustering problem.
+Based on Definition~\ref{def_centralized_clustering}, the decision version of this problem is to ask whether there exists a no-empty $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C\in \mathcal{S}'} f(C) \geqslant \lambda$ where $\lambda$ is a real number.
+We have the following theorem on complexity.
 
@@
 \label{theorem1}
-CRN clustering problem is NP-hard, when the maximum size of clusters $k\geqslant 3$.
+Robust clustering problem in CRN is NP-hard, when the maximum size of clusters $k\geqslant 3$.
 %Assume a CRN can be represented by a connected graph, and there is at least one common channel between any pair of neighbours, then forming at least two CR nodes into one cluster is NP-complete.
@@
 The proof is in Appendix~\ref{proof_theorem1}.
+As it is not likely to generate clusters with size of 2, this theorem actually indicates that the robust clustering problem in CRN is NP-hard. 
 In the following sections, both centralized and distributed solutions will be introduced.
@@
 %Exact cover problem can be solved with Knuth's Algorithm X~\cite{dancingLinks_Knuth} as it finds out all the instances of exact cover, then we can choose the one with the biggest sum of weights. 
-As the robust clustering problem in CRN is NP hard, there is no polynomial algorithm to solve the problem, \ie maximizing the sum of CCCs in all non-singleton clusters.
-Thus, we formulate the problem into a binary linear programming problem, where the objective function and the constraints are heuristic, in particular, the objective is different from the object in the Definition~\ref{def_centralized_clustering}.
-%Note that binary linear programming is in NP-complete.
+As the robust clustering problem in CRN is NP hard, there is no polynomial solution available.
+In this paper we formulate the problem into a binary linear programming problem.
+To make the formulation possible, we adopt heuristics in both the objective function and the constraints, besides, the objective is not totally aligned with the object in the Definition~\ref{def_centralized_clustering}.
 
@@
 %These tailored parameters don't harm the validity of the performance gap between the two schemes.
-
-Given a CRN $\mathcal{N}$ and desired cluster size $\delta$, we obtain a collection of clusters $\mathcal{G}$ which contains all the \textit{legitimate} clusters, and the sizes of these clusters are $1,2,\ldots,\delta$.
-Legitimate clusters are the clusters which satisfy the conditions in Section~\ref{def_cluster}. 
-Note that the legitimate clusters include the \textit{singleton} ones, \ie the cluster which has only one CR node, so that we can guarantee the partition of any network is always feasible.
-%
-With $N=|\mathcal{N}|, G=|\mathcal{G}|$, we construct a constant $G\times N$ matrix $Q_{G\text{x}N}$. 
-The element of matrix $Q$ is $q_{ij}$, where the subscript $i$ is the index of legitimate cluster, and $j$ is the node ID of one CR node.
-%Note that $C_i$ means $i$th cluster in the collection $\mathcal{G}$, doesn't denote the cluster where cluster head is $i$, this notation is only valid in this subsection.
-There are $i\in \{1,2,\cdots,G-1, G\}$, and $j\in \{1,2,\cdots,N-1, N\}$.
-Element $q_{ij}= |K(C_i)|$ if node $j\in C_i$, and $q_{ij}= 0$ if $j\notin C_i$.
-In other words, each non-zero element $q_{ij}$ denotes the number of CCCs of the cluster $i$ where node $j$ resides.
-
-\begin{figure}[ht!]
-\centering
-\bordermatrix{~ 		& 1 	& 2 	& 3 	& \cdots & j & \cdots	& N-1 	& N	\cr
-                  1 	& |K(C_1)| 	& |K(C_1)| 	& 0 	& \cdots & \cdots &\cdots	& 0 	& 0	\cr
-                  2 	& |K(C_2)| 	& 0 	& |K(C_2)| 	& \cdots & \cdots & \cdots 	& 0 	& 0	\cr
-				\vdots  	&\vdots & 	 	& 		&  \vdots		& 		& \vdots \cr
-				i 	& 0 	& |K(C_i)| 	& 0 	& \cdots  & \cdots & \cdots 	& |K(C_i)| 	& 0	\cr
-				\vdots  	&\vdots & 	 	& 		&  \vdots & \cdots & \cdots 		& 		& \vdots \cr
-				\vdots 	& \vdots  	& 0 	& 0 	& \cdots & \cdots & \cdots 	& |K(C_i')| 	& 0	\cr
-				G  	& |K(C_G)| & \cdots	 	& 		&  \vdots	& \cdots & \cdots& 		& \vdots \cr}	
-\caption{An example of Matrix $Q$, its rows correspond to all legitimate clusters, and columns correspond to the CR nodes in the CRN.}
-\label{xx}
-\end{figure}
-
-We build a $G\times N$ binary variable matrix $X$, which illustrates the clustering solution.
-The element of matrix $X$ is binary variable $x_{ij}, i=1, \ldots, G, j=1, \ldots, N$.
-%$x_{ij}=1$ denotes node $i$ is in the $j$th legitimate cluster, and the cluster is chosen in the solution, $x_{ij}=0$ means the $j$th legitimate cluster is not adopted by the partition.
-%Note that matrix $Q$ contains only constant elements, and matrix $X$ contains only binary variables.
-Now, we can formulate the optimization problem as follows,
 
@@
 
-The objective is a sum of two components, the first component is the sum of products of cluster size and the corresponding number of CCCs, which is the sole metric adopted by the scheme SOC~\cite{LIU_TMC11_2}.
-The second component is the \textit{punishment} for choosing the clusters whose sizes are not $\delta$.
-In fact, the second part is particularly designed to eliminates the drawbacks of SOC, \ie SOC produces a large number of singleton clusters and a few large clusters.
-In practical computation, we minimize the opposite of the first part, and the punishment is a positive value.
-%
-The first constraint restricts each node $j$ to reside in exactly one cluster.
-In the second constraint, $w_i$ is an auxiliary binary variable which denotes whether cluster $C_i$ is chosen by the solution, in particular, 
+The objective is to maximize the sum of the products of cluster size and the corresponding number of CCCs.
+The second component is designed to be the \textit{punishment} for forming clusters whose sizes are not $\delta$, which is the preferred cluster size.
+We minimize the opposite of the real objective to make this problem solvable.
+The constraints guarantee to obtain the clusters which don't overlap.
+Now we introduce the formulation in details.
+
+$N=|\mathcal{N}|, G=|\mathcal{G}|$.
+$\mathcal{G}$ is the collective of all the \textit{potential} clusters in a CRN $\mathcal{N}$, and the sizes of these clusters are $1,2,\ldots,\delta$, where $\delta$ is the preferred size for clusters.
+%Given a CRN $\mathcal{N}$ and desired cluster size $\delta$, we obtain a collection of clusters $\mathcal{G}$ which contains all the \textit{potential} clusters, and the sizes of these clusters are $1,2,\ldots,\delta$.
+Potential clusters are the clusters which satisfy the conditions in Section~\ref{def_cluster}. 
+Note that the potential clusters include the \textit{singleton} ones, \ie the cluster which has only one CR node.
+By permitting the existence of the singleton clusters, we can ensure that the $\mathcal{S}'$ in Definition~\ref{def_centralized_clustering} is always be feasible.
+
+Constant $q_{ij}$ is the element of the constant $G\times N$ matrix $Q_{G\text{x}N}$ which is shown in Figure~\ref{costant_matrix_Q}. 
+The subscript $i$ is the index of a potential cluster, $j$ is the node ID of a CR node, $q_{ij}= |K(C_i)|$ when there is $j\in C_i$, and $q_{ij}= 0$ when there is $j\notin C_i$.
+In other words, each non-zero element $q_{ij}$ denotes the number of CCCs of the cluster $i$ where node $j$ resides.
+Knowing the meanings of subscripts $i$ and $j$, it is easy to notice there are $i\in \{1,2,\cdots,G-1, G\}$ and $j\in \{1,2,\cdots,N-1, N\}$.
+%
+The binary variable $x_{ij}$'s subscripts have the same meanings with that of $q_{ij}$, thus they have the same scope.
+$x_{ij}$ indicates whether the CR node $j$ resides in the potential cluster $i$, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$. 
+%
+
+\begin{figure}[ht!]
+\centering
+\bordermatrix{~ 		& 1 	& 2 	& 3 	& \cdots & j & \cdots	& N-1 	& N	\cr
+                  1 	& |K(C_1)| 	& |K(C_1)| 	& 0 	& \cdots & \cdots &\cdots	& 0 	& 0	\cr
+                  2 	& |K(C_2)| 	& 0 	& |K(C_2)| 	& \cdots & \cdots & \cdots 	& 0 	& 0	\cr
+				\vdots  	&\vdots & 	 	& 		&  \vdots		& 		& \vdots \cr
+				i 	& 0 	& |K(C_i)| 	& 0 	& \cdots  & \cdots & \cdots 	& |K(C_i)| 	& 0	\cr
+				\vdots  	&\vdots & 	 	& 		&  \vdots & \cdots & \vdots 		& 		& \vdots \cr
+				\vdots 	& 0  	& 0 	& 0 	& \cdots & \cdots & \cdots 	& |K(C_i')| 	& 0	\cr
+				G  	& |K(C_G)| & \cdots	 	& 		&  \vdots	& \cdots & \vdots& 		& \vdots \cr}	
+\caption{An example of Matrix $Q$, its rows correspond to all potential clusters, and columns correspond to the CR nodes in the CRN. }
+\label{costant_matrix_Q}
+\end{figure}
+
+Now let us have a look at the objective function again.
+Although the related work SOC~\cite{LIU_TMC11_2} adopts the product of cluster size and number of CCCs as its sole metric, SOC still generates a large number of singleton clusters and a few large clusters.
+To refrain the clusters which don't have preferred clusters sizes, the second item is designed, where
+
 $$
 w_i = \left\{ \begin{array}{rl}
-0 &\mbox{if $i$th legitimate cluster $C_i$ is chosen} \\
-1 &\mbox{if $i$th legitimate cluster $C_i$ is not chosen} \\
+0 &\mbox{if $i$th potential cluster $C_i$ is chosen} \\
+1 &\mbox{if $i$th potential cluster $C_i$ is not chosen} \\
 \end{array} \right.
 $$
-The second constraint regulates that when the $i$th legitimate cluster $C_i$ is chosen, the number of elements which equal to 1 in the $i$th row of the matrix $X$ is $|C_i|$.
-%
-Now we explain how does the mechanism of the punishment in the objective work. 
-The parameter $p$ is defined as follows,
+$w_i$ is an auxiliary binary variable which denotes whether cluster $C_i$ is chosen by the clustering solution or not.
+When $w_i$ is zero, it means $C_i$ is chosen by the clustering solution, in this case, the second item in the objective function is $p$, which is defined as follows,
+
 $$
@@
 $$
-where $\alpha_i>0$ and increases when $|C_i|$ diverges from $\delta$.
-Because of $w_i$, any chosen cluster ($w=0$) brings certain \textit{punishment}.
-When the chosen cluster's size is desired size $\delta$, the punishment is zero.
+where $\alpha_x$ is a positive value, which increases with the divergence between $|C_i|$ and $\delta$, thus these is $\alpha_2> \alpha_1>0$.
+Because of $w_i$, any cluster which appears in the clustering solution ($w=0$) will bring certain \textit{punishment}.
+Only when that cluster's size is exactly the preferred size $\delta$, the punishment is zero.
 In contrary, when the chosen cluster's size diverges from $\delta$, the objective function suffers \textit{loss}.
 In particular, when $w_i=0$ and $|C_i|=1$, the punishment is the most severe.
-This design doesn't follow the definition of $f(C)$ in Definition~\ref{def_centralized_clustering} strictly, where $f(C_i)=0$ when $|C_i|=1$, but our design echoes the definition by exerting the most severe punishment on the singleton clusters in the clustering solution.
-Choice of $\alpha_i$ affects the resultant clusters.
+With such design, the solution is encouraged not to generate singleton clusters.
+%doesn't follow the definition of $f(C)$ in Definition~\ref{def_centralized_clustering} strictly, where $f(C_i)=0$ when $|C_i|=1$, but our design echoes the definition by exerting the most severe punishment on the singleton clusters in the clustering solution.
+%Choice of $\alpha_i$ affects the resultant clusters.
+
+As to the constraints, the first constraint restricts each node $j$ to reside in exactly one cluster.
+The second constraint regulates that when the $i$th potential cluster $C_i$ is chosen, there will be exactly $|C_i|$ CR nodes residing in cluster $C_i$.
 
@@
 %We reiterate the reasons for pursuing the heuristic scheme, 
-%Note the collection of legitimate clusters is dependant on the network topology and spectrum availability in the network, thus to each specific CRN, the space of solution is different.
+%Note the collection of potential clusters is dependant on the network topology and spectrum availability in the network, thus to each specific CRN, the space of solution is different.
 
@@
 \label{ross}
-The cluster formation of one CRN can be obtained by solving the proposed optimization problem, but centralized scheme is inherently not suitable for the CRN which involves dynamics, \eg the mobility of CR users and the variance of the available spectrum due to primary users' operation.
+The centralized robust clustering scheme is inherently not suitable for the CRN which involves dynamics in multiple aspects.
+Whenever clustering or re-clustering is necessary, which could be triggered by either the mobility of CR users or the variance of the available spectrum, the centralized entity needs to collect the information from all the CR nodes, and then distributes the clustering solution after computation.
+
 In this section we introduce the distributed clustering scheme ROSS.
-%
 ROSS consists of two cascaded phases: \textit{cluster formation} and \textit{membership clarification}.
@@
 \label{phaseI}
-After conducting spectrum sensing and communication with neighbours, every CR node is aware of the available channels available for themselves as well as for all its neighbors.
-For each CR user $i$, two metrics are proposed to characterize the spectrum proximity between $u$ and its neighborhood:
-%\newtheorem{def1}{Definition}
-%\label{def1}
-%\begin{def1}
-%Connection vector $\left\{d_i,g_i\right\}$ of CR node $i$:
-%spectrum connectivity degree: 
-%\begin{equation}
-%\label{d_i}
-%d_i=\sum_{j\in N_i}\vert V_i\cap V_j\vert
-%\end{equation}
-%Social Connection degree:
-%\begin{equation}
-%\label{g_i}
-%g_i=|\bigcap_{j\in N_i}V_j|
-%\end{equation}
-%\end{def1}
+After conducting spectrum sensing and communicating with neighbors, every CR node is aware of the channels which are available on themselves and also those on their one hop neighbors.
+Two metrics are proposed to characterize the proximity in terms of available spectrum between CR node $i$ and its neighborhood:
+
 \begin{itemize}
@@
 \item \textit{Individual connectivity degree} $d_i$: $d_i=\sum_{j\in \text{Nb}(i)}\vert K_i\cap K_j\vert$. 
-It denotes the sum of the numbers of common controls channels between node $i$ and every neighbour.
-It is an indicator of node $i$'s adhesive property to the CRN.
-
-\item \textit{Social connectivity degree} $g_i$: $g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$. It is the number of common channels available to $i$ and all its neighbors.
-$g_i$ represents the ability of $i$ to form a robust cluster with its neighbours.
+$d_i$ is the total number of the CCCs between node $i$ and every its neighbor.
+It is an indicator of node $i$'s adhesion to the CRN.
+
+\item \textit{neighborhood connectivity degree} $g_i$: $g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$. 
+It is the number of CCCs which are available for $i$ and all its neighbors.
+$g_i$ represents the ability of $i$ to form a robust cluster with its neighbors.
 \end{itemize}
-Individual connectivity degree $d_i$ and social connectivity degree $g_i$ together form the \textit{connectivity vector}.
-Figure~\ref{fig1} illustrates an example CRN where each node's connectivity vector is shown.	
+Individual connectivity degree $d_i$ and neighborhood connectivity degree $g_i$ together form the \textit{connectivity vector}.
+Figure~\ref{fig1} illustrates an example CRN where every node's connectivity vector is shown.	
 \begin{figure}[ht!]
@@
 Dashed edge indicates the end nodes are within each other's transmission range.}
-	% The number of common channels between two nodes is shown by the edge.
 	\label{fig1}
@@
 After introducing the connectivity vector, we proceed to introduce the first phase of algorithm ROSS.
-To put it briefly, in this phase cluster heads are determined in the beginning. Then clusters are formed on the basis of the cluster heads' neighborhoods.
-
-\subsubsection{Determining Cluster Heads and Form the Initial Clusters}
+In this phase, cluster heads are determined through a series of autonomous negotiations among the CR users, then the neighborhoods of the cluster heads become clusters.
+
+\subsubsection{Determining Cluster Heads and Form Clusters}
 In this phase, each CR node decides whether it is a cluster head by comparing its connectivity vector with its neighbors.
-When CR node $i$ has lower individual connectivity degree than any neighbors except for those which have already become cluster heads (the appearance of cluster heads will be explained in Section~\ref{membershipClarification}), then node $i$ becomes clusters head.
+When CR node $i$ has lower individual connectivity degree than all its neighbors except for those which have already identified to be cluster heads, node $i$ becomes a cluster head.
 %In other words, CR node $i$ becomes cluster head if $d_i > d_k, \forall k\in \texttt{Nb}_i\setminus CHs$ ($CHs$ donate the cluster heads existing in $\texttt{Nb}_i$).
-If there is another CR node $j$ in its neighborhood which has the same individual connectivity degree as $i$, \ie $d_j = d_i$ and $d_j < d_{k}, \forall k\in \text{Nb}(j)\setminus \{\text{CHs}\cup i\}$, then the node out of $\{i, j\}$ with higher social connectivity degree becomes cluster head.
-The other nodes become a member of that cluster.
-If $g_i = g_j$ as well, the node ID is used to break the tie, \ie the one with smaller node ID becomes the cluster's head.
-%
-The node which becomes cluster head broadcasts a message of its eligibility of being cluster head to notify its neighbours, and claims its neighbourhood as its cluster.
+If there is another CR node $j$ in its neighborhood which has the same individual connectivity degree as $i$, \ie $d_j = d_i$ and $d_j < d_{k}, \forall k\in \text{Nb}(j)\setminus \{\text{CHs}\cup i\}$, then the node between $i$ and $j$, which has higher neighborhood connectivity degree will become the cluster head, and the other node become one member of the newly identified cluster head.
+If $g_i = g_j$ as well, the node ID is used to break the tie, \ie the one with smaller node ID becomes a cluster head.
+%
+The node which is identified as a cluster head broadcasts a message to notify its neighbors of this change, and its neighbors which are not cluster heads become cluster members
+\footnote{The reasons for the occurrence of the cluster heads in the neighborhood of a new cluster head will be explained in Section~\ref{ross_p1_guarantee_ccc} and \ref{ross_p2_cluster_pruning})}.
 The pseudo code for the cluster head decision and the initial cluster formation is shown in Algorithm~\ref{alg0} in the appendix.
@@
 After receiving the notification from a cluster head, a CR node $i$ is aware that it becomes a member of a cluster. 
-Consequently, $i$ sets its individual connectivity degree to a positive number $M > |\mathcal{K}| \cdot N$.
-%, which is smaller than all the possible individual connectivity degrees in the CR network.
-Then $i$ broadcasts its new individual connectivity degree to all its neighbors. 
+Consequently, $i$ sets its individual connectivity degree to a positive number $M > |\mathcal{K}| \cdot N$, and broadcasts the new individual connectivity degree to all its neighbors. 
 %wrong:
@@
 %\end{proof}
-We manipulate the individual connectivity degree of the CR nodes which are included in certain clusters.
-Hence, nodes located outside of the a formed cluster can possibly become cluster heads or can also be included into other clusters.
-When a CR node $i$ is associated to multiple clusters, \ie $i$ has received multiple notifications of cluster head eligibility from different CR nodes, $d_i$ is still set to $M$.
-%Then every CR node becomes either cluster head or one member of at least one cluster.
+When a CR node $i$ is associated to multiple clusters, \ie $i$ has received multiple notifications of cluster head eligibility from different CR nodes, $d_i$ is still set to be $M$. 
 %In other words, with this manipulation on its individual connectivity degree, every CR node in the network will be involved in the clustering process, the proof will be given later.
-%Every CR user is involved in the clustering process and becomes either cluster head or member is described in theorem~\ref{clustering:theorem}.
-We have the following theorem to show that as long as a secondary user's individual connectivity degree is greater than zero, that secondary user will eventually be integrated into a certain cluster, or it eventually becomes a cluster head.
+The manipulation of the individual connectivity degree of the cluster members fastens the speed of completing choosing the cluster heads.
+%, which enables the nodes which are outside of the cluster can possibly become cluster heads or can also be included into other clusters.
+We have the following theorem to show that as long as a secondary user's individual connectivity degree is greater than zero, every secondary user will eventually be either integrated into a certain cluster, or becomes a cluster head.
 \begin{theorem}
@@
 The procedure of the proof also illustrates the time needed to conduct Algorithm~\ref{clustering:theorem}. 
-Consider an extreme scenario, where all the secondary nodes sequentially execute Algorithm~\ref{alg0}, \ie they constitute one list as discussed in the example in the proof.
+Consider an extreme scenario, where all the secondary nodes sequentially execute Algorithm~\ref{alg0}, \ie they constitute a list as discussed in the example in the proof.
 %
@@
 \subsubsection{Guarantee the Availability of Common Control Channel}
+\label{ross_p1_guarantee_ccc}
 %After deciding itself being cluster head, CR node broadcasts to notify its neighbours on the dedicated control channel, meanwhile, $i$'s initial cluster is formed immediately, which is $i$'s neighbourhood except for those nodes which have become cluster heads, \ie $C_i=(\text{Nb}_i\setminus \text{CHs})\cup i$.
-After executing phase I of ROSS, it is possible that certain formed clusters don't own CCCs.
-%We solve this problem with the following method.
-%there are some secondary users which become cluster heads.
-%The cluster head and its neighbourhood (except for the CHs) form a cluster.
-%
-As decreasing cluster size increases the number of CCCs within the cluster, for those clusters having no CCCs, certain nodes need to be eliminated to gain at least one CCC.
+After executing Algorithm~\ref{alg0}, certain formed clusters may don't possess any CCCs.
+As decreasing cluster size increases the CCCs within a cluster, for those clusters having no CCCs, certain nodes need to be eliminated to obtain at least one CCC.
 The sequence of elimination is performed according to an ascending list of nodes which are sorted by the number of common channels between the nodes and the cluster head. 
-In other words, the cluster member which has the least number of common channels with the cluster head is excluded first.
+In other words, the cluster member which has the least common channels with the cluster head is excluded first.
 If there are multiple nodes having the same number of common channels with the cluster head, the node whose elimination brings in more common channels will be excluded.
 If this criterion meets a tie, the tie will be broken by deleting the node with smaller node ID.
-It is possible that the cluster head excludes all its neighbours and resulting in a \textit{singleton cluster} which is composed by itself.
+It is possible that the cluster head excludes all its neighbors and resulting in a singleton cluster which is composed by itself.
 %At the end of this procedure every formed cluster has at least one common channel.
 The pseudo code for cluster head to obtain at least one common channel is shown in Algorithm~\ref{alg_size_control_available_CCC}.
-As to the nodes eliminated in this procedure, they restore their original individual connectivity degrees, and become either cluster heads or get included into other clusters afterwards according to Theorem~\ref{clustering:theorem}.
+As to the nodes which are eliminated from the previous clusters, they restore their original individual connectivity degrees, executes Algorithm~\ref{alg0}, and become either cluster heads or get included into other clusters afterwards according to Theorem~\ref{clustering:theorem}.
+
+During Phase I, when ever a CR node is decided to be a cluster head and accordingly forms a cluster, or its cluster's composition is changed, the cluster head will broadcast the updated information about its cluster, which includes the sets of available channels on all its cluster members.
 
 \subsubsection{Cluster Size Control in Dense CRN}
-\label{cluster_pruning}
-
-In the following we illustrate the pressing necessity to control the cluster size when CRN becomes dense via both theoretical analysis and simulation.
+\label{ross_p2_cluster_pruning}
+
+In this subsection, we illustrate the pressing necessity to control the cluster size when CRN becomes denser.
+
+We consider a cluster $C(i)$ where $i$ is CH in a dense CRN. 
+To make the analysis easier, we assume there is no CHs which are generated within $i$'s neighborhood during the procedure of guaranteeing CCCs.
 Assuming the CR users and PUs are evenly distributed and PUs occupy the licensed channels randomly, then both CR nodes density and channel availability in the CRN can be seen to be spatially homogeneous.
-%Based on Algorithm~\ref{alg0}, cluster heads are the CR nodes which possess the biggest individual connectivity degrees in their neighborhood respectively, and they are surrounded by CR nodes.
-%In contrast, CR nodes residing on edge are unlikely to become cluster heads as their neighbourhoods are only half the nodes locating away from edge.
-The formed clusters are the neighbourhoods of cluster heads, and the neighbourhood is decided by the transmission range and network density.
-%
-We consider a cluster $C(i)$ where $i$ is CH in a dense CRN. 
-When we don't consider the CHs which could appear within $i$'s neighbourhood in the procedure of guaranteeing CCCs, according to Algorithm~\ref{alg0}, the nearest cluster heads could locate just outside node $i$'s transmission range.
+In this case the formed clusters are decided by the transmission range and network density.
+According to Algorithm~\ref{alg0}, the nearest cluster heads could locate just outside node $i$'s transmission range.
+%
 An instance of this situation is shown in Figure~\ref{clusters_denseNetwork}.
-%
 In the figure, black dots represent cluster heads, the circles denotes the transmission ranges of cluster heads.
@@
 \end{figure}
-%\begin{figure}
-%\floatbox[{\capbeside\thisfloatsetup{capbesideposition={left,top},capbesidewidth=4cm}}]{figure}[\FBwidth]
-%{\caption{Clusters formation in extremely dense CRN. Black dots are cluster heads, other cluster members are not drawn.}\label{clusters_denseNetwork}}
-%{\includegraphics[width=0.3\linewidth]{clusters_denseNetwork_2.pdf}}
-%\end{figure}
 Let $l$ be the length of side of simulation plan square, and $r$ be CR's transmission radius.
@@
 Both analysis and simulation show that when applying ROSS, after the number of clusters saturates with the increase of network density, the cluster size increases linearly with the network density, thus certain measures are needed to curb this problem.
-
 This task falls to the cluster heads.
@@
 
-%Note that ROSS generates clusters on basis of cluster heads' neighbourhood, thus the $\delta$ is smaller than the average neighbourhood size.
-%As there are extensive overlaps between clusters, the threshold that the cluster size satisfies requirement should be larger than $\delta$.
-%In practise, we set this threshold as $5*\delta/2$.
-%This process ends when the size of resultant cluster is at most $5*\delta/2$ and at least one CCC is available.
-
-%Figure~\ref{fig2} shows the clusters formed in the example in Figure~\ref{fig1} when the desired cluster size is 3.
-
-%Especially, it forster the connectivity between the clusters. It can do so, as the nodes with larger connectivity degree are not cluster heads but members. 
-%As basin nodes have smaller $d_i$ compared with its cluster members, and many of the cluster members locate between the basin node and neighbor clusters,  %the bigger $d_i$ with bigger robustness of Social Connection, i.e, with bigger $d$ are located around cluster heads,
-%After clusters are formed, with aid of \textit{control channel rotation scheme} proposed in \cite{LIU_TMC11_2}, intra and inter cluster communication is conducted and for each debable node (XXX Debatable nodes are not defined yet), the membership and channel availablity of the clusters concluding it is known.
-
 \begin{figure}[ht!]
@@
   \includegraphics[width=0.5\linewidth]{figure2.pdf}
-  \caption{Clusters formation after the phase I of ROSS. Some nodes are debatable nodes, \ie belonging to more than one cluster.}
+  \caption{Clusters formation after the phase I of ROSS. CR nodes $A, B, D$ are debatable nodes as they belong to more than one cluster.}
   \label{fig2}
@@
 After applying phase I of ROSS to the example in Figure~\ref{fig1}, the resulted clusters are shown in Figure~\ref{fig2}.
-We notice nodes $A, B, D$ are included in more than one cluster. 
-We refer these nodes as \textit{debatable nodes} as their cluster affiliations are not clear, and the clusters which include the debatable node $i$ are called \textit{claiming clusters} of node $i$, and are denoted as $S_i$.
-Actually, debatable nodes extensively exist in CRN with larger scale.
-Debatable nodes should be exclusively associated with only one cluster and be removed from the other claiming clusters, this procedure is called \textit{cluster membership clarification}.
-We will introduce the solution for cluster membership clarification in the following.
-
-%In the second phase of ROSS, debatable nodes will chose only one cluster to reside.
+We notice that nodes $A, B, D$ are included in more than one cluster. 
+We refer these nodes as \textit{debatable nodes} as their cluster affiliations are not decided.
+The clusters which include the debatable node $i$ are called \textit{claiming clusters} of node $i$, and the set of these clusters is denoted as $S_i$.  
+%Actually, debatable nodes extensively exist in CRN with larger scale.
+The debatable nodes which are generated from the first phase of ROSS should be exclusively associated with only one cluster and be removed from the other claiming clusters, this procedure is called \textit{cluster membership clarification}.
+%We will introduce the solution for cluster membership clarification in the following.
 
@@
 %Debatable node $i$ is aware of all its claiming clusters in $S_i$. 
-After Phase I, debatable nodes, \eg $i$ needs to decide one cluster $C\in S_i$ to stay, and thereafter leaves the rest others in $S_i$.
-The principle for debatable node $i$ to choose one claiming cluster is that its decision can result in the greatest increase of common channels in all its claiming clusters.
+Assume a debatable node $i$ needs to decide one cluster $C\in S_i$ to stay, and thereafter leaves the rest others in $S_i$.
+In this process, the principle for $i$ is that its move should result in the greatest increase of CCCs in all its claiming clusters.
 %The set of available channels of one cluster are known by the debatable nodes which locate in that cluster. %this is finished 
-Since node $i$ is a neighbour of all the cluster heads in $S_i$, node $i$ is aware of the channel availability on these claiming cluster heads, and the common control channels in these claiming clusters.
-With these information, node $i$ is able to calculate how how many more CCCs will be produced in one claiming cluster if $i$ leaves that cluster.
+Note that node $i$ is aware of the spectrum availability on all the cluster members of each claiming cluster, thus node $i$ is able to calculate how many more CCCs can be produced in one claiming cluster if $i$ leaves that cluster.
 %Based on this calculation, $i$ decides on one claiming cluster to stay and leaves the other claiming clusters.
 If there exists one cluster $C\in S_i$, when $i$ leaves this cluster brings the least increased CCCs than leaving any other claiming clusters, then $i$ chooses to stay in cluster $C$.
-When there comes a tie, among the relevant claiming clusters, $i$ chooses to stay in the cluster whose cluster head shares the most CCCs with $i$.
-In case there are multiple claiming clusters demonstrating the same on the aforementioned criteria, node $i$ chooses to stay in the claiming cluster which has the smallest size.
-Node IDs of cluster heads will be used to break tie if the previous rules could not decide on the unique claiming cluster to stay.
-The pseudo code of this algorithm is described as Algorithm~\ref{alg4}.
+When there comes a tie, among the claiming clusters, $i$ chooses to stay in the cluster whose cluster head shares the most CCCs with $i$.
+In case there are multiple claiming clusters demonstrating the same on the aforementioned metric, node $i$ chooses to stay in the claiming cluster which has the smallest size.
+Node IDs of cluster heads will be used to break tie if all the previous metrics could not decide on the unique claiming cluster for $i$ to stay.
+The pseudo code of this algorithm is given as Algorithm~\ref{alg4}.
 %To conduct Algorithm~\ref{alg4}, debatable node $i$ needs to know the necessary information about its claiming clusters, \ie $K(C)$ (the set of available channels in cluster $C$), $K(h_C)$ (the set of available channels on $C$'s cluster head $h_C$) and $|C|, C\in S_i$ (sizes of $i$'s claiming clusters).
-After deciding its membership, debatable node $i$ notifies all its claiming clusters, and retrieves the updated information of the claiming clusters, \eg $K(C)$, $K_{h_C}$, $|C|$, where $C\in S_i$.
-%
-%This procedure raises a concern that the debatable nodes may never stop changing their affiliations, because a debatable nodes' choice is based on the members of its claiming clusters, and the members are changed by other debatable nodes' choices.
+After deciding its membership, debatable node $i$ notifies all its claiming clusters of its choice, and the claiming clusters from which node $i$ leaves also broadcast their new cluster composition and the spectrum availability on all their cluster members.
+
+The autonomous decisions of the debatable CR nodes' raise the concern on the endless chain effect.
+For instance,
+
+debatable nodes may never stop changing their affiliations, because a debatable nodes' choice is based on the members of its claiming clusters, and the members are changed by other debatable nodes' choices.
 %In a word, debatable nodes' choices on cluster affiliation are dependent on each other, thus there could be an infinite chain effect in the process of membership clarification.
@@
 %%, and if it converges, how good such a distributed scheme performs.
-%
+
 In the following we show that the process of membership clarification can be formulated into a game, and a equilibrium is reached after a finite number of best response updates made by the debatable nodes.
@@
 \item \textbf{Robustness of the clusters against newly added PUs.}
-We increase the number of PUs to challenge the clusters, and count the number of \textit{unclustered} CR nodes which are the CR nodes which are not included in any non-singleton clusters.
+We increase the number of PUs to challenge the clusters, and count the number of \textit{unclustered} CR nodes which are the synonyms of the singleton clusters.
 This metric indicates the robustness of clusters from a more practical point of view, \ie as to the clusters formed for a given CRN and spectrum availability, how many CR nodes can still make use of the clusters when the spectrum availability decreases.
@@
  Scheme 				&Message Complexity 	&   Quantitative number of messages 		& Content of message (size of message) 									\\ \hline
- ROSS-DGA, ROSS-$\delta$-DGA 	&$\mathcal{O}(N^3)$ (worst case)		&   $h+2*m^2d$ (upper bound)  				&   \multirow{2}{*}{\parbox{6.4cm}{Phase I: notification from cluster head (1 byte), new individual connectivity degree (1 byte);  Phase II: update of debatable nodes' affiliation (1 byte), claiming cluster $i$' new membership ($|C(i)|$ bytes)}}								\\ \cline{1-3}
+ ROSS-DGA, ROSS-$\delta$-DGA 	&$\mathcal{O}(N^3)$ (worst case)		&   $h+2*m^2d$ (upper bound)  				&   \multirow{2}{*}{\parbox{6.4cm}{Cluster head broadcasts cluster composition ($|C(i)|* |\mathcal{K}|$ bytes).
+Cluster members broadcast the manipulated new individual connectivity degree (1 byte)}}								\\ \cline{1-3}
  ROSS-DFA, ROSS-$\delta$-DFA 	&$\mathcal{O}(N)$ (worst case)		&   $h + 2m$	 (upper bound) 					& 	      												\\ \hline
@@
 \begin{algorithm}              % enter the algorithm environment
-\caption{ROSS phase I: cluster head determination and initial cluster formation for Unclustered CR node $i$}          % give the algorithm a caption
+\caption{ROSS phase I: cluster head determination and initial cluster formation for CR node $i$}          % give the algorithm a caption
 \label{alg0} 
@@
 To simplify the discussion, we assume the secondary users have unique individual connectivity degrees. 
-Each user has an identical ID and a social connectivity degree.
-This assumption is fair as the social connectivity degrees and node ID are used to break ties in Algorithm~\ref{alg0}, when the individual connectivity degrees are unique, it is not necessary to use the former two metrics.
+Each user has an identical ID and a neighborhood connectivity degree.
+This assumption is fair as the neighborhood connectivity degrees and node ID are used to break ties in Algorithm~\ref{alg0}, when the individual connectivity degrees are unique, it is not necessary to use the former two metrics.
 %(COMMENT: What do you mean by breaking ties??

### 2016-09-25 journal-draft/bare_jrnl_comsoc.tex
before changing ccc to cc

@@
 %
-In this hierarchical spectrum access model~\cite{zhao_survey_DSA_2007}, the licensed users are also called primary users (PU), while the unlicensed users are referred to as secondary users and constitute the cognitive radio networks (CRN).
+In this hierarchical spectrum access model~\cite{zhao_survey_DSA_2007}, the licensed users are also called primary users (PU), while the unlicensed users are referred to as secondary users and constitute a so called cognitive radio network (CRN).
 %
 %cluster
-Regarding to the operation of CRN, efficient spectrum sensing is identified to be critical for a smooth operation of a cognitive radio network~\cite{Sahai_FundamentalDesignTradeoffs2006}.
+Regarding the operation of CRN, efficient spectrum sensing is identified to be critical for a smooth operation of a cognitive radio network~\cite{Sahai_FundamentalDesignTradeoffs2006}.
 This can be achieved by cooperative spectrum sensing of multiple secondary users, which has been shown to cope effectively with noise uncertainty and channel fading, thus remarkably improving the sensing accuracy~\cite{coorperativeSensing_Akyildiz11}.
@@
 %Furthermore, the clustering algorithm also determines the connectivity between several clusters which ultimately determines the robustness of the entire network on the respect of connectivity. 
-There is a trade-off between CCCs in the formation process and the collaborative sensing performance, as less members in a cluster yield in general a higher number of CCCs while this reduces the sensing accuracy~\cite{Consensus_based_clustering12}.
-In addition, there are other reasons that motivate clusters with more members.
+In the formation process, there is a trade-off between CCCs and the collaborative sensing performance, as less members in a cluster yield in general a higher number of CCCs while this reduces the sensing accuracy~\cite{Consensus_based_clustering12}.
+In addition, there are other reasons that motivate clusters to have more members.
 For example, instead of less members, the proper cluster size results in smaller power consumption~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
@@
 
-Before mentioning our proposed robust clustering scheme, we will look back briefly on the research about clustering in wireless networks.
+There has been a lot of research done for clustering in wireless networks.
 %Prior to the emergence of cognitive radio, clustering has been proposed as an important method to manage network ad-hoc networks~\cite{Kawadia03,Lin97adaptiveclustering,Basagni99}, wireless mesh networks\cite{clustering_mesh_globecom2010} and sensor networks~\cite{Abbasi_survey_07}.
@@
 %Clustering scheme~\cite{clustering_globecom11} obtains the best cluster size which minimizes power consumption caused by communication within and among clusters.
-\cite{clustering_globecom11, TWC2012_cooperative_communication} target on the QoS poisoning and energy efficiency.
-\cite{cluster_EW10} exploits the multiple CCCs in clusters after forming them.
+\cite{clustering_globecom11, TWC2012_cooperative_communication} target on the QoS provisioning and energy efficiency.
+\cite{cluster_EW10} forms clusters to coordinate the control channel usage within one cluster.
 A event-driven clustering scheme is proposed for cognitive radio sensor network in \cite{Ozger_cluster_crsn_13}.
@@
 %The cluster heads are selected according to node degree, spectrum availability and the distance to the sink, and the clusters are no longer available after the event ends.
-These schemes do not provide robustness to formed clusters against primary users.
+No one among the above mentioned schemes provides the robustness to the formed clusters against primary users.
 
@@
 
-A clustering scheme (denoted by SOC) which is commited to generate robust clusters against primary users is proposed in~\cite{LIU_TMC11_2}.
+A clustering scheme (denoted by SOC) which is designed to generate robust clusters against primary users is proposed in~\cite{LIU_TMC11_2}.
 SOC involves three phases of distributed executions.
-In the first phase, every secondary user forms clusters with some one-hop neighbors, in the second and third phase, each secondary user seeks to either merger other clusters around it, or join one of them.
+In the first phase, every secondary user forms clusters with some one-hop neighbors, in the second and third phase, each secondary user seeks to either merge other clusters around it, or join one of them.
 The metric adopted by every secondary user in the three phases is the product of the the number of CCCs and cluster size (the number of secondary users in the cluster).
-To the best of our knowledge, SOC is the only work emphasizing on the robustness of clustering structure among the related works. 
-But this robust clustering scheme is inherently flawed.
+%To the best of our knowledge, SOC is the only work emphasizing on the robustness of clustering structure among the related works. 
+But this robust clustering scheme has some drawbacks.
 Although the adopted metric covers both cluster size and the number of CCCs, the formation of certain clusters may be easily dominated by only one factor, e.g.
@@
 %The first two propose a distributed scheme where the metric is the product of cluster size and the number of common control channels.
-\cite{mansoor_15_cluster_robust} presents a heuristic method to form clusters, although the authors claim robustness is one goal to achieve, they actually uphold the minimum number of formed clusters.
-
-In this paper, a decentralized clustering approach ROSS (RObust Spectrum Sharing) is proposed to cover the issues of robustness and size control of clusters in CRN.
-ROSS is able to form clusters with desired sizes, and when compared with previous works, ROSS involves smaller signalling overhead, and the generated clusters are significantly more robust against the primary users which appear after the clusters are formed.
+\cite{mansoor_15_cluster_robust} presents a heuristic method to form clusters, although the authors claim robustness is one goal to achieve, the minimum number of clusters is pursued.
+\cite{Li11_ROSS} proposes a distributed clustering scheme under the game theoretic framework. 
+Compared with the clustering schemes introduced so far, the clusters are formed in shorter time and posses more CCCs within and among clusters.
+But this scheme doesn't consider the the factor of size in the algorithm design.
+
+In this paper we will give a comprehensive analysis of the robust clustering problem and propose solutions. 
+We stick to the motivation of forming robust clusters in CRN \ie let more CR users benefited from the cooperative decision making which is due to the clusters. 
+We propose both centralized and distributed clustering schemes, which result in more CR users in the clusters composed with multiple CR users, not only when the clusters are just formed, but also afterwards when the primary users' activity changes.
+Besides, both centralized and distributed schemes take the cluster size into consideration, and both can control the sizes of the formed clusters to certain extent.
+In particular, the decentralized clustering approach ROSS (RObust Spectrum Sharing) is able to form clusters with desired sizes.
+When compared with other distributed works, ROSS involves smaller signaling overhead and the generated clusters are significantly more robust against the primary users which appear after the clusters are formed.
 %thesis
@@
 %For our scheme we can prove convergence in cluster formation phase and resolve ambiguities with respect to cluster membership in a game-theoretic setting. 
-We also propose the light weighted versions of ROSS, which involve less overheads and thus are more suitable for fast deployment.
+We also propose the light weighted versions of ROSS, which involve less overheads and thus are more suitable for the scenario where fast deployment is desired.
 Throughout this paper, we refer the clustering schemes on the basis of ROSS as \textit{variants of ROSS}, \ie the fast versions, or that with size control feature.
@@
 Extensive performance evaluation is presented in Section~\ref{performance}.
-Finally, we conclude our work and point out the direction for the future research in Section~\ref{conclusion}.
+Finally, we conclude our work and point out the direction for future research in Section~\ref{conclusion}.
 
@@
 %These users share a number of non-overlapping licensed channels according to the spectrum overlay model. 
-The CR users opportunistically a set of licensed channels, which is denoted as $\mathcal{K}$. 
+The CR users use a set of licensed channels opportunistically, which is denoted as $\mathcal{K}$. 
 The CR users are allowed to transmit on channel $k \in \mathcal{K}$ only if no primary user is detected on channel $k$. 
@@
 %The sensing duration and frequency on one channel is a research topic~\cite{sensing_survey_2009}, and 
-We assume that every node can detect the presence of primary user on each channel with certain accuracy.
+We assume that every node can detect the presence of a primary user on each channel with certain accuracy.
 \footnote{The spectrum availability can be validated with a certain probability of detection.
@@
 %Both primary users and CR users have fixed transmission ranges respectively, and all the channels are regarded to be identical in terms of signal propagation.
-If a CR node locates within the transmission range of primary user which is working, that CR node is not allowed to use the channel which is being used by that primary user.
+If a CR node locates within the transmission range of an active primary user, that CR node is not allowed to use the channel which is being used by that primary user.
 %In our system model, we assume that a secondary node $n$ is able to detect for each channel $c$ whether any primary user utilizes $c$.
@@
 %
-If a secondary user $i$ is not in the transmission range of a primary user $p$, $i$ can certainly not detect the presence of $p$.
-As the transmission range of primary users is limited and secondary users are located at different locations, different secondary users may have different views of the spectrum availability, i.e., for any $i, j \in \mathcal{N}$, $K_i = K_{j}$ does not necessarily hold.
+If a secondary user $i$ is not in the transmission range of an active primary user $p$, $i$ can certainly not detect the presence of $p$.
+As the transmission range of primary users is limited and secondary users have different locations, different secondary users may have different views of the spectrum availability, i.e., for any $i, j \in \mathcal{N}$, $K_i = K_{j}$ does not necessarily hold.
 %
@@
 %\end{itemize}
-A cluster $C \subseteq \mathcal{N}$ is a set of secondary nodes consisting of a cluster head $h_C$ and a number of cluster members.
+A cluster $C$ is a set of secondary nodes consisting of a cluster head $h_C$ and a number of cluster members.
 The cluster head is able to communicate with any cluster member directly.
@@
 
-Cluster is denoted as $C(i)$ when its cluster head is $i$.
+In this paper, sometimes we need to mention a cluster with the information of its cluster head \ie a cluster is denoted as $C(i)$ where $i$ is its cluster head.
 Cluster size of $C(i)$ is written as $|C(i)|$.
@@
 $ K(C) = \cap_{i\in C} K_i$, $K(C)$ denotes the set of common control channels in cluster $C$.
-Clustering is performed periodicity, as secondary users are mobile and the channel availability on secondary users are changing as primary users change their operation state.%, or the most current clusters can not maintain due to lack of CCCs when primary users' operation is intense.
+Clustering is performed periodically, as secondary users are mobile and the channel availability on secondary users are changing as primary users change their operation state.%, or the most current clusters can not maintain due to lack of CCCs when primary users' operation is intense.
 
@@
 
-The autonomous decisions of the debatable CR nodes' raise the concern on the endless chain effect.
-For instance,
-
-debatable nodes may never stop changing their affiliations, because a debatable nodes' choice is based on the members of its claiming clusters, and the members are changed by other debatable nodes' choices.
-%In a word, debatable nodes' choices on cluster affiliation are dependent on each other, thus there could be an infinite chain effect in the process of membership clarification.
+The autonomous decisions made by the debatable CR nodes raise the concern on the endless chain effect in the membership clarification phase.
+A debatable node's choice is dependent on the compositions of its claiming clusters, which can be changed by other debatable nodes' decisions.
+As a result, the debatable node which makes decision first may change its original choice, and this process may go on forever.
+To erase this concern, we formulate the process of membership clarification into a game, where a equilibrium is reached after a finite number of best response updates made by the debatable nodes.
+
 %%  update their choices based on other debatable nodes' choices, and this process 
@@
 
-In the following we show that the process of membership clarification can be formulated into a game, and a equilibrium is reached after a finite number of best response updates made by the debatable nodes.
-
 \subsubsection{Bridging ROSS-DGA with Congestion Game}
@@
 %The convergence speed of DGA is large recalling that the number of steps is of $\mathcal{O}(N^3)$.
-We propose a faster version of ROSS, ROSS-DFA, which differs from ROSS-DGA in the second phase.
+On the basis of ROSS-DGA, we propose a faster version ROSS-DFA which differs from ROSS-DGA in the second phase.
 With ROSS-DFA, debatable nodes decide their respective cluster heads once.
@@
 \item ROSS-$\delta$-DGA and ROSS-$\delta$-DFA, which are the variants of ROSS with the size control feature.
-$\delta$ is the desired cluster size.
+$\delta$ is the preferred cluster size.
 \item SOC~\cite{LIU_TMC11_2}, a distributed clustering scheme pursuing cluster robustness.
@@
 The centralized schemes produce no unclustered CR nodes, ROSS-DGA/DFA generate 3\% unclustered nodes, as comparison, 10\% of nodes are unclustered when applying SOC.
-ROSS-DGA and ROSS-DFA with size control feature generate 5\%-8\% unclustered CR nodes, which is due to the cluster pruning procedure (discussed in section~\ref{cluster_pruning}).
+ROSS-DGA and ROSS-DFA with size control feature generate 5\%-8\% unclustered CR nodes, which is due to the cluster pruning procedure (discussed in section~\ref{ross_p1_guarantee_ccc} and section~\ref{ross_p2_cluster_pruning}).
 Second, the centralized schemes and cluster size control mechanism of RPSS generate clusters which satisfy the requirement on cluster size strictly.
@@
 According to~\cite{complexity_aggregation_2011}, the message complexity is defined as the number of messages used by all nodes.
-To have the same criterion to compare, we count \textit{the number of transmissions of control messages}, without distinguishing they are sent with broadcast or unicast.
+To have the same metric to compare, we count \textit{the number of transmissions of control messages}, without distinguishing they are sent with broadcast or unicast.
 This metric is synonymous with \textit{the number of updates} discussed in Section~\ref{ross}.
@@
  ROSS-DFA, ROSS-$\delta$-DFA 	&$\mathcal{O}(N)$ (worst case)		&   $h + 2m$	 (upper bound) 					& 	      												\\ \hline
- SOC 					&$\mathcal{O}(N)$		&   $3*N$									& $C(i)$ ($|C(i)|$ bytes), $K(C(i))$ ($|\mathcal{P}|$ bytes), $i\in \mathcal{N}$						\\ \hline
+ SOC 					&$\mathcal{O}(N)$		&   $3*N$									& $C(i)$ ($|C(i)|$ bytes) and $K(C(i))$ ($|\mathcal{P}|$ bytes), $i\in \mathcal{N}$						\\ \hline
  Centralized			&$\mathcal{O}(N)$			&	$h + m + N$ (upper bound)~\cite{Efficient_broadcasting_gathering_adhoc}		& $\{C\}$ ($|C_i|*N$ bytes)        					\\ \hline
@@
 
-\subsection{Comparison between Distributed Schemes}
+\subsection{Comparison among the Distributed Schemes}
 \label{largeScaleCRN}
@@
 Figure~\ref{nClusters_largeNetwork} shows when the network density scales up, the number of formed clusters by ROSS increases by smaller margin, and that generated by SOC increases linearly.
-This result coincides with the analysis in Section~\ref{cluster_pruning}.
+This result coincides with the analysis in Section~\ref{ross_p2_cluster_pruning}.
 %When the network becomes denser, more clusters are generated by SOC compared with ROSS variants.
@@
 \label{conclusion}
-In this paper we investigate the robust clustering problem in CRN extensively, in order to generate robust clusters against primary users' influence, so that more CR users can benefit from operative decision making provided by the clusters.
-We provide the mathematical description of the problem, and propose both centralized and distributed schemes.
-We prove the NP hardness of this problem, and the congestion game model in game theory is used to design the distributed scheme.
-A Light weighted clustering scheme ROSS is also proposed.
-Through simulation and theoretical analysis, we find that distributed schemes achieve similar performance with centralized optimization in terms of cluster robustness, signalling overhead and cluster sizes, and outperform the comparison distributed scheme on the above mentioned metrics.
+In this paper we investigate the robust clustering problem in CRN extensively.
+The proposed scheme results in a cluster structure in CRN, which has longer time expectancy against the primary users' activity.
+Besides, the clusters generated have similar sizes compared with other distributed schemes.
+%generate robust clusters against primary users' influence, so that more CR users can benefit from operative decision making provided by the clusters.
+We provide the mathematical description of the problem and prove the NP hardness of it.
+We propose both centralized and distributed schemes, where the congestion game model in game theory is used to design the distributed schemes.
+%A Light weighted clustering scheme ROSS is also proposed.
+Through simulation and theoretical analysis, we find that distributed schemes achieve similar performance with centralized optimization in terms of cluster robustness, signaling overhead and cluster sizes, and outperform the comparison distributed scheme on the above mentioned metrics.
 %, which is important to form clusters which maintains unbroken to the greatest extent possible under primary users' activity.
@@
 
-The shortage of ROSS scheme is it doesn't generate big clusters whose sizes exceed the cluster head's neighbourhood.
-This problem is attributed to fact that ROSS forms clusters on the basis of cluster head's neighbourhood, and doesn't involve interaction with the nodes outside its neighbourhood.
-In the other way around, forming big cluster which extends a cluster head's neighbourhood has limited applications, as multiple hop communication and coordination are required within such clusters.
+The shortage of ROSS scheme is it doesn't generate big clusters whose sizes exceed the cluster head's neighborhood.
+This problem is attributed to fact that ROSS forms clusters on the basis of cluster head's neighborhood, and doesn't involve interaction with the nodes outside its neighborhood.
+In the other way around, forming big cluster which extends a cluster head's neighborhood has limited applications, as multiple hop communication and coordination are required within such clusters.
 

### 2016-09-26 journal-draft/bare_jrnl_comsoc.tex
modified the centralised section

@@
 To form a cluster which is composed by the CR users, there should be channels available for communication within the cluster.
-Usually there are multiple unlicensed channels available for all the CR nodes in the cluster, which are referred to in the following of this paper as \textit{common control channels} (CCC).
-Out of the available CCCs, there are always one or multiple channels which are used for the payload communication.
+Usually there are multiple unlicensed channels available for all the CR nodes in the cluster, which are referred to in the following of this paper as \textit{common licensed channels} (or common channels for short, which is abbreviated as CC).
+Out of the available CCs, there are always one or multiple channels which are used for the payload communication.
 %The communication within a cluster is conducted in the spectrum which is available for every member in that cluster.
-When one or several cluster members can not use one certain CCC for example because primary user activity has been detected on that channel, it will be excluded from the set of CCCs.
-If the channel is being used for payload communication, all the cluster members will switch to another channel in the set of available CCCs to achieve seamless transmission.
-As long as there is a CCC available, the corresponding cluster can continue to exchange payload data.
-In the context of CRN, as the activity of primary users is unknown to the secondary users, the availability of CCCs of the formed clusters is totally dependent on primary users' activity.
-Thus, the clusters with more CCCs are in general better as this anticipates a longer time span that payload can be exchanged.
-In this paper the robustness of a cluster against primary users is synonymous with the affluence of CCCs which are possessed by that cluster. 
-%In other words, the availability of CCCs of the formed clusters is passive and can not be guaranteed.
-%Thus, the number of CCCs in one formed cluster indicates the robustness of it when facing the unpredictable influence from primary users.
-%In CRN, one cluster survives the influence of primary users when at least one CCC is available in that cluster.
-%As the primary users' operation is assumed to be unknown to the CR users, a cluster formed with more CCCs will survive with higher probability.
-
-%It is easy to see that forming clusters with different neighbours leads to different amount of CCCs in the clusters.
+When one or several cluster members can not use one certain CC for example because primary user activity has been detected on that channel, it will be excluded from the set of CCs.
+If the channel is being used for payload communication, all the cluster members will switch to another channel in the set of available CCs to achieve seamless transmission.
+As long as there is a CC available, the corresponding cluster can continue to exchange payload data.
+In the context of CRN, as the activity of primary users is unknown to the secondary users, the availability of CCs of the formed clusters is totally dependent on primary users' activity.
+Thus, the clusters with more CCs are in general better as this anticipates a longer time span that payload can be exchanged.
+In this paper the robustness of a cluster against primary users is synonymous with the affluence of CCs which are possessed by that cluster. 
+%In other words, the availability of CCs of the formed clusters is passive and can not be guaranteed.
+%Thus, the number of CCs in one formed cluster indicates the robustness of it when facing the unpredictable influence from primary users.
+%In CRN, one cluster survives the influence of primary users when at least one CC is available in that cluster.
+%As the primary users' operation is assumed to be unknown to the CR users, a cluster formed with more CCs will survive with higher probability.
+
+%It is easy to see that forming clusters with different neighbours results in different number of CCs in the clusters.
 %As a result, how to form the clusters plays an important role on the robustness of clusters in CRN.
 %Furthermore, the clustering algorithm also determines the connectivity between several clusters which ultimately determines the robustness of the entire network on the respect of connectivity. 
-In the formation process, there is a trade-off between CCCs and the collaborative sensing performance, as less members in a cluster yield in general a higher number of CCCs while this reduces the sensing accuracy~\cite{Consensus_based_clustering12}.
+In the formation process, there is a trade-off between CCs and the collaborative sensing performance, as less members in a cluster yield in general a higher number of CCs while this reduces the sensing accuracy~\cite{Consensus_based_clustering12}.
 In addition, there are other reasons that motivate clusters to have more members.
@@
 %Apparently this contradicts our motivation of proposing cluster in cognitive radio network to enable cooperative decision making.
-Thus the cluster robustness discussed in terms of number of CCCs carries little meaning when the sizes of formed clusters are not given consideration.
+Thus the cluster robustness discussed in terms of number of CCs carries little meaning when the sizes of formed clusters are not given consideration.
 
@@
 %\cite{clustering_globecom11} proposes clustering strategy in cognitive radio network, which looks into the relationship between cluster size and power consumption and accordingly controlling the cluster size to decrease power consumption.
-The clustering schemes proposed in~\cite{Zhao07, Chen07,Affinity_clustering_09icccn} form clusters which meet the basic condition, having CCC in every cluster.
+The clustering schemes proposed in~\cite{Zhao07, Chen07,Affinity_clustering_09icccn} form clusters which meet the basic condition, having CC in every cluster.
 Clustering scheme~\cite{Consensus_based_clustering12} improves spectrum sensing accuracy.
@@
 In the first phase, every secondary user forms clusters with some one-hop neighbors, in the second and third phase, each secondary user seeks to either merge other clusters around it, or join one of them.
-The metric adopted by every secondary user in the three phases is the product of the the number of CCCs and cluster size (the number of secondary users in the cluster).
+The metric adopted by every secondary user in the three phases is the product of the the number of CCs and cluster size (the number of secondary users in the cluster).
 %To the best of our knowledge, SOC is the only work emphasizing on the robustness of clustering structure among the related works. 
 But this robust clustering scheme has some drawbacks.
-Although the adopted metric covers both cluster size and the number of CCCs, the formation of certain clusters may be easily dominated by only one factor, e.g.
+Although the adopted metric covers both cluster size and the number of CCs, the formation of certain clusters may be easily dominated by only one factor, e.g.
 a node which is able to use many channels will exclude its neighbor and form a cluster by itself.
@@
 In addition, this scheme leads to the high variance of the cluster sizes, which is not desired in certain applications as discussed in~\cite{clustering_globecom11, cluster_EW10}.
-%The first two propose a distributed scheme where the metric is the product of cluster size and the number of common control channels.
+%The first two propose a distributed scheme where the metric is the product of cluster size and the number of common channels.
 \cite{mansoor_15_cluster_robust} presents a heuristic method to form clusters, although the authors claim robustness is one goal to achieve, the minimum number of clusters is pursued.
 \cite{Li11_ROSS} proposes a distributed clustering scheme under the game theoretic framework. 
-Compared with the clustering schemes introduced so far, the clusters are formed in shorter time and posses more CCCs within and among clusters.
+Compared with the clustering schemes introduced so far, the clusters are formed in shorter time and posses more CCs within and among clusters.
 But this scheme doesn't consider the the factor of size in the algorithm design.
@@
 
-\section{System Model}
+\section{System Model and Problem Formulation}
 \label{sec:model}
@@
 %The sensing duration and frequency on one channel is a research topic~\cite{sensing_survey_2009}, and 
-We assume that every node can detect the presence of a primary user on each channel with certain accuracy.
+We assume that every node can detect the presence of an active primary user on each channel with certain accuracy.
 \footnote{The spectrum availability can be validated with a certain probability of detection.
@@
 
-We assume that in addition to the licensed channels, there is one dedicated control channel.
+We assume there is one dedicated control channel which is used to exchange signaling messages during clustering process.
 This control channel could be one of the ISM bands or other reserved spectrum which is exclusively used for transmitting control messages.
@@
 In the following, we refer to the word \textit{channel} in general as licensed channel, unless we mention the control channel explicitly. 
-
-%Primary users also have fixed transmission range on the licensed channels\footnote{This assumption is made to simplify the discussion, and doesn't affect the effectiveness of the proposed scheme}.
-
-%As to a pair of secondary users, when the Euclidean distance between them is smaller than secondary users' transmission range, we assume the pair is able to communicate on both control channel and licensed channel, and the both are considered to be neighbours of each other.
-DEFINE DISTANCE!
-\textcolor{brown}{distance, done}
+%
 %
@@
 %%The clustering phase is initialized during which any control message is again conveyed by the control channel.
-%In the rest of this paper, \textit{channel} only refers to the licensed common control channel unless the dedicated control channel is particularly mentioned.
+%In the rest of this paper, \textit{channel} only refers to the licensed common channel unless the dedicated control channel is particularly mentioned.
 Then, a cognitive radio network can be represented as a graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{i, j\} \in E$  if, and only if, there exists a channel $k \in \mathcal{K}$ with $k \in K_{i} \cap K_{i'}$.
@@
 
-\section{Robust Clustering Problem in CRN}
-\label{problem}
-In this section, we present the definition of cluster in the context of CRNs, define the clustering problem and discuss its complexity.
-
-\subsection{Cluster in CRN}
-\label{def_cluster}
+%In this subsection, we present the definition of cluster in the context of CRNs, define the clustering problem and discuss its complexity.
 %We give the description of cluster in the context of CRN, all the clusters discussed in this paper comply with it.
@@
 %\item Cluster head $H_C$ is able to communicate with any cluster member \textit{directly}, \ie for any cluster member $i\in C$, there is $i\in \texttt{Nb}_{H_C}$.
-%\item There exists as least one common control channel in the cluster, \ie $\cap_{i\in C} V_i \neq \emptyset$.
+%\item There exists as least one common channel in the cluster, \ie $\cap_{i\in C} V_i \neq \emptyset$.
 %\end{itemize}
-A cluster $C$ is a set of secondary nodes consisting of a cluster head $h_C$ and a number of cluster members.
+A cluster $C$ is a set of secondary nodes, which consists a cluster head $h_C$ and a number of cluster members.
 The cluster head is able to communicate with any cluster member directly.
 In other terms, for any cluster member $i \in C$, $i \in \text{Nb} (h_C) $ holds.
-
+%
 %A cluster head coordinates the activities of cluster members, \ie it notifies all the members to vacate a channel if a primary user's presence is detected by one cluster member.
-Further it also notifies the members to use a different common control channel for payload communication.
+Further it also notifies the members to use a different common channel for payload communication.
 %(\textcolor{red}{(Not clear what the meaning of payload communication is.
@@
 Thus I think it is necessary to leave it here.}
-
+%
+%
 In this paper, sometimes we need to mention a cluster with the information of its cluster head \ie a cluster is denoted as $C(i)$ where $i$ is its cluster head.
 Cluster size of $C(i)$ is written as $|C(i)|$.
-%, for the sake of concision, $C_i$ is also named as cluster $i$ in the following part of this paper.
-$ K(C) = \cap_{i\in C} K_i$, $K(C)$ denotes the set of common control channels in cluster $C$.
-Clustering is performed periodically, as secondary users are mobile and the channel availability on secondary users are changing as primary users change their operation state.%, or the most current clusters can not maintain due to lack of CCCs when primary users' operation is intense.
-
-%We propose distributed scheme ROSS to form clusters to generate robust clusters, and in the same time clusters have preferred sizes, \ie fewer number of singleton clusters (the cluster which consist with only one CR node) compared with state of art.
-
-%Besides, cluster size is also considered in to clustering solution.
-%Size preference can be met after minor modifications on ROSS.
-
-%The metric is summation of the number of channels available to be used for each node when they reside in a certain cluster, together with a cost for not following the desired cluster size, \ie when the desired cluster size is $\delta$ and the other cluster sizes are denoted as $\delta'$, the metric is,
-%\begin{equation}
-%\label{metric}
-%\sum_{i=1}^{N}(ICC_i)
-%\end{equation}
-%$N$ is the number of CR nodes in the network.
-
-%Also, we refer to the common channels between neighbouring clusters by the term \textit{outward common channels} (OCC).
-We define the set of OCCs of cluster $C$ to be the set of available common channels between any member of $C$ and any other CR user of a neighbouring cluster:
-%\begin{equation}
-%\label{numocc}
-%R_{C}=\bigcup_{j\in C, k\in N_j, k\notin C}(V_{j}\cap V_{k})
-%\end{equation}
-
-%In the process of clustering, when there is no restriction on cluster size, the metric will only be the summation of the number of channels for each node when they reside in a certain cluster.
-%When we try to maximize the summation of ICCs, an obvious correlation between cluster size and number of ICCs is encountered, \ie when each node constitutes one cluster, the aforementioned metric will be maximized.
-%The goal of the proposed clustering scheme is to let as more CR nodes as possible to form clusters, meanwhile the clusters have more common channels and preferred cluster size.
-
-%\textcolor{red}{The notation is not well chosen.
-Does it make sense to have only one letter for a potential cluster?
-What happens if we have two clusters?
-Find some comments next to your proposed notation.}
-
+$ K(C) = \cap_{i\in C} K_i$, $K(C)$ denotes the set of common licensed channels in cluster $C$.
+Clustering is performed periodically, as secondary users are mobile and the channel availability on secondary users are changing as primary users change their operation state.%, or the most current clusters can not maintain due to lack of CCs when primary users' operation is intense.
+
+The notations used in the system model and the following problem description are listed in the Table~\ref{tab1}.
 \begin{table}[h!]
@@
 $K_i$   & the set of available channels at CR node $i$  \\
-$K(C(i))$   & the set of available CCCs of cluster $C(i)$ \\
+$K(C(i))$   & the set of available CCs of cluster $C(i)$ \\
 %$h(C)$ & cluster head of a cluster $C$\\
@@
 $g_i$  & neighborhood connectivity degree of CR node $i$\\
-$C_i$  & the $i$th potential cluster (only used in Sec.~\ref{centralized_opt})\\
+$f(C)$ & the number of CCs of a cluster $C$, which is used \\
+& in the problem description\\
+$C_i$  & the $i$th potential cluster in a collection of clusters \\
 \bottomrule
@@
 
-\subsection{Robust Clustering Problem}
-\label{centralized_scheme}
-
+%We propose distributed scheme ROSS to form clusters to generate robust clusters, and in the same time clusters have preferred sizes, \ie fewer number of singleton clusters (the cluster which consist with only one CR node) compared with state of art.
+
+%Besides, cluster size is also considered in to clustering solution.
+%Size preference can be met after minor modifications on ROSS.
+
+%The metric is summation of the number of channels available to be used for each node when they reside in a certain cluster, together with a cost for not following the desired cluster size, \ie when the desired cluster size is $\delta$ and the other cluster sizes are denoted as $\delta'$, the metric is,
+%\begin{equation}
+%\label{metric}
+%\sum_{i=1}^{N}(ICC_i)
+%\end{equation}
+%$N$ is the number of CR nodes in the network.
+
+%Also, we refer to the common channels between neighbouring clusters by the term \textit{outward common channels} (OCC).
+We define the set of OCCs of cluster $C$ to be the set of available common channels between any member of $C$ and any other CR user of a neighbouring cluster:
+%\begin{equation}
+%\label{numocc}
+%R_{C}=\bigcup_{j\in C, k\in N_j, k\notin C}(V_{j}\cap V_{k})
+%\end{equation}
+
+%In the process of clustering, when there is no restriction on cluster size, the metric will only be the summation of the number of channels for each node when they reside in a certain cluster.
+%When we try to maximize the summation of ICCs, an obvious correlation between cluster size and number of ICCs is encountered, \ie when each node constitutes one cluster, the aforementioned metric will be maximized.
+%The goal of the proposed clustering scheme is to let as more CR nodes as possible to form clusters, meanwhile the clusters have more common channels and preferred cluster size.
+
+%\textcolor{red}{The notation is not well chosen.
+Does it make sense to have only one letter for a potential cluster?
+What happens if we have two clusters?
+Find some comments next to your proposed notation.}
+
+\subsection{Robust Clustering Problem in CRN}
+\label{problem}
 %paper given by james is useful which provides a survey from the perspective of wsn!
-
-The clustering scheme we propose in the paper aims to form clusters with preferred sizes, meanwhile maximize the average number of CCCs per cluster.
-%In the following, we refer this problem as \textit{centralized clustering}. 
+As introduced in the section of introduction, in order to be robust against primary users' activity, the formed clusters should have more CCs to expect longer time expectancy.
+Meanwhile, the sizes of the formed clusters should not diverge from the desired size too much, and there are two reasons.
+First, the generation of the \textit{singleton clusters}, \ie the cluster which has only one CR node, should be avoided, because it contradicts the motivation of forming clusters thus the benefits brought in by the collective of the cluster members are compromised.
+Second, Large clusters are not preferred in some scenarios neither, \eg for the CRN composed with resource limited users, managing the cluster members is a substantial burden. 
+Hence, the cluster size should fall in a desired range according to different application scenarios~\cite{Chen04clusteringalgorithms, capacity_cluster_06}.
+Considering the above mentioned requirements on the formed clusters, we will present the definition of robust clustering problem as follows.
+%The clustering scheme we propose in the paper aims to form clusters with preferred sizes, meanwhile maximize the average number of CCs per cluster.
 %We have mentioned that the sizes of the formed clusters should be given consideration, which is import for the discussion on cluster robustness, \ie 
-when perusing the cluster robustness without specifying the requirement on cluster sizes, a clustering method will be inclined to form small clusters.
-In that case, although more CCCs are obtained per cluster, the benefits brought in by the collective of the cluster members are compromised.
+%When perusing the cluster robustness without specifying the requirement on cluster sizes, a clustering method will be inclined to form small clusters.
+%In that case, although more CCs are obtained per cluster, the benefits brought in by the collective of the cluster members are compromised.
 %Except for cooperative sensing, clusters need to conduct some other functionalities.
-Large clusters are not preferred in some scenarios neither, \eg for the CRN composed with resource limited users, managing the cluster members is a substantial burden. 
-Hence, the cluster size should fall in a desired range~\cite{Chen04clusteringalgorithms, capacity_cluster_06}.
-In the following, we present the formal definition of robust clustering problem.
 
@@
 
-Given a cognitive radio network $\mathcal{N}$ where $|\mathcal{N}|=N$, secondary users are indexed from 1 to $N$.
-A cluster $C$ can be composed with one or multiple secondary users when $|K(C)|>0$, and any two cluster members can communicate either directly, or through other members belonging to the same cluster.
-We use $f(C)$ to denote the number of CCCs of a cluster $C$, and give it a new definition as follows, the number of common control channels is $f(C) = |K(C)|$ if $|C|>1$, and $f(C)=0$ when $|C|=1$.
-The size of cluster $C$ is not bigger than a positive integer $k$.
-The collection of such clusters $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$, satisfies the following condition: $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$ and $1\leq i \leq |\mathcal{S}|$.
-
-%, which distinguishes the centralized clustering problem discussed in this paper.
-
-The robust clustering problem is to find a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, so that $\sum_{C\in \mathcal{S}'} f(C)$ is maximized, and $\mathcal{S}'$ satisfies the following conditions, $\bigcup_{C_j\in \mathcal{S}'} C_j = \mathcal{N}$ and $C_{j'}\cap C_j =\emptyset$ where $C_{j'}, C_j\in \mathcal{S}'$ and $j'\neq j$.
+Given a cognitive radio network $\mathcal{N}$ where $|\mathcal{N}|=N$,  the secondary users are indexed from 1 to $N$.
+A cluster $C$ is formed when first, it is composed with one or multiple secondary users and there is $|K(C)|>0$, second, any two cluster members can communicate either directly, or through other members which belong to the same cluster.
+The collection of all the possible clusters in $\mathcal{N}$ is denoted as $\mathcal{S}$, there is $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$ where $C_i$ is the $i$ th cluster in $\mathcal{S}$\footnote{The sequence of the clusters can be decided in any convenient way \ie the sequence of identifying them.}.
+%the clustering solution will be composed by the elements of $\mathcal{S}$. 
+As to $\mathcal{S}$, there is $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$.
+
+To formulate the problem, we propose a new definition for the number of CCs in a cluster.
+We use $f(C_i)$ to denote the number of CCs of a cluster $C_i\in \mathcal{S}$, which is as follows,
+%and the number of common licensed channels is $f(C_i) = |K(C_i)|$ if $|C_i|>1$, and $f(C_i)=0$ when $|C_i|=1$.
+$$
+f(C_i) = \left\{ \begin{array}{rl}
+|K(C_i)| 	&\mbox{$|C_i|>1$} \\
+0 				&\mbox{$|C_i|=1$} \\
+\end{array} \right.
+$$
+
+%The size of cluster $C$ is not bigger than a positive integer $k$.
+%Then the sum of the number of CCs of the formed clusters is $\sum_{C\in \mathcal{S}'} f(C)$
+
+Then the robust clustering problem is to find a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, so that the sum of the numbers of CCs of the formed clusters $\sum_{C\in \mathcal{S}'} (f(C)\cdot|C|)$ is maximized.
+Besides, the formed clusters should satisfy the requirements on cluster sizes, for example, all the formed clusters should have the same desired size $\delta$, or the sizes should be within a scope $\langle\delta_1, \delta_2\rangle$, where $\delta, \delta_1, \delta_2\in \mathbb{Z}^+$, and $\delta_1 < \delta_2$.
+According to the new definition of the number of CCs in a cluster, the singleton clusters in $\mathcal{S'}$ don't contribute to the value to be maximized.
+
+A clustering solution is a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, which satisfies the following conditions, $\bigcup_{C_i\in \mathcal{S}'} C_i = \mathcal{N}$ and $C_{i'}\cap C_i =\emptyset$ when $C_{i'}, C_i\in \mathcal{S}'$ and $i'\neq i$.
+
 % when $|C|>1$, and $f(\cdot)=0$ when $|C|=1$.
@@
 
-\subsection{Complexity of the Robust Clustering Problem}
-%In this section we investigate the complexity of robust clustering problem.
-Based on Definition~\ref{def_centralized_clustering}, the decision version of this problem is to ask whether there exists a no-empty $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C\in \mathcal{S}'} f(C) \geqslant \lambda$ where $\lambda$ is a real number.
+\section{Centralized Solution for Robust Clustering}
+\label{centralized_opt}
+
+Based on Definition~\ref{def_centralized_clustering}, the decision version of this problem is to determine whether there exists a non-empty $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C\in \mathcal{S}'} f(C) \geqslant \lambda$ where $\lambda$ is a real number and $C$ is a cluster.
 We have the following theorem on complexity.
@@
 \label{theorem1}
-Robust clustering problem in CRN is NP-hard, when the maximum size of clusters $k\geqslant 3$.
+Robust clustering problem in CRN is NP-hard, when the maximum size of clusters is larger than 3.
 %Assume a CRN can be represented by a connected graph, and there is at least one common channel between any pair of neighbours, then forming at least two CR nodes into one cluster is NP-complete.
@@
 The proof is in Appendix~\ref{proof_theorem1}.
-As it is not likely to generate clusters with size of 2, this theorem actually indicates that the robust clustering problem in CRN is NP-hard. 
-In the following sections, both centralized and distributed solutions will be introduced.
-
-\section{Centralized Solution for Robust Clustering}
-\label{centralized_opt}
+%This theorem actually indicates that the robust clustering problem in CRN is NP-hard.
+
+As the robust clustering problem in CRN is NP hard, there is no polynomial solution available.
+In this section, we will propose a centralized solution which approaches to the global optimal.
+The result will be used as a comparison with the proposed distributed schemes.
+%looks for the solution which approaches to the global optimum, and the latter is the solution which is more suitable for the practical implementation.
+%
 %Exact cover problem can be solved with Knuth's Algorithm X~\cite{dancingLinks_Knuth} as it finds out all the instances of exact cover, then we can choose the one with the biggest sum of weights. 
-As the robust clustering problem in CRN is NP hard, there is no polynomial solution available.
-In this paper we formulate the problem into a binary linear programming problem.
-To make the formulation possible, we adopt heuristics in both the objective function and the constraints, besides, the objective is not totally aligned with the object in the Definition~\ref{def_centralized_clustering}.
+%To make the formulation possible, we adopt heuristics in both the objective function and the constraints, besides, the objective is not totally aligned with the object in the Definition~\ref{def_centralized_clustering}.
+The problem by the Definition~\ref{def_centralized_clustering} is formulate into an optimization problem~\ref{centralized_opt} which is a binary linear programming problem.
 
@@
    &&& i\in \{1,2, \cdots G\}, \hspace{0.3cm} j\in \{1,2,\cdots N\}
-\notag
+%\notag
 \end{aligned}
+\label{centralized_opt}
 \end{equation}
 
-The objective is to maximize the sum of the products of cluster size and the corresponding number of CCCs.
-The second component is designed to be the \textit{punishment} for forming clusters whose sizes are not $\delta$, which is the preferred cluster size.
+The objective is to maximize the sum of the products of the size and the corresponding number of CCs of all the clusters.
+%The second component is designed to help generate the clusters whose sizes are the desired cluster size $\delta$.
 We minimize the opposite of the real objective to make this problem solvable.
-The constraints guarantee to obtain the clusters which don't overlap.
-Now we introduce the formulation in details.
-
-$N=|\mathcal{N}|, G=|\mathcal{G}|$.
-$\mathcal{G}$ is the collective of all the \textit{potential} clusters in a CRN $\mathcal{N}$, and the sizes of these clusters are $1,2,\ldots,\delta$, where $\delta$ is the preferred size for clusters.
+The constraints guarantee to obtain the clusters which together include all the CR users and don't overlap.
+
+The variables of this problem are $x_{ij}$ where $i\in \{1,2,\cdots,G-1, G\}$ and $j\in \{1,2,\cdots,N-1, N\}$.
+$N$ is the total number of CR users in network $\mathcal{N}$.
+$G = |\mathcal{G}|$ and $\mathcal{G}$ is the collective of clusters in a CRN $\mathcal{N}$, there is $\mathcal{G} \subseteq \mathcal{S}$, where $\mathcal{S}$ is the collection of all the possible clusters as described in Definition~\ref{def_centralized_clustering}.
+The subscript $i$ indicates the $i$th cluster in $\mathcal{G}$, and $j$ corresponds to the node ID of a CR node. 
+$x_{ij}$ indicates whether the CR node $j$ resides in the $i$th potential cluster, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$. 
+%
 %Given a CRN $\mathcal{N}$ and desired cluster size $\delta$, we obtain a collection of clusters $\mathcal{G}$ which contains all the \textit{potential} clusters, and the sizes of these clusters are $1,2,\ldots,\delta$.
-Potential clusters are the clusters which satisfy the conditions in Section~\ref{def_cluster}. 
-Note that the potential clusters include the \textit{singleton} ones, \ie the cluster which has only one CR node.
-By permitting the existence of the singleton clusters, we can ensure that the $\mathcal{S}'$ in Definition~\ref{def_centralized_clustering} is always be feasible.
-
-Constant $q_{ij}$ is the element of the constant $G\times N$ matrix $Q_{G\text{x}N}$ which is shown in Figure~\ref{costant_matrix_Q}. 
-The subscript $i$ is the index of a potential cluster, $j$ is the node ID of a CR node, $q_{ij}= |K(C_i)|$ when there is $j\in C_i$, and $q_{ij}= 0$ when there is $j\notin C_i$.
-In other words, each non-zero element $q_{ij}$ denotes the number of CCCs of the cluster $i$ where node $j$ resides.
-Knowing the meanings of subscripts $i$ and $j$, it is easy to notice there are $i\in \{1,2,\cdots,G-1, G\}$ and $j\in \{1,2,\cdots,N-1, N\}$.
-%
-The binary variable $x_{ij}$'s subscripts have the same meanings with that of $q_{ij}$, thus they have the same scope.
-$x_{ij}$ indicates whether the CR node $j$ resides in the potential cluster $i$, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$. 
-%
+%Potential clusters are the clusters which satisfy the conditions introduced in Section~\ref{sec:model}. 
+%Note that the potential clusters include the singleton ones.
+%By permitting the existence of the singleton clusters, we can ensure that the $\mathcal{S}'$ in Definition~\ref{def_centralized_clustering} is always be feasible.
+Based on the knowledge on $\mathcal{G}$, we construct a $G\times N$ matrix $Q_{G\text{x}N}$ which is shown in Figure~\ref{costant_matrix_Q}. 
+Constant $q_{ij}$ is the element of $Q_{G\text{x}N}$, and its subscripts correspond to the $i$th cluster and CR node $j$ respectively.
+$q_{ij}= |K(C_i)|$ when there is $j\in C_i$, and $q_{ij}= 0$ when there is $j\notin C_i$.
+In other words, each non-zero element $q_{ij}$ means the number of CCs of the cluster $i$ where node $j$ resides.
 
@@
 				G  	& |K(C_G)| & \cdots	 	& 		&  \vdots	& \cdots & \vdots& 		& \vdots \cr}	
-\caption{An example of Matrix $Q$, its rows correspond to all potential clusters, and columns correspond to the CR nodes in the CRN. }
+\caption{An example of Matrix $Q$, its rows correspond to all possible clusters, and columns correspond to the CR nodes in the CRN. }
 \label{costant_matrix_Q}
@@
 
-Now let us have a look at the objective function again.
-Although the related work SOC~\cite{LIU_TMC11_2} adopts the product of cluster size and number of CCCs as its sole metric, SOC still generates a large number of singleton clusters and a few large clusters.
-To refrain the clusters which don't have preferred clusters sizes, the second item is designed, where
+Now let us have a look at the second component in the objective function.
+%Although the related work SOC~\cite{LIU_TMC11_2} adopts the product of cluster size and number of CCs as its sole metric, SOC still generates a large number of singleton clusters and a few large clusters.
+To discourage the optimization algorithm from generating the clusters which don't have the preferred size, the second item compromises the first component in the objective function when those clusters are generated.
+$w_i$ is the auxiliary binary variable which denotes whether the $i$th  cluster $C_i$ is chosen by the optimization algorithm or not.
 
@@
 w_i = \left\{ \begin{array}{rl}
-0 &\mbox{if $i$th potential cluster $C_i$ is chosen} \\
-1 &\mbox{if $i$th potential cluster $C_i$ is not chosen} \\
+0 &\mbox{if $i$th possible cluster $C_i$ is chosen} \\
+1 &\mbox{if $i$th possible cluster $C_i$ is not chosen} \\
 \end{array} \right.
 $$
-$w_i$ is an auxiliary binary variable which denotes whether cluster $C_i$ is chosen by the clustering solution or not.
-When $w_i$ is zero, it means $C_i$ is chosen by the clustering solution, in this case, the second item in the objective function is $p$, which is defined as follows,
+When $w_i$ is zero, it means $C_i$ is chosen by the optimization algorithm, in this case, the second item in the objective function becomes $p$, which is defined as follows,
 
@@
 0 &\mbox{ if $|C_i|=\delta$} \\
-\alpha_1 &\mbox{if $|C_i|=\delta-1$} \\
-\alpha_2 &\mbox{if $|C_i|=\delta-2$} \\
+\alpha_1 &\mbox{if $|C_i|=\delta-1$ or $|C_i|=\delta+1$} \\
+\alpha_2 &\mbox{if $|C_i|=\delta-2$ or $|C_i|=\delta+2$} \\
 \dots
@@
 $$
-where $\alpha_x$ is a positive value, which increases with the divergence between $|C_i|$ and $\delta$, thus these is $\alpha_2> \alpha_1>0$.
-Because of $w_i$, any cluster which appears in the clustering solution ($w=0$) will bring certain \textit{punishment}.
-Only when that cluster's size is exactly the preferred size $\delta$, the punishment is zero.
-In contrary, when the chosen cluster's size diverges from $\delta$, the objective function suffers \textit{loss}.
-In particular, when $w_i=0$ and $|C_i|=1$, the punishment is the most severe.
-With such design, the solution is encouraged not to generate singleton clusters.
+where $\alpha_1, \alpha_2, \cdots$ are positive values, then when $w_i$ is zero ($C_i$ is chosen by the optimization algorithm) and its size is not the desired size $\delta$, the second component will be greater than zero, which will compromise the first component.
+In particular, $\alpha$ increases with the divergence between $|C_i|$ and $\delta$ \ie these is $\alpha_2> \alpha_1>0$.
+%Because of $w_i$, any cluster which appears in the clustering solution ($w=0$) will compromise the first component.
+%Only when that cluster's size is exactly the preferred size $\delta$, the punishment is zero.
+%In contrary, when the chosen cluster's size diverges from $\delta$, the objective function suffers \textit{loss}.
+%Then it is easy to notice that when the optimization algorithm adopts singleton clusters, the first xx.
+%With such design, the solution is encouraged not to generate singleton clusters.
 %doesn't follow the definition of $f(C)$ in Definition~\ref{def_centralized_clustering} strictly, where $f(C_i)=0$ when $|C_i|=1$, but our design echoes the definition by exerting the most severe punishment on the singleton clusters in the clustering solution.
@@
 
-As to the constraints, the first constraint restricts each node $j$ to reside in exactly one cluster.
-The second constraint regulates that when the $i$th potential cluster $C_i$ is chosen, there will be exactly $|C_i|$ CR nodes residing in cluster $C_i$.
+As to the constraints, the first constraint regulates that each CR node should reside in exactly one cluster.
+The second constraint regulates that when the $i$th possible cluster $C_i$ is chosen, there will be exactly $|C_i|$ CR nodes residing in the cluster $C_i$.
 
@@
 
-In this section we introduce the distributed clustering scheme ROSS.
+In this section we will introduce the distributed clustering scheme ROSS.
+With ROSS, CR nodes form clusters based on the proximity of the available spectrum in their neighborhood. 
 ROSS consists of two cascaded phases: \textit{cluster formation} and \textit{membership clarification}.
-With ROSS, CR nodes form clusters based on the proximity of the available spectrum in their neighbourhood. Afterwards, CR nodes belong to one certain cluster. %by interacting with certain neighbours.
+
 %is based on the spectrum sensing results in its neighbours , then
@@
 \item \textit{Individual connectivity degree} $d_i$: $d_i=\sum_{j\in \text{Nb}(i)}\vert K_i\cap K_j\vert$. 
-$d_i$ is the total number of the CCCs between node $i$ and every its neighbor.
+$d_i$ is the total number of the CCs between node $i$ and every its neighbor.
 It is an indicator of node $i$'s adhesion to the CRN.
@@
 \item \textit{neighborhood connectivity degree} $g_i$: $g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$. 
-It is the number of CCCs which are available for $i$ and all its neighbors.
+It is the number of CCs which are available for $i$ and all its neighbors.
 $g_i$ represents the ability of $i$ to form a robust cluster with its neighbors.
@@
 
-\subsubsection{Guarantee the Availability of Common Control Channel}
+\subsubsection{Guarantee the Existence of Common Channels in Every Cluster}
 \label{ross_p1_guarantee_ccc}
 %After deciding itself being cluster head, CR node broadcasts to notify its neighbours on the dedicated control channel, meanwhile, $i$'s initial cluster is formed immediately, which is $i$'s neighbourhood except for those nodes which have become cluster heads, \ie $C_i=(\text{Nb}_i\setminus \text{CHs})\cup i$.
-After executing Algorithm~\ref{alg0}, certain formed clusters may don't possess any CCCs.
-As decreasing cluster size increases the CCCs within a cluster, for those clusters having no CCCs, certain nodes need to be eliminated to obtain at least one CCC.
+After executing Algorithm~\ref{alg0}, certain formed clusters may don't possess any CCs.
+As decreasing cluster size increases the CCs within a cluster, for those clusters having no CCs, certain nodes need to be eliminated to obtain at least one CC.
 The sequence of elimination is performed according to an ascending list of nodes which are sorted by the number of common channels between the nodes and the cluster head. 
@@
 We consider a cluster $C(i)$ where $i$ is CH in a dense CRN. 
-To make the analysis easier, we assume there is no CHs which are generated within $i$'s neighborhood during the procedure of guaranteeing CCCs.
+To make the analysis easier, we assume there is no CHs which are generated within $i$'s neighborhood during the procedure of guaranteeing CCs.
 Assuming the CR users and PUs are evenly distributed and PUs occupy the licensed channels randomly, then both CR nodes density and channel availability in the CRN can be seen to be spatially homogeneous.
@@
 Given the desired size $\delta$, a cluster head excludes members sequentially according to the following principle, the absence of one cluster member leads to the maximum increase of common channels within the cluster.
-This process ends when the size of resultant cluster is $\delta$ and at least one CCC is available.
-This procedure is similar with that to guarantee CCCs in cluster, thus the algorithm can reuse Algorithm~\ref{alg_size_control_available_CCC}.
+This process ends when the size of resultant cluster is $\delta$ and at least one CC is available.
+This procedure is similar with that to guarantee the existence of CCs in cluster, thus the algorithm can reuse Algorithm~\ref{alg_size_control_available_CCC}.
 
@@
 Assume a debatable node $i$ needs to decide one cluster $C\in S_i$ to stay, and thereafter leaves the rest others in $S_i$.
-In this process, the principle for $i$ is that its move should result in the greatest increase of CCCs in all its claiming clusters.
+In this process, the principle for $i$ is that its move should result in the greatest increase of CCs in all its claiming clusters.
 %The set of available channels of one cluster are known by the debatable nodes which locate in that cluster. %this is finished 
-Note that node $i$ is aware of the spectrum availability on all the cluster members of each claiming cluster, thus node $i$ is able to calculate how many more CCCs can be produced in one claiming cluster if $i$ leaves that cluster.
+Note that node $i$ is aware of the spectrum availability on all the cluster members of each claiming cluster, thus node $i$ is able to calculate how many more CCs can be produced in one claiming cluster if $i$ leaves that cluster.
 %Based on this calculation, $i$ decides on one claiming cluster to stay and leaves the other claiming clusters.
-If there exists one cluster $C\in S_i$, when $i$ leaves this cluster brings the least increased CCCs than leaving any other claiming clusters, then $i$ chooses to stay in cluster $C$.
-When there comes a tie, among the claiming clusters, $i$ chooses to stay in the cluster whose cluster head shares the most CCCs with $i$.
+If there exists one cluster $C\in S_i$, when $i$ leaves this cluster brings the least increased CCs than leaving any other claiming clusters, then $i$ chooses to stay in cluster $C$.
+When there comes a tie, among the claiming clusters, $i$ chooses to stay in the cluster whose cluster head shares the most CCs with $i$.
 In case there are multiple claiming clusters demonstrating the same on the aforementioned metric, node $i$ chooses to stay in the claiming cluster which has the smallest size.
@@
 %Assuming node $i$ decides to stay in cluster $C$, then one another debatable nodes $j$ decides its affiliation, and there is $j\in C\in S_i$.
-%$j$'s move decreases cluster $C$'s size, and could possibly trigger node $i$ to alter its previous decision to leave $C$, as $C$'s size is smaller now and leaving it may result in more increase of CCCs in $S_i$.
+%$j$'s move decreases cluster $C$'s size, and could possibly trigger node $i$ to alter its previous decision to leave $C$, as $C$'s size is smaller now and leaving it may result in more increase of CCs in $S_i$.
 %At this point of time, debatable node $j$ may rejoin cluster $C$ due to the changes in $S_j$, then both node $i$ and $j$ face the \textit{same} situation again.
@@
 Now for the debatable nodes, the previous problem of deciding which clusters to leave becomes a new problem that which cluster to join.
-In the new problem, debatable node $i$ chooses one cluster $C$ out of $S_i$ to join if the decrease of CCCs in cluster $C$ is the smallest in $S_i$, and the decrease of CCCs in cluster $C$ is $\sum_{C\in S_i}\Delta\vert K(C) \vert=\sum_{C\in S_i}({\vert K(C) \vert-\vert K(C\cup i) \vert})$.
+In the new problem, debatable node $i$ chooses one cluster $C$ out of $S_i$ to join if the decrease of CCs in cluster $C$ is the smallest in $S_i$, and the decrease of CCs in cluster $C$ is $\sum_{C\in S_i}\Delta\vert K(C) \vert=\sum_{C\in S_i}({\vert K(C) \vert-\vert K(C\cup i) \vert})$.
 The interaction between the debatable nodes and the claiming clusters is shown in Figure~\ref{debatable_nodes_claiming_cluster}.
@@
 	The utility (cost) function $f(C)$ as to a resource $C$. 
-	$f(C) = \Delta\vert K^i(C)|, C\in S_i$, which represents the decrease of CCCs in cluster $C$ when debatable node $i$ joins $C$.
-	As to cluster $C\in S_i$, the decrease of CCCs caused by the enrolment of debatable nodes is $\sum_{i:C\in S_i, i\rightarrow C} \Delta\vert K^i(C) \vert$. 
+	$f(C) = \Delta\vert K^i(C)|, C\in S_i$, which represents the decreased number of CCs in cluster $C$ when debatable node $i$ joins $C$.
+	As to cluster $C\in S_i$, the decrease of CCs caused by including the debatable nodes is $\sum_{i:C\in S_i, i\rightarrow C} \Delta\vert K^i(C) \vert$. 
 $i\rightarrow C$ means $i$ joins cluster $C$.
@@
 Hence, this congestion game is player specific~\cite{Ackermann06purenash}.
-In this game, every player greedily updates its strategy (choosing one claiming cluster to join) if joining a different claiming cluster minimizes the decrease of CCCs $\sum_{i:C\in S_i} \Delta\vert K^i(C) \vert$, and a player's strategy in the game is exactly the same with the behaviour of a debatable node in the membership clarification phas.
+In this game, every player greedily updates its strategy (choosing one claiming cluster to join) if joining a different claiming cluster minimizes the decrease of CCs $\sum_{i:C\in S_i} \Delta\vert K^i(C) \vert$, and a player's strategy in the game is exactly the same with the behaviour of a debatable node in the membership clarification phas.
 
@@
 The two possible strategies of node $A$ is illustrated in Figure \ref{fig3}.
-In Figure \ref{AinC}, node $A$ staying in $C(C)$ and leaving $C(H)$ brings 2 more CCCs to $S_A$, which is more than that brought by another strategy showed in \ref{AinH}.
+In Figure \ref{AinC}, node $A$ staying in $C(C)$ and leaving $C(H)$ brings 2 more CCs to $S_A$, which is more than that brought by another strategy showed in \ref{AinH}.
 After the decisions made similarly by the other debatable nodes $B$ and $D$, the final clusters are formed as shown in Figure~\ref{final_clustering_ross}.
@@
 As to the centralized robust clustering scheme, we let the desired cluster size $\delta$ be 3.
-A collection of clusters $\mathcal{G}$ is obtained, which contains all the clusters satisfying the conditions of cluster in Section~\ref{def_cluster} and the sizes of clusters are 1, 2 or 3. 
+A collection of clusters $\mathcal{G}$ is obtained, which contains all the clusters satisfying the conditions of clusters in Section~\ref{sec:model} and the sizes of clusters are 1, 2 or 3. 
 $\mathcal{G}=\{\{A\}, \{B\},\dots,\{B,C\},\{B,A\},\{B,H\},\cdots,\{B,A,C\},$\\$\{B,H,C\}, \{A,D,C\},\cdots\}$, and $G = |\mathcal{G}|=38$.
@@
 When $\alpha_1$ and $\alpha_1$ are set as 0.2 and 0.8, the formed clusters are shown in Fig.~\ref{fig:final_clustering_LP}.
-%$\{\{D,E,F\},\{A,C,G\},\{H,G\}\}$, the numbers of CCCs are 2, 3, 3.
-The resulted clustering solutions from SOC is shown in Fig.~\ref{fig:final_clustering_soc}.%, clusters are $\{A,B,C,D,G\},\{E,F\},\{H\}$, and the numbers of CCCs are 2, 3, 4.
-%The solution resulted from ROSS-DGA is $\{\{B,H,G\},\{C,A\},\{D,E,F\}\}$ (in Figure~\ref{fig4}), the numbers of CCCs are 2, 4, 2.
+%$\{\{D,E,F\},\{A,C,G\},\{H,G\}\}$, the numbers of CCs are 2, 3, 3.
+The resulted clustering solutions from SOC is shown in Fig.~\ref{fig:final_clustering_soc}.%, clusters are $\{A,B,C,D,G\},\{E,F\},\{H\}$, and the numbers of CCs are 2, 3, 4.
+%The solution resulted from ROSS-DGA is $\{\{B,H,G\},\{C,A\},\{D,E,F\}\}$ (in Figure~\ref{fig4}), the numbers of CCs are 2, 4, 2.
 %ROSS-DFA generates the same result with ROSS-DGA in this example.
 
-As to the average number of CCCs, the results of ROSS (including both ROSS-DGA and ROSS-DFA), centralized and SOC are 2.66, 2.66, and 3 respectively. 
+As to the average number of CCs, the results of ROSS (including both ROSS-DGA and ROSS-DFA), centralized and SOC are 2.66, 2.66, and 3 respectively. 
 Note there is one singleton cluster $C(H)$ generated by SOC, which is not preferred.
@@
 \end{itemize}
-The authors of~\cite{LIU_TMC11_2} compared SOC with other schemes in terms of the average number of CCCs of the formed cluster, on which SOC outperforms other schemes by 50\%-100\%. 
+The authors of~\cite{LIU_TMC11_2} compared SOC with other schemes in terms of the average number of CCs of the formed cluster, on which SOC outperforms other schemes by 50\%-100\%. 
 SOC's comparison schemes are designed either for ad hoc network without consideration of channel availability~\cite{Basagni99}, or for CRN but just considering connection among CR nodes~\cite{Zhao07}.
@@
 \begin{itemize}
-\item \textbf{Average number of CCCs per non-singleton cluster.}
+\item \textbf{Average number of CCs per non-singleton cluster.}
 Non-singleton cluster refers the cluster whose cluster size is larger than 1.
 %This metric denotes the robustness of the formed non-singleton clusters.
-Comparing with the metric adopted by SOC~\cite{LIU_TMC11_2}, which is the average number of CCCs per cluster without excluding the singleton clusters, this metric provides an more accurate description of the robustness of the non-singleton cluster.
-The larger number of CCCs per non-singleton clusters means these clusters have higher probability to survive when the primary users' operation becomes more intense.
+Comparing with the metric adopted by SOC~\cite{LIU_TMC11_2}, which is the average number of CCs per cluster without excluding the singleton clusters, this metric provides an more accurate description of the robustness of the non-singleton cluster.
+Having more CCs per non-singleton clusters means these clusters have higher probability to survive when the primary users' operation becomes more intense.
 %which is biased as the singleton clusters (isolated CR users) don't get benefits from the cluster structure.
-Although this metric doesn't disclose the information about the CR nodes which are not included in any non-singleton clusters, we still examine this metric as the number of CCCs is involved in the utility which is adopted by all robust clustering schemes.
+Although this metric doesn't disclose the information about the CR nodes which are not included in any non-singleton clusters, we still examine this metric as the number of CCs is involved in the utility which is adopted by all robust clustering schemes.
 %, thus it fails to give an overview of how many CR nodes can benefit from non-singleton clusters.
@@
 
-\subsubsection{Number of CCCs in Non-singleton Clusters}
+\subsubsection{Number of CCs in Non-singleton Clusters}
 \label{ccc_20}
 %We first have a look at the average number of common channels per non-singleton cluster.
-% shows the average number of the CCCs of non-singleton clusters,
+% shows the average number of the CCs of non-singleton clusters,
 %as the singleton clusters (in other words unclustered nodes) don't execute any functionalities of clusters, which are has be discussed in Section~\ref{intro}.
@@
 As to the distributed schemes, SOC achieves the best than all the variants of ROSS.
-The reason is, SOC is liable to group the neighbouring CRs which share the most abundant spectrum together, no matter how many of them are, thus the number of CCC of the formed clusters is higher.
+The reason is, SOC is liable to group the neighbouring CRs which share the most abundant spectrum together, no matter how many of them are, thus the number of CC of the formed clusters is higher.
 We have discussed the flaw of this metric as it doesn't convey the number of unclustered CR nodes, in fact, SOC generates the most unclustered CRs, which can be seen when we discuss the performance on the number of unclustered CR nodes.
-As to the variants of ROSS, we notice that the greedy mechanism increases CCCs in non-singleton clusters significantly.
-%, this is due to the procedure that debatable nodes greedily look for better affiliation to improve the number of CCCs.
-%We also notice that the size control feature doesn't affect the number of CCCs for both ROSS-DGA and ROSS-DFA.
+As to the variants of ROSS, we notice that the greedy mechanism increases CCs in non-singleton clusters significantly.
+%, this is due to the procedure that debatable nodes greedily look for better affiliation to improve the number of CCs.
+%We also notice that the size control feature doesn't affect the number of CCs for both ROSS-DGA and ROSS-DFA.
 %Size control mechanism converts the large clusters into small ones, but meanwhile clusters with the desired sizes have to be made when forming smaller clusters is possible.
@@
 
-%This is because the desired cluster size happens to be the average size of clusters generated by ROSS-DGA and ROSS-DFA, then the size control functionality doesn't play effect to increase the number of CCCs.
+%This is because the desired cluster size happens to be the average size of clusters generated by ROSS-DGA and ROSS-DFA, then the size control functionality doesn't play effect to increase the number of CCs.
 
@@
 \subsubsection{Robustness of the clusters against newly added PUs}
-%When the number of PUs in CRN increases, or their operation becomes more intensive, some clusters don't seize any CCCs any more, so that the cluster members and the cluster heads become unclustered, or singleton clusters.
-%If there is no common control channels available any more because of the new added PRs, the cluster is regarded as destroyed and the former cluster member CRs become unclustered CRs or in other words singleton clusters.
+%When the number of PUs in CRN increases, or their operation becomes more intensive, some clusters don't seize any CCs any more, so that the cluster members and the cluster heads become unclustered, or singleton clusters.
+%If there is no common channels available any more because of the new added PRs, the cluster is regarded as destroyed and the former cluster member CRs become unclustered CRs or in other words singleton clusters.
 %We investigate the number of singleton clusters with primary users whose intensity of activities are varying.
@@
 Among the robust clustering schemes, the centralized scheme with desired size of two generates the most robust clusters, meanwhile, SOC results in the most vulnerable clusters.
-The centralized scheme with desired size of three doesn't outperform the variants of ROSS, because the centralized scheme peruses clusters with size of 3 at the expenses of sanctifying CCCs.
+The centralized scheme with desired size of three doesn't outperform the variants of ROSS, because the centralized scheme peruses clusters with size of 3 at the expenses of sanctifying CCs.
 In contrary, the variants of ROSS generate some smaller clusters which are more likely to survive when PUs' activities become intense.
@@
 %Greedy strategy adopted in the second phase of ROSS improves the robustness of clusters, i.e. ROSS-DGA exceeds ROSS-DFA, and ROSS-$\delta$-DGA surpasses ROSS-$\delta$-DFA.
-%When the debatable CRs greedily update their affiliations, one of the metrics is the maximum increase of CCCs of the demanding clusters. 
+%When the debatable CRs greedily update their affiliations, one of the metrics is the maximum increase of CCs of the demanding clusters. 
 %This observation complies with the result shown in Figure~\ref{ccc_per_nonsingleton}.
@@
 As to ROSS, the control messages are generated in both phases.
-In the first phase, when a CR node decides itself to be the cluster head, it broadcasts a message containing its ID, cluster members and the set of CCCs in its cluster.
+In the first phase, when a CR node decides itself to be the cluster head, it broadcasts a message containing its ID, cluster members and the set of CCs in its cluster.
 %As to ROSS with size control feature, there are same amount of cluster heads with ROSS without enabling size control feature, and the cluster head broadcasts the available channels of the pruned cluster.
@@
 
-\subsubsection{Number of CCCs per Non-singleton Clusters}
+\subsubsection{Number of CCs per Non-singleton Clusters}
 
@@
 
-Figure~\ref{ccc_large_scale} shows the average number of CCCs of the non-singleton clusters.
-We notice that SOC achieves the most CCCs per non-singleton cluster, although the lead over the variants of ROSS shrinks significantly when $N$ increases.
-%\ie when $N=300$, the number of CCCs achieved by ROSS variants (except for ROSS-$\delta$-DFA) is almost the same as that resulted from SOC.
-%This means SOC out performs in terms of the average number of CCCs per non-singleton cluster when network is sparse.
+Figure~\ref{ccc_large_scale} shows the average number of CCs of the non-singleton clusters.
+We notice that SOC achieves the most CCs per non-singleton cluster, although the lead over the variants of ROSS shrinks significantly when $N$ increases.
+%\ie when $N=300$, the number of CCs achieved by ROSS variants (except for ROSS-$\delta$-DFA) is almost the same as that resulted from SOC.
+%This means SOC out performs in terms of the average number of CCs per non-singleton cluster when network is sparse.
 %This is also observed in the evaluation in Section \ref{ccc_20} where $N=20$.
-%When the network becomes denser, even this metric favours SOC as discussed in the beginning of Section~\ref{performance}, ROSS-DGA achieves even more CCCs than SOC, and ROSS-DFA and ROSS-$\delta$-DGA increase the number of CCCs visibly.
+%When the network becomes denser, even this metric favours SOC as discussed in the beginning of Section~\ref{performance}, ROSS-DGA achieves even more CCs than SOC, and ROSS-DFA and ROSS-$\delta$-DGA increase the number of CCs visibly.
 
@@
 
-We also notice that the metric that the number of CCCs per non-singleton cluster doesn't indicate the robustness of clusters as shown in Figure~\ref{singleton_clusters} and \ref{unclustered_100_200_300}, although it is adopted as the metric in the formation of clusters.
+We also notice that  as a metric, the number of CCs per non-singleton cluster doesn't indicate the robustness of clusters as shown in Figure~\ref{singleton_clusters} and \ref{unclustered_100_200_300}, although it is adopted as the metric in the formation of clusters.
 
@@
 \begin{algorithm}               % enter the algorithm environment
-\caption{ROSS phase I: cluster head guarantees the availability of CCC (start from line 1) / cluster size control (start from line 2)}          % give the algorithm a caption
+\caption{ROSS phase I: cluster head guarantees the availability of CC (start from line 1) / cluster size control (start from line 2)}          % give the algorithm a caption
 \label{alg_size_control_available_CCC}
@@
 \KwIn{Cluster C, empty sets $\tau_1, \tau_2$}
-\KwOut{Cluster C has at least one CCC, or satisfies the requirement on cluster size}
-%\tcc*[r]{When to guarantee available CCCs, execute from line 1, when to control cluster size, execute from line 2}
+\KwOut{Cluster C has at least one CC, or satisfies the requirement on cluster size}
+%\tcc*[r]{When to guarantee available CCs, execute from line 1, when to control cluster size, execute from line 2}
 \While {$K_C =\emptyset$} {
@@
 %We define a set of CR nodes $\mathcal{N} = \{ 1, \ldots , N \}$
-We further regulate that, each set in $\mathcal{I'}$ has a corresponding cluster, \ie there is a bijection between a set in $\mathcal{I'}$ and a set of node IDs in a cluster, besides, the number of CCCs is equal to the weight of the corresponding set.
+We further regulate that, each set in $\mathcal{I'}$ has a corresponding cluster, \ie there is a bijection between a set in $\mathcal{I'}$ and a set of node IDs in a cluster, besides, the number of CCs is equal to the weight of the corresponding set.
 
@@
 %We find it is impossible to map the sets into clusters in the same time (SORRY, which sets??
-The sets you mentioned before are already clusters, isn't it?), because the number of CCCs of the cluster which bases on $s_1$ should be no less than the cluster which bases on $s_2$, as the latter has one extra node compared with the former cluster.
+The sets you mentioned before are already clusters, isn't it?), because the number of CCs of the cluster which bases on $s_1$ should be no less than the cluster which bases on $s_2$, as the latter has one extra node compared with the former cluster.
 %%When $s_1'$ and $s_2'$ are mapped to CRN respectively, there is contradiction between them, because the number of common channels of CR node group $\{1,1,2,2\}$ is smaller than that of $\{1,1,2,2,3,3,4,4\}$.
@@
 We one-to-one map these elements to CR nodes, and arbitrarily put these CR nodes in the plane, and these CR nodes become single node clusters.
-According to the definition of clustering problem in CRN, the number of CCCs in these single node clusters is 0.
+According to the definition of clustering problem in CRN, the number of CCs in these single node clusters is 0.
 These singleton clusters and the clusters mapped from $\mathcal{I'}$ constitute a clustering proposal, and finding these singleton clusters requires at most $N$ steps.
@@
 
-When there are only disjoint sets in an instance $\mathcal{I}$ for weighted k-set packing, the sum weight is identical to the sum number of CCCs in the CRN mapped from $\mathcal{I'}$, even $\mathcal{I}$ contains sets which only have one element.
-Thus, when a instance $\mathcal{I}$ for k-set packing problem is true, \ie the sum of weights is greater than $\lambda$, then in the CRN which is mapped from $\mathcal{I'}$, the summed number of CCCs of the clusters is greater than $\lambda$.
+When there are only disjoint sets in an instance $\mathcal{I}$ for weighted k-set packing, the sum of weights is identical to the sum of the numbers of CCs in the CRN mapped from $\mathcal{I'}$, even $\mathcal{I}$ contains sets which only have one element.
+Thus, when a instance $\mathcal{I}$ for k-set packing problem is true, \ie the sum of weights is greater than $\lambda$, then in the CRN which is mapped from $\mathcal{I'}$, the sum of the numbers of CCs of the clusters is greater than $\lambda$.
 In the other way around, when an instance if false for weighted k-set packing problem,
@@
 %%Meanwhile, the number of common channels of all the other single node cluster is 0.
-the summed number of CCCs of the clusters in the mapped CRN is smaller than $\lambda$, and there is no clustering solution satisfying the centralized clustering problem.
+the sum of the numbers of CCs of the clusters in the mapped CRN is smaller than $\lambda$, and there is no clustering solution satisfying the centralized clustering problem.
 

### 2016-11-06 journal-draft/bare_jrnl_comsoc.tex
start to modify the proof 2

@@
+% to do : add more notations
+% the new notation t.
 \documentclass[10pt,journal,compsoc]{IEEEtran}
@@
 \usepackage{tabularx,colortbl} % colored table background
-\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
-\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
-\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
+%\usepackage{tablefootnote}
+\newcolumntype{C}[1]{>{\centering\arraybackslash}m{#1}}
+\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}m{#1}}
+\newcolumntype{L}[1]{>{\raggedright\arraybackslash}m{#1}}
+
 % Table spacings
@@
 \setlist[itemize]{leftmargin=*}
+\usepackage[referable]{threeparttablex}
+\renewlist{tablenotes}{enumerate}{1}
+\makeatletter
+\setlist[tablenotes]{label=\tnote{\alph*},ref=\alph*,itemsep=\z@,topsep=\z@skip,partopsep=\z@skip,parsep=\z@,itemindent=\z@,labelindent=\tabcolsep,labelsep=.2em,leftmargin=*,align=left,before={\footnotesize}}
+\makeatother
 %%%%%%%%%%%%%%%%%%%%%%%%%% copied from thesis
@@
 $C_i$  & the $i$th potential cluster in a collection of clusters \\
+ $\mathcal{G}$ & a collection of some possible clusters in $\mathcal{N}$\\
+ $\mathcal{S}$ & the collection of all the possible clusters in $\mathcal{N}$\\
 \bottomrule
@@
 First, the generation of the \textit{singleton clusters}, \ie the cluster which has only one CR node, should be avoided, because it contradicts the motivation of forming clusters thus the benefits brought in by the collective of the cluster members are compromised.
-Second, Large clusters are not preferred in some scenarios neither, \eg for the CRN composed with resource limited users, managing the cluster members is a substantial burden. 
+Second, large clusters are not preferred in some scenarios neither, \eg for the CRN composed with resource limited users, managing the cluster members is a substantial burden. 
 Hence, the cluster size should fall in a desired range according to different application scenarios~\cite{Chen04clusteringalgorithms, capacity_cluster_06}.
-Considering the above mentioned requirements on the formed clusters, we will present the definition of robust clustering problem as follows.
+Considering the above mentioned requirements on the formed clusters, we present the definition of robust clustering problem as follows.
 %The clustering scheme we propose in the paper aims to form clusters with preferred sizes, meanwhile maximize the average number of CCs per cluster.
@@
 Given a cognitive radio network $\mathcal{N}$ where $|\mathcal{N}|=N$,  the secondary users are indexed from 1 to $N$.
-A cluster $C$ is formed when first, it is composed with one or multiple secondary users and there is $|K(C)|>0$, second, any two cluster members can communicate either directly, or through other members which belong to the same cluster.
+A cluster $C$ is formed when first, it is composed with one or multiple secondary users and there are CCs in $C$ \ie $|K(C)|>0$, second, any two cluster members can communicate either directly, or through other members which belong to the same cluster.
 The collection of all the possible clusters in $\mathcal{N}$ is denoted as $\mathcal{S}$, there is $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$ where $C_i$ is the $i$ th cluster in $\mathcal{S}$\footnote{The sequence of the clusters can be decided in any convenient way \ie the sequence of identifying them.}.
@@
 Based on Definition~\ref{def_centralized_clustering}, the decision version of this problem is to determine whether there exists a non-empty $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C\in \mathcal{S}'} f(C) \geqslant \lambda$ where $\lambda$ is a real number and $C$ is a cluster.
-We have the following theorem on complexity.
+We have the following theorem on the complexity of this problem.
 
@@
 
-As the robust clustering problem in CRN is NP hard, there is no polynomial solution available.
-In this section, we will propose a centralized solution which approaches to the global optimal.
+With the definition of the robust clustering problem, we need to present this problem in the form of optimization to solve in the centralized manner.
+The optimization is a binary linear programming problem as shown in~\ref{centralized_opt}.
+%Binary linear programming problem is NP complement, but with the 
 The result will be used as a comparison with the proposed distributed schemes.
@@
 %To make the formulation possible, we adopt heuristics in both the objective function and the constraints, besides, the objective is not totally aligned with the object in the Definition~\ref{def_centralized_clustering}.
-The problem by the Definition~\ref{def_centralized_clustering} is formulate into an optimization problem~\ref{centralized_opt} which is a binary linear programming problem.
+%The problem by the Definition~\ref{def_centralized_clustering} is formulate
 
@@
 $N$ is the total number of CR users in network $\mathcal{N}$.
-$G = |\mathcal{G}|$ and $\mathcal{G}$ is the collective of clusters in a CRN $\mathcal{N}$, there is $\mathcal{G} \subseteq \mathcal{S}$, where $\mathcal{S}$ is the collection of all the possible clusters as described in Definition~\ref{def_centralized_clustering}.
+$G = |\mathcal{G}|$ and $\mathcal{G}$ is a collective of clusters in a CRN $\mathcal{N}$.
+There is $\mathcal{G} \subseteq \mathcal{S}$, where $\mathcal{S}$ is the collection of all the possible clusters as described in Definition~\ref{def_centralized_clustering}.
+In practice, we can solve the problem with $\mathcal{G} = \mathcal{S}$ when $|\mathcal{S}|$ is not large. 
 The subscript $i$ indicates the $i$th cluster in $\mathcal{G}$, and $j$ corresponds to the node ID of a CR node. 
@@
 \label{ross}
-The centralized robust clustering scheme is inherently not suitable for the CRN which involves dynamics in multiple aspects.
-Whenever clustering or re-clustering is necessary, which could be triggered by either the mobility of CR users or the variance of the available spectrum, the centralized entity needs to collect the information from all the CR nodes, and then distributes the clustering solution after computation.
-
+To do clustering with the centralized scheme for a CRN, the centralized entity firstly needs to collect the information from all the CR nodes, then computes the clustering solution and distributes it across the whole network.
+This process involves a large number of communication overheads.
+In CRN, it is necessary to do clustering again on some occasions.
+For example, when a certain amount of CR users move away from their clusters, \ie they loose the direction connection with any member in their previous clusters, or a certain amount of clusters can not be maintained as the CC in these clusters don't exist any longer due to primary users' activity.
+Hence, when the spectrum availability and the CR users' location change frequently, the centralized robust clustering scheme is not suitable for CRN.
+%
 In this section we will introduce the distributed clustering scheme ROSS.
-With ROSS, CR nodes form clusters based on the proximity of the available spectrum in their neighborhood. 
+With ROSS, CR nodes form clusters based on the proximity of the available spectrum in their neighborhood after a series of interactions with their neighbors. 
 ROSS consists of two cascaded phases: \textit{cluster formation} and \textit{membership clarification}.
@@
 \label{phaseI}
-After conducting spectrum sensing and communicating with neighbors, every CR node is aware of the channels which are available on themselves and also those on their one hop neighbors.
-Two metrics are proposed to characterize the proximity in terms of available spectrum between CR node $i$ and its neighborhood:
+We assume that before conducting clustering, spectrum sensing, neighbor discovery and exchange of spectrum availability have been completed, so that every CR node is aware of the available channels on themselves and their neighbors.
+In this phase, cluster heads are determined after a series of comparisons with their neighbors. 
+Two metrics are proposed to characterize the proximity in terms of available spectrum between CR node $i$ and its neighborhood, which are used in the comparisons to decide on the cluster heads.
+
+%After introducing the connectivity vector, we can proceed to introduce the first phase of algorithm ROSS.
+
+%When a CR user is identified as cluster head, its neighborhood becomes a cluster.
 
@@
 	\caption{Connectivity graph of the example CRN and the connectivity vector $(d_i, g_i)$ for each node.
+The desired cluster size $\delta =3$.
 The sets of the indices of the available channels sensed by each node are: $K_A=\{1,2,3,4,5,6,10\}, K_B=\{1,2,3,5,7\}, K_C=\{1,3,4,10\}, K_D=\{1,2,3,5\}, K_E=\{2,3,5,7\}, K_F=\{2,4,5,6,7\}, K_G=\{1,2,3,4,8\}, K_H=\{1,2,5,8\}$.
@@
 
-After introducing the connectivity vector, we proceed to introduce the first phase of algorithm ROSS.
-In this phase, cluster heads are determined through a series of autonomous negotiations among the CR users, then the neighborhoods of the cluster heads become clusters.
-
 \subsubsection{Determining Cluster Heads and Form Clusters}
-In this phase, each CR node decides whether it is a cluster head by comparing its connectivity vector with its neighbors.
+The procedure of determining the cluster heads is as follows.
+Each CR node decides whether it is a cluster head by comparing its connectivity vector with its neighbors.
 When CR node $i$ has lower individual connectivity degree than all its neighbors except for those which have already identified to be cluster heads, node $i$ becomes a cluster head.
@@
 
-\subsubsection{Guarantee the Existence of Common Channels in Every Cluster}
+\subsubsection{Guarantee the Existence of Common Channels}
 \label{ross_p1_guarantee_ccc}
@@
 %At the end of this procedure every formed cluster has at least one common channel.
-The pseudo code for cluster head to obtain at least one common channel is shown in Algorithm~\ref{alg_size_control_available_CCC}.
+%The pseudo code for cluster head to obtain at least one common channel is shown in Algorithm~\ref{alg_size_control_available_CCC}.
+The pseudo code for this procedure is shown in Algorithm~\ref{alg_size_control_available_CCC}.
 As to the nodes which are eliminated from the previous clusters, they restore their original individual connectivity degrees, executes Algorithm~\ref{alg0}, and become either cluster heads or get included into other clusters afterwards according to Theorem~\ref{clustering:theorem}.
@@
 
-Both analysis and simulation show that when applying ROSS, after the number of clusters saturates with the increase of network density, the cluster size increases linearly with the network density, thus certain measures are needed to curb this problem.
+Both analysis and simulation show that when applying ROSS, after the clusters are saturated with the increase of network density, the cluster size increases linearly with the network density, thus certain measures are needed to curb this problem.
 This task falls to the cluster heads.
-To control the cluster size, cluster heads prune their cluster members to achieve the desired cluster size.
+To control the cluster size, cluster heads prune their cluster members to reach the desired cluster size.
 The desired size $\delta$ is decided based on the capability of the CR users and the tasks to be conveyed.
-Given the desired size $\delta$, a cluster head excludes members sequentially according to the following principle, the absence of one cluster member leads to the maximum increase of common channels within the cluster.
-This process ends when the size of resultant cluster is $\delta$ and at least one CC is available.
-This procedure is similar with that to guarantee the existence of CCs in cluster, thus the algorithm can reuse Algorithm~\ref{alg_size_control_available_CCC}.
+As there are overlaps between neighboring clusters, the sizes of the clusters formed in this phase are larger than that of the finally formed clusters.
+Hence, a cluster head excludes some cluster members when the cluster size exceeds $t\cdot \delta$, where constant parameter $t$ is dependent on the network density and CR nodes' transmission range and $t>1$.
+In particular, the cluster head removes the cluster members sequentially according to the following principle, the absence of one cluster member leads to the maximum increase of common channels within the cluster.
+This process ends when each cluster's size is smaller or equal to $t \cdot\delta$.
+ %delta needs to be changed, f(delta) XXXXXXX
+This procedure is similar with guaranteeing the existence of CCs in cluster, thus can reuse Algorithm~\ref{alg_size_control_available_CCC}.
+The $t$ is set to 1.3.
 
@@
   \includegraphics[width=0.5\linewidth]{figure2.pdf}
-  \caption{Clusters formation after the phase I of ROSS. CR nodes $A, B, D$ are debatable nodes as they belong to more than one cluster.}
+  \caption{Clusters formation after the phase I of ROSS. CR nodes $A, B, D$ are debatable nodes as they belong to multiple clusters.}
   \label{fig2}
@@
 %\subsubsection*{Problem Description}
-After applying phase I of ROSS to the example in Figure~\ref{fig1}, the resulted clusters are shown in Figure~\ref{fig2}.
+As to the example CRN shown in Figure~\ref{fig1}, the resulted clusters are shown in Figure~\ref{fig2} after running phase I of ROSS.
 We notice that nodes $A, B, D$ are included in more than one cluster. 
@@
   \includegraphics[width=0.5\linewidth]{final_clustering_ross.pdf}
-  \caption{Final formation of clusters. $K(C(C)),K(C(E)),K(C(H))$ are shown beside corresponding clusters.}
+  \caption{Final formation of clusters. Common channels are shown beside corresponding clusters.}
   \label{final_clustering_ross}
-\end{figure}
-
-\subsection{Apply the Centralized and Comparison Distributed Schemes in the Example CRN}
-After introducing the resulted clusters from ROSS in Fig.~\ref{final_clustering_ross}, we apply the other robust clustering schemes in the same example CRN in Figure~\ref{fig1}.
-%We look into how does the centralized scheme perform in the toy example of the CRN in Figure~\ref{fig1}.
-%
-As to the centralized robust clustering scheme, we let the desired cluster size $\delta$ be 3.
-A collection of clusters $\mathcal{G}$ is obtained, which contains all the clusters satisfying the conditions of clusters in Section~\ref{sec:model} and the sizes of clusters are 1, 2 or 3. 
-$\mathcal{G}=\{\{A\}, \{B\},\dots,\{B,C\},\{B,A\},\{B,H\},\cdots,\{B,A,C\},$\\$\{B,H,C\}, \{A,D,C\},\cdots\}$, and $G = |\mathcal{G}|=38$.
-%
-When $\alpha_1$ and $\alpha_1$ are set as 0.2 and 0.8, the formed clusters are shown in Fig.~\ref{fig:final_clustering_LP}.
-%$\{\{D,E,F\},\{A,C,G\},\{H,G\}\}$, the numbers of CCs are 2, 3, 3.
-The resulted clustering solutions from SOC is shown in Fig.~\ref{fig:final_clustering_soc}.%, clusters are $\{A,B,C,D,G\},\{E,F\},\{H\}$, and the numbers of CCs are 2, 3, 4.
-%The solution resulted from ROSS-DGA is $\{\{B,H,G\},\{C,A\},\{D,E,F\}\}$ (in Figure~\ref{fig4}), the numbers of CCs are 2, 4, 2.
-%ROSS-DFA generates the same result with ROSS-DGA in this example.
-
-As to the average number of CCs, the results of ROSS (including both ROSS-DGA and ROSS-DFA), centralized and SOC are 2.66, 2.66, and 3 respectively. 
-Note there is one singleton cluster $C(H)$ generated by SOC, which is not preferred.
-When we take no account of the singleton clusters, then the average number of common channels of SOC drops to 2.5. 
-\begin{figure}[ht]
-\begin{center}
-\subfigure[Resulted from SOC]{\includegraphics[width=0.435\linewidth]{final_clustering_soc}\label{fig:final_clustering_soc}}
-\hspace{0.15 in}
-\subfigure[Resulted from the centralized clustering scheme]{\includegraphics[width=0.435\linewidth]{final_clustering_LP}\label{fig:final_clustering_LP}}
-\end{center}
-\caption{Final clusters formed in the example network when being applied with SOC and the centralized clustering scheme.}
-\label{fig:final_clustering}
 \end{figure}
@@
 \item ROSS without size control, \ie ROSS-DGA and ROSS-DFA.
-\item ROSS-$\delta$-DGA and ROSS-$\delta$-DFA, which are the variants of ROSS with the size control feature.
-$\delta$ is the preferred cluster size.
+\item ROSS with size control. \ie ROSS-$\delta$-DGA and ROSS-$\delta$-DFA where $\delta$ is the desired cluster size.
+In the following, when we mention the variants of ROSS, we refer the above mentioned four schemes.
 \item SOC~\cite{LIU_TMC11_2}, a distributed clustering scheme pursuing cluster robustness.
 \item Centralized robust clustering scheme. 
-The formulated optimization is an integer linear optimization problem, which is solved by the function $bintprog$ provided in MATLAB.
+The formulated optimization is an integer linear optimization problem, which is solved by MATLAB with the function $bintprog$.
 \end{itemize}
+
+The ROSS without size control mechanism is similar with the schemes proposed in \cite{Li11_ROSS}.
 The authors of~\cite{LIU_TMC11_2} compared SOC with other schemes in terms of the average number of CCs of the formed cluster, on which SOC outperforms other schemes by 50\%-100\%. 
@@
 Thus SOC is chosen to be the only distributed scheme as comparison, besides, we also compare ROSS with the centralized scheme.
-%
-We investigate the schemes with the following metrics.
+
+Before we investigating the performance of the clustering schemes with simulation, we apply the two comparison clustering schemes in the example CRN in Figure~\ref{fig1}, and make an initial comparison in terms of the amount of CCs.
+As to the centralized robust clustering scheme, we set the desired cluster size $\delta$ as 3, as a result, according to the network topology, the collection of all the possible clusters
+$\mathcal{S}=\{\{A\}, \{B\},\dots,\{B,C\},\{B,A\},\{B,H\},\cdots,\{B,A,C\},$\\$\{B,H,C\}, \{A,D,C\},\cdots\}$, and $|\mathcal{S}|=38$.
+We set $\alpha_1$ and $\alpha_1$ as 0.2 and 0.8 respectively.
+The formed clusters by the centralized clustering scheme are shown in Fig.~\ref{fig:final_clustering_LP}.
+%$\{\{D,E,F\},\{A,C,G\},\{H,G\}\}$, the numbers of CCs are 2, 3, 3.
+The resulted clustering solutions from SOC is shown in Fig.~\ref{fig:final_clustering_soc}.
+%
+We compare the average number of CCs achieved by different schemes, the results of ROSS\footnote{In this example network, both ROSS-DGA and ROSS-DFA and their size control variants form the same clusters)}, centralized and SOC are 2.66, 2.66, and 3 respectively.
+Note there is one singleton cluster $C(H)$ generated by SOC, which is not preferred.
+When we only consider the clusters which are not singleton, the average number of common channels of SOC drops to 2.5. 
+\begin{figure}[ht]
+\begin{center}
+\subfigure[Generated by SOC]{\includegraphics[width=0.435\linewidth]{final_clustering_soc}\label{fig:final_clustering_soc}}
+\hspace{0.15 in}
+\subfigure[Generated by the centralized clustering scheme]{\includegraphics[width=0.435\linewidth]{final_clustering_LP}\label{fig:final_clustering_LP}}
+\end{center}
+\caption{Final clusters formed by the centralized clustering scheme and SOC.}
+\label{fig:final_clustering}
+\end{figure}
+
+In the simulation, we investigate the schemes with four metrics.
 
 \begin{itemize}
-\item \textbf{Average number of CCs per non-singleton cluster.}
+\item \textbf{The average number of CCs per non-singleton cluster.}
 Non-singleton cluster refers the cluster whose cluster size is larger than 1.
 %This metric denotes the robustness of the formed non-singleton clusters.
-Comparing with the metric adopted by SOC~\cite{LIU_TMC11_2}, which is the average number of CCs per cluster without excluding the singleton clusters, this metric provides an more accurate description of the robustness of the non-singleton cluster.
-Having more CCs per non-singleton clusters means these clusters have higher probability to survive when the primary users' operation becomes more intense.
+Comparing with the metric adopted by SOC~\cite{LIU_TMC11_2}, which is the average number of CCs of all the clusters, this metric provides a more accurate description of the robustness of the non-singleton clusters.
+Having more CCs per non-singleton clusters means these clusters have longer life expectancy when the primary users' operation becomes more intense.
 %which is biased as the singleton clusters (isolated CR users) don't get benefits from the cluster structure.
-Although this metric doesn't disclose the information about the CR nodes which are not included in any non-singleton clusters, we still examine this metric as the number of CCs is involved in the utility which is adopted by all robust clustering schemes.
-%, thus it fails to give an overview of how many CR nodes can benefit from non-singleton clusters.
-
-%the CR nodes with more channels could be formulated as singleton clusters.
-%This happens in SOC solution, whose objective is to improve the average number of common channel over \textit{all} clusters, \ie including the singleton clusters, thus many CR nodes with more channels are turned into clusters.
-%As we try to look into the robustness of clusters of CRs, we exclude those singleton clusters.
+Although this metric doesn't disclose the information about the \textit{unclustered} CR nodes which are the synonyms of the singleton clusters, we still examine this metric as the number of CCs is involved in the utility adopted by all the variants of ROSS and SOC.
 
@@
 %Specific clusters size is pursued in many applications due to energy preservation and the system design ~\cite{clustering_globecom11}.
-The distribution of CRs residing in the formed clusters with different sizes is presented.
+We investigate the distribution of CRs residing in the formed clusters with different sizes.
 
 \item \textbf{Robustness of the clusters against newly added PUs.}
-We increase the number of PUs to challenge the clusters, and count the number of \textit{unclustered} CR nodes which are the synonyms of the singleton clusters.
-This metric indicates the robustness of clusters from a more practical point of view, \ie as to the clusters formed for a given CRN and spectrum availability, how many CR nodes can still make use of the clusters when the spectrum availability decreases.
+We increase the number of PUs to challenge the non-singleton clusters, and count the number of the unclustered CR nodes.
+This metric directly indicates the robustness of clusters from a more practical point of view, \ie as to the clusters formed for a given CRN and spectrum availability, how many CR nodes can still make use of the clusters when the spectrum availability decreases.
 %robustness of clusters, as this metric directly shows how many nodes can make use of the cluster structure.
@@
 
-Simulation consists of two parts, in the first part, we investigate the performance of centralized scheme, and the gap between the distributed schemes and the centralized scheme.
-This part is conducted in a small network, as there is no polynomial time solution available to solve the centralized problem.
+Simulation consists of two parts, first we investigate the performance of centralized scheme and the distributed schemes in a small network, as there is no polynomial time solution available to solve the centralized problem.
 In the second part, we investigate the performance of the proposed distributed schemes in the CRN with different scales and densities.
-
-We give a brief introduction to the settings which are common for both simulation parts.
+The following simulation settings is the same for both simulation parts.
 CRs and PUs are deployed on a two-dimensional Euclidean plane.
@@
 \subsection{Centralized Schemes vs. Decentralized Schemes}
-There are 10 primary users and 20 CR users are dropped randomly (with uniform distribution) within a square area of size $A^{2}$, where we set the transmission ranges of primary and CR users to $A/3$.
+There are 10 primary users and 20 CR users dropped randomly (with uniform distribution) within a square area of size $A^{2}$, where we set the transmission ranges of primary and CR users to $A/3$.
 %There are 10 available channels. 
@@
 When clustering scheme is executed, around 7 channels are available on each CR node.
-The desired cluster size $\delta$ is 3, the parameters used in the \textit{punishment} for choosing the clusters with undesired sizes are set as follows, $\alpha_1 =  0.4$, $\alpha_2 =  0.6$.
-
-\subsubsection{Number of CCs in Non-singleton Clusters}
+The desired cluster size $\delta$ is 3.
+As to the centralized scheme, the parameters used in the \textit{punishment} for choosing the clusters with undesired sizes are set as follows, $\alpha_1 =  0.4$, $\alpha_2 =  0.6$.
+
+\subsubsection{Average number of CCs in Non-singleton Clusters}
 \label{ccc_20}
@@
 From Figure~\ref{ccc_per_nonsingleton}, we can see the centralized schemes outperform the distributed schemes.
-As to the distributed schemes, SOC achieves the best than all the variants of ROSS.
-The reason is, SOC is liable to group the neighbouring CRs which share the most abundant spectrum together, no matter how many of them are, thus the number of CC of the formed clusters is higher.
-We have discussed the flaw of this metric as it doesn't convey the number of unclustered CR nodes, in fact, SOC generates the most unclustered CRs, which can be seen when we discuss the performance on the number of unclustered CR nodes.
+Among the distributed schemes, SOC achieves the most CCs.
+The reason is, SOC is liable to group the neighboring CRs which share the most abundant spectrum together, no matter how many of them are there, thus the number of CC of the formed clusters is higher.
+%We have discussed the flaw of this metric as it doesn't convey the number of unclustered CR nodes, in fact, 
+In the other hand, SOC generates the most unclustered CRs, which can be seen when we discuss the performance on the number of unclustered CR nodes. 
 As to the variants of ROSS, we notice that the greedy mechanism increases CCs in non-singleton clusters significantly.
@@
 
-\subsubsection{Cluster Size Control}
+\subsubsection{Cluster Size}
 \label{cluster_size}
@@
 
-Figure~\ref{size_control} depicts the empirical cumulative distribution of the CRs residing in certain sized clusters, from which we have two conclusions.
+Figure~\ref{size_control} depicts the empirical cumulative distribution of the CRs in clusters of different sizes, from which we have two conclusions.
 The first, SOC generates more unclustered CR nodes than other schemes.
-The centralized schemes produce no unclustered CR nodes, ROSS-DGA/DFA generate 3\% unclustered nodes, as comparison, 10\% of nodes are unclustered when applying SOC.
+The centralized schemes don't produce unclustered CR nodes in the simulation, the unclustered nodes generated by ROSS-DGA/DFA account for 3\% of the total CR nodes, as comparison, 10\% of nodes are unclustered when applying SOC.
 ROSS-DGA and ROSS-DFA with size control feature generate 5\%-8\% unclustered CR nodes, which is due to the cluster pruning procedure (discussed in section~\ref{ross_p1_guarantee_ccc} and section~\ref{ross_p2_cluster_pruning}).
-Second, the centralized schemes and cluster size control mechanism of RPSS generate clusters which satisfy the requirement on cluster size strictly.
+Second, the centralized schemes and cluster size control mechanism of ROSS generate clusters with the desired cluster size.
 %When the desired size is 2, each generated cluster has two members, whereas when the desired size is 3, about 15\% CRs are formed into 2 node clusters.
@@
 %ROSS-3-DGA decreases the clusters sizes and results in more 2 node clusters, the second most CRs are found in 3 node clusters.
-The sizes of clusters resulted from ROSS-DGA and ROSS-DFA are disperse, but appear to be better than SOC, i.e., the 50\% percentiles for ROSS-DGA, ROSS-DFA and SOC are 4.5, 5, and 5.5, and the 90\% percentiles for the three schemes are 8, 8, and 9.
+The sizes of clusters resulted from ROSS-DGA and ROSS-DFA are disperse, but appear to be better than SOC, i.e., the 50\% percentiles for ROSS-DGA, ROSS-DFA and SOC are 4.5, 5, and 5.5, and the 90\% percentiles for the three schemes are 8, 8, and 9, the corresponding sizes of ROSS are closer to the desired size.
 %Figure~\ref{size_control} shows distributed clustering schemes are not able to control cluster sizes perfectly, but ROSS-DGA and ROSS-DFA eliminate the clusters whose size diverges largely with the desired one, \ie single node clusters and clusters with size of 13 and 14.
@@
 %First, we will know how many CR nodes are unclusterred by applying the robust clustering schemes in a given CRN.
-We add PUs in the CRN to decrease the available spectrum, and observe the number of unclustered CR nodes.
-Clusters are formed with the presence of 10 PUs in the beginning, then extra 20 batches of PUs are added sequentially, where each batch includes 5 PUs. 
+In this part of simulation, we put PUs sequentially into CRN to decrease the available spectrum.
+10 PUs are in the network in the beginning, then extra 19 batches of PUs are added sequentially, where each batch includes 5 PUs. 
 %The transmission range and channel occupancy of the new PU is the same with the previous ones, \ie transmission range is $A/3$, and one channel out of 10 is randomly chosen to operate.
 
-Figure~\ref{singleton_clusters} shows with the increase of PUs, certain clusters disappear and the number of unclustered CR nodes increases.
-Among the robust clustering schemes, the centralized scheme with desired size of two generates the most robust clusters, meanwhile, SOC results in the most vulnerable clusters.
-The centralized scheme with desired size of three doesn't outperform the variants of ROSS, because the centralized scheme peruses clusters with size of 3 at the expenses of sanctifying CCs.
-In contrary, the variants of ROSS generate some smaller clusters which are more likely to survive when PUs' activities become intense.
+Figure~\ref{singleton_clusters} shows certain clusters can not maintain and the number of unclustered CR nodes grows when the number of PUs increases.
+The centralized scheme with desired size of 2 generates the most robust clusters, meanwhile, SOC results in the most vulnerable clusters.
+The centralized scheme with desired size of 3 doesn't outperform the variants of ROSS, because pursuing cluster size prevents forming the the clusters with more CCs.
+In contrary, the variants of ROSS generate some smaller clusters which are more likely to maintain when there are more PUs.
 %The comparison on cluster sizes will be given in Section~\ref{cluster_size}.
@@
 
-\subsubsection{Control Signalling Overhead}
+\subsubsection{Control Signaling Overhead}
 %Different from the clustering schemes proposed in ~\cite{LIU_TMC11_2, clustering_globecom11}, 
@@
 
-In this section we compare the overhead of signalling involved in different clustering schemes.
+In this section we compare the overhead of signaling involved in different clustering schemes.
 %In order to highlight the amount of control signalling only for clustering, 
-We omit the control messaged involved in neighbourhood discovery, which is the premise for any clustering scheme.
+We don't consider the the control messages which are involved in neighborhood discovery, which is the premise and deemed to be the same for all clustering schemes.
 According to~\cite{complexity_aggregation_2011}, the message complexity is defined as the number of messages used by all nodes.
-To have the same metric to compare, we count \textit{the number of transmissions of control messages}, without distinguishing they are sent with broadcast or unicast.
+To have the same metric to compare, we count \textit{the number of transmissions of control messages}, without distinguishing broadcast or uni-cast control messages.
 This metric is synonymous with \textit{the number of updates} discussed in Section~\ref{ross}.
@@
 In the first phase, when a CR node decides itself to be the cluster head, it broadcasts a message containing its ID, cluster members and the set of CCs in its cluster.
-%As to ROSS with size control feature, there are same amount of cluster heads with ROSS without enabling size control feature, and the cluster head broadcasts the available channels of the pruned cluster.
 In the second phase, a debatable node broadcasts its affiliation to inform its claiming clusters, then the $\text{CH}$s of the claiming clusters  broadcast message about the new cluster members if they are changed due to the debatable node's decision.
-The total number of the decisions involved in cluster formation has been analysed in Theorem~\ref{clustering:theorem} and Section~\ref{clustering:phaseII:game} respectively.
-
-Comparison scheme SOC involves three rounds of execution. 
-In the first two rounds, every CR node maintains its own cluster and seek to integrate neighbouring clusters, or joins one of them.
+The upper bound of the total number of the control messages involved in cluster formation is analyzed in Theorem~\ref{clustering:theorem} and Section~\ref{clustering:phaseII:game}.
+
+The comparison scheme SOC involves three rounds of execution. 
+In the first two rounds, every CR node maintains its own cluster and seeks either to integrate neighboring clusters or to join one neighboring cluster.
 The final clusters are obtained in the third round. 
@@
 The first phase is information aggregation, in which every CR node's channel availability and neighborhood is transmitted to the centralized controller.
-The second phase is broadcasting, where the clustering solution is disseminated to every CR node.
+iIn the second phase, the control broadcasts the clustering solution, which is disseminated to every CR node.
 %
 We adopt the algorithm proposed in~\cite{Efficient_broadcasting_gathering_adhoc} to broadcast and gather information as the algorithm is simple and self-stabilizing.
-This scheme needs building a backbone structure to support the communication, and we apply ROSS to generate cluster heads which serve as the backbone, besides, the debatable nodes as used as the gateway nodes between the backbone nodes.
-As the backbone is built once and support transmission for multiple times, the messages involved in the clustering process are not counted.
-As to the process of information gathering, we assume that every cluster member sends the spectrum availability and its ID to its cluster head, which further forwards or the message to the controller, thus the number of transmission is $N$.
-As to the process of dissemination, in an extreme situation where all the gateway and the backbone nodes broadcast, the number of transmission is $h + m$, where $h$ is the number of cluster heads and $m$ is number of debatable nodes.
+This scheme needs building a backbone structure to support the communication. 
+We apply ROSS to generate cluster heads which serve as the backbone, and the debatable nodes are used as the gateway nodes between the backbone nodes.
+As the backbone is built for one time and supports the transmission of control messages later on, we don't take account the messages involved in building the backbone.
+As to the process of information gathering, we assume that every cluster member sends the spectrum availability and its ID to its cluster head, which further forwards the message to the controller, then the number of transmissions is $N$.
+As to the process of dissemination, in an extreme situation where all the gateway and the backbone nodes broadcast, the number of transmissions is $h + m$, where $h$ is the number of cluster heads and $m$ is number of debatable nodes.
 %, $d$ is the average number of demanding clusters for each debatable node.
 
-The number of control messages which are involved in both ROSS and the centralized scheme is related with the number of debatable nodes.
-Figure~\ref{percentage_overlapping_node} shows the percentage of debatable nodes when the CRN network becomes denser, from which we can obtain the value of $m$.
+The number of control messages which are involved in ROSS variants and the centralized scheme is related with the number of debatable nodes.
+Figure~\ref{percentage_overlapping_node} shows the percentage of debatable nodes with different network densities, from which we can obtain the value of $m$.
 \begin{figure}[ht!]
@@
 %The complexity parameters are the number of nodes $n$ in network, number of clusters $h$.
-The message complexity, quantitative analysis of the number of control messages involved in clustering, and the size of control messages are shown in Table \ref{tab_overhead}.
-%$D(s)$: the maximum distance between centralized controller and CR users.
-%
-Figure~\ref{control_msg} shows the number of transmissions of SOC, the upper bound of the number of transmissions for ROSS, and the analytical number of transmissions of the centralised scheme. 
-%Note that the curve for the centralized scheme is from theoretical analysis, which is $h+m+N$ as discussed beforehand.
-%Note the overhead involved to construct the backbone (clusters) is not included.
+Table \ref{tab_overhead} shows the message complexity, quantitative amount of the control messages, and the size of control messages.
+Figure~\ref{control_msg} shows the analytical result of the amount of transmissions involved in different schemes.
+%the upper bound of the number of transmissions of ROSS, and the analytic number of transmissions of the centralized scheme.
 
@@
 \caption{Signalling overhead}\label{tab_overhead}
+{\renewcommand{\arraystretch}{1.15} %<- modify value to suit your needs
 {\small
 \hfill{}
-\begin{tabular}{|L{2.2 cm}|C{2.8 cm}|C{3.15 cm}|C{6.6 cm}|}
+\begin{threeparttable}
+\begin{tabular}{|C{2 cm}|C{2.8 cm}|C{3.15 cm}|C{7.7 cm}|}
 \hline
  Scheme 				&Message Complexity 	&   Quantitative number of messages 		& Content of message (size of message) 									\\ \hline
- ROSS-DGA, ROSS-$\delta$-DGA 	&$\mathcal{O}(N^3)$ (worst case)		&   $h+2*m^2d$ (upper bound)  				&   \multirow{2}{*}{\parbox{6.4cm}{Cluster head broadcasts cluster composition ($|C(i)|* |\mathcal{K}|$ bytes).
-Cluster members broadcast the manipulated new individual connectivity degree (1 byte)}}								\\ \cline{1-3}
+ ROSS-DGA, ROSS-$\delta$-DGA 	&$\mathcal{O}(N^3)$ (worst case)		&   $h+2m^2d$ (upper bound)  				&   \multirow{2}{*}{\parbox{7.7cm}{Cluster head $i$ broadcasts channel availability on all cluster members ($|C(i)| |\mathcal{K}|$ bytes); Cluster member $i$ broadcasts the new individual connectivity $d_i$ after being included in one or more clusters (1 byte)}}								\\ \cline{1-3}
  ROSS-DFA, ROSS-$\delta$-DFA 	&$\mathcal{O}(N)$ (worst case)		&   $h + 2m$	 (upper bound) 					& 	      												\\ \hline
- SOC 					&$\mathcal{O}(N)$		&   $3*N$									& $C(i)$ ($|C(i)|$ bytes) and $K(C(i))$ ($|\mathcal{P}|$ bytes), $i\in \mathcal{N}$						\\ \hline
- Centralized			&$\mathcal{O}(N)$			&	$h + m + N$ (upper bound)~\cite{Efficient_broadcasting_gathering_adhoc}		& $\{C\}$ ($|C_i|*N$ bytes)        					\\ \hline
+ SOC 					&$\mathcal{O}(N)$		&   $3N$									& Every CR node $i$ broadcasts channel availability on all cluster members ($|C(i)| |\mathcal{K}|$ bytes)
+ \\ \hline
+ Centralized			&$\mathcal{O}(N)$			&	$h + m + N$ (upper bound)~\cite{Efficient_broadcasting_gathering_adhoc}		& clustering result (2$N$ bytes) \tnotex{tnote:robots-r1} 					\\ \hline
 \end{tabular}
+    \begin{tablenotes}
+      \item\label{tnote:robots-r1}Assuming the data structure of the clustering result is given as \{ Node ID $i$, cluster head ID h($C$) where $i\in C$, $i\in \mathcal{N}$ \}.
+    \end{tablenotes}
+    \end{threeparttable}
+}
 }
@@
 \end{center}
-% centralized: $\mathcal{O}(D(s)+log N)$ + $\mathcal{O}(1+D(s)+log N)$
 
@@
   \includegraphics[width=0.6\linewidth]{number_controlMsg.pdf}
-  \caption{Number of control messages. Note the curves of ROSS-DGA and ROSS-DFA are the upper bounds}
+  \caption{Quantitative amount of control messages.}
   \label{control_msg}
@@
 In this section we investigate the performances of distributed clustering schemes in CRN with different network scales and densities.
-The transmission range of CR is $A/5$, PR's transmission range is $2A/5$.
+The transmission range of CR is $A/5$, PU's transmission range is $2A/5$.
 The initial number of PU is 30.
@@
 The desired sizes adopted are listed in the Table~\ref{Simulation_para}, which is about 60\% of the average number of neighbours.
+When run ROSS, the parameter $t$ which is used to control cluster size in phase I is 1.3.
 
@@
 %When the network becomes denser, more clusters are generated by SOC compared with ROSS variants.
-To better understand the distribution of the sizes of formed clusters, we depict the empirical cumulative distribution of CR nodes which reside in clusters with certain sizes in CRNs in Figures~\ref{cdf_clusterSize_100}~\ref{cdf_clusterSize_200}~\ref{cdf_clusterSize_300}.
-
-%In this group of evaluation, the number of PRs is 30.
+To better understand the distribution of the sizes of formed clusters, we depict the empirical cumulative distribution of CR nodes in clusters with different sizes in Figures~\ref{cdf_clusterSize_100}~\ref{cdf_clusterSize_200}~\ref{cdf_clusterSize_300}.
 
@@
 
-Overviewing Figure~\ref{cdf_100_200_300}, we conclude that the sizes of the clusters generated by ROSS are limited by the network density, the sizes of the clusters formed by ROSS with size control feature are restricted by the desired size.
+From Figure~\ref{cdf_100_200_300}, we conclude that the sizes of the clusters generated by ROSS are limited by the network density, the sizes of the clusters formed by ROSS with size control feature are restricted by the desired size.
 In contrary, the clusters generated from SOC demonstrate strong divergence on cluster sizes.
 
-\subsection{Insights from the Simulation}
-The centralized clustering scheme can form the clusters which satisfy the requirement on cluster size strictly, and the clusters are robust against the newly added PUs, besides, it generates the smallest control overhead in the process of cluster formation.
-
-As distributed schemes, ROSS outperform the comparison scheme SOC considerately on three metrics.
-ROSS generates much less singleton clusters than SOC, and the resulted clusters are robuster than SOC in front of newly added PUs.
-The signalling overhead involved in ROSS is about half of that needed for SOC, and the signalling messages are much shorter that the latter.
-The sizes of the clusters which are generated by ROSS are restricted by the network density, which demonstrate smaller discrepancy than that of SOC.
-%
-Besides, ROSS achieves similar performance to the centralized scheme, \ie the cluster sizes obtained by ROSS with size control feature are limited by the desired size, and the cluster robustness is similar when applying the variants of ROSS and the centralized scheme respectively.
-As to the variants of ROSS, the greedy mechanism in ROSS-DGA helps to improve the performance on cluster size and cluster robustness at the cost of mildly increased signalling overhead.
-
+\subsection{Insights Obtained from the Simulation}
+The centralized clustering scheme is able to form the clusters which satisfy the requirement on cluster size strictly, and the clusters are robust against the PUs' activity, besides, it generates the smallest control overhead in the process of clustering.
+
+As distributed schemes, the variants of ROSS outperform SOC considerately on three metrics.
+The variants of ROSS generate much less singleton clusters than SOC, and the resulted clusters are robuster than SOC when facing the newly added PUs.
+The signaling overhead involved in ROSS is about half of that needed for SOC, and the signaling messages are much shorter that the latter.
+The sizes of the clusters generated by ROSS demonstrate smaller discrepancy than that of SOC.
+Besides, the ROSS variants with size control features achieve similar performance to the centralized scheme in terms of cluster size, and the cluster robustness is similar when applying the variants of ROSS and the centralized scheme respectively.
+
+As to the variants of ROSS, the greedy mechanism in ROSS-DGA helps to improve the performance on cluster size and cluster robustness at the cost of mildly increased signaling overhead.
 We also notice that  as a metric, the number of CCs per non-singleton cluster doesn't indicate the robustness of clusters as shown in Figure~\ref{singleton_clusters} and \ref{unclustered_100_200_300}, although it is adopted as the metric in the formation of clusters.
@@
 In this paper we investigate the robust clustering problem in CRN extensively.
-The proposed scheme results in a cluster structure in CRN, which has longer time expectancy against the primary users' activity.
-Besides, the clusters generated have similar sizes compared with other distributed schemes.
 %generate robust clusters against primary users' influence, so that more CR users can benefit from operative decision making provided by the clusters.
 We provide the mathematical description of the problem and prove the NP hardness of it.
-We propose both centralized and distributed schemes, where the congestion game model in game theory is used to design the distributed schemes.
+We propose both centralized and distributed schemes ROSS, the cluster structure generated by them has longer time expectancy against the primary users' activity.
+Besides, the proposed schemes can generate clusters with desired sizes.
+The congestion game model in game theory is used to design the distributed schemes.
 %A Light weighted clustering scheme ROSS is also proposed.
@@
 
-The shortage of ROSS scheme is it doesn't generate big clusters whose sizes exceed the cluster head's neighborhood.
-This problem is attributed to fact that ROSS forms clusters on the basis of cluster head's neighborhood, and doesn't involve interaction with the nodes outside its neighborhood.
-In the other way around, forming big cluster which extends a cluster head's neighborhood has limited applications, as multiple hop communication and coordination are required within such clusters.
+The shortcoming of distributed scheme ROSS is it doesn't generate clusters whose sizes exceed the cluster head's neighborhood.
+The reason is with ROSS, cluster heads form clusters on the basis of their neighborhood, and don't involve the nodes which are outside the neighborhood.
+In the other way around, forming big cluster which extends a cluster head's neighborhood has limited application scenarios, as multiple hop communication and coordination are required within these clusters.
 
@@
 \While {$K_C =\emptyset$} {
-\While{$|C|> \delta$}{
+\While{$|C|> t\cdot \delta$}{
 	%calculate $\lambda = \min_{i\in C, i\neq H_C}(|K_{H_C}\cap K_i|)$;\\
@@
 \begin{proof}
-We put the definition of weighted k-set packing problem here as it to be used in the analysis on the complexity of the centralised clustering problem.
-
+To prove the robust clustering problem is NP-hard, we reduce the NP-hard problem \textit{weighted k-set packing} to it to show the robust clustering problem is at least as hard as the weighted $k$-set packing problem.
+The definition of weighted $k$-set packing problem is given as bellow.
 \begin{mydef}
@@
 
-Given a finite set $\mathcal{G} = \{ g_1, \ldots , g_N \} \subsetneq \mathbb{N}$ of non-negative integers and a collection of sets $\mathcal{Q}=\{S_1,S_2,\cdots,S_m\}$ such that $S_i \subseteq \mathcal{G}$ for every $1 \leq i \leq N$.
-Each set $S \in \mathcal{Q}$ is associated with a weight $\omega(S) \in \mathbb{R}$.
-Further, we are given a threshold value $\lambda \in \mathbb{N}$.\\
-The question is whether there exists a collection $\mathcal{S} \subseteq \mathcal{Q}$ such that $\mathcal{S}$ contains only pairwise disjoint sets, i.e., for all $S, S' \in \mathcal{S}$ with $S \neq S'$ it holds that $S \cap S' = \emptyset$, and the total weight of the sets in $\mathcal{S}$ is greater than $\lambda$, i.e., $\sum_{S \in \mathcal{S}} \omega(S) > \lambda$.
+Given a finite set $\mathcal{G}$ of non-negative integers where $\mathcal{G} \subsetneq \mathbb{N}$, and a collection of sets $\mathcal{Q}=\{S_1,S_2,\cdots,S_m\}$ where $S_i \subseteq \mathcal{G}$ for $1 \leq i \leq m$, besides, every set $S$ in $\mathcal{Q}$ has a weight $\omega(S) \in \mathbb{R}$.
+%Further, we are given a threshold value $\lambda \in \mathbb{N}$.\\
+The weighted $k$-set packing problem is to find a collection $\mathcal{S} \subseteq \mathcal{Q}$ such that $\mathcal{S}$ contains only pairwise disjoint sets and the total weight of the sets in $\mathcal{S}$ is greater than a given positive number $\lambda$, i.e., $\sum_{S \in \mathcal{S}} \omega(S) > \lambda$.
 \end{mydef}
 
-Weighted k-set packing is NP-hard when $k\geqslant 3$.~\cite{Computers_a_Intractability}
-
-To prove that the centralized clustering problem is NP-hard, we reduce the NP-hard problem \textit{weighted k-set packing} to it to prove the former is at least as hard as the latter.
-%, which means centralized clustering in CRN problem is as hard as weighted k-set packing to be solved.
-%To complete the reduction, we need to conduct following two steps:
-%\begin{itemize}
-%\item Step 1: We show the existence a polynomial algorithm $\sigma$, by which any instance $\mathcal{S}$ of a weighted k-set packing can be transformed to a clustering solution $\sigma(\mathcal{S})$ which complies with Definition~\ref{def_centralized_clustering}.
-%\item Step 2: Show that $\mathcal{S}$ is a \textit{yes} instance of weighted k-set packing if and only if $\sigma(\mathcal{S})$ is a \textit{yes} instance for CRN clustering problem.
-%\end{itemize}
-We show the existence of a polynomial-time algorithm $\sigma$ that transforms any instance $\mathcal{I}$ of a weighted $k$-set packing into an instance $\sigma(\mathcal{I})$) of centralized clustering problem.
-
-%We continue to use the notation adopted in the problem definition in Section~\ref{centralized_opt}.
+Weighted $k$-set packing is known to be NP-hard when $k\geqslant 3$~\cite{Computers_a_Intractability}.
+In the proof, we will show the existence of a polynomial-time algorithm $\sigma$ which transforms any instance $\mathcal{I}$ of a weighted $k$-set packing problem, \ie a collection of sets, into a formation of clusters for the robust clustering problem.
 W.l.o.g. let set $\mathcal{G} = \{ 1, \ldots , N \}$.
-%$\mathcal{Q}$ is a collection of sets $\{s_1, s_2,\cdots s_m\}$, each set is composed with certain elements in $\mathcal{G}$. REPEATING THE DEF??
-%Assume $\mathcal{S}\subseteq \mathcal{Q}$ is one instance of weighted k-set packing, and the sets in $\mathcal{S}$ are disjoint.
-%$\omega$ indicates the weight for each set $s$, $\omega:\mathcal{S}\rightarrow \mathbb{Z}^{+}$. COMMENT: again unnecessary. Already contained in the definition!
-%As the number of common channel of clusters is always integer
-%give new weight to them in following way
-The polynomial algorithm $\sigma$ consists of three steps.
+The polynomial algorithm $\sigma$ consists of four steps.
 
@@
 
-\item In the first step, we transform the instance $\mathcal{I}$ to $\mathcal{I'}$ by adding dummy elements into each set in $\mathcal{I}$.
-Formally, for each set $s_i\in \mathcal{I}$, we create $s_i' = s_i \times \{ 1,2\}$.
-Then we change the dummy elements by adding $N$ on them.
- %for instance, given $s_i=\{1, 4, 6\}$, the dummy set $s_i'$ is $\{1,1',4,4',6,6' \}$.
-%By doing this, we obtain the dummy sets and constitute the dummy instance $\mathcal{S}'$ based on $\mathcal{S}$.
-The purpose of this transformation is to eliminate the set in $\mathcal{I}$, which has single element.
-The weight of these sets remain unchanged, \ie $\omega(s_i') = \omega(s_i)$.
-%After this transmission, there is no set with only one element.
-%This transformation requires $\sum_{s_i \in \mathcal{S}} |s_i|$ steps.
-
-\item Mapping the elements in $\mathcal{I'}$ to CR nodes on a two-dimensional Euclidean plane, and mapping the sets in $\mathcal{I'}$ to clusters.
-There is a bijection between the union of sets in $\mathcal{I'}$ to the CRN which consists of the CR nodes, in particular, each element one-to-one corresponds to the CR node whose node ID equals to the element.
+\item In the first step, we transform the instance $\mathcal{I}$ to $\mathcal{I'}$ by duplicating the elements of the sets in $\mathcal{I}$.
+In particular, as to each set $S\in \mathcal{I}$, we duplicate every element and assign a new value to the new element, which is N bigger than the original element.
+%Formally, for each set $s_i\in \mathcal{I}$, we create $s_i' = s_i \times \{ 1,2\}$.
+%Then we change the dummy elements by adding $N$ on them.
+The purpose of this transformation is to eliminate the set in $\mathcal{I}$, which has only one element.
+The weight of these sets remain unchanged.
+
+\item In the second step, all the elements in $\mathcal{I'}$ are mapped to CR nodes on a two-dimensional Euclidean plane.
+In particular, there is a bijection between every element in $\mathcal{I'}$ to one CR node whose ID is identical with the element value.
 %Given a collection $\mathcal{Q}$, on basis of which we construct a CRN. (I DON'T UNDERSTAND THAT. What do you mean?)
@@
 %We define a set of CR nodes $\mathcal{N} = \{ 1, \ldots , N \}$
-We further regulate that, each set in $\mathcal{I'}$ has a corresponding cluster, \ie there is a bijection between a set in $\mathcal{I'}$ and a set of node IDs in a cluster, besides, the number of CCs is equal to the weight of the corresponding set.
+Accordingly, there is also a bijection between a set in $\mathcal{I'}$ and a cluster in the CRN.
+We regulate the number of CCs is equal to the weight of the corresponding set.
 
@@
 %%When $s_1'$ and $s_2'$ are mapped to CRN respectively, there is contradiction between them, because the number of common channels of CR node group $\{1,1,2,2\}$ is smaller than that of $\{1,1,2,2,3,3,4,4\}$.
-%But as to any instance of the solution to the weighted k-set packing problem, this contradiction doesn't happen because the instance $\mathcal{S}$ contains only disjoint sets, thus at most only one set of $s_1$ and $s_2$ appears in $\mathcal{S}$.%, then we can safely delete the connections based on the deleted set from the CRN, and the contradiction is eliminated.
+%But as to any instance of the solution to the weighted $k$-set packing problem, this contradiction doesn't happen because the instance $\mathcal{S}$ contains only disjoint sets, thus at most only one set of $s_1$ and $s_2$ appears in $\mathcal{S}$.%, then we can safely delete the connections based on the deleted set from the CRN, and the contradiction is eliminated.
 %(THIS PARAGRAPH IS TOO DIFFICULT FOR ME TO UNDERSTAND.)
 
-\item In this step, we transform the instance $\mathcal{I'}$ to a clustering proposal for CRN.
+\item In this step, we transform the instance $\mathcal{I}$ to a formation of clusters for CRN.
 %We prepare a second pool of CR nodes which are identical with the CR nodes prepared in step 1, i.e., identical IDs and channel availabilities on them, we call these CR nodes dummy nodes.
-We adjust the locations of the CR nodes which are mapped from the dummy elements in the instance $\mathcal{I'}$, and let them beside the CR nodes whose ID is exact $N$ smaller.
+We adjust the locations of the CR nodes so that one pair of CR nodes whose IDs are exact $N$ apart are neighbors to each other.
 % (THAT DOESN'T MAKE SENSE.
@@
 (YOU DON'T NEED TO GIVE PRACTICAL MOTIVATION IN A HARDNESS-PROOF.)
-Because of the dummy nodes, the clustering solution which corresponds to $\mathcal{I'}$ doesn't have singleton cluster.
-This transformation requires $2\cdot\sum_{s_i \in \mathcal{I'}} |s_i|$ steps.
-%
-Now we look back to the elements in $\mathcal{Q}$, which don't appear in $\mathcal{I'}$. 
-We one-to-one map these elements to CR nodes, and arbitrarily put these CR nodes in the plane, and these CR nodes become single node clusters.
-According to the definition of clustering problem in CRN, the number of CCs in these single node clusters is 0.
-These singleton clusters and the clusters mapped from $\mathcal{I'}$ constitute a clustering proposal, and finding these singleton clusters requires at most $N$ steps.
+Because of the CR nodes which are mapped from the duplicated elements in $\mathcal{I'}$, there is no singleton cluster.
+This transformation requires $2\cdot\sum_{S_i \in \mathcal{I'}} |S_i|$ steps.
+%
+\item Now we map the elements in $\mathcal{Q}\setminus \mathcal{I}$ to CR nodes. 
+We arbitrarily put these CR nodes in the plane, and these CR nodes form single node clusters by themselves.
+According to the definition of robust clustering problem in CRN, the number of CCs in these single node clusters is 0.
+These singleton clusters and the clusters mapped from $\mathcal{I'}$ constitute a clustering solution, and finding these singleton clusters requires at most $N$ steps.
 %We deliberately locate them so that at least one CR node can communicate with the rest of them.
@@
 %
-An example is shown in Table~\ref{no_hard_proof_instance}.
+
+%As to duplicated elements, we also map them into a CR node, thus there exist CR nodes with identical ID.
+%As a result, these CR nodes constitute a collection of CR nodes, and they can not be called as a CRN yet as there are not communication links drawn between them.
+%Connections in CRN under this context is decided by physical conditions, which means to have a communication link, the two CR nodes should have common channels and locate within each other's transmission range.
+%We further assume that all CR nodes locate in a way that any two pair of nodes has potential to be connected if their IDs are in the same set in $\mathcal{S}$, the instance for weighted $k$-set packing.
+%\item Mere isolated nodes don't constitute network, thus we add connections in CRN based on the sets in $\mathcal{S}'$ sequentially.
+%For each set $s'\in \mathcal{S}'$, we add connection between two CR nodes if their IDs can be found in $s'$.
+%No connection exists between two CR nodes if their IDs don't appear in the same set in $\mathcal{S}$.
+
+%We complete the polynomial algorithm $\sigma$ for the the transformation so far.
+%The number of common channels of cluster $f$ is non-increasing function of cluster size, while, the weight of set in weighted $k$-set packing problem doesn't have this property.
+%In weighted $k$-set packing, the weight of a set with smaller size could be larger than a set with more elements.
+%But this difference doesn't hinder the transformation because an instance of weighted $k$-set packing contains only disjoint sets in $\mathcal{G}$.
+
+\end{itemize}
+
+We have crossed the hurdle of finding one polynomial algorithm $\sigma$ which transforms an instance of weighted $k$-set packing to an instance of the clustering problem in CRN.
+%Now we look into the step 2 in the reduction.
+When $\mathcal{I}$ is not an instance for weighted $k$-set packing problem due to the existence of joint sets, the corresponding cluster strategy is not a solution for the centralized clustering problem, as there are overlapped clusters.
+
+When there are only disjoint sets in an instance $\mathcal{I}$ for weighted $k$-set packing, the sum of weights is identical to the sum of the numbers of CCs in the CRN which are mapped from $\mathcal{I'}$, even $\mathcal{I}$ contains sets which only have one element.
+Thus, when a instance $\mathcal{I}$ for $k$-set packing problem is true, \ie the sum of weights is greater than $\lambda$, then in the CRN which is mapped from $\mathcal{I'}$, the sum of the numbers of CCs of the clusters is greater than $\lambda$.
+In the other way around, when an instance is false for weighted $k$-set packing problem, the sum of the numbers of CCs of the clusters in the mapped CRN is smaller than $\lambda$, then the formation of the clusters is not a solution for the robust clustering problem.
+
+Hence, the weighted $k$-set packing can be reduced to the robust clustering problem in CRN, then the latter problem is of NP-hard.
+An example of the reduction is shown in Table~\ref{no_hard_proof_instance}.
 \begin{table}[h!]
      \begin{center}
-     \begin{tabular}{ p{3cm}  p{4.5cm} }
+     \begin{tabular}{ C{3cm}  C{4.5cm} }
      \toprule
@@
     \cmidrule(r){1-1}\cmidrule(lr){2-2}     
-      Instance for Weighted k-set packing  & $\{ \{1\}, \{2,3\}, \{4\} \}$\\ 
+      Instance for Weighted $k$-set packing  & $\{ \{1\}, \{2,3\}, \{4\} \}$\\ 
     \cmidrule(r){1-1}\cmidrule(lr){2-2}
-      Instance with dummy elements
+      Instance with dummy elements (step 1)
       & 
@@
       \\    \cmidrule(r){1-1}\cmidrule(lr){2-2}
-	Instance for clustering solution (dashed circles are dummy nodes)
+	clusters mapped from $\mathcal{I}$  (step 2 \& 3)
 	  &
-	  %\raisebox{-\totalheight}{\includegraphics[width=0.8\linewidth]{np_hard_proof_dummy.pdf}}      
 	  \begin{minipage}{.3\textwidth}	
-      \includegraphics[width=0.6\linewidth]{np_hard_proof_dummy.pdf}
+      \includegraphics[width=0.6\linewidth]{np_hard_proof_step_2_3.pdf}
+    \end{minipage}
+          \\    \cmidrule(r){1-1}\cmidrule(lr){2-2}
+	formation of clusters (step 4)
+	  &
+	  \begin{minipage}{.3\textwidth}	
+      \includegraphics[width=0.6\linewidth]{np_hard_proof_step4.pdf}
     \end{minipage}
@@
 
-%As to duplicated elements, we also map them into a CR node, thus there exist CR nodes with identical ID.
-%As a result, these CR nodes constitute a collection of CR nodes, and they can not be called as a CRN yet as there are not communication links drawn between them.
-%Connections in CRN under this context is decided by physical conditions, which means to have a communication link, the two CR nodes should have common channels and locate within each other's transmission range.
-%We further assume that all CR nodes locate in a way that any two pair of nodes has potential to be connected if their IDs are in the same set in $\mathcal{S}$, the instance for weighted k-set packing.
-%\item Mere isolated nodes don't constitute network, thus we add connections in CRN based on the sets in $\mathcal{S}'$ sequentially.
-%For each set $s'\in \mathcal{S}'$, we add connection between two CR nodes if their IDs can be found in $s'$.
-%No connection exists between two CR nodes if their IDs don't appear in the same set in $\mathcal{S}$.
-
-%We complete the polynomial algorithm $\sigma$ for the the transformation so far.
-%The number of common channels of cluster $f$ is non-increasing function of cluster size, while, the weight of set in weighted k-set packing problem doesn't have this property.
-%In weighted k-set packing, the weight of a set with smaller size could be larger than a set with more elements.
-%But this difference doesn't hinder the transformation because an instance of weighted k-set packing contains only disjoint sets in $\mathcal{G}$.
-
-\end{itemize}
-
-We have crossed the hurdle of finding one polynomial algorithm $\sigma$ which transforms an instance of weighted k-set packing to an instance of the clustering problem in CRN.
-%Now we look into the step 2 in the reduction.
-When $\mathcal{I}$ is not an instance for weighted k-set packing problem due to the existence of joint sets, the corresponding cluster strategy is not a solution for the centralized clustering problem, as there are overlapped clusters.
-
-When there are only disjoint sets in an instance $\mathcal{I}$ for weighted k-set packing, the sum of weights is identical to the sum of the numbers of CCs in the CRN mapped from $\mathcal{I'}$, even $\mathcal{I}$ contains sets which only have one element.
-Thus, when a instance $\mathcal{I}$ for k-set packing problem is true, \ie the sum of weights is greater than $\lambda$, then in the CRN which is mapped from $\mathcal{I'}$, the sum of the numbers of CCs of the clusters is greater than $\lambda$.
-In the other way around, when an instance if false for weighted k-set packing problem,
-%let's assume the maximum sum of weights of all instances is $\sum_{s_i\in \mathcal{S}}\omega(s_i)=\delta < \lambda$. 
-%The dummy set of each $s_i\in \mathcal{S}$ is mapped to cluster of CR nodes.
-%Definition of CRN clustering regulates that the number of common channels is 0 when the cluster has only one node.
-%As to $|s_i|=1$, the mapped cluster has two nodes, with one of them is the dummy CR node.
-%Then number of common channels is on longer 0 but equals to the weight of corresponding set $s_i$.
-%%Meanwhile, the number of common channels of all the other single node cluster is 0.
-the sum of the numbers of CCs of the clusters in the mapped CRN is smaller than $\lambda$, and there is no clustering solution satisfying the centralized clustering problem.
-
-%When an instance $\mathcal{I}$ contains joint sets, there will be overlapped clusters among the mapped clusters, then neither is solution to their corresponding problem.
-
-Thus, weighted k-set packing can be reduced to clustering problem in CRN, then the latter problem is of NP-hard.
 \end{proof}

### 2016-11-13 journal-draft/bare_jrnl_comsoc.tex
before final modification

@@
 
-Then the robust clustering problem is to find a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, so that the sum of the numbers of CCs of the formed clusters $\sum_{C\in \mathcal{S}'} (f(C)\cdot|C|)$ is maximized.
+Then the robust clustering problem is to find a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, so that the sum of the numbers of CCs of the formed clusters $\sum_{C\in \mathcal{S}'} f(C)$ is maximized.
 Besides, the formed clusters should satisfy the requirements on cluster sizes, for example, all the formed clusters should have the same desired size $\delta$, or the sizes should be within a scope $\langle\delta_1, \delta_2\rangle$, where $\delta, \delta_1, \delta_2\in \mathbb{Z}^+$, and $\delta_1 < \delta_2$.
@@
 \begin{proof}
-To prove the robust clustering problem is NP-hard, we reduce the NP-hard problem \textit{weighted k-set packing} to it to show the robust clustering problem is at least as hard as the weighted $k$-set packing problem.
-The definition of weighted $k$-set packing problem is given as bellow.
+To prove the robust clustering problem is NP-hard, we reduce the \textit{maximum weighted k-set packing problem}, which is NP-hard when $k\geqslant 3$~\cite{Computers_a_Intractability}, to the the robust clustering problem to show the latter is at least as hard as the former.
+Given a collection of sets of cardinality at most $k$ with weights for each set, the maximum weighted packing problem is that of finding a collection of disjoint sets of maximum total weight.
+The decision version of weighted $k$-set packing problem is,
 \begin{mydef}
 \label{def_kset_packing}
-\textit{Weighted k-set packing.}
-
-Given a finite set $\mathcal{G}$ of non-negative integers where $\mathcal{G} \subsetneq \mathbb{N}$, and a collection of sets $\mathcal{Q}=\{S_1,S_2,\cdots,S_m\}$ where $S_i \subseteq \mathcal{G}$ for $1 \leq i \leq m$, besides, every set $S$ in $\mathcal{Q}$ has a weight $\omega(S) \in \mathbb{R}$.
-%Further, we are given a threshold value $\lambda \in \mathbb{N}$.\\
-The weighted $k$-set packing problem is to find a collection $\mathcal{S} \subseteq \mathcal{Q}$ such that $\mathcal{S}$ contains only pairwise disjoint sets and the total weight of the sets in $\mathcal{S}$ is greater than a given positive number $\lambda$, i.e., $\sum_{S \in \mathcal{S}} \omega(S) > \lambda$.
+Given a finite set $\mathcal{G}$ of non-negative integers where $\mathcal{G} \subsetneq \mathbb{N}$, and a collection of sets $\mathcal{Q}=\{S_1,S_2,\cdots,S_m\}$ where $S_i \subseteq \mathcal{G}$ for $1 \leq i \leq m$, every set $S$ in $\mathcal{Q}$ has a weight $\omega(S) \in \mathbb{R}$.
+%
+The problem is to find a collection $\mathcal{S} \subseteq \mathcal{Q}$ such that $\mathcal{S}$ contains only pairwise disjoint sets and the total weight of the sets in $\mathcal{S}$ is greater than a given positive number $\lambda$, i.e., $\sum_{S \in \mathcal{S}} \omega(S) > \lambda$.
 \end{mydef}
 
-Weighted $k$-set packing is known to be NP-hard when $k\geqslant 3$~\cite{Computers_a_Intractability}.
-In the proof, we will show the existence of a polynomial-time algorithm $\sigma$ which transforms any instance $\mathcal{I}$ of a weighted $k$-set packing problem, \ie a collection of sets, into a formation of clusters for the robust clustering problem.
+We assume the weights of sets are positive integers.
+Then we will show the existence of a polynomial-time algorithm $\sigma$ which transforms any instance $\mathcal{I}$ of a weighted $k$-set packing problem, \ie a collection of sets, into a formation of clusters for a CRN.
 W.l.o.g. let set $\mathcal{G} = \{ 1, \ldots , N \}$.
-The polynomial algorithm $\sigma$ consists of four steps.
+The polynomial algorithm $\sigma$ consists of three steps.
 
@@
 \item In the first step, we transform the instance $\mathcal{I}$ to $\mathcal{I'}$ by duplicating the elements of the sets in $\mathcal{I}$.
-In particular, as to each set $S\in \mathcal{I}$, we duplicate every element and assign a new value to the new element, which is N bigger than the original element.
-%Formally, for each set $s_i\in \mathcal{I}$, we create $s_i' = s_i \times \{ 1,2\}$.
-%Then we change the dummy elements by adding $N$ on them.
+In particular, as to each element in set $S\in \mathcal{I}$, we duplicate the element and assign a new index which is N bigger than the original index.
+The weight of these sets remain unchanged.
 The purpose of this transformation is to eliminate the set in $\mathcal{I}$, which has only one element.
-The weight of these sets remain unchanged.
-
-\item In the second step, all the elements in $\mathcal{I'}$ are mapped to CR nodes on a two-dimensional Euclidean plane.
-In particular, there is a bijection between every element in $\mathcal{I'}$ to one CR node whose ID is identical with the element value.
-%Given a collection $\mathcal{Q}$, on basis of which we construct a CRN. (I DON'T UNDERSTAND THAT. What do you mean?)
-%We prepare $N$ CR nodes who are labelled from 1 to $N$, put them on a 2 dimension space, and deem a pair of them can communicate if they appear in one same set in $\mathcal{Q}$.
-%We define a set of CR nodes $\mathcal{N} = \{ 1, \ldots , N \}$
-Accordingly, there is also a bijection between a set in $\mathcal{I'}$ and a cluster in the CRN.
-We regulate the number of CCs is equal to the weight of the corresponding set.
-
-%%There is one situation deserving extra explanation in the second transformation, we adopt one example to discuss it.
-%Assuming two sets in $\mathcal{Q}$ are $s_1=\{1,2\}$ and $s_2=\{1,2,3\}$, then their weights are 3 and 5 respectively. (THAT'S TOO HAND-WAVY.)
-%%Their dummy sets are $s_1'=\{1,1,2,2\}$ and $s_2'=\{1,1,2,2,3,3,4,4\}$ and their new weights are 3 and 5 as before.
-%We find it is impossible to map the sets into clusters in the same time (SORRY, which sets??
-The sets you mentioned before are already clusters, isn't it?), because the number of CCs of the cluster which bases on $s_1$ should be no less than the cluster which bases on $s_2$, as the latter has one extra node compared with the former cluster.
-%%When $s_1'$ and $s_2'$ are mapped to CRN respectively, there is contradiction between them, because the number of common channels of CR node group $\{1,1,2,2\}$ is smaller than that of $\{1,1,2,2,3,3,4,4\}$.
-%But as to any instance of the solution to the weighted $k$-set packing problem, this contradiction doesn't happen because the instance $\mathcal{S}$ contains only disjoint sets, thus at most only one set of $s_1$ and $s_2$ appears in $\mathcal{S}$.%, then we can safely delete the connections based on the deleted set from the CRN, and the contradiction is eliminated.
-%(THIS PARAGRAPH IS TOO DIFFICULT FOR ME TO UNDERSTAND.)
-
-\item In this step, we transform the instance $\mathcal{I}$ to a formation of clusters for CRN.
-%We prepare a second pool of CR nodes which are identical with the CR nodes prepared in step 1, i.e., identical IDs and channel availabilities on them, we call these CR nodes dummy nodes.
-We adjust the locations of the CR nodes so that one pair of CR nodes whose IDs are exact $N$ apart are neighbors to each other.
-% (THAT DOESN'T MAKE SENSE.
-THEN THE ID IS NOT UNIQUE ANYMORE.) in the CRN built in step 1, and there is connection between the CR node and its dummy node (the one CR node and its dummy node can be seen as two transceivers at one node).
-(YOU DON'T NEED TO GIVE PRACTICAL MOTIVATION IN A HARDNESS-PROOF.)
-Because of the CR nodes which are mapped from the duplicated elements in $\mathcal{I'}$, there is no singleton cluster.
-This transformation requires $2\cdot\sum_{S_i \in \mathcal{I'}} |S_i|$ steps.
-%
-\item Now we map the elements in $\mathcal{Q}\setminus \mathcal{I}$ to CR nodes. 
-We arbitrarily put these CR nodes in the plane, and these CR nodes form single node clusters by themselves.
-According to the definition of robust clustering problem in CRN, the number of CCs in these single node clusters is 0.
-These singleton clusters and the clusters mapped from $\mathcal{I'}$ constitute a clustering solution, and finding these singleton clusters requires at most $N$ steps.
-%We deliberately locate them so that at least one CR node can communicate with the rest of them.
-%map every element in $\mathcal{S}$ into one CR node, \ie each integer corresponds to one CR node, in particular, that integer becomes the CR node's ID.
-%As $s'$ is dummy set which has duplicated elements, we also deploy the the same CR node twice.
-%
+
+\item In the second step, all the elements in $\mathcal{I'}$ are mapped to CR nodes on a two-dimensional Euclidean plane, where the CR user ID is identical with the corresponding element's index.
+In particular, as to each set $S\in \mathcal{I'}$, we set up a cluster $C$ which consists of the CR users mapped from the elements in $S$, and we assign the available channels for each cluster member so that $|K(C)|$ equals to the $\omega(S)$.
+The channel availability on the CR nodes whose IDs are $N$ apart is the same.
+%Besides, there is a bijection between every set in $\mathcal{I'}$ and one cluster in the CRN.
+%In this process, we decide the channel availability on each CR node so that the number of CCs in each cluster is equal to the weight of the corresponding set.
+%
+When there are two sets in $\mathcal{I'}$ and one is a subset of the other one, \ie  $S_1\subset S_2$, and $\omega(S_1) < \omega(S_2)$, then we should swap the weights of the sets before mapping them into clusters.
+
+\item In this step, we map the elements in $\mathcal{Q}\setminus \mathcal{I}$ to CR nodes. 
+We arbitrarily put these CR nodes in the CRN, then these CR nodes form singleton clusters by themselves.
+According to the definition of robust clustering problem in CRN, the number of CCs of these singleton clusters is 0.
+These singleton clusters and the clusters mapped from $\mathcal{I'}$ constitute a clustering solution.
+
+% finding these singleton clusters requires at most $N$ steps.
 
@@
 %Now we look into the step 2 in the reduction.
-When $\mathcal{I}$ is not an instance for weighted $k$-set packing problem due to the existence of joint sets, the corresponding cluster strategy is not a solution for the centralized clustering problem, as there are overlapped clusters.
-
-When there are only disjoint sets in an instance $\mathcal{I}$ for weighted $k$-set packing, the sum of weights is identical to the sum of the numbers of CCs in the CRN which are mapped from $\mathcal{I'}$, even $\mathcal{I}$ contains sets which only have one element.
-Thus, when a instance $\mathcal{I}$ for $k$-set packing problem is true, \ie the sum of weights is greater than $\lambda$, then in the CRN which is mapped from $\mathcal{I'}$, the sum of the numbers of CCs of the clusters is greater than $\lambda$.
-In the other way around, when an instance is false for weighted $k$-set packing problem, the sum of the numbers of CCs of the clusters in the mapped CRN is smaller than $\lambda$, then the formation of the clusters is not a solution for the robust clustering problem.
+When $\mathcal{I}$ is not an instance for weighted $k$-set packing problem due to the existence of joint sets, the corresponding clustering instance is not a successful cluster partition for the robust clustering problem, as there are overlapped clusters.
+%
+When the sets in an instance $\mathcal{I}$ for weighted $k$-set packing are disjoint, the sum of weights is identical to the total number of the CCs in the CRN which are mapped from $\mathcal{I'}$.
+Thus, when a instance $\mathcal{I}$ for $k$-set packing problem is true (or false), \ie the sum of weights is greater than $\lambda$, then in the CRN which is mapped from $\mathcal{I'}$, the sum of the numbers of CCs of the clusters is greater (or smaller) than $\lambda$.
+%In the other hand, when an instance is false for weighted $k$-set packing problem, the sum of the numbers of CCs of the clusters in the mapped CRN is smaller than $\lambda$, then the formation of the clusters is not a solution for the robust clustering problem.
 
@@
     \cmidrule(r){1-1}\cmidrule(lr){2-2}     
-      Instance for Weighted $k$-set packing  & $\{ \{1\}, \{2,3\}, \{4\} \}$\\ 
+      Instance for Weighted $k$-set packing  & $\{ \{1\}, \{2,3\}, \{4\} \}$, weights are 2, 3, 4\\ 
     \cmidrule(r){1-1}\cmidrule(lr){2-2}
@@
       \\    \cmidrule(r){1-1}\cmidrule(lr){2-2}
-	clusters mapped from $\mathcal{I}$  (step 2 \& 3)
+	clusters mapped from $\mathcal{I}$  (step 2)
 	  &
@@
           \\    \cmidrule(r){1-1}\cmidrule(lr){2-2}
-	formation of clusters (step 4)
+	formation of clusters (step 3)
 	  &

### 2016-11-14 journal-draft/bare_jrnl_comsoc.tex
polkished version, improvement on proof of complexity is needed

@@
 \label{sec:model}
-%Let us consider a two dimensional area where primary and secondary users coexist together.
-%They share the licensed channels according to the spectrum overlay model, where secondary transmitters are only allowed to transmit when the prifcan exchange its spectrum sensing resulmary users are detected as being idle, and they should vacate the working channel when the presence of primary user is detected.
-%The set of primary users and secondary users are presented by $\mathcal{P}$ and $\mathcal{N}$ separately, there are $|\mathcal{P}| = P$ and $|\mathcal{N}| = N$.
-%Cognitive radio ad hoc network is constituted by all the secondary users in $\mathcal{N}$.
-%The collection of non-overlapping licensed frequency bands is denoted as $\mathcal{F}$ with $|\mathcal{F}| =F$, which is shared by the the primary and secondary users.
-%We assume that primary users have a relatively low variation in activity (periods of activity and inactivity in the range of seconds or minutes).
-%%
-%Primary users access the allocated channels in $\mathcal{F}$ according to its need without sending any explicit notification to secondary users.
 
 We consider a set of cognitive radio users $\mathcal{N}$ and a set of primary users distributed over a given area.
-%We denote the set of these nodes as $V$ which is partitioned into sets of primary users $V_P$ and secondary users $V_N$, i.e., $V~=~V_P~\dot\cup~V_N$. 
-%These users share a number of non-overlapping licensed channels according to the spectrum overlay model. 
-The CR users use a set of licensed channels opportunistically, which is denoted as $\mathcal{K}$. 
-The CR users are allowed to transmit on channel $k \in \mathcal{K}$ only if no primary user is detected on channel $k$. 
-%The available channels sensed on secondary user $i$ is denoted by $V_i$ and there is $\vert V_i \vert \leq F$. % indicating the total number of 
-%%Each secondary user notifies its neighbours of the sensing result about the available channels.
+The CR users use a set of licensed channels $\mathcal{K}$ opportunistically. 
+The CR users are allowed to transmit on any channel $k \in \mathcal{K}$ only if no primary user is detected on channel $k$. 
 CR users conduct spectrum sensing independently and sequentially on all licensed channels.
-%The sensing duration and frequency on one channel is a research topic~\cite{sensing_survey_2009}, and 
 We assume that every node can detect the presence of an active primary user on each channel with certain accuracy.
@@
 We adopt the unit disk model~\cite{unitDiskModel} for the transmission of both primary and CR users.
-%Both primary users and CR users have fixed transmission ranges respectively, and all the channels are regarded to be identical in terms of signal propagation.
-If a CR node locates within the transmission range of an active primary user, that CR node is not allowed to use the channel which is being used by that primary user.
-%In our system model, we assume that a secondary node $n$ is able to detect for each channel $c$ whether any primary user utilizes $c$.
+As to the relation between the primary and secondary users, If a CR node $i$ locates within the transmission range of an active primary user $p$, then $i$ is not allowed to use the channel which is being used by $p$.
+On the other hand, If $i$ is not in the transmission range of primary user $p$, $i$ can certainly not detect the presence of $p$.
 As the result of spectrum sensing, $K_i \subseteq \mathcal{K}$ denotes the set of licensed channels which can be used by $i$.
-%
-%One dedicated control channel is assumed to be available for all the secondary nodes to exchange control messages with neighbours in the process of cluster formation.
-%Note that the assumption of dedicated control channel is to simplify the discussion so that we can focus on the kernel of this paper, the robustness of clusters.
-%Actually, the control messages involved in the clustering process can be conveyed on available licensed channels through rendezvous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}.
-%Over the control channel, secondary users exchange their spectrum sensing results $V_{i}$ with one hop neighbours. 
-%Secondary users have the same transmission range on both licensed and control channel, and the communication links are reciprocal.
-%
+As the transmission range of primary users is limited and secondary users have different locations, different secondary users may have different views of the spectrum availability, i.e., for any $i, j \in \mathcal{N}$, $K_i = K_{j}$ does not necessarily hold.
+Among the secondary users, we denote $\text{Nb}(i)$ as user $i$'s neighborhood, which consists of the CR nodes located within the transmission range of $i$.
 
@@
 This control channel could be one of the ISM bands or other reserved spectrum which is exclusively used for transmitting control messages.
-\footnote{Actually, the control messages involved in the clustering process can also be transmitted on the available licensed channels through a rendezvous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}, i.e., two neighbouring nodes establish communication on the same channel.}
-Over the control channel, a secondary user $i$ can exchange its spectrum sensing result $K_i$ to all its one hop neighbors $\text{Nb}(i)$, where $\text{Nb}(i)$ is the neighbors of $i$, and is simply defined as the set of CR nodes located within the transmission range of $i$.
-%It is available for any secondary node $i$ to exchange control messages with any other node in its neighborhood $\text{Nb}(i)$ during the cluster formation phase.
-In the following, we refer to the word \textit{channel} in general as licensed channel, unless we mention the control channel explicitly. 
-%
-%
-If a secondary user $i$ is not in the transmission range of an active primary user $p$, $i$ can certainly not detect the presence of $p$.
-As the transmission range of primary users is limited and secondary users have different locations, different secondary users may have different views of the spectrum availability, i.e., for any $i, j \in \mathcal{N}$, $K_i = K_{j}$ does not necessarily hold.
-%
-%Neighbourhood establishment and maintenance with control channel and according to a neighborhood discovery protocol which is out of scope of our work.
-%While primary users are assumed to be fixed, secondary users can be mobile.
-%Validation refers to the process of ensuring that no primary transmission is actually taking place on the respective channel.
-%All $N$ secondary users constitute an ad-hoc network in which data can be transmitted from one certain node to any other node should available c.hannels are available on the source node, destination node and other intermediate nodes.
-%Communication on licensed channels is possible only when nodes $i, j$ are both located in each other's transmission range and both share a validated licensed channel.
-%As the assumed $0/1$ state of connectivity is solely based on the Euclidean distance between secondary users,
-%CRN can be represented by a graph $\mathcal{G}(I,\mathcal{E})$, where $\mathcal{E}=\lbrace(i,j,v) \vert i, j \in \mathcal{N} \wedge v\in V_i \wedge v\in V_j \rbrace$ is wireless link between any secondary node $i$ and its neighbour $j$ with licensed channel $v$.
-%Due to relatively low primary user dynamics, time index is omitted here.
-%%In order to perform clustering, CR users first need to establish their neighborhood.
-%For secondary node $i$, its neighborhood $Nb_i$ consists of all the secondary users locating within its transmission range, regardless whether common licensed channels exist or not. 
-%% and have at least one common channel with node $i$ each, i.e. $ j\in Nb_i \Rightarrow V_i\cap V_j\neq \emptyset$.
-%%The clustering phase is initialized during which any control message is again conveyed by the control channel.
-%In the rest of this paper, \textit{channel} only refers to the licensed common channel unless the dedicated control channel is particularly mentioned.
-Then, a cognitive radio network can be represented as a graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{i, j\} \in E$  if, and only if, there exists a channel $k \in \mathcal{K}$ with $k \in K_{i} \cap K_{i'}$.
-%Note that the channel availability is that when the clustering process is performed. 
-%For the rest of this paper the word channel is referred to licensed channel, if the control channel is not explicitly mentioned.
-
-%In this subsection, we present the definition of cluster in the context of CRNs, define the clustering problem and discuss its complexity.
-%We give the description of cluster in the context of CRN, all the clusters discussed in this paper comply with it.
-%A cluster $C$ is composed with one cluster head and cluster members, which satisfies the following conditions:
-%\begin{itemize}
-%\item Cluster head $H_C$ is able to communicate with any cluster member \textit{directly}, \ie for any cluster member $i\in C$, there is $i\in \texttt{Nb}_{H_C}$.
-%\item There exists as least one common channel in the cluster, \ie $\cap_{i\in C} V_i \neq \emptyset$.
-%\end{itemize}
+\footnote{Actually, the control messages involved in the clustering process can also be transmitted on the available licensed channels through a rendezvous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}, i.e., two neighboring nodes establish communication on the same channel.}
+Over the control channel, a secondary user $i$ can exchange its spectrum sensing result $K_i$ to all its one hop neighbors $\text{Nb}(i)$.
+In the following, we refer to the licensed channel as \textit{channel} in general, unless we mention the control channel explicitly. 
+Then, a cognitive radio network can be represented as a graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{i, j\} \in E$  if, and only if,$K_{i} \cap K_{j}\neq \emptyset$ and $d_{i,j} < r$ where $d_{i,j}$ is the distance between $i, j$ and $r$ is the radius of the secondary user's transmission range.
+
 A cluster $C$ is a set of secondary nodes, which consists a cluster head $h_C$ and a number of cluster members.
@@
 In other terms, for any cluster member $i \in C$, $i \in \text{Nb} (h_C) $ holds.
-%
-%A cluster head coordinates the activities of cluster members, \ie it notifies all the members to vacate a channel if a primary user's presence is detected by one cluster member.
-Further it also notifies the members to use a different common channel for payload communication.
-%(\textcolor{red}{(Not clear what the meaning of payload communication is.
-Why not omitting payload here?)} \textcolor{brown}{payload communication happens when the clusters are formed, and start to support network functionalities, e.g.
-routing.
-Thus I think it is necessary to leave it here.}
-%
-%
-In this paper, sometimes we need to mention a cluster with the information of its cluster head \ie a cluster is denoted as $C(i)$ where $i$ is its cluster head.
+In this paper, we denote a cluster as $C$, or $C(i)$ when we want to point out the cluster head is $i$.
 Cluster size of $C(i)$ is written as $|C(i)|$.
 $ K(C) = \cap_{i\in C} K_i$, $K(C)$ denotes the set of common licensed channels in cluster $C$.
-Clustering is performed periodically, as secondary users are mobile and the channel availability on secondary users are changing as primary users change their operation state.%, or the most current clusters can not maintain due to lack of CCs when primary users' operation is intense.
-
+Clustering is performed periodically, because the secondary users are mobile and the primary users change their operation channels, thus the channel availability on secondary users changes accordingly.
 The notations used in the system model and the following problem description are listed in the Table~\ref{tab1}.
@@
 
-%We propose distributed scheme ROSS to form clusters to generate robust clusters, and in the same time clusters have preferred sizes, \ie fewer number of singleton clusters (the cluster which consist with only one CR node) compared with state of art.
-
-%Besides, cluster size is also considered in to clustering solution.
-%Size preference can be met after minor modifications on ROSS.
-
-%The metric is summation of the number of channels available to be used for each node when they reside in a certain cluster, together with a cost for not following the desired cluster size, \ie when the desired cluster size is $\delta$ and the other cluster sizes are denoted as $\delta'$, the metric is,
-%\begin{equation}
-%\label{metric}
-%\sum_{i=1}^{N}(ICC_i)
-%\end{equation}
-%$N$ is the number of CR nodes in the network.
-
-%Also, we refer to the common channels between neighbouring clusters by the term \textit{outward common channels} (OCC).
-We define the set of OCCs of cluster $C$ to be the set of available common channels between any member of $C$ and any other CR user of a neighbouring cluster:
-%\begin{equation}
-%\label{numocc}
-%R_{C}=\bigcup_{j\in C, k\in N_j, k\notin C}(V_{j}\cap V_{k})
-%\end{equation}
-
-%In the process of clustering, when there is no restriction on cluster size, the metric will only be the summation of the number of channels for each node when they reside in a certain cluster.
-%When we try to maximize the summation of ICCs, an obvious correlation between cluster size and number of ICCs is encountered, \ie when each node constitutes one cluster, the aforementioned metric will be maximized.
-%The goal of the proposed clustering scheme is to let as more CR nodes as possible to form clusters, meanwhile the clusters have more common channels and preferred cluster size.
-
-%\textcolor{red}{The notation is not well chosen.
-Does it make sense to have only one letter for a potential cluster?
-What happens if we have two clusters?
-Find some comments next to your proposed notation.}
-
 \subsection{Robust Clustering Problem in CRN}
 \label{problem}
-%paper given by james is useful which provides a survey from the perspective of wsn!
-As introduced in the section of introduction, in order to be robust against primary users' activity, the formed clusters should have more CCs to expect longer time expectancy.
-Meanwhile, the sizes of the formed clusters should not diverge from the desired size too much, and there are two reasons.
-First, the generation of the \textit{singleton clusters}, \ie the cluster which has only one CR node, should be avoided, because it contradicts the motivation of forming clusters thus the benefits brought in by the collective of the cluster members are compromised.
-Second, large clusters are not preferred in some scenarios neither, \eg for the CRN composed with resource limited users, managing the cluster members is a substantial burden. 
+
+As introduced in Section I, in order to be robust against primary users' activity, the formed clusters should have more CCs to expect longer time expectancy.
+Meanwhile, the sizes of the formed clusters should not diverge from the desired size greatly.
+The formation of small clusters or the \textit{singleton clusters}, \ie the cluster which has only one CR node, contradicts the motivation of forming clusters, as the benefits brought in by the collective of the cluster members are compromised.
+On the other hand, large clusters are not preferred in some scenarios neither, \eg for the CRN composed with resource limited users, managing the cluster members in a large cluster is a substantial burden.
 Hence, the cluster size should fall in a desired range according to different application scenarios~\cite{Chen04clusteringalgorithms, capacity_cluster_06}.
-Considering the above mentioned requirements on the formed clusters, we present the definition of robust clustering problem as follows.
-%The clustering scheme we propose in the paper aims to form clusters with preferred sizes, meanwhile maximize the average number of CCs per cluster.
-%We have mentioned that the sizes of the formed clusters should be given consideration, which is import for the discussion on cluster robustness, \ie 
-%When perusing the cluster robustness without specifying the requirement on cluster sizes, a clustering method will be inclined to form small clusters.
-%In that case, although more CCs are obtained per cluster, the benefits brought in by the collective of the cluster members are compromised.
-%Except for cooperative sensing, clusters need to conduct some other functionalities.
+Considering the above mentioned requirements, we present the definition of robust clustering problem as follows.
 
@@
 A cluster $C$ is formed when first, it is composed with one or multiple secondary users and there are CCs in $C$ \ie $|K(C)|>0$, second, any two cluster members can communicate either directly, or through other members which belong to the same cluster.
-The collection of all the possible clusters in $\mathcal{N}$ is denoted as $\mathcal{S}$, there is $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$ where $C_i$ is the $i$ th cluster in $\mathcal{S}$\footnote{The sequence of the clusters can be decided in any convenient way \ie the sequence of identifying them.}.
-%the clustering solution will be composed by the elements of $\mathcal{S}$. 
+The collection of all the possible clusters in $\mathcal{N}$ is denoted as $\mathcal{S}$, there is $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$ where $C_i$ is the $i$ th cluster in $\mathcal{S}$.\footnote{The sequence of the clusters can be decided in any convenient way \ie the sequence of identifying them.}
 As to $\mathcal{S}$, there is $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$.
@@
 To formulate the problem, we propose a new definition for the number of CCs in a cluster.
-We use $f(C_i)$ to denote the number of CCs of a cluster $C_i\in \mathcal{S}$, which is as follows,
+We use $f(C_i)$ to denote the number of CCs of a cluster $C_i\in \mathcal{S}$, which is,
 %and the number of common licensed channels is $f(C_i) = |K(C_i)|$ if $|C_i|>1$, and $f(C_i)=0$ when $|C_i|=1$.
@@
 
-%The size of cluster $C$ is not bigger than a positive integer $k$.
-%Then the sum of the number of CCs of the formed clusters is $\sum_{C\in \mathcal{S}'} f(C)$
-
-Then the robust clustering problem is to find a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, so that the sum of the numbers of CCs of the formed clusters $\sum_{C\in \mathcal{S}'} f(C)$ is maximized.
-Besides, the formed clusters should satisfy the requirements on cluster sizes, for example, all the formed clusters should have the same desired size $\delta$, or the sizes should be within a scope $\langle\delta_1, \delta_2\rangle$, where $\delta, \delta_1, \delta_2\in \mathbb{Z}^+$, and $\delta_1 < \delta_2$.
+A clustering solution is a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, which satisfies $\bigcup_{C_i\in \mathcal{S}'} C_i = \mathcal{N}$ and $C_{i'}\cap C_i =\emptyset$ when $C_{i'}, C_i\in \mathcal{S}'$ and $i'\neq i$, so that the sum of the numbers of CCs of the formed clusters $\sum_{C\in \mathcal{S}'} f(C)$ is maximized.
+Besides, the formed clusters should satisfy the requirements on cluster size, for example, the sizes should be within a scope $\langle\delta_1, \delta_2\rangle$, where $\delta, \delta_1, \delta_2\in \mathbb{Z}^+$, and $\delta_1 < \delta_2$.
 According to the new definition of the number of CCs in a cluster, the singleton clusters in $\mathcal{S'}$ don't contribute to the value to be maximized.
 
-A clustering solution is a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, which satisfies the following conditions, $\bigcup_{C_i\in \mathcal{S}'} C_i = \mathcal{N}$ and $C_{i'}\cap C_i =\emptyset$ when $C_{i'}, C_i\in \mathcal{S}'$ and $i'\neq i$.
-
-% when $|C|>1$, and $f(\cdot)=0$ when $|C|=1$.
-%As to $f(\cdot):z\rightarrow z$, under this problem setting, if only number of common channels are given consideration, only singleton clusters will be preferred, which contradicts to our goal of clustering CR nodes together, thus we choose $f(\cdot)= |K_{C}|\cdot |C|$, the product of number of common channels and cluster size.
 \end{mydef}
@@
 The objective is to maximize the sum of the products of the size and the corresponding number of CCs of all the clusters.
-%The second component is designed to help generate the clusters whose sizes are the desired cluster size $\delta$.
 We minimize the opposite of the real objective to make this problem solvable.
-The constraints guarantee to obtain the clusters which together include all the CR users and don't overlap.
-
+%
 The variables of this problem are $x_{ij}$ where $i\in \{1,2,\cdots,G-1, G\}$ and $j\in \{1,2,\cdots,N-1, N\}$.
@@
 There is $\mathcal{G} \subseteq \mathcal{S}$, where $\mathcal{S}$ is the collection of all the possible clusters as described in Definition~\ref{def_centralized_clustering}.
-In practice, we can solve the problem with $\mathcal{G} = \mathcal{S}$ when $|\mathcal{S}|$ is not large. 
+%In practice, we can solve the problem with $\mathcal{G} = \mathcal{S}$ when $|\mathcal{S}|$ is not large. 
 The subscript $i$ indicates the $i$th cluster in $\mathcal{G}$, and $j$ corresponds to the node ID of a CR node. 
@@
 
-As to the constraints, the first constraint regulates that each CR node should reside in exactly one cluster.
+The constraints guarantee to obtain the clusters which together include all the CR users and don't overlap.
+The first constraint regulates that each CR node should reside in exactly one cluster.
 The second constraint regulates that when the $i$th possible cluster $C_i$ is chosen, there will be exactly $|C_i|$ CR nodes residing in the cluster $C_i$.
@@
 \item ROSS with size control. \ie ROSS-$\delta$-DGA and ROSS-$\delta$-DFA where $\delta$ is the desired cluster size.
-In the following, when we mention the variants of ROSS, we refer the above mentioned four schemes.
+In the following, we refer to the above mentioned four schemes as the variants of ROSS.
 \item SOC~\cite{LIU_TMC11_2}, a distributed clustering scheme pursuing cluster robustness.
@@
 Note there is one singleton cluster $C(H)$ generated by SOC, which is not preferred.
-When we only consider the clusters which are not singleton, the average number of common channels of SOC drops to 2.5. 
+When we only consider the clusters which are not singleton, the average number of CCs of SOC drops to 2.5. 
 \begin{figure}[ht]
@@
 
-In the simulation, we investigate the schemes with four metrics.
+We investigate the schemes with four metrics.
 
@@
     \begin{tablenotes}
-      \item\label{tnote:robots-r1}Assuming the data structure of the clustering result is given as \{ Node ID $i$, cluster head ID h($C$) where $i\in C$, $i\in \mathcal{N}$ \}.
+      \item\label{tnote:robots-r1}Assuming the data structure of the clustering result is in the form of \{ Node ID $i$, cluster head ID h($C$) where $i\in C$, for every $i\in \mathcal{N}$ \}.
     \end{tablenotes}
@@
 We add extra 20 batches of PUs sequentially in the CRN, where each batch includes 10 PUs. 
-%In this part of simulation, we investigate the robustness of clusters by increasing the PUs working on certain channels.
 Figure~\ref{singleton_clusters_100} and \ref{singleton_clusters_200} show that when $N=100$ and 200, more unclustered CR nodes appear in the CRN where SOC is applied.
-When the network becomes denser, ROSS-DGA/DFA generate slightly more unclustered CR nodes than SOC when new PUs are not many, but SOC's performance deteriorates quickly when the number of PUs becomes larger.
+When the network becomes denser, as shown in Figure~\ref{singleton_clusters_300}, ROSS-DGA/DFA generate slightly more unclustered CR nodes than SOC when new PUs are not many, but SOC's performance deteriorates quickly when the number of PUs becomes larger.
 We only show the average values of the variants of ROSS as their confidence intervals overlap.
@@
 Besides, the greedy mechanism moderately strengthens the robustness of the clusters.
-%It can be seen that greedy algorithms result in slightly less singleton clusters than their counterparts.
-%
-%Figure ~\ref{singleton_clusters_300} depicts a denser CRN where $N=300$.
-%SOC noticeably causes more singleton clusters than ROSS variants, except that ROSS-20-DFA results in more singleton clusters when PUs are few.
-%The reason is ROSS-20-DFA conducts cluster membership clarification for only once, which causes large number of singleton clusters.
-%ROSS-20-DGA increases the size of smaller clusters through debatable nodes' repeated updates thus drastically decreases the number of singleton clusters.
-%\begin{figure}[!h]
-%  \centering
-%  \includegraphics[width=0.7\linewidth]{survival_rate_100_edge50.pdf}
-%  \caption{Percentage of CRs which are not included in any clusters with the increasing number of primary users, $N=100$}
-%  \label{singleton_clusters_100}
-%\end{figure}
-%  
-%  \begin{figure}[!h]
-%    \centering
-%   \includegraphics[width=0.7\linewidth]{survival_rate_300_edge50.pdf}
-%  \caption{Percentage of CRs which are not included in any clusters with the increasing number of primary users, $N=300$}
-%  \label{singleton_clusters_300}
-%\end{figure}
 
@@
 
-%\begin{figure}[ht]
-%\begin{center}
-%%\centering
-%\subfigure[100 CRs, 30 PRs]{\label{result1:1}\includegraphics[width=0.48\linewidth]{cdf_clusterSize_100.pdf}}
-%\subfigure[300 CRns, 30 PRns]{\label{result1:2}\includegraphics[width=0.48\linewidth]{cdf_clusterSize_300.pdf}}
-%\end{center} 
-%\caption[Cluster sizes]{Distribution of CRs in clusters with different sizes} %{\subref{a}, \subref{b}, \subref{c}, \subref{d}}
-%\label{result1}
-%\end{figure}
-
 The sizes of clusters generated by ROSS-DGA and ROSS-DFA span a wider range than ROSS with size control feature.
@@
 The 50\% percentile of the ROSS-DGA curve is roughly the desired size $\delta$.
-%
-%The desired cluster sizes are 5, 8 and 13, which are around 45\% of the average number of neighbours in respective CRNs. 
 When the variants of ROSS with size control feature are applied, the sizes of the most generated clusters are smaller than $\delta$.
-%This means the size control feature effectively restricts the size of clusters, which is able to prevent the clusters from ungovernable growing with the increase of network density.
-%But the range where most of the CRs (80\% which exclude the CR nodes residing in small and big clusters) resides centres a value, which is roughly the half of the average number of neighbours.
 As to the curves of SOC, the 95\% percentiles are 36, 30, and 40 in respective networks.
-
+%
 From Figure~\ref{cdf_100_200_300}, we conclude that the sizes of the clusters generated by ROSS are limited by the network density, the sizes of the clusters formed by ROSS with size control feature are restricted by the desired size.
@@
 
-As distributed schemes, the variants of ROSS outperform SOC considerately on three metrics.
+As distributed schemes, the variants of ROSS outperform SOC considerably on three metrics.
 The variants of ROSS generate much less singleton clusters than SOC, and the resulted clusters are robuster than SOC when facing the newly added PUs.

### 2016-11-29 journal-draft/bare_jrnl_comsoc.tex
modified the 2nd paragraph in Section 1

@@
 
-Forming clusters is conducted in the very beginning or periodically according to the dynamics of the CRN.
-To form a cluster which is composed by the CR users, there should be channels available for communication within the cluster.
-Usually there are multiple unlicensed channels available for all the CR nodes in the cluster, which are referred to in the following of this paper as \textit{common licensed channels} (or common channels for short, which is abbreviated as CC).
-Out of the available CCs, there are always one or multiple channels which are used for the payload communication.
-%The communication within a cluster is conducted in the spectrum which is available for every member in that cluster.
-When one or several cluster members can not use one certain CC for example because primary user activity has been detected on that channel, it will be excluded from the set of CCs.
-If the channel is being used for payload communication, all the cluster members will switch to another channel in the set of available CCs to achieve seamless transmission.
-As long as there is a CC available, the corresponding cluster can continue to exchange payload data.
-In the context of CRN, as the activity of primary users is unknown to the secondary users, the availability of CCs of the formed clusters is totally dependent on primary users' activity.
-Thus, the clusters with more CCs are in general better as this anticipates a longer time span that payload can be exchanged.
-In this paper the robustness of a cluster against primary users is synonymous with the affluence of CCs which are possessed by that cluster. 
-%In other words, the availability of CCs of the formed clusters is passive and can not be guaranteed.
-%Thus, the number of CCs in one formed cluster indicates the robustness of it when facing the unpredictable influence from primary users.
-%In CRN, one cluster survives the influence of primary users when at least one CC is available in that cluster.
-%As the primary users' operation is assumed to be unknown to the CR users, a cluster formed with more CCs will survive with higher probability.
-
-%It is easy to see that forming clusters with different neighbours results in different number of CCs in the clusters.
-%As a result, how to form the clusters plays an important role on the robustness of clusters in CRN.
-%Furthermore, the clustering algorithm also determines the connectivity between several clusters which ultimately determines the robustness of the entire network on the respect of connectivity. 
-In the formation process, there is a trade-off between CCs and the collaborative sensing performance, as less members in a cluster yield in general a higher number of CCs while this reduces the sensing accuracy~\cite{Consensus_based_clustering12}.
-In addition, there are other reasons that motivate clusters to have more members.
-For example, instead of less members, the proper cluster size results in smaller power consumption~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
-%
+Clusters are formed in the very beginning of the network operation, and re-formed periodically according to the dynamics of the CRN.
+Each formed cluster has one or multiple unlicensed channels which are available for every CR node in the cluster.
+The available unlicensed channels are referred to in the following of this paper as \textit{common licensed channels} (or common channels for short, which is abbreviated as CC).
+Both payload and control overheads can be transmitted on the CCs.
+%Out of the available CCs, there are always one or multiple channels which are used for the payload communication.
+When one or several cluster members can not access one certain CC on which primary user activity is detected, the channel will be excluded from the set of CCs.
+In particular, if that channel is being used for payload communication, the communication pair will stop and resume the transmission on another available channel from CCs.
+The availability of CCs within a cluster defines the existence of that cluster, \ie no CCs are available means the corresponding cluster doesn't exist.
+%As long as there is a CC available, the corresponding cluster can continue to exchange payload data.
+In the context of CRN, the activity of primary users is usually unknown to the secondary users, thus when the primary users' activity is deemed as random, the cluster which secures more CCs will anticipate a longer time span.
+It is obvious that fewer members in a cluster yield more CCs, but obtaining more CCs by decreasing the cluster size contradicts to the motivation of clustering, \ie benefit the cluster members with cooperative decision making.
+For example, spectrum sensing accuracy coralates with the cluster size~\cite{Consensus_based_clustering12}, and power consumption doesn't favor small clusters~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
+%
+In this paper the robustness of clusters means the ability of the clusters to sustain the increasing activity of primary users.
+%is synonymous with the affluence of CCs which are possessed by that cluster, to ....
+
 %To solely pursue cluster robustness against the primary users' activity, \ie to achieve more common channels within clusters, the ultimately best clustering strategy is ironically that every node constitutes one cluster (called as \textit{singleton cluster} in this paper).
@@
 %Apparently this contradicts our motivation of proposing cluster in cognitive radio network to enable cooperative decision making.
-Thus the cluster robustness discussed in terms of number of CCs carries little meaning when the sizes of formed clusters are not given consideration.
+%Thus the cluster robustness discussed in terms of number of CCs carries little meaning when the sizes of formed clusters are not given consideration.
 

### 2016-11-29 journal-draft/bare_jrnl_comsoc.tex
modified Section 2

@@
 For example, spectrum sensing accuracy coralates with the cluster size~\cite{Consensus_based_clustering12}, and power consumption doesn't favor small clusters~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
-%
 In this paper the robustness of clusters means the ability of the clusters to sustain the increasing activity of primary users.
@@
 There has been a lot of research done for clustering in wireless networks.
-%Prior to the emergence of cognitive radio, clustering has been proposed as an important method to manage network ad-hoc networks~\cite{Kawadia03,Lin97adaptiveclustering,Basagni99}, wireless mesh networks\cite{clustering_mesh_globecom2010} and sensor networks~\cite{Abbasi_survey_07}.
 In ad-hoc and mesh networks, the major goal of clustering is to maximize connectivity or to improve the performance of routes~\cite{Kawadia03, clustering_mesh_globecom2010}.
 The emphasis of clustering in sensor networks is on network lifetime and coverage~\cite{Abbasi_survey_07}.
-%Few works also take the overhead of clustering into account in ad-hoc network~\cite{clusterRoutingOverhead02infocom, clusterRoutingOverhead_wcnc04}.
-Various clustering schemes are proposed to target different aspects in cognitive radio networks.
+%Various clustering schemes are proposed to target different aspects in cognitive radio networks.
 %Work~\cite{Consensus_based_clustering12} improves spectrum sensing ability by grouping the CR users with potentially best detection performance into the same cluster.
@@
 %\cite{clustering_globecom11} proposes clustering strategy in cognitive radio network, which looks into the relationship between cluster size and power consumption and accordingly controlling the cluster size to decrease power consumption.
-The clustering schemes proposed in~\cite{Zhao07, Chen07,Affinity_clustering_09icccn} form clusters which meet the basic condition, having CC in every cluster.
-Clustering scheme~\cite{Consensus_based_clustering12} improves spectrum sensing accuracy.
+In respect of CRN, \cite{Zhao07, Chen07,Affinity_clustering_09icccn} propose the clustering schemes to form clusters, where securing CCs is the only goal.
+Clustering scheme~\cite{Consensus_based_clustering12} improves spectrum sensing accuracy with cluster structure.
 %Clustering scheme~\cite{clustering_globecom11} obtains the best cluster size which minimizes power consumption caused by communication within and among clusters.
-\cite{clustering_globecom11, TWC2012_cooperative_communication} target on the QoS provisioning and energy efficiency.
+\cite{clustering_globecom11, TWC2012_cooperative_communication} target on the QoS provisioning and energy efficiency with cluster structure.
 \cite{cluster_EW10} forms clusters to coordinate the control channel usage within one cluster.
-A event-driven clustering scheme is proposed for cognitive radio sensor network in \cite{Ozger_cluster_crsn_13}.
-% optimize the sizes of the formed clusters to decrease power consumption.
-%the channel available to the largest set of one-hop neighbours is selected as common channel which yields a partition of the CRN into clusters. 
-%This approach minimizes the set of distinct frequency bands (and hence, the set of clusters) used as common channels within the CRN.
-%However, bigger cluster sizes generally lead to less options within one cluster to switch to if the common channel is reclaimed by a primary node. 
-%This method pays attention to the communication among the formed clusters, but cluster robustness is not considered.
-%\cite{TWC2012_cooperative_communication} targets on the QoS poisoning and energy efficiency. 
-%This approach first decides on the relay nodes which minimize transmission power consumption, then the chosen nodes become cluster heads and clusters are formed in a dynamic coalition process.
-%This work emphasis on power efficiency and doesn't take into account the channel availability and the issue of robustness of the formed clusters.
-%\cite{cluster_EW10} deploys cluster structure in order to implement common channel control, medium access  with multiple channel and channel allocation. 
-%The node with the maximum number of common channels within its k-hop neighborhood is chosen as cluster head, but how to avoid one node appearing in multiple clusters is not given consideration.
-%A event-driven clustering scheme is proposed for cognitive radio sensor network in \cite{Ozger_cluster_crsn_13}.
-%The cluster heads are selected according to node degree, spectrum availability and the distance to the sink, and the clusters are no longer available after the event ends.
+An event-driven clustering scheme is proposed for cognitive radio sensor network in \cite{Ozger_cluster_crsn_13}.
 No one among the above mentioned schemes provides the robustness to the formed clusters against primary users. 
-
-%Forming robust clusters is considered in~\cite{LIU_TMC11_2, mansoor_15_cluster_robust}.
-
-A clustering scheme (denoted by SOC) which is designed to generate robust clusters against primary users is proposed in~\cite{LIU_TMC11_2}.
+%
+A clustering scheme (denoted as SOC) which is designed to generate robust clusters against primary users is proposed in~\cite{LIU_TMC11_2}.
 SOC involves three phases of distributed executions.
-In the first phase, every secondary user forms clusters with some one-hop neighbors, in the second and third phase, each secondary user seeks to either merge other clusters around it, or join one of them.
-The metric adopted by every secondary user in the three phases is the product of the the number of CCs and cluster size (the number of secondary users in the cluster).
-%To the best of our knowledge, SOC is the only work emphasizing on the robustness of clustering structure among the related works. 
-But this robust clustering scheme has some drawbacks.
-Although the adopted metric covers both cluster size and the number of CCs, the formation of certain clusters may be easily dominated by only one factor, e.g.
-a node which is able to use many channels will exclude its neighbor and form a cluster by itself.
-%emphasis on improving the numbers of common channels within clusters, in order to strengthening robustness of clusters, but the perused metric is not examined or proved to be able to maintain cluster structure under vigorous intensity of primary users’ activities.
-%The authors consider the balance between the number of idle common channels within cluster and cluster size and propose an algorithm that increases the number of common channels within clusters. 
-%However, this work neglects the issue of connectivity between clusters. 
-%One drawback of this scheme is, in order to increase the number of common channels within clusters, the scheme excludes certain CR nodes from the formed clusters, so that isolated nodes have to form clusters themselves.
+In the first phase, every secondary user forms clusters with some one-hop neighbors, in the second and third phase, each secondary user seeks to either merge other clusters or join one of them.
+The metric adopted by every secondary user in the three phases is the product of the number of CCs and cluster size.
+The drawbacks are as follows, although the adopted metric considers both cluster size and the number of CCs, cluster formation can be easily dominated by only one factor, e.g.
+a node which can access many channels may exclude its neighbor and form a cluster by itself.
 In addition, this scheme leads to the high variance of the cluster sizes, which is not desired in certain applications as discussed in~\cite{clustering_globecom11, cluster_EW10}.
-%The first two propose a distributed scheme where the metric is the product of cluster size and the number of common channels.
-\cite{mansoor_15_cluster_robust} presents a heuristic method to form clusters, although the authors claim robustness is one goal to achieve, the minimum number of clusters is pursued.
-\cite{Li11_ROSS} proposes a distributed clustering scheme under the game theoretic framework. 
-Compared with the clustering schemes introduced so far, the clusters are formed in shorter time and posses more CCs within and among clusters.
-But this scheme doesn't consider the the factor of size in the algorithm design.
-
-In this paper we will give a comprehensive analysis of the robust clustering problem and propose solutions. 
-We stick to the motivation of forming robust clusters in CRN \ie let more CR users benefited from the cooperative decision making which is due to the clusters. 
-We propose both centralized and distributed clustering schemes, which result in more CR users in the clusters composed with multiple CR users, not only when the clusters are just formed, but also afterwards when the primary users' activity changes.
-Besides, both centralized and distributed schemes take the cluster size into consideration, and both can control the sizes of the formed clusters to certain extent.
-In particular, the decentralized clustering approach ROSS (RObust Spectrum Sharing) is able to form clusters with desired sizes.
-When compared with other distributed works, ROSS involves smaller signaling overhead and the generated clusters are significantly more robust against the primary users which appear after the clusters are formed.
+\cite{mansoor_15_cluster_robust} presents a heuristic method to form clusters, although the authors claim robustness is one goal to achieve, the minimum number of clusters is finally pursued.
+
+A distributed clustering scheme ROSS is proposed in~\cite{Li11_ROSS} under the game theoretic framework . 
+Compared with the clustering schemes introduced above, the clusters are formed faster and the clusters possess more CCs within and among clusters than SOC.
+But this work doesn't intervene the outcome of singleton clusters, although the cluster sizes are not as divergent as SOC.
+Furthermore, this work doesn't consider the robustness of clusters against the increasing activity of primary users, which leaves their claim of robustness unverified.
+%
+This paper is on the basis of the work in~\cite{Li11_ROSS}, but extends in two directions.
+First, this paper sticks to a new metric of robustness, and considers the clusters when primary users' activity becomes more dynamic.
+Second, this paper proposes size control mechanism, which solves the problem of devergence of clusters sizes in ~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
+Besides, this paper provides a comprehensive analysis of the robust clustering problem and proposes the centralized solution. 
+%We stick to the motivation of forming robust clusters in CRN \ie let more CR users benefited from the cooperative decision making which is due to the clusters. 
+%We propose both centralized and distributed clustering schemes, which result in more CR users in the clusters composed with multiple CR users, not only when the clusters are just formed, but also afterwards when the primary users' activity changes.
+%Besides, both centralized and distributed schemes take the cluster size into consideration, and both can control the sizes of the formed clusters to certain extent.
+%In particular, the decentralized clustering approach ROSS (RObust Spectrum Sharing) is able to form clusters with desired sizes.
+%When compared with other distributed works, ROSS involves smaller signaling overhead and the generated clusters are significantly more robust against the primary users which appear after the clusters are formed.
 %thesis
@@
 %For our scheme we can prove convergence in cluster formation phase and resolve ambiguities with respect to cluster membership in a game-theoretic setting. 
-We also propose the light weighted versions of ROSS, which involve less overheads and thus are more suitable for the scenario where fast deployment is desired.
-Throughout this paper, we refer the clustering schemes on the basis of ROSS as \textit{variants of ROSS}, \ie the fast versions, or that with size control feature.
+The new extensions are made on basis of ROSS and its light weighted version, the latter involves less overheads thus are more suitable for the scenario where fast deployment is desired.
+Throughout this paper, we refer to the clustering schemes on the basis of ROSS as \textit{variants of ROSS}, which include the fast versions and that with size control function.
 
 The rest of paper is organized as follows. 
-We present the system model in Section~\ref{sec:model}. 
-Then the formal description of robust clustering problem in CRN and the properties of the problem are given in Section~\ref{problem}.
-The centralized and distributed solutions are introduced in Section~\ref{centralized_opt} and \ref{ross} respectively.
+We present the system model and the robust clustering problem in Section~\ref{sec:model}. 
+The centralized and distributed solutions are introduced in Section~\ref{centralized_solution} and~\ref{ross} respectively.
 %The clustering problem is given through analysis and a centralized scheme is proposed in section~\ref{centralized_scheme}.
@@
 \section{Centralized Solution for Robust Clustering}
-\label{centralized_opt}
+\label{centralized_solution}
 

### 2016-11-30 journal-draft/bare_jrnl_comsoc.tex
modified system model

@@
 
-We consider a set of cognitive radio users $\mathcal{N}$ and a set of primary users distributed over a given area.
-The CR users use a set of licensed channels $\mathcal{K}$ opportunistically. 
-The CR users are allowed to transmit on any channel $k \in \mathcal{K}$ only if no primary user is detected on channel $k$. 
-CR users conduct spectrum sensing independently and sequentially on all licensed channels.
-We assume that every node can detect the presence of an active primary user on each channel with certain accuracy.
-\footnote{The spectrum availability can be validated with a certain probability of detection.
+We consider a set of CR users $\mathcal{N}$ and a set of primary users distributed over a given area.
+A set of licensed channels $\mathcal{K}$ is available for the primary users. 
+The CR users are allowed to transmit on channel $k \in \mathcal{K}$ only if no primary user is detected on channel $k$. 
+CR users conduct spectrum sensing independently and sequentially on all licensed channels.\footnote{We assume that every node can detect the presence of an active primary user on each channel with certain accuracy.
+The spectrum availability can be validated with a certain probability of detection.
 Spectrum sensing/validation is out of the scope of this paper.}
-We adopt the unit disk model~\cite{unitDiskModel} for the transmission of both primary and CR users.
-As to the relation between the primary and secondary users, If a CR node $i$ locates within the transmission range of an active primary user $p$, then $i$ is not allowed to use the channel which is being used by $p$.
-On the other hand, If $i$ is not in the transmission range of primary user $p$, $i$ can certainly not detect the presence of $p$.
-As the result of spectrum sensing, $K_i \subseteq \mathcal{K}$ denotes the set of licensed channels which can be used by $i$.
+We adopt the unit disk model~\cite{unitDiskModel} for both primary and CR users' transmission.
+%As to the relation between the primary and secondary users,
+If a CR node $i$ locates within the transmission range of an active primary user $p$, then $i$ is not allowed to use the channel which is being used by $p$.
+%On the other hand, if $i$ is not in the transmission range of primary user $p$, $i$ can certainly not detect the presence of $p$.
+We assume the primary users change their operation channels slowly, then we omit the time index for the spectrum availability, \ie as the result of spectrum sensing, $K_i \subseteq \mathcal{K}$ denotes the set of available licensed channels for CR user $i$ at a time point.
 As the transmission range of primary users is limited and secondary users have different locations, different secondary users may have different views of the spectrum availability, i.e., for any $i, j \in \mathcal{N}$, $K_i = K_{j}$ does not necessarily hold.
+A cognitive radio network can be represented as a graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{i, j\} \in E$ if and only if $K_{i} \cap K_{j}\neq \emptyset$ and $d_{i,j} < r$, where $d_{i,j}$ is the distance between $i, j$, $r$ is the radius of secondary user's transmission range.
+%
 Among the secondary users, we denote $\text{Nb}(i)$ as user $i$'s neighborhood, which consists of the CR nodes located within the transmission range of $i$.
@@
 We assume there is one dedicated control channel which is used to exchange signaling messages during clustering process.
-This control channel could be one of the ISM bands or other reserved spectrum which is exclusively used for transmitting control messages.
-\footnote{Actually, the control messages involved in the clustering process can also be transmitted on the available licensed channels through a rendezvous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}, i.e., two neighboring nodes establish communication on the same channel.}
-Over the control channel, a secondary user $i$ can exchange its spectrum sensing result $K_i$ to all its one hop neighbors $\text{Nb}(i)$.
-In the following, we refer to the licensed channel as \textit{channel} in general, unless we mention the control channel explicitly. 
-Then, a cognitive radio network can be represented as a graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{i, j\} \in E$  if, and only if,$K_{i} \cap K_{j}\neq \emptyset$ and $d_{i,j} < r$ where $d_{i,j}$ is the distance between $i, j$ and $r$ is the radius of the secondary user's transmission range.
-
-A cluster $C$ is a set of secondary nodes, which consists a cluster head $h_C$ and a number of cluster members.
+This control channel could be one of the ISM bands or other reserved spectrum which is exclusively used for transmitting control messages.\footnote{Actually, the control messages involved in the clustering process can also be transmitted on the available licensed channels through a rendezvous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}, i.e., two neighboring nodes establish communication on the same channel.}
+Over the control channel, a secondary user $i$ can exchange its spectrum sensing result $K_i$ with all its one hop neighbors $\text{Nb}(i)$.
+In the following, we refer to the licensed channel as \textit{channel} in general, and will explicitly mention the dedicated control channel if necessary.
+
+A cluster $C$ is a set of secondary nodes, which consists of a cluster head $h_C$ and a number of cluster members.
 The cluster head is able to communicate with any cluster member directly.
-In other terms, for any cluster member $i \in C$, $i \in \text{Nb} (h_C) $ holds.
-In this paper, we denote a cluster as $C$, or $C(i)$ when we want to point out the cluster head is $i$.
-Cluster size of $C(i)$ is written as $|C(i)|$.
-$ K(C) = \cap_{i\in C} K_i$, $K(C)$ denotes the set of common licensed channels in cluster $C$.
-Clustering is performed periodically, because the secondary users are mobile and the primary users change their operation channels, thus the channel availability on secondary users changes accordingly.
-The notations used in the system model and the following problem description are listed in the Table~\ref{tab1}.
+$\text{Nb}(i)$ denotes node $i$'s neighborhood which consists of all its one hop neighbors.
+%For any cluster member $i \in C$, $i \in \text{Nb} (h_C) $ holds.
+Cluster size of $C$ is written as $|C|$.
+Cluster $C(i)$ means the cluster head of this cluster is $i$.
+$ K(C) = \cap_{i\in C} K_i$, $K(C)$, which denotes the set of CCs in cluster $C$.
+%Clustering is performed periodically, because the secondary users are mobile and the primary users change their operation channels, thus the channel availability on secondary users changes accordingly.
+The notations used in the system model and the following problem description are listed in Table~\ref{tab1}.
 \begin{table}[h!]
@@
 
-As introduced in Section I, in order to be robust against primary users' activity, the formed clusters should have more CCs to expect longer time expectancy.
+As introduced in Section~\ref{intro}, in order to be robust against primary users' activity, the formed clusters should have more CCs to expect longer time expectancy.
 Meanwhile, the sizes of the formed clusters should not diverge from the desired size greatly.

### 2016-12-04 journal-draft/bare_jrnl_comsoc.tex
minor change

@@
 \midrule
-$\mathcal{N}$  & collection of CR users in a CRN\\
+$\mathcal{N}$  & set of CR users in a CRN\\
 $N$ & number of CR users in a CRN, $N=|\mathcal{N}|$\\

### 2016-12-04 journal-draft/bare_jrnl_comsoc.tex
change the notation h_C--> h(C)

@@
 
-A distributed clustering scheme ROSS is proposed in~\cite{Li11_ROSS} under the game theoretic framework . 
+A distributed clustering scheme ROSS is proposed in~\cite{Li11_ROSS} under the game theoretic framework. 
 Compared with the clustering schemes introduced above, the clusters are formed faster and the clusters possess more CCs within and among clusters than SOC.
@@
 
-A cluster $C$ is a set of secondary nodes, which consists of a cluster head $h_C$ and a number of cluster members.
+A cluster $C$ is a set of secondary nodes, which consists of a cluster head $h(C)$ and a number of cluster members.
 The cluster head is able to communicate with any cluster member directly.
@@
 %$h(C)$ & cluster head of a cluster $C$\\
-$h_C$ & the cluster head of a cluster C\\
+$h(C)$ & the cluster head of a cluster C\\
 $\text{CH}$ & cluster head\\
@@
 
-As introduced in Section~\ref{intro}, in order to be robust against primary users' activity, the formed clusters should have more CCs to expect longer time expectancy.
-Meanwhile, the sizes of the formed clusters should not diverge from the desired size greatly.
+As introduced in Section~\ref{intro}, in order to be robust against primary users' activity, the formed clusters should have more CCs to expect longer life expectancy.
+On the other hand, the sizes of the formed clusters should not diverge from the desired size greatly.
 The formation of small clusters or the \textit{singleton clusters}, \ie the cluster which has only one CR node, contradicts the motivation of forming clusters, as the benefits brought in by the collective of the cluster members are compromised.
@@
 Let us apply Algorithm~\ref{alg0} to the example shown in Figure~\ref{fig1}.
-Node $B$ and $H$ have the same individual connectivity degree, i.e., $d_B=d_H$. As $g_H=2>g_B=1$, node $H$ becomes the cluster head and cluster $C_H$ is $\{H, B, A, G\}$.
+Node $B$ and $H$ have the same individual connectivity degree, i.e., $d_B=d_H$. As $g_H=2>g_B=1$, node $H$ becomes the cluster head and cluster $C(H)$ is $\{H, B, A, G\}$.
 

### 2016-12-04 journal-draft/bare_jrnl_comsoc.tex
modify part of 'robust clustering problem' definition, and proof

@@
 
-A cluster $C$ is a set of secondary nodes, which consists of a cluster head $h(C)$ and a number of cluster members.
-The cluster head is able to communicate with any cluster member directly.
+A cluster $C$ is a set of secondary nodes which possess the same set of CCs.
+In particular, one cluster consists of a cluster head $h(C)$ and a number of cluster members, and the cluster head is able to communicate with any cluster member directly.
+A cluster can be composed only by the cluster head.
 $\text{Nb}(i)$ denotes node $i$'s neighborhood which consists of all its one hop neighbors.
@@
 Cluster $C(i)$ means the cluster head of this cluster is $i$.
-$ K(C) = \cap_{i\in C} K_i$, $K(C)$, which denotes the set of CCs in cluster $C$.
+$K(C)$ denotes the set of CCs in cluster $C$, $ K(C) = \cap_{i\in C} K_i$.
 %Clustering is performed periodically, because the secondary users are mobile and the primary users change their operation channels, thus the channel availability on secondary users changes accordingly.
@@
 
-Given a cognitive radio network $\mathcal{N}$ where $|\mathcal{N}|=N$,  the secondary users are indexed from 1 to $N$.
-A cluster $C$ is formed when first, it is composed with one or multiple secondary users and there are CCs in $C$ \ie $|K(C)|>0$, second, any two cluster members can communicate either directly, or through other members which belong to the same cluster.
-The collection of all the possible clusters in $\mathcal{N}$ is denoted as $\mathcal{S}$, there is $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$ where $C_i$ is the $i$ th cluster in $\mathcal{S}$.\footnote{The sequence of the clusters can be decided in any convenient way \ie the sequence of identifying them.}
-As to $\mathcal{S}$, there is $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$.
-
-To formulate the problem, we propose a new definition for the number of CCs in a cluster.
-We use $f(C_i)$ to denote the number of CCs of a cluster $C_i\in \mathcal{S}$, which is,
-%and the number of common licensed channels is $f(C_i) = |K(C_i)|$ if $|C_i|>1$, and $f(C_i)=0$ when $|C_i|=1$.
-$$
-f(C_i) = \left\{ \begin{array}{rl}
-|K(C_i)| 	&\mbox{$|C_i|>1$} \\
-0 				&\mbox{$|C_i|=1$} \\
-\end{array} \right.
-$$
-
-A clustering solution is a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, which satisfies $\bigcup_{C_i\in \mathcal{S}'} C_i = \mathcal{N}$ and $C_{i'}\cap C_i =\emptyset$ when $C_{i'}, C_i\in \mathcal{S}'$ and $i'\neq i$, so that the sum of the numbers of CCs of the formed clusters $\sum_{C\in \mathcal{S}'} f(C)$ is maximized.
-Besides, the formed clusters should satisfy the requirements on cluster size, for example, the sizes should be within a scope $\langle\delta_1, \delta_2\rangle$, where $\delta, \delta_1, \delta_2\in \mathbb{Z}^+$, and $\delta_1 < \delta_2$.
-According to the new definition of the number of CCs in a cluster, the singleton clusters in $\mathcal{S'}$ don't contribute to the value to be maximized.
+Given a cognitive radio network $\mathcal{N}$ where $|\mathcal{N}|=N$, the collection of all the possible clusters\footnote{Possible cluster means the collection of CR nodes, which complies with the definition in~\ref{sec:model}} in $\mathcal{N}$ is denoted as $\mathcal{S}$ where $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$ \footnote{The subscripts of the clusters can be decided in any convenient way \ie the sequence of identifying them.} and there is $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$.
+
+Then the requirements on the cluster size are enforced, \ie the desired size is $\delta$ and the cluster sizes should fall in the scope $\langle\delta_1, \delta_2\rangle$, where $\delta, \delta_1, \delta_2\in \mathbb{Z}^+$, and $\delta_1 \leq \delta\leq \delta_2$.
+Then a feasible clustering solution is a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, which satisfies 
+$\delta_1\leq|C_i|\leq \delta_2, \bigcup_{C_i\in \mathcal{S}'} C_i = \mathcal{N}$ and $C_{i'}\cap C_i =\emptyset$ where $C_{i'}, C_i\in \mathcal{S}'$ and $i'\neq i$.
+The optimal clustering solution is the feasible clustering solution whose sum of the numbers of CCs of clusters $\sum_{C\in \mathcal{S}'} f(C)$ is the maximal.
+
+%To formulate the problem, we propose a new definition for the number of CCs in a cluster.
+%We use $f(C_i)$ to denote the number of CCs of a cluster $C_i\in \mathcal{S}$, which is,
+%%and the number of common licensed channels is $f(C_i) = |K(C_i)|$ if $|C_i|>1$, and $f(C_i)=0$ when $|C_i|=1$.
+%$$
+%f(C_i) = \left\{ \begin{array}{rl}
+%|K(C_i)| 	&\mbox{$|C_i|>1$} \\
+%0 				&\mbox{$|C_i|=1$} \\
+%\end{array} \right.
+%$$
+%According to the new definition of the number of CCs in a cluster, the singleton clusters in $\mathcal{S'}$ don't contribute to the value to be maximized.
 
@@
 
-We have crossed the hurdle of finding one polynomial algorithm $\sigma$ which transforms an instance of weighted $k$-set packing to an instance of the clustering problem in CRN.
-%Now we look into the step 2 in the reduction.
-When $\mathcal{I}$ is not an instance for weighted $k$-set packing problem due to the existence of joint sets, the corresponding clustering instance is not a successful cluster partition for the robust clustering problem, as there are overlapped clusters.
-%
-When the sets in an instance $\mathcal{I}$ for weighted $k$-set packing are disjoint, the sum of weights is identical to the total number of the CCs in the CRN which are mapped from $\mathcal{I'}$.
-Thus, when a instance $\mathcal{I}$ for $k$-set packing problem is true (or false), \ie the sum of weights is greater than $\lambda$, then in the CRN which is mapped from $\mathcal{I'}$, the sum of the numbers of CCs of the clusters is greater (or smaller) than $\lambda$.
-%In the other hand, when an instance is false for weighted $k$-set packing problem, the sum of the numbers of CCs of the clusters in the mapped CRN is smaller than $\lambda$, then the formation of the clusters is not a solution for the robust clustering problem.
+We have found the polynomial algorithm $\sigma$ which transforms an instance of weighted $k$-set packing to an instance of the robust clustering problem in CRN.
+Assume we have a robust clustering black box which can check whether the clustering instance meets the requirement, \ie the total sum of CCs exceed $\lamda$ or not.
+If \textit{yes} is said, then the total weight of the corresponding instance of the maximum weighted k-set packing problem is greater than $\lamda$.
+If the black box said \textit{no},
+
+ The direction is wrong!!
+%When $\mathcal{I}$ is not an instance for weighted $k$-set packing problem due to the existence of joint sets, the corresponding clustering instance is not a successful cluster partition for the robust clustering problem, as there are overlapped clusters.
+%%
+%When the sets in an instance $\mathcal{I}$ for weighted $k$-set packing are disjoint, the sum of weights is identical to the total number of the CCs in the CRN which are mapped from $\mathcal{I'}$.
+%Thus, when a instance $\mathcal{I}$ for $k$-set packing problem is true (or false), \ie the sum of weights is greater than $\lambda$, then in the CRN which is mapped from $\mathcal{I'}$, the sum of the numbers of CCs of the clusters is greater (or smaller) than $\lambda$.
 
@@
 An example of the reduction is shown in Table~\ref{no_hard_proof_instance}.
+
+XXXXXXXXXXXXx
+
 \begin{table}[h!]

### 2016-12-04 journal-draft/bare_jrnl_comsoc.tex
modified proof

@@
 We assume the weights of sets are positive integers.
-Then we will show the existence of a polynomial-time algorithm $\sigma$ which transforms any instance $\mathcal{I}$ of a weighted $k$-set packing problem, \ie a collection of sets, into a formation of clusters for a CRN.
+Then we will show that any instance $\mathcal{I}$ of a weighted $k$-set packing problem, \ie a collection of sets, can be transformed to a clusters formation for a CRN.
 W.l.o.g. let set $\mathcal{G} = \{ 1, \ldots , N \}$.
@@
 
-\item In the first step, we transform the instance $\mathcal{I}$ to $\mathcal{I'}$ by duplicating the elements of the sets in $\mathcal{I}$.
-In particular, as to each element in set $S\in \mathcal{I}$, we duplicate the element and assign a new index which is N bigger than the original index.
-The weight of these sets remain unchanged.
-The purpose of this transformation is to eliminate the set in $\mathcal{I}$, which has only one element.
-
-\item In the second step, all the elements in $\mathcal{I'}$ are mapped to CR nodes on a two-dimensional Euclidean plane, where the CR user ID is identical with the corresponding element's index.
-In particular, as to each set $S\in \mathcal{I'}$, we set up a cluster $C$ which consists of the CR users mapped from the elements in $S$, and we assign the available channels for each cluster member so that $|K(C)|$ equals to the $\omega(S)$.
-The channel availability on the CR nodes whose IDs are $N$ apart is the same.
+%\item In the first step, we transform the instance $\mathcal{I}$ to $\mathcal{I'}$ by duplicating the elements of the sets in $\mathcal{I}$.
+%In particular, as to each element in set $S\in \mathcal{I}$, we duplicate the element and assign a new index which is N bigger than the original index.
+%The weight of these sets remain unchanged.
+%The purpose of this transformation is to eliminate the set in $\mathcal{I}$, which has only one element.
+
+\item First, the sets in the instance $\mathcal{I}$ are mapped sequentially to the clusters of CR nodes on a two-dimensional Euclidean plane, where the CR user ID is identical with the corresponding element's index.
+
+\item Second, for each mapped cluster $C$, we assign the channels for the nodes in $C$ so that $|K(C)|$ equals to the $\omega(S)$.
+We can simply assign the first $|K(C)|$ channels to each CR node in $C$, without considering the possible mismatch when the same CR node appears in different clusters and is assigned with different channels.
+%The channel availability on the CR nodes whose IDs are $N$ apart is the same.
 %Besides, there is a bijection between every set in $\mathcal{I'}$ and one cluster in the CRN.
@@
 %
-When there are two sets in $\mathcal{I'}$ and one is a subset of the other one, \ie  $S_1\subset S_2$, and $\omega(S_1) < \omega(S_2)$, then we should swap the weights of the sets before mapping them into clusters.
-
-\item In this step, we map the elements in $\mathcal{Q}\setminus \mathcal{I}$ to CR nodes. 
-We arbitrarily put these CR nodes in the CRN, then these CR nodes form singleton clusters by themselves.
-According to the definition of robust clustering problem in CRN, the number of CCs of these singleton clusters is 0.
-These singleton clusters and the clusters mapped from $\mathcal{I'}$ constitute a clustering solution.
+%When there are two sets in $\mathcal{I'}$ and one is a subset of the other one, \ie  $S_1\subset S_2$, and $\omega(S_1) < \omega(S_2)$, then we should swap the weights of the sets before mapping them into clusters.
+
+%\item In second step, we map the elements in $\mathcal{Q}\setminus \mathcal{I}$ to CR nodes. 
+%We arbitrarily put these CR nodes in the CRN, then these CR nodes form singleton clusters by themselves.
+%According to the definition of robust clustering problem in CRN, the number of CCs of these singleton clusters is 0.
+%These singleton clusters and the clusters mapped from $\mathcal{I'}$ constitute a clustering solution.
 
@@
 \end{itemize}
-
-We have found the polynomial algorithm $\sigma$ which transforms an instance of weighted $k$-set packing to an instance of the robust clustering problem in CRN.
-Assume we have a robust clustering black box which can check whether the clustering instance meets the requirement, \ie the total sum of CCs exceed $\lamda$ or not.
-If \textit{yes} is said, then the total weight of the corresponding instance of the maximum weighted k-set packing problem is greater than $\lamda$.
-If the black box said \textit{no},
-
- The direction is wrong!!
+The number of steps is dependent on $\mathcal{I}$, which is between 1 and $N^2$
+
+%We have found the polynomial algorithm $\sigma$ which transforms an instance of weighted $k$-set packing to an instance of the robust clustering problem in CRN.
+Assume we have a robust clustering black box which can check whether the clustering instance meets the requirement, \ie clusters are not overlapping and the total sum of CCs exceed $\lambda$ or not.
+If \textit{yes} is said, then the total weight of the corresponding instance of the maximum weighted k-set packing problem is greater than $\lambda$.
+If the black box said \textit{no}, either due to overlapping clusters, or the sum of CCs over all clusters is smaller than $\lambda$, the corresponding instance of the packing problem is not an solution.
+
+% The direction is wrong!!
 %When $\mathcal{I}$ is not an instance for weighted $k$-set packing problem due to the existence of joint sets, the corresponding clustering instance is not a successful cluster partition for the robust clustering problem, as there are overlapped clusters.
@@
 Hence, the weighted $k$-set packing can be reduced to the robust clustering problem in CRN, then the latter problem is of NP-hard.
-An example of the reduction is shown in Table~\ref{no_hard_proof_instance}.
-
-XXXXXXXXXXXXx
-
-\begin{table}[h!]
-     \begin{center}
-     \begin{tabular}{ C{3cm}  C{4.5cm} }
-     \toprule
-      $\mathcal{N}$  & $\{0, 1,2,3,4,5,6, 7, 8, 9\}$\\ 
-    \cmidrule(r){1-1}\cmidrule(lr){2-2}     
-      $\mathcal{Q}$  & $\{ \{1\}, \{1, 5\}, \{1,2,4\}, \{2,3\}, \{4\} \}$\\ 
-    \cmidrule(r){1-1}\cmidrule(lr){2-2}     
-      Instance for Weighted $k$-set packing  & $\{ \{1\}, \{2,3\}, \{4\} \}$, weights are 2, 3, 4\\ 
-    \cmidrule(r){1-1}\cmidrule(lr){2-2}
-      Instance with dummy elements (step 1)
-      & 
-		$\{ \, \{1,11\},\{2,12, 3, 13\}, \{ 4,14\} \, \}$
-      \\    \cmidrule(r){1-1}\cmidrule(lr){2-2}
-	clusters mapped from $\mathcal{I}$  (step 2)
-	  &
-	  \begin{minipage}{.3\textwidth}	
-      \includegraphics[width=0.6\linewidth]{np_hard_proof_step_2_3.pdf}
-    \end{minipage}
-          \\    \cmidrule(r){1-1}\cmidrule(lr){2-2}
-	formation of clusters (step 3)
-	  &
-	  \begin{minipage}{.3\textwidth}	
-      \includegraphics[width=0.6\linewidth]{np_hard_proof_step4.pdf}
-    \end{minipage}
-	  \\       \bottomrule
-      \end{tabular}
-      \caption{}
-      \label{no_hard_proof_instance}
-      \end{center}
-      \end{table}
+%An example of the reduction is shown in Table~\ref{no_hard_proof_instance}.
+
+%\begin{table}[h!]
+%     \begin{center}
+%     \begin{tabular}{ C{3cm}  C{4.5cm} }
+%     \toprule
+%      $\mathcal{N}$  & $\{0, 1,2,3,4,5,6, 7, 8, 9\}$\\ 
+%    \cmidrule(r){1-1}\cmidrule(lr){2-2}     
+%      $\mathcal{Q}$  & $\{ \{1\}, \{1, 5\}, \{1,2,4\}, \{2,3\}, \{4\} \}$\\ 
+%    \cmidrule(r){1-1}\cmidrule(lr){2-2}     
+%      Instance for Weighted $k$-set packing  & $\{ \{1\}, \{2,3\}, \{4\} \}$, weights are 2, 3, 4\\ 
+%    \cmidrule(r){1-1}\cmidrule(lr){2-2}
+%      Instance with dummy elements (step 1)
+%      & 
+%		$\{ \, \{1,11\},\{2,12, 3, 13\}, \{ 4,14\} \, \}$
+%      \\    \cmidrule(r){1-1}\cmidrule(lr){2-2}
+%	clusters mapped from $\mathcal{I}$  (step 2)
+%	  &
+%	  \begin{minipage}{.3\textwidth}	
+%      \includegraphics[width=0.6\linewidth]{np_hard_proof_step_2_3.pdf}
+%    \end{minipage}
+%          \\    \cmidrule(r){1-1}\cmidrule(lr){2-2}
+%	formation of clusters (step 3)
+%	  &
+%	  \begin{minipage}{.3\textwidth}	
+%      \includegraphics[width=0.6\linewidth]{np_hard_proof_step4.pdf}
+%    \end{minipage}
+%	  \\       \bottomrule
+%      \end{tabular}
+%      \caption{}
+%      \label{no_hard_proof_instance}
+%      \end{center}
+%      \end{table}
 

### 2016-12-06 journal-draft/bare_jrnl_comsoc.tex
modifying sec 2 and 3

@@
 \label{theorem1}
-Robust clustering problem in CRN is NP-hard, when the maximum size of clusters is larger than 3.
+Robust clustering problem in CRN is NP-hard, when the maximum size of clusters is larger than 3, and $\delta_1=1$ and $\delta_2 = N$ .
 %Assume a CRN can be represented by a connected graph, and there is at least one common channel between any pair of neighbours, then forming at least two CR nodes into one cluster is NP-complete.
@@
 %Binary linear programming problem is NP complement, but with the 
-The result will be used as a comparison with the proposed distributed schemes.
+%The result will be used as a comparison with the proposed distributed schemes.
 %looks for the solution which approaches to the global optimum, and the latter is the solution which is more suitable for the practical implementation.
@@
 
-The objective is to maximize the sum of the products of the size and the corresponding number of CCs of all the clusters.
+The objective is to maximize the sum of CCs of all the clusters.
 We minimize the opposite of the real objective to make this problem solvable.
@@
 \label{def_kset_packing}
-Given a finite set $\mathcal{G}$ of non-negative integers where $\mathcal{G} \subsetneq \mathbb{N}$, and a collection of sets $\mathcal{Q}=\{S_1,S_2,\cdots,S_m\}$ where $S_i \subseteq \mathcal{G}$ for $1 \leq i \leq m$, every set $S$ in $\mathcal{Q}$ has a weight $\omega(S) \in \mathbb{R}$.
+Given a finite set $\mathcal{G}$ of non-negative integers where $\mathcal{G} \subsetneq \mathbb{N}$, and a collection of sets $\mathcal{Q}=\{S_1,S_2,\cdots,S_m\}$ where $S_i \subseteq \mathcal{G}$ and $\max(S_i)\geq 3$ for $1 \leq i \leq m$.
+Every set $S$ in $\mathcal{Q}$ has a weight $\omega(S) \in \mathbb{R}$. 
 %

### 2016-12-06 journal-draft/bare_jrnl_comsoc.tex
modified sec 2

@@
 Given a cognitive radio network $\mathcal{N}$ where $|\mathcal{N}|=N$, the collection of all the possible clusters\footnote{Possible cluster means the collection of CR nodes, which complies with the definition in~\ref{sec:model}} in $\mathcal{N}$ is denoted as $\mathcal{S}$ where $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$ \footnote{The subscripts of the clusters can be decided in any convenient way \ie the sequence of identifying them.} and there is $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$.
-
-Then the requirements on the cluster size are enforced, \ie the desired size is $\delta$ and the cluster sizes should fall in the scope $\langle\delta_1, \delta_2\rangle$, where $\delta, \delta_1, \delta_2\in \mathbb{Z}^+$, and $\delta_1 \leq \delta\leq \delta_2$.
-Then a feasible clustering solution is a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, which satisfies 
+%
+With the requirements on the cluster size are enforced, \ie the desired size is $\delta$ and the cluster sizes should fall in the scope $\langle\delta_1, \delta_2\rangle$, where $\delta, \delta_1, \delta_2\in \mathbb{Z}^+$, and $\delta_1 \leq \delta\leq \delta_2$, a feasible clustering solution is a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, which satisfies
 $\delta_1\leq|C_i|\leq \delta_2, \bigcup_{C_i\in \mathcal{S}'} C_i = \mathcal{N}$ and $C_{i'}\cap C_i =\emptyset$ where $C_{i'}, C_i\in \mathcal{S}'$ and $i'\neq i$.

### 2016-12-06 journal-draft/bare_jrnl_comsoc.tex
before rewriting the opt

@@
 
-Based on Definition~\ref{def_centralized_clustering}, the decision version of this problem is to determine whether there exists a non-empty $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C\in \mathcal{S}'} f(C) \geqslant \lambda$ where $\lambda$ is a real number and $C$ is a cluster.
+Based on Definition~\ref{def_centralized_clustering}, the decision version of this problem is to determine whether there is a non-empty $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C\in \mathcal{S}'} f(C) \geqslant \lambda$ where $\lambda$ is a real number.
 We have the following theorem on the complexity of this problem.
@@
 
-With the definition of the robust clustering problem, we need to present this problem in the form of optimization to solve in the centralized manner.
-The optimization is a binary linear programming problem as shown in~\ref{centralized_opt}.
+Although the robust clustering problem is NP-hard, it can be solved by standard solvers. 
+Thus, a central node with all knowledge of all clusters could solve the problem based on your formulation. 
+%we need to present this problem in the form of optimization to solve in the centralized manner.
+
 %Binary linear programming problem is NP complement, but with the 
@@
 
+The optimization is a binary linear programming problem as shown in~\ref{centralized_opt}.
 The objective is to maximize the sum of CCs of all the clusters.

### 2016-12-06 journal-draft/bare_jrnl_comsoc.tex
modified sec 3

@@
 
+We give the definition of cluster in CRN as follows. 
 A cluster $C$ is a set of secondary nodes which possess the same set of CCs.
@@
 & in the problem description\\
-$C_i$  & the $i$th potential cluster in a collection of clusters \\
- $\mathcal{G}$ & a collection of some possible clusters in $\mathcal{N}$\\
+% $\mathcal{G}$ & a collection of some possible clusters in $\mathcal{N}$\\
  $\mathcal{S}$ & the collection of all the possible clusters in $\mathcal{N}$\\
+ $C_i$  & the $i$th cluster in $\mathcal{S}$ \\
 \bottomrule
@@
 \label{theorem1}
-Robust clustering problem in CRN is NP-hard, when the maximum size of clusters is larger than 3, and $\delta_1=1$ and $\delta_2 = N$ .
+Robust clustering problem in CRN is NP-hard, when the maximum size of clusters is larger than 3, and $\delta_1=1$ and $\delta_2 = N$.
 %Assume a CRN can be represented by a connected graph, and there is at least one common channel between any pair of neighbours, then forming at least two CR nodes into one cluster is NP-complete.
@@
 
-Although the robust clustering problem is NP-hard, it can be solved by standard solvers. 
-Thus, a central node with all knowledge of all clusters could solve the problem based on your formulation. 
-%we need to present this problem in the form of optimization to solve in the centralized manner.
-
-%Binary linear programming problem is NP complement, but with the 
-%The result will be used as a comparison with the proposed distributed schemes.
-%looks for the solution which approaches to the global optimum, and the latter is the solution which is more suitable for the practical implementation.
-%
+We propose a centralized solution which solves an optimization with standard solvers. 
+To formulate the optimization, we need to do some preparation beforehand.
+All the possible clusters complying with the Description in the system model are found and constitute a set $\mathcal{S}$.
+Besides, we assign a weight to each cluster, which correlates with the difference between the cluster size and the desired cluster size. 
+In particular, considering $|\mathcal{S}|=M$ and $C_i\in \mathcal{S}$ means the $i$ th cluster in $\mathcal{S}$, and $\delta$ is the desired size, then the weight for each cluster is given as follows,
+$$
+p_i(C_i) = \left\{ \begin{array}{rl}
+0 &\mbox{ if $|C_i|=\delta$} \\
+\alpha_1 &\mbox{if $|C_i|=\delta-1$ or $|C_i|=\delta+1$} \\
+\alpha_2 &\mbox{if $|C_i|=\delta-2$ or $|C_i|=\delta+2$} \\
+\vdots
+\end{array} \right.
+$$
+where $\alpha_1, \alpha_2, \cdots$ are positive values.
+In particular, $\alpha$ increases with the divergence between $|C_i|$ and $\delta$ \ie these is $\alpha_2> \alpha_1>0$.
+
+The optimization searches the set $\mathcal{S}$ and decides on certain clusters which constitute the whole CRN without overlapping between any two of them, besides, the sum of CCs of the chosen clusters is maximized.
+Then, a central node (or controller) with the knowledge of all CR nodes (also the possible clusters) will solve the problem based on the following formulation.
+
 %Exact cover problem can be solved with Knuth's Algorithm X~\cite{dancingLinks_Knuth} as it finds out all the instances of exact cover, then we can choose the one with the biggest sum of weights. 
@@
 \begin{aligned}
-     &\min\limits_{x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^G (-x_{ij}q_{ij} + (1-w_i)*p) \\
+     &\min\limits_{w_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (w_i*t_{ij}) \\
      &\text{subject to}   && \Sigma_{i=1}^G x_{ij} = 1, for \forall j=1, \ldots, N \\
-   &&& \Sigma_{j=1}^N x_{ij} = |C_i|*(1-w_i), for \forall i=1, \ldots, G \\
+   &&& \Sigma_{j=1}^N x_{ij} = |C_i|*w_i, for \forall i=1, \ldots, M \\
    &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
-   &&& i\in \{1,2, \cdots G\}, \hspace{0.3cm} j\in \{1,2,\cdots N\}
+   &&& i\in \{1,2, \cdots M\}, \hspace{0.3cm} j\in \{1,2,\cdots N\}
 %\notag
@@
 
-The optimization is a binary linear programming problem as shown in~\ref{centralized_opt}.
+%The optimization is a binary linear programming problem.
 The objective is to maximize the sum of CCs of all the clusters.
-We minimize the opposite of the real objective to make this problem solvable.
-%
-The variables of this problem are $x_{ij}$ where $i\in \{1,2,\cdots,G-1, G\}$ and $j\in \{1,2,\cdots,N-1, N\}$.
-$N$ is the total number of CR users in network $\mathcal{N}$.
-$G = |\mathcal{G}|$ and $\mathcal{G}$ is a collective of clusters in a CRN $\mathcal{N}$.
-There is $\mathcal{G} \subseteq \mathcal{S}$, where $\mathcal{S}$ is the collection of all the possible clusters as described in Definition~\ref{def_centralized_clustering}.
+%We minimize the opposite of the real objective to make this problem solvable.
+$w_i$ and $x_{ij}$ are the two binary variables in this problem.
+% where $j\in \{1,2,\cdots,N-1, N\}$ and $i\in \{1,2,\cdots,M-1, M\}$.
+$N$ is the total number of CR users in network $\mathcal{N}$, $M = |\mathcal{S}|$.
+%$G = |\mathcal{G}|$ and there is $\mathcal{G} \subseteq \mathcal{S}$.
+Being either 1 or 0, $w_i$ denotes whether the $i$th cluster $C_i$ in $\mathcal{S}$ is chosen to be in the solution or not.
+$x_{ij}$ indicates whether the CR node $j$ resides in the $i$th potential cluster, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$. 
+Node index $j$ is identical to the node ID.
 %In practice, we can solve the problem with $\mathcal{G} = \mathcal{S}$ when $|\mathcal{S}|$ is not large. 
-The subscript $i$ indicates the $i$th cluster in $\mathcal{G}$, and $j$ corresponds to the node ID of a CR node. 
-$x_{ij}$ indicates whether the CR node $j$ resides in the $i$th potential cluster, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$. 
+%
 %
@@
 %By permitting the existence of the singleton clusters, we can ensure that the $\mathcal{S}'$ in Definition~\ref{def_centralized_clustering} is always be feasible.
-Based on the knowledge on $\mathcal{G}$, we construct a $G\times N$ matrix $Q_{G\text{x}N}$ which is shown in Figure~\ref{costant_matrix_Q}. 
-Constant $q_{ij}$ is the element of $Q_{G\text{x}N}$, and its subscripts correspond to the $i$th cluster and CR node $j$ respectively.
+$t_{ij}$ is a constant which is $p_i(C_i) - \frac{q_{ij}}{|C_i|}$.
 $q_{ij}= |K(C_i)|$ when there is $j\in C_i$, and $q_{ij}= 0$ when there is $j\notin C_i$.
-In other words, each non-zero element $q_{ij}$ means the number of CCs of the cluster $i$ where node $j$ resides.
-
-\begin{figure}[ht!]
-\centering
-\bordermatrix{~ 		& 1 	& 2 	& 3 	& \cdots & j & \cdots	& N-1 	& N	\cr
-                  1 	& |K(C_1)| 	& |K(C_1)| 	& 0 	& \cdots & \cdots &\cdots	& 0 	& 0	\cr
-                  2 	& |K(C_2)| 	& 0 	& |K(C_2)| 	& \cdots & \cdots & \cdots 	& 0 	& 0	\cr
-				\vdots  	&\vdots & 	 	& 		&  \vdots		& 		& \vdots \cr
-				i 	& 0 	& |K(C_i)| 	& 0 	& \cdots  & \cdots & \cdots 	& |K(C_i)| 	& 0	\cr
-				\vdots  	&\vdots & 	 	& 		&  \vdots & \cdots & \vdots 		& 		& \vdots \cr
-				\vdots 	& 0  	& 0 	& 0 	& \cdots & \cdots & \cdots 	& |K(C_i')| 	& 0	\cr
-				G  	& |K(C_G)| & \cdots	 	& 		&  \vdots	& \cdots & \vdots& 		& \vdots \cr}	
-\caption{An example of Matrix $Q$, its rows correspond to all possible clusters, and columns correspond to the CR nodes in the CRN. }
-\label{costant_matrix_Q}
-\end{figure}
-
-Now let us have a look at the second component in the objective function.
-%Although the related work SOC~\cite{LIU_TMC11_2} adopts the product of cluster size and number of CCs as its sole metric, SOC still generates a large number of singleton clusters and a few large clusters.
-To discourage the optimization algorithm from generating the clusters which don't have the preferred size, the second item compromises the first component in the objective function when those clusters are generated.
-$w_i$ is the auxiliary binary variable which denotes whether the $i$th  cluster $C_i$ is chosen by the optimization algorithm or not.
-
-$$
-w_i = \left\{ \begin{array}{rl}
-0 &\mbox{if $i$th possible cluster $C_i$ is chosen} \\
-1 &\mbox{if $i$th possible cluster $C_i$ is not chosen} \\
-\end{array} \right.
-$$
-When $w_i$ is zero, it means $C_i$ is chosen by the optimization algorithm, in this case, the second item in the objective function becomes $p$, which is defined as follows,
-
-$$
-p = \left\{ \begin{array}{rl}
-0 &\mbox{ if $|C_i|=\delta$} \\
-\alpha_1 &\mbox{if $|C_i|=\delta-1$ or $|C_i|=\delta+1$} \\
-\alpha_2 &\mbox{if $|C_i|=\delta-2$ or $|C_i|=\delta+2$} \\
-\dots
-\end{array} \right.
-$$
-where $\alpha_1, \alpha_2, \cdots$ are positive values, then when $w_i$ is zero ($C_i$ is chosen by the optimization algorithm) and its size is not the desired size $\delta$, the second component will be greater than zero, which will compromise the first component.
-In particular, $\alpha$ increases with the divergence between $|C_i|$ and $\delta$ \ie these is $\alpha_2> \alpha_1>0$.
+$|K(C_i)|$ is the number of CCs of cluster $C_i$, and $|C_i|$ is the size of cluster $C_i$.
+%%Based on the knowledge on $\mathcal{S}$, we construct a $M\times N$ matrix $Q_{M\text{x}N}$ which is shown in Figure~\ref{costant_matrix_Q}. 
+%%Constant $q_{ij}$ is the element of $Q_{M\text{x}N}$, and its subscripts correspond to the $i$th cluster and CR node $j$ respectively.
+%$q_{ij}= |K(C_i)|/|C_i|$ when there is $j\in C_i$, and $q_{ij}= 0$ when there is $j\notin C_i$.
+%In other words, each non-zero element $q_{ij}$ means the number of CCs of the cluster $i$ where node $j$ resides.
+
+%\begin{figure}[ht!]
+%\centering
+%\bordermatrix{~ 		& 1 	& 2 	& 3 	& \cdots & j & \cdots	& N-1 	& N	\cr
+%                  1 	& |K(C_1)| 	& |K(C_1)| 	& 0 	& \cdots & \cdots &\cdots	& 0 	& 0	\cr
+%                  2 	& |K(C_2)| 	& 0 	& |K(C_2)| 	& \cdots & \cdots & \cdots 	& 0 	& 0	\cr
+%				\vdots  	&\vdots & 	 	& 		&  \vdots		& 		& \vdots \cr
+%				i 	& 0 	& |K(C_i)| 	& 0 	& \cdots  & \cdots & \cdots 	& |K(C_i)| 	& 0	\cr
+%				\vdots  	&\vdots & 	 	& 		&  \vdots & \cdots & \vdots 		& 		& \vdots \cr
+%				\vdots 	& 0  	& 0 	& 0 	& \cdots & \cdots & \cdots 	& |K(C_i')| 	& 0	\cr
+%				G  	& |K(C_G)| & \cdots	 	& 		&  \vdots	& \cdots & \vdots& 		& \vdots \cr}	
+%\caption{An example of Matrix $Q$, its rows correspond to all possible clusters, and columns correspond to the CR nodes in the CRN. }
+%\label{costant_matrix_Q}
+%\end{figure}
+
+Now we examine the objective function to see whether it in line with the goal to maximize the total number of CCs meanwhile consider the restriction on cluster size.
+The objective function can be written as,
+\begin{equation}
+\begin{aligned}
+     &\min\limits_{w_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (-w_i* \frac{q_{ij}}{|C_i|} + w_i*p_i(C_i)) \\
+\notag
+\end{aligned}
+\label{centralized_opt}
+\end{equation}
+The sum of the first items is the sum of CCs of all the chosen clusters.
+The minus sign in front of the first item explains the reason why we minimize instead to maximize the objective function.
+As to the second item, when $w_i$ is zero ($C_i$ is chosen), if $|C_i|\neq\delta$, the second component will be positive which contradicts the direction of the optimization.
+Thus the second item discourages the appearance the clusters whose sizes are different from $\delta$, especially those whose sizes diverge far from $\delta$.
+
+%$$
+%w_i = \left\{ \begin{array}{rl}
+%0 &\mbox{if $i$th possible cluster $C_i$ is chosen} \\
+%1 &\mbox{if $i$th possible cluster $C_i$ is not chosen} \\
+%\end{array} \right.
+%$$
+%When $w_i$ is zero, it means $C_i$ is chosen by the optimization algorithm, in this case, the second item in the objective function becomes $p$, which is defined as follows,
+
 %Because of $w_i$, any cluster which appears in the clustering solution ($w=0$) will compromise the first component.

### 2016-12-06 journal-draft/bare_jrnl_comsoc.tex
modified sec 3, minor changes

@@
 To formulate the optimization, we need to do some preparation beforehand.
-All the possible clusters complying with the Description in the system model are found and constitute a set $\mathcal{S}$.
-Besides, we assign a weight to each cluster, which correlates with the difference between the cluster size and the desired cluster size. 
-In particular, considering $|\mathcal{S}|=M$ and $C_i\in \mathcal{S}$ means the $i$ th cluster in $\mathcal{S}$, and $\delta$ is the desired size, then the weight for each cluster is given as follows,
+First, all the possible clusters complying with the description in the system model are found and constitute a set $\mathcal{S}$.
+Second, we assign a weight about size to each cluster, which correlates with the difference between the cluster size and the desired cluster size. 
+In particular, considering $|\mathcal{S}|=M$, $C_i\in \mathcal{S}$ means the $i$ th cluster in $\mathcal{S}$, and $\delta$ is the desired size, the weight about size for each cluster is given as follows,
 $$
@@
 where $\alpha_1, \alpha_2, \cdots$ are positive values.
-In particular, $\alpha$ increases with the divergence between $|C_i|$ and $\delta$ \ie these is $\alpha_2> \alpha_1>0$.
+In particular, $\alpha$ increases with the divergence between $|C_i|$ and $\delta$, \ie these is $\alpha_2> \alpha_1>0$.
 
@@
 
-%This example indicates the chose of $\mathcal{C}$ plays an important role on the resultant clustering strategy.
 %Meanwhile, it provide a chance to constrain the cluster size by putting groups with desired sizes into $\mathcal{C}$.
@@
 %the maximum size of $S$ is the \textit{Bell number} of $N$, and $S$ contains the conditions cluster .
-%In this case, the resultant $\mathcal{C}$ is composed with all the singleton clusters, \ie, the cluster which contains one node, and the objective is -38.
-
-%it is possible that there doesn't exist combination of clusters with the same cluster size.
+
 %We thus list all possible clusters whose sizes are from 2 to one certain number \footnote{this number of decided by the density of CR network, along with the occupation of PUs.
@@
 %The complexity of computation is thus \bigO$(N^\delta)$, $\delta$ is the preferred cluster size.
-
-%The global optimal clustering scheme with respect to the number of common channels is investigated to show the gap with the distributed schemes.
 
@@
 The first constraint regulates that each CR node should reside in exactly one cluster.
-The second constraint regulates that when the $i$th possible cluster $C_i$ is chosen, there will be exactly $|C_i|$ CR nodes residing in the cluster $C_i$.
+The second constraint regulates that when the $i$th possible cluster $C_i$ is chosen, there will be exactly $|C_i|$ CR nodes residing in $C_i$.
 
@@
 %Note the collection of potential clusters is dependant on the network topology and spectrum availability in the network, thus to each specific CRN, the space of solution is different.
+
+This problem is a binary linear programming problem.
+The difficulty of using this method lies in the preparation of the set $\mathcal{S}$.
+In the worst case \ie the CRN forms a full connected graph, the size of $S$ is $\Sigma_{r=1}^{N}\ {N \choose r} = 2^N-1$.
+To levitate this problem, a smaller set \ie $\mathcal{G} \subset \mathcal{S}$ can be used.
+$\mathcal{G}$ can be prepared based on the cluster size, and it is recommended to include all the singleton clusters to make sure the availability of feasible solutions.
+
+%We thus list all possible clusters whose sizes are from 2 to one certain number \footnote{this number of decided by the density of CR network, along with the occupation of PUs.
+We set this number as cluster size of the biggest cluster ever appears when conducting distributed schemes.}, and check each combination of clusters to find the best covering of network on the aspect of number of ICCs per cluster.
+%The complexity of computation is thus \bigO$(N^\delta)$, $\delta$ is the preferred cluster size.
 

### 2016-12-07 journal-draft/bare_jrnl_comsoc.tex
modified before 4.1.3

@@
 
-This problem is a binary linear programming problem.
+This problem is a binary linear programming problem, which can be solved by many available solvers.
 The difficulty of using this method lies in the preparation of the set $\mathcal{S}$.
@@
 
-%We thus list all possible clusters whose sizes are from 2 to one certain number \footnote{this number of decided by the density of CR network, along with the occupation of PUs.
-We set this number as cluster size of the biggest cluster ever appears when conducting distributed schemes.}, and check each combination of clusters to find the best covering of network on the aspect of number of ICCs per cluster.
-%The complexity of computation is thus \bigO$(N^\delta)$, $\delta$ is the preferred cluster size.
-
-\section{Distributed Clustering Algorithm: ROSS}
-\label{ross}
-To do clustering with the centralized scheme for a CRN, the centralized entity firstly needs to collect the information from all the CR nodes, then computes the clustering solution and distributes it across the whole network.
+Another obstacle to apply this centralized scheme is, the centralized entity firstly needs to collect the information from all the CR nodes, then computes the clustering solution and distributes it across the whole network.
 This process involves a large number of communication overheads.
@@
 Hence, when the spectrum availability and the CR users' location change frequently, the centralized robust clustering scheme is not suitable for CRN.
-%
-In this section we will introduce the distributed clustering scheme ROSS.
+
+%We thus list all possible clusters whose sizes are from 2 to one certain number \footnote{this number of decided by the density of CR network, along with the occupation of PUs.
+We set this number as cluster size of the biggest cluster ever appears when conducting distributed schemes.}, and check each combination of clusters to find the best covering of network on the aspect of number of ICCs per cluster.
+%The complexity of computation is thus \bigO$(N^\delta)$, $\delta$ is the preferred cluster size.
+
+\section{Distributed Clustering Algorithm: ROSS}
+\label{ross}
+
+In this section we introduce the distributed clustering scheme ROSS.
 With ROSS, CR nodes form clusters based on the proximity of the available spectrum in their neighborhood after a series of interactions with their neighbors.
 ROSS consists of two cascaded phases: \textit{cluster formation} and \textit{membership clarification}.
+In the first phase, clusters are formed quickly and every CR user becomes either a cluster head or a cluster member.
+In the second phase, non-overlapping clusters are formed in a way that the CCs of relevant clusters are mostly increased.
 
@@
 
-\subsubsection{Determining Cluster Heads and Form Clusters}
+\subsubsection{Determining Cluster Heads and Forming Clusters}
 The procedure of determining the cluster heads is as follows.
@@
 %After deciding itself being cluster head, CR node broadcasts to notify its neighbours on the dedicated control channel, meanwhile, $i$'s initial cluster is formed immediately, which is $i$'s neighbourhood except for those nodes which have become cluster heads, \ie $C_i=(\text{Nb}_i\setminus \text{CHs})\cup i$.
-After executing Algorithm~\ref{alg0}, certain formed clusters may don't possess any CCs.
+After executing Algorithm~\ref{alg0}, certain formed clusters may not possess any CCs.
 As decreasing cluster size increases the CCs within a cluster, for those clusters having no CCs, certain nodes need to be eliminated to obtain at least one CC.
@@
 The pseudo code for this procedure is shown in Algorithm~\ref{alg_size_control_available_CCC}.
-As to the nodes which are eliminated from the previous clusters, they restore their original individual connectivity degrees, executes Algorithm~\ref{alg0}, and become either cluster heads or get included into other clusters afterwards according to Theorem~\ref{clustering:theorem}.
+As to the nodes which are eliminated from the previous clusters, they restore their original individual connectivity degrees, execute Algorithm~\ref{alg0} and become either cluster heads or get included into other clusters afterwards according to Theorem~\ref{clustering:theorem}.
 

### 2016-12-07 journal-draft/bare_jrnl_comsoc.tex
before removing 4.1.3 Cluster Size Control in Dense CRN

@@
 An instance of this situation is shown in Figure~\ref{clusters_denseNetwork}.
-In the figure, black dots represent cluster heads, the circles denotes the transmission ranges of cluster heads.
+In the figure, black dots represent cluster heads, the circles denote the transmission ranges of cluster heads.
 Cluster members are not shown in the figure.
@@
 We notice that nodes $A, B, D$ are included in more than one cluster. 
-We refer these nodes as \textit{debatable nodes} as their cluster affiliations are not decided.
+We refer to these nodes as \textit{debatable nodes} as their cluster affiliations are not decided.
 The clusters which include the debatable node $i$ are called \textit{claiming clusters} of node $i$, and the set of these clusters is denoted as $S_i$.  
@@
 The debatable nodes which are generated from the first phase of ROSS should be exclusively associated with only one cluster and be removed from the other claiming clusters, this procedure is called \textit{cluster membership clarification}.
-%We will introduce the solution for cluster membership clarification in the following.
 

### 2016-12-07 journal-draft/bare_jrnl_comsoc.tex
change \alpha in the optimization to \rho

@@
 0 &\mbox{ if $|C_i|=\delta$} \\
-\alpha_1 &\mbox{if $|C_i|=\delta-1$ or $|C_i|=\delta+1$} \\
-\alpha_2 &\mbox{if $|C_i|=\delta-2$ or $|C_i|=\delta+2$} \\
+\rho_1 &\mbox{if $|C_i|=\delta-1$ or $|C_i|=\delta+1$} \\
+\rho_2 &\mbox{if $|C_i|=\delta-2$ or $|C_i|=\delta+2$} \\
 \vdots
@@
 $$
-where $\alpha_1, \alpha_2, \cdots$ are positive values.
-In particular, $\alpha$ increases with the divergence between $|C_i|$ and $\delta$, \ie these is $\alpha_2> \alpha_1>0$.
+where $\rho_1, \rho_2, \cdots$ are positive values.
+In particular, $\rho$ increases with the divergence between $|C_i|$ and $\delta$, \ie these is $\rho_2> \rho_1>0$.
 
@@
 %doesn't follow the definition of $f(C)$ in Definition~\ref{def_centralized_clustering} strictly, where $f(C_i)=0$ when $|C_i|=1$, but our design echoes the definition by exerting the most severe punishment on the singleton clusters in the clustering solution.
-%Choice of $\alpha_i$ affects the resultant clusters.
+%Choice of $\rho_i$ affects the resultant clusters.
 
@@
 $\mathcal{S}=\{\{A\}, \{B\},\dots,\{B,C\},\{B,A\},\{B,H\},\cdots,\{B,A,C\},$\\$\{B,H,C\}, \{A,D,C\},\cdots\}$, and $|\mathcal{S}|=38$.
-We set $\alpha_1$ and $\alpha_1$ as 0.2 and 0.8 respectively.
+We set $\rho_1$ and $\rho_1$ as 0.2 and 0.8 respectively.
 The formed clusters by the centralized clustering scheme are shown in Fig.~\ref{fig:final_clustering_LP}.
@@
 The desired cluster size $\delta$ is 3.
-As to the centralized scheme, the parameters used in the \textit{punishment} for choosing the clusters with undesired sizes are set as follows, $\alpha_1 =  0.4$, $\alpha_2 =  0.6$.
+As to the centralized scheme, the parameters used in the \textit{punishment} for choosing the clusters with undesired sizes are set as follows, $\rho_1 =  0.4$, $\rho_2 =  0.6$.
 

### 2016-12-07 journal-draft/bare_jrnl_comsoc.tex
change CH to \Lambda

@@
 Clustering is also efficient to coordinate the channel switch operation when primary users are detected by at least one CR node residing in the cluster.
-The cluster head (CH) can enable all the CR devices within the same cluster to stop payload transmission swiftly on the operating channel and to vacate the channel ~\cite{willkomm08}.
+The cluster head can enable all the CR devices within the same cluster to stop payload transmission swiftly on the operating channel and to vacate the channel ~\cite{willkomm08}.
 %
@@
 $h(C)$ & the cluster head of a cluster C\\
-$\text{CH}$ & cluster head\\
+%$\text{CH}$ & cluster head\\
 %$\text{CH}$ & cluster head\\
@@
 %In other words, CR node $i$ becomes cluster head if $d_i > d_k, \forall k\in \texttt{Nb}_i\setminus CHs$ ($CHs$ donate the cluster heads existing in $\texttt{Nb}_i$).
-If there is another CR node $j$ in its neighborhood which has the same individual connectivity degree as $i$, \ie $d_j = d_i$ and $d_j < d_{k}, \forall k\in \text{Nb}(j)\setminus \{\text{CHs}\cup i\}$, then the node between $i$ and $j$, which has higher neighborhood connectivity degree will become the cluster head, and the other node become one member of the newly identified cluster head.
+If there is another CR node $j$ in its neighborhood which has the same individual connectivity degree as $i$, \ie $d_j = d_i$ and $d_j < d_{k}, \forall k\in \text{Nb}(j)\setminus \{\Lambda\cup i\}$ where $\Lambda$ denotes the cluster heads, then the node between $i$ and $j$, which has higher neighborhood connectivity degree will become the cluster head, and the other node become one member of the newly identified cluster head.
 If $g_i = g_j$ as well, the node ID is used to break the tie, \ie the one with smaller node ID becomes a cluster head.
@@
 
-We consider a cluster $C(i)$ where $i$ is CH in a dense CRN. 
-To make the analysis easier, we assume there is no CHs which are generated within $i$'s neighborhood during the procedure of guaranteeing CCs.
+We consider a cluster $C(i)$ where $i$ is the cluster head in a dense CRN. 
+To make the analysis easier, we assume there is no cluster heads which are generated within $i$'s neighborhood during the procedure of guaranteeing CCs.
 Assuming the CR users and PUs are evenly distributed and PUs occupy the licensed channels randomly, then both CR nodes density and channel availability in the CRN can be seen to be spatially homogeneous.
@@
 In the first phase, when a CR node decides itself to be the cluster head, it broadcasts a message containing its ID, cluster members and the set of CCs in its cluster.
-In the second phase, a debatable node broadcasts its affiliation to inform its claiming clusters, then the $\text{CH}$s of the claiming clusters  broadcast message about the new cluster members if they are changed due to the debatable node's decision.
+In the second phase, a debatable node broadcasts its affiliation to inform its claiming clusters, then the cluster heads of the claiming clusters broadcast message about the new cluster members if they are changed due to the debatable node's decision.
 The upper bound of the total number of the control messages involved in cluster formation is analyzed in Theorem~\ref{clustering:theorem} and Section~\ref{clustering:phaseII:game}.
@@
 \SetAlgoLined
-\KwIn{$d_j, g_j, j\in \text{Nb}_i\setminus \text{CHs}$. Empty sets $\tau_1,\tau_2$}
-\KwResult{Returning 1 means $i$ is cluster head, then $d_j$ is set to 0, $j\in \text{Nb}_i\setminus \text{CHs}$. returning 0 means $i$ is not CH.}
-
-\If{$\nexists j\in \text{Nb}_i\setminus \text{CHs}$, such that $d_i \geq d_j$}{
+\KwIn{$d_j, g_j, j\in \text{Nb}_i\setminus \Lambda$, $\Lambda$ means cluster heads. Empty sets $\tau_1,\tau_2$}
+\KwResult{Returning 1 means $i$ is cluster head, then $d_j$ is set to 0, $j\in \text{Nb}_i\setminus \Lambda$. returning 0 means $i$ is not cluster head.}
+
+\If{$\nexists j\in \text{Nb}_i\setminus \Lambda$, such that $d_i \geq d_j$}{
 	return 1;
 	}
-\eIf{$\exists j\in \text{Nb}_i\setminus CHs$, such that $d_i > d_j$}{
+\eIf{$\exists j\in \text{Nb}_i\setminus \Lambda$, such that $d_i > d_j$}{
 	return 0;}{
-	\If{$\nexists j\in \text{Nb}_i\setminus CHs$, such that $d_j == d_i$}{
+	\If{$\nexists j\in \text{Nb}_i\setminus \Lambda$, such that $d_j == d_i$}{
 	$\tau_1 \leftarrow j$

### 2016-12-08 journal-draft/bare_jrnl_comsoc.tex
polish the section 3

@@
 
-Given a cognitive radio network $\mathcal{N}$ where $|\mathcal{N}|=N$, the collection of all the possible clusters\footnote{Possible cluster means the collection of CR nodes, which complies with the definition in~\ref{sec:model}} in $\mathcal{N}$ is denoted as $\mathcal{S}$ where $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$ \footnote{The subscripts of the clusters can be decided in any convenient way \ie the sequence of identifying them.} and there is $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$.
+Given a cognitive radio network $\mathcal{N}$ where $|\mathcal{N}|=N$, the collection of all the possible clusters\footnote{Possible cluster means the collection of CR nodes, which complies with the definition in~\ref{sec:model}} in $\mathcal{N}$ is denoted as $\mathcal{S}$ where $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$ \footnote{The subscripts of the clusters can be decided in any convenient way, \ie the sequence of identifying them.} and there is $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$.
 %
@@
 \label{theorem1}
-Robust clustering problem in CRN is NP-hard, when the maximum size of clusters is larger than 3, and $\delta_1=1$ and $\delta_2 = N$.
+Robust clustering problem in CRN is NP-hard, when the maximum size of clusters is larger than 3, $\delta_1=1$ and $\delta_2 = N$.
 %Assume a CRN can be represented by a connected graph, and there is at least one common channel between any pair of neighbours, then forming at least two CR nodes into one cluster is NP-complete.
@@
 First, all the possible clusters complying with the description in the system model are found and constitute a set $\mathcal{S}$.
-Second, we assign a weight about size to each cluster, which correlates with the difference between the cluster size and the desired cluster size. 
-In particular, considering $|\mathcal{S}|=M$, $C_i\in \mathcal{S}$ means the $i$ th cluster in $\mathcal{S}$, and $\delta$ is the desired size, the weight about size for each cluster is given as follows,
+Second, we assign a cluster size related weight to each cluster, which is positively correlated with the difference between the cluster size and the desired cluster size. 
+In particular, considering $|\mathcal{S}|=M$, $C_i\in \mathcal{S}$ means the $i$ th cluster in $\mathcal{S}$, and $\delta$ is the desired size, the size related weight for each cluster is given as follows,
 $$
@@
 0 &\mbox{ if $|C_i|=\delta$} \\
-\rho_1 &\mbox{if $|C_i|=\delta-1$ or $|C_i|=\delta+1$} \\
-\rho_2 &\mbox{if $|C_i|=\delta-2$ or $|C_i|=\delta+2$} \\
+\rho_1 &\mbox{if $||C_i|-1|=\delta$} \\
+\rho_2 &\mbox{if $||C_i|-2|=\delta$} \\
 \vdots
@@
 The optimization searches the set $\mathcal{S}$ and decides on certain clusters which constitute the whole CRN without overlapping between any two of them, besides, the sum of CCs of the chosen clusters is maximized.
-Then, a central node (or controller) with the knowledge of all CR nodes (also the possible clusters) will solve the problem based on the following formulation.
+Then, a central node (or controller) with the knowledge of all CR nodes (and also the possible clusters) will solve the problem based on the following formulation.
 
@@
      &\min\limits_{w_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (w_i*t_{ij}) \\
-     &\text{subject to}   && \Sigma_{i=1}^G x_{ij} = 1, for \forall j=1, \ldots, N \\
-   &&& \Sigma_{j=1}^N x_{ij} = |C_i|*w_i, for \forall i=1, \ldots, M \\
-   &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
+     &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, for\,\,\forall j=1, \ldots, N \\
+   &&& \Sigma_{j=1}^N x_{ij} = |C_i|*w_i,\, for\,\,\forall i=1, \ldots, M \\
+  % &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
    &&& i\in \{1,2, \cdots M\}, \hspace{0.3cm} j\in \{1,2,\cdots N\}
@@
 % where $j\in \{1,2,\cdots,N-1, N\}$ and $i\in \{1,2,\cdots,M-1, M\}$.
-$N$ is the total number of CR users in network $\mathcal{N}$, $M = |\mathcal{S}|$.
+$N$ is the total number of CR users in network $\mathcal{N}$, $M$ is the number of possible clusters in $\mathcal{S}$.
 %$G = |\mathcal{G}|$ and there is $\mathcal{G} \subseteq \mathcal{S}$.
-Being either 1 or 0, $w_i$ denotes whether the $i$th cluster $C_i$ in $\mathcal{S}$ is chosen to be in the solution or not.
+Being either 1 or 0, $w_i$ denotes whether the $i$th cluster $C_i$ in $\mathcal{S}$ is chosen by the solution or not.
 $x_{ij}$ indicates whether the CR node $j$ resides in the $i$th potential cluster, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$. 
@@
 $|K(C_i)|$ is the number of CCs of cluster $C_i$, and $|C_i|$ is the size of cluster $C_i$.
+$p_i(C_i)$ is the size related weight which has been introduced.
 %%Based on the knowledge on $\mathcal{S}$, we construct a $M\times N$ matrix $Q_{M\text{x}N}$ which is shown in Figure~\ref{costant_matrix_Q}. 
@@
 
-Now we examine the objective function to see whether it in line with the goal to maximize the total number of CCs meanwhile consider the restriction on cluster size.
-The objective function can be written as,
+Now we examine the objective function to see whether it in line with the goal to maximize the total number of CCs meanwhile consider the restriction on the cluster size.
+Replacing $t_{ij}$ with $p_i(C_i) - \frac{q_{ij}}{|C_i|}$, the objective function becomes,
 \begin{equation}
@@
 This problem is a binary linear programming problem, which can be solved by many available solvers.
-The difficulty of using this method lies in the preparation of the set $\mathcal{S}$.
-In the worst case \ie the CRN forms a full connected graph, the size of $S$ is $\Sigma_{r=1}^{N}\ {N \choose r} = 2^N-1$.
-To levitate this problem, a smaller set \ie $\mathcal{G} \subset \mathcal{S}$ can be used.
+The difficulty of using this method lies in obtaining the set $\mathcal{S}$.
+In the worst case, \ie the CRN forms a full connected graph, the size of $S$ is $\Sigma_{r=1}^{N}\ {N \choose r} = 2^N-1$.
+To levitate this problem, a smaller set, \ie $\mathcal{G} \subset \mathcal{S}$ can be used.
 $\mathcal{G}$ can be prepared based on the cluster size, and it is recommended to include all the singleton clusters to make sure the availability of feasible solutions.
@@
 In CRN, it is necessary to do clustering again on some occasions.
-For example, when a certain amount of CR users move away from their clusters, \ie they loose the direction connection with any member in their previous clusters, or a certain amount of clusters can not be maintained as the CC in these clusters don't exist any longer due to primary users' activity.
+For example, when a certain amount of CR users move away from their clusters, \ie they loose the direction connection with any member in their previous clusters, or a certain amount of clusters can not be maintained as the CCs in these clusters don't exist any longer due to primary users' activity.
 Hence, when the spectrum availability and the CR users' location change frequently, the centralized robust clustering scheme is not suitable for CRN.
@@
 
-In this subsection, we illustrate the pressing necessity to control the cluster size when CRN becomes denser.
-
-We consider a cluster $C(i)$ where $i$ is the cluster head in a dense CRN. 
-To make the analysis easier, we assume there is no cluster heads which are generated within $i$'s neighborhood during the procedure of guaranteeing CCs.
-Assuming the CR users and PUs are evenly distributed and PUs occupy the licensed channels randomly, then both CR nodes density and channel availability in the CRN can be seen to be spatially homogeneous.
-In this case the formed clusters are decided by the transmission range and network density.
-According to Algorithm~\ref{alg0}, the nearest cluster heads could locate just outside node $i$'s transmission range.
-%
-An instance of this situation is shown in Figure~\ref{clusters_denseNetwork}.
-In the figure, black dots represent cluster heads, the circles denote the transmission ranges of cluster heads.
-Cluster members are not shown in the figure.
-%Circles represent the transmission range of cluster head, within which CR nodes are absorbed in cluster.
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.3\linewidth]{clusters_denseNetwork_2.pdf}
-  \caption{Clusters formation in extremely dense CRN. Black dots are cluster heads, cluster members are not drawn.}
-  \label{clusters_denseNetwork}
-\end{figure}
-Let $l$ be the length of side of simulation plan square, and $r$ be CR's transmission radius.
-Based on the aforementioned analysis and geometry illustration as shown in Figure~\ref{clusters_denseNetwork}, we give an estimate on the maximum number of generated clusters, which is the product of the number of cluster heads in one row and that number in one line, $l/r * l/r = l^2/r^2$.
-%Now we verify the estimation with simulation.
-%We distribute CR and primary users randomly on a square plain, $r$=10 and $l$=50.
-%Network density is increased by adding more CR users.
-%We now have a look at how does the network density affect the cluster size when the transmission range is constant.
-%This implicates when the cluster size is decided by the density of the network.
-%As to SOC, the membership of one cluster is decided after a complex process, and the cluster size is roughly the same with one neighborhood.xxxx
-%We can see from the example that although two neighbouring clusters can overlap greatly with each other, no cluster head will be covered by other clusters.
-Given $r$=10 and $l$=50, the maximum number of clusters is 25.
-The number of clusters in the simulation is shown in Figure~\ref{number_clusters_scale}.
-Simulation is run for 50 times and the confidence interval is 95\%.
-With the increase of CR users, network density (the average number of neighbours) increases linearly, and the number of clusters approaches to 25 which complies with the estimation.
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=0.7\linewidth]{number_clusters_upperBound.pdf}
-  \caption{The correlation between the number of formed clusters and network density.}
-  \label{number_clusters_scale}
-\end{figure}
-
-Both analysis and simulation show that when applying ROSS, after the clusters are saturated with the increase of network density, the cluster size increases linearly with the network density, thus certain measures are needed to curb this problem.
+%In this subsection, we illustrate the pressing necessity to control the cluster size when CRN becomes denser.
+%
+%We consider a cluster $C(i)$ where $i$ is the cluster head in a dense CRN. 
+%To make the analysis easier, we assume there is no cluster heads which are generated within $i$'s neighborhood during the procedure of guaranteeing CCs.
+%Assuming the CR users and PUs are evenly distributed and PUs occupy the licensed channels randomly, then both CR nodes density and channel availability in the CRN can be seen to be spatially homogeneous.
+%In this case the formed clusters are decided by the transmission range and network density.
+%According to Algorithm~\ref{alg0}, the nearest cluster heads could locate just outside node $i$'s transmission range.
+%%
+%An instance of this situation is shown in Figure~\ref{clusters_denseNetwork}.
+%In the figure, black dots represent cluster heads, the circles denote the transmission ranges of cluster heads.
+%Cluster members are not shown in the figure.
+%%Circles represent the transmission range of cluster head, within which CR nodes are absorbed in cluster.
+%\begin{figure}[h!]
+%  \centering
+%  \includegraphics[width=0.3\linewidth]{clusters_denseNetwork_2.pdf}
+%  \caption{Clusters formation in extremely dense CRN. Black dots are cluster heads, cluster members are not drawn.}
+%  \label{clusters_denseNetwork}
+%\end{figure}
+%Let $l$ be the length of side of simulation plan square, and $r$ be CR's transmission radius.
+%Based on the aforementioned analysis and geometry illustration as shown in Figure~\ref{clusters_denseNetwork}, we give an estimate on the maximum number of generated clusters, which is the product of the number of cluster heads in one row and that number in one line, $l/r * l/r = l^2/r^2$.
+%%Now we verify the estimation with simulation.
+%%We distribute CR and primary users randomly on a square plain, $r$=10 and $l$=50.
+%%Network density is increased by adding more CR users.
+%%We now have a look at how does the network density affect the cluster size when the transmission range is constant.
+%%This implicates when the cluster size is decided by the density of the network.
+%%As to SOC, the membership of one cluster is decided after a complex process, and the cluster size is roughly the same with one neighborhood.xxxx
+%%We can see from the example that although two neighbouring clusters can overlap greatly with each other, no cluster head will be covered by other clusters.
+%Given $r$=10 and $l$=50, the maximum number of clusters is 25.
+%The number of clusters in the simulation is shown in Figure~\ref{number_clusters_scale}.
+%Simulation is run for 50 times and the confidence interval is 95\%.
+%With the increase of CR users, network density (the average number of neighbours) increases linearly, and the number of clusters approaches to 25 which complies with the estimation.
+%
+%\begin{figure}[h]
+%  \centering
+%  \includegraphics[width=0.7\linewidth]{number_clusters_upperBound.pdf}
+%  \caption{The correlation between the number of formed clusters and network density.}
+%  \label{number_clusters_scale}
+%\end{figure}
+It is necessary to control the cluster size when CRN becomes denser.
+Both analysis and simulation~\cite{robust_clustering_arxiv} show that when applying ROSS, after the clusters are saturated with the increase of network density, the cluster size increases linearly with the network density, thus certain measures are needed to curb this problem.
 This task falls to the cluster heads.
@@
 This process ends when each cluster's size is smaller or equal to $t \cdot\delta$.
- %delta needs to be changed, f(delta) XXXXXXX
 This procedure is similar with guaranteeing the existence of CCs in cluster, thus can reuse Algorithm~\ref{alg_size_control_available_CCC}.
@@
 \item ROSS without size control, \ie ROSS-DGA and ROSS-DFA.
-\item ROSS with size control. \ie ROSS-$\delta$-DGA and ROSS-$\delta$-DFA where $\delta$ is the desired cluster size.
+\item ROSS with size control, \ie ROSS-$\delta$-DGA and ROSS-$\delta$-DFA where $\delta$ is the desired cluster size.
 In the following, we refer to the above mentioned four schemes as the variants of ROSS.

### 2016-12-08 journal-draft/bare_jrnl_comsoc.tex
modified some notations and minor errors

@@
 \begin{aligned}
-     &\min\limits_{w_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (w_i*t_{ij}) \\
+     &\min\limits_{w_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (w_i\cdot t_{ij}) \\
      &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, for\,\,\forall j=1, \ldots, N \\
-   &&& \Sigma_{j=1}^N x_{ij} = |C_i|*w_i,\, for\,\,\forall i=1, \ldots, M \\
+   &&& \Sigma_{j=1}^N x_{ij} = |C_i|\cdot w_i,\, for\,\,\forall i=1, \ldots, M \\
   % &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
@@
 \begin{aligned}
-     &\min\limits_{w_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (-w_i* \frac{q_{ij}}{|C_i|} + w_i*p_i(C_i)) \\
+     &\min\limits_{w_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (-w_i\cdot \frac{q_{ij}}{|C_i|} + w_i\cdot p_i(C_i)) \\
 \notag
@@
 The number of clusters heads, as discussed in Section~\ref{phaseI}, is dependent on the network density and the CR node's transmission range.
-As shown in Figure~\ref{number_clusters_scale}, the cluster heads take up only 3.4\% to 20\% of the total number of CR nodes.
+The simulation in \cite{robust_clustering_arxiv} shows that the cluster heads are only 3.4\% to 20\% of the total CR nodes.
 
@@
 \SetAlgoLined
-\KwIn{$d_j, g_j, j\in \text{Nb}_i\setminus \Lambda$, $\Lambda$ means cluster heads. Empty sets $\tau_1,\tau_2$}
-\KwResult{Returning 1 means $i$ is cluster head, then $d_j$ is set to 0, $j\in \text{Nb}_i\setminus \Lambda$. returning 0 means $i$ is not cluster head.}
-
-\If{$\nexists j\in \text{Nb}_i\setminus \Lambda$, such that $d_i \geq d_j$}{
+\KwIn{$d_j, g_j, j\in \text{Nb}(i)\setminus \Lambda$, $\Lambda$ means cluster heads. Empty sets $\tau_1,\tau_2$}
+\KwResult{Returning 1 means $i$ is cluster head, then $d_j$ is set to 0, $j\in \text{Nb}(i)\setminus \Lambda$. returning 0 means $i$ is not cluster head.}
+
+\If{$\nexists j\in \text{Nb}(i)\setminus \Lambda$, such that $d_i \geq d_j$}{
 	return 1;
 	}
-\eIf{$\exists j\in \text{Nb}_i\setminus \Lambda$, such that $d_i > d_j$}{
+\eIf{$\exists j\in \text{Nb}(i)\setminus \Lambda$, such that $d_i > d_j$}{
 	return 0;}{
-	\If{$\nexists j\in \text{Nb}_i\setminus \Lambda$, such that $d_j == d_i$}{
+	\If{$\nexists j\in \text{Nb}(i)\setminus \Lambda$, such that $d_j == d_i$}{
 	$\tau_1 \leftarrow j$
@@
 	%calculate $\lambda = \min_{i\in C, i\neq H_C}(|K_{H_C}\cap K_i|)$;\\
-	\eIf{$\exists$ only one $i\in C\setminus H_C$, $i = \argmin(|K_{H_C}\cap K_i|)$}{
+	\eIf{$\exists$ only one $i\in C\setminus h(C)$, $i = \argmin(|K_{h(C)}\cap K_i|)$}{
 			$C=C\setminus i$;
 		}{
-				$\exists$ multiple $i$ which satisfies $i = \argmin(|K_{H_C}\cap K_i|)$;\\ $\tau_1\leftarrow i$;		
+				$\exists$ multiple $i$ which satisfies $i = \argmin(|K_{h(C)}\cap K_i|)$;\\ $\tau_1\leftarrow i$;		
 		}
@@
 		}
-	\eIf{$\exists$ only one $C\in \tau_1$, $C = \argmax(K_{h_C}\cap K_i)$}{
+	\eIf{$\exists$ only one $C\in \tau_1$, $C = \argmax(K_{h(C)}\cap K_i)$}{
 			return $C$;
 		}{
-				$\exists$ multiple $C\in S_i$ which satisfies $C = \argmax(K_{h_C}\cap K_i)$;\\ 
+				$\exists$ multiple $C\in S_i$ which satisfies $C = \argmax(K_{h(C)}\cap K_i)$;\\ 
 				$\tau_2\leftarrow C$;		
@@
 		}{
-				return $\argmin_{C\in \tau_2}h_C$;\\
+				return $\argmin_{C\in \tau_2}h(C)$;\\
 		}

### 2016-12-10 journal-draft/bare_jrnl_comsoc.tex
minor modification, before full polishing

@@
 %
-A clustering scheme (denoted as SOC) which is designed to generate robust clusters against primary users is proposed in~\cite{LIU_TMC11_2}.
+A distributed clustering scheme (denoted as SOC) which is designed to generate robust clusters against primary users is proposed in~\cite{LIU_TMC11_2}.
+The robustness of the clusters is obtained from the multiple CCs.
 SOC involves three phases of distributed executions.
 In the first phase, every secondary user forms clusters with some one-hop neighbors, in the second and third phase, each secondary user seeks to either merge other clusters or join one of them.
-The metric adopted by every secondary user in the three phases is the product of the number of CCs and cluster size.
+The metric adopted by every secondary user in all the phases is the product of the number of CCs and cluster size.
 The drawbacks are as follows, although the adopted metric considers both cluster size and the number of CCs, cluster formation can be easily dominated by only one factor, e.g.
@@
 Compared with the clustering schemes introduced above, the clusters are formed faster and the clusters possess more CCs within and among clusters than SOC.
-But this work doesn't intervene the outcome of singleton clusters, although the cluster sizes are not as divergent as SOC.
+But as all the other clustering schemes, this work doesn't intervene the outcome of the very small or very large clusters which are not desirable, although the cluster sizes are not as divergent as SOC.
 Furthermore, this work doesn't consider the robustness of clusters against the increasing activity of primary users, which leaves their claim of robustness unverified.
@@
 %
-With the requirements on the cluster size are enforced, \ie the desired size is $\delta$ and the cluster sizes should fall in the scope $\langle\delta_1, \delta_2\rangle$, where $\delta, \delta_1, \delta_2\in \mathbb{Z}^+$, and $\delta_1 \leq \delta\leq \delta_2$, a feasible clustering solution is a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, which satisfies
-$\delta_1\leq|C_i|\leq \delta_2, \bigcup_{C_i\in \mathcal{S}'} C_i = \mathcal{N}$ and $C_{i'}\cap C_i =\emptyset$ where $C_{i'}, C_i\in \mathcal{S}'$ and $i'\neq i$.
-The optimal clustering solution is the feasible clustering solution whose sum of the numbers of CCs of clusters $\sum_{C\in \mathcal{S}'} f(C)$ is the maximal.
+When the requirements on the cluster size are enforced, \ie the desired size is $\delta$ and the cluster sizes should fall in the scope $\langle\delta_1, \delta_2\rangle$, where $\delta, \delta_1, \delta_2\in \mathbb{Z}^+$, and $\delta_1 \leq \delta\leq \delta_2$, a feasible clustering solution is a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, which satisfies
+$\delta_1\leq|C_i|\leq \delta_2, \bigcup_{C_i\in \mathcal{S}'} C_i = \mathcal{N}$ and $C_{i'}\cap C_i =\emptyset$ where $C_{i'}, C_i\in \mathcal{S}'$, $i'\neq i$.
+
+The robust clustering problem in CRN is to find the optimal clustering solution from the feasible clustering solutions, whose sum of the numbers of CCs of clusters $\sum_{C\in \mathcal{S}'} f(C)$ is the maximal.
 

### 2016-12-11 journal-draft/bare_jrnl_comsoc.tex
polished sec 1-4

@@
 % Do not put math or special symbols in the title.
-\title{Versatile Robust Clustering of Ad Hoc Cognitive Radio Network}
+\title{Robust Clustering for Ad Hoc Cognitive Radio Network}
 %
@@
 %As long as there is a CC available, the corresponding cluster can continue to exchange payload data.
-In the context of CRN, the activity of primary users is usually unknown to the secondary users, thus when the primary users' activity is deemed as random, the cluster which secures more CCs will anticipate a longer time span.
+In the context of CRN, the activity of primary users is usually unknown to the secondary users, thus when the primary users' activity is deemed as random, the cluster which secures more CCs will anticipate a longer life expectancy.
 It is obvious that fewer members in a cluster yield more CCs, but obtaining more CCs by decreasing the cluster size contradicts to the motivation of clustering, \ie benefit the cluster members with cooperative decision making.
@@
 %\cite{clustering_globecom11} proposes clustering strategy in cognitive radio network, which looks into the relationship between cluster size and power consumption and accordingly controlling the cluster size to decrease power consumption.
-In respect of CRN, \cite{Zhao07, Chen07,Affinity_clustering_09icccn} propose the clustering schemes to form clusters, where securing CCs is the only goal.
+In respect of CRN, \cite{Zhao07, Chen07,Affinity_clustering_09icccn} propose the clustering schemes which partition the CRN and make sure that every cluster possesses at least one CC.
 Clustering scheme~\cite{Consensus_based_clustering12} improves spectrum sensing accuracy with cluster structure.
@@
 \cite{clustering_globecom11, TWC2012_cooperative_communication} target on the QoS provisioning and energy efficiency with cluster structure.
-\cite{cluster_EW10} forms clusters to coordinate the control channel usage within one cluster.
+\cite{cluster_EW10} forms clusters to coordinate the control channel usage within the clusters.
 An event-driven clustering scheme is proposed for cognitive radio sensor network in \cite{Ozger_cluster_crsn_13}.
@@
 A distributed clustering scheme (denoted as SOC) which is designed to generate robust clusters against primary users is proposed in~\cite{LIU_TMC11_2}.
-The robustness of the clusters is obtained from the multiple CCs.
+The robustness of the clusters is obtained from the multiple CCs in each cluster.
 SOC involves three phases of distributed executions.
@@
 The metric adopted by every secondary user in all the phases is the product of the number of CCs and cluster size.
-The drawbacks are as follows, although the adopted metric considers both cluster size and the number of CCs, cluster formation can be easily dominated by only one factor, e.g.
+The drawbacks of this scheme are as follows, although the adopted metric considers both cluster size and the number of CCs, cluster formation can be easily dominated by only one factor, e.g.
 a node which can access many channels may exclude its neighbor and form a cluster by itself.
@@
 A distributed clustering scheme ROSS is proposed in~\cite{Li11_ROSS} under the game theoretic framework. 
-Compared with the clustering schemes introduced above, the clusters are formed faster and the clusters possess more CCs within and among clusters than SOC.
-But as all the other clustering schemes, this work doesn't intervene the outcome of the very small or very large clusters which are not desirable, although the cluster sizes are not as divergent as SOC.
+Compared with the clustering schemes introduced above, the clusters are formed faster and the clusters possess more CCs than SOC.
+But as all the other clustering schemes, this work doesn't intervene the outcome of the very small or very large clusters which are not desirable.
 Furthermore, this work doesn't consider the robustness of clusters against the increasing activity of primary users, which leaves their claim of robustness unverified.
 %
-This paper is on the basis of the work in~\cite{Li11_ROSS}, but extends in two directions.
-First, this paper sticks to a new metric of robustness, and considers the clusters when primary users' activity becomes more dynamic.
+This paper is on the basis of the work in~\cite{Li11_ROSS}, but extends in two dimensions.
+First, this paper renews the definition of robustness of clusters in a CRN, which is no longer the average number of CCs of clusters, but the ability of the clusters to sustain when the primary users' activity becomes more dynamic.
 Second, this paper proposes size control mechanism, which solves the problem of devergence of clusters sizes in ~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
@@
 %For our scheme we can prove convergence in cluster formation phase and resolve ambiguities with respect to cluster membership in a game-theoretic setting. 
-The new extensions are made on basis of ROSS and its light weighted version, the latter involves less overheads thus are more suitable for the scenario where fast deployment is desired.
-Throughout this paper, we refer to the clustering schemes on the basis of ROSS as \textit{variants of ROSS}, which include the fast versions and that with size control function.
+The new extensions are made on basis of ROSS and its light weight version, the latter involves less overheads thus are more suitable for the scenario where fast deployment is desired.
+Throughout this paper, we refer to the clustering schemes on the basis of ROSS as the \textit{variants of ROSS}.
 
@@
 %As to the relation between the primary and secondary users,
-If a CR node $i$ locates within the transmission range of an active primary user $p$, then $i$ is not allowed to use the channel which is being used by $p$.
+If a CR node $i$ locates within the transmission range of an active primary user $p$, $i$ is not allowed to use the channel which is being used by $p$.
 %On the other hand, if $i$ is not in the transmission range of primary user $p$, $i$ can certainly not detect the presence of $p$.
@@
 In particular, one cluster consists of a cluster head $h(C)$ and a number of cluster members, and the cluster head is able to communicate with any cluster member directly.
-A cluster can be composed only by the cluster head.
-$\text{Nb}(i)$ denotes node $i$'s neighborhood which consists of all its one hop neighbors.
+A cluster can be formed only by the cluster head.
+%$\text{Nb}(i)$ denotes node $i$'s neighborhood which consists of all its one hop neighbors.
 %For any cluster member $i \in C$, $i \in \text{Nb} (h_C) $ holds.
@@
 
-Given a cognitive radio network $\mathcal{N}$ where $|\mathcal{N}|=N$, the collection of all the possible clusters\footnote{Possible cluster means the collection of CR nodes, which complies with the definition in~\ref{sec:model}} in $\mathcal{N}$ is denoted as $\mathcal{S}$ where $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$ \footnote{The subscripts of the clusters can be decided in any convenient way, \ie the sequence of identifying them.} and there is $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$.
-%
-When the requirements on the cluster size are enforced, \ie the desired size is $\delta$ and the cluster sizes should fall in the scope $\langle\delta_1, \delta_2\rangle$, where $\delta, \delta_1, \delta_2\in \mathbb{Z}^+$, and $\delta_1 \leq \delta\leq \delta_2$, a feasible clustering solution is a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, which satisfies
-$\delta_1\leq|C_i|\leq \delta_2, \bigcup_{C_i\in \mathcal{S}'} C_i = \mathcal{N}$ and $C_{i'}\cap C_i =\emptyset$ where $C_{i'}, C_i\in \mathcal{S}'$, $i'\neq i$.
+Given a cognitive radio network $\mathcal{N}$ where $|\mathcal{N}|=N$, the collection of all the possible clusters\footnote{Possible cluster means the collection of CR nodes, which complies with the definition in~\ref{sec:model}} is denoted as $\mathcal{S}$ where $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$ \footnote{The subscripts of the clusters can be decided in any convenient way, \ie the sequence of identifying them.} and there is $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$.
+%
+When the requirements on the cluster size are enforced, \ie the desired size is $\delta$ and the cluster sizes should fall in the scope $\langle\delta_1, \delta_2\rangle$, where $\delta, \delta_1, \delta_2\in \mathbb{Z}^+$, $\delta_1 \leq \delta\leq \delta_2$, then a feasible clustering solution is a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, which satisfies
+$\delta_1\leq|C_i|\leq \delta_2, \bigcup_{C_i\in \mathcal{S}'} C_i = \mathcal{N}$ and $C_{i'}\cap C_i =\emptyset$, $C_{i'}, C_i\in \mathcal{S}'$, $i'\neq i$.
 
@@
 The proof is in Appendix~\ref{proof_theorem1}.
-%This theorem actually indicates that the robust clustering problem in CRN is NP-hard.
-
-We propose a centralized solution which solves an optimization with standard solvers. 
+
+We propose a centralized solution for the robust clustering problem, which solves an optimization with standard solvers. 
 To formulate the optimization, we need to do some preparation beforehand.
@@
 Second, we assign a cluster size related weight to each cluster, which is positively correlated with the difference between the cluster size and the desired cluster size. 
-In particular, considering $|\mathcal{S}|=M$, $C_i\in \mathcal{S}$ means the $i$ th cluster in $\mathcal{S}$, and $\delta$ is the desired size, the size related weight for each cluster is given as follows,
+Considering $|\mathcal{S}|=M$, $C_i\in \mathcal{S}$ means the $i$ th cluster in $\mathcal{S}$, and $\delta$ is the desired size, the size related weight for each cluster is given as follows,
 $$
@@
 The optimization searches the set $\mathcal{S}$ and decides on certain clusters which constitute the whole CRN without overlapping between any two of them, besides, the sum of CCs of the chosen clusters is maximized.
-Then, a central node (or controller) with the knowledge of all CR nodes (and also the possible clusters) will solve the problem based on the following formulation.
+Then, a central node (or controller) with the knowledge of all CR nodes (and also the possible clusters) can solve the problem based on the following formulation.
 
@@
 \begin{aligned}
-     &\min\limits_{w_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (w_i\cdot t_{ij}) \\
+     &\max\limits_{w_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (w_i\cdot t_{ij}) \\
      &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, for\,\,\forall j=1, \ldots, N \\
@@
 %By permitting the existence of the singleton clusters, we can ensure that the $\mathcal{S}'$ in Definition~\ref{def_centralized_clustering} is always be feasible.
-$t_{ij}$ is a constant which is $p_i(C_i) - \frac{q_{ij}}{|C_i|}$.
+$t_{ij}$ is a constant which is $\frac{q_{ij}}{|C_i|} - p_i(C_i)$.
 $q_{ij}= |K(C_i)|$ when there is $j\in C_i$, and $q_{ij}= 0$ when there is $j\notin C_i$.
@@
 Now we examine the objective function to see whether it in line with the goal to maximize the total number of CCs meanwhile consider the restriction on the cluster size.
-Replacing $t_{ij}$ with $p_i(C_i) - \frac{q_{ij}}{|C_i|}$, the objective function becomes,
+Replacing $t_{ij}$ with $\frac{q_{ij}}{|C_i|} - p_i(C_i)$, the objective function becomes,
 \begin{equation}
 \begin{aligned}
-     &\min\limits_{w_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (-w_i\cdot \frac{q_{ij}}{|C_i|} + w_i\cdot p_i(C_i)) \\
+     &\max\limits_{w_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (w_i\cdot \frac{q_{ij}}{|C_i|} - w_i\cdot p_i(C_i)) \\
 \notag
@@
 The sum of the first items is the sum of CCs of all the chosen clusters.
-The minus sign in front of the first item explains the reason why we minimize instead to maximize the objective function.
-As to the second item, when $w_i$ is zero ($C_i$ is chosen), if $|C_i|\neq\delta$, the second component will be positive which contradicts the direction of the optimization.
-Thus the second item discourages the appearance the clusters whose sizes are different from $\delta$, especially those whose sizes diverge far from $\delta$.
+As to the second item, when $w_i$ is 1 ($C_i$ is chosen) and $|C_i|\neq\delta$, it will be negative, which contradicts the direction of the optimization.
+Thus the second item discourages the appearance the clusters whose sizes are different from $\delta$, especially those whose sizes are not $\delta$.
 
@@
 To levitate this problem, a smaller set, \ie $\mathcal{G} \subset \mathcal{S}$ can be used.
+In this case, the global optimal may not be found.
 $\mathcal{G}$ can be prepared based on the cluster size, and it is recommended to include all the singleton clusters to make sure the availability of feasible solutions.
@@
 ROSS consists of two cascaded phases: \textit{cluster formation} and \textit{membership clarification}.
-In the first phase, clusters are formed quickly and every CR user becomes either a cluster head or a cluster member.
+In the first phase, clusters are formed quickly and every CR user becomes either a cluster head or a cluster member, besides, cluster size control is implemented in this phase.
 In the second phase, non-overlapping clusters are formed in a way that the CCs of relevant clusters are mostly increased.
@@
 %In other words, CR node $i$ becomes cluster head if $d_i > d_k, \forall k\in \texttt{Nb}_i\setminus CHs$ ($CHs$ donate the cluster heads existing in $\texttt{Nb}_i$).
-If there is another CR node $j$ in its neighborhood which has the same individual connectivity degree as $i$, \ie $d_j = d_i$ and $d_j < d_{k}, \forall k\in \text{Nb}(j)\setminus \{\Lambda\cup i\}$ where $\Lambda$ denotes the cluster heads, then the node between $i$ and $j$, which has higher neighborhood connectivity degree will become the cluster head, and the other node become one member of the newly identified cluster head.
-If $g_i = g_j$ as well, the node ID is used to break the tie, \ie the one with smaller node ID becomes a cluster head.
+If there is another CR node $j$ in its neighborhood which has the same individual connectivity degree as $i$, \ie $d_j = d_i$ and $d_j < d_{k}, \forall k\in \text{Nb}(j)\setminus \{\Lambda\cup i\}$ where $\Lambda$ denotes the cluster heads, then the node between $i$ and $j$, which has higher neighborhood connectivity degree will become the cluster head, and the other node will become one member of the newly identified cluster head.
+If $g_i = g_j$ as well, the node ID is used to break the tie, \ie the one with smaller node ID becomes the cluster head.
 %
@@
 %\end{proof}
-When a CR node $i$ is associated to multiple clusters, \ie $i$ has received multiple notifications of cluster head eligibility from different CR nodes, $d_i$ is still set to be $M$. 
+When a CR node $i$ is associated to multiple clusters, \ie $i$ has received multiple notifications from different cluster heads, $d_i$ is still set to be $M$. 
 %In other words, with this manipulation on its individual connectivity degree, every CR node in the network will be involved in the clustering process, the proof will be given later.
-The manipulation of the individual connectivity degree of the cluster members fastens the speed of completing choosing the cluster heads.
+The manipulation of the individual connectivity degree of the cluster members accelerates the decision on the cluster heads.
 %, which enables the nodes which are outside of the cluster can possibly become cluster heads or can also be included into other clusters.
-We have the following theorem to show that as long as a secondary user's individual connectivity degree is greater than zero, every secondary user will eventually be either integrated into a certain cluster, or becomes a cluster head.
+We have the following theorem to show that when the secondary users' individual connectivity degrees are greater than zero, every secondary user will eventually be either integrated into a certain cluster, or becomes a cluster head.
 \begin{theorem}
@@
 
-The procedure of the proof also illustrates the time needed to conduct Algorithm~\ref{clustering:theorem}. 
+The procedure of the proof also illustrates the maximal time needed to conduct Algorithm~\ref{clustering:theorem}. 
 Consider an extreme scenario, where all the secondary nodes sequentially execute Algorithm~\ref{alg0}, \ie they constitute a list as discussed in the example in the proof.
@@
 The pseudo code for this procedure is shown in Algorithm~\ref{alg_size_control_available_CCC}.
-As to the nodes which are eliminated from the previous clusters, they restore their original individual connectivity degrees, execute Algorithm~\ref{alg0} and become either cluster heads or get included into other clusters afterwards according to Theorem~\ref{clustering:theorem}.
-
-During Phase I, when ever a CR node is decided to be a cluster head and accordingly forms a cluster, or its cluster's composition is changed, the cluster head will broadcast the updated information about its cluster, which includes the sets of available channels on all its cluster members.
+As to the nodes which are eliminated from the previous clusters, they restore their original individual connectivity degrees, then execute Algorithm~\ref{alg0} and become either cluster heads or get included into other clusters afterwards according to Theorem~\ref{clustering:theorem}.
+
+During Phase I, whenever ever a CR node is decided to be a cluster head and accordingly forms a cluster, or its cluster's composition is changed, the cluster head will broadcast the updated information about its cluster, which includes the sets of available channels on all its cluster members.
 
@@
 Both analysis and simulation~\cite{robust_clustering_arxiv} show that when applying ROSS, after the clusters are saturated with the increase of network density, the cluster size increases linearly with the network density, thus certain measures are needed to curb this problem.
-This task falls to the cluster heads.
+This task falls upon the cluster heads.
 To control the cluster size, cluster heads prune their cluster members to reach the desired cluster size.
@@
 Hence, a cluster head excludes some cluster members when the cluster size exceeds $t\cdot \delta$, where constant parameter $t$ is dependent on the network density and CR nodes' transmission range and $t>1$.
-In particular, the cluster head removes the cluster members sequentially according to the following principle, the absence of one cluster member leads to the maximum increase of common channels within the cluster.
+In particular, the cluster head removes the cluster members sequentially according to the following principle, the absence of one cluster member leads to the maximum increase of the CCs within the cluster.
 This process ends when each cluster's size is smaller or equal to $t \cdot\delta$.
-This procedure is similar with guaranteeing the existence of CCs in cluster, thus can reuse Algorithm~\ref{alg_size_control_available_CCC}.
+This procedure is similar with that in Section~\ref{ross_p1_guarantee_ccc}, thus Algorithm~\ref{alg_size_control_available_CCC} can be reused.
 The $t$ is set to 1.3.
@@
 %The set of available channels of one cluster are known by the debatable nodes which locate in that cluster. %this is finished 
-Note that node $i$ is aware of the spectrum availability on all the cluster members of each claiming cluster, thus node $i$ is able to calculate how many more CCs can be produced in one claiming cluster if $i$ leaves that cluster.
+Note that node $i$ has been notified of the spectrum availability on all the cluster members of each claiming cluster, thus node $i$ is able to calculate how many more CCs can be produced in one claiming cluster if $i$ leaves that cluster.
 %Based on this calculation, $i$ decides on one claiming cluster to stay and leaves the other claiming clusters.
-If there exists one cluster $C\in S_i$, when $i$ leaves this cluster brings the least increased CCs than leaving any other claiming clusters, then $i$ chooses to stay in cluster $C$.
+If there exists one cluster $C\in S_i$, when $i$ leaves this cluster brings less increased CCs than leaving any other claiming clusters, then $i$ chooses to stay in cluster $C$.
 When there comes a tie, among the claiming clusters, $i$ chooses to stay in the cluster whose cluster head shares the most CCs with $i$.
@@
 Game theory is a powerful mathematical tool for studying, modelling and analysing the interactions among individuals.
-A game consists of three elements: a set of players, a selfish utility for each player, and a set of feasible strategy space for each player.
+A game consists of three elements: a set of players, a selfish utility for each player, and a feasible strategy space for each player.
 In a game, the players are rational and intelligent decision makers, which are related with one explicit formalized incentive expression (the utility or cost).
@@
 To formulate the debatable nodes' membership clarification into the desired congestion game, we observe this process from a different (or opposite) perspective. 
-From the new perspective, the debatable nodes are regarded to be isolated and don't belong to any cluster, in other words, their claiming clusters become clusters which are beside them. 
+From the new perspective, the debatable nodes are regarded as isolated and don't belong to any cluster, in other words, their claiming clusters become clusters which are beside them. 
 Now for the debatable nodes, the previous problem of deciding which clusters to leave becomes a new problem that which cluster to join.
@@
 	\item $\mathcal{R} = \cup S_i, i\in \mathcal{P}$, denotes the set of resources for players to choose, in our problem, $S_i$ is the set of claiming clusters of node $i$, and $\mathcal{R}$ is the set of all claiming clusters.
-	\item Strategy space $\sum_i, i \in \mathcal{P}$ is the set of claiming clusters $S_i$.
+	\item Strategy space $\sum_i, i \in \mathcal{P}$, $\sum_i$ is the set of claiming clusters $S_i$ for $i$.
 	As debatable node $i$ is supposed to choose only one claiming cluster, then only one piece of resource will be allocated to $i$.%, accordingly this congestion game is a singleton game.
@@
 Hence, this congestion game is player specific~\cite{Ackermann06purenash}.
-In this game, every player greedily updates its strategy (choosing one claiming cluster to join) if joining a different claiming cluster minimizes the decrease of CCs $\sum_{i:C\in S_i} \Delta\vert K^i(C) \vert$, and a player's strategy in the game is exactly the same with the behaviour of a debatable node in the membership clarification phas.
+In this game, every player greedily updates its strategy (choosing one claiming cluster to join) if joining a different claiming cluster minimizes the decrease of CCs $\sum_{i:C\in S_i} \Delta\vert K^i(C) \vert$, and a player's strategy in the game is exactly the same with the behaviour of a debatable node in the membership clarification phase.
 
@@
 In our problem, the players are the debatable nodes, and the resources are the claiming clusters.
-Thus the upper bound of the number of steps can be expressed as $\mathcal{O}(N^3)$.
+Thus the number of steps can be expressed as $\mathcal{O}(N^3)$.
 
@@
 The percentage of debatable nodes in $\mathcal{N}$ is illustrated in Figure~\ref{percentage_overlapping_node}, which is between 10\% to 60\% of the total number of CR nodes in the network.
-The number of clusters heads, as discussed in Section~\ref{phaseI}, is dependent on the network density and the CR node's transmission range.
+The number of clusters heads, as mentioned in Section~\ref{phaseI}, is dependent on the network density and the CR node's transmission range.
 The simulation in \cite{robust_clustering_arxiv} shows that the cluster heads are only 3.4\% to 20\% of the total CR nodes.

### 2016-12-11 journal-draft/bare_jrnl_comsoc.tex
polished section 5-6

@@
 
-\item \textit{neighborhood connectivity degree} $g_i$: $g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$. 
+\item \textit{Neighborhood connectivity degree} $g_i$: $g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$. 
 It is the number of CCs which are available for $i$ and all its neighbors.
@@
 On the basis of ROSS-DGA, we propose a faster version ROSS-DFA which differs from ROSS-DGA in the second phase.
-With ROSS-DFA, debatable nodes decide their respective cluster heads once.
+With ROSS-DFA, debatable nodes decide their respective cluster heads only once.
 The debatable nodes consider their claiming clusters to include all their debatable nodes, thus the membership of claiming clusters is static and all the debatable nodes can make decision simultaneously without considering the change of membership of their claiming clusters.
@@
 SOC's comparison schemes are designed either for ad hoc network without consideration of channel availability~\cite{Basagni99}, or for CRN but just considering connection among CR nodes~\cite{Zhao07}.
-Thus SOC is chosen to be the only distributed scheme as comparison, besides, we also compare ROSS with the centralized scheme.
-
-Before we investigating the performance of the clustering schemes with simulation, we apply the two comparison clustering schemes in the example CRN in Figure~\ref{fig1}, and make an initial comparison in terms of the amount of CCs.
-As to the centralized robust clustering scheme, we set the desired cluster size $\delta$ as 3, as a result, according to the network topology, the collection of all the possible clusters
-$\mathcal{S}=\{\{A\}, \{B\},\dots,\{B,C\},\{B,A\},\{B,H\},\cdots,\{B,A,C\},$\\$\{B,H,C\}, \{A,D,C\},\cdots\}$, and $|\mathcal{S}|=38$.
-We set $\rho_1$ and $\rho_1$ as 0.2 and 0.8 respectively.
-The formed clusters by the centralized clustering scheme are shown in Fig.~\ref{fig:final_clustering_LP}.
-%$\{\{D,E,F\},\{A,C,G\},\{H,G\}\}$, the numbers of CCs are 2, 3, 3.
-The resulted clustering solutions from SOC is shown in Fig.~\ref{fig:final_clustering_soc}.
-%
-We compare the average number of CCs achieved by different schemes, the results of ROSS\footnote{In this example network, both ROSS-DGA and ROSS-DFA and their size control variants form the same clusters)}, centralized and SOC are 2.66, 2.66, and 3 respectively.
-Note there is one singleton cluster $C(H)$ generated by SOC, which is not preferred.
-When we only consider the clusters which are not singleton, the average number of CCs of SOC drops to 2.5. 
+Thus SOC is the only distributed scheme as comparison.
+As to the CRN shown in Figure~\ref{fig1}, the resulted clusters by the centralized scheme and SOC are shown in Figure~\ref{fig:final_clustering}.
+
+%Before we investigating the performance of the clustering schemes with simulation, we apply the two comparison clustering schemes in the example CRN in Figure~\ref{fig1}, and make an initial comparison in terms of the amount of CCs.
+%As to the centralized robust clustering scheme, we set the desired cluster size $\delta$ as 3, as a result, according to the network topology, the collection of all the possible clusters
+%$\mathcal{S}=\{\{A\}, \{B\},\dots,\{B,C\},\{B,A\},\{B,H\},\cdots,\{B,A,C\},$\\$\{B,H,C\}, \{A,D,C\},\cdots\}$, and $|\mathcal{S}|=38$.
+%We set $\rho_1$ and $\rho_1$ as 0.2 and 0.8 respectively.
+%The formed clusters by the centralized clustering scheme are shown in Fig.~\ref{fig:final_clustering_LP}.
+%%$\{\{D,E,F\},\{A,C,G\},\{H,G\}\}$, the numbers of CCs are 2, 3, 3.
+%The resulted clustering solutions from SOC is shown in Fig.~\ref{fig:final_clustering_soc}.
+%%
+%We compare the average number of CCs achieved by different schemes, the results of ROSS\footnote{In this example network, both ROSS-DGA and ROSS-DFA and their size control variants form the same clusters)}, centralized and SOC are 2.66, 2.66, and 3 respectively.
+%Note there is one singleton cluster $C(H)$ generated by SOC, which is not preferred.
+%When we only consider the clusters which are not singleton, the average number of CCs of SOC drops to 2.5. 
 \begin{figure}[ht]
@@
 \item \textbf{The average number of CCs per non-singleton cluster.}
-Non-singleton cluster refers the cluster whose cluster size is larger than 1.
-%This metric denotes the robustness of the formed non-singleton clusters.
-Comparing with the metric adopted by SOC~\cite{LIU_TMC11_2}, which is the average number of CCs of all the clusters, this metric provides a more accurate description of the robustness of the non-singleton clusters.
-Having more CCs per non-singleton clusters means these clusters have longer life expectancy when the primary users' operation becomes more intense.
-%which is biased as the singleton clusters (isolated CR users) don't get benefits from the cluster structure.
-Although this metric doesn't disclose the information about the \textit{unclustered} CR nodes which are the synonyms of the singleton clusters, we still examine this metric as the number of CCs is involved in the utility adopted by all the variants of ROSS and SOC.
+Non-singleton cluster refers to the cluster whose cluster size is larger than 1.
+Previous work \cite{LIU_TMC11_2} and \cite{Li11_ROSS} claim that the larger average number of CCs over all the clusters indicates longer life expectancy when the primary users' operation becomes more intense.
+We see two flaws in this claim.
+First, the unclustered CR nodes (synonym of singleton clusters) should not be considered when obtaining the average number of CCs, as singleton clusters doesn't contribute to the collaborative computing.
+Second, the average number of CCs doesn't necessarily indicate the robustness of individual clusters, because the ability for a cluster to sustain also depends on the cluster size and the locations of the cluster members, and these information is not illustrated in the average number of CCs.
+In the performance evaluation, We will examine the metric of average number of CCs per non-singleton cluster, which excludes the bias brought in by the unclustered CR nodes.
+More importantly, we will examine whether this metric reflects the robustness of the clusters against increasingly active primary users.
 
@@
 The desired cluster size $\delta$ is 3.
+The constant for size control is 1.3.
 As to the centralized scheme, the parameters used in the \textit{punishment} for choosing the clusters with undesired sizes are set as follows, $\rho_1 =  0.4$, $\rho_2 =  0.6$.
@@
 %We have discussed the flaw of this metric as it doesn't convey the number of unclustered CR nodes, in fact, 
-In the other hand, SOC generates the most unclustered CRs, which can be seen when we discuss the performance on the number of unclustered CR nodes. 
+In the other hand, SOC generates the most unclustered CRs.
 As to the variants of ROSS, we notice that the greedy mechanism increases CCs in non-singleton clusters significantly.
@@
 Figure~\ref{size_control} depicts the empirical cumulative distribution of the CRs in clusters of different sizes, from which we have two conclusions.
-The first, SOC generates more unclustered CR nodes than other schemes.
+First, given the channel availability in the CRN, SOC generates more unclustered CR nodes than other schemes.
 The centralized schemes don't produce unclustered CR nodes in the simulation, the unclustered nodes generated by ROSS-DGA/DFA account for 3\% of the total CR nodes, as comparison, 10\% of nodes are unclustered when applying SOC.
@@
 In contrary, the variants of ROSS generate some smaller clusters which are more likely to maintain when there are more PUs.
-%The comparison on cluster sizes will be given in Section~\ref{cluster_size}.
-% when the number of PRs is 10$\sim$30, when number of PUs is 30$\sim$60, same amount of unclustered CRs are generated with variants of ROSS.
-%When there are 75 and more new PRs, centralized scheme with cluster size of 3 results in more unclustered CR nodes than variants of ROSS.
-%ROSS with size control distinguishes itself as the size control avoid the appearance of the clusters with large size.
-
-%As to the variants of ROSS, the greedy process in ROSS improves the performance.
-
-%Greedy strategy adopted in the second phase of ROSS improves the robustness of clusters, i.e. ROSS-DGA exceeds ROSS-DFA, and ROSS-$\delta$-DGA surpasses ROSS-$\delta$-DFA.
-%When the debatable CRs greedily update their affiliations, one of the metrics is the maximum increase of CCs of the demanding clusters. 
-%This observation complies with the result shown in Figure~\ref{ccc_per_nonsingleton}.
-%Meanwhile, sizes of more clusters become smaller also contributes more robustness.
-
-%\begin{figure}[h!]
-%  \centering
-%  \includegraphics[width=0.8\linewidth]{ccc_20.pdf}
-%  \caption{Number of common channels for non-singleton clusters, the numbers in the names of schemes annotate the desired cluster size.}
-%  \label{ccc_per_nonsingleton}
-%\end{figure}
-%
-%
-%\begin{figure}[h]
-%  \centering
-%  \includegraphics[width=0.8\linewidth]{survival_rate_20.pdf}
-%  \caption{Number of CRs which are not included in any clusters}
-%  \label{singleton_clusters}
-%\end{figure}
+
+The above observation shows that the average number of CCs of non-singleton clusters doesn't necessarily illustrate the robustness  of cluster against increasingly active PRs, \ie SOC obtains the largest average CCs, but generates the most vulnerable clusters.
+Besides, with similar distribution of sizes, the clusters generated by ROSS-DGA and ROSS-DFA are more robust than that by SOC.
 
@@
 \subsection{Insights Obtained from the Simulation}
+The simulation in the large CRN network confirms the conclusion made based on the simulation in the small CRN network, which is the average number of CCs along is not able to denote the robustness of the clusters, because the cluster size and the cluster members also affect the robustness.
+
 The centralized clustering scheme is able to form the clusters which satisfy the requirement on cluster size strictly, and the clusters are robust against the PUs' activity, besides, it generates the smallest control overhead in the process of clustering.
@@
 As distributed schemes, the variants of ROSS outperform SOC considerably on three metrics.
-The variants of ROSS generate much less singleton clusters than SOC, and the resulted clusters are robuster than SOC when facing the newly added PUs.
-The signaling overhead involved in ROSS is about half of that needed for SOC, and the signaling messages are much shorter that the latter.
-The sizes of the clusters generated by ROSS demonstrate smaller discrepancy than that of SOC.
-Besides, the ROSS variants with size control features achieve similar performance to the centralized scheme in terms of cluster size, and the cluster robustness is similar when applying the variants of ROSS and the centralized scheme respectively.
-
+First, the variants of ROSS generate less singleton clusters than SOC for a given CRN, and the resulted clusters are more robust than SOC when PUs become more active.
+Second, the signaling overhead involved in ROSS is about half of that needed for SOC, and the signaling messages are much shorter that the latter.
+Third, the sizes of the clusters generated by ROSS demonstrate smaller discrepancy than that of SOC.
+Moreover, the ROSS variants with size control features achieve similar performance to the centralized scheme in terms of cluster size, and the cluster robustness is similar when applying the variants of ROSS and the centralized scheme respectively.
+%
 As to the variants of ROSS, the greedy mechanism in ROSS-DGA helps to improve the performance on cluster size and cluster robustness at the cost of mildly increased signaling overhead.
@@
 Besides, the proposed schemes can generate clusters with desired sizes.
-The congestion game model in game theory is used to design the distributed schemes.
+%The congestion game model in game theory is used to design the distributed schemes.
 %A Light weighted clustering scheme ROSS is also proposed.
 Through simulation and theoretical analysis, we find that distributed schemes achieve similar performance with centralized optimization in terms of cluster robustness, signaling overhead and cluster sizes, and outperform the comparison distributed scheme on the above mentioned metrics.
-%, which is important to form clusters which maintains unbroken to the greatest extent possible under primary users' activity.
-%These schemes outperform other distributed clustering scheme in terms of both cluster survival ratio and control overhead.
-
-%The clusters resulted from ROSS-DGA and its faster version ROSS-DFA are less vulnerable compared with other distributed clustering schemes, and demonstrates similar survival rate with centralized scheme under primary users' influence.
-%An light weighted cluster size control mechanism is contained in both ROSS-DGA and ROSS-DFA, which is advantageous for cooperative sensing and network operation with clusters.
-%Furthermore, considerable less control messages are generated when compared with other clustering schemes.
 

### 2016-12-11 journal-draft/bare_jrnl_comsoc.tex
polished section 5-6 and proof 1

@@
 %When the number of PUs in CRN increases, or their operation becomes more intensive, some clusters don't seize any CCs any more, so that the cluster members and the cluster heads become unclustered, or singleton clusters.
-%If there is no common channels available any more because of the new added PRs, the cluster is regarded as destroyed and the former cluster member CRs become unclustered CRs or in other words singleton clusters.
+%If there is no common channels available any more because of the new added PUs, the cluster is regarded as destroyed and the former cluster member CRs become unclustered CRs or in other words singleton clusters.
 %We investigate the number of singleton clusters with primary users whose intensity of activities are varying.
@@
 10 PUs are in the network in the beginning, then extra 19 batches of PUs are added sequentially, where each batch includes 5 PUs. 
-%The transmission range and channel occupancy of the new PU is the same with the previous ones, \ie transmission range is $A/3$, and one channel out of 10 is randomly chosen to operate.
-
+%
 Figure~\ref{singleton_clusters} shows certain clusters can not maintain and the number of unclustered CR nodes grows when the number of PUs increases.
@@
 
-The above observation shows that the average number of CCs of non-singleton clusters doesn't necessarily illustrate the robustness  of cluster against increasingly active PRs, \ie SOC obtains the largest average CCs, but generates the most vulnerable clusters.
+The above observation shows that the average number of CCs of non-singleton clusters doesn't necessarily illustrate the robustness  of cluster against increasingly active PUs, \ie SOC obtains the largest average CCs, but generates the most vulnerable clusters.
 Besides, with similar distribution of sizes, the clusters generated by ROSS-DGA and ROSS-DFA are more robust than that by SOC.
@@
 To better understand the distribution of the sizes of formed clusters, we depict the empirical cumulative distribution of CR nodes in clusters with different sizes in Figures~\ref{cdf_clusterSize_100}~\ref{cdf_clusterSize_200}~\ref{cdf_clusterSize_300}.
-
 \begin{figure}[!h]
@@
 \end{figure}
-
 The sizes of clusters generated by ROSS-DGA and ROSS-DFA span a wider range than ROSS with size control feature.
@@
 %we assume every node has at least one neighbour.
-For the sake of contradiction, let us assume there exist some secondary user $\alpha$ which is not included into any cluster.
-Then there is at least one node $\beta\in \text{Nb}_\alpha$ such that $d_{\alpha} > d_{\beta}$. 
-According to Algorithm~\ref{alg0}, $\delta$ is not included in any clusters, because otherwise $d_{\beta} = M$, a large positive integer.
+For the sake of contradiction, let us assume there exist a secondary user $\alpha$ which is not included into any cluster.
+Then there is at least one node $\beta\in \text{Nb}(\alpha)$ such that $d_{\alpha} > d_{\beta}$ (otherwise $\alpha$ becomes cluster head). 
+In this case, according to Algorithm~\ref{alg0}, $\beta$ is not included in any clusters, because otherwise $d_{\beta} = M$, a large positive integer, which contradicts to $d_{\alpha} > d_{\beta}$.
 Now, we distinguish between two cases: 
@@
 % (COMMENT: $\beta$ not being a cluster head and $\beta$ not belonging to any cluster is not the same statement!!! ANSWER(Di): I add some more words)
-Till now, when there is no cluster head identified, the unclustered nodes, \ie $\alpha$, $\beta$ form a linked list, where their connectivity degrees monotonically decrease.
+So far, when there is no cluster head identified, the unclustered nodes, \ie $\alpha$, $\beta$ form a linked list, where their connectivity degrees monotonically decrease.
 But this list will not continue to grow, because the minimum individual connectivity degree is zero, and the length of this list is upper bounded by the total number of nodes in the CRN.

### 2017-01-18 journal-draft/bare_jrnl_comsoc.tex
typos on first page

@@
 When one or several cluster members can not access one certain CC on which primary user activity is detected, the channel will be excluded from the set of CCs.
-In particular, if that channel is being used for payload communication, the communication pair will stop and resume the transmission on another available channel from CCs.
+In particular, if that channel is being used for payload communication, the communication pair will stop and resume the transmission on another available CC.
 The availability of CCs within a cluster defines the existence of that cluster, \ie no CCs are available means the corresponding cluster doesn't exist.
@@
 It is obvious that fewer members in a cluster yield more CCs, but obtaining more CCs by decreasing the cluster size contradicts to the motivation of clustering, \ie benefit the cluster members with cooperative decision making.
-For example, spectrum sensing accuracy coralates with the cluster size~\cite{Consensus_based_clustering12}, and power consumption doesn't favor small clusters~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
+For example, spectrum sensing accuracy correlates with the cluster size~\cite{Consensus_based_clustering12}, and power consumption doesn't favor small clusters~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
 In this paper the robustness of clusters means the ability of the clusters to sustain the increasing activity of primary users.
@@
 
-There has been a lot of research done for clustering in wireless networks.
+There has been a lot of research done on clustering in wireless networks.
 In ad-hoc and mesh networks, the major goal of clustering is to maximize connectivity or to improve the performance of routes~\cite{Kawadia03, clustering_mesh_globecom2010}.

### 2017-02-05 journal-draft/bare_jrnl_comsoc.tex
modified before 2.1

@@
 Compared with the clustering schemes introduced above, the clusters are formed faster and the clusters possess more CCs than SOC.
-But as all the other clustering schemes, this work doesn't intervene the outcome of the very small or very large clusters which are not desirable.
+But as all the other clustering schemes, this scheme doesn't have control over the formation of the very small or very large clusters which are not desirable.
 Furthermore, this work doesn't consider the robustness of clusters against the increasing activity of primary users, which leaves their claim of robustness unverified.
@@
 Second, this paper proposes size control mechanism, which solves the problem of devergence of clusters sizes in ~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
-Besides, this paper provides a comprehensive analysis of the robust clustering problem and proposes the centralized solution. 
+Besides, this paper provides a comprehensive analysis of the robust clustering problem and proposes a centralized solution. 
 %We stick to the motivation of forming robust clusters in CRN \ie let more CR users benefited from the cooperative decision making which is due to the clusters. 
@@
 %On the other hand, if $i$ is not in the transmission range of primary user $p$, $i$ can certainly not detect the presence of $p$.
-We assume the primary users change their operation channels slowly, then we omit the time index for the spectrum availability, \ie as the result of spectrum sensing, $K_i \subseteq \mathcal{K}$ denotes the set of available licensed channels for CR user $i$ at a time point.
-As the transmission range of primary users is limited and secondary users have different locations, different secondary users may have different views of the spectrum availability, i.e., for any $i, j \in \mathcal{N}$, $K_i = K_{j}$ does not necessarily hold.
-A cognitive radio network can be represented as a graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{i, j\} \in E$ if and only if $K_{i} \cap K_{j}\neq \emptyset$ and $d_{i,j} < r$, where $d_{i,j}$ is the distance between $i, j$, $r$ is the radius of secondary user's transmission range.
-%
-Among the secondary users, we denote $\text{Nb}(i)$ as user $i$'s neighborhood, which consists of the CR nodes located within the transmission range of $i$.
-
-We assume there is one dedicated control channel which is used to exchange signaling messages during clustering process.
+We assume the primary users change their operation channels slowly thus we omit the time index for the spectrum availability.
+As the result of spectrum sensing, $K_i \subseteq \mathcal{K}$ denotes the set of available licensed channels for CR user $i$.
+As the transmission range of primary users is limited and secondary users have different locations, different secondary users have different views of the spectrum availability, i.e., for any $i, j \in \mathcal{N}$, $K_i = K_{j}$ does not necessarily hold.
+We therefore represent the network of CR nodes by a graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{i, j\} \in E$ if and only if $K_{i} \cap K_{j}\neq \emptyset$ and $d_{i,j} < r$, where $d_{i,j}$ is the distance between $i, j$ and $r$ is the radius of secondary user's transmission range.
+%
+Among the secondary users, we denote by $\text{Nb}(i)$ user $i$'s neighborhood, which consists of the CR nodes located within the transmission range of $i$.
+
+We assume there is one dedicated control channel which is used to exchange signaling messages during the clustering process.
 This control channel could be one of the ISM bands or other reserved spectrum which is exclusively used for transmitting control messages.\footnote{Actually, the control messages involved in the clustering process can also be transmitted on the available licensed channels through a rendezvous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}, i.e., two neighboring nodes establish communication on the same channel.}
 Over the control channel, a secondary user $i$ can exchange its spectrum sensing result $K_i$ with all its one hop neighbors $\text{Nb}(i)$.
-In the following, we refer to the licensed channel as \textit{channel} in general, and will explicitly mention the dedicated control channel if necessary.
+In the following, we refer to the licensed channel as channels in general, and will explicitly mention the dedicated control channel if necessary.
 
 We give the definition of cluster in CRN as follows. 
-A cluster $C$ is a set of secondary nodes which possess the same set of CCs.
-In particular, one cluster consists of a cluster head $h(C)$ and a number of cluster members, and the cluster head is able to communicate with any cluster member directly.
+A cluster $C$ is a set of secondary nodes which possess the same set of common channels.
+In particular, a cluster consists of a cluster head $h(C)$ and a number of cluster members, and the cluster head is able to communicate with any cluster member directly.
 A cluster can be formed only by the cluster head.
@@
 %For any cluster member $i \in C$, $i \in \text{Nb} (h_C) $ holds.
-Cluster size of $C$ is written as $|C|$.
-Cluster $C(i)$ means the cluster head of this cluster is $i$.
-$K(C)$ denotes the set of CCs in cluster $C$, $ K(C) = \cap_{i\in C} K_i$.
+The size of $C$ is denoted by $|C|$.
+When the cluster head of a cluster is $i$, we denote that cluster by $C(i)$.
+$K(C)$ denotes the set of CCs in cluster $C$, $ K(C) = \Cap_{i\in C} K_i$.
 %Clustering is performed periodically, because the secondary users are mobile and the primary users change their operation channels, thus the channel availability on secondary users changes accordingly.
-The notations used in the system model and the following problem description are listed in Table~\ref{tab1}.
+The notations used in the system model are listed in Table~\ref{tab1}.
 \begin{table}[h!]

### 2017-03-19 journal-draft/bare_jrnl_comsoc.tex
discuss the necessity of size control in the introduction, modify related works

@@
 Regarding the operation of CRN, efficient spectrum sensing is identified to be critical for a smooth operation of a cognitive radio network~\cite{Sahai_FundamentalDesignTradeoffs2006}.
-This can be achieved by cooperative spectrum sensing of multiple secondary users, which has been shown to cope effectively with noise uncertainty and channel fading, thus remarkably improving the sensing accuracy~\cite{coorperativeSensing_Akyildiz11}.
+Efficient spectrum sensing can be achieved by cooperative spectrum sensing of multiple secondary users, which has been shown to cope effectively with noise uncertainty and channel fading, thus remarkably improving the sensing accuracy~\cite{coorperativeSensing_Akyildiz11}.
 Collaborative sensing relies on the consensus of CR users\footnote{The terms user and node appear interchangeably in this paper.
@@
 % ... decreases considerably the negative probability due to the random channel effects like fading and shadowing.
-Clustering is a process of grouping certain users in a proximity into a collective.
-Clustering is also efficient to coordinate the channel switch operation when primary users are detected by at least one CR node residing in the cluster.
-The cluster head can enable all the CR devices within the same cluster to stop payload transmission swiftly on the operating channel and to vacate the channel ~\cite{willkomm08}.
-%
+Clustering is a process of grouping certain users in geographic proximity into a collective.
+In the context of cognitive radio netowrks, a formed cluster helps the participants not only improve the spectrum sensing accuracy, but also coordinate the channel switch operation when the primary users are detected by at least one secondary user in that cluster, then all the cluster menmbers can stop payload transmission swiftly and vacate the operating channel ~\cite{willkomm08}.
+Clustering also benefits the operation of a CRN by reducing the interference between cognitive clusters~\cite{centralizedSharing80222}, and supporting routing~\cite{Abbasi_survey_07}.
 %As to the coexistence of CR users, they can be notified by cluster head (CH) or other cluster members about the possible collision, the possibility for them to interfere neighbouring clusters is reduced~\cite{centralizedSharing80222}.
-In addition to the collaborate sensing advantage, the use of clusters is beneficial as it reduces the interference between cognitive clusters~\cite{centralizedSharing80222}.
-Clustering algorithm has also been proposed to support routing in cognitive radio networks ~\cite{Abbasi_survey_07}.
+Except for benefiting the dynamic spectrum sharing in CRN, clustering contributes to the other wireless networks in many aspects, which has already been discussed in many works.
 
@@
 
-Clusters are formed in the very beginning of the network operation, and re-formed periodically according to the dynamics of the CRN.
+In CRN, clusters are formed in the very beginning of the network operation, and re-formed periodically according to the dynamics of the CRN.
 Each formed cluster has one or multiple unlicensed channels which are available for every CR node in the cluster.
@@
 In the context of CRN, the activity of primary users is usually unknown to the secondary users, thus when the primary users' activity is deemed as random, the cluster which secures more CCs will anticipate a longer life expectancy.
-It is obvious that fewer members in a cluster yield more CCs, but obtaining more CCs by decreasing the cluster size contradicts to the motivation of clustering, \ie benefit the cluster members with cooperative decision making.
-For example, spectrum sensing accuracy correlates with the cluster size~\cite{Consensus_based_clustering12}, and power consumption doesn't favor small clusters~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
-In this paper the robustness of clusters means the ability of the clusters to sustain the increasing activity of primary users.
-%is synonymous with the affluence of CCs which are possessed by that cluster, to ....
+It is obvious that fewer secondary in one cluster yield more CCs, but this contradicts to one of the motivations of clustering, \ie the cooperative decision making, where more users result in more accurate sensing result~\cite{Consensus_based_clustering12}.
+
+Note that the purpose of this paper is to introduce a robust cluster structure for CRN, and the robustness here means the ability of the clusters to sustain under the influence of the increasing activity of primary users.
+We focus on the efficient formation of the clusters and the evaluation of the robustness of the formed clusters, 
+%with the intention to provide a robust infrastructure for the applications which may be conducted above that in CRN.
+that being said, when we design this clustering scheme in CRN, we do consider the services to be delivered by the network.
+Cluster sizes affect the power consumption directly in wirelss sensor networks~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
+When the cluster size is not deliberately discussed, it is also decided alongside the optimization of the network, \eg the opimal selection of the aggregation points in a wireless sensor network results in the clusters~\cite{data_aggr_algorithm_04}.
+Our scheme is able to generate the clusters with the desired size, which gives the network designers more freedom when the power consumption is involved in the design of network applications.
 
@@
 There has been a lot of research done on clustering in wireless networks.
-In ad-hoc and mesh networks, the major goal of clustering is to maximize connectivity or to improve the performance of routes~\cite{Kawadia03, clustering_mesh_globecom2010}.
-The emphasis of clustering in sensor networks is on network lifetime and coverage~\cite{Abbasi_survey_07}.
+As there is no restriction on the nodes to access the spectrum in wireless ad-hoc, mesh networks and sensor networks, the objective of clustering is to decrease the transmission power consumption~\cite{Kawadia03}, to improve the routing performance~\cite{clustering_mesh_globecom2010}, or to imrove the network lifetime and coverage~\cite{Abbasi_survey_07}.
 %Various clustering schemes are proposed to target different aspects in cognitive radio networks.
@@
 %\cite{clustering_globecom11} proposes clustering strategy in cognitive radio network, which looks into the relationship between cluster size and power consumption and accordingly controlling the cluster size to decrease power consumption.
-In respect of CRN, \cite{Zhao07, Chen07,Affinity_clustering_09icccn} propose the clustering schemes which partition the CRN and make sure that every cluster possesses at least one CC.
-Clustering scheme~\cite{Consensus_based_clustering12} improves spectrum sensing accuracy with cluster structure.
+With regard to forming clusters in CRN, deciding on the common channel within each cluster is the foremost question to answer.
+\cite{Zhao07, Chen07,Affinity_clustering_09icccn} propose the clustering schemes and make sure every cluster possesses at least one CC.
+Clustering scheme~\cite{Consensus_based_clustering12} looks for the network partition which improves the accuracy of spectrum sensing with the cluster structure.
 %Clustering scheme~\cite{clustering_globecom11} obtains the best cluster size which minimizes power consumption caused by communication within and among clusters.
-\cite{clustering_globecom11, TWC2012_cooperative_communication} target on the QoS provisioning and energy efficiency with cluster structure.
-\cite{cluster_EW10} forms clusters to coordinate the control channel usage within the clusters.
+\cite{TWC2012_cooperative_communication} forms the clusters by deciding on the cluster heads, where the transmit power for the long-haul transmission between the cluster heads is minimized.
+\cite{clustering_globecom11} proposes a cluster structure which promises energy efficiency.
+\cite{cluster_EW10} proposes strategy on how to decide on the CCs and access the multiple CCs within clusters.
 An event-driven clustering scheme is proposed for cognitive radio sensor network in \cite{Ozger_cluster_crsn_13}.
 No one among the above mentioned schemes provides the robustness to the formed clusters against primary users.
-%
-A distributed clustering scheme (denoted as SOC) which is designed to generate robust clusters against primary users is proposed in~\cite{LIU_TMC11_2}.
-The robustness of the clusters is obtained from the multiple CCs in each cluster.
+
+Robustness of clusters is discussed in~\cite{LIU_TMC11_2}, where a distributed clustering scheme (denoted as SOC) which is designed to generate robust clusters against primary users is proposed.
+The robustness of the clusters comes from the fact that there are multiple CCs available for the clusters.
 SOC involves three phases of distributed executions.
@@
 \cite{mansoor_15_cluster_robust} presents a heuristic method to form clusters, although the authors claim robustness is one goal to achieve, the minimum number of clusters is finally pursued.
-
+%
 A distributed clustering scheme ROSS is proposed in~\cite{Li11_ROSS} under the game theoretic framework. 
@@
 %For our scheme we can prove convergence in cluster formation phase and resolve ambiguities with respect to cluster membership in a game-theoretic setting. 
-The new extensions are made on basis of ROSS and its light weight version, the latter involves less overheads thus are more suitable for the scenario where fast deployment is desired.
+The new extensions are made on basis of ROSS and its light weight version, the latter involves less overheads thus is more suitable for the scenario where fast deployment is desired.
 Throughout this paper, we refer to the clustering schemes on the basis of ROSS as the \textit{variants of ROSS}.
@@
 
-As introduced in Section~\ref{intro}, in order to be robust against primary users' activity, the formed clusters should have more CCs to expect longer life expectancy.
+As introduced in Section~\ref{intro}, in order to be robust against primary users' activity, the formed clusters should have more CCs.
 On the other hand, the sizes of the formed clusters should not diverge from the desired size greatly.

### 2017-03-20 journal-draft/bare_jrnl_comsoc.tex
finished introduction section

@@
 %As long as there is a CC available, the corresponding cluster can continue to exchange payload data.
-In the context of CRN, the activity of primary users is usually unknown to the secondary users, thus when the primary users' activity is deemed as random, the cluster which secures more CCs will anticipate a longer life expectancy.
-It is obvious that fewer secondary in one cluster yield more CCs, but this contradicts to one of the motivations of clustering, \ie the cooperative decision making, where more users result in more accurate sensing result~\cite{Consensus_based_clustering12}.
-
-Note that the purpose of this paper is to introduce a robust cluster structure for CRN, and the robustness here means the ability of the clusters to sustain under the influence of the increasing activity of primary users.
-We focus on the efficient formation of the clusters and the evaluation of the robustness of the formed clusters, 
+In the context of CRN, the activity of primary users is usually unknown to the secondary users, then the primary users' activity is deemed as random.
+In this case, the cluster which secures more CCs will anticipate a longer life expectancy, in other words, is more robust.
+It is obvious that fewer secondary users in one cluster yield more CCs, but this contradicts to one of the motivations of clustering, \ie the cooperative decision making, where more users result in more accurate sensing result~\cite{Consensus_based_clustering12}.
+Thus the number of small clusters, especially the \textit{singleton clusters}, \ie the cluster which has only one CR node, should be minimized.
+As to the cluster which consists of many nodes, although the spectrum sensing is benefited, it usually leads to less common channels, which undermines the robustness of the cluster.
+Thus the cluster robustness discussed in terms of number of CCs carries little meaning when the sizes of formed clusters are not given consideration.
+Cluster size also plays a part in transmission power consumption~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
+In this paper we focus on the efficient formation of the clusters and the evaluation of the robustness of the formed clusters, but our scheme is also able to generate the clusters with the desired size, which gives the network designers more freedom when the power consumption is involved in the design of network applications.
+%In this paper we will introduce a robust cluster structure for CRN, where the robustness means the ability of the clusters to sustain under the influence of the increasing activity of primary users, and the direct metric is the number of CCs in the clusters.
+
+%On the other hand, large clusters are not preferred in some scenarios neither, \eg for the CRN composed with resource limited users, managing the cluster members in a large cluster is a substantial burden.
+%Hence, the cluster size should fall in a desired range according to different application scenarios~\cite{Chen04clusteringalgorithms, capacity_cluster_06}.
+
 %with the intention to provide a robust infrastructure for the applications which may be conducted above that in CRN.
-that being said, when we design this clustering scheme in CRN, we do consider the services to be delivered by the network.
-Cluster sizes affect the power consumption directly in wirelss sensor networks~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
-When the cluster size is not deliberately discussed, it is also decided alongside the optimization of the network, \eg the opimal selection of the aggregation points in a wireless sensor network results in the clusters~\cite{data_aggr_algorithm_04}.
-Our scheme is able to generate the clusters with the desired size, which gives the network designers more freedom when the power consumption is involved in the design of network applications.
-
-%To solely pursue cluster robustness against the primary users' activity, \ie to achieve more common channels within clusters, the ultimately best clustering strategy is ironically that every node constitutes one cluster (called as \textit{singleton cluster} in this paper).
-%%In that case, the common channels within cluster are the available channels available at that node's place.
-%Apparently this contradicts our motivation of proposing cluster in cognitive radio network to enable cooperative decision making.
-%Thus the cluster robustness discussed in terms of number of CCs carries little meaning when the sizes of formed clusters are not given consideration.
+%that being said, when we design this clustering scheme in CRN, we do consider the services to be delivered by the network.
+%Cluster sizes affect the power consumption directly in wirelss sensor networks~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
+%When the cluster size is not deliberately discussed, it is also decided alongside the optimization of the network, \eg the opimal selection of the aggregation points in a wireless sensor network results in the clusters~\cite{data_aggr_algorithm_04}.
 
@@
 Over the control channel, a secondary user $i$ can exchange its spectrum sensing result $K_i$ with all its one hop neighbors $\text{Nb}(i)$.
-In the following, we refer to the licensed channel as channels in general, and will explicitly mention the dedicated control channel if necessary.
+In the following, we refer to the licensed channels as channels in general, and will explicitly mention the dedicated control channel if necessary.
 
@@
 As introduced in Section~\ref{intro}, in order to be robust against primary users' activity, the formed clusters should have more CCs.
-On the other hand, the sizes of the formed clusters should not diverge from the desired size greatly.
-The formation of small clusters or the \textit{singleton clusters}, \ie the cluster which has only one CR node, contradicts the motivation of forming clusters, as the benefits brought in by the collective of the cluster members are compromised.
-On the other hand, large clusters are not preferred in some scenarios neither, \eg for the CRN composed with resource limited users, managing the cluster members in a large cluster is a substantial burden.
-Hence, the cluster size should fall in a desired range according to different application scenarios~\cite{Chen04clusteringalgorithms, capacity_cluster_06}.
-Considering the above mentioned requirements, we present the definition of robust clustering problem as follows.
+On the other hand, the sizes of the formed clusters should be regulated, \ie they don't diverge from a given value greatly.
+%Considering the above mentioned requirements, we present the definition of robust clustering problem as follows.
 

### 2017-03-26 journal-draft/bare_jrnl_comsoc.tex
minor changes
first 5 pages modified

@@
 Thus the cluster robustness discussed in terms of number of CCs carries little meaning when the sizes of formed clusters are not given consideration.
-Cluster size also plays a part in transmission power consumption~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
+Cluster size also plays a part in transmission power consumption, \ie cluster size affects the transmission power consumption when routing is conducted~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
 In this paper we focus on the efficient formation of the clusters and the evaluation of the robustness of the formed clusters, but our scheme is also able to generate the clusters with the desired size, which gives the network designers more freedom when the power consumption is involved in the design of network applications.
@@
 
-There has been a lot of research done on clustering in wireless networks.
+Different clustering strategies have been proposed for wireless networks of different type.
 As there is no restriction on the nodes to access the spectrum in wireless ad-hoc, mesh networks and sensor networks, the objective of clustering is to decrease the transmission power consumption~\cite{Kawadia03}, to improve the routing performance~\cite{clustering_mesh_globecom2010}, or to imrove the network lifetime and coverage~\cite{Abbasi_survey_07}.
@@
 %On the other hand, if $i$ is not in the transmission range of primary user $p$, $i$ can certainly not detect the presence of $p$.
-We assume the primary users change their operation channels slowly thus we omit the time index for the spectrum availability. 
+We assume the primary users change their operation channels slowly, thus we consider the clustering problem at some point in time given some degree of information of the availability of the control channels.
+Due to the same reason, we omit the time index for the spectrum availability. 
 As the result of spectrum sensing, $K_i \subseteq \mathcal{K}$ denotes the set of available licensed channels for CR user $i$.
@@
  $\mathcal{S}$ & the collection of all the possible clusters in $\mathcal{N}$\\
- $C_i$  & the $i$th cluster in $\mathcal{S}$ \\
+ $C_i$  & the $i$-th cluster in $\mathcal{S}$ \\
+ $|C_i|$ & size of the cluster $C_i$\\
+ $|K(C_i)|$ & the number of CCs of cluster $C_i$\\
 \bottomrule
@@
 
-Given a cognitive radio network $\mathcal{N}$ where $|\mathcal{N}|=N$, the collection of all the possible clusters\footnote{Possible cluster means the collection of CR nodes, which complies with the definition in~\ref{sec:model}} is denoted as $\mathcal{S}$ where $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$ \footnote{The subscripts of the clusters can be decided in any convenient way, \ie the sequence of identifying them.} and there is $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$.
-%
-When the requirements on the cluster size are enforced, \ie the desired size is $\delta$ and the cluster sizes should fall in the scope $\langle\delta_1, \delta_2\rangle$, where $\delta, \delta_1, \delta_2\in \mathbb{Z}^+$, $\delta_1 \leq \delta\leq \delta_2$, then a feasible clustering solution is a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, which satisfies
-$\delta_1\leq|C_i|\leq \delta_2, \bigcup_{C_i\in \mathcal{S}'} C_i = \mathcal{N}$ and $C_{i'}\cap C_i =\emptyset$, $C_{i'}, C_i\in \mathcal{S}'$, $i'\neq i$.
-
-The robust clustering problem in CRN is to find the optimal clustering solution from the feasible clustering solutions, whose sum of the numbers of CCs of clusters $\sum_{C\in \mathcal{S}'} f(C)$ is the maximal.
+As to a cognitive radio network, where the set of CR nodes is $\mathcal{N}$.
+Each cluster complies with the definition in~\ref{sec:model}, whose number of CCs in a cluster $C$ is $f(C)$.
+The robust clustering problem is to decide the set of clusters $\mathcal{T}$, where 
+\begin{enumerate}
+\item the sum of the $f(C) is the maximal$, where $C\in \mathcal{T}$ 
+\item the intersection of any two clusters in $\mathcal{T}$ is an empty set
+\item the union of clusters in $\mathcal{T}$ is $\mathcal{N}$
+\item the cluster sizes should fall in the scope $\langle\delta_1, \delta_2\rangle$, where $\delta, \delta_1, \delta_2\in \mathbb{Z}^+$, $\delta_1 \leq \delta\leq \delta_2$, and $\delta$ is decided according to the application to be implemented.
+\end{enumerate}
+
+\end{mydef}
+
+Assume we have obtained the set of $\mathcal{S}$ which contains all the possible clusters in $\mathcal{N}$, \ie $\mathcal{S}=\{C_1, C_2,\ldots,C_i, \ldots, C_{|\mathcal{S}|}\}$ \footnote{The subscript $i$ means the $i$-th cluster in $\mathcal{S}$.} and there is $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = \mathcal{N}$.
+The decision version of this problem is to determine whether there is a non-empty set $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C_i\in \mathcal{S}'} f(C_i) \geqslant \lambda$ where $\lambda$ is a real number.
+We have the following theorem on the complexity of this problem.
+
+\begin{theorem}
+\label{theorem1}
+The robust clustering problem in CRN is NP-hard, when the maximum size of clusters is larger than 3, $\delta_1=1$ and $\delta_2 = N$.
+%Assume a CRN can be represented by a connected graph, and there is at least one common channel between any pair of neighbours, then forming at least two CR nodes into one cluster is NP-complete.
+\end{theorem}
+The proof is in Appendix~\ref{proof_theorem1}.
 
@@
 
-\end{mydef}
-
 %The decision version of \textit{weighted exact cover problem}: 
@@
 \label{centralized_solution}
-
-Based on Definition~\ref{def_centralized_clustering}, the decision version of this problem is to determine whether there is a non-empty $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C\in \mathcal{S}'} f(C) \geqslant \lambda$ where $\lambda$ is a real number.
-We have the following theorem on the complexity of this problem.
-
-\begin{theorem}
-\label{theorem1}
-Robust clustering problem in CRN is NP-hard, when the maximum size of clusters is larger than 3, $\delta_1=1$ and $\delta_2 = N$.
-%Assume a CRN can be represented by a connected graph, and there is at least one common channel between any pair of neighbours, then forming at least two CR nodes into one cluster is NP-complete.
-\end{theorem}
-The proof is in Appendix~\ref{proof_theorem1}.
-
-We propose a centralized solution for the robust clustering problem, which solves an optimization with standard solvers. 
-To formulate the optimization, we need to do some preparation beforehand.
-First, all the possible clusters complying with the description in the system model are found and constitute a set $\mathcal{S}$.
-Second, we assign a cluster size related weight to each cluster, which is positively correlated with the difference between the cluster size and the desired cluster size. 
-Considering $|\mathcal{S}|=M$, $C_i\in \mathcal{S}$ means the $i$ th cluster in $\mathcal{S}$, and $\delta$ is the desired size, the size related weight for each cluster is given as follows,
-$$
-p_i(C_i) = \left\{ \begin{array}{rl}
-0 &\mbox{ if $|C_i|=\delta$} \\
-\rho_1 &\mbox{if $||C_i|-1|=\delta$} \\
-\rho_2 &\mbox{if $||C_i|-2|=\delta$} \\
-\vdots
-\end{array} \right.
-$$
-where $\rho_1, \rho_2, \cdots$ are positive values.
-In particular, $\rho$ increases with the divergence between $|C_i|$ and $\delta$, \ie these is $\rho_2> \rho_1>0$.
-
-The optimization searches the set $\mathcal{S}$ and decides on certain clusters which constitute the whole CRN without overlapping between any two of them, besides, the sum of CCs of the chosen clusters is maximized.
-Then, a central node (or controller) with the knowledge of all CR nodes (and also the possible clusters) can solve the problem based on the following formulation.
+When the global knowledge of the CRN is available to us, we can propose a centralized scheme as comparison.
+The proposed centralized solution formulates the problem in Definition~\ref{def_centralized_clustering} as an optimization problem, then the latter is solved with standard software packages.
+The optimization searches the set $\mathcal{S}$ and decides on the clusters according to the following optimization formulation,
+%
+%which constitute the whole CRN without overlapping between any two of them, besides, the sum of CCs of the chosen clusters is maximized.
+%Then, a central node (or controller) with the knowledge of all CR nodes (and also the possible clusters) can solve the problem based on the following formulation. 
+%
+%Second, we assign a cluster size related weight to each cluster, which is positively correlated with the difference between the cluster size and the desired cluster size.
 
@@
 \end{equation}
+This problem is a binary linear programming problem, which can be solved by many available solvers.
+$w_i$ and $x_{ij}$ are two binary variables.
+% where $j\in \{1,2,\cdots,N-1, N\}$ and $i\in \{1,2,\cdots,M-1, M\}$.
+%$G = |\mathcal{G}|$ and there is $\mathcal{G} \subseteq \mathcal{S}$.
+Being either 1 or 0, $w_i$ denotes whether the $i$-th cluster $C_i$ in $\mathcal{S}$ is chosen or not.
+$x_{ij}$ indicates whether the CR node $j$ resides in the cluster $C_i$, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$. 
+%Node index $j$ is identical to the node ID.
+$N$ is the total number of CR users in network $\mathcal{N}$, $M$ is the number of possible clusters in $\mathcal{S}$.
+
+The constraints guarantee to obtain the clusters which together include all the CR users and don't overlap.
+The first constraint regulates that a CR node should reside in exactly one cluster.
+The second constraint regulates that when the $i$-th cluster $C_i$ is chosen, there will be exactly $|C_i|$ CR nodes residing in $C_i$.
 
 %The optimization is a binary linear programming problem.
-The objective is to maximize the sum of CCs of all the clusters.
-%We minimize the opposite of the real objective to make this problem solvable.
-$w_i$ and $x_{ij}$ are the two binary variables in this problem.
-% where $j\in \{1,2,\cdots,N-1, N\}$ and $i\in \{1,2,\cdots,M-1, M\}$.
-$N$ is the total number of CR users in network $\mathcal{N}$, $M$ is the number of possible clusters in $\mathcal{S}$.
-%$G = |\mathcal{G}|$ and there is $\mathcal{G} \subseteq \mathcal{S}$.
-Being either 1 or 0, $w_i$ denotes whether the $i$th cluster $C_i$ in $\mathcal{S}$ is chosen by the solution or not.
-$x_{ij}$ indicates whether the CR node $j$ resides in the $i$th potential cluster, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$. 
-Node index $j$ is identical to the node ID.
+The objective is to maximize the sum of the numbers of CCs in the clusters which constitute the whole CRN.
+$t_{ij}$ is a constant and there is,
 %In practice, we can solve the problem with $\mathcal{G} = \mathcal{S}$ when $|\mathcal{S}|$ is not large. 
@@
 %By permitting the existence of the singleton clusters, we can ensure that the $\mathcal{S}'$ in Definition~\ref{def_centralized_clustering} is always be feasible.
-$t_{ij}$ is a constant which is $\frac{q_{ij}}{|C_i|} - p_i(C_i)$.
-$q_{ij}= |K(C_i)|$ when there is $j\in C_i$, and $q_{ij}= 0$ when there is $j\notin C_i$.
-$|K(C_i)|$ is the number of CCs of cluster $C_i$, and $|C_i|$ is the size of cluster $C_i$.
-$p_i(C_i)$ is the size related weight which has been introduced.
+
+\begin{equation}
+t_{ij} = \frac{q_{ij}}{|C_i|} - p_i(C_i)
+\end{equation}
+where $q_{ij}= |K(C_i)|$ when node $j\in C_i$, and $q_{ij}= 0$ when node $j\notin C_i$.
+%$|K(C_i)|$ is the number of CCs of cluster $C_i$, and $|C_i|$ is the size of cluster $C_i$.
+$p_i(C_i)$ is the size-related weight, which reflects the deviation between the size of $C_i$ and the desired size.
+Assuming $\delta$ is the desired size, then
+$$
+p_i(C_i) = \left\{ \begin{array}{rl}
+0 &\mbox{ if $|C_i|=\delta$} \\
+\rho_1 &\mbox{if $||C_i|-1|=\delta$} \\
+\rho_2 &\mbox{if $||C_i|-2|=\delta$} \\
+\vdots
+\end{array} \right.
+$$
+where $\rho_1, \rho_2, \cdots$ are positive values and these is $\rho_2> \rho_1>0$.
+
 %%Based on the knowledge on $\mathcal{S}$, we construct a $M\times N$ matrix $Q_{M\text{x}N}$ which is shown in Figure~\ref{costant_matrix_Q}. 
@@
 As to the second item, when $w_i$ is 1 ($C_i$ is chosen) and $|C_i|\neq\delta$, it will be negative, which contradicts the direction of the optimization.
-Thus the second item discourages the appearance the clusters whose sizes are different from $\delta$, especially those whose sizes are not $\delta$.
+Thus the second item discourages the appearance the clusters whose sizes deviate from $\delta$.
 
@@
 
-The constraints guarantee to obtain the clusters which together include all the CR users and don't overlap.
-The first constraint regulates that each CR node should reside in exactly one cluster.
-The second constraint regulates that when the $i$th possible cluster $C_i$ is chosen, there will be exactly $|C_i|$ CR nodes residing in $C_i$.
-
 %\begin{figure}[ht!]
@@
 
-This problem is a binary linear programming problem, which can be solved by many available solvers.
 The difficulty of using this method lies in obtaining the set $\mathcal{S}$.
-In the worst case, \ie the CRN forms a full connected graph, the size of $S$ is $\Sigma_{r=1}^{N}\ {N \choose r} = 2^N-1$.
-To levitate this problem, a smaller set, \ie $\mathcal{G} \subset \mathcal{S}$ can be used.
-In this case, the global optimal may not be found.
-$\mathcal{G}$ can be prepared based on the cluster size, and it is recommended to include all the singleton clusters to make sure the availability of feasible solutions.
-
-Another obstacle to apply this centralized scheme is, the centralized entity firstly needs to collect the information from all the CR nodes, then computes the clustering solution and distributes it across the whole network.
-This process involves a large number of communication overheads.
+In the worst case, \ie the CRN forms a full connected graph, the size of $\mathcal{S}$ is $\Sigma_{r=1}^{N}\ {N \choose r} = 2^N-1$.
+%To levitate this problem, a smaller set, \ie $\mathcal{G} \subset \mathcal{S}$ can be used.
+%In this case, the global optimal may not be found.
+%$\mathcal{G}$ can be prepared based on the cluster size, and it is recommended to include all the singleton clusters to make sure the availability of feasible solutions.
+
+Another obstacle to apply this centralized scheme comes from the characteristics of CRN.
+In order to apply this scheme in practice, a large over head needs to be factored in in collecting the channel usage as seen by the R nodes, as well as the connectivity between the CR nodes.
+After computing the clustering solution, the centralized node needs to distribute it across the whole network.
+
 In CRN, it is necessary to do clustering again on some occasions.
@@
 \label{phaseI}
-We assume that before conducting clustering, spectrum sensing, neighbor discovery and exchange of spectrum availability have been completed, so that every CR node is aware of the available channels on themselves and their neighbors.
+We assume that before conducting clustering, spectrum sensing, neighbor discovery and exchange of spectrum availability have been completed, so that every CR node is aware of the available channels for themselves and their neighbors.
 In this phase, cluster heads are determined after a series of comparisons with their neighbors. 
@@
 \item \textit{Individual connectivity degree} $d_i$: $d_i=\sum_{j\in \text{Nb}(i)}\vert K_i\cap K_j\vert$. 
-$d_i$ is the total number of the CCs between node $i$ and every its neighbor.
-It is an indicator of node $i$'s adhesion to the CRN.
-
-\item \textit{Neighborhood connectivity degree} $g_i$: $g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$. 
-It is the number of CCs which are available for $i$ and all its neighbors.
-$g_i$ represents the ability of $i$ to form a robust cluster with its neighbors.
+$d_i$ is the total number of the CCs between node $i$ and each of its neighbors.
+%It is an indicator of node $i$'s adhesion to the CRN.
+
+\item \textit{Neighborhood connectivity degree} $g_i$: the number of CCs which are available for $i$ and all its neighbors.
+$g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$, which represents the ability of $i$ to form a robust cluster with its neighbors.
 \end{itemize}
@@
 The node which is identified as a cluster head broadcasts a message to notify its neighbors of this change, and its neighbors which are not cluster heads become cluster members
-\footnote{The reasons for the occurrence of the cluster heads in the neighborhood of a new cluster head will be explained in Section~\ref{ross_p1_guarantee_ccc} and \ref{ross_p2_cluster_pruning})}.
+\footnote{The reason for the occurrence of the cluster heads in the neighborhood of a new cluster head will be explained in Section~\ref{ross_p1_guarantee_ccc} and \ref{ross_p2_cluster_pruning})}.
 The pseudo code for the cluster head decision and the initial cluster formation is shown in Algorithm~\ref{alg0} in the appendix.
@@
 %, which enables the nodes which are outside of the cluster can possibly become cluster heads or can also be included into other clusters.
-We have the following theorem to show that when the secondary users' individual connectivity degrees are greater than zero, every secondary user will eventually be either integrated into a certain cluster, or becomes a cluster head.
+We have the following theorem to show that when there is no one secondary which shares no CC with any other secondary users, \ie
+all secondary users' individual connectivity degrees are greater than zero, then every secondary user will eventually be either integrated into a certain cluster, or becomes a cluster head.
 \begin{theorem}
@@
 %
-If one step can be finished within certain time $T$, then the total time needed for the network to conduct Algorithm~\ref{clustering:theorem} is $N*T$.
-In other scenarios, as Algorithm~\ref{alg0} can be executed concurrently by secondary users which locate in different places, the needed time can be considerably reduced.
+If one step can be finished within a certain time span $T$, then the total time needed for the network to conduct Algorithm~\ref{clustering:theorem} is $N*T$.
+Actually as Algorithm~\ref{alg0} can be executed concurrently by different secondary users, the needed time can be considerably reduced.
 %According to Theorem~\ref{clustering:theorem}, Phase I completes within a reasonable amount of time.
@@
 %This judgement is conducted periodically, and phase I ends after every node ascertains it is cluster head or not.
-Let us apply Algorithm~\ref{alg0} to the example shown in Figure~\ref{fig1}.
+If we apply Algorithm~\ref{alg0} to the example shown in Figure~\ref{fig1}, then the outcome is shown in Figure~\ref{fig2}.
 Node $B$ and $H$ have the same individual connectivity degree, i.e., $d_B=d_H$. As $g_H=2>g_B=1$, node $H$ becomes the cluster head and cluster $C(H)$ is $\{H, B, A, G\}$.
 
-\subsubsection{Guarantee the Existence of Common Channels}
+\subsubsection{The Existence of Common Channels}
 \label{ross_p1_guarantee_ccc}
@@
 If this criterion meets a tie, the tie will be broken by deleting the node with smaller node ID.
-It is possible that the cluster head excludes all its neighbors and resulting in a singleton cluster which is composed by itself.
+It is possible that the cluster head excludes all its neighbors, resulting in a singleton cluster which is composed by itself.
 %At the end of this procedure every formed cluster has at least one common channel.
@@
 
-During Phase I, whenever ever a CR node is decided to be a cluster head and accordingly forms a cluster, or its cluster's composition is changed, the cluster head will broadcast the updated information about its cluster, which includes the sets of available channels on all its cluster members.
+During Phase I, whenever a CR node is decided to be a cluster head and accordingly forms a cluster, or its cluster's composition is changed, the cluster head will broadcast the updated information about its cluster, which includes the sets of available channels on all its cluster members.
 
@@
 %Debatable node $i$ is aware of all its claiming clusters in $S_i$. 
-Assume a debatable node $i$ needs to decide one cluster $C\in S_i$ to stay, and thereafter leaves the rest others in $S_i$.
-In this process, the principle for $i$ is that its move should result in the greatest increase of CCs in all its claiming clusters.
-%The set of available channels of one cluster are known by the debatable nodes which locate in that cluster. %this is finished 
-Note that node $i$ has been notified of the spectrum availability on all the cluster members of each claiming cluster, thus node $i$ is able to calculate how many more CCs can be produced in one claiming cluster if $i$ leaves that cluster.
+Assuming a debatable node $i$ which needs to decide one cluster $C\in S_i$ to stay and leaves the other clusters in $S_i$, then the principle for $i$ is its decision should result in the greatest increase of CCs in all its claiming clusters.
+As node $i$ has been notified of the spectrum availability on all the nodes in each claiming cluster, node $i$ is able to calculate how many more CCs will be produced in a claiming cluster if $i$ leaves that cluster.
 %Based on this calculation, $i$ decides on one claiming cluster to stay and leaves the other claiming clusters.
-If there exists one cluster $C\in S_i$, when $i$ leaves this cluster brings less increased CCs than leaving any other claiming clusters, then $i$ chooses to stay in cluster $C$.
-When there comes a tie, among the claiming clusters, $i$ chooses to stay in the cluster whose cluster head shares the most CCs with $i$.
-In case there are multiple claiming clusters demonstrating the same on the aforementioned metric, node $i$ chooses to stay in the claiming cluster which has the smallest size.
+Then node $i$ decides on the cluster $C\in S_i$, if $i$ leaving cluster $C$ results in less increased CCs than leaving any other claiming clusters in $S_i$.
+%As to a cluster $C\in S_i$, if $i$ leaves cluster $C$ and results in less increased CCs than leaving any other claiming clusters, then $i$ chooses to stay in cluster $C$.
+When there comes a tie between two claiming clusters, $i$ chooses to stay in the cluster whose cluster head shares the most CCs with $i$.
+When the tie still exists, node $i$ chooses to stay in the claiming cluster which has the smallest size.
 Node IDs of cluster heads will be used to break tie if all the previous metrics could not decide on the unique claiming cluster for $i$ to stay.
-The pseudo code of this algorithm is given as Algorithm~\ref{alg4}.
+The pseudo code of this algorithm is given in Algorithm~\ref{alg4}.
 %To conduct Algorithm~\ref{alg4}, debatable node $i$ needs to know the necessary information about its claiming clusters, \ie $K(C)$ (the set of available channels in cluster $C$), $K(h_C)$ (the set of available channels on $C$'s cluster head $h_C$) and $|C|, C\in S_i$ (sizes of $i$'s claiming clusters).
@@
 \appendices
-%\section{Algorithm~\ref{alg0}}
-\section*{}
+\section{Peudo Code for the Algorithm~\ref{alg0}, \ref{alg_size_control_available_CCC} and~\ref{alg4}}
 \begin{algorithm}              % enter the algorithm environment
@@
 %\section*{Algorithm~\ref{alg_size_control_available_CCC}}
-\section*{}
+%\section{}
 \begin{algorithm}               % enter the algorithm environment
@@
 
-\section*{}
+%\section{}
 \begin{algorithm}               % enter the algorithm environment
@@
 
-\section*{Proof of Theorem~\ref{clustering:theorem}}
+\section{Proof of Theorem~\ref{clustering:theorem}}
+\begin{proof}
 \label{proof_clustering:theorem}
-\begin{proof}
 %Note that the formed cluster can be a singleton cluster, \ie cluster size is 1.
@@
 %
-\section*{Proof of Theorem~\ref{theorem1}}
+\section{Proof of Theorem~\ref{theorem1}}
 \label{proof_theorem1}

### 2017-03-26 journal-draft/bare_jrnl_comsoc.tex
first 7 papges

@@
 In the past few years, game theory has been extensively applied to problems in communication and networking~\cite{Neel06analysisand, Wang_gtc_crn_survey_2010}.
-Congestion game is an attractive game model which describes the problem where participants compete for limited resources in a non-cooperative manner, it has good property that Nash equilibrium can be achieved after finite steps of best response dynamic, \ie each player choose strategy to maximizes/minimizes its utility/cost with respect to the other players' strategies.
-Congestion game has been used to model certain problems in internet-centric applications or cloud computing, where self-interested clients compete for the centralized resources and meanwhile interact with each other.
+Congestion game is an attractive game model which describes the problem where participants compete for limited resources in a non-cooperative manner, it has the good property that Nash equilibrium can be achieved after finite steps of best response dynamic, \ie each player chooses the strategy to maximize/minimize its utility/cost with respect to the other players' strategies.
+The framework of the congestion game has been used to model certain problems in internet-centric applications or cloud computing, where self-interested clients compete for the centralized resources and meanwhile interact with each other.
 For example, server selection is involved in distributed computing platforms~\cite{Cloud_Computing_2010}, or users downloading files from cloud, etc.
 
-To formulate the debatable nodes' membership clarification into the desired congestion game, we observe this process from a different (or opposite) perspective. 
-From the new perspective, the debatable nodes are regarded as isolated and don't belong to any cluster, in other words, their claiming clusters become clusters which are beside them. 
-Now for the debatable nodes, the previous problem of deciding which clusters to leave becomes a new problem that which cluster to join.
-In the new problem, debatable node $i$ chooses one cluster $C$ out of $S_i$ to join if the decrease of CCs in cluster $C$ is the smallest in $S_i$, and the decrease of CCs in cluster $C$ is $\sum_{C\in S_i}\Delta\vert K(C) \vert=\sum_{C\in S_i}({\vert K(C) \vert-\vert K(C\cup i) \vert})$.
+To formulate the debatable nodes' membership clarification into the desired congestion game, we reexamine this process from a different (or opposite) perspective. 
+From the new perspective, the debatable nodes are not included in any cluster, and they are looking for the proper cluster to join.
+% in other words, their claiming clusters become clusters which are beside them. 
+%Now for the debatable nodes, the previous problem of deciding which clusters to leave becomes a new problem that which cluster to join.
+A debatable node $i$ chooses one cluster $C$ out of $S_i$ to join if the decrease of CCs in cluster $C$ is the smaller than any other cluster in $S_i$.
+The decrease of CCs in cluster $C$ is $\sum_{C\in S_i}\Delta\vert K(C) \vert=\sum_{C\in S_i}({\vert K(C) \vert-\vert K(C\cup i) \vert})$.
 The interaction between the debatable nodes and the claiming clusters is shown in Figure~\ref{debatable_nodes_claiming_cluster}.
@@
 In the following, we show that the decision of debatable nodes to clarify their membership can be mapped to the behaviour of the players in a \textit{player-specific singleton congestion game} when proper cost function is given.
-The game to be constructed is represented with a 4-tuple $\Gamma=(\mathcal{P},\mathcal{R},\sum_{i, i \in \mathcal{P}}, f)$, and the elements in $\Gamma$ are explained below,
+The game to be constructed is represented with a 4-tuple $\Gamma=(\mathcal{P},\mathcal{R},\sum_{i, i \in \mathcal{P}}, f)$ with the following elements:
 %To make the model of this game more clear, we make some change to our original problem.
@@
 With ROSS-DFA, debatable nodes decide their respective cluster heads only once.
-The debatable nodes consider their claiming clusters to include all their debatable nodes, thus the membership of claiming clusters is static and all the debatable nodes can make decision simultaneously without considering the change of membership of their claiming clusters.
+The debatable nodes consider their claiming clusters to include all their debatable nodes, thus the membership of claiming clusters is static and all the debatable nodes can make decisions simultaneously without considering the change of membership of their claiming clusters.
 As ROSS-DFA is quicker than ROSS-DGA, the former is especially suitable for the CRN where the channel availability changes dynamically and re-clustering is necessary.
-To run ROSS-DFA, debatable node executes only one loop in Algorithm~\ref{alg4}.
+To run ROSS-DFA, debatable nodes execute only one loop in Algorithm~\ref{alg4}.
 
@@
 The two possible strategies of node $A$ is illustrated in Figure \ref{fig3}.
-In Figure \ref{AinC}, node $A$ staying in $C(C)$ and leaving $C(H)$ brings 2 more CCs to $S_A$, which is more than that brought by another strategy showed in \ref{AinH}.
+In Figure \ref{AinC}, node $A$ staying in $C(C)$ and leaving $C(H)$ brings 2 more CCs to $S_A$, which is more than that brought by another strategy shown in \ref{AinH}.
 After the decisions made similarly by the other debatable nodes $B$ and $D$, the final clusters are formed as shown in Figure~\ref{final_clustering_ross}.
@@
 \item Centralized robust clustering scheme. 
-The formulated optimization is an integer linear optimization problem, which is solved by MATLAB with the function $bintprog$.
+As shown in Section~\ref{centralized_solution}, the centralized robust clustering scheme is formulated as an integer linear optimization problem and is solved by MATLAB with the function $bintprog$.
 \end{itemize}
@@
 Thus SOC is the only distributed scheme as comparison.
-As to the CRN shown in Figure~\ref{fig1}, the resulted clusters by the centralized scheme and SOC are shown in Figure~\ref{fig:final_clustering}.
+As to the CRN shown in Figure~\ref{fig1}, the resulting clusters by the centralized scheme and SOC are shown in Figure~\ref{fig:final_clustering}.
 
@@
 
-We investigate the schemes with four metrics.
+We investigate the schemes with respect to four metrics.
 
@@
 We see two flaws in this claim.
-First, the unclustered CR nodes (synonym of singleton clusters) should not be considered when obtaining the average number of CCs, as singleton clusters doesn't contribute to the collaborative computing.
-Second, the average number of CCs doesn't necessarily indicate the robustness of individual clusters, because the ability for a cluster to sustain also depends on the cluster size and the locations of the cluster members, and these information is not illustrated in the average number of CCs.
-In the performance evaluation, We will examine the metric of average number of CCs per non-singleton cluster, which excludes the bias brought in by the unclustered CR nodes.
+First, the unclustered CR nodes (synonym of singleton clusters) should not be considered when obtaining the average number of CCs, as singleton clusters don't contribute to the collaborative computing.
+Second, the average number of CCs doesn't necessarily indicate the robustness of individual clusters, because the ability for a cluster to sustain also depends on the cluster size and the locations of the cluster members, and this information is not illustrated in the average number of CCs.
+In the performance evaluation, we will examine the metric of average number of CCs per non-singleton cluster, which excludes the bias brought in by the unclustered CR nodes.
 More importantly, we will examine whether this metric reflects the robustness of the clusters against increasingly active primary users.
@@
 In the second part, we investigate the performance of the proposed distributed schemes in the CRN with different scales and densities.
-The following simulation settings is the same for both simulation parts.
+The following simulation setting is the same for both simulation parts.
 CRs and PUs are deployed on a two-dimensional Euclidean plane.
@@
 The desired cluster size $\delta$ is 3.
-The constant for size control is 1.3.
-As to the centralized scheme, the parameters used in the \textit{punishment} for choosing the clusters with undesired sizes are set as follows, $\rho_1 =  0.4$, $\rho_2 =  0.6$.
+The constant $t$ (discussed in Section~\ref{ross_p2_cluster_pruning}) for size control is 1.3.
+As for the centralized scheme, the parameters used in the \textit{punishment} for choosing the clusters with undesired sizes are set as follows, $\rho_1 =  0.4$, $\rho_2 =  0.6$.
 
@@
 %We have discussed the flaw of this metric as it doesn't convey the number of unclustered CR nodes, in fact, 
-In the other hand, SOC generates the most unclustered CRs.
+On the other hand, SOC generates the most unclustered CRs.
 As to the variants of ROSS, we notice that the greedy mechanism increases CCs in non-singleton clusters significantly.
@@
 
-The comparison scheme SOC involves three rounds of execution. 
+The comparison scheme SOC consists of three rounds of execution. 
 In the first two rounds, every CR node maintains its own cluster and seeks either to integrate neighboring clusters or to join one neighboring cluster.

### 2017-04-01 journal-draft/bare_jrnl_comsoc.tex
abstract and the first part of the simulation

@@
 Cluster structure in cognitive radio networks facilitates cooperative spectrum sensing, routing and other functionalities.
-The unlicensed channels, which are available for every member of a group of cognitive radio users, consolidate the group into a cluster, and the availability of unlicensed channels decides the robustness of that cluster against the licensed users' influence.
-%Thus there should be more unlicensed channels in the clusters.
-This paper analyses the problem that how to form robust clusters in cognitive radio network, so that more cognitive radio users can get benefits from cluster structure even when the primary users' operation are intense.
+The unlicensed channels which are available for a group of cognitive radio users, consolidate the group into a cluster and the number of the available unlicensed channels decides that cluster's robustness against the licensed users' influence.
+This paper analyses the problem of how to form robust clusters in cognitive radio network, so that more cognitive radio users can get the benefits from cluster structure when the primary users' operation becomes more intense.
 %In the process of forming clusters, every secondary user decides with whom to form a cluster, or which cluster to join.
-We provide a formal description of robust clustering problem, prove it to be NP-hard and propose a centralized solution, besides, a distributed solution is proposed to suit the dynamics in the ad hoc cognitive radio network.
-Congestion game model is adopted to analyse the process of cluster formation, which not only contributes designing the distributed clustering scheme directly, but also provides the guarantee of convergence into Nash Equilibrium and convergence speed.
-Our proposed clustering solution is versatile to fulfill some other requirements such as faster convergence and cluster size control.
-The proposed distributed clustering scheme outperforms the related work in terms of cluster robustness, convergence speed and overhead.
+We give a formal description of the robust clustering problem, prove it to be NP-hard and propose both centralized and distributed solutions.
+The congestion game model is adopted to analyse the process of cluster formation, which not only contributes the design of the distributed clustering scheme, but also provides the guarantee on the convergence into Nash Equilibrium and the convergence speed.
+%Our proposed clustering solution is versatile to fulfill some other requirements such as faster convergence and cluster size control.
+The proposed distributed clustering scheme outperforms the related works in terms of cluster robustness, convergence speed and overhead.
 %Besides, we prove the clustering problem is NP-hard, and also propose the centralized solution.
-The extensive simulation supports our claims.
+The extensive simulation is conducted, which clearly supports our claims.
 \end{abstract}
@@
 The number of licensed channels is 10, each PU is operating on each channel with probability of 50\%.
+The constant $t$ which is used to control cluster size for ROSS (discussed in Section~\ref{ross_p2_cluster_pruning}) is 1.3.
 CR users are assumed to be able to sense the existence of primary users and identify available channels.
@@
 The desired cluster size $\delta$ is 3.
-The constant $t$ (discussed in Section~\ref{ross_p2_cluster_pruning}) for size control is 1.3.
 As for the centralized scheme, the parameters used in the \textit{punishment} for choosing the clusters with undesired sizes are set as follows, $\rho_1 =  0.4$, $\rho_2 =  0.6$.
@@
 The desired sizes adopted are listed in the Table~\ref{Simulation_para}, which is about 60\% of the average number of neighbours.
-When run ROSS, the parameter $t$ which is used to control cluster size in phase I is 1.3.
+%When run ROSS, the parameter $t$ which is used to control cluster size in phase I is 1.3.
 
@@
 \label{conclusion}
-In this paper we investigate the robust clustering problem in CRN extensively.
+In this paper we investigate the robust clustering problem in CRN extensively and propose an efficient distributed clustering solution.
 %generate robust clusters against primary users' influence, so that more CR users can benefit from operative decision making provided by the clusters.

### 2017-04-01 journal-draft/bare_jrnl_comsoc.tex
message compelxity

@@
  $|K(C_i)|$ & the number of CCs of cluster $C_i$\\
+ $n$ & the number of debatable nodes\\
+ $m$ & the number of claiming cluster heads\\
 \bottomrule
@@
 
-In fact, the number of steps which are actually involved in this process is much smaller than $N^3$, as both $n$ and $m$ are considerably smaller than $N$.
-The percentage of debatable nodes in $\mathcal{N}$ is illustrated in Figure~\ref{percentage_overlapping_node}, which is between 10\% to 60\% of the total number of CR nodes in the network.
-The number of clusters heads, as mentioned in Section~\ref{phaseI}, is dependent on the network density and the CR node's transmission range.
+In fact, the upper bound of the number of steps which are actually involved in this process is much smaller than $N^3$.%, as both $n$ and $m$ are considerably smaller than $N$.
+The percentage of debatable nodes in the network is illustrated in Figure~\ref{percentage_overlapping_node}, which is between 10\% to 60\% of the total number of CR nodes in the network.
+In the other hand, the number of clusters heads is dependent on the network density and the CR node's transmission range as mentioned in Section~\ref{phaseI}.
 The simulation in \cite{robust_clustering_arxiv} shows that the cluster heads are only 3.4\% to 20\% of the total CR nodes.
@@
 \subsubsection{Control Signaling Overhead}
-%Different from the clustering schemes proposed in ~\cite{LIU_TMC11_2, clustering_globecom11}, 
-%There are two phases for any variants of ROSS.
-%Clusters are formed in the first phase, in the second phase, cluster membership is decided so that each node only resides in one cluster.
-%Control message exchanges between CR nodes are involved in both phases.
 
 In this section we compare the overhead of signaling involved in different clustering schemes.
-%In order to highlight the amount of control signalling only for clustering, 
-We don't consider the the control messages which are involved in neighborhood discovery, which is the premise and deemed to be the same for all clustering schemes.
-According to~\cite{complexity_aggregation_2011}, the message complexity is defined as the number of messages used by all nodes.
-To have the same metric to compare, we count \textit{the number of transmissions of control messages}, without distinguishing broadcast or uni-cast control messages.
-This metric is synonymous with \textit{the number of updates} discussed in Section~\ref{ross}.
-
-As to ROSS, the control messages are generated in both phases.
-In the first phase, when a CR node decides itself to be the cluster head, it broadcasts a message containing its ID, cluster members and the set of CCs in its cluster.
-In the second phase, a debatable node broadcasts its affiliation to inform its claiming clusters, then the cluster heads of the claiming clusters broadcast message about the new cluster members if they are changed due to the debatable node's decision.
-The upper bound of the total number of the control messages involved in cluster formation is analyzed in Theorem~\ref{clustering:theorem} and Section~\ref{clustering:phaseII:game}.
-
-The comparison scheme SOC consists of three rounds of execution. 
-In the first two rounds, every CR node maintains its own cluster and seeks either to integrate neighboring clusters or to join one neighboring cluster.
-The final clusters are obtained in the third round. 
-In each round, every CR node is involved in comparisons and cluster mergers.
-%Comparing with the second phase of ROSS, only debatable nodes to communicate with cluster heads to clarify their membership.
-%The signalling overhead for centralized scheme comes from two processes, the the process of collecting information to the centralized controller, and the process that the controller spreads the clustering result to all the CR nodes.
-
-The centralized scheme is conducted at the centralized control device, but it involves two phases of control message transmission.
-The first phase is information aggregation, in which every CR node's channel availability and neighborhood is transmitted to the centralized controller.
-iIn the second phase, the control broadcasts the clustering solution, which is disseminated to every CR node.
-%
-We adopt the algorithm proposed in~\cite{Efficient_broadcasting_gathering_adhoc} to broadcast and gather information as the algorithm is simple and self-stabilizing.
-This scheme needs building a backbone structure to support the communication. 
-We apply ROSS to generate cluster heads which serve as the backbone, and the debatable nodes are used as the gateway nodes between the backbone nodes.
-As the backbone is built for one time and supports the transmission of control messages later on, we don't take account the messages involved in building the backbone.
-As to the process of information gathering, we assume that every cluster member sends the spectrum availability and its ID to its cluster head, which further forwards the message to the controller, then the number of transmissions is $N$.
-As to the process of dissemination, in an extreme situation where all the gateway and the backbone nodes broadcast, the number of transmissions is $h + m$, where $h$ is the number of cluster heads and $m$ is number of debatable nodes.
-%, $d$ is the average number of demanding clusters for each debatable node.
+We count the number of \textit{transmissions of control messages} as message complexity~\cite{complexity_aggregation_2011}, and without distinguishing broadcast or uni-cast control messages.
+In Section~\ref{ross}, this metric is synonymous with the \textit{the number of updates}.
+%We don't consider the the control messages which are involved in neighborhood discovery, which is the premise and deemed to be the same for all clustering schemes.
+%According to~\cite{complexity_aggregation_2011}, the message complexity is defined as the number of messages used by all nodes.
+%To have the same metric to compare,
+
+As to ROSS, in the first phase the maximal number of broadcast is $N$ according to~\ref{clustering:theorem}.
+The upper bounds of the transmissions are $n^2m$ and $n$ for ROSS-DGA and ROSS-DFA respectively.
+Scheme SOC consists of three rounds and in each round every node needs to broadcast in order to do comparisons and cluster mergers.
+The centralized scheme is conducted at the centralized control device, and it involves information aggregation and clustering decision dissemination.
+We adopt the backbone structure proposed in~\cite{Efficient_broadcasting_gathering_adhoc} to analyze the centralized scheme's message complexity.
+We apply ROSS to generate cluster heads which serve as the backbone.
+In the process of information aggregation, all the nodes transmit information to the cluster heads which forward the messages to the controller, then in the process of dissemination, all the cluster heads and the debatable nodes broadcast the clustering result, thus the upper bound of the number of broadcast is $N+m+n$.
+
+%
+%, when a CR node decides itself to be the cluster head, it broadcasts a message containing its ID, cluster members and the set of CCs in its cluster.
+%In the second phase, a debatable node broadcasts its affiliation to inform its claiming clusters, then the cluster heads of the claiming clusters broadcast message about the new cluster members if they are changed due to the debatable node's decision.
+%The upper bound of the total number of the control messages involved in cluster formation is analyzed in Theorem~\ref{clustering:theorem} and Section~\ref{clustering:phaseII:game}.
+%
+%The comparison scheme SOC consists of three rounds of execution. 
+%In the first two rounds, every CR node maintains its own cluster and seeks either to integrate neighboring clusters or to join one neighboring cluster.
+%The final clusters are obtained in the third round. 
+%In each round, every CR node is involved in comparisons and cluster mergers.
+%%Comparing with the second phase of ROSS, only debatable nodes to communicate with cluster heads to clarify their membership.
+%%The signalling overhead for centralized scheme comes from two processes, the the process of collecting information to the centralized controller, and the process that the controller spreads the clustering result to all the CR nodes.
+%
+%The centralized scheme is conducted at the centralized control device, but it involves two phases of control message transmission.
+%The first phase is information aggregation, in which every CR node's channel availability and neighborhood is transmitted to the centralized controller.
+%iIn the second phase, the control broadcasts the clustering solution, which is disseminated to every CR node.
+%%
+%We adopt the algorithm proposed in~\cite{Efficient_broadcasting_gathering_adhoc} to broadcast and gather information as the algorithm is simple and self-stabilizing.
+%This scheme needs building a backbone structure to support the communication. 
+%We apply ROSS to generate cluster heads which serve as the backbone, and the debatable nodes are used as the gateway nodes between the backbone nodes.
+%As the backbone is built for one time and supports the transmission of control messages later on, we don't take account the messages involved in building the backbone.
+%As to the process of information gathering, we assume that every cluster member sends the spectrum availability and its ID to its cluster head, which further forwards the message to the controller, then the number of transmissions is $N$.
+%As to the process of dissemination, in an extreme situation where all the gateway and the backbone nodes broadcast, the number of transmissions is $m + n$, where $m$ is the number of cluster heads and $n$ is number of debatable nodes.
 
 The number of control messages which are involved in ROSS variants and the centralized scheme is related with the number of debatable nodes.
-Figure~\ref{percentage_overlapping_node} shows the percentage of debatable nodes with different network densities, from which we can obtain the value of $m$.
+Figure~\ref{percentage_overlapping_node} shows the percentage of debatable nodes with different network densities.
 \begin{figure}[ht!]
@@
 \hline
- Scheme 				&Message Complexity 	&   Quantitative number of messages 		& Content of message (size of message) 									\\ \hline
- ROSS-DGA, ROSS-$\delta$-DGA 	&$\mathcal{O}(N^3)$ (worst case)		&   $h+2m^2d$ (upper bound)  				&   \multirow{2}{*}{\parbox{7.7cm}{Cluster head $i$ broadcasts channel availability on all cluster members ($|C(i)| |\mathcal{K}|$ bytes); Cluster member $i$ broadcasts the new individual connectivity $d_i$ after being included in one or more clusters (1 byte)}}								\\ \cline{1-3}
- ROSS-DFA, ROSS-$\delta$-DFA 	&$\mathcal{O}(N)$ (worst case)		&   $h + 2m$	 (upper bound) 					& 	      												\\ \hline
+ Scheme 				&Message Complexity 	&   Quantitative number of messages 		& Content and size of the message 									\\ \hline
+ ROSS-DGA, ROSS-$\delta$-DGA 	&$\mathcal{O}(N^3)$ (worst case)		&   $N+n^2m$ (upper bound)  				&   \multirow{2}{*}{\parbox{7.7cm}{PhaseI: ID, $d_i$,$g_i$, which are 3 bytes;\\ PhaseII: Cluster head $i$ broadcasts channel availability on all cluster members, where are $|C(i)| |\mathcal{K}|$ bytes}}								\\ \cline{1-3}
+ ROSS-DFA, ROSS-$\delta$-DFA 	&$\mathcal{O}(N)$ (worst case)		&   $N + n$	 (upper bound) 					& 	      												\\ \hline
  SOC 					&$\mathcal{O}(N)$		&   $3N$									& Every CR node $i$ broadcasts channel availability on all cluster members ($|C(i)| |\mathcal{K}|$ bytes)
  \\ \hline
- Centralized			&$\mathcal{O}(N)$			&	$h + m + N$ (upper bound)~\cite{Efficient_broadcasting_gathering_adhoc}		& clustering result (2$N$ bytes) \tnotex{tnote:robots-r1} 					\\ \hline
+ Centralized			&$\mathcal{O}(N)$			&	$N + n + m$ (upper bound) \cite{Efficient_broadcasting_gathering_adhoc}		& clustering result, which is 2$N$ bytes \tnotex{tnote:robots-r1} 					\\ \hline
 \end{tabular}
     \begin{tablenotes}
-      \item\label{tnote:robots-r1}Assuming the data structure of the clustering result is in the form of \{ Node ID $i$, cluster head ID h($C$) where $i\in C$, for every $i\in \mathcal{N}$ \}.
+      \item\label{tnote:robots-r1}Assuming the data structure of the clustering result is in the form of $\{i, C\}, i\in C, i\in \mathcal{N}$.
     \end{tablenotes}
@@
 \label{largeScaleCRN}
-In this section we investigate the performances of distributed clustering schemes in CRN with different network scales and densities.
+In this section we investigate the performances of the proposed distributed clustering schemes in CRN with different network scales and densities.
 The transmission range of CR is $A/5$, PU's transmission range is $2A/5$.
@@
 
-\subsubsection{Robustness of the clusters against newly added PUs}
+\subsubsection{Robustness of the clusters against increased PUs}
 We add extra 20 batches of PUs sequentially in the CRN, where each batch includes 10 PUs. 

### 2017-04-01 journal-draft/bare_jrnl_comsoc.tex
message compelxity

@@
  ROSS-DFA, ROSS-$\delta$-DFA 	&$\mathcal{O}(N)$ (worst case)		&   $N + n$	 (upper bound) 					& 	      												\\ \hline
- SOC 					&$\mathcal{O}(N)$		&   $3N$									& Every CR node $i$ broadcasts channel availability on all cluster members ($|C(i)| |\mathcal{K}|$ bytes)
+ SOC 					&$\mathcal{O}(N)$		&   $3N$									& Every CR node $i$ broadcasts channel availability on all cluster members, which is $|C(i)| |\mathcal{K}|$ bytes
  \\ \hline

### 2017-04-01 journal-draft/bare_jrnl_comsoc.tex
modified section 3

@@
 When the global knowledge of the CRN is available to us, we can propose a centralized scheme as comparison.
-The proposed centralized solution formulates the problem in Definition~\ref{def_centralized_clustering} as an optimization problem, then the latter is solved with standard software packages.
+The proposed centralized solution formulates the problem in Definition~\ref{def_centralized_clustering} as an optimization problem which is solved with standard software packages.
 The optimization searches the set $\mathcal{S}$ and decides on the clusters according to the following optimization formulation,
@@
 \begin{aligned}
-     &\max\limits_{w_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (w_i\cdot t_{ij}) \\
+     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot t_{ij}) \\
      &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, for\,\,\forall j=1, \ldots, N \\
-   &&& \Sigma_{j=1}^N x_{ij} = |C_i|\cdot w_i,\, for\,\,\forall i=1, \ldots, M \\
+   &&& \Sigma_{j=1}^N x_{ij} = |C_i|\cdot y_i,\, for\,\,\forall i=1, \ldots, M \\
   % &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
@@
 This problem is a binary linear programming problem, which can be solved by many available solvers.
-$w_i$ and $x_{ij}$ are two binary variables.
+$y_i$ and $x_{ij}$ are two binary variables.
 % where $j\in \{1,2,\cdots,N-1, N\}$ and $i\in \{1,2,\cdots,M-1, M\}$.
 %$G = |\mathcal{G}|$ and there is $\mathcal{G} \subseteq \mathcal{S}$.
-Being either 1 or 0, $w_i$ denotes whether the $i$-th cluster $C_i$ in $\mathcal{S}$ is chosen or not.
+Being either 1 or 0, $y_i$ denotes whether the $i$-th cluster $C_i$ in $\mathcal{S}$ is chosen or not.
 $x_{ij}$ indicates whether the CR node $j$ resides in the cluster $C_i$, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$. 
 %Node index $j$ is identical to the node ID.
-$N$ is the total number of CR users in network $\mathcal{N}$, $M$ is the number of possible clusters in $\mathcal{S}$.
+$N$ is the total number of CR users in network $\mathcal{N}$, $M$ is the number of clusters in $\mathcal{S}$.
 
@@
 %The optimization is a binary linear programming problem.
-The objective is to maximize the sum of the numbers of CCs in the clusters which constitute the whole CRN.
-$t_{ij}$ is a constant and there is,
+The objective is to maximize the sum of the numbers of CCs in the clusters which constitute the CRN.
+$t_{ij}$ is a constant and there is
 %In practice, we can solve the problem with $\mathcal{G} = \mathcal{S}$ when $|\mathcal{S}|$ is not large. 
@@
 \end{equation}
-where $q_{ij}= |K(C_i)|$ when node $j\in C_i$, and $q_{ij}= 0$ when node $j\notin C_i$.
+where constant $q_{ij}= |K(C_i)|$ when node $j\in C_i$, and $q_{ij}= 0$ when node $j\notin C_i$.
 %$|K(C_i)|$ is the number of CCs of cluster $C_i$, and $|C_i|$ is the size of cluster $C_i$.
-$p_i(C_i)$ is the size-related weight, which reflects the deviation between the size of $C_i$ and the desired size.
-Assuming $\delta$ is the desired size, then
+$p_i(C_i)$ is the size-related weight, which reflects the deviation of $C_i$'s size from the desired size.
+Assuming $\delta$ is the desired size, then there is
 $$
@@
 
-Now we examine the objective function to see whether it in line with the goal to maximize the total number of CCs meanwhile consider the restriction on the cluster size.
-Replacing $t_{ij}$ with $\frac{q_{ij}}{|C_i|} - p_i(C_i)$, the objective function becomes,
+%Now we examine the objective function to see whether it in line with the goal to maximize the total number of CCs meanwhile consider the restriction on the cluster size.
+When $t_{ij}$ is replaced with $\frac{q_{ij}}{|C_i|} - p_i(C_i)$, the objective function becomes,
 \begin{equation}
 \begin{aligned}
-     &\max\limits_{w_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (w_i\cdot \frac{q_{ij}}{|C_i|} - w_i\cdot p_i(C_i)) \\
+     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p_i(C_i)) \\
 \notag
@@
 %$\mathcal{G}$ can be prepared based on the cluster size, and it is recommended to include all the singleton clusters to make sure the availability of feasible solutions.
-
-Another obstacle to apply this centralized scheme comes from the characteristics of CRN.
-In order to apply this scheme in practice, a large over head needs to be factored in in collecting the channel usage as seen by the R nodes, as well as the connectivity between the CR nodes.
-After computing the clustering solution, the centralized node needs to distribute it across the whole network.
-
-In CRN, it is necessary to do clustering again on some occasions.
-For example, when a certain amount of CR users move away from their clusters, \ie they loose the direction connection with any member in their previous clusters, or a certain amount of clusters can not be maintained as the CCs in these clusters don't exist any longer due to primary users' activity.
-Hence, when the spectrum availability and the CR users' location change frequently, the centralized robust clustering scheme is not suitable for CRN.
+Another obstacle comes from the fact that the centralized controller needs to be reliable at anytime, which is a challenge for CRN as the spectrum on the controller can not be guaranteed.
+%In order to apply this scheme in practice, a large over head needs to be factored in in collecting the channel usage as seen by the R nodes, as well as the connectivity between the CR nodes.
+%After computing the clustering solution, the centralized node needs to distribute it across the whole network.
+
+%In CRN, it is necessary to do clustering again on some occasions.
+%For example, when a certain amount of CR users move away from their clusters, \ie they loose the direction connection with any member in their previous clusters, or a certain amount of clusters can not be maintained as the CCs in these clusters don't exist any longer due to primary users' activity.
+%Hence, when the spectrum availability and the CR users' location change frequently, the centralized robust clustering scheme is not suitable for CRN.
 
@@
  \\ \hline
- Centralized			&$\mathcal{O}(N)$			&	$N + n + m$ (upper bound) \cite{Efficient_broadcasting_gathering_adhoc}		& clustering result, which is 2$N$ bytes \tnotex{tnote:robots-r1} 					\\ \hline
+ Centralized			&$\mathcal{O}(N)$			&	$N + n + m$ (upper bound) 		& clustering result, which is 2$N$ bytes \tnotex{tnote:robots-r1} 					\\ \hline
 \end{tabular}

### 2017-04-01 journal-draft/bare_jrnl_comsoc.tex
minor changes in 5.3 and conclusion section

@@
 \subsection{Insights Obtained from the Simulation}
-The simulation in the large CRN network confirms the conclusion made based on the simulation in the small CRN network, which is the average number of CCs along is not able to denote the robustness of the clusters, because the cluster size and the cluster members also affect the robustness.
+The simulation in the large CRN network confirms the conclusion made based on the simulation in the small CRN network, which is that the average number of CCs along is not able to denote the robustness of the clusters, because the cluster size and the constitution of the cluster also affect the robustness.
 
@@
 
-The shortcoming of distributed scheme ROSS is it doesn't generate clusters whose sizes exceed the cluster head's neighborhood.
+The limitation of distributed scheme ROSS is it doesn't generate clusters whose sizes exceed the cluster head's neighborhood.
 The reason is with ROSS, cluster heads form clusters on the basis of their neighborhood, and don't involve the nodes which are outside the neighborhood.

### 2017-04-03 journal-draft/bare_jrnl_comsoc.tex
simulation, conclusion polished

@@
         and James~Gross,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
-\thanks{D. Li was with RWTH Aachen university, Germany.}% <-this % stops a space
-\thanks{Erwin. Fang is with ETH, Switzerland.}% <-this % stops a space
-\thanks{J. Gross is with KTH Royal Institute of Technology, Sweden.}% <-this % stops a space
+\thanks{Di Li was with RWTH Aachen university, Germany.}% <-this % stops a space
+\thanks{Erwin Fang is with ETH, Switzerland.}% <-this % stops a space
+\thanks{James Gross is with KTH Royal Institute of Technology, Sweden.}% <-this % stops a space
 \thanks{Manuscript received xxxx xx, 20xx; revised xxxx xx, 20xx.}}
@@
 
-Figure~\ref{ccc_large_scale} shows the average number of CCs of the non-singleton clusters.
-We notice that SOC achieves the most CCs per non-singleton cluster, although the lead over the variants of ROSS shrinks significantly when $N$ increases.
+The average number of CCs of the non-singleton clusters is shown in Figure~\ref{ccc_large_scale}.
+SOC achieves the most CCs per non-singleton cluster, but the lead over the variants of ROSS decreases significantly when $N$ increases.
 %\ie when $N=300$, the number of CCs achieved by ROSS variants (except for ROSS-$\delta$-DFA) is almost the same as that resulted from SOC.
@@
 \subsubsection{Robustness of the clusters against increased PUs}
-We add extra 20 batches of PUs sequentially in the CRN, where each batch includes 10 PUs. 
-Figure~\ref{singleton_clusters_100} and \ref{singleton_clusters_200} show that when $N=100$ and 200, more unclustered CR nodes appear in the CRN where SOC is applied.
-When the network becomes denser, as shown in Figure~\ref{singleton_clusters_300}, ROSS-DGA/DFA generate slightly more unclustered CR nodes than SOC when new PUs are not many, but SOC's performance deteriorates quickly when the number of PUs becomes larger.
+We increase the primary users' activity by importing 20 batches of PUs sequentially in the CRN, where each batch includes 10 PUs.
+
+Figure~\ref{singleton_clusters_100} and \ref{singleton_clusters_200} show that when $N=100$ and 200, compared with the variants of ROSS, more unclustered CR nodes are generated by SOC.
+When $N=300$ as shown in Figure~\ref{singleton_clusters_300} and the new PUs are not many, ROSS-DGA/DFA generate slightly more unclustered CR nodes than SOC, but SOC's performance deteriorates quickly when the PUs continue increasing.
+%
+From Figure~\ref{singleton_clusters_100} to~\ref{singleton_clusters_300}, we can see that significantly less unclustered CR nodes are generated by the variants of ROSS whcih have size control mechanism.
+Besides, the greedy mechanism moderately strengthens the robustness of the clusters.
 We only show the average values of the variants of ROSS as their confidence intervals overlap.
-%
-When applying ROSS with size control mechanism, significantly less unclustered CR nodes are generated.
-Besides, the greedy mechanism moderately strengthens the robustness of the clusters.
 
@@
 \subsubsection{Cluster Size Control}
-Figure~\ref{nClusters_largeNetwork} shows when the network density scales up, the number of formed clusters by ROSS increases by smaller margin, and that generated by SOC increases linearly.
+Figure~\ref{nClusters_largeNetwork} shows when the network density increases, \ie $N$ changes from 100 to 300, the number of generated clusters by SOC increases linearly, whereas that by ROSS increases by a smaller margin.
 This result coincides with the analysis in Section~\ref{ross_p2_cluster_pruning}.
 %When the network becomes denser, more clusters are generated by SOC compared with ROSS variants.
-To better understand the distribution of the sizes of formed clusters, we depict the empirical cumulative distribution of CR nodes in clusters with different sizes in Figures~\ref{cdf_clusterSize_100}~\ref{cdf_clusterSize_200}~\ref{cdf_clusterSize_300}.
+To better understand the distribution of the sizes of formed clusters, for each network density, we depict the empirical cumulative distribution of CR nodes which are in clusters with different sizes in Figures~\ref{cdf_clusterSize_100}~\ref{cdf_clusterSize_200}~\ref{cdf_clusterSize_300} respectively.
 \begin{figure}[!h]
@@
 \end{figure}
-The sizes of clusters generated by ROSS-DGA and ROSS-DFA span a wider range than ROSS with size control feature.
-Most of the generated clusters are smaller than the average number of neighbours, which is roughly equal with the 95\% percentile of the ROSS-DGA curve.
-The 50\% percentile of the ROSS-DGA curve is roughly the desired size $\delta$.
-When the variants of ROSS with size control feature are applied, the sizes of the most generated clusters are smaller than $\delta$.
-As to the curves of SOC, the 95\% percentiles are 36, 30, and 40 in respective networks.
-%
-From Figure~\ref{cdf_100_200_300}, we conclude that the sizes of the clusters generated by ROSS are limited by the network density, the sizes of the clusters formed by ROSS with size control feature are restricted by the desired size.
-In contrary, the clusters generated from SOC demonstrate strong divergence on cluster sizes.
+
+The variants of ROSS generate more clusters whose sizes are closer to the desired size, \ie when $N=100$ and desired cluster size is 6 as shown in Figures~\ref{cdf_clusterSize_100}, 90\% of CR nodes are in the clusters whose sizes are from 3 to 9, while as to SOC, only 17\% of nodes are in the clusters with these sizes.
+Similarly, when $N=200$ and the desired size is 12 as shown in Figure~\ref{cdf_clusterSize_200}, 80\% of nodes are in the clusters whose sizes are from 6 to 18, meanwhile only 30\% of nodes constitute clusters of these sizes when SOC is executed.
+%Now we check how many CR nodes are in the clusters whose sizes deviate not much from the desired size, where we put the deviation limit at $\pm 50\%$ of the desired size.
+The clusters sizes from ROSS-$\delta$-DGA and ROSS-$\delta$-DFA concentrates more than that from ROSS-DGA and ROSS-DFA.
+In contrary, the clusters from SOC demonstrates obvious divergence on cluster sizes.
+
+%As to ROSS-DGA, the 95\% percentiles of the ROSS-DGA curves are 8, 18 and 20.
+%When the size control feature is implemented, the 95\% percentiles of ROSS-$\delta$-DGA is 5,12,13. 
+%Meanwhile, the 50\% percentiles of the ROSS-DGA curves are 6, 10 and 14 respectively, and the 50\% percentiles of the ROSS-$\delta$-DGA are 4,7,9.
+%As comparison, the 95\% percentiles of SOC are 36, 30, and 40 in the respective networks.
+
+%This means that the sizes of the clusters generated by ROSS-DGA are limited by the network density, and the size control feature further restricts the appearances of the big clusters, thus when the variants of ROSS are implemented, most of the CR nodes are in the clusters which are slightly smaller than the desired size.
 
 \subsection{Insights Obtained from the Simulation}
-The simulation in the large CRN network confirms the conclusion made based on the simulation in the small CRN network, which is that the average number of CCs along is not able to denote the robustness of the clusters, because the cluster size and the constitution of the cluster also affect the robustness.
-
-The centralized clustering scheme is able to form the clusters which satisfy the requirement on cluster size strictly, and the clusters are robust against the PUs' activity, besides, it generates the smallest control overhead in the process of clustering.
-
+The simulation made with the large CRN network confirms that made with the small CRN network, which is that the average number of CCs along doesn't tell the robustness of the clusters, because the cluster size and the constitution of the cluster also affect the robustness.
+
+The centralized clustering scheme is able to form the clusters which satisfy the requirement on cluster size strictly, and the clusters are robust against the PUs' activity, besides, it involves the smallest control overhead in the process of clustering.
 As distributed schemes, the variants of ROSS outperform SOC considerably on three metrics.
-First, the variants of ROSS generate less singleton clusters than SOC for a given CRN, and the resulted clusters are more robust than SOC when PUs become more active.
+First, the variants of ROSS generate less unclustered nodes than SOC for a given CRN, and the resulted clusters are more robust than SOC when PUs become more active.
 Second, the signaling overhead involved in ROSS is about half of that needed for SOC, and the signaling messages are much shorter that the latter.
@@
 %
-As to the variants of ROSS, the greedy mechanism in ROSS-DGA helps to improve the performance on cluster size and cluster robustness at the cost of mildly increased signaling overhead.
-We also notice that  as a metric, the number of CCs per non-singleton cluster doesn't indicate the robustness of clusters as shown in Figure~\ref{singleton_clusters} and \ref{unclustered_100_200_300}, although it is adopted as the metric in the formation of clusters.
+As to the variants of ROSS, the greedy mechanism in ROSS-DGA helps to improve the performance on cluster size and cluster robustness at the cost of increased signaling overhead.
+%We also notice that as a metric, the number of CCs per non-singleton cluster doesn't indicate the robustness of clusters as shown in Figure~\ref{singleton_clusters} and \ref{unclustered_100_200_300}, although it is adopted as the metric in the formation of clusters.
 
@@
 \label{conclusion}
-In this paper we investigate the robust clustering problem in CRN extensively and propose an efficient distributed clustering solution.
+In this paper we investigate the robust clustering problem in CRN extensively and propose both centralized and distributed clustering solutions.
 %generate robust clusters against primary users' influence, so that more CR users can benefit from operative decision making provided by the clusters.
 We provide the mathematical description of the problem and prove the NP hardness of it.
-We propose both centralized and distributed schemes ROSS, the cluster structure generated by them has longer time expectancy against the primary users' activity.
-Besides, the proposed schemes can generate clusters with desired sizes.
+The proposed clustering schemes generate clusters which have long time expectancy against the primary users' activity, besides, the proposed schemes generate clusters which have desired sizes.
 %The congestion game model in game theory is used to design the distributed schemes.
 %A Light weighted clustering scheme ROSS is also proposed.
-Through simulation and theoretical analysis, we find that distributed schemes achieve similar performance with centralized optimization in terms of cluster robustness, signaling overhead and cluster sizes, and outperform the comparison distributed scheme on the above mentioned metrics.
+Through simulation and theoretical analysis, we find that the distributed schemes achieve similar performance with the centralized scheme in terms of cluster robustness, signaling overhead and cluster sizes, and outperform the comparison distributed scheme on the above mentioned metrics.
 
@@
 The reason is with ROSS, cluster heads form clusters on the basis of their neighborhood, and don't involve the nodes which are outside the neighborhood.
-In the other way around, forming big cluster which extends a cluster head's neighborhood has limited application scenarios, as multiple hop communication and coordination are required within these clusters.
+%In the other way around, forming big cluster which extends a cluster head's neighborhood has limited application scenarios, as multiple hop communication and coordination are required within these clusters.
 

### 2017-04-08 journal-draft/ettdoc.tex
add ettdoc files

--- 2017-04-03 journal-draft/bare_jrnl_comsoc.tex
@@
-% to do : add more notations
-% the new notation t.
-\documentclass[10pt,journal,compsoc]{IEEEtran}
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[journal,comsoc]{../sty/IEEEtran}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% copied from thesis
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Packages für Formeln %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage[colorlinks,
-            linkcolor=red,
-            anchorcolor=blue,
-            citecolor=green
-            ]{hyperref}
-\usepackage{amsmath}
-\usepackage{amsthm}
-%\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{booktabs}
-\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
-
-%% Packages
-%\usepackage{tikz}
-%\usetikzlibrary{shapes,arrows}
-%\usetikzlibrary{positioning}
+% ettdoc.tex V2.10, 19 June 2012
+
+\documentclass[times]{ettauth}
+\usepackage[toc,page]{appendix}
+\usepackage{moreverb}
+
+\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
+
+\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
+T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
+\def\volumeyear{2012}
+
+\newcommand{\eg}{e.g., }
+\newcommand{\ie}{i.e., }
+\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
+%\usepackage{algorithmic}
+\usepackage{times}
+%\usepackage{mathptmx}
+\usepackage{mathtools}
+\usepackage[draft,nomargin,marginclue,footnote,silent]{fixme}
+\setcounter{tocdepth}{2} %table of contents
+
+\theoremstyle{mytheoremstyle}
+\newtheorem{theorem}{Theorem}[section]
+
+\theoremstyle{mytheoremstyle}
+\newtheorem{corollary}{Corollary}[section]
+
+\theoremstyle{mytheoremstyle}
+\newtheorem{lemma}{Lemma}[section]
+
+\newtheorem{mydef}{Definition}
+
+\DeclareMathOperator*{\Max}{Max}
+\DeclareMathOperator*{\Min}{Min}
+
+\newcommand{\bigO}{\ensuremath{\mathcal{O}}}% big-O notation/symbol
+\usepackage{subfigure}
+\usepackage{adjustbox}
+\usepackage{multirow}
+\usepackage{enumitem}
+\usepackage{lipsum}
+\setlist[itemize]{leftmargin=*}
+\usepackage[referable]{threeparttablex}
+\renewlist{tablenotes}{enumerate}{1}
+\makeatletter
+\setlist[tablenotes]{label=\tnote{\alph*},ref=\alph*,itemsep=\z@,topsep=\z@skip,partopsep=\z@skip,parsep=\z@,itemindent=\z@,labelindent=\tabcolsep,labelsep=.2em,leftmargin=*,align=left,before={\footnotesize}}
+\makeatother
+
 \usepackage{graphicx}
@@
 \usepackage{multicol}
-%\usepackage{colortbl}
-%\usepackage{todonotes}	
-\newcounter{todocounter}
-\newcommand{\todonum}[2][]
-{\stepcounter{todocounter}\todo[inline,backgroundcolor=blue!10!white, #1]{\thetodocounter: #2}}
-
-%% Zeilenabstand %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{setspace}
-%\singlespacing        %% 1-zeilig (Standard)
-%\onehalfspacing       %% 1,5-zeilig
-%\doublespacing        %% 2-zeilig
 
@@
 \newcolumntype{L}[1]{>{\raggedright\arraybackslash}m{#1}}
-
 % Table spacings
@@
 
-\newtheoremstyle{mytheoremstyle} % name
-        {\topsep}                    % Space above
-        {\topsep}                    % Space below
-        {\itshape\fontfamily{ptm}\selectfont}                   % Body font, ptm is times new roma
-        {}                           % Indent amount
-        {\fontfamily{ptm}\selectfont\scshape\color{black}\bfseries}                   % Theorem head font
-        {:}                          % Punctuation after theorem head
-        {.5em}                       % Space after theorem head
-        {}  % Theorem head spec (can be left empty, meaning ‘normal’)
-
-\theoremstyle{mytheoremstyle}
-\newtheorem{theorem}{Theorem}[section]
-
-\theoremstyle{mytheoremstyle}
-\newtheorem{corollary}{Corollary}[section]
-
-\theoremstyle{mytheoremstyle}
-\newtheorem{lemma}{Lemma}[section]
-
-%\theoremstyle{mytheoremstyle}
-%\let\definition\relax
-\newtheorem{mydef}{Definition}%[section]
-
-%%%%%%
-%%%%%% Proof
-    \makeatletter
-    \renewenvironment{proof}[1][\proofname]{%
-      \par\pushQED{\qed}\fontfamily{ptm}\selectfont%
-      \topsep6\p@\@plus6\p@\relax
-      \trivlist\item[\hskip\labelsep\bfseries#1\@addpunct{.}]%
-      \ignorespaces
-    }{%
-      \popQED\endtrivlist\@endpefalse
-    }
-    \makeatother 
-%%%%%%%%%%%%%%%%%
-
-\newcommand{\eg}{e.g., }
-\newcommand{\ie}{i.e., }
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-%\usepackage{algorithmic}
-\usepackage{times}
-%\usepackage{mathptmx}
-\usepackage{mathtools}
-\usepackage[draft,nomargin,marginclue,footnote,silent]{fixme}
-\setcounter{tocdepth}{2} %table of contents
-
-\makeatother
-\usepackage{comment}
-\newcommand{\Tau}{\mathrm{T}}
-\usepackage[colorinlistoftodos]{todonotes}
-\DeclareMathOperator*{\Max}{Max}
-\DeclareMathOperator*{\Min}{Min}
-
-\newcommand{\bigO}{\ensuremath{\mathcal{O}}}% big-O notation/symbol
-\usepackage{subfigure}
-\usepackage{adjustbox}
-\usepackage{multirow}
-\usepackage{enumitem}
-\usepackage{lipsum}
-\setlist[itemize]{leftmargin=*}
-\usepackage[referable]{threeparttablex}
-\renewlist{tablenotes}{enumerate}{1}
-\makeatletter
-\setlist[tablenotes]{label=\tnote{\alph*},ref=\alph*,itemsep=\z@,topsep=\z@skip,partopsep=\z@skip,parsep=\z@,itemindent=\z@,labelindent=\tabcolsep,labelsep=.2em,leftmargin=*,align=left,before={\footnotesize}}
-\makeatother
-%%%%%%%%%%%%%%%%%%%%%%%%%% copied from thesis
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\usepackage[T1]{fontenc}% optional T1 font encoding
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at: 
-% http://www.ctan.org/pkg/graphicx
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/pkg/epslatex
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-\usepackage{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
-% Do NOT use the amsbsy package under comsoc mode as that feature is
-% already built into the Times Math font (newtxmath, mathtime, etc.).
-% 
-% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/amsmath
-
-% Select a Times math font under comsoc mode or else one will automatically
-% be selected for you at the document start. This is required as Communications
-% Society journals use a Times, not Computer Modern, math font.
-%\usepackage[cmintegrals]{newtxmath}
-\usepackage{txfonts}
-% The freely available newtxmath package was written by Michael Sharpe and
-% provides a feature rich Times math font. The cmintegrals option, which is
-% the default under IEEEtran, is needed to get the correct style integral
-% symbols used in Communications Society journals. Version 1.451, July 28,
-% 2015 or later is recommended. Also, do *not* load the newtxtext.sty package
-% as doing so would alter the main text font.
-% http://www.ctan.org/pkg/newtx
-%
-% Alternatively, you can use the MathTime commercial fonts if you have them
-% installed on your system:
-%\usepackage{mtpro2}
-%\usepackage{mt11p}
-%\usepackage{mathtime}
-
-%\usepackage{bm}
-% The bm.sty package was written by David Carlisle and Frank Mittelbach.
-% This package provides a \bm{} to produce bold math symbols.
-% http://www.ctan.org/pkg/bm
-
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\argmax}{arg\,max}
-
 \begin{document}
-%
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
+
+\runningheads{A.~N.~Other}{A demonstration of the \journalabb\
+class file}
+
+\articletype{RESEARCH ARTICLE}
+
 \title{Robust Clustering for Ad Hoc Cognitive Radio Network}
-%
-%
-% author names and IEEE memberships
-% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
-% a structure at a ~ so this keeps an author's name from being broken across
-% two lines.
-% use \thanks{} to gain access to the first footnote area
-% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
-% was not built to handle multiple paragraphs
-%
-
-\author{Di~Li,~\IEEEmembership{Member,~IEEE,}
-        Erwin~Fang,
-        and James~Gross,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
-\thanks{Di Li was with RWTH Aachen university, Germany.}% <-this % stops a space
-\thanks{Erwin Fang is with ETH, Switzerland.}% <-this % stops a space
-\thanks{James Gross is with KTH Royal Institute of Technology, Sweden.}% <-this % stops a space
-\thanks{Manuscript received xxxx xx, 20xx; revised xxxx xx, 20xx.}}
-
-% note the % following the last \IEEEmembership and also \thanks - 
-% these prevent an unwanted space from occurring between the last author name
-% and the end of the author line. i.e., if you had this:
-% 
-% \author{....lastname \thanks{...} \thanks{...} }
-%                     ^------------^------------^----Do not want these spaces!
-%
-% a space would be appended to the last name and could cause every name on that
-% line to be shifted left slightly. This is one of those "LaTeX things". For
-% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
-% "AB" then you have to do: "\textbf{A}\textbf{B}"
-% \thanks is no different in this regard, so shield the last } of each \thanks
-% that ends a line with a % and do not let a space in before the next \thanks.
-% Spaces after \IEEEmembership other than the last one are OK (and needed) as
-% you are supposed to have spaces between the names. For what it is worth,
-% this is a minor point as most people would not even notice if the said evil
-% space somehow managed to creep in.
-
-% The paper headers
-\markboth{Journal of xxxxx,~Vol.~xx, No.~x, xxxx~20xx}%
-{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Communications Society Journals}
-% The only time the second header will appear is for the odd numbered pages
-% after the title page when using the twoside option.
-% 
-% *** Note that you probably will NOT want to include the author's ***
-% *** name in the headers of peer review papers.                   ***
-% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
-% you desire.
-
-% If you want to put a publisher's ID mark on the page you can do it like
-% this:
-%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
-% Remember, if you use this you must call \IEEEpubidadjcol in the second
-% column for its text to clear the IEEEpubid mark.
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
-\maketitle
-
-% As a general rule, do not put math, special symbols or citations
-% in the abstract or keywords.
+
+\author{Di Li, Erwin Fang, James Gross\corrauth}
+
+\address{John Wiley \& Sons, Ltd, The Atrium, Southern Gate, Chichester,
+West Sussex, PO19~8SQ, UK}
+
+\corraddr{Journals Production Department, John Wiley \& Sons, Ltd,
+The Atrium, Southern Gate, Chichester, West Sussex, PO19~8SQ, UK.}
+
 \begin{abstract}
@@
 
-% Note that keywords are not normally used for peerreview papers.
-\begin{IEEEkeywords}
-cognitive radio, robust cluster, game theory, congestion game, distributed, centralized, cluster size control.
-\end{IEEEkeywords}
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
+%\keywords{class file; \LaTeXe; \emph{\journalabb}}
+
+\maketitle
 \graphicspath{
@@
 %CR concept
-\IEEEPARstart{C}{ognitive} radio (CR) is a promising technology to solve the spectrum scarcity problem~\cite{Mitola}.
+Cognitive radio (CR) is a promising technology to solve the spectrum scarcity problem~\cite{Mitola}.
 Licensed users access the spectrum allocated to them whenever there is information to be transmitted.
@@
 
-\section*{Acknowledgment}
-
-The authors would like to thank xxxx
-
-% Can use something like this to put references on a page
-% by themselves when using endfloat and the captionsoff option.
-\ifCLASSOPTIONcaptionsoff
-  \newpage
-\fi
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-
-% You can push biographies down or up by placing
-% a \vfill before or after them. The appropriate
-% use of \vfill depends on what kind of text is
-% on the last page and whether or not the columns
-% are being equalized.
-
-%\vfill
-
-% Can be used to pull up biographies so that the bottom of the last one
-% is flush with the other column.
-%\enlargethispage{-5in}
-\bibliographystyle{IEEEtran}
 \bibliography{../backmatter/myrefs}
 
-% biography section
-% 
-% If you have an EPS/PDF photo (graphicx package needed) extra braces are
-% needed around the contents of the optional argument to biography to prevent
-% the LaTeX parser from getting confused when it sees the complicated
-% \includegraphics command within an optional argument. (You could create
-% your own custom macro containing the \includegraphics command to make things
-% simpler here.)
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
-% or if you just want to reserve a space for a photo:
-%IEEEbiographynophoto
-\begin{IEEEbiography}{Di Li}
-received BE and MS degrees in control engineering from Zhejiang University and Shaanxi University of Science and Technology respectively in China.
-He worked with James Gross for his PhD in RWTH Aachen University since 2010.
-\end{IEEEbiography}
-
-% if you will not have a photo at all:
-\begin{IEEEbiography}{Erwin Fang}
-Biography text here.
-Biography text here.
-Biography text here.
-Biography text here.
-Biography text here.
-Biography text here.
-
-\end{IEEEbiography}
-%\vspace{-50 mm}
-% insert where needed to balance the two columns on the last page with
-% biographies
-%\newpage
-
-\begin{IEEEbiography}{James Gross}
-Biography text here.
-Biography text here.
-Biography text here.
-Biography text here.
-Biography text here.
-Biography text here.
-Biography text here.
-
-\end{IEEEbiography}
+\ack This class file was developed by Sunrise Setting Ltd,
+Paignton, Devon, UK. Website:\\
+\href{http://www.sunrise-setting.co.uk}{\texttt{www.sunrise-setting.co.uk}}
 

### 2017-04-08 journal-draft/ettdoc.tex
latex file is OK, but 15 pages
adjust the space

@@
 \usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-%\usepackage{algorithmic}
+\DeclareMathOperator*{\argmin}{arg\,min}
+\DeclareMathOperator*{\argmax}{arg\,max}
+
 \usepackage{times}
@@
 \begin{enumerate}
+\setlength{\itemindent}{-.17in}
 \item the sum of the $f(C) is the maximal$, where $C\in \mathcal{T}$ 
@@
   \includegraphics[width=0.5\linewidth]{figure2.pdf}
-  \caption{Clusters formation after the phase I of ROSS. CR nodes $A, B, D$ are debatable nodes as they belong to multiple clusters.}
+  \caption{Clusters formation after the phase I of ROSS. Nodes $A, B, D$ are debatable nodes as they belong to multiple clusters.}
   \label{fig2}
@@
 \begin{threeparttable}
-\begin{tabular}{|C{2 cm}|C{2.8 cm}|C{3.15 cm}|C{7.7 cm}|}
+\begin{tabular}{|C{1.8 cm}|C{2.6 cm}|C{3 cm}|C{6.3 cm}|}
 \hline
  Scheme 				&Message Complexity 	&   Quantitative number of messages 		& Content and size of the message 									\\ \hline
- ROSS-DGA, ROSS-$\delta$-DGA 	&$\mathcal{O}(N^3)$ (worst case)		&   $N+n^2m$ (upper bound)  				&   \multirow{2}{*}{\parbox{7.7cm}{PhaseI: ID, $d_i$,$g_i$, which are 3 bytes;\\ PhaseII: Cluster head $i$ broadcasts channel availability on all cluster members, where are $|C(i)| |\mathcal{K}|$ bytes}}								\\ \cline{1-3}
+ ROSS-DGA, ROSS-$\delta$-DGA 	&$\mathcal{O}(N^3)$ (worst case)		&   $N+n^2m$ (upper bound)  				&   \multirow{2}{*}{\parbox{7.7cm}{PhaseI: ID, $d_i$,$g_i$, which are 3 bytes;\\ PhaseII: Cluster head $i$ broadcasts channel availability to all \\ members, where are $|C(i)| |\mathcal{K}|$ bytes}}								\\ \cline{1-3}
  ROSS-DFA, ROSS-$\delta$-DFA 	&$\mathcal{O}(N)$ (worst case)		&   $N + n$	 (upper bound) 					& 	      												\\ \hline
@@
 {\small
-\hfill{}
-\begin{tabular}{|L{3.7 cm}|C{1 cm}|C{1 cm}|C{1 cm}|}
+%\hfill{}
+\begin{tabular}{|L{3 cm}|C{0.85 cm}|C{0.85 cm}|C{0.85 cm}|}
 \hline
@@
 }
-\hfill{}
+%\hfill{}
 \end{table}
@@
 
-% you can choose not to have a title for an appendix
-% if you want by leaving the argument blank
-%\section*{Algorithm~\ref{alg_size_control_available_CCC}}
-%\section{}
 \begin{algorithm}               % enter the algorithm environment
@@
 
-%\begin{table}[h!]
-%     \begin{center}
-%     \begin{tabular}{ C{3cm}  C{4.5cm} }
-%     \toprule
-%      $\mathcal{N}$  & $\{0, 1,2,3,4,5,6, 7, 8, 9\}$\\ 
-%    \cmidrule(r){1-1}\cmidrule(lr){2-2}     
-%      $\mathcal{Q}$  & $\{ \{1\}, \{1, 5\}, \{1,2,4\}, \{2,3\}, \{4\} \}$\\ 
-%    \cmidrule(r){1-1}\cmidrule(lr){2-2}     
-%      Instance for Weighted $k$-set packing  & $\{ \{1\}, \{2,3\}, \{4\} \}$, weights are 2, 3, 4\\ 
-%    \cmidrule(r){1-1}\cmidrule(lr){2-2}
-%      Instance with dummy elements (step 1)
-%      & 
-%		$\{ \, \{1,11\},\{2,12, 3, 13\}, \{ 4,14\} \, \}$
-%      \\    \cmidrule(r){1-1}\cmidrule(lr){2-2}
-%	clusters mapped from $\mathcal{I}$  (step 2)
-%	  &
-%	  \begin{minipage}{.3\textwidth}	
-%      \includegraphics[width=0.6\linewidth]{np_hard_proof_step_2_3.pdf}
-%    \end{minipage}
-%          \\    \cmidrule(r){1-1}\cmidrule(lr){2-2}
-%	formation of clusters (step 3)
-%	  &
-%	  \begin{minipage}{.3\textwidth}	
-%      \includegraphics[width=0.6\linewidth]{np_hard_proof_step4.pdf}
-%    \end{minipage}
-%	  \\       \bottomrule
-%      \end{tabular}
-%      \caption{}
-%      \label{no_hard_proof_instance}
-%      \end{center}
-%      \end{table}
-
 \end{proof}
 
+\bibliographystyle{IEEEtran}
 \bibliography{../backmatter/myrefs}

### 2017-04-09 journal-draft/ettdoc.tex
proofreading, modified minor mistakes

@@
 \setlist[itemize]{leftmargin=*}
+\setlist[enumerate]{wide=\parindent}
 \usepackage[referable]{threeparttablex}
@@
 Cluster size also plays a part in transmission power consumption, \ie cluster size affects the transmission power consumption when routing is conducted~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
-In this paper we focus on the efficient formation of the clusters and the evaluation of the robustness of the formed clusters, but our scheme is also able to generate the clusters with the desired size, which gives the network designers more freedom when the power consumption is involved in the design of network applications.
+In this paper we will analyze the robust clustering and propose efficient solutions.
+Our schemes generate the clusters which demonstrate both the robustness against the increasing primary activity and the compliance with the desired cluster sizes.
+Hence our schemes provide the network designers with more freedom when the power consumption is involved in the design of network applications.
 %In this paper we will introduce a robust cluster structure for CRN, where the robustness means the ability of the clusters to sustain under the influence of the increasing activity of primary users, and the direct metric is the number of CCs in the clusters.
@@
 
-Different clustering strategies have been proposed for wireless networks of different type.
+Different clustering strategies have been proposed for wireless networks of different types.
 As there is no restriction on the nodes to access the spectrum in wireless ad-hoc, mesh networks and sensor networks, the objective of clustering is to decrease the transmission power consumption~\cite{Kawadia03}, to improve the routing performance~\cite{clustering_mesh_globecom2010}, or to imrove the network lifetime and coverage~\cite{Abbasi_survey_07}.
@@
 First, this paper renews the definition of robustness of clusters in a CRN, which is no longer the average number of CCs of clusters, but the ability of the clusters to sustain when the primary users' activity becomes more dynamic.
-Second, this paper proposes size control mechanism, which solves the problem of devergence of clusters sizes in ~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
+Second, this paper proposes size control mechanism, which solves the problem of devergence of clusters sizes in~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
 Besides, this paper provides a comprehensive analysis of the robust clustering problem and proposes a centralized solution. 
@@
 We give the definition of cluster in CRN as follows. 
-A cluster $C$ is a set of secondary nodes which possess the same set of common channels.
+A cluster $C$ is a set of secondary nodes, and there is one set of common channels which are available for each node.
 In particular, a cluster consists of a cluster head $h(C)$ and a number of cluster members, and the cluster head is able to communicate with any cluster member directly.
@@
 When the cluster head of a cluster is $i$, we denote that cluster by $C(i)$.
-$K(C)$ denotes the set of CCs in cluster $C$, $ K(C) = \Cap_{i\in C} K_i$.
+$K(C)$ denotes the set of CCs in cluster $C$, $ K(C) = \bigcap_{i\in C} K_i$.
 %Clustering is performed periodically, because the secondary users are mobile and the primary users change their operation channels, thus the channel availability on secondary users changes accordingly.
@@
 As to a cognitive radio network, where the set of CR nodes is $\mathcal{N}$.
-Each cluster complies with the definition in~\ref{sec:model}, whose number of CCs in a cluster $C$ is $f(C)$.
+%Each cluster complies with the definition in , whose number of CCs in a cluster $C$ is $f(C)$.
 The robust clustering problem is to decide the set of clusters $\mathcal{T}$, where 
 \begin{enumerate}
-\setlength{\itemindent}{-.17in}
-\item the sum of the $f(C) is the maximal$, where $C\in \mathcal{T}$ 
+\setlength{\itemindent}{.05in}
+\item the sum of the $f(C)$ is the maximal, where $C\in \mathcal{T}$ 
 \item the intersection of any two clusters in $\mathcal{T}$ is an empty set
 \item the union of clusters in $\mathcal{T}$ is $\mathcal{N}$
-\item the cluster sizes should fall in the scope $\langle\delta_1, \delta_2\rangle$, where $\delta, \delta_1, \delta_2\in \mathbb{Z}^+$, $\delta_1 \leq \delta\leq \delta_2$, and $\delta$ is decided according to the application to be implemented.
+\item the cluster sizes should fall in the scope $\langle\delta_1, \delta_2\rangle$, where $\delta, \delta_1, \delta_2\in \mathbb{Z}^+$, $\delta_1 \leq \delta\leq \delta_2$, and $\delta$ is decided according to the application to be implemented in the CRN.
 \end{enumerate}
@@
 
-Assume we have obtained the set of $\mathcal{S}$ which contains all the possible clusters in $\mathcal{N}$, \ie $\mathcal{S}=\{C_1, C_2,\ldots,C_i, \ldots, C_{|\mathcal{S}|}\}$ \footnote{The subscript $i$ means the $i$-th cluster in $\mathcal{S}$.} and there is $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = \mathcal{N}$.
+Assume we have obtained the set of $\mathcal{S}$ which contains all the clusters in $\mathcal{N}$, \ie $\mathcal{S}=\{C_1, C_2,\ldots,C_i, \ldots, C_{|\mathcal{S}|}\}$ \footnote{The subscript $i$ means the $i$-th cluster in $\mathcal{S}$.} and there is $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = \mathcal{N}$.
 The decision version of this problem is to determine whether there is a non-empty set $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C_i\in \mathcal{S}'} f(C_i) \geqslant \lambda$ where $\lambda$ is a real number.
@@
 
-To formulate the debatable nodes' membership clarification into the desired congestion game, we reexamine this process from a different (or opposite) perspective. 
-From the new perspective, the debatable nodes are not included in any cluster, and they are looking for the proper cluster to join.
-% in other words, their claiming clusters become clusters which are beside them. 
-%Now for the debatable nodes, the previous problem of deciding which clusters to leave becomes a new problem that which cluster to join.
-A debatable node $i$ chooses one cluster $C$ out of $S_i$ to join if the decrease of CCs in cluster $C$ is the smaller than any other cluster in $S_i$.
-The decrease of CCs in cluster $C$ is $\sum_{C\in S_i}\Delta\vert K(C) \vert=\sum_{C\in S_i}({\vert K(C) \vert-\vert K(C\cup i) \vert})$.
-The interaction between the debatable nodes and the claiming clusters is shown in Figure~\ref{debatable_nodes_claiming_cluster}.
+To formulate the debatable nodes' membership clarification into the desired congestion game, we reexamine this process from a different/opposite perspective. 
+From the new perspective, the debatable nodes are not included in any cluster and they need to decide on one cluster to join.
+When a debatable node $i$ join one cluster $C$, the decrease of CCs in cluster $C$ is $\sum_{C\in S_i}\Delta\vert K(C) \vert=\sum_{C\in S_i}({\vert K(C) \vert-\vert K(C\cup i) \vert})$.
+Then, node $i$ chooses the cluster $C$, where the decrease of CCs in cluster $C$ is smaller than the decrease if $i$ would have joined any other claiming cluster in $S_i$.
+The relation between the debatable nodes and the claiming clusters is shown in Figure~\ref{debatable_nodes_claiming_cluster}.
 %The concern on convergence appears again as we have discussed in the previous subsubsection.
@@
 
-In fact, the upper bound of the number of steps which are actually involved in this process is much smaller than $N^3$.%, as both $n$ and $m$ are considerably smaller than $N$.
-The percentage of debatable nodes in the network is illustrated in Figure~\ref{percentage_overlapping_node}, which is between 10\% to 60\% of the total number of CR nodes in the network.
+In fact, the upper bound for the number of steps which are actually involved in this process is much smaller than $N^3$.
+The percentage of debatable nodes in the network is shown in Figure~\ref{percentage_overlapping_node}, which is between 10\% to 60\% of the total CR nodes in the network.
 In the other hand, the number of clusters heads is dependent on the network density and the CR node's transmission range as mentioned in Section~\ref{phaseI}.
@@
 We increase the number of PUs to challenge the non-singleton clusters, and count the number of the unclustered CR nodes.
-This metric directly indicates the robustness of clusters from a more practical point of view, \ie as to the clusters formed for a given CRN and spectrum availability, how many CR nodes can still make use of the clusters when the spectrum availability decreases.
-%robustness of clusters, as this metric directly shows how many nodes can make use of the cluster structure.
-%When we investigate the performance with moderate and vigorous intensity of primary users' activities, 
-%All the robust clustering schemes are proposed for a given CRN, when the available spectrum becomes scarce when the primary users' operation becomes more intense, the metric can illustrate the robustness of clusters by showing the unclustered CR nodes.
-%This metric is closely related with cluster robustness, \ie the less CR nodes which are not  nodes means more CR nodes are included into non-singleton clusters which survive the primary users' influence.
-%When we vary the intensity of primary users' activity, \eg from low to medium level by increasing the number of primary users, 
-%The drawback of this metric is, it doesn't indicate the robustness of the non-singleton clusters when the primary users conquer more spectrum.
+This metric indicates the robustness of the clusters, \ie as to the clusters formed for a given CRN and spectrum availability, how many CR nodes can still be benefited from the clusters when the spectrum availability decreases.
 
@@
 
-\subsubsection{Average number of CCs in Non-singleton Clusters}
+\subsubsection{CCs in Non-singleton Clusters}
 \label{ccc_20}
@@
 \begin{multicols}{3}
-    \includegraphics[width=\linewidth]{ccc_20.pdf}\par\caption{Number of common channels of non-singleton clusters}\label{ccc_per_nonsingleton}
+    \includegraphics[width=\linewidth]{ccc_20.pdf}\par\caption{Average number of CCs of non-singleton clusters}\label{ccc_per_nonsingleton}
     \includegraphics[width=\linewidth]{cdf_clusterSize_20.pdf}\par\caption{Cumulative distribution of CRs residing in clusters with different sizes}\label{size_control}    
@@
 
-\subsubsection{Robustness of the clusters against newly added PUs}
+\subsubsection{Robustness of the formed clusters}
 %When the number of PUs in CRN increases, or their operation becomes more intensive, some clusters don't seize any CCs any more, so that the cluster members and the cluster heads become unclustered, or singleton clusters.
@@
   \includegraphics[width=.7\linewidth]{ccc_large_scale_color.pdf}
-  \caption{Number of common channels of non-singleton clusters.}
+  \caption{Average number of CCs of non-singleton clusters}
   \label{ccc_large_scale}
@@
 
-\subsubsection{Robustness of the clusters against increased PUs}
+\subsubsection{Robustness of the formed clusters}
 We increase the primary users' activity by importing 20 batches of PUs sequentially in the CRN, where each batch includes 10 PUs.
@@
     \includegraphics[width=\linewidth]{survival_rate_300_edge50.pdf}\par\caption{300 CRs}\label{singleton_clusters_300}
-\end{multicols}\caption{Percentage of CR nodes which are not included in any non-singleton clusters}
-\label{unclustered_100_200_300}
+\end{multicols}
+%\caption{Percentage of CR nodes which are not included in any non-singleton clusters}
+%\label{unclustered_100_200_300}
 \end{figure*}
@@
 \end{multicols}
-\caption{Cumulative distribution of CRs residing in clusters with different sizes}
-\label{cdf_100_200_300}
+%\caption{Cumulative distribution of CRs residing in clusters with different sizes}
+%\label{cdf_100_200_300}
 \end{figure*}

### 2017-04-09 journal-draft/ettdoc.tex
proofreading

@@
 
-\address{John Wiley \& Sons, Ltd, The Atrium, Southern Gate, Chichester,
-West Sussex, PO19~8SQ, UK}
-
-\corraddr{Journals Production Department, John Wiley \& Sons, Ltd,
-The Atrium, Southern Gate, Chichester, West Sussex, PO19~8SQ, UK.}
+\address{RWTH Aachen University, ETH Zurich, KTH Royal Institute of Technology }
+
+\corraddr{Communication Theory Lab
+School of Electrical Engineering
+KTH Royal Institute of Technology
+SE - 100 44 Stockholm\\Email: james.gross@ee.kth.se}
 
@@
 Collaborative sensing relies on the consensus of CR users\footnote{The terms user and node appear interchangeably in this paper.
-In particular, user is adopted when its networking or cognitive ability are discussed or stressed, while we refer node typicallly in the context of the topology.} within a certain area, in this regard, clustering is regarded as an effective method to realize cooperative spectrum sensing~\cite{Sun07_clustering_spectrum_secsing, Zhao07}.
+In particular, user is adopted when its networking or cognitive ability are discussed or stressed, while we refer node typicallly in the context of the topology.} within a certain area, in this regard, clustering is regarded as an effective method to realize cooperative spectrum sensing~\cite{Sun07_clustering_spectrum_secsing}.
 % ... decreases considerably the negative probability due to the random channel effects like fading and shadowing.
@@
 We adopt the unit disk model~\cite{unitDiskModel} for both primary and CR users' transmission.
-%As to the relation between the primary and secondary users,
 If a CR node $i$ locates within the transmission range of an active primary user $p$, $i$ is not allowed to use the channel which is being used by $p$.
@@
 As the result of spectrum sensing, $K_i \subseteq \mathcal{K}$ denotes the set of available licensed channels for CR user $i$.
-As the transmission range of primary users is limited and secondary users have different locations, different secondary users have different views of the spectrum availability, i.e., for any $i, j \in \mathcal{N}$, $K_i = K_{j}$ does not necessarily hold.
-We therefore represent the network of CR nodes by a graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{i, j\} \in E$ if and only if $K_{i} \cap K_{j}\neq \emptyset$ and $d_{i,j} < r$, where $d_{i,j}$ is the distance between $i, j$ and $r$ is the radius of secondary user's transmission range.
-%
-Among the secondary users, we denote by $\text{Nb}(i)$ user $i$'s neighborhood, which consists of the CR nodes located within the transmission range of $i$.
+As the transmission range of primary users is limited and CR users have different locations, different CR users have different views of the spectrum availability, i.e., for any $i, j \in \mathcal{N}$, $K_i = K_{j}$ does not necessarily hold.
+We therefore represent the network of CR nodes by a graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{i, j\} \in E$ if and only if $K_{i} \cap K_{j}\neq \emptyset$ and $d_{i,j} < r$, where $d_{i,j}$ is the distance between $i, j$ and $r$ is the radius of CR user's transmission range.
+%
+Among the CR users, we denote by $\text{Nb}(i)$ the neighborhood of $i$, which consists of the CR nodes located within $i$'s transmission range.
 
@@
 The decision version of this problem is to determine whether there is a non-empty set $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C_i\in \mathcal{S}'} f(C_i) \geqslant \lambda$ where $\lambda$ is a real number.
-We have the following theorem on the complexity of this problem.
-
+We have the following theorem on the problem's complexity.
 \begin{theorem}
@@
 When CR node $i$ has lower individual connectivity degree than all its neighbors except for those which have already identified to be cluster heads, node $i$ becomes a cluster head.
-%In other words, CR node $i$ becomes cluster head if $d_i > d_k, \forall k\in \texttt{Nb}_i\setminus CHs$ ($CHs$ donate the cluster heads existing in $\texttt{Nb}_i$).
-If there is another CR node $j$ in its neighborhood which has the same individual connectivity degree as $i$, \ie $d_j = d_i$ and $d_j < d_{k}, \forall k\in \text{Nb}(j)\setminus \{\Lambda\cup i\}$ where $\Lambda$ denotes the cluster heads, then the node between $i$ and $j$, which has higher neighborhood connectivity degree will become the cluster head, and the other node will become one member of the newly identified cluster head.
+If there is another CR node $j$ in its neighborhood, which has the same individual connectivity degree as $i$, \ie $d_j = d_i$ and $d_j < d_{k}, \forall k\in \text{Nb}(j)\setminus \{\Lambda\cup i\}$ where $\Lambda$ denotes the cluster heads, then the node between $i$ and $j$, which has higher neighborhood connectivity degree will become the cluster head.
 If $g_i = g_j$ as well, the node ID is used to break the tie, \ie the one with smaller node ID becomes the cluster head.
@@
 %, which enables the nodes which are outside of the cluster can possibly become cluster heads or can also be included into other clusters.
-We have the following theorem to show that when there is no one secondary which shares no CC with any other secondary users, \ie
-all secondary users' individual connectivity degrees are greater than zero, then every secondary user will eventually be either integrated into a certain cluster, or becomes a cluster head.
+%We have the following theorem to show that when there is no one secondary which shares no CC with any other secondary users, \ie
+%all secondary users' individual connectivity degrees are greater than zero, then every secondary user will eventually be either integrated into a certain cluster, or becomes a cluster head.
+We have the following theorem to show that every secondary user will eventually be either integrated into a certain cluster or becomes a cluster head.
 \begin{theorem}
@@
 The Proof is in Appendix~\ref{proof_clustering:theorem}.
-
+%
 The procedure of the proof also illustrates the maximal time needed to conduct Algorithm~\ref{clustering:theorem}. 
@@
 If one step can be finished within a certain time span $T$, then the total time needed for the network to conduct Algorithm~\ref{clustering:theorem} is $N*T$.
-Actually as Algorithm~\ref{alg0} can be executed concurrently by different secondary users, the needed time can be considerably reduced.
+As Algorithm~\ref{alg0} can be executed concurrently by different secondary users, the needed time can be considerably reduced.
 %According to Theorem~\ref{clustering:theorem}, Phase I completes within a reasonable amount of time.
@@
 %	\item $\mathcal{R}=\left\{1,\ldots,m\right\}$, the set of resources which player can choose, which are all the clusters in our model.
-	\item $\mathcal{R} = \cup S_i, i\in \mathcal{P}$, denotes the set of resources for players to choose, in our problem, $S_i$ is the set of claiming clusters of node $i$, and $\mathcal{R}$ is the set of all claiming clusters.
-	\item Strategy space $\sum_i, i \in \mathcal{P}$, $\sum_i$ is the set of claiming clusters $S_i$ for $i$.
+	\item $\mathcal{R} = \cup S_i, i\in \mathcal{P}$, the set of the resources for players to choose.
+In our problem, $S_i$ is the set of the claiming clusters of $i$, and $\mathcal{R}$ is the set of all claiming clusters.
+	\item Strategy space $\sum_i, i \in \mathcal{P}$, $\sum_i$ is the set of the claiming clusters $S_i$.
 	As debatable node $i$ is supposed to choose only one claiming cluster, then only one piece of resource will be allocated to $i$.%, accordingly this congestion game is a singleton game.
@@
 Thus the number of steps can be expressed as $\mathcal{O}(N^3)$.
-
-In fact, the upper bound for the number of steps which are actually involved in this process is much smaller than $N^3$.
+%
+In fact, the upper bound for the number of steps which are involved in this process is much smaller than $N^3$.
 The percentage of debatable nodes in the network is shown in Figure~\ref{percentage_overlapping_node}, which is between 10\% to 60\% of the total CR nodes in the network.
 In the other hand, the number of clusters heads is dependent on the network density and the CR node's transmission range as mentioned in Section~\ref{phaseI}.
-The simulation in \cite{robust_clustering_arxiv} shows that the cluster heads are only 3.4\% to 20\% of the total CR nodes.
+The simulation in \cite{robust_clustering_arxiv} shows the cluster heads are only 3.4\% to 20\% of the total CR nodes.
 
@@
 The debatable nodes consider their claiming clusters to include all their debatable nodes, thus the membership of claiming clusters is static and all the debatable nodes can make decisions simultaneously without considering the change of membership of their claiming clusters.
-As ROSS-DFA is quicker than ROSS-DGA, the former is especially suitable for the CRN where the channel availability changes dynamically and re-clustering is necessary.
+As ROSS-DFA is quicker than ROSS-DGA, the former is especially suitable for the CRN where the channel availability changes frequently.
 To run ROSS-DFA, debatable nodes execute only one loop in Algorithm~\ref{alg4}.
@@
 %In this section, we evaluate the performances of ROSS.
-The schemes involved in the simulation are listed as follows,
+The schemes involved in the simulation are as follows,
 \begin{itemize}
-\item ROSS without size control, \ie ROSS-DGA and ROSS-DFA.
+\item ROSS without size control, \ie ROSS-DGA, ROSS-DFA.
 \item ROSS with size control, \ie ROSS-$\delta$-DGA and ROSS-$\delta$-DFA where $\delta$ is the desired cluster size.
@@
 \item \textbf{The average number of CCs per non-singleton cluster.}
-Non-singleton cluster refers to the cluster whose cluster size is larger than 1.
-Previous work \cite{LIU_TMC11_2} and \cite{Li11_ROSS} claim that the larger average number of CCs over all the clusters indicates longer life expectancy when the primary users' operation becomes more intense.
-We see two flaws in this claim.
-First, the unclustered CR nodes (synonym of singleton clusters) should not be considered when obtaining the average number of CCs, as singleton clusters don't contribute to the collaborative computing.
-Second, the average number of CCs doesn't necessarily indicate the robustness of individual clusters, because the ability for a cluster to sustain also depends on the cluster size and the locations of the cluster members, and this information is not illustrated in the average number of CCs.
+Non-singleton cluster refers to the cluster whose cluster size is larger than one.
+Previous work \cite{LIU_TMC11_2} and \cite{Li11_ROSS} claim that the larger average number of CCs over all the clusters indicates robustness , from which we see two flaws.
+First, the unclustered CR nodes (synonym of singleton clusters) should not be considered when calculating the average number of CCs, as singleton clusters don't contribute to the collaborative computing or sensing.
+Second, the average number of CCs doesn't necessarily indicate the robustness of individual clusters, because the ability for a cluster to sustain also depends on cluster size and the locations of the cluster members, but these information can not be illustrated in the average number of CCs.
 In the performance evaluation, we will examine the metric of average number of CCs per non-singleton cluster, which excludes the bias brought in by the unclustered CR nodes.
-More importantly, we will examine whether this metric reflects the robustness of the clusters against increasingly active primary users.
+Moreover, we will examine whether this metric reflects the robustness of the clusters.
 
@@
 
-The above observation shows that the average number of CCs of non-singleton clusters doesn't necessarily illustrate the robustness  of cluster against increasingly active PUs, \ie SOC obtains the largest average CCs, but generates the most vulnerable clusters.
+The above observation shows that the average number of CCs of non-singleton clusters doesn't necessarily illustrate the robustness  of cluster, \ie SOC obtains the most CCs for the clusters which are meanwhile the most vulnerable.
 Besides, with similar distribution of sizes, the clusters generated by ROSS-DGA and ROSS-DFA are more robust than that by SOC.
@@
 As to ROSS, in the first phase the maximal number of broadcast is $N$ according to~\ref{clustering:theorem}.
-The upper bounds of the transmissions are $n^2m$ and $n$ for ROSS-DGA and ROSS-DFA respectively.
-Scheme SOC consists of three rounds and in each round every node needs to broadcast in order to do comparisons and cluster mergers.
-The centralized scheme is conducted at the centralized control device, and it involves information aggregation and clustering decision dissemination.
+The upper bounds for the transmissions are $n^2m$ and $n$ for ROSS-DGA and ROSS-DFA respectively.
+Scheme SOC consists of three rounds, and in each round every node needs to broadcast to do comparisons and cluster mergers.
+The centralized scheme is conducted at the centralized control device, which involves information aggregation and clustering decision dissemination.
 We adopt the backbone structure proposed in~\cite{Efficient_broadcasting_gathering_adhoc} to analyze the centralized scheme's message complexity.
 We apply ROSS to generate cluster heads which serve as the backbone.
-In the process of information aggregation, all the nodes transmit information to the cluster heads which forward the messages to the controller, then in the process of dissemination, all the cluster heads and the debatable nodes broadcast the clustering result, thus the upper bound of the number of broadcast is $N+m+n$.
+In the process of information aggregation, all the nodes transmit information to the cluster heads which forward the messages to the controller, then in the process of dissemination, all the cluster heads and the debatable nodes broadcast the clustering result, thus the upper bound for the number of broadcast is $N+m+n$.
 
@@
 We increase the primary users' activity by importing 20 batches of PUs sequentially in the CRN, where each batch includes 10 PUs. 
-
+%
 Figure~\ref{singleton_clusters_100} and \ref{singleton_clusters_200} show that when $N=100$ and 200, compared with the variants of ROSS, more unclustered CR nodes are generated by SOC.
@@
 In this paper we investigate the robust clustering problem in CRN extensively and propose both centralized and distributed clustering solutions.
-%generate robust clusters against primary users' influence, so that more CR users can benefit from operative decision making provided by the clusters.
-We provide the mathematical description of the problem and prove the NP hardness of it.
-The proposed clustering schemes generate clusters which have long time expectancy against the primary users' activity, besides, the proposed schemes generate clusters which have desired sizes.
+We give the mathematical description of the problem and prove the NP hardness of it.
+The proposed clustering schemes generate clusters which have long life expectancy against the primary users' activity, and the generated clusters have similar sizes with the desired one.
 %The congestion game model in game theory is used to design the distributed schemes.
 %A Light weighted clustering scheme ROSS is also proposed.
-Through simulation and theoretical analysis, we find that the distributed schemes achieve similar performance with the centralized scheme in terms of cluster robustness, signaling overhead and cluster sizes, and outperform the comparison distributed scheme on the above mentioned metrics.
+Through simulation, the distributed schemes demonstrate similar performance with the centralized scheme in terms of cluster robustness, signaling overhead and cluster sizes, and outperform the comparison distributed scheme on all metrics.
 
@@
 
-In this example, node $\omega$ is at the tail of the list.
+In this example, node $\omega$ is at the tail of a list.
 As $\omega$ does not have neighboring nodes with lower individual connectivity degree, $\omega$ becomes a cluster head.
 Then $\omega$ incorporates all its one-hop neighbours (here we assume that every newly formed cluster has common channels), including the nodes which precede $\omega$ in the list.
-The nodes which join a cluster set their individual connection degrees to $M$, which enables the node immediately precede in the list to become a cluster head.
-In this way, cluster heads are generated from the tail of list to the head of the list, and all the nodes in the list are in at least one cluster, which contradicts the assumption that $\alpha$ is not included in any cluster.
+The nodes which join a cluster set their individual connection degrees to $M$, which makes the node immediately precede in the list to become a cluster head.
+In this way, cluster heads are generated from the tail to the head in the list, and every node in the list is in at least one cluster, which contradicts the assumption that $\alpha$ is not included in any cluster.
 
@@
 \end{itemize}
-The number of steps is dependent on $\mathcal{I}$, which is between 1 and $N^2$
-
-%We have found the polynomial algorithm $\sigma$ which transforms an instance of weighted $k$-set packing to an instance of the robust clustering problem in CRN.
-Assume we have a robust clustering black box which can check whether the clustering instance meets the requirement, \ie clusters are not overlapping and the total sum of CCs exceed $\lambda$ or not.
+The number of steps is dependent on $\mathcal{I}$, which is between 1 and $N^2$.
+%
+Assume we have a robust clustering black box which checks whether the clustering instance meets the requirement, \ie clusters are not overlapping and the total sum of CCs exceeds $\lambda$ or not.
 If \textit{yes} is said, then the total weight of the corresponding instance of the maximum weighted k-set packing problem is greater than $\lambda$.
-If the black box said \textit{no}, either due to overlapping clusters, or the sum of CCs over all clusters is smaller than $\lambda$, the corresponding instance of the packing problem is not an solution.
+If the black box says \textit{no}, either due to overlapping clusters or the sum of CCs is smaller than $\lambda$, the corresponding instance of the packing problem is not a solution.
 

### 2017-04-10 journal-draft/ettdoc.tex
add one reference

@@
 
-\def\volumeyear{2012}
+\def\volumeyear{2017}
 
@@
 \captionsetup[table]{format=plain,labelformat=simple,labelsep=period}%
+%\usepackage{authblk}
 
@@
 
-\runningheads{A.~N.~Other}{A demonstration of the \journalabb\
-class file}
+%\runningheads{A.~N.~Other}{A demonstration of the \journalabb\
+%class file}
 
@@
 \title{Robust Clustering for Ad Hoc Cognitive Radio Network}
-
+%\author[1]{Di Li\thanks{li@umic.rwth-aachen.de}}
+%\author[2]{Erwin Fang\thanks{xx}}
+%\author[3]{James Gross}
 \author{Di Li, Erwin Fang, James Gross\corrauth}
-
+%\affil[1]{RWTH Aachen University}
+%\affil[2]{ETH Zurich}
+%\affil[3]{KTH Royal Institute of Technology}
 \address{RWTH Aachen University, ETH Zurich, KTH Royal Institute of Technology }
-
+%\renewcommand\Authands{ and }
 \corraddr{Communication Theory Lab
-School of Electrical Engineering
+School of Electrical Engineering, 
 KTH Royal Institute of Technology
@@
 %CR concept
-Cognitive radio (CR) is a promising technology to solve the spectrum scarcity problem~\cite{Mitola}.
+Cognitive radio (CR) is a promising technology to solve the spectrum scarcity problem for the upcomging era of internet of things~\cite{Mitola, Rawat20161}.
 Licensed users access the spectrum allocated to them whenever there is information to be transmitted.

### 2017-04-11 journal-draft/ettdoc.tex
author symbol

@@
 \usepackage{caption}% http://ctan.org/pkg/caption
-\captionsetup[table]{format=plain,labelformat=simple,labelsep=period}%
+\captionsetup[table]{format=plain,labelformat=simple,labelsep=period}
 %\usepackage{authblk}
@@
 %\author[3]{James Gross}
-\author{Di Li, Erwin Fang, James Gross\corrauth}
+\author{Di Li\textsuperscript{1}, Erwin Fang\textsuperscript{2}, James Gross\textsuperscript{3}\corrauth}
 %\affil[1]{RWTH Aachen University}
@@
 %\affil[3]{KTH Royal Institute of Technology}
-\address{RWTH Aachen University, ETH Zurich, KTH Royal Institute of Technology }
+\address{RWTH Aachen University\textsuperscript{1}, ETH Zurich\textsuperscript{2}, KTH Royal Institute of Technology\textsuperscript{3} }
 %\renewcommand\Authands{ and }

### 2017-04-16 journal-draft/ettdoc.tex
comment out ack
modify typos

@@
 \begin{abstract}
-Cluster structure in cognitive radio networks facilitates cooperative spectrum sensing, routing and other functionalities.
+Cluster structure in cognitive radio networks facilitates cooperative spectrum sensing, routing and other functionality.
 The unlicensed channels which are available for a group of cognitive radio users, consolidate the group into a cluster and the number of the available unlicensed channels decides that cluster's robustness against the licensed users' influence.
@@
 We give a formal description of the robust clustering problem, prove it to be NP-hard and propose both centralized and distributed solutions.
-The congestion game model is adopted to analyse the process of cluster formation, which not only contributes the design of the distributed clustering scheme, but also provides the guarantee on the convergence into Nash Equilibrium and the convergence speed.
+The congestion game model is adopted to analyze the process of cluster formation, which not only contributes the design of the distributed clustering scheme, but also provides the guarantee on the convergence into Nash Equilibrium and the convergence speed.
 %Our proposed clustering solution is versatile to fulfill some other requirements such as faster convergence and cluster size control.
@@
 \label{clustering:phaseII:game}
-Game theory is a powerful mathematical tool for studying, modelling and analysing the interactions among individuals.
+Game theory is a powerful mathematical tool for studying, modeling and analyzing the interactions among individuals.
 A game consists of three elements: a set of players, a selfish utility for each player, and a feasible strategy space for each player.
@@
 %The number of CR is 100, 200 and 300, and the average number of neighbours of each CR is 9.5, 20, and 31.
-The desired sizes adopted are listed in the Table~\ref{Simulation_para}, which is about 60\% of the average number of neighbours.
+The desired sizes adopted are listed in the Table~\ref{Simulation_para}, which is about 60\% of the average number of neighbors.
 %When run ROSS, the parameter $t$ which is used to control cluster size in phase I is 1.3.
@@
 Number of CRs			& 100 	&  200 					& 300 \\ \hline
-Average num. of neighbours 	&9.5	&   20		& 31  \\ \hline
+Average num. of neighbors 	&9.5	&   20		& 31  \\ \hline
 Desired size $\delta$ 	& 6	&   12 						& 20      \\ \hline
@@
 %
-From Figure~\ref{singleton_clusters_100} to~\ref{singleton_clusters_300}, we can see that significantly less unclustered CR nodes are generated by the variants of ROSS whcih have size control mechanism.
+From Figure~\ref{singleton_clusters_100} to~\ref{singleton_clusters_300}, we can see that significantly less unclustered CR nodes are generated by the variants of ROSS which have size control mechanism.
 Besides, the greedy mechanism moderately strengthens the robustness of the clusters.
@@
 \end{algorithm}
-
-% use section* for acknowledgment
 
@@
 If $\beta$ becomes cluster head, node $\alpha$ is included, the assumption is not true.
-If $\beta$ is not a cluster head, then $\beta$ is not in any cluster, we can repeat the previous analysis made on node $\alpha$, and deduce that node $\beta$ has at least one neighbouring node $\gamma$ with $d_{\gamma} < d_{\beta}$.
+If $\beta$ is not a cluster head, then $\beta$ is not in any cluster, we can repeat the previous analysis made on node $\alpha$, and deduce that node $\beta$ has at least one neighboring node $\gamma$ with $d_{\gamma} < d_{\beta}$.
 % (COMMENT: $\beta$ not being a cluster head and $\beta$ not belonging to any cluster is not the same statement!!! ANSWER(Di): I add some more words)
@@
 As $\omega$ does not have neighboring nodes with lower individual connectivity degree, $\omega$ becomes a cluster head.
-Then $\omega$ incorporates all its one-hop neighbours (here we assume that every newly formed cluster has common channels), including the nodes which precede $\omega$ in the list.
+Then $\omega$ incorporates all its one-hop neighbors (here we assume that every newly formed cluster has common channels), including the nodes which precede $\omega$ in the list.
 The nodes which join a cluster set their individual connection degrees to $M$, which makes the node immediately precede in the list to become a cluster head.
@@
 
-\ack This class file was developed by Sunrise Setting Ltd,
-Paignton, Devon, UK. Website:\\
-\href{http://www.sunrise-setting.co.uk}{\texttt{www.sunrise-setting.co.uk}}
+%\ack This class file was developed by Sunrise Setting Ltd,
+%Paignton, Devon, UK. Website:\\
+%\href{http://www.sunrise-setting.co.uk}{\texttt{www.sunrise-setting.co.uk}}
 

### 2017-04-16 journal-draft/ettdoc.tex
expand 4.1.3. Cluster Size Control in Dense CRN

@@
 \label{ross_p2_cluster_pruning}
-
-%In this subsection, we illustrate the pressing necessity to control the cluster size when CRN becomes denser.
-%
-%We consider a cluster $C(i)$ where $i$ is the cluster head in a dense CRN. 
-%To make the analysis easier, we assume there is no cluster heads which are generated within $i$'s neighborhood during the procedure of guaranteeing CCs.
-%Assuming the CR users and PUs are evenly distributed and PUs occupy the licensed channels randomly, then both CR nodes density and channel availability in the CRN can be seen to be spatially homogeneous.
-%In this case the formed clusters are decided by the transmission range and network density.
-%According to Algorithm~\ref{alg0}, the nearest cluster heads could locate just outside node $i$'s transmission range.
-%%
-%An instance of this situation is shown in Figure~\ref{clusters_denseNetwork}.
-%In the figure, black dots represent cluster heads, the circles denote the transmission ranges of cluster heads.
-%Cluster members are not shown in the figure.
-%%Circles represent the transmission range of cluster head, within which CR nodes are absorbed in cluster.
-%\begin{figure}[h!]
-%  \centering
-%  \includegraphics[width=0.3\linewidth]{clusters_denseNetwork_2.pdf}
-%  \caption{Clusters formation in extremely dense CRN. Black dots are cluster heads, cluster members are not drawn.}
-%  \label{clusters_denseNetwork}
-%\end{figure}
-%Let $l$ be the length of side of simulation plan square, and $r$ be CR's transmission radius.
-%Based on the aforementioned analysis and geometry illustration as shown in Figure~\ref{clusters_denseNetwork}, we give an estimate on the maximum number of generated clusters, which is the product of the number of cluster heads in one row and that number in one line, $l/r * l/r = l^2/r^2$.
-%%Now we verify the estimation with simulation.
-%%We distribute CR and primary users randomly on a square plain, $r$=10 and $l$=50.
-%%Network density is increased by adding more CR users.
-%%We now have a look at how does the network density affect the cluster size when the transmission range is constant.
-%%This implicates when the cluster size is decided by the density of the network.
-%%As to SOC, the membership of one cluster is decided after a complex process, and the cluster size is roughly the same with one neighborhood.xxxx
-%%We can see from the example that although two neighbouring clusters can overlap greatly with each other, no cluster head will be covered by other clusters.
-%Given $r$=10 and $l$=50, the maximum number of clusters is 25.
-%The number of clusters in the simulation is shown in Figure~\ref{number_clusters_scale}.
-%Simulation is run for 50 times and the confidence interval is 95\%.
-%With the increase of CR users, network density (the average number of neighbours) increases linearly, and the number of clusters approaches to 25 which complies with the estimation.
-%
-%\begin{figure}[h]
-%  \centering
-%  \includegraphics[width=0.7\linewidth]{number_clusters_upperBound.pdf}
-%  \caption{The correlation between the number of formed clusters and network density.}
-%  \label{number_clusters_scale}
-%\end{figure}
-It is necessary to control the cluster size when CRN becomes denser.
-Both analysis and simulation~\cite{robust_clustering_arxiv} show that when applying ROSS, after the clusters are saturated with the increase of network density, the cluster size increases linearly with the network density, thus certain measures are needed to curb this problem.
-This task falls upon the cluster heads.
+In this subsection, we illustrate the pressing necessity to control the cluster size when CRN becomes denser.
+We consider a cluster $C(i)$ where $i$ is the cluster head in a dense CRN. 
+To make the analysis easier, we assume there is no cluster heads which are generated within $i$'s neighborhood during the procedure of guaranteeing CCs.
+Assuming the CR users and PUs are evenly distributed and PUs occupy the licensed channels randomly, then both CR nodes density and channel availability in the CRN can be seen to be spatially homogeneous.
+In this case the formed clusters are decided by the transmission range and network density.
+According to Algorithm~\ref{alg0}, the nearest cluster heads could locate just outside node $i$'s transmission range.
+%
+An instance of this situation is shown in Figure~\ref{clusters_denseNetwork}.
+In the figure, black dots represent cluster heads, the circles denote the transmission ranges of cluster heads.
+Cluster members are not shown in the figure.
+%Circles represent the transmission range of cluster head, within which CR nodes are absorbed in cluster.
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.3\linewidth]{clusters_denseNetwork_2.pdf}
+  \caption{Clusters formation in extremely dense CRN. Black dots are cluster heads, cluster members are not drawn.}
+  \label{clusters_denseNetwork}
+\end{figure}
+Let $l$ be the length of side of simulation plan square, and $r$ be CR's transmission radius.
+Based on the aforementioned analysis and geometry illustration as shown in Figure~\ref{clusters_denseNetwork}, we give an estimate on the maximum number of generated clusters, which is the product of the number of cluster heads in one row and that number in one line, $l/r * l/r = l^2/r^2$.
+%Now we verify the estimation with simulation.
+%We distribute CR and primary users randomly on a square plain, $r$=10 and $l$=50.
+%Network density is increased by adding more CR users.
+%We now have a look at how does the network density affect the cluster size when the transmission range is constant.
+%This implicates when the cluster size is decided by the density of the network.
+%As to SOC, the membership of one cluster is decided after a complex process, and the cluster size is roughly the same with one neighborhood.xxxx
+%We can see from the example that although two neighbouring clusters can overlap greatly with each other, no cluster head will be covered by other clusters.
+Given $r$=10 and $l$=50, the maximum number of clusters is 25.
+The number of clusters in the simulation is shown in Figure~\ref{number_clusters_scale}.
+Simulation is run for 50 times and the confidence interval is 95\%.
+With the increase of CR users, network density (the average number of neighbours) increases linearly, and the number of clusters approaches to 25 which complies with the estimation.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.7\linewidth]{number_clusters_upperBound.pdf}
+  \caption{The correlation between the number of formed clusters and network density.}
+  \label{number_clusters_scale}
+\end{figure}
+
+Both analysis and simulation show that when applying ROSS, after the clusters are saturated with the increase of network density, the cluster size increases linearly with the network density, thus certain measures are needed to curb this problem.
+This task falls to the cluster heads.
 To control the cluster size, cluster heads prune their cluster members to reach the desired cluster size.
@@
 Hence, a cluster head excludes some cluster members when the cluster size exceeds $t\cdot \delta$, where constant parameter $t$ is dependent on the network density and CR nodes' transmission range and $t>1$.
-In particular, the cluster head removes the cluster members sequentially according to the following principle, the absence of one cluster member leads to the maximum increase of the CCs within the cluster.
+In particular, the cluster head removes the cluster members sequentially according to the following principle, the absence of one cluster member leads to the maximum increase of common channels within the cluster.
 This process ends when each cluster's size is smaller or equal to $t \cdot\delta$.
-This procedure is similar with that in Section~\ref{ross_p1_guarantee_ccc}, thus Algorithm~\ref{alg_size_control_available_CCC} can be reused.
+ %delta needs to be changed, f(delta) XXXXXXX
+This procedure is similar with guaranteeing the existence of CCs in cluster, thus can reuse Algorithm~\ref{alg_size_control_available_CCC}.
 The $t$ is set to 1.3.
@@
   \includegraphics[width=0.5\linewidth]{figure2.pdf}
-  \caption{Clusters formation after the phase I of ROSS. Nodes $A, B, D$ are debatable nodes as they belong to multiple clusters.}
+  \caption{Clusters formation after the phase I of ROSS. CR nodes $A, B, D$ are debatable nodes as they belong to multiple clusters.}
   \label{fig2}

### 2017-04-16 journal-draft/ettdoc.tex
modify the title of 4.1.3
delete the headers, change the authors

@@
-% ettdoc.tex V2.10, 19 June 2012
-
-\documentclass[times]{ettauth}
-\usepackage[toc,page]{appendix}
-\usepackage{moreverb}
-
-\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
-
-\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
-T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-
-\def\volumeyear{2017}
-
-\newcommand{\eg}{e.g., }
-\newcommand{\ie}{i.e., }
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\argmax}{arg\,max}
-
-\usepackage{times}
-%\usepackage{mathptmx}
-\usepackage{mathtools}
-\usepackage[draft,nomargin,marginclue,footnote,silent]{fixme}
-\setcounter{tocdepth}{2} %table of contents
-
-\theoremstyle{mytheoremstyle}
-\newtheorem{theorem}{Theorem}[section]
-
-\theoremstyle{mytheoremstyle}
-\newtheorem{corollary}{Corollary}[section]
-
-\theoremstyle{mytheoremstyle}
-\newtheorem{lemma}{Lemma}[section]
-
-\newtheorem{mydef}{Definition}
-
-\DeclareMathOperator*{\Max}{Max}
-\DeclareMathOperator*{\Min}{Min}
-
-\newcommand{\bigO}{\ensuremath{\mathcal{O}}}% big-O notation/symbol
-\usepackage{subfigure}
-\usepackage{adjustbox}
-\usepackage{multirow}
-\usepackage{enumitem}
-\usepackage{lipsum}
-\setlist[itemize]{leftmargin=*}
-\setlist[enumerate]{wide=\parindent}
-\usepackage[referable]{threeparttablex}
-\renewlist{tablenotes}{enumerate}{1}
-\makeatletter
-\setlist[tablenotes]{label=\tnote{\alph*},ref=\alph*,itemsep=\z@,topsep=\z@skip,partopsep=\z@skip,parsep=\z@,itemindent=\z@,labelindent=\tabcolsep,labelsep=.2em,leftmargin=*,align=left,before={\footnotesize}}
-\makeatother
-
+% to do : add more notations
+% the new notation t.
+\documentclass[10pt,journal,compsoc]{IEEEtran}
+%
+% If IEEEtran.cls has not been installed into the LaTeX system files,
+% manually specify the path to it like:
+% \documentclass[journal,comsoc]{../sty/IEEEtran}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% copied from thesis
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Packages für Formeln %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage[colorlinks,
+            linkcolor=red,
+            anchorcolor=blue,
+            citecolor=green
+            ]{hyperref}
+\usepackage{amsmath}
+\usepackage{amsthm}
+%\usepackage{amsfonts}
+\usepackage{amssymb}
+\usepackage{booktabs}
+\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
+
+%% Packages
+%\usepackage{tikz}
+%\usetikzlibrary{shapes,arrows}
+%\usetikzlibrary{positioning}
 \usepackage{graphicx}
@@
 \usepackage{multicol}
+%\usepackage{colortbl}
+%\usepackage{todonotes}	
+\newcounter{todocounter}
+\newcommand{\todonum}[2][]
+{\stepcounter{todocounter}\todo[inline,backgroundcolor=blue!10!white, #1]{\thetodocounter: #2}}
+
+%% Zeilenabstand %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage{setspace}
+%\singlespacing        %% 1-zeilig (Standard)
+%\onehalfspacing       %% 1,5-zeilig
+%\doublespacing        %% 2-zeilig
 
@@
 \newcolumntype{L}[1]{>{\raggedright\arraybackslash}m{#1}}
+
 % Table spacings
@@
 \usepackage{caption}% http://ctan.org/pkg/caption
-\captionsetup[table]{format=plain,labelformat=simple,labelsep=period}
-%\usepackage{authblk}
+\captionsetup[table]{format=plain,labelformat=simple,labelsep=period}%
+
+\newtheoremstyle{mytheoremstyle} % name
+        {\topsep}                    % Space above
+        {\topsep}                    % Space below
+        {\itshape\fontfamily{ptm}\selectfont}                   % Body font, ptm is times new roma
+        {}                           % Indent amount
+        {\fontfamily{ptm}\selectfont\scshape\color{black}\bfseries}                   % Theorem head font
+        {:}                          % Punctuation after theorem head
+        {.5em}                       % Space after theorem head
+        {}  % Theorem head spec (can be left empty, meaning ‘normal’)
+
+\theoremstyle{mytheoremstyle}
+\newtheorem{theorem}{Theorem}[section]
+
+\theoremstyle{mytheoremstyle}
+\newtheorem{corollary}{Corollary}[section]
+
+\theoremstyle{mytheoremstyle}
+\newtheorem{lemma}{Lemma}[section]
+
+%\theoremstyle{mytheoremstyle}
+%\let\definition\relax
+\newtheorem{mydef}{Definition}%[section]
+
+%%%%%%
+%%%%%% Proof
+    \makeatletter
+    \renewenvironment{proof}[1][\proofname]{%
+      \par\pushQED{\qed}\fontfamily{ptm}\selectfont%
+      \topsep6\p@\@plus6\p@\relax
+      \trivlist\item[\hskip\labelsep\bfseries#1\@addpunct{.}]%
+      \ignorespaces
+    }{%
+      \popQED\endtrivlist\@endpefalse
+    }
+    \makeatother 
+%%%%%%%%%%%%%%%%%
+
+\newcommand{\eg}{e.g., }
+\newcommand{\ie}{i.e., }
+\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
+%\usepackage{algorithmic}
+\usepackage{times}
+%\usepackage{mathptmx}
+\usepackage{mathtools}
+\usepackage[draft,nomargin,marginclue,footnote,silent]{fixme}
+\setcounter{tocdepth}{2} %table of contents
+
+\makeatother
+\usepackage{comment}
+\newcommand{\Tau}{\mathrm{T}}
+\usepackage[colorinlistoftodos]{todonotes}
+\DeclareMathOperator*{\Max}{Max}
+\DeclareMathOperator*{\Min}{Min}
+
+\newcommand{\bigO}{\ensuremath{\mathcal{O}}}% big-O notation/symbol
+\usepackage{subfigure}
+\usepackage{adjustbox}
+\usepackage{multirow}
+\usepackage{enumitem}
+\usepackage{lipsum}
+\setlist[itemize]{leftmargin=*}
+\usepackage[referable]{threeparttablex}
+\renewlist{tablenotes}{enumerate}{1}
+\makeatletter
+\setlist[tablenotes]{label=\tnote{\alph*},ref=\alph*,itemsep=\z@,topsep=\z@skip,partopsep=\z@skip,parsep=\z@,itemindent=\z@,labelindent=\tabcolsep,labelsep=.2em,leftmargin=*,align=left,before={\footnotesize}}
+\makeatother
+%%%%%%%%%%%%%%%%%%%%%%%%%% copied from thesis
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\usepackage[T1]{fontenc}% optional T1 font encoding
+
+% *** GRAPHICS RELATED PACKAGES ***
+%
+\ifCLASSINFOpdf
+  % \usepackage[pdftex]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../pdf/}{../jpeg/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+\else
+  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
+  % will default to the driver specified in the system graphics.cfg if no
+  % driver is specified.
+  % \usepackage[dvips]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../eps/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.eps}
+\fi
+% graphicx was written by David Carlisle and Sebastian Rahtz. It is
+% required if you want graphics, photos, etc. graphicx.sty is already
+% installed on most LaTeX systems. The latest version and documentation
+% can be obtained at: 
+% http://www.ctan.org/pkg/graphicx
+% Another good source of documentation is "Using Imported Graphics in
+% LaTeX2e" by Keith Reckdahl which can be found at:
+% http://www.ctan.org/pkg/epslatex
+%
+% latex, and pdflatex in dvi mode, support graphics in encapsulated
+% postscript (.eps) format. pdflatex in pdf mode supports graphics
+% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
+% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
+% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
+% which can result in "jaggedy"/blurry rendering of lines and letters as
+% well as large increases in file sizes.
+%
+% You can find documentation about the pdfTeX application at:
+% http://www.tug.org/applications/pdftex
+
+% *** MATH PACKAGES ***
+%
+\usepackage{amsmath}
+% A popular package from the American Mathematical Society that provides
+% many useful and powerful commands for dealing with mathematics.
+% Do NOT use the amsbsy package under comsoc mode as that feature is
+% already built into the Times Math font (newtxmath, mathtime, etc.).
+% 
+% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
+% thus preventing page breaks from occurring within multiline equations. Use:
+\interdisplaylinepenalty=2500
+% after loading amsmath to restore such page breaks as IEEEtran.cls normally
+% does. amsmath.sty is already installed on most LaTeX systems. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/pkg/amsmath
+
+% Select a Times math font under comsoc mode or else one will automatically
+% be selected for you at the document start. This is required as Communications
+% Society journals use a Times, not Computer Modern, math font.
+%\usepackage[cmintegrals]{newtxmath}
+\usepackage{txfonts}
+% The freely available newtxmath package was written by Michael Sharpe and
+% provides a feature rich Times math font. The cmintegrals option, which is
+% the default under IEEEtran, is needed to get the correct style integral
+% symbols used in Communications Society journals. Version 1.451, July 28,
+% 2015 or later is recommended. Also, do *not* load the newtxtext.sty package
+% as doing so would alter the main text font.
+% http://www.ctan.org/pkg/newtx
+%
+% Alternatively, you can use the MathTime commercial fonts if you have them
+% installed on your system:
+%\usepackage{mtpro2}
+%\usepackage{mt11p}
+%\usepackage{mathtime}
+
+%\usepackage{bm}
+% The bm.sty package was written by David Carlisle and Frank Mittelbach.
+% This package provides a \bm{} to produce bold math symbols.
+% http://www.ctan.org/pkg/bm
+
+% correct bad hyphenation here
+\hyphenation{op-tical net-works semi-conduc-tor}
+\DeclareMathOperator*{\argmin}{arg\,min}
+\DeclareMathOperator*{\argmax}{arg\,max}
 
 \begin{document}
-
-%\runningheads{A.~N.~Other}{A demonstration of the \journalabb\
-%class file}
-
-\articletype{RESEARCH ARTICLE}
-
-\title{Robust Clustering for Ad Hoc Cognitive Radio Network}
-%\author[1]{Di Li\thanks{li@umic.rwth-aachen.de}}
-%\author[2]{Erwin Fang\thanks{xx}}
-%\author[3]{James Gross}
-\author{Di Li\textsuperscript{1}, Erwin Fang\textsuperscript{2}, James Gross\textsuperscript{3}\corrauth}
-%\affil[1]{RWTH Aachen University}
-%\affil[2]{ETH Zurich}
-%\affil[3]{KTH Royal Institute of Technology}
-\address{RWTH Aachen University\textsuperscript{1}, ETH Zurich\textsuperscript{2}, KTH Royal Institute of Technology\textsuperscript{3} }
-%\renewcommand\Authands{ and }
-\corraddr{Communication Theory Lab
-School of Electrical Engineering, 
-KTH Royal Institute of Technology
-SE - 100 44 Stockholm\\Email: james.gross@ee.kth.se}
-
+%
+% paper title
+% Titles are generally capitalized except for words such as a, an, and, as,
+% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
+% not capitalized unless they are the first or last word of the title.
+% Linebreaks \\ can be used within to get better formatting as desired.
+% Do not put math or special symbols in the title.
+\title{Versatile Robust Clustering of Ad Hoc Cognitive Radio Network}
+%
+%
+% author names and IEEE memberships
+% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
+% a structure at a ~ so this keeps an author's name from being broken across
+% two lines.
+% use \thanks{} to gain access to the first footnote area
+% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
+% was not built to handle multiple paragraphs
+%
+
+\author{Di~Li,~\IEEEmembership{Member,~IEEE,}
+        Erwin~Fang,
+        and James~Gross,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
+\thanks{D. Li (li@umic.rwth-aachen.de) was with RWTH Aachen university where this work is conducted.}% <-this % stops a space
+\thanks{Erwin. Fang was with ETH, Switzerland when this work is conducted.}% <-this % stops a space
+\thanks{J. Gross (james.gross@ee.kth.se) is with KTH Royal Institute of Technology, Sweden.}% <-this % stops a space
+%\thanks{Manuscript received xxxx xx, 20xx; revised xxxx xx, 20xx.}
+}
+
+% note the % following the last \IEEEmembership and also \thanks - 
+% these prevent an unwanted space from occurring between the last author name
+% and the end of the author line. i.e., if you had this:
+% 
+% \author{....lastname \thanks{...} \thanks{...} }
+%                     ^------------^------------^----Do not want these spaces!
+%
+% a space would be appended to the last name and could cause every name on that
+% line to be shifted left slightly. This is one of those "LaTeX things". For
+% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
+% "AB" then you have to do: "\textbf{A}\textbf{B}"
+% \thanks is no different in this regard, so shield the last } of each \thanks
+% that ends a line with a % and do not let a space in before the next \thanks.
+% Spaces after \IEEEmembership other than the last one are OK (and needed) as
+% you are supposed to have spaces between the names. For what it is worth,
+% this is a minor point as most people would not even notice if the said evil
+% space somehow managed to creep in.
+
+% The paper headers
+%\markboth{Journal of xxxxx,~Vol.~xx, No.~x, xxxx~20xx}%
+%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Communications Society Journals}
+% The only time the second header will appear is for the odd numbered pages
+% after the title page when using the twoside option.
+% 
+% *** Note that you probably will NOT want to include the author's ***
+% *** name in the headers of peer review papers.                   ***
+% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
+% you desire.
+
+% If you want to put a publisher's ID mark on the page you can do it like
+% this:
+%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
+% Remember, if you use this you must call \IEEEpubidadjcol in the second
+% column for its text to clear the IEEEpubid mark.
+
+% use for special paper notices
+%\IEEEspecialpapernotice{(Invited Paper)}
+
+% make the title area
+\maketitle
+
+% As a general rule, do not put math, special symbols or citations
+% in the abstract or keywords.
 \begin{abstract}
-Cluster structure in cognitive radio networks facilitates cooperative spectrum sensing, routing and other functionality.
-The unlicensed channels which are available for a group of cognitive radio users, consolidate the group into a cluster and the number of the available unlicensed channels decides that cluster's robustness against the licensed users' influence.
-This paper analyses the problem of how to form robust clusters in cognitive radio network, so that more cognitive radio users can get the benefits from cluster structure when the primary users' operation becomes more intense.
+Cluster structure in cognitive radio networks facilitates cooperative spectrum sensing, routing and other functionalities.
+The unlicensed channels, which are available for every member of a group of cognitive radio users, consolidate the group into a cluster, and the availability of unlicensed channels decides the robustness of that cluster against the licensed users' influence.
+%Thus there should be more unlicensed channels in the clusters.
+This paper analyses the problem that how to form robust clusters in cognitive radio network, so that more cognitive radio users can get benefits from cluster structure even when the primary users' operation are intense.
 %In the process of forming clusters, every secondary user decides with whom to form a cluster, or which cluster to join.
-We give a formal description of the robust clustering problem, prove it to be NP-hard and propose both centralized and distributed solutions.
-The congestion game model is adopted to analyze the process of cluster formation, which not only contributes the design of the distributed clustering scheme, but also provides the guarantee on the convergence into Nash Equilibrium and the convergence speed.
-%Our proposed clustering solution is versatile to fulfill some other requirements such as faster convergence and cluster size control.
-The proposed distributed clustering scheme outperforms the related works in terms of cluster robustness, convergence speed and overhead.
+We provide a formal description of robust clustering problem, prove it to be NP-hard and propose a centralized solution, besides, a distributed solution is proposed to suit the dynamics in the ad hoc cognitive radio network.
+Congestion game model is adopted to analyse the process of cluster formation, which not only contributes designing the distributed clustering scheme directly, but also provides the guarantee of convergence into Nash Equilibrium and convergence speed.
+Our proposed clustering solution is versatile to fulfill some other requirements such as faster convergence and cluster size control.
+The proposed distributed clustering scheme outperforms the related work in terms of cluster robustness, convergence speed and overhead.
 %Besides, we prove the clustering problem is NP-hard, and also propose the centralized solution.
-The extensive simulation is conducted, which clearly supports our claims.
+The extensive simulation supports our claims.
 \end{abstract}
 
-%\keywords{class file; \LaTeXe; \emph{\journalabb}}
-
-\maketitle
+% Note that keywords are not normally used for peerreview papers.
+\begin{IEEEkeywords}
+cognitive radio, robust cluster, game theory, congestion game, distributed, centralized, cluster size control.
+\end{IEEEkeywords}
+
+% For peer review papers, you can put extra information on the cover
+% page as needed:
+% \ifCLASSOPTIONpeerreview
+% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
+% \fi
+%
+% For peerreview papers, this IEEEtran command inserts a page break and
+% creates the second title. It will be ignored for other modes.
+\IEEEpeerreviewmaketitle
+
 \graphicspath{
@@
 %CR concept
-Cognitive radio (CR) is a promising technology to solve the spectrum scarcity problem for the upcomging era of internet of things~\cite{Mitola, Rawat20161}.
+\IEEEPARstart{C}{ognitive} radio (CR) is a promising technology to solve the spectrum scarcity problem~\cite{Mitola}.
 Licensed users access the spectrum allocated to them whenever there is information to be transmitted.
@@
 Regarding the operation of CRN, efficient spectrum sensing is identified to be critical for a smooth operation of a cognitive radio network~\cite{Sahai_FundamentalDesignTradeoffs2006}.
-Efficient spectrum sensing can be achieved by cooperative spectrum sensing of multiple secondary users, which has been shown to cope effectively with noise uncertainty and channel fading, thus remarkably improving the sensing accuracy~\cite{coorperativeSensing_Akyildiz11}.
+This can be achieved by cooperative spectrum sensing of multiple secondary users, which has been shown to cope effectively with noise uncertainty and channel fading, thus remarkably improving the sensing accuracy~\cite{coorperativeSensing_Akyildiz11}.
 Collaborative sensing relies on the consensus of CR users\footnote{The terms user and node appear interchangeably in this paper.
-In particular, user is adopted when its networking or cognitive ability are discussed or stressed, while we refer node typicallly in the context of the topology.} within a certain area, in this regard, clustering is regarded as an effective method to realize cooperative spectrum sensing~\cite{Sun07_clustering_spectrum_secsing}.
+In particular, user is adopted when its networking or cognitive ability are discussed or stressed, while we refer node typicallly in the context of the topology.} within a certain area, in this regard, clustering is regarded as an effective method to realize cooperative spectrum sensing~\cite{Sun07_clustering_spectrum_secsing, Zhao07}.
 % ... decreases considerably the negative probability due to the random channel effects like fading and shadowing.
-Clustering is a process of grouping certain users in geographic proximity into a collective.
-In the context of cognitive radio netowrks, a formed cluster helps the participants not only improve the spectrum sensing accuracy, but also coordinate the channel switch operation when the primary users are detected by at least one secondary user in that cluster, then all the cluster menmbers can stop payload transmission swiftly and vacate the operating channel ~\cite{willkomm08}.
-Clustering also benefits the operation of a CRN by reducing the interference between cognitive clusters~\cite{centralizedSharing80222}, and supporting routing~\cite{Abbasi_survey_07}.
+Clustering is a process of grouping certain users in a proximity into a collective.
+Clustering is also efficient to coordinate the channel switch operation when primary users are detected by at least one CR node residing in the cluster.
+The cluster head can enable all the CR devices within the same cluster to stop payload transmission swiftly on the operating channel and to vacate the channel ~\cite{willkomm08}.
+%
 %As to the coexistence of CR users, they can be notified by cluster head (CH) or other cluster members about the possible collision, the possibility for them to interfere neighbouring clusters is reduced~\cite{centralizedSharing80222}.
-Except for benefiting the dynamic spectrum sharing in CRN, clustering contributes to the other wireless networks in many aspects, which has already been discussed in many works.
+In addition to the collaborate sensing advantage, the use of clusters is beneficial as it reduces the interference between cognitive clusters~\cite{centralizedSharing80222}.
+Clustering algorithm has also been proposed to support routing in cognitive radio networks ~\cite{Abbasi_survey_07}.
 
@@
 
-In CRN, clusters are formed in the very beginning of the network operation, and re-formed periodically according to the dynamics of the CRN.
+Clusters are formed in the very beginning of the network operation, and re-formed periodically according to the dynamics of the CRN.
 Each formed cluster has one or multiple unlicensed channels which are available for every CR node in the cluster.
@@
 When one or several cluster members can not access one certain CC on which primary user activity is detected, the channel will be excluded from the set of CCs.
-In particular, if that channel is being used for payload communication, the communication pair will stop and resume the transmission on another available CC.
+In particular, if that channel is being used for payload communication, the communication pair will stop and resume the transmission on another available channel from CCs.
 The availability of CCs within a cluster defines the existence of that cluster, \ie no CCs are available means the corresponding cluster doesn't exist.
 %As long as there is a CC available, the corresponding cluster can continue to exchange payload data.
-In the context of CRN, the activity of primary users is usually unknown to the secondary users, then the primary users' activity is deemed as random.
-In this case, the cluster which secures more CCs will anticipate a longer life expectancy, in other words, is more robust.
-It is obvious that fewer secondary users in one cluster yield more CCs, but this contradicts to one of the motivations of clustering, \ie the cooperative decision making, where more users result in more accurate sensing result~\cite{Consensus_based_clustering12}.
-Thus the number of small clusters, especially the \textit{singleton clusters}, \ie the cluster which has only one CR node, should be minimized.
-As to the cluster which consists of many nodes, although the spectrum sensing is benefited, it usually leads to less common channels, which undermines the robustness of the cluster.
-Thus the cluster robustness discussed in terms of number of CCs carries little meaning when the sizes of formed clusters are not given consideration.
-Cluster size also plays a part in transmission power consumption, \ie cluster size affects the transmission power consumption when routing is conducted~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
-In this paper we will analyze the robust clustering and propose efficient solutions.
-Our schemes generate the clusters which demonstrate both the robustness against the increasing primary activity and the compliance with the desired cluster sizes.
-Hence our schemes provide the network designers with more freedom when the power consumption is involved in the design of network applications.
-%In this paper we will introduce a robust cluster structure for CRN, where the robustness means the ability of the clusters to sustain under the influence of the increasing activity of primary users, and the direct metric is the number of CCs in the clusters.
-
-%On the other hand, large clusters are not preferred in some scenarios neither, \eg for the CRN composed with resource limited users, managing the cluster members in a large cluster is a substantial burden.
-%Hence, the cluster size should fall in a desired range according to different application scenarios~\cite{Chen04clusteringalgorithms, capacity_cluster_06}.
-
-%with the intention to provide a robust infrastructure for the applications which may be conducted above that in CRN.
-%that being said, when we design this clustering scheme in CRN, we do consider the services to be delivered by the network.
-%Cluster sizes affect the power consumption directly in wirelss sensor networks~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
-%When the cluster size is not deliberately discussed, it is also decided alongside the optimization of the network, \eg the opimal selection of the aggregation points in a wireless sensor network results in the clusters~\cite{data_aggr_algorithm_04}.
-
-Different clustering strategies have been proposed for wireless networks of different types.
-As there is no restriction on the nodes to access the spectrum in wireless ad-hoc, mesh networks and sensor networks, the objective of clustering is to decrease the transmission power consumption~\cite{Kawadia03}, to improve the routing performance~\cite{clustering_mesh_globecom2010}, or to imrove the network lifetime and coverage~\cite{Abbasi_survey_07}.
+In the context of CRN, the activity of primary users is usually unknown to the secondary users, thus when the primary users' activity is deemed as random, the cluster which secures more CCs will anticipate a longer time span.
+It is obvious that fewer members in a cluster yield more CCs, but obtaining more CCs by decreasing the cluster size contradicts to the motivation of clustering, \ie benefit the cluster members with cooperative decision making.
+For example, spectrum sensing accuracy coralates with the cluster size~\cite{Consensus_based_clustering12}, and power consumption doesn't favor small clusters~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
+In this paper the robustness of clusters means the ability of the clusters to sustain the increasing activity of primary users.
+%is synonymous with the affluence of CCs which are possessed by that cluster, to ....
+
+%To solely pursue cluster robustness against the primary users' activity, \ie to achieve more common channels within clusters, the ultimately best clustering strategy is ironically that every node constitutes one cluster (called as \textit{singleton cluster} in this paper).
+%%In that case, the common channels within cluster are the available channels available at that node's place.
+%Apparently this contradicts our motivation of proposing cluster in cognitive radio network to enable cooperative decision making.
+%Thus the cluster robustness discussed in terms of number of CCs carries little meaning when the sizes of formed clusters are not given consideration.
+
+There has been a lot of research done for clustering in wireless networks.
+In ad-hoc and mesh networks, the major goal of clustering is to maximize connectivity or to improve the performance of routes~\cite{Kawadia03, clustering_mesh_globecom2010}.
+The emphasis of clustering in sensor networks is on network lifetime and coverage~\cite{Abbasi_survey_07}.
 %Various clustering schemes are proposed to target different aspects in cognitive radio networks.
@@
 %\cite{clustering_globecom11} proposes clustering strategy in cognitive radio network, which looks into the relationship between cluster size and power consumption and accordingly controlling the cluster size to decrease power consumption.
-With regard to forming clusters in CRN, deciding on the common channel within each cluster is the foremost question to answer.
-\cite{Zhao07, Chen07,Affinity_clustering_09icccn} propose the clustering schemes and make sure every cluster possesses at least one CC.
-Clustering scheme~\cite{Consensus_based_clustering12} looks for the network partition which improves the accuracy of spectrum sensing with the cluster structure.
+In respect of CRN, \cite{Zhao07, Chen07,Affinity_clustering_09icccn} propose the clustering schemes to form clusters, where securing CCs is the only goal.
+Clustering scheme~\cite{Consensus_based_clustering12} improves spectrum sensing accuracy with cluster structure.
 %Clustering scheme~\cite{clustering_globecom11} obtains the best cluster size which minimizes power consumption caused by communication within and among clusters.
-\cite{TWC2012_cooperative_communication} forms the clusters by deciding on the cluster heads, where the transmit power for the long-haul transmission between the cluster heads is minimized.
-\cite{clustering_globecom11} proposes a cluster structure which promises energy efficiency.
-\cite{cluster_EW10} proposes strategy on how to decide on the CCs and access the multiple CCs within clusters.
+\cite{clustering_globecom11, TWC2012_cooperative_communication} target on the QoS provisioning and energy efficiency with cluster structure.
+\cite{cluster_EW10} forms clusters to coordinate the control channel usage within one cluster.
 An event-driven clustering scheme is proposed for cognitive radio sensor network in \cite{Ozger_cluster_crsn_13}.
 No one among the above mentioned schemes provides the robustness to the formed clusters against primary users. 
-
-Robustness of clusters is discussed in~\cite{LIU_TMC11_2}, where a distributed clustering scheme (denoted as SOC) which is designed to generate robust clusters against primary users is proposed.
-The robustness of the clusters comes from the fact that there are multiple CCs available for the clusters.
+%
+A clustering scheme (denoted as SOC) which is designed to generate robust clusters against primary users is proposed in~\cite{LIU_TMC11_2}.
 SOC involves three phases of distributed executions.
 In the first phase, every secondary user forms clusters with some one-hop neighbors, in the second and third phase, each secondary user seeks to either merge other clusters or join one of them.
-The metric adopted by every secondary user in all the phases is the product of the number of CCs and cluster size.
-The drawbacks of this scheme are as follows, although the adopted metric considers both cluster size and the number of CCs, cluster formation can be easily dominated by only one factor, e.g.
+The metric adopted by every secondary user in the three phases is the product of the number of CCs and cluster size.
+The drawbacks are as follows, although the adopted metric considers both cluster size and the number of CCs, cluster formation can be easily dominated by only one factor, e.g.
 a node which can access many channels may exclude its neighbor and form a cluster by itself.
@@
 \cite{mansoor_15_cluster_robust} presents a heuristic method to form clusters, although the authors claim robustness is one goal to achieve, the minimum number of clusters is finally pursued.
-%
+
 A distributed clustering scheme ROSS is proposed in~\cite{Li11_ROSS} under the game theoretic framework. 
-Compared with the clustering schemes introduced above, the clusters are formed faster and the clusters possess more CCs than SOC.
-But as all the other clustering schemes, this scheme doesn't have control over the formation of the very small or very large clusters which are not desirable.
+Compared with the clustering schemes introduced above, the clusters are formed faster and the clusters possess more CCs within and among clusters than SOC.
+But this work doesn't intervene the outcome of singleton clusters, although the cluster sizes are not as divergent as SOC.
 Furthermore, this work doesn't consider the robustness of clusters against the increasing activity of primary users, which leaves their claim of robustness unverified.
 %
-This paper is on the basis of the work in~\cite{Li11_ROSS}, but extends in two dimensions.
-First, this paper renews the definition of robustness of clusters in a CRN, which is no longer the average number of CCs of clusters, but the ability of the clusters to sustain when the primary users' activity becomes more dynamic.
-Second, this paper proposes size control mechanism, which solves the problem of devergence of clusters sizes in~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
-Besides, this paper provides a comprehensive analysis of the robust clustering problem and proposes a centralized solution. 
+This paper is on the basis of the work in~\cite{Li11_ROSS}, but extends in two directions.
+First, this paper sticks to a new metric of robustness, and considers the clusters when primary users' activity becomes more dynamic.
+Second, this paper proposes size control mechanism, which solves the problem of devergence of clusters sizes in ~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
+Besides, this paper provides a comprehensive analysis of the robust clustering problem and proposes the centralized solution. 
 %We stick to the motivation of forming robust clusters in CRN \ie let more CR users benefited from the cooperative decision making which is due to the clusters. 
@@
 %For our scheme we can prove convergence in cluster formation phase and resolve ambiguities with respect to cluster membership in a game-theoretic setting. 
-The new extensions are made on basis of ROSS and its light weight version, the latter involves less overheads thus is more suitable for the scenario where fast deployment is desired.
-Throughout this paper, we refer to the clustering schemes on the basis of ROSS as the \textit{variants of ROSS}.
+The new extensions are made on basis of ROSS and its light weighted version, the latter involves less overheads thus are more suitable for the scenario where fast deployment is desired.
+Throughout this paper, we refer to the clustering schemes on the basis of ROSS as \textit{variants of ROSS}, which include the fast versions and that with size control function.
 
@@
 We adopt the unit disk model~\cite{unitDiskModel} for both primary and CR users' transmission.
-If a CR node $i$ locates within the transmission range of an active primary user $p$, $i$ is not allowed to use the channel which is being used by $p$.
+%As to the relation between the primary and secondary users,
+If a CR node $i$ locates within the transmission range of an active primary user $p$, then $i$ is not allowed to use the channel which is being used by $p$.
 %On the other hand, if $i$ is not in the transmission range of primary user $p$, $i$ can certainly not detect the presence of $p$.
-We assume the primary users change their operation channels slowly, thus we consider the clustering problem at some point in time given some degree of information of the availability of the control channels.
-Due to the same reason, we omit the time index for the spectrum availability. 
-As the result of spectrum sensing, $K_i \subseteq \mathcal{K}$ denotes the set of available licensed channels for CR user $i$.
-As the transmission range of primary users is limited and CR users have different locations, different CR users have different views of the spectrum availability, i.e., for any $i, j \in \mathcal{N}$, $K_i = K_{j}$ does not necessarily hold.
-We therefore represent the network of CR nodes by a graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{i, j\} \in E$ if and only if $K_{i} \cap K_{j}\neq \emptyset$ and $d_{i,j} < r$, where $d_{i,j}$ is the distance between $i, j$ and $r$ is the radius of CR user's transmission range.
-%
-Among the CR users, we denote by $\text{Nb}(i)$ the neighborhood of $i$, which consists of the CR nodes located within $i$'s transmission range.
-
-We assume there is one dedicated control channel which is used to exchange signaling messages during the clustering process.
+We assume the primary users change their operation channels slowly, then we omit the time index for the spectrum availability, \ie as the result of spectrum sensing, $K_i \subseteq \mathcal{K}$ denotes the set of available licensed channels for CR user $i$ at a time point.
+As the transmission range of primary users is limited and secondary users have different locations, different secondary users may have different views of the spectrum availability, i.e., for any $i, j \in \mathcal{N}$, $K_i = K_{j}$ does not necessarily hold.
+A cognitive radio network can be represented as a graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{i, j\} \in E$ if and only if $K_{i} \cap K_{j}\neq \emptyset$ and $d_{i,j} < r$, where $d_{i,j}$ is the distance between $i, j$, $r$ is the radius of secondary user's transmission range.
+%
+Among the secondary users, we denote $\text{Nb}(i)$ as user $i$'s neighborhood, which consists of the CR nodes located within the transmission range of $i$.
+
+We assume there is one dedicated control channel which is used to exchange signaling messages during clustering process.
 This control channel could be one of the ISM bands or other reserved spectrum which is exclusively used for transmitting control messages.\footnote{Actually, the control messages involved in the clustering process can also be transmitted on the available licensed channels through a rendezvous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}, i.e., two neighboring nodes establish communication on the same channel.}
 Over the control channel, a secondary user $i$ can exchange its spectrum sensing result $K_i$ with all its one hop neighbors $\text{Nb}(i)$.
-In the following, we refer to the licensed channels as channels in general, and will explicitly mention the dedicated control channel if necessary.
+In the following, we refer to the licensed channel as \textit{channel} in general, and will explicitly mention the dedicated control channel if necessary.
 
 We give the definition of cluster in CRN as follows. 
-A cluster $C$ is a set of secondary nodes, and there is one set of common channels which are available for each node.
-In particular, a cluster consists of a cluster head $h(C)$ and a number of cluster members, and the cluster head is able to communicate with any cluster member directly.
-A cluster can be formed only by the cluster head.
-%$\text{Nb}(i)$ denotes node $i$'s neighborhood which consists of all its one hop neighbors.
+A cluster $C$ is a set of secondary nodes which possess the same set of CCs.
+In particular, one cluster consists of a cluster head $h(C)$ and a number of cluster members, and the cluster head is able to communicate with any cluster member directly.
+A cluster can be composed only by the cluster head.
+$\text{Nb}(i)$ denotes node $i$'s neighborhood which consists of all its one hop neighbors.
 %For any cluster member $i \in C$, $i \in \text{Nb} (h_C) $ holds.
-The size of $C$ is denoted by $|C|$.
-When the cluster head of a cluster is $i$, we denote that cluster by $C(i)$.
-$K(C)$ denotes the set of CCs in cluster $C$, $ K(C) = \bigcap_{i\in C} K_i$.
+Cluster size of $C$ is written as $|C|$.
+Cluster $C(i)$ means the cluster head of this cluster is $i$.
+$K(C)$ denotes the set of CCs in cluster $C$, $ K(C) = \cap_{i\in C} K_i$.
 %Clustering is performed periodically, because the secondary users are mobile and the primary users change their operation channels, thus the channel availability on secondary users changes accordingly.
-The notations used in the system model are listed in Table~\ref{tab1}.
+The notations used in the system model and the following problem description are listed in Table~\ref{tab1}.
 \begin{table}[h!]
@@
  $\mathcal{S}$ & the collection of all the possible clusters in $\mathcal{N}$\\
- $C_i$  & the $i$-th cluster in $\mathcal{S}$ \\
- $|C_i|$ & size of the cluster $C_i$\\
- $|K(C_i)|$ & the number of CCs of cluster $C_i$\\
- $n$ & the number of debatable nodes\\
- $m$ & the number of claiming cluster heads\\
+ $C_i$  & the $i$th cluster in $\mathcal{S}$ \\
 \bottomrule
@@
 
-As introduced in Section~\ref{intro}, in order to be robust against primary users' activity, the formed clusters should have more CCs.
-On the other hand, the sizes of the formed clusters should be regulated, \ie they don't diverge from a given value greatly.
-%Considering the above mentioned requirements, we present the definition of robust clustering problem as follows.
+As introduced in Section~\ref{intro}, in order to be robust against primary users' activity, the formed clusters should have more CCs to expect longer life expectancy.
+On the other hand, the sizes of the formed clusters should not diverge from the desired size greatly.
+The formation of small clusters or the \textit{singleton clusters}, \ie the cluster which has only one CR node, contradicts the motivation of forming clusters, as the benefits brought in by the collective of the cluster members are compromised.
+On the other hand, large clusters are not preferred in some scenarios neither, \eg for the CRN composed with resource limited users, managing the cluster members in a large cluster is a substantial burden.
+Hence, the cluster size should fall in a desired range according to different application scenarios~\cite{Chen04clusteringalgorithms, capacity_cluster_06}.
+Considering the above mentioned requirements, we present the definition of robust clustering problem as follows.
 
@@
 
-As to a cognitive radio network, where the set of CR nodes is $\mathcal{N}$.
-%Each cluster complies with the definition in , whose number of CCs in a cluster $C$ is $f(C)$.
-The robust clustering problem is to decide the set of clusters $\mathcal{T}$, where 
-\begin{enumerate}
-\setlength{\itemindent}{.05in}
-\item the sum of the $f(C)$ is the maximal, where $C\in \mathcal{T}$ 
-\item the intersection of any two clusters in $\mathcal{T}$ is an empty set
-\item the union of clusters in $\mathcal{T}$ is $\mathcal{N}$
-\item the cluster sizes should fall in the scope $\langle\delta_1, \delta_2\rangle$, where $\delta, \delta_1, \delta_2\in \mathbb{Z}^+$, $\delta_1 \leq \delta\leq \delta_2$, and $\delta$ is decided according to the application to be implemented in the CRN.
-\end{enumerate}
-
-\end{mydef}
-
-Assume we have obtained the set of $\mathcal{S}$ which contains all the clusters in $\mathcal{N}$, \ie $\mathcal{S}=\{C_1, C_2,\ldots,C_i, \ldots, C_{|\mathcal{S}|}\}$ \footnote{The subscript $i$ means the $i$-th cluster in $\mathcal{S}$.} and there is $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = \mathcal{N}$.
-The decision version of this problem is to determine whether there is a non-empty set $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C_i\in \mathcal{S}'} f(C_i) \geqslant \lambda$ where $\lambda$ is a real number.
-We have the following theorem on the problem's complexity.
-\begin{theorem}
-\label{theorem1}
-The robust clustering problem in CRN is NP-hard, when the maximum size of clusters is larger than 3, $\delta_1=1$ and $\delta_2 = N$.
-%Assume a CRN can be represented by a connected graph, and there is at least one common channel between any pair of neighbours, then forming at least two CR nodes into one cluster is NP-complete.
-\end{theorem}
-The proof is in Appendix~\ref{proof_theorem1}.
+Given a cognitive radio network $\mathcal{N}$ where $|\mathcal{N}|=N$, the collection of all the possible clusters\footnote{Possible cluster means the collection of CR nodes, which complies with the definition in~\ref{sec:model}} in $\mathcal{N}$ is denoted as $\mathcal{S}$ where $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$ \footnote{The subscripts of the clusters can be decided in any convenient way \ie the sequence of identifying them.} and there is $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$.
+%
+With the requirements on the cluster size are enforced, \ie the desired size is $\delta$ and the cluster sizes should fall in the scope $\langle\delta_1, \delta_2\rangle$, where $\delta, \delta_1, \delta_2\in \mathbb{Z}^+$, and $\delta_1 \leq \delta\leq \delta_2$, a feasible clustering solution is a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, which satisfies
+$\delta_1\leq|C_i|\leq \delta_2, \bigcup_{C_i\in \mathcal{S}'} C_i = \mathcal{N}$ and $C_{i'}\cap C_i =\emptyset$ where $C_{i'}, C_i\in \mathcal{S}'$ and $i'\neq i$.
+The optimal clustering solution is the feasible clustering solution whose sum of the numbers of CCs of clusters $\sum_{C\in \mathcal{S}'} f(C)$ is the maximal.
 
@@
 
+\end{mydef}
+
 %The decision version of \textit{weighted exact cover problem}: 
@@
 \label{centralized_solution}
-When the global knowledge of the CRN is available to us, we can propose a centralized scheme as comparison.
-The proposed centralized solution formulates the problem in Definition~\ref{def_centralized_clustering} as an optimization problem which is solved with standard software packages.
-The optimization searches the set $\mathcal{S}$ and decides on the clusters according to the following optimization formulation,
-%
-%which constitute the whole CRN without overlapping between any two of them, besides, the sum of CCs of the chosen clusters is maximized.
-%Then, a central node (or controller) with the knowledge of all CR nodes (and also the possible clusters) can solve the problem based on the following formulation. 
-%
-%Second, we assign a cluster size related weight to each cluster, which is positively correlated with the difference between the cluster size and the desired cluster size.
+
+Based on Definition~\ref{def_centralized_clustering}, the decision version of this problem is to determine whether there is a non-empty $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C\in \mathcal{S}'} f(C) \geqslant \lambda$ where $\lambda$ is a real number.
+We have the following theorem on the complexity of this problem.
+
+\begin{theorem}
+\label{theorem1}
+Robust clustering problem in CRN is NP-hard, when the maximum size of clusters is larger than 3, and $\delta_1=1$ and $\delta_2 = N$.
+%Assume a CRN can be represented by a connected graph, and there is at least one common channel between any pair of neighbours, then forming at least two CR nodes into one cluster is NP-complete.
+\end{theorem}
+The proof is in Appendix~\ref{proof_theorem1}.
+%This theorem actually indicates that the robust clustering problem in CRN is NP-hard.
+
+We propose a centralized solution which solves an optimization with standard solvers. 
+To formulate the optimization, we need to do some preparation beforehand.
+First, all the possible clusters complying with the description in the system model are found and constitute a set $\mathcal{S}$.
+Second, we assign a weight about size to each cluster, which correlates with the difference between the cluster size and the desired cluster size. 
+In particular, considering $|\mathcal{S}|=M$, $C_i\in \mathcal{S}$ means the $i$ th cluster in $\mathcal{S}$, and $\delta$ is the desired size, the weight about size for each cluster is given as follows,
+$$
+p_i(C_i) = \left\{ \begin{array}{rl}
+0 &\mbox{ if $|C_i|=\delta$} \\
+\rho_1 &\mbox{if $|C_i|=\delta-1$ or $|C_i|=\delta+1$} \\
+\rho_2 &\mbox{if $|C_i|=\delta-2$ or $|C_i|=\delta+2$} \\
+\vdots
+\end{array} \right.
+$$
+where $\rho_1, \rho_2, \cdots$ are positive values.
+In particular, $\rho$ increases with the divergence between $|C_i|$ and $\delta$, \ie these is $\rho_2> \rho_1>0$.
+
+The optimization searches the set $\mathcal{S}$ and decides on certain clusters which constitute the whole CRN without overlapping between any two of them, besides, the sum of CCs of the chosen clusters is maximized.
+Then, a central node (or controller) with the knowledge of all CR nodes (also the possible clusters) will solve the problem based on the following formulation.
 
@@
 \begin{aligned}
-     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot t_{ij}) \\
-     &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, for\,\,\forall j=1, \ldots, N \\
-   &&& \Sigma_{j=1}^N x_{ij} = |C_i|\cdot y_i,\, for\,\,\forall i=1, \ldots, M \\
-  % &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
+     &\min\limits_{w_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (w_i*t_{ij}) \\
+     &\text{subject to}   && \Sigma_{i=1}^G x_{ij} = 1, for \forall j=1, \ldots, N \\
+   &&& \Sigma_{j=1}^N x_{ij} = |C_i|*w_i, for \forall i=1, \ldots, M \\
+   &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
    &&& i\in \{1,2, \cdots M\}, \hspace{0.3cm} j\in \{1,2,\cdots N\}
@@
 \end{equation}
-This problem is a binary linear programming problem, which can be solved by many available solvers.
-$y_i$ and $x_{ij}$ are two binary variables.
+
+%The optimization is a binary linear programming problem.
+The objective is to maximize the sum of CCs of all the clusters.
+%We minimize the opposite of the real objective to make this problem solvable.
+$w_i$ and $x_{ij}$ are the two binary variables in this problem.
 % where $j\in \{1,2,\cdots,N-1, N\}$ and $i\in \{1,2,\cdots,M-1, M\}$.
+$N$ is the total number of CR users in network $\mathcal{N}$, $M = |\mathcal{S}|$.
 %$G = |\mathcal{G}|$ and there is $\mathcal{G} \subseteq \mathcal{S}$.
-Being either 1 or 0, $y_i$ denotes whether the $i$-th cluster $C_i$ in $\mathcal{S}$ is chosen or not.
-$x_{ij}$ indicates whether the CR node $j$ resides in the cluster $C_i$, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$. 
-%Node index $j$ is identical to the node ID.
-$N$ is the total number of CR users in network $\mathcal{N}$, $M$ is the number of clusters in $\mathcal{S}$.
-
-The constraints guarantee to obtain the clusters which together include all the CR users and don't overlap.
-The first constraint regulates that a CR node should reside in exactly one cluster.
-The second constraint regulates that when the $i$-th cluster $C_i$ is chosen, there will be exactly $|C_i|$ CR nodes residing in $C_i$.
-
-%The optimization is a binary linear programming problem.
-The objective is to maximize the sum of the numbers of CCs in the clusters which constitute the CRN.
-$t_{ij}$ is a constant and there is
+Being either 1 or 0, $w_i$ denotes whether the $i$th cluster $C_i$ in $\mathcal{S}$ is chosen to be in the solution or not.
+$x_{ij}$ indicates whether the CR node $j$ resides in the $i$th potential cluster, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$. 
+Node index $j$ is identical to the node ID.
 %In practice, we can solve the problem with $\mathcal{G} = \mathcal{S}$ when $|\mathcal{S}|$ is not large. 
@@
 %By permitting the existence of the singleton clusters, we can ensure that the $\mathcal{S}'$ in Definition~\ref{def_centralized_clustering} is always be feasible.
-
-\begin{equation}
-t_{ij} = \frac{q_{ij}}{|C_i|} - p_i(C_i)
-\end{equation}
-where constant $q_{ij}= |K(C_i)|$ when node $j\in C_i$, and $q_{ij}= 0$ when node $j\notin C_i$.
-%$|K(C_i)|$ is the number of CCs of cluster $C_i$, and $|C_i|$ is the size of cluster $C_i$.
-$p_i(C_i)$ is the size-related weight, which reflects the deviation of $C_i$'s size from the desired size.
-Assuming $\delta$ is the desired size, then there is
-$$
-p_i(C_i) = \left\{ \begin{array}{rl}
-0 &\mbox{ if $|C_i|=\delta$} \\
-\rho_1 &\mbox{if $||C_i|-1|=\delta$} \\
-\rho_2 &\mbox{if $||C_i|-2|=\delta$} \\
-\vdots
-\end{array} \right.
-$$
-where $\rho_1, \rho_2, \cdots$ are positive values and these is $\rho_2> \rho_1>0$.
-
+$t_{ij}$ is a constant which is $p_i(C_i) - \frac{q_{ij}}{|C_i|}$.
+$q_{ij}= |K(C_i)|$ when there is $j\in C_i$, and $q_{ij}= 0$ when there is $j\notin C_i$.
+$|K(C_i)|$ is the number of CCs of cluster $C_i$, and $|C_i|$ is the size of cluster $C_i$.
 %%Based on the knowledge on $\mathcal{S}$, we construct a $M\times N$ matrix $Q_{M\text{x}N}$ which is shown in Figure~\ref{costant_matrix_Q}. 
@@
 
-%Now we examine the objective function to see whether it in line with the goal to maximize the total number of CCs meanwhile consider the restriction on the cluster size.
-When $t_{ij}$ is replaced with $\frac{q_{ij}}{|C_i|} - p_i(C_i)$, the objective function becomes,
+Now we examine the objective function to see whether it in line with the goal to maximize the total number of CCs meanwhile consider the restriction on cluster size.
+The objective function can be written as,
 \begin{equation}
 \begin{aligned}
-     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p_i(C_i)) \\
+     &\min\limits_{w_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (-w_i* \frac{q_{ij}}{|C_i|} + w_i*p_i(C_i)) \\
 \notag
@@
 The sum of the first items is the sum of CCs of all the chosen clusters.
-As to the second item, when $w_i$ is 1 ($C_i$ is chosen) and $|C_i|\neq\delta$, it will be negative, which contradicts the direction of the optimization.
-Thus the second item discourages the appearance the clusters whose sizes deviate from $\delta$.
+The minus sign in front of the first item explains the reason why we minimize instead to maximize the objective function.
+As to the second item, when $w_i$ is zero ($C_i$ is chosen), if $|C_i|\neq\delta$, the second component will be positive which contradicts the direction of the optimization.
+Thus the second item discourages the appearance the clusters whose sizes are different from $\delta$, especially those whose sizes diverge far from $\delta$.
 
@@
 
+The constraints guarantee to obtain the clusters which together include all the CR users and don't overlap.
+The first constraint regulates that each CR node should reside in exactly one cluster.
+The second constraint regulates that when the $i$th possible cluster $C_i$ is chosen, there will be exactly $|C_i|$ CR nodes residing in $C_i$.
+
 %\begin{figure}[ht!]
@@
 
-The difficulty of using this method lies in obtaining the set $\mathcal{S}$.
-In the worst case, \ie the CRN forms a full connected graph, the size of $\mathcal{S}$ is $\Sigma_{r=1}^{N}\ {N \choose r} = 2^N-1$.
-%To levitate this problem, a smaller set, \ie $\mathcal{G} \subset \mathcal{S}$ can be used.
-%In this case, the global optimal may not be found.
-%$\mathcal{G}$ can be prepared based on the cluster size, and it is recommended to include all the singleton clusters to make sure the availability of feasible solutions.
-Another obstacle comes from the fact that the centralized controller needs to be reliable at anytime, which is a challenge for CRN as the spectrum on the controller can not be guaranteed.
-%In order to apply this scheme in practice, a large over head needs to be factored in in collecting the channel usage as seen by the R nodes, as well as the connectivity between the CR nodes.
-%After computing the clustering solution, the centralized node needs to distribute it across the whole network.
-
-%In CRN, it is necessary to do clustering again on some occasions.
-%For example, when a certain amount of CR users move away from their clusters, \ie they loose the direction connection with any member in their previous clusters, or a certain amount of clusters can not be maintained as the CCs in these clusters don't exist any longer due to primary users' activity.
-%Hence, when the spectrum availability and the CR users' location change frequently, the centralized robust clustering scheme is not suitable for CRN.
+This problem is a binary linear programming problem, which can be solved by many available solvers.
+The difficulty of using this method lies in the preparation of the set $\mathcal{S}$.
+In the worst case \ie the CRN forms a full connected graph, the size of $S$ is $\Sigma_{r=1}^{N}\ {N \choose r} = 2^N-1$.
+To levitate this problem, a smaller set \ie $\mathcal{G} \subset \mathcal{S}$ can be used.
+$\mathcal{G}$ can be prepared based on the cluster size, and it is recommended to include all the singleton clusters to make sure the availability of feasible solutions.
+
+Another obstacle to apply this centralized scheme is, the centralized entity firstly needs to collect the information from all the CR nodes, then computes the clustering solution and distributes it across the whole network.
+This process involves a large number of communication overheads.
+In CRN, it is necessary to do clustering again on some occasions.
+For example, when a certain amount of CR users move away from their clusters, \ie they loose the direction connection with any member in their previous clusters, or a certain amount of clusters can not be maintained as the CC in these clusters don't exist any longer due to primary users' activity.
+Hence, when the spectrum availability and the CR users' location change frequently, the centralized robust clustering scheme is not suitable for CRN.
 
@@
 ROSS consists of two cascaded phases: \textit{cluster formation} and \textit{membership clarification}.
-In the first phase, clusters are formed quickly and every CR user becomes either a cluster head or a cluster member, besides, cluster size control is implemented in this phase.
+In the first phase, clusters are formed quickly and every CR user becomes either a cluster head or a cluster member.
 In the second phase, non-overlapping clusters are formed in a way that the CCs of relevant clusters are mostly increased.
@@
 \label{phaseI}
-We assume that before conducting clustering, spectrum sensing, neighbor discovery and exchange of spectrum availability have been completed, so that every CR node is aware of the available channels for themselves and their neighbors.
+We assume that before conducting clustering, spectrum sensing, neighbor discovery and exchange of spectrum availability have been completed, so that every CR node is aware of the available channels on themselves and their neighbors.
 In this phase, cluster heads are determined after a series of comparisons with their neighbors. 
@@
 \item \textit{Individual connectivity degree} $d_i$: $d_i=\sum_{j\in \text{Nb}(i)}\vert K_i\cap K_j\vert$. 
-$d_i$ is the total number of the CCs between node $i$ and each of its neighbors.
-%It is an indicator of node $i$'s adhesion to the CRN.
-
-\item \textit{Neighborhood connectivity degree} $g_i$: the number of CCs which are available for $i$ and all its neighbors.
-$g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$, which represents the ability of $i$ to form a robust cluster with its neighbors.
+$d_i$ is the total number of the CCs between node $i$ and every its neighbor.
+It is an indicator of node $i$'s adhesion to the CRN.
+
+\item \textit{neighborhood connectivity degree} $g_i$: $g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$. 
+It is the number of CCs which are available for $i$ and all its neighbors.
+$g_i$ represents the ability of $i$ to form a robust cluster with its neighbors.
 \end{itemize}
@@
 When CR node $i$ has lower individual connectivity degree than all its neighbors except for those which have already identified to be cluster heads, node $i$ becomes a cluster head.
-If there is another CR node $j$ in its neighborhood, which has the same individual connectivity degree as $i$, \ie $d_j = d_i$ and $d_j < d_{k}, \forall k\in \text{Nb}(j)\setminus \{\Lambda\cup i\}$ where $\Lambda$ denotes the cluster heads, then the node between $i$ and $j$, which has higher neighborhood connectivity degree will become the cluster head.
-If $g_i = g_j$ as well, the node ID is used to break the tie, \ie the one with smaller node ID becomes the cluster head.
+%In other words, CR node $i$ becomes cluster head if $d_i > d_k, \forall k\in \texttt{Nb}_i\setminus CHs$ ($CHs$ donate the cluster heads existing in $\texttt{Nb}_i$).
+If there is another CR node $j$ in its neighborhood which has the same individual connectivity degree as $i$, \ie $d_j = d_i$ and $d_j < d_{k}, \forall k\in \text{Nb}(j)\setminus \{\Lambda\cup i\}$ where $\Lambda$ denotes the cluster heads, then the node between $i$ and $j$, which has higher neighborhood connectivity degree will become the cluster head, and the other node become one member of the newly identified cluster head.
+If $g_i = g_j$ as well, the node ID is used to break the tie, \ie the one with smaller node ID becomes a cluster head.
 %
 The node which is identified as a cluster head broadcasts a message to notify its neighbors of this change, and its neighbors which are not cluster heads become cluster members
-\footnote{The reason for the occurrence of the cluster heads in the neighborhood of a new cluster head will be explained in Section~\ref{ross_p1_guarantee_ccc} and \ref{ross_p2_cluster_pruning})}.
+\footnote{The reasons for the occurrence of the cluster heads in the neighborhood of a new cluster head will be explained in Section~\ref{ross_p1_guarantee_ccc} and \ref{ross_p2_cluster_pruning})}.
 The pseudo code for the cluster head decision and the initial cluster formation is shown in Algorithm~\ref{alg0} in the appendix.
@@
 %\end{proof}
-When a CR node $i$ is associated to multiple clusters, \ie $i$ has received multiple notifications from different cluster heads, $d_i$ is still set to be $M$. 
+When a CR node $i$ is associated to multiple clusters, \ie $i$ has received multiple notifications of cluster head eligibility from different CR nodes, $d_i$ is still set to be $M$. 
 %In other words, with this manipulation on its individual connectivity degree, every CR node in the network will be involved in the clustering process, the proof will be given later.
-The manipulation of the individual connectivity degree of the cluster members accelerates the decision on the cluster heads.
+The manipulation of the individual connectivity degree of the cluster members fastens the speed of completing choosing the cluster heads.
 %, which enables the nodes which are outside of the cluster can possibly become cluster heads or can also be included into other clusters.
-%We have the following theorem to show that when there is no one secondary which shares no CC with any other secondary users, \ie
-%all secondary users' individual connectivity degrees are greater than zero, then every secondary user will eventually be either integrated into a certain cluster, or becomes a cluster head.
-We have the following theorem to show that every secondary user will eventually be either integrated into a certain cluster or becomes a cluster head.
+We have the following theorem to show that as long as a secondary user's individual connectivity degree is greater than zero, every secondary user will eventually be either integrated into a certain cluster, or becomes a cluster head.
 \begin{theorem}
@@
 The Proof is in Appendix~\ref{proof_clustering:theorem}.
-%
-The procedure of the proof also illustrates the maximal time needed to conduct Algorithm~\ref{clustering:theorem}. 
+
+The procedure of the proof also illustrates the time needed to conduct Algorithm~\ref{clustering:theorem}. 
 Consider an extreme scenario, where all the secondary nodes sequentially execute Algorithm~\ref{alg0}, \ie they constitute a list as discussed in the example in the proof.
 %
-If one step can be finished within a certain time span $T$, then the total time needed for the network to conduct Algorithm~\ref{clustering:theorem} is $N*T$.
-As Algorithm~\ref{alg0} can be executed concurrently by different secondary users, the needed time can be considerably reduced.
+If one step can be finished within certain time $T$, then the total time needed for the network to conduct Algorithm~\ref{clustering:theorem} is $N*T$.
+In other scenarios, as Algorithm~\ref{alg0} can be executed concurrently by secondary users which locate in different places, the needed time can be considerably reduced.
 %According to Theorem~\ref{clustering:theorem}, Phase I completes within a reasonable amount of time.
@@
 %This judgement is conducted periodically, and phase I ends after every node ascertains it is cluster head or not.
-If we apply Algorithm~\ref{alg0} to the example shown in Figure~\ref{fig1}, then the outcome is shown in Figure~\ref{fig2}.
+Let us apply Algorithm~\ref{alg0} to the example shown in Figure~\ref{fig1}.
 Node $B$ and $H$ have the same individual connectivity degree, i.e., $d_B=d_H$. As $g_H=2>g_B=1$, node $H$ becomes the cluster head and cluster $C(H)$ is $\{H, B, A, G\}$.
 
-\subsubsection{The Existence of Common Channels}
+\subsubsection{Guarantee the Existence of Common Channels}
 \label{ross_p1_guarantee_ccc}
@@
 If this criterion meets a tie, the tie will be broken by deleting the node with smaller node ID.
-It is possible that the cluster head excludes all its neighbors, resulting in a singleton cluster which is composed by itself.
+It is possible that the cluster head excludes all its neighbors and resulting in a singleton cluster which is composed by itself.
 %At the end of this procedure every formed cluster has at least one common channel.
@@
 The pseudo code for this procedure is shown in Algorithm~\ref{alg_size_control_available_CCC}.
-As to the nodes which are eliminated from the previous clusters, they restore their original individual connectivity degrees, then execute Algorithm~\ref{alg0} and become either cluster heads or get included into other clusters afterwards according to Theorem~\ref{clustering:theorem}.
-
-During Phase I, whenever a CR node is decided to be a cluster head and accordingly forms a cluster, or its cluster's composition is changed, the cluster head will broadcast the updated information about its cluster, which includes the sets of available channels on all its cluster members.
+As to the nodes which are eliminated from the previous clusters, they restore their original individual connectivity degrees, execute Algorithm~\ref{alg0} and become either cluster heads or get included into other clusters afterwards according to Theorem~\ref{clustering:theorem}.
+
+During Phase I, when ever a CR node is decided to be a cluster head and accordingly forms a cluster, or its cluster's composition is changed, the cluster head will broadcast the updated information about its cluster, which includes the sets of available channels on all its cluster members.
 
@@
 \label{ross_p2_cluster_pruning}
+
 In this subsection, we illustrate the pressing necessity to control the cluster size when CRN becomes denser.
+
 We consider a cluster $C(i)$ where $i$ is the cluster head in a dense CRN. 
@@
   \centering
-  \includegraphics[width=0.3\linewidth]{clusters_denseNetwork_2.pdf}
+  \includegraphics[width=0.4\linewidth]{clusters_denseNetwork_2.pdf}
   \caption{Clusters formation in extremely dense CRN. Black dots are cluster heads, cluster members are not drawn.}
@@
 %Debatable node $i$ is aware of all its claiming clusters in $S_i$. 
-Assuming a debatable node $i$ which needs to decide one cluster $C\in S_i$ to stay and leaves the other clusters in $S_i$, then the principle for $i$ is its decision should result in the greatest increase of CCs in all its claiming clusters.
-As node $i$ has been notified of the spectrum availability on all the nodes in each claiming cluster, node $i$ is able to calculate how many more CCs will be produced in a claiming cluster if $i$ leaves that cluster.
+Assume a debatable node $i$ needs to decide one cluster $C\in S_i$ to stay, and thereafter leaves the rest others in $S_i$.
+In this process, the principle for $i$ is that its move should result in the greatest increase of CCs in all its claiming clusters.
+%The set of available channels of one cluster are known by the debatable nodes which locate in that cluster. %this is finished 
+Note that node $i$ is aware of the spectrum availability on all the cluster members of each claiming cluster, thus node $i$ is able to calculate how many more CCs can be produced in one claiming cluster if $i$ leaves that cluster.
 %Based on this calculation, $i$ decides on one claiming cluster to stay and leaves the other claiming clusters.
-Then node $i$ decides on the cluster $C\in S_i$, if $i$ leaving cluster $C$ results in less increased CCs than leaving any other claiming clusters in $S_i$.
-%As to a cluster $C\in S_i$, if $i$ leaves cluster $C$ and results in less increased CCs than leaving any other claiming clusters, then $i$ chooses to stay in cluster $C$.
-When there comes a tie between two claiming clusters, $i$ chooses to stay in the cluster whose cluster head shares the most CCs with $i$.
-When the tie still exists, node $i$ chooses to stay in the claiming cluster which has the smallest size.
+If there exists one cluster $C\in S_i$, when $i$ leaves this cluster brings the least increased CCs than leaving any other claiming clusters, then $i$ chooses to stay in cluster $C$.
+When there comes a tie, among the claiming clusters, $i$ chooses to stay in the cluster whose cluster head shares the most CCs with $i$.
+In case there are multiple claiming clusters demonstrating the same on the aforementioned metric, node $i$ chooses to stay in the claiming cluster which has the smallest size.
 Node IDs of cluster heads will be used to break tie if all the previous metrics could not decide on the unique claiming cluster for $i$ to stay.
-The pseudo code of this algorithm is given in Algorithm~\ref{alg4}.
+The pseudo code of this algorithm is given as Algorithm~\ref{alg4}.
 %To conduct Algorithm~\ref{alg4}, debatable node $i$ needs to know the necessary information about its claiming clusters, \ie $K(C)$ (the set of available channels in cluster $C$), $K(h_C)$ (the set of available channels on $C$'s cluster head $h_C$) and $|C|, C\in S_i$ (sizes of $i$'s claiming clusters).
@@
 \label{clustering:phaseII:game}
-Game theory is a powerful mathematical tool for studying, modeling and analyzing the interactions among individuals.
-A game consists of three elements: a set of players, a selfish utility for each player, and a feasible strategy space for each player.
+Game theory is a powerful mathematical tool for studying, modelling and analysing the interactions among individuals.
+A game consists of three elements: a set of players, a selfish utility for each player, and a set of feasible strategy space for each player.
 In a game, the players are rational and intelligent decision makers, which are related with one explicit formalized incentive expression (the utility or cost).
@@
 In the past few years, game theory has been extensively applied to problems in communication and networking~\cite{Neel06analysisand, Wang_gtc_crn_survey_2010}.
-Congestion game is an attractive game model which describes the problem where participants compete for limited resources in a non-cooperative manner, it has the good property that Nash equilibrium can be achieved after finite steps of best response dynamic, \ie each player chooses the strategy to maximize/minimize its utility/cost with respect to the other players' strategies.
-The framework of the congestion game has been used to model certain problems in internet-centric applications or cloud computing, where self-interested clients compete for the centralized resources and meanwhile interact with each other.
+Congestion game is an attractive game model which describes the problem where participants compete for limited resources in a non-cooperative manner, it has good property that Nash equilibrium can be achieved after finite steps of best response dynamic, \ie each player choose strategy to maximizes/minimizes its utility/cost with respect to the other players' strategies.
+Congestion game has been used to model certain problems in internet-centric applications or cloud computing, where self-interested clients compete for the centralized resources and meanwhile interact with each other.
 For example, server selection is involved in distributed computing platforms~\cite{Cloud_Computing_2010}, or users downloading files from cloud, etc.
 
-To formulate the debatable nodes' membership clarification into the desired congestion game, we reexamine this process from a different/opposite perspective. 
-From the new perspective, the debatable nodes are not included in any cluster and they need to decide on one cluster to join.
-When a debatable node $i$ join one cluster $C$, the decrease of CCs in cluster $C$ is $\sum_{C\in S_i}\Delta\vert K(C) \vert=\sum_{C\in S_i}({\vert K(C) \vert-\vert K(C\cup i) \vert})$.
-Then, node $i$ chooses the cluster $C$, where the decrease of CCs in cluster $C$ is smaller than the decrease if $i$ would have joined any other claiming cluster in $S_i$.
-The relation between the debatable nodes and the claiming clusters is shown in Figure~\ref{debatable_nodes_claiming_cluster}.
+To formulate the debatable nodes' membership clarification into the desired congestion game, we observe this process from a different (or opposite) perspective. 
+From the new perspective, the debatable nodes are regarded to be isolated and don't belong to any cluster, in other words, their claiming clusters become clusters which are beside them. 
+Now for the debatable nodes, the previous problem of deciding which clusters to leave becomes a new problem that which cluster to join.
+In the new problem, debatable node $i$ chooses one cluster $C$ out of $S_i$ to join if the decrease of CCs in cluster $C$ is the smallest in $S_i$, and the decrease of CCs in cluster $C$ is $\sum_{C\in S_i}\Delta\vert K(C) \vert=\sum_{C\in S_i}({\vert K(C) \vert-\vert K(C\cup i) \vert})$.
+The interaction between the debatable nodes and the claiming clusters is shown in Figure~\ref{debatable_nodes_claiming_cluster}.
 %The concern on convergence appears again as we have discussed in the previous subsubsection.
@@
 In the following, we show that the decision of debatable nodes to clarify their membership can be mapped to the behaviour of the players in a \textit{player-specific singleton congestion game} when proper cost function is given.
-The game to be constructed is represented with a 4-tuple $\Gamma=(\mathcal{P},\mathcal{R},\sum_{i, i \in \mathcal{P}}, f)$ with the following elements:
+The game to be constructed is represented with a 4-tuple $\Gamma=(\mathcal{P},\mathcal{R},\sum_{i, i \in \mathcal{P}}, f)$, and the elements in $\Gamma$ are explained below,
 %To make the model of this game more clear, we make some change to our original problem.
@@
 %	\item $\mathcal{R}=\left\{1,\ldots,m\right\}$, the set of resources which player can choose, which are all the clusters in our model.
-	\item $\mathcal{R} = \cup S_i, i\in \mathcal{P}$, the set of the resources for players to choose.
-In our problem, $S_i$ is the set of the claiming clusters of $i$, and $\mathcal{R}$ is the set of all claiming clusters.
-	\item Strategy space $\sum_i, i \in \mathcal{P}$, $\sum_i$ is the set of the claiming clusters $S_i$.
+	\item $\mathcal{R} = \cup S_i, i\in \mathcal{P}$, denotes the set of resources for players to choose, in our problem, $S_i$ is the set of claiming clusters of node $i$, and $\mathcal{R}$ is the set of all claiming clusters.
+	\item Strategy space $\sum_i, i \in \mathcal{P}$ is the set of claiming clusters $S_i$.
 	As debatable node $i$ is supposed to choose only one claiming cluster, then only one piece of resource will be allocated to $i$.%, accordingly this congestion game is a singleton game.
@@
 Hence, this congestion game is player specific~\cite{Ackermann06purenash}.
-In this game, every player greedily updates its strategy (choosing one claiming cluster to join) if joining a different claiming cluster minimizes the decrease of CCs $\sum_{i:C\in S_i} \Delta\vert K^i(C) \vert$, and a player's strategy in the game is exactly the same with the behaviour of a debatable node in the membership clarification phase.
+In this game, every player greedily updates its strategy (choosing one claiming cluster to join) if joining a different claiming cluster minimizes the decrease of CCs $\sum_{i:C\in S_i} \Delta\vert K^i(C) \vert$, and a player's strategy in the game is exactly the same with the behaviour of a debatable node in the membership clarification phas.
 
@@
 In our problem, the players are the debatable nodes, and the resources are the claiming clusters.
-Thus the number of steps can be expressed as $\mathcal{O}(N^3)$.
-%
-In fact, the upper bound for the number of steps which are involved in this process is much smaller than $N^3$.
-The percentage of debatable nodes in the network is shown in Figure~\ref{percentage_overlapping_node}, which is between 10\% to 60\% of the total CR nodes in the network.
-In the other hand, the number of clusters heads is dependent on the network density and the CR node's transmission range as mentioned in Section~\ref{phaseI}.
-The simulation in \cite{robust_clustering_arxiv} shows the cluster heads are only 3.4\% to 20\% of the total CR nodes.
+Thus the upper bound of the number of steps can be expressed as $\mathcal{O}(N^3)$.
+
+In fact, the number of steps which are actually involved in this process is much smaller than $N^3$, as both $n$ and $m$ are considerably smaller than $N$.
+The percentage of debatable nodes in $\mathcal{N}$ is illustrated in Figure~\ref{percentage_overlapping_node}, which is between 10\% to 60\% of the total number of CR nodes in the network.
+The number of clusters heads, as discussed in Section~\ref{phaseI}, is dependent on the network density and the CR node's transmission range.
+As shown in Figure~\ref{number_clusters_scale}, the cluster heads take up only 3.4\% to 20\% of the total number of CR nodes.
 
@@
 On the basis of ROSS-DGA, we propose a faster version ROSS-DFA which differs from ROSS-DGA in the second phase.
-With ROSS-DFA, debatable nodes decide their respective cluster heads only once.
-The debatable nodes consider their claiming clusters to include all their debatable nodes, thus the membership of claiming clusters is static and all the debatable nodes can make decisions simultaneously without considering the change of membership of their claiming clusters.
-As ROSS-DFA is quicker than ROSS-DGA, the former is especially suitable for the CRN where the channel availability changes frequently.
-To run ROSS-DFA, debatable nodes execute only one loop in Algorithm~\ref{alg4}.
+With ROSS-DFA, debatable nodes decide their respective cluster heads once.
+The debatable nodes consider their claiming clusters to include all their debatable nodes, thus the membership of claiming clusters is static and all the debatable nodes can make decision simultaneously without considering the change of membership of their claiming clusters.
+As ROSS-DFA is quicker than ROSS-DGA, the former is especially suitable for the CRN where the channel availability changes dynamically and re-clustering is necessary.
+To run ROSS-DFA, debatable node executes only one loop in Algorithm~\ref{alg4}.
 
@@
 The two possible strategies of node $A$ is illustrated in Figure \ref{fig3}.
-In Figure \ref{AinC}, node $A$ staying in $C(C)$ and leaving $C(H)$ brings 2 more CCs to $S_A$, which is more than that brought by another strategy shown in \ref{AinH}.
+In Figure \ref{AinC}, node $A$ staying in $C(C)$ and leaving $C(H)$ brings 2 more CCs to $S_A$, which is more than that brought by another strategy showed in \ref{AinH}.
 After the decisions made similarly by the other debatable nodes $B$ and $D$, the final clusters are formed as shown in Figure~\ref{final_clustering_ross}.
@@
 %In this section, we evaluate the performances of ROSS.
-The schemes involved in the simulation are as follows,
+The schemes involved in the simulation are listed as follows,
 \begin{itemize}
-\item ROSS without size control, \ie ROSS-DGA, ROSS-DFA.
-\item ROSS with size control, \ie ROSS-$\delta$-DGA and ROSS-$\delta$-DFA where $\delta$ is the desired cluster size.
+\item ROSS without size control, \ie ROSS-DGA and ROSS-DFA.
+\item ROSS with size control. \ie ROSS-$\delta$-DGA and ROSS-$\delta$-DFA where $\delta$ is the desired cluster size.
 In the following, we refer to the above mentioned four schemes as the variants of ROSS.
@@
 \item Centralized robust clustering scheme. 
-As shown in Section~\ref{centralized_solution}, the centralized robust clustering scheme is formulated as an integer linear optimization problem and is solved by MATLAB with the function $bintprog$.
+The formulated optimization is an integer linear optimization problem, which is solved by MATLAB with the function $bintprog$.
 \end{itemize}
@@
 SOC's comparison schemes are designed either for ad hoc network without consideration of channel availability~\cite{Basagni99}, or for CRN but just considering connection among CR nodes~\cite{Zhao07}.
-Thus SOC is the only distributed scheme as comparison.
-As to the CRN shown in Figure~\ref{fig1}, the resulting clusters by the centralized scheme and SOC are shown in Figure~\ref{fig:final_clustering}.
-
-%Before we investigating the performance of the clustering schemes with simulation, we apply the two comparison clustering schemes in the example CRN in Figure~\ref{fig1}, and make an initial comparison in terms of the amount of CCs.
-%As to the centralized robust clustering scheme, we set the desired cluster size $\delta$ as 3, as a result, according to the network topology, the collection of all the possible clusters
-%$\mathcal{S}=\{\{A\}, \{B\},\dots,\{B,C\},\{B,A\},\{B,H\},\cdots,\{B,A,C\},$\\$\{B,H,C\}, \{A,D,C\},\cdots\}$, and $|\mathcal{S}|=38$.
-%We set $\rho_1$ and $\rho_1$ as 0.2 and 0.8 respectively.
-%The formed clusters by the centralized clustering scheme are shown in Fig.~\ref{fig:final_clustering_LP}.
-%%$\{\{D,E,F\},\{A,C,G\},\{H,G\}\}$, the numbers of CCs are 2, 3, 3.
-%The resulted clustering solutions from SOC is shown in Fig.~\ref{fig:final_clustering_soc}.
-%%
-%We compare the average number of CCs achieved by different schemes, the results of ROSS\footnote{In this example network, both ROSS-DGA and ROSS-DFA and their size control variants form the same clusters)}, centralized and SOC are 2.66, 2.66, and 3 respectively.
-%Note there is one singleton cluster $C(H)$ generated by SOC, which is not preferred.
-%When we only consider the clusters which are not singleton, the average number of CCs of SOC drops to 2.5. 
+Thus SOC is chosen to be the only distributed scheme as comparison, besides, we also compare ROSS with the centralized scheme.
+
+Before we investigating the performance of the clustering schemes with simulation, we apply the two comparison clustering schemes in the example CRN in Figure~\ref{fig1}, and make an initial comparison in terms of the amount of CCs.
+As to the centralized robust clustering scheme, we set the desired cluster size $\delta$ as 3, as a result, according to the network topology, the collection of all the possible clusters
+$\mathcal{S}=\{\{A\}, \{B\},\dots,\{B,C\},\{B,A\},\{B,H\},\cdots,\{B,A,C\},$\\$\{B,H,C\}, \{A,D,C\},\cdots\}$, and $|\mathcal{S}|=38$.
+We set $\rho_1$ and $\rho_1$ as 0.2 and 0.8 respectively.
+The formed clusters by the centralized clustering scheme are shown in Fig.~\ref{fig:final_clustering_LP}.
+%$\{\{D,E,F\},\{A,C,G\},\{H,G\}\}$, the numbers of CCs are 2, 3, 3.
+The resulted clustering solutions from SOC is shown in Fig.~\ref{fig:final_clustering_soc}.
+%
+We compare the average number of CCs achieved by different schemes, the results of ROSS\footnote{In this example network, both ROSS-DGA and ROSS-DFA and their size control variants form the same clusters)}, centralized and SOC are 2.66, 2.66, and 3 respectively.
+Note there is one singleton cluster $C(H)$ generated by SOC, which is not preferred.
+When we only consider the clusters which are not singleton, the average number of CCs of SOC drops to 2.5. 
 \begin{figure}[ht]
@@
 
-We investigate the schemes with respect to four metrics.
+We investigate the schemes with four metrics.
 
@@
 \item \textbf{The average number of CCs per non-singleton cluster.}
-Non-singleton cluster refers to the cluster whose cluster size is larger than one.
-Previous work \cite{LIU_TMC11_2} and \cite{Li11_ROSS} claim that the larger average number of CCs over all the clusters indicates robustness , from which we see two flaws.
-First, the unclustered CR nodes (synonym of singleton clusters) should not be considered when calculating the average number of CCs, as singleton clusters don't contribute to the collaborative computing or sensing.
-Second, the average number of CCs doesn't necessarily indicate the robustness of individual clusters, because the ability for a cluster to sustain also depends on cluster size and the locations of the cluster members, but these information can not be illustrated in the average number of CCs.
-In the performance evaluation, we will examine the metric of average number of CCs per non-singleton cluster, which excludes the bias brought in by the unclustered CR nodes.
-Moreover, we will examine whether this metric reflects the robustness of the clusters.
+Non-singleton cluster refers the cluster whose cluster size is larger than 1.
+%This metric denotes the robustness of the formed non-singleton clusters.
+Comparing with the metric adopted by SOC~\cite{LIU_TMC11_2}, which is the average number of CCs of all the clusters, this metric provides a more accurate description of the robustness of the non-singleton clusters.
+Having more CCs per non-singleton clusters means these clusters have longer life expectancy when the primary users' operation becomes more intense.
+%which is biased as the singleton clusters (isolated CR users) don't get benefits from the cluster structure.
+Although this metric doesn't disclose the information about the \textit{unclustered} CR nodes which are the synonyms of the singleton clusters, we still examine this metric as the number of CCs is involved in the utility adopted by all the variants of ROSS and SOC.
 
@@
 We increase the number of PUs to challenge the non-singleton clusters, and count the number of the unclustered CR nodes.
-This metric indicates the robustness of the clusters, \ie as to the clusters formed for a given CRN and spectrum availability, how many CR nodes can still be benefited from the clusters when the spectrum availability decreases.
+This metric directly indicates the robustness of clusters from a more practical point of view, \ie as to the clusters formed for a given CRN and spectrum availability, how many CR nodes can still make use of the clusters when the spectrum availability decreases.
+%robustness of clusters, as this metric directly shows how many nodes can make use of the cluster structure.
+%When we investigate the performance with moderate and vigorous intensity of primary users' activities, 
+%All the robust clustering schemes are proposed for a given CRN, when the available spectrum becomes scarce when the primary users' operation becomes more intense, the metric can illustrate the robustness of clusters by showing the unclustered CR nodes.
+%This metric is closely related with cluster robustness, \ie the less CR nodes which are not  nodes means more CR nodes are included into non-singleton clusters which survive the primary users' influence.
+%When we vary the intensity of primary users' activity, \eg from low to medium level by increasing the number of primary users, 
+%The drawback of this metric is, it doesn't indicate the robustness of the non-singleton clusters when the primary users conquer more spectrum.
 
@@
 In the second part, we investigate the performance of the proposed distributed schemes in the CRN with different scales and densities.
-The following simulation setting is the same for both simulation parts.
+The following simulation settings is the same for both simulation parts.
 CRs and PUs are deployed on a two-dimensional Euclidean plane.
@@
 The number of licensed channels is 10, each PU is operating on each channel with probability of 50\%.
-The constant $t$ which is used to control cluster size for ROSS (discussed in Section~\ref{ross_p2_cluster_pruning}) is 1.3.
 CR users are assumed to be able to sense the existence of primary users and identify available channels.
@@
 The desired cluster size $\delta$ is 3.
-As for the centralized scheme, the parameters used in the \textit{punishment} for choosing the clusters with undesired sizes are set as follows, $\rho_1 =  0.4$, $\rho_2 =  0.6$.
-
-\subsubsection{CCs in Non-singleton Clusters}
+As to the centralized scheme, the parameters used in the \textit{punishment} for choosing the clusters with undesired sizes are set as follows, $\rho_1 =  0.4$, $\rho_2 =  0.6$.
+
+\subsubsection{Average number of CCs in Non-singleton Clusters}
 \label{ccc_20}
@@
 %We have discussed the flaw of this metric as it doesn't convey the number of unclustered CR nodes, in fact, 
-On the other hand, SOC generates the most unclustered CRs.
+In the other hand, SOC generates the most unclustered CRs, which can be seen when we discuss the performance on the number of unclustered CR nodes. 
 As to the variants of ROSS, we notice that the greedy mechanism increases CCs in non-singleton clusters significantly.
@@
 \begin{multicols}{3}
-    \includegraphics[width=\linewidth]{ccc_20.pdf}\par\caption{Average number of CCs of non-singleton clusters}\label{ccc_per_nonsingleton}
+    \includegraphics[width=\linewidth]{ccc_20.pdf}\par\caption{Number of common channels of non-singleton clusters}\label{ccc_per_nonsingleton}
     \includegraphics[width=\linewidth]{cdf_clusterSize_20.pdf}\par\caption{Cumulative distribution of CRs residing in clusters with different sizes}\label{size_control}    
@@
 Figure~\ref{size_control} depicts the empirical cumulative distribution of the CRs in clusters of different sizes, from which we have two conclusions.
-First, given the channel availability in the CRN, SOC generates more unclustered CR nodes than other schemes.
+The first, SOC generates more unclustered CR nodes than other schemes.
 The centralized schemes don't produce unclustered CR nodes in the simulation, the unclustered nodes generated by ROSS-DGA/DFA account for 3\% of the total CR nodes, as comparison, 10\% of nodes are unclustered when applying SOC.
@@
 
-\subsubsection{Robustness of the formed clusters}
+\subsubsection{Robustness of the clusters against newly added PUs}
 %When the number of PUs in CRN increases, or their operation becomes more intensive, some clusters don't seize any CCs any more, so that the cluster members and the cluster heads become unclustered, or singleton clusters.
-%If there is no common channels available any more because of the new added PUs, the cluster is regarded as destroyed and the former cluster member CRs become unclustered CRs or in other words singleton clusters.
+%If there is no common channels available any more because of the new added PRs, the cluster is regarded as destroyed and the former cluster member CRs become unclustered CRs or in other words singleton clusters.
 %We investigate the number of singleton clusters with primary users whose intensity of activities are varying.
@@
 10 PUs are in the network in the beginning, then extra 19 batches of PUs are added sequentially, where each batch includes 5 PUs. 
-%
+%The transmission range and channel occupancy of the new PU is the same with the previous ones, \ie transmission range is $A/3$, and one channel out of 10 is randomly chosen to operate.
+
 Figure~\ref{singleton_clusters} shows certain clusters can not maintain and the number of unclustered CR nodes grows when the number of PUs increases.
@@
 In contrary, the variants of ROSS generate some smaller clusters which are more likely to maintain when there are more PUs.
-
-The above observation shows that the average number of CCs of non-singleton clusters doesn't necessarily illustrate the robustness  of cluster, \ie SOC obtains the most CCs for the clusters which are meanwhile the most vulnerable.
-Besides, with similar distribution of sizes, the clusters generated by ROSS-DGA and ROSS-DFA are more robust than that by SOC.
+%The comparison on cluster sizes will be given in Section~\ref{cluster_size}.
+% when the number of PRs is 10$\sim$30, when number of PUs is 30$\sim$60, same amount of unclustered CRs are generated with variants of ROSS.
+%When there are 75 and more new PRs, centralized scheme with cluster size of 3 results in more unclustered CR nodes than variants of ROSS.
+%ROSS with size control distinguishes itself as the size control avoid the appearance of the clusters with large size.
+
+%As to the variants of ROSS, the greedy process in ROSS improves the performance.
+
+%Greedy strategy adopted in the second phase of ROSS improves the robustness of clusters, i.e. ROSS-DGA exceeds ROSS-DFA, and ROSS-$\delta$-DGA surpasses ROSS-$\delta$-DFA.
+%When the debatable CRs greedily update their affiliations, one of the metrics is the maximum increase of CCs of the demanding clusters. 
+%This observation complies with the result shown in Figure~\ref{ccc_per_nonsingleton}.
+%Meanwhile, sizes of more clusters become smaller also contributes more robustness.
+
+%\begin{figure}[h!]
+%  \centering
+%  \includegraphics[width=0.8\linewidth]{ccc_20.pdf}
+%  \caption{Number of common channels for non-singleton clusters, the numbers in the names of schemes annotate the desired cluster size.}
+%  \label{ccc_per_nonsingleton}
+%\end{figure}
+%
+%
+%\begin{figure}[h]
+%  \centering
+%  \includegraphics[width=0.8\linewidth]{survival_rate_20.pdf}
+%  \caption{Number of CRs which are not included in any clusters}
+%  \label{singleton_clusters}
+%\end{figure}
 
 \subsubsection{Control Signaling Overhead}
+%Different from the clustering schemes proposed in ~\cite{LIU_TMC11_2, clustering_globecom11}, 
+%There are two phases for any variants of ROSS.
+%Clusters are formed in the first phase, in the second phase, cluster membership is decided so that each node only resides in one cluster.
+%Control message exchanges between CR nodes are involved in both phases.
 
 In this section we compare the overhead of signaling involved in different clustering schemes.
-We count the number of \textit{transmissions of control messages} as message complexity~\cite{complexity_aggregation_2011}, and without distinguishing broadcast or uni-cast control messages.
-In Section~\ref{ross}, this metric is synonymous with the \textit{the number of updates}.
-%We don't consider the the control messages which are involved in neighborhood discovery, which is the premise and deemed to be the same for all clustering schemes.
-%According to~\cite{complexity_aggregation_2011}, the message complexity is defined as the number of messages used by all nodes.
-%To have the same metric to compare,
-
-As to ROSS, in the first phase the maximal number of broadcast is $N$ according to~\ref{clustering:theorem}.
-The upper bounds for the transmissions are $n^2m$ and $n$ for ROSS-DGA and ROSS-DFA respectively.
-Scheme SOC consists of three rounds, and in each round every node needs to broadcast to do comparisons and cluster mergers.
-The centralized scheme is conducted at the centralized control device, which involves information aggregation and clustering decision dissemination.
-We adopt the backbone structure proposed in~\cite{Efficient_broadcasting_gathering_adhoc} to analyze the centralized scheme's message complexity.
-We apply ROSS to generate cluster heads which serve as the backbone.
-In the process of information aggregation, all the nodes transmit information to the cluster heads which forward the messages to the controller, then in the process of dissemination, all the cluster heads and the debatable nodes broadcast the clustering result, thus the upper bound for the number of broadcast is $N+m+n$.
-
-%
-%, when a CR node decides itself to be the cluster head, it broadcasts a message containing its ID, cluster members and the set of CCs in its cluster.
-%In the second phase, a debatable node broadcasts its affiliation to inform its claiming clusters, then the cluster heads of the claiming clusters broadcast message about the new cluster members if they are changed due to the debatable node's decision.
-%The upper bound of the total number of the control messages involved in cluster formation is analyzed in Theorem~\ref{clustering:theorem} and Section~\ref{clustering:phaseII:game}.
-%
-%The comparison scheme SOC consists of three rounds of execution. 
-%In the first two rounds, every CR node maintains its own cluster and seeks either to integrate neighboring clusters or to join one neighboring cluster.
-%The final clusters are obtained in the third round. 
-%In each round, every CR node is involved in comparisons and cluster mergers.
-%%Comparing with the second phase of ROSS, only debatable nodes to communicate with cluster heads to clarify their membership.
-%%The signalling overhead for centralized scheme comes from two processes, the the process of collecting information to the centralized controller, and the process that the controller spreads the clustering result to all the CR nodes.
-%
-%The centralized scheme is conducted at the centralized control device, but it involves two phases of control message transmission.
-%The first phase is information aggregation, in which every CR node's channel availability and neighborhood is transmitted to the centralized controller.
-%iIn the second phase, the control broadcasts the clustering solution, which is disseminated to every CR node.
-%%
-%We adopt the algorithm proposed in~\cite{Efficient_broadcasting_gathering_adhoc} to broadcast and gather information as the algorithm is simple and self-stabilizing.
-%This scheme needs building a backbone structure to support the communication. 
-%We apply ROSS to generate cluster heads which serve as the backbone, and the debatable nodes are used as the gateway nodes between the backbone nodes.
-%As the backbone is built for one time and supports the transmission of control messages later on, we don't take account the messages involved in building the backbone.
-%As to the process of information gathering, we assume that every cluster member sends the spectrum availability and its ID to its cluster head, which further forwards the message to the controller, then the number of transmissions is $N$.
-%As to the process of dissemination, in an extreme situation where all the gateway and the backbone nodes broadcast, the number of transmissions is $m + n$, where $m$ is the number of cluster heads and $n$ is number of debatable nodes.
+%In order to highlight the amount of control signalling only for clustering, 
+We don't consider the the control messages which are involved in neighborhood discovery, which is the premise and deemed to be the same for all clustering schemes.
+According to~\cite{complexity_aggregation_2011}, the message complexity is defined as the number of messages used by all nodes.
+To have the same metric to compare, we count \textit{the number of transmissions of control messages}, without distinguishing broadcast or uni-cast control messages.
+This metric is synonymous with \textit{the number of updates} discussed in Section~\ref{ross}.
+
+As to ROSS, the control messages are generated in both phases.
+In the first phase, when a CR node decides itself to be the cluster head, it broadcasts a message containing its ID, cluster members and the set of CCs in its cluster.
+In the second phase, a debatable node broadcasts its affiliation to inform its claiming clusters, then the cluster heads of the claiming clusters broadcast message about the new cluster members if they are changed due to the debatable node's decision.
+The upper bound of the total number of the control messages involved in cluster formation is analyzed in Theorem~\ref{clustering:theorem} and Section~\ref{clustering:phaseII:game}.
+
+The comparison scheme SOC involves three rounds of execution. 
+In the first two rounds, every CR node maintains its own cluster and seeks either to integrate neighboring clusters or to join one neighboring cluster.
+The final clusters are obtained in the third round. 
+In each round, every CR node is involved in comparisons and cluster mergers.
+%Comparing with the second phase of ROSS, only debatable nodes to communicate with cluster heads to clarify their membership.
+%The signalling overhead for centralized scheme comes from two processes, the the process of collecting information to the centralized controller, and the process that the controller spreads the clustering result to all the CR nodes.
+
+The centralized scheme is conducted at the centralized control device, but it involves two phases of control message transmission.
+The first phase is information aggregation, in which every CR node's channel availability and neighborhood is transmitted to the centralized controller.
+iIn the second phase, the control broadcasts the clustering solution, which is disseminated to every CR node.
+%
+We adopt the algorithm proposed in~\cite{Efficient_broadcasting_gathering_adhoc} to broadcast and gather information as the algorithm is simple and self-stabilizing.
+This scheme needs building a backbone structure to support the communication. 
+We apply ROSS to generate cluster heads which serve as the backbone, and the debatable nodes are used as the gateway nodes between the backbone nodes.
+As the backbone is built for one time and supports the transmission of control messages later on, we don't take account the messages involved in building the backbone.
+As to the process of information gathering, we assume that every cluster member sends the spectrum availability and its ID to its cluster head, which further forwards the message to the controller, then the number of transmissions is $N$.
+As to the process of dissemination, in an extreme situation where all the gateway and the backbone nodes broadcast, the number of transmissions is $h + m$, where $h$ is the number of cluster heads and $m$ is number of debatable nodes.
+%, $d$ is the average number of demanding clusters for each debatable node.
 
 The number of control messages which are involved in ROSS variants and the centralized scheme is related with the number of debatable nodes.
-Figure~\ref{percentage_overlapping_node} shows the percentage of debatable nodes with different network densities.
+Figure~\ref{percentage_overlapping_node} shows the percentage of debatable nodes with different network densities, from which we can obtain the value of $m$.
 \begin{figure}[ht!]
@@
 \begin{threeparttable}
-\begin{tabular}{|C{1.8 cm}|C{2.6 cm}|C{3 cm}|C{6.3 cm}|}
+\begin{tabular}{|C{2 cm}|C{2.8 cm}|C{3.15 cm}|C{7.7 cm}|}
 \hline
- Scheme 				&Message Complexity 	&   Quantitative number of messages 		& Content and size of the message 									\\ \hline
- ROSS-DGA, ROSS-$\delta$-DGA 	&$\mathcal{O}(N^3)$ (worst case)		&   $N+n^2m$ (upper bound)  				&   \multirow{2}{*}{\parbox{7.7cm}{PhaseI: ID, $d_i$,$g_i$, which are 3 bytes;\\ PhaseII: Cluster head $i$ broadcasts channel availability to all \\ members, where are $|C(i)| |\mathcal{K}|$ bytes}}								\\ \cline{1-3}
- ROSS-DFA, ROSS-$\delta$-DFA 	&$\mathcal{O}(N)$ (worst case)		&   $N + n$	 (upper bound) 					& 	      												\\ \hline
- SOC 					&$\mathcal{O}(N)$		&   $3N$									& Every CR node $i$ broadcasts channel availability on all cluster members, which is $|C(i)| |\mathcal{K}|$ bytes
+ Scheme 				&Message Complexity 	&   Quantitative number of messages 		& Content of message (size of message) 									\\ \hline
+ ROSS-DGA, ROSS-$\delta$-DGA 	&$\mathcal{O}(N^3)$ (worst case)		&   $h+2m^2d$ (upper bound)  				&   \multirow{2}{*}{\parbox{7.7cm}{Cluster head $i$ broadcasts channel availability on all cluster members ($|C(i)| |\mathcal{K}|$ bytes); Cluster member $i$ broadcasts the new individual connectivity $d_i$ after being included in one or more clusters (1 byte)}}								\\ \cline{1-3}
+ ROSS-DFA, ROSS-$\delta$-DFA 	&$\mathcal{O}(N)$ (worst case)		&   $h + 2m$	 (upper bound) 					& 	      												\\ \hline
+ SOC 					&$\mathcal{O}(N)$		&   $3N$									& Every CR node $i$ broadcasts channel availability on all cluster members ($|C(i)| |\mathcal{K}|$ bytes)
  \\ \hline
- Centralized			&$\mathcal{O}(N)$			&	$N + n + m$ (upper bound) 		& clustering result, which is 2$N$ bytes \tnotex{tnote:robots-r1} 					\\ \hline
+ Centralized			&$\mathcal{O}(N)$			&	$h + m + N$ (upper bound)~\cite{Efficient_broadcasting_gathering_adhoc}		& clustering result (2$N$ bytes) \tnotex{tnote:robots-r1} 					\\ \hline
 \end{tabular}
     \begin{tablenotes}
-      \item\label{tnote:robots-r1}Assuming the data structure of the clustering result is in the form of $\{i, C\}, i\in C, i\in \mathcal{N}$.
+      \item\label{tnote:robots-r1}Assuming the data structure of the clustering result is in the form of \{ Node ID $i$, cluster head ID h($C$) where $i\in C$, for every $i\in \mathcal{N}$ \}.
     \end{tablenotes}
@@
 \label{largeScaleCRN}
-In this section we investigate the performances of the proposed distributed clustering schemes in CRN with different network scales and densities.
+In this section we investigate the performances of distributed clustering schemes in CRN with different network scales and densities.
 The transmission range of CR is $A/5$, PU's transmission range is $2A/5$.
@@
 %The number of CR is 100, 200 and 300, and the average number of neighbours of each CR is 9.5, 20, and 31.
-The desired sizes adopted are listed in the Table~\ref{Simulation_para}, which is about 60\% of the average number of neighbors.
-%When run ROSS, the parameter $t$ which is used to control cluster size in phase I is 1.3.
+The desired sizes adopted are listed in the Table~\ref{Simulation_para}, which is about 60\% of the average number of neighbours.
+When run ROSS, the parameter $t$ which is used to control cluster size in phase I is 1.3.
 
@@
 {\small
-%\hfill{}
-\begin{tabular}{|L{3 cm}|C{0.85 cm}|C{0.85 cm}|C{0.85 cm}|}
+\hfill{}
+\begin{tabular}{|L{3.7 cm}|C{1 cm}|C{1 cm}|C{1 cm}|}
 \hline
 Number of CRs			& 100 	&  200 					& 300 \\ \hline
-Average num. of neighbors 	&9.5	&   20		& 31  \\ \hline
+Average num. of neighbours 	&9.5	&   20		& 31  \\ \hline
 Desired size $\delta$ 	& 6	&   12 						& 20      \\ \hline
@@
 }
-%\hfill{}
+\hfill{}
 \end{table}
@@
   \includegraphics[width=.7\linewidth]{ccc_large_scale_color.pdf}
-  \caption{Average number of CCs of non-singleton clusters}
+  \caption{Number of common channels of non-singleton clusters.}
   \label{ccc_large_scale}
@@
 
-The average number of CCs of the non-singleton clusters is shown in Figure~\ref{ccc_large_scale}.
-SOC achieves the most CCs per non-singleton cluster, but the lead over the variants of ROSS decreases significantly when $N$ increases.
+Figure~\ref{ccc_large_scale} shows the average number of CCs of the non-singleton clusters.
+We notice that SOC achieves the most CCs per non-singleton cluster, although the lead over the variants of ROSS shrinks significantly when $N$ increases.
 %\ie when $N=300$, the number of CCs achieved by ROSS variants (except for ROSS-$\delta$-DFA) is almost the same as that resulted from SOC.
@@
 
-\subsubsection{Robustness of the formed clusters}
-We increase the primary users' activity by importing 20 batches of PUs sequentially in the CRN, where each batch includes 10 PUs. 
-%
-Figure~\ref{singleton_clusters_100} and \ref{singleton_clusters_200} show that when $N=100$ and 200, compared with the variants of ROSS, more unclustered CR nodes are generated by SOC.
-When $N=300$ as shown in Figure~\ref{singleton_clusters_300} and the new PUs are not many, ROSS-DGA/DFA generate slightly more unclustered CR nodes than SOC, but SOC's performance deteriorates quickly when the PUs continue increasing.
-%
-From Figure~\ref{singleton_clusters_100} to~\ref{singleton_clusters_300}, we can see that significantly less unclustered CR nodes are generated by the variants of ROSS which have size control mechanism.
+\subsubsection{Robustness of the clusters against newly added PUs}
+We add extra 20 batches of PUs sequentially in the CRN, where each batch includes 10 PUs. 
+Figure~\ref{singleton_clusters_100} and \ref{singleton_clusters_200} show that when $N=100$ and 200, more unclustered CR nodes appear in the CRN where SOC is applied.
+When the network becomes denser, as shown in Figure~\ref{singleton_clusters_300}, ROSS-DGA/DFA generate slightly more unclustered CR nodes than SOC when new PUs are not many, but SOC's performance deteriorates quickly when the number of PUs becomes larger.
+We only show the average values of the variants of ROSS as their confidence intervals overlap.
+%
+When applying ROSS with size control mechanism, significantly less unclustered CR nodes are generated.
 Besides, the greedy mechanism moderately strengthens the robustness of the clusters.
-We only show the average values of the variants of ROSS as their confidence intervals overlap.
 
@@
     \includegraphics[width=\linewidth]{survival_rate_300_edge50.pdf}\par\caption{300 CRs}\label{singleton_clusters_300}
-\end{multicols}
-%\caption{Percentage of CR nodes which are not included in any non-singleton clusters}
-%\label{unclustered_100_200_300}
+\end{multicols}\caption{Percentage of CR nodes which are not included in any non-singleton clusters}
+\label{unclustered_100_200_300}
 \end{figure*}
@@
 \end{multicols}
-%\caption{Cumulative distribution of CRs residing in clusters with different sizes}
-%\label{cdf_100_200_300}
+\caption{Cumulative distribution of CRs residing in clusters with different sizes}
+\label{cdf_100_200_300}
 \end{figure*}
@@
 \subsubsection{Cluster Size Control}
-Figure~\ref{nClusters_largeNetwork} shows when the network density increases, \ie $N$ changes from 100 to 300, the number of generated clusters by SOC increases linearly, whereas that by ROSS increases by a smaller margin.
+Figure~\ref{nClusters_largeNetwork} shows when the network density scales up, the number of formed clusters by ROSS increases by smaller margin, and that generated by SOC increases linearly.
 This result coincides with the analysis in Section~\ref{ross_p2_cluster_pruning}.
 %When the network becomes denser, more clusters are generated by SOC compared with ROSS variants.
-To better understand the distribution of the sizes of formed clusters, for each network density, we depict the empirical cumulative distribution of CR nodes which are in clusters with different sizes in Figures~\ref{cdf_clusterSize_100}~\ref{cdf_clusterSize_200}~\ref{cdf_clusterSize_300} respectively.
+To better understand the distribution of the sizes of formed clusters, we depict the empirical cumulative distribution of CR nodes in clusters with different sizes in Figures~\ref{cdf_clusterSize_100}~\ref{cdf_clusterSize_200}~\ref{cdf_clusterSize_300}.
+
 \begin{figure}[!h]
@@
 
-The variants of ROSS generate more clusters whose sizes are closer to the desired size, \ie when $N=100$ and desired cluster size is 6 as shown in Figures~\ref{cdf_clusterSize_100}, 90\% of CR nodes are in the clusters whose sizes are from 3 to 9, while as to SOC, only 17\% of nodes are in the clusters with these sizes.
-Similarly, when $N=200$ and the desired size is 12 as shown in Figure~\ref{cdf_clusterSize_200}, 80\% of nodes are in the clusters whose sizes are from 6 to 18, meanwhile only 30\% of nodes constitute clusters of these sizes when SOC is executed.
-%Now we check how many CR nodes are in the clusters whose sizes deviate not much from the desired size, where we put the deviation limit at $\pm 50\%$ of the desired size.
-The clusters sizes from ROSS-$\delta$-DGA and ROSS-$\delta$-DFA concentrates more than that from ROSS-DGA and ROSS-DFA.
-In contrary, the clusters from SOC demonstrates obvious divergence on cluster sizes.
-
-%As to ROSS-DGA, the 95\% percentiles of the ROSS-DGA curves are 8, 18 and 20.
-%When the size control feature is implemented, the 95\% percentiles of ROSS-$\delta$-DGA is 5,12,13. 
-%Meanwhile, the 50\% percentiles of the ROSS-DGA curves are 6, 10 and 14 respectively, and the 50\% percentiles of the ROSS-$\delta$-DGA are 4,7,9.
-%As comparison, the 95\% percentiles of SOC are 36, 30, and 40 in the respective networks.
-
-%This means that the sizes of the clusters generated by ROSS-DGA are limited by the network density, and the size control feature further restricts the appearances of the big clusters, thus when the variants of ROSS are implemented, most of the CR nodes are in the clusters which are slightly smaller than the desired size.
+The sizes of clusters generated by ROSS-DGA and ROSS-DFA span a wider range than ROSS with size control feature.
+Most of the generated clusters are smaller than the average number of neighbours, which is roughly equal with the 95\% percentile of the ROSS-DGA curve.
+The 50\% percentile of the ROSS-DGA curve is roughly the desired size $\delta$.
+When the variants of ROSS with size control feature are applied, the sizes of the most generated clusters are smaller than $\delta$.
+As to the curves of SOC, the 95\% percentiles are 36, 30, and 40 in respective networks.
+%
+From Figure~\ref{cdf_100_200_300}, we conclude that the sizes of the clusters generated by ROSS are limited by the network density, the sizes of the clusters formed by ROSS with size control feature are restricted by the desired size.
+In contrary, the clusters generated from SOC demonstrate strong divergence on cluster sizes.
 
 \subsection{Insights Obtained from the Simulation}
-The simulation made with the large CRN network confirms that made with the small CRN network, which is that the average number of CCs along doesn't tell the robustness of the clusters, because the cluster size and the constitution of the cluster also affect the robustness.
-
-The centralized clustering scheme is able to form the clusters which satisfy the requirement on cluster size strictly, and the clusters are robust against the PUs' activity, besides, it involves the smallest control overhead in the process of clustering.
+The centralized clustering scheme is able to form the clusters which satisfy the requirement on cluster size strictly, and the clusters are robust against the PUs' activity, besides, it generates the smallest control overhead in the process of clustering.
+
 As distributed schemes, the variants of ROSS outperform SOC considerably on three metrics.
-First, the variants of ROSS generate less unclustered nodes than SOC for a given CRN, and the resulted clusters are more robust than SOC when PUs become more active.
-Second, the signaling overhead involved in ROSS is about half of that needed for SOC, and the signaling messages are much shorter that the latter.
-Third, the sizes of the clusters generated by ROSS demonstrate smaller discrepancy than that of SOC.
-Moreover, the ROSS variants with size control features achieve similar performance to the centralized scheme in terms of cluster size, and the cluster robustness is similar when applying the variants of ROSS and the centralized scheme respectively.
-%
-As to the variants of ROSS, the greedy mechanism in ROSS-DGA helps to improve the performance on cluster size and cluster robustness at the cost of increased signaling overhead.
-%We also notice that as a metric, the number of CCs per non-singleton cluster doesn't indicate the robustness of clusters as shown in Figure~\ref{singleton_clusters} and \ref{unclustered_100_200_300}, although it is adopted as the metric in the formation of clusters.
+The variants of ROSS generate much less singleton clusters than SOC, and the resulted clusters are robuster than SOC when facing the newly added PUs.
+The signaling overhead involved in ROSS is about half of that needed for SOC, and the signaling messages are much shorter that the latter.
+The sizes of the clusters generated by ROSS demonstrate smaller discrepancy than that of SOC.
+Besides, the ROSS variants with size control features achieve similar performance to the centralized scheme in terms of cluster size, and the cluster robustness is similar when applying the variants of ROSS and the centralized scheme respectively.
+
+As to the variants of ROSS, the greedy mechanism in ROSS-DGA helps to improve the performance on cluster size and cluster robustness at the cost of mildly increased signaling overhead.
+We also notice that  as a metric, the number of CCs per non-singleton cluster doesn't indicate the robustness of clusters as shown in Figure~\ref{singleton_clusters} and \ref{unclustered_100_200_300}, although it is adopted as the metric in the formation of clusters.
 
@@
 \label{conclusion}
-In this paper we investigate the robust clustering problem in CRN extensively and propose both centralized and distributed clustering solutions.
-We give the mathematical description of the problem and prove the NP hardness of it.
-The proposed clustering schemes generate clusters which have long life expectancy against the primary users' activity, and the generated clusters have similar sizes with the desired one.
-%The congestion game model in game theory is used to design the distributed schemes.
+In this paper we investigate the robust clustering problem in CRN extensively.
+%generate robust clusters against primary users' influence, so that more CR users can benefit from operative decision making provided by the clusters.
+We provide the mathematical description of the problem and prove the NP hardness of it.
+We propose both centralized and distributed schemes ROSS, the cluster structure generated by them has longer time expectancy against the primary users' activity.
+Besides, the proposed schemes can generate clusters with desired sizes.
+The congestion game model in game theory is used to design the distributed schemes.
 %A Light weighted clustering scheme ROSS is also proposed.
-Through simulation, the distributed schemes demonstrate similar performance with the centralized scheme in terms of cluster robustness, signaling overhead and cluster sizes, and outperform the comparison distributed scheme on all metrics.
-
-The limitation of distributed scheme ROSS is it doesn't generate clusters whose sizes exceed the cluster head's neighborhood.
+Through simulation and theoretical analysis, we find that distributed schemes achieve similar performance with centralized optimization in terms of cluster robustness, signaling overhead and cluster sizes, and outperform the comparison distributed scheme on the above mentioned metrics.
+%, which is important to form clusters which maintains unbroken to the greatest extent possible under primary users' activity.
+%These schemes outperform other distributed clustering scheme in terms of both cluster survival ratio and control overhead.
+
+%The clusters resulted from ROSS-DGA and its faster version ROSS-DFA are less vulnerable compared with other distributed clustering schemes, and demonstrates similar survival rate with centralized scheme under primary users' influence.
+%An light weighted cluster size control mechanism is contained in both ROSS-DGA and ROSS-DFA, which is advantageous for cooperative sensing and network operation with clusters.
+%Furthermore, considerable less control messages are generated when compared with other clustering schemes.
+
+The shortcoming of distributed scheme ROSS is it doesn't generate clusters whose sizes exceed the cluster head's neighborhood.
 The reason is with ROSS, cluster heads form clusters on the basis of their neighborhood, and don't involve the nodes which are outside the neighborhood.
-%In the other way around, forming big cluster which extends a cluster head's neighborhood has limited application scenarios, as multiple hop communication and coordination are required within these clusters.
+In the other way around, forming big cluster which extends a cluster head's neighborhood has limited application scenarios, as multiple hop communication and coordination are required within these clusters.
 
@@
 \appendices
-\section{Peudo Code for the Algorithm~\ref{alg0}, \ref{alg_size_control_available_CCC} and~\ref{alg4}}
+%\section{Algorithm~\ref{alg0}}
+\section*{}
 \begin{algorithm}              % enter the algorithm environment
@@
 \SetAlgoLined
-\KwIn{$d_j, g_j, j\in \text{Nb}(i)\setminus \Lambda$, $\Lambda$ means cluster heads. Empty sets $\tau_1,\tau_2$}
-\KwResult{Returning 1 means $i$ is cluster head, then $d_j$ is set to 0, $j\in \text{Nb}(i)\setminus \Lambda$. returning 0 means $i$ is not cluster head.}
-
-\If{$\nexists j\in \text{Nb}(i)\setminus \Lambda$, such that $d_i \geq d_j$}{
+\KwIn{$d_j, g_j, j\in \text{Nb}_i\setminus \Lambda$, $\Lambda$ means cluster heads. Empty sets $\tau_1,\tau_2$}
+\KwResult{Returning 1 means $i$ is cluster head, then $d_j$ is set to 0, $j\in \text{Nb}_i\setminus \Lambda$. returning 0 means $i$ is not cluster head.}
+
+\If{$\nexists j\in \text{Nb}_i\setminus \Lambda$, such that $d_i \geq d_j$}{
 	return 1;
 	}
-\eIf{$\exists j\in \text{Nb}(i)\setminus \Lambda$, such that $d_i > d_j$}{
+\eIf{$\exists j\in \text{Nb}_i\setminus \Lambda$, such that $d_i > d_j$}{
 	return 0;}{
-	\If{$\nexists j\in \text{Nb}(i)\setminus \Lambda$, such that $d_j == d_i$}{
+	\If{$\nexists j\in \text{Nb}_i\setminus \Lambda$, such that $d_j == d_i$}{
 	$\tau_1 \leftarrow j$
@@
 
+% you can choose not to have a title for an appendix
+% if you want by leaving the argument blank
+%\section*{Algorithm~\ref{alg_size_control_available_CCC}}
+\section*{}
 \begin{algorithm}               % enter the algorithm environment
@@
 	%calculate $\lambda = \min_{i\in C, i\neq H_C}(|K_{H_C}\cap K_i|)$;\\
-	\eIf{$\exists$ only one $i\in C\setminus h(C)$, $i = \argmin(|K_{h(C)}\cap K_i|)$}{
+	\eIf{$\exists$ only one $i\in C\setminus H_C$, $i = \argmin(|K_{H_C}\cap K_i|)$}{
 			$C=C\setminus i$;
 		}{
-				$\exists$ multiple $i$ which satisfies $i = \argmin(|K_{h(C)}\cap K_i|)$;\\ $\tau_1\leftarrow i$;		
+				$\exists$ multiple $i$ which satisfies $i = \argmin(|K_{H_C}\cap K_i|)$;\\ $\tau_1\leftarrow i$;		
 		}
@@
 
-%\section{}
+\section*{}
 \begin{algorithm}               % enter the algorithm environment
@@
 		}
-	\eIf{$\exists$ only one $C\in \tau_1$, $C = \argmax(K_{h(C)}\cap K_i)$}{
+	\eIf{$\exists$ only one $C\in \tau_1$, $C = \argmax(K_{h_C}\cap K_i)$}{
 			return $C$;
 		}{
-				$\exists$ multiple $C\in S_i$ which satisfies $C = \argmax(K_{h(C)}\cap K_i)$;\\ 
+				$\exists$ multiple $C\in S_i$ which satisfies $C = \argmax(K_{h_C}\cap K_i)$;\\ 
 				$\tau_2\leftarrow C$;		
@@
 		}{
-				return $\argmin_{C\in \tau_2}h(C)$;\\
+				return $\argmin_{C\in \tau_2}h_C$;\\
 		}
@@
 
-\section{Proof of Theorem~\ref{clustering:theorem}}
+% use section* for acknowledgment
+
+\section*{Proof of Theorem~\ref{clustering:theorem}}
+\label{proof_clustering:theorem}
 \begin{proof}
-\label{proof_clustering:theorem}
 %Note that the formed cluster can be a singleton cluster, \ie cluster size is 1.
@@
 %we assume every node has at least one neighbour.
-For the sake of contradiction, let us assume there exist a secondary user $\alpha$ which is not included into any cluster.
-Then there is at least one node $\beta\in \text{Nb}(\alpha)$ such that $d_{\alpha} > d_{\beta}$ (otherwise $\alpha$ becomes cluster head). 
-In this case, according to Algorithm~\ref{alg0}, $\beta$ is not included in any clusters, because otherwise $d_{\beta} = M$, a large positive integer, which contradicts to $d_{\alpha} > d_{\beta}$.
+For the sake of contradiction, let us assume there exist some secondary user $\alpha$ which is not included into any cluster.
+Then there is at least one node $\beta\in \text{Nb}_\alpha$ such that $d_{\alpha} > d_{\beta}$. 
+According to Algorithm~\ref{alg0}, $\delta$ is not included in any clusters, because otherwise $d_{\beta} = M$, a large positive integer.
 Now, we distinguish between two cases: 
@@
 If $\beta$ becomes cluster head, node $\alpha$ is included, the assumption is not true.
-If $\beta$ is not a cluster head, then $\beta$ is not in any cluster, we can repeat the previous analysis made on node $\alpha$, and deduce that node $\beta$ has at least one neighboring node $\gamma$ with $d_{\gamma} < d_{\beta}$.
+If $\beta$ is not a cluster head, then $\beta$ is not in any cluster, we can repeat the previous analysis made on node $\alpha$, and deduce that node $\beta$ has at least one neighbouring node $\gamma$ with $d_{\gamma} < d_{\beta}$.
 % (COMMENT: $\beta$ not being a cluster head and $\beta$ not belonging to any cluster is not the same statement!!! ANSWER(Di): I add some more words)
-So far, when there is no cluster head identified, the unclustered nodes, \ie $\alpha$, $\beta$ form a linked list, where their connectivity degrees monotonically decrease.
+Till now, when there is no cluster head identified, the unclustered nodes, \ie $\alpha$, $\beta$ form a linked list, where their connectivity degrees monotonically decrease.
 But this list will not continue to grow, because the minimum individual connectivity degree is zero, and the length of this list is upper bounded by the total number of nodes in the CRN.
@@
 
-In this example, node $\omega$ is at the tail of a list.
+In this example, node $\omega$ is at the tail of the list.
 As $\omega$ does not have neighboring nodes with lower individual connectivity degree, $\omega$ becomes a cluster head.
-Then $\omega$ incorporates all its one-hop neighbors (here we assume that every newly formed cluster has common channels), including the nodes which precede $\omega$ in the list.
-The nodes which join a cluster set their individual connection degrees to $M$, which makes the node immediately precede in the list to become a cluster head.
-In this way, cluster heads are generated from the tail to the head in the list, and every node in the list is in at least one cluster, which contradicts the assumption that $\alpha$ is not included in any cluster.
+Then $\omega$ incorporates all its one-hop neighbours (here we assume that every newly formed cluster has common channels), including the nodes which precede $\omega$ in the list.
+The nodes which join a cluster set their individual connection degrees to $M$, which enables the node immediately precede in the list to become a cluster head.
+In this way, cluster heads are generated from the tail of list to the head of the list, and all the nodes in the list are in at least one cluster, which contradicts the assumption that $\alpha$ is not included in any cluster.
 
@@
 %
-\section{Proof of Theorem~\ref{theorem1}}
+\section*{Proof of Theorem~\ref{theorem1}}
 \label{proof_theorem1}
@@
 \end{itemize}
-The number of steps is dependent on $\mathcal{I}$, which is between 1 and $N^2$.
-%
-Assume we have a robust clustering black box which checks whether the clustering instance meets the requirement, \ie clusters are not overlapping and the total sum of CCs exceeds $\lambda$ or not.
+The number of steps is dependent on $\mathcal{I}$, which is between 1 and $N^2$
+
+%We have found the polynomial algorithm $\sigma$ which transforms an instance of weighted $k$-set packing to an instance of the robust clustering problem in CRN.
+Assume we have a robust clustering black box which can check whether the clustering instance meets the requirement, \ie clusters are not overlapping and the total sum of CCs exceed $\lambda$ or not.
 If \textit{yes} is said, then the total weight of the corresponding instance of the maximum weighted k-set packing problem is greater than $\lambda$.
-If the black box says \textit{no}, either due to overlapping clusters or the sum of CCs is smaller than $\lambda$, the corresponding instance of the packing problem is not a solution.
+If the black box said \textit{no}, either due to overlapping clusters, or the sum of CCs over all clusters is smaller than $\lambda$, the corresponding instance of the packing problem is not an solution.
 
@@
 
+%\begin{table}[h!]
+%     \begin{center}
+%     \begin{tabular}{ C{3cm}  C{4.5cm} }
+%     \toprule
+%      $\mathcal{N}$  & $\{0, 1,2,3,4,5,6, 7, 8, 9\}$\\ 
+%    \cmidrule(r){1-1}\cmidrule(lr){2-2}     
+%      $\mathcal{Q}$  & $\{ \{1\}, \{1, 5\}, \{1,2,4\}, \{2,3\}, \{4\} \}$\\ 
+%    \cmidrule(r){1-1}\cmidrule(lr){2-2}     
+%      Instance for Weighted $k$-set packing  & $\{ \{1\}, \{2,3\}, \{4\} \}$, weights are 2, 3, 4\\ 
+%    \cmidrule(r){1-1}\cmidrule(lr){2-2}
+%      Instance with dummy elements (step 1)
+%      & 
+%		$\{ \, \{1,11\},\{2,12, 3, 13\}, \{ 4,14\} \, \}$
+%      \\    \cmidrule(r){1-1}\cmidrule(lr){2-2}
+%	clusters mapped from $\mathcal{I}$  (step 2)
+%	  &
+%	  \begin{minipage}{.3\textwidth}	
+%      \includegraphics[width=0.6\linewidth]{np_hard_proof_step_2_3.pdf}
+%    \end{minipage}
+%          \\    \cmidrule(r){1-1}\cmidrule(lr){2-2}
+%	formation of clusters (step 3)
+%	  &
+%	  \begin{minipage}{.3\textwidth}	
+%      \includegraphics[width=0.6\linewidth]{np_hard_proof_step4.pdf}
+%    \end{minipage}
+%	  \\       \bottomrule
+%      \end{tabular}
+%      \caption{}
+%      \label{no_hard_proof_instance}
+%      \end{center}
+%      \end{table}
+
 \end{proof}
 
+%\section*{Acknowledgment}
+%
+%The authors would like to thank xxxx
+
+% Can use something like this to put references on a page
+% by themselves when using endfloat and the captionsoff option.
+\ifCLASSOPTIONcaptionsoff
+  \newpage
+\fi
+
+% trigger a \newpage just before the given reference
+% number - used to balance the columns on the last page
+% adjust value as needed - may need to be readjusted if
+% the document is modified later
+%\IEEEtriggeratref{8}
+% The "triggered" command can be changed if desired:
+%\IEEEtriggercmd{\enlargethispage{-5in}}
+
+% references section
+
+% can use a bibliography generated by BibTeX as a .bbl file
+% BibTeX documentation can be easily obtained at:
+% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
+% The IEEEtran BibTeX style support page is at:
+% http://www.michaelshell.org/tex/ieeetran/bibtex/
+%\bibliographystyle{IEEEtran}
+% argument is your BibTeX string definitions and bibliography database(s)
+%\bibliography{IEEEabrv,../bib/paper}
+%
+% <OR> manually copy in the resultant .bbl file
+% set second argument of \begin to the number of references
+% (used to reserve space for the reference number labels box)
+
+% You can push biographies down or up by placing
+% a \vfill before or after them. The appropriate
+% use of \vfill depends on what kind of text is
+% on the last page and whether or not the columns
+% are being equalized.
+
+%\vfill
+
+% Can be used to pull up biographies so that the bottom of the last one
+% is flush with the other column.
+%\enlargethispage{-5in}
 \bibliographystyle{IEEEtran}
@@
 
-%\ack This class file was developed by Sunrise Setting Ltd,
-%Paignton, Devon, UK. Website:\\
-%\href{http://www.sunrise-setting.co.uk}{\texttt{www.sunrise-setting.co.uk}}
+% biography section
+% 
+% If you have an EPS/PDF photo (graphicx package needed) extra braces are
+% needed around the contents of the optional argument to biography to prevent
+% the LaTeX parser from getting confused when it sees the complicated
+% \includegraphics command within an optional argument. (You could create
+% your own custom macro containing the \includegraphics command to make things
+% simpler here.)
+%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
+% or if you just want to reserve a space for a photo:
+%IEEEbiographynophoto
 

### 2017-04-17 journal-draft/ettdoc.tex
change 'all its neighbors' to all of its neighbors

--- 2017-04-16 journal-draft/ettdoc.tex
@@
 
-\item \textit{Neighborhood connectivity degree} $g_i$: the number of CCs which are available for $i$ and all its neighbors.
+\item \textit{Neighborhood connectivity degree} $g_i$: the number of CCs which are available for $i$ and all of its neighbors.
 $g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$, which represents the ability of $i$ to form a robust cluster with its neighbors.
@@
 Each CR node decides whether it is a cluster head by comparing its connectivity vector with its neighbors.
-When CR node $i$ has lower individual connectivity degree than all its neighbors except for those which have already identified to be cluster heads, node $i$ becomes a cluster head.
+When CR node $i$ has lower individual connectivity degree than all of its neighbors except for those which have already identified to be cluster heads, node $i$ becomes a cluster head.
 If there is another CR node $j$ in its neighborhood, which has the same individual connectivity degree as $i$, \ie $d_j = d_i$ and $d_j < d_{k}, \forall k\in \text{Nb}(j)\setminus \{\Lambda\cup i\}$ where $\Lambda$ denotes the cluster heads, then the node between $i$ and $j$, which has higher neighborhood connectivity degree will become the cluster head.
@@
 After receiving the notification from a cluster head, a CR node $i$ is aware that it becomes a member of a cluster. 
-Consequently, $i$ sets its individual connectivity degree to a positive number $M > |\mathcal{K}| \cdot N$, and broadcasts the new individual connectivity degree to all its neighbors. 
+Consequently, $i$ sets its individual connectivity degree to a positive number $M > |\mathcal{K}| \cdot N$, and broadcasts the new individual connectivity degree to all of its neighbors. 
 %wrong:
@@
 If this criterion meets a tie, the tie will be broken by deleting the node with smaller node ID.
-It is possible that the cluster head excludes all its neighbors, resulting in a singleton cluster which is composed by itself.
+It is possible that the cluster head excludes all of its neighbors, resulting in a singleton cluster which is composed by itself.
 %At the end of this procedure every formed cluster has at least one common channel.

### 2017-04-17 journal-draft/ettdoc.tex
minor wording improvement

@@
 
-As to a cognitive radio network, where the set of CR nodes is $\mathcal{N}$.
-%Each cluster complies with the definition in , whose number of CCs in a cluster $C$ is $f(C)$.
-The robust clustering problem is to decide the set of clusters $\mathcal{T}$, where 
+As to a cognitive radio network where the set of CR nodes is $\mathcal{N}$, the robust clustering problem is to decide the set of clusters $\mathcal{T}$, where 
 \begin{enumerate}
@@
 %Now we examine the objective function to see whether it in line with the goal to maximize the total number of CCs meanwhile consider the restriction on the cluster size.
-When $t_{ij}$ is replaced with $\frac{q_{ij}}{|C_i|} - p_i(C_i)$, the objective function becomes,
+When $t_{ij}$ is replaced by $\frac{q_{ij}}{|C_i|} - p_i(C_i)$, the objective function becomes,
 \begin{equation}

### 2017-04-17 journal-draft/ettdoc.tex
change the expression of weight p

@@
 %$|K(C_i)|$ is the number of CCs of cluster $C_i$, and $|C_i|$ is the size of cluster $C_i$.
-$p_i(C_i)$ is the size-related weight, which reflects the deviation of $C_i$'s size from the desired size.
-Assuming $\delta$ is the desired size, then there is
+$p(C_i)$ is the size-related weight, which reflects the deviation of $C_i$'s size from the desired size.
+Assuming $\delta$ is the desired size, then the weight $p$ is decided according to the different cluster sizes, \ie 1,2, $\cdots$, $\sigma$.  
 $$
-p_i(C_i) = \left\{ \begin{array}{rl}
+p(C_i) = \left\{ \begin{array}{rl}
 0 &\mbox{ if $|C_i|=\delta$} \\
@@
 \rho_2 &\mbox{if $||C_i|-2|=\delta$} \\
-\vdots
+\vdots\\
+\rho_\sigma &\mbox{if $||C_i|-\sigma|=\delta$} \\
 \end{array} \right.
 $$
-where $\rho_1, \rho_2, \cdots$ are positive values and these is $\rho_2> \rho_1>0$.
+where $\rho_1, \rho_2, \cdots, \rho_\sigma$ are positive values and these is $\sigma > \rho_2> \rho_1>0$.
 
@@
 %Now we examine the objective function to see whether it in line with the goal to maximize the total number of CCs meanwhile consider the restriction on the cluster size.
-When $t_{ij}$ is replaced by $\frac{q_{ij}}{|C_i|} - p_i(C_i)$, the objective function becomes,
+When $t_{ij}$ is replaced by $\frac{q_{ij}}{|C_i|} - p(C_i)$, the objective function becomes,
 \begin{equation}
 \begin{aligned}
-     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p_i(C_i)) \\
+     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p(C_i)) \\
 \notag

### 2017-04-18 journal-draft/ettdoc.tex
update the arxiv citation

@@
 It is necessary to control the cluster size when CRN becomes denser.
-Both analysis and simulation~\cite{robust_clustering_arxiv} show that when applying ROSS, after the clusters are saturated with the increase of network density, the cluster size increases linearly with the network density, thus certain measures are needed to curb this problem.
+Both analysis and simulation~\cite{2017arXiv170404828L} show that when applying ROSS, after the clusters are saturated with the increase of network density, the cluster size increases linearly with the network density, thus certain measures are needed to curb this problem.
 This task falls upon the cluster heads.

### 2017-04-21 journal-draft/ettdoc.tex
Corrections and suggestions on abstract and intro

@@
 %\affil[3]{KTH Royal Institute of Technology}
-\address{RWTH Aachen University\textsuperscript{1}, ETH Zurich\textsuperscript{2}, KTH Royal Institute of Technology\textsuperscript{3} }
+\address{RWTH Aachen University\textsuperscript{1}, Swisscom (Schweiz) AG\textsuperscript{2}, KTH Royal Institute of Technology\textsuperscript{3} }
 %\renewcommand\Authands{ and }
@@
 \begin{abstract}
-Cluster structure in cognitive radio networks facilitates cooperative spectrum sensing, routing and other functionality.
-The unlicensed channels which are available for a group of cognitive radio users, consolidate the group into a cluster and the number of the available unlicensed channels decides that cluster's robustness against the licensed users' influence.
-This paper analyses the problem of how to form robust clusters in cognitive radio network, so that more cognitive radio users can get the benefits from cluster structure when the primary users' operation becomes more intense.
+Cluster structure in cognitive radio networks facilitates cooperative spectrum sensing, routing and other functionalities.
+Unlicensed channels, which are available for a group of cognitive radio users, consolidate the group into a cluster and the number of the available unlicensed channels decides that cluster's robustness against the licensed users' influence.
+This paper analyses the problem of how to form robust clusters in a cognitive radio network so that more cognitive radio users can get the benefits from cluster structure when the primary users' operations becomes more intense.
 %In the process of forming clusters, every secondary user decides with whom to form a cluster, or which cluster to join.
 We give a formal description of the robust clustering problem, prove it to be NP-hard and propose both centralized and distributed solutions.
-The congestion game model is adopted to analyze the process of cluster formation, which not only contributes the design of the distributed clustering scheme, but also provides the guarantee on the convergence into Nash Equilibrium and the convergence speed.
+The congestion game model is adopted to analyze the process of cluster formation, which not only contributes to the design of the distributed clustering scheme, but also provides the guarantee on the convergence into Nash Equilibrium and the convergence speed.
 %Our proposed clustering solution is versatile to fulfill some other requirements such as faster convergence and cluster size control.
-The proposed distributed clustering scheme outperforms the related works in terms of cluster robustness, convergence speed and overhead.
+The proposed distributed clustering scheme outperforms state-of-the-art related works in terms of cluster robustness, convergence speed and overhead.
 %Besides, we prove the clustering problem is NP-hard, and also propose the centralized solution.
-The extensive simulation is conducted, which clearly supports our claims.
+Extensive simulations have been conducted which clearly support our claims.
 \end{abstract}
@@
 Collaborative sensing relies on the consensus of CR users\footnote{The terms user and node appear interchangeably in this paper.
-In particular, user is adopted when its networking or cognitive ability are discussed or stressed, while we refer node typicallly in the context of the topology.} within a certain area, in this regard, clustering is regarded as an effective method to realize cooperative spectrum sensing~\cite{Sun07_clustering_spectrum_secsing}.
+In particular, user is adopted when its networking or cognitive ability are discussed or stressed, while we refer to nodes typicallly in the context of the network topology.} within a certain area, in this regard, clustering is regarded as an effective method to realize cooperative spectrum sensing~\cite{Sun07_clustering_spectrum_secsing}.
 % ... decreases considerably the negative probability due to the random channel effects like fading and shadowing.
 Clustering is a process of grouping certain users in geographic proximity into a collective.
-In the context of cognitive radio netowrks, a formed cluster helps the participants not only improve the spectrum sensing accuracy, but also coordinate the channel switch operation when the primary users are detected by at least one secondary user in that cluster, then all the cluster menmbers can stop payload transmission swiftly and vacate the operating channel ~\cite{willkomm08}.
+In the context of cognitive radio netowrks, a formed cluster helps the participants not only to improve the spectrum sensing accuracy, but also to coordinate the channel switch operation when the primary users are detected by at least one secondary user in that cluster.
+Then all the cluster menmbers can stop payload transmission swiftly and vacate the operating channel ~\cite{willkomm08}.
 Clustering also benefits the operation of a CRN by reducing the interference between cognitive clusters~\cite{centralizedSharing80222}, and supporting routing~\cite{Abbasi_survey_07}.
 %As to the coexistence of CR users, they can be notified by cluster head (CH) or other cluster members about the possible collision, the possibility for them to interfere neighbouring clusters is reduced~\cite{centralizedSharing80222}.
-Except for benefiting the dynamic spectrum sharing in CRN, clustering contributes to the other wireless networks in many aspects, which has already been discussed in many works.
+Except for benefiting the dynamic spectrum sharing in CRN, clustering contributes to the other wireless networks in many aspects, which has already been discussed in many works. [CITATION MISSING]
 
@@
 Each formed cluster has one or multiple unlicensed channels which are available for every CR node in the cluster.
-The available unlicensed channels are referred to in the following of this paper as \textit{common licensed channels} (or common channels for short, which is abbreviated as CC).
+In this paper available unlicensed channels are called \textit{common licensed channels} (or common channels for short, which is abbreviated as CC).
 Both payload and control overheads can be transmitted on the CCs.
 %Out of the available CCs, there are always one or multiple channels which are used for the payload communication.
-When one or several cluster members can not access one certain CC on which primary user activity is detected, the channel will be excluded from the set of CCs.
+When one or several cluster members can not access one certain CC on which primary some user activity is detected, the channel will be excluded from the set of CCs.
 In particular, if that channel is being used for payload communication, the communication pair will stop and resume the transmission on another available CC.
-The availability of CCs within a cluster defines the existence of that cluster, \ie no CCs are available means the corresponding cluster doesn't exist.
+The availability of CCs within a cluster defines the existence of that cluster, \ie if no CCs are available then the corresponding cluster does not exist.
 %As long as there is a CC available, the corresponding cluster can continue to exchange payload data.
-In the context of CRN, the activity of primary users is usually unknown to the secondary users, then the primary users' activity is deemed as random.
-In this case, the cluster which secures more CCs will anticipate a longer life expectancy, in other words, is more robust.
-It is obvious that fewer secondary users in one cluster yield more CCs, but this contradicts to one of the motivations of clustering, \ie the cooperative decision making, where more users result in more accurate sensing result~\cite{Consensus_based_clustering12}.
+In the context of CRN, the activity of primary users is usually unknown to the secondary users. In such cases the primary users' activity is deemed as random.
+Consequently, a cluster which secures more CCs will anticipate a longer life expectancy. In other words, such clusters are more robust.
+It is obvious that fewer secondary users in one cluster yield more CCs.
+However, this contradicts to one of the motivations of clustering, \ie the cooperative decision making, where more users result in more accurate sensing result~\cite{Consensus_based_clustering12}.
 Thus the number of small clusters, especially the \textit{singleton clusters}, \ie the cluster which has only one CR node, should be minimized.
-As to the cluster which consists of many nodes, although the spectrum sensing is benefited, it usually leads to less common channels, which undermines the robustness of the cluster.
-Thus the cluster robustness discussed in terms of number of CCs carries little meaning when the sizes of formed clusters are not given consideration.
-Cluster size also plays a part in transmission power consumption, \ie cluster size affects the transmission power consumption when routing is conducted~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
-In this paper we will analyze the robust clustering and propose efficient solutions.
+As to the cluster which consists of many nodes, although the spectrum sensing is benefited, it usually leads to less common channels. This undermines the robustness of the cluster.
+Thus, the cluster robustness discussed in terms of number of CCs carries little meaning when the sizes of formed clusters are not considered.
+Cluster sizes also play a role in transmission power consumption, \ie cluster size affects the transmission power consumption when routing is conducted~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
+In this paper we will analyze the robust clustering problem and propose efficient solutions.
 Our schemes generate the clusters which demonstrate both the robustness against the increasing primary activity and the compliance with the desired cluster sizes.
@@
 With regard to forming clusters in CRN, deciding on the common channel within each cluster is the foremost question to answer.
-\cite{Zhao07, Chen07,Affinity_clustering_09icccn} propose the clustering schemes and make sure every cluster possesses at least one CC.
-Clustering scheme~\cite{Consensus_based_clustering12} looks for the network partition which improves the accuracy of spectrum sensing with the cluster structure.
+\cite{Zhao07, Chen07,Affinity_clustering_09icccn} propose the clustering schemes and enforce that every cluster possesses at least one CC.
+Clustering scheme~\cite{Consensus_based_clustering12} looks for a network partition which improves the accuracy of spectrum sensing with the cluster structure.
 %Clustering scheme~\cite{clustering_globecom11} obtains the best cluster size which minimizes power consumption caused by communication within and among clusters.
@@
 \cite{cluster_EW10} proposes strategy on how to decide on the CCs and access the multiple CCs within clusters.
-An event-driven clustering scheme is proposed for cognitive radio sensor network in \cite{Ozger_cluster_crsn_13}.
-No one among the above mentioned schemes provides the robustness to the formed clusters against primary users.
-
-Robustness of clusters is discussed in~\cite{LIU_TMC11_2}, where a distributed clustering scheme (denoted as SOC) which is designed to generate robust clusters against primary users is proposed.
+An event-driven clustering scheme is proposed for cognitive radio sensor networks in \cite{Ozger_cluster_crsn_13}.
+None of the above mentioned schemes provides a certain robustness to formed clusters against primary users.
+
+Robustness of clusters is discussed in~\cite{LIU_TMC11_2}. A distributed clustering scheme (denoted as SOC) which is designed to generate robust clusters against primary users is proposed.
 The robustness of the clusters comes from the fact that there are multiple CCs available for the clusters.
 SOC involves three phases of distributed executions.
-In the first phase, every secondary user forms clusters with some one-hop neighbors, in the second and third phase, each secondary user seeks to either merge other clusters or join one of them.
+In the first phase, every secondary user forms clusters with some one-hop neighbors. In the second and third phase, each secondary user seeks to either merge other clusters or join one of them.
 The metric adopted by every secondary user in all the phases is the product of the number of CCs and cluster size.
@@
 a node which can access many channels may exclude its neighbor and form a cluster by itself.
+(THIS SENTENCE IS TOO COMPLICATED.
+BREAK IT DOWN TO 2 OR 3 PLEASE.)
 In addition, this scheme leads to the high variance of the cluster sizes, which is not desired in certain applications as discussed in~\cite{clustering_globecom11, cluster_EW10}.
-\cite{mansoor_15_cluster_robust} presents a heuristic method to form clusters, although the authors claim robustness is one goal to achieve, the minimum number of clusters is finally pursued.
+\cite{mansoor_15_cluster_robust} presents a heuristic method to form clusters. Although the authors claim that robustness is one goal to achieve, the minimum number of clusters is finally pursued.
 %
@@
 Compared with the clustering schemes introduced above, the clusters are formed faster and the clusters possess more CCs than SOC.
-But as all the other clustering schemes, this scheme doesn't have control over the formation of the very small or very large clusters which are not desirable.
+However, as all the other clustering schemes, this scheme does not have control over the formation of the very small or very large clusters which are not desirable.
 Furthermore, this work doesn't consider the robustness of clusters against the increasing activity of primary users, which leaves their claim of robustness unverified.
 %
-This paper is on the basis of the work in~\cite{Li11_ROSS}, but extends in two dimensions.
+This paper extends~\cite{Li11_ROSS} in two dimensions.
 First, this paper renews the definition of robustness of clusters in a CRN, which is no longer the average number of CCs of clusters, but the ability of the clusters to sustain when the primary users' activity becomes more dynamic.
+(BAD FORMULATION TO SAY "renew".
+Changing definitions itself does not impose any benefit.
+Is there any an improval?)
 Second, this paper proposes size control mechanism, which solves the problem of devergence of clusters sizes in~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
@@
 %The clustering problem is given through analysis and a centralized scheme is proposed in section~\ref{centralized_scheme}.
-Extensive performance evaluation is presented in Section~\ref{performance}.
+Some Extensive performance evaluation is presented in Section~\ref{performance}.
 Finally, we conclude our work and point out the direction for future research in Section~\ref{conclusion}.

### 2017-04-30 journal-draft/ettdoc.tex
Modify the robust clustering definition and proof of complexity, but there is flaw in the proof

@@
 \setlength{\itemindent}{.05in}
-\item the sum of the $f(C)$ is the maximal, where $C\in \mathcal{T}$ 
 \item the intersection of any two clusters in $\mathcal{T}$ is an empty set
 \item the union of clusters in $\mathcal{T}$ is $\mathcal{N}$
-\item the cluster sizes should fall in the scope $\langle\delta_1, \delta_2\rangle$, where $\delta, \delta_1, \delta_2\in \mathbb{Z}^+$, $\delta_1 \leq \delta\leq \delta_2$, and $\delta$ is decided according to the application to be implemented in the CRN.
+\item the sum of the $f(C)$ is the maximal, where $C\in \mathcal{T}$ and meanwhile the cluster sizes fall in the scope $\langle\delta_1, \delta_2\rangle$.
+$\delta_1, \delta_2\in \mathbb{Z}^+$ and $\delta_1 \leq \delta_2$.
+\item the size of $C$ in $\mathcal{T}$ is allowed to be 1.
+%, and $\delta$ is decided according to the application to be implemented in the CRN.
 \end{enumerate}
-
 \end{mydef}
 
-Assume we have obtained the set of $\mathcal{S}$ which contains all the clusters in $\mathcal{N}$, \ie $\mathcal{S}=\{C_1, C_2,\ldots,C_i, \ldots, C_{|\mathcal{S}|}\}$ \footnote{The subscript $i$ means the $i$-th cluster in $\mathcal{S}$.} and there is $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = \mathcal{N}$.
-The decision version of this problem is to determine whether there is a non-empty set $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C_i\in \mathcal{S}'} f(C_i) \geqslant \lambda$ where $\lambda$ is a real number.
+The decision version of this problem is to determine whether there is a set of clusters, say $\mathcal{X}$, so that $\sum_{\forall C\in \mathcal{X}} f(C) \geqslant \lambda$ where $\lambda$ is a real number.
 We have the following theorem on the problem's complexity.
@@
 \label{theorem1}
-The robust clustering problem in CRN is NP-hard, when the maximum size of clusters is larger than 3, $\delta_1=1$ and $\delta_2 = N$.
+The robust clustering problem in CRN is NP-hard, when $\delta_1=2$ and $\delta_2 > 3$.
+%when the maximum size of clusters is larger than 3
 %Assume a CRN can be represented by a connected graph, and there is at least one common channel between any pair of neighbours, then forming at least two CR nodes into one cluster is NP-complete.
@@
 When the global knowledge of the CRN is available to us, we can propose a centralized scheme as comparison.
+We obtain the set of $\mathcal{S}$ which contains all the clusters in $\mathcal{N}$, \ie $\mathcal{S}=\{C_1, C_2,\ldots,C_i, \ldots, C_{|\mathcal{S}|}\}$ \footnote{The subscript $i$ means the $i$-th cluster in $\mathcal{S}$.} and there is $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = \mathcal{N}$.
 The proposed centralized solution formulates the problem in Definition~\ref{def_centralized_clustering} as an optimization problem which is solved with standard software packages.
-The optimization searches the set $\mathcal{S}$ and decides on the clusters according to the following optimization formulation,
+The optimization decides on the clusters according to the following optimization formulation,
 %
@@
 To prove the robust clustering problem is NP-hard, we reduce the \textit{maximum weighted k-set packing problem}, which is NP-hard when $k\geqslant 3$~\cite{Computers_a_Intractability}, to the the robust clustering problem to show the latter is at least as hard as the former.
-Given a collection of sets of cardinality at most $k$ with weights for each set, the maximum weighted packing problem is that of finding a collection of disjoint sets of maximum total weight.
-The decision version of weighted $k$-set packing problem is,
+Given a collection of sets of cardinality at most $k$ and with weights for each set, the maximum weighted packing problem is that of finding a collection of disjoint sets of maximum total weight.
+The decision version of the weighted $k$-set packing problem is,
 \begin{mydef}
 \label{def_kset_packing}
-Given a finite set $\mathcal{G}$ of non-negative integers where $\mathcal{G} \subsetneq \mathbb{N}$, and a collection of sets $\mathcal{Q}=\{S_1,S_2,\cdots,S_m\}$ where $S_i \subseteq \mathcal{G}$ and $\max(S_i)\geq 3$ for $1 \leq i \leq m$.
-Every set $S$ in $\mathcal{Q}$ has a weight $\omega(S) \in \mathbb{R}$. 
-%
-The problem is to find a collection $\mathcal{S} \subseteq \mathcal{Q}$ such that $\mathcal{S}$ contains only pairwise disjoint sets and the total weight of the sets in $\mathcal{S}$ is greater than a given positive number $\lambda$, i.e., $\sum_{S \in \mathcal{S}} \omega(S) > \lambda$.
+Given a finite set $\mathcal{G}$ of non-negative integers where $\mathcal{G} \subsetneq \mathbb{N}$, and a collection of sets $\mathcal{Q}=\{S_1,S_2,\cdots,S_m\}$ where $S_i \subseteq \mathcal{G}$ and $\max(|S_i|)\geq 3$ for $1 \leq i \leq m$.
+Every set $S$ in $\mathcal{Q}$ has a weight $\omega(S) \in \mathbb{N}^+$. 
+%
+The problem is to find a collection $\mathcal{I} \subseteq \mathcal{Q}$ such that $\mathcal{I}$ contains only the pairwise disjoint sets and the total weight of these sets is greater than a given positive number $\lambda$, i.e., $\sum_{\forall S \in \mathcal{I}} \omega(S) > \lambda$.
 \end{mydef}
 
-We assume the weights of sets are positive integers.
-Then we will show that any instance $\mathcal{I}$ of a weighted $k$-set packing problem, \ie a collection of sets, can be transformed to a clusters formation for a CRN.
-W.l.o.g. let set $\mathcal{G} = \{ 1, \ldots , N \}$.
-The polynomial algorithm $\sigma$ consists of three steps.
-
+%We assume the weights of sets are positive integers.
+We will show that any instance $\mathcal{I}$ of a weighted $k$-set packing problem, \ie a collection of sets, can be transformed into an instance of a robust clustering for a CRN within polynomial time.
+W.l.o.g. let set $\mathcal{G} = \{ 1, \ldots , N \}$, and redeem there are $N$ CR nodes in the CRN which is to form clusters.
+
+The procedure of the transformation is as follows.
 \begin{itemize}
-
-%\item In the first step, we transform the instance $\mathcal{I}$ to $\mathcal{I'}$ by duplicating the elements of the sets in $\mathcal{I}$.
-%In particular, as to each element in set $S\in \mathcal{I}$, we duplicate the element and assign a new index which is N bigger than the original index.
-%The weight of these sets remain unchanged.
-%The purpose of this transformation is to eliminate the set in $\mathcal{I}$, which has only one element.
-
-\item First, the sets in the instance $\mathcal{I}$ are mapped sequentially to the clusters of CR nodes on a two-dimensional Euclidean plane, where the CR user ID is identical with the corresponding element's index.
-
-\item Second, for each mapped cluster $C$, we assign the channels for the nodes in $C$ so that $|K(C)|$ equals to the $\omega(S)$.
-We can simply assign the first $|K(C)|$ channels to each CR node in $C$, without considering the possible mismatch when the same CR node appears in different clusters and is assigned with different channels.
-%The channel availability on the CR nodes whose IDs are $N$ apart is the same.
-%Besides, there is a bijection between every set in $\mathcal{I'}$ and one cluster in the CRN.
-%In this process, we decide the channel availability on each CR node so that the number of CCs in each cluster is equal to the weight of the corresponding set.
-%
-%When there are two sets in $\mathcal{I'}$ and one is a subset of the other one, \ie  $S_1\subset S_2$, and $\omega(S_1) < \omega(S_2)$, then we should swap the weights of the sets before mapping them into clusters.
-
-%\item In second step, we map the elements in $\mathcal{Q}\setminus \mathcal{I}$ to CR nodes. 
-%We arbitrarily put these CR nodes in the CRN, then these CR nodes form singleton clusters by themselves.
-%According to the definition of robust clustering problem in CRN, the number of CCs of these singleton clusters is 0.
-%These singleton clusters and the clusters mapped from $\mathcal{I'}$ constitute a clustering solution.
-
-% finding these singleton clusters requires at most $N$ steps.
-
-%As to duplicated elements, we also map them into a CR node, thus there exist CR nodes with identical ID.
-%As a result, these CR nodes constitute a collection of CR nodes, and they can not be called as a CRN yet as there are not communication links drawn between them.
-%Connections in CRN under this context is decided by physical conditions, which means to have a communication link, the two CR nodes should have common channels and locate within each other's transmission range.
-%We further assume that all CR nodes locate in a way that any two pair of nodes has potential to be connected if their IDs are in the same set in $\mathcal{S}$, the instance for weighted $k$-set packing.
-%\item Mere isolated nodes don't constitute network, thus we add connections in CRN based on the sets in $\mathcal{S}'$ sequentially.
-%For each set $s'\in \mathcal{S}'$, we add connection between two CR nodes if their IDs can be found in $s'$.
-%No connection exists between two CR nodes if their IDs don't appear in the same set in $\mathcal{S}$.
-
-%We complete the polynomial algorithm $\sigma$ for the the transformation so far.
-%The number of common channels of cluster $f$ is non-increasing function of cluster size, while, the weight of set in weighted $k$-set packing problem doesn't have this property.
-%In weighted $k$-set packing, the weight of a set with smaller size could be larger than a set with more elements.
-%But this difference doesn't hinder the transformation because an instance of weighted $k$-set packing contains only disjoint sets in $\mathcal{G}$.
+\item First, all the sets in the instance $\mathcal{I}$ are mapped sequentially to a group of clusters, \ie for a set $S\in\mathcal{I}$, the elements in $S$ are mapped to CR nodes which compose a cluster $C$, moreover, the resultant CR node's ID equals to the corresponding element in $\mathcal{S}$.
+This transformation takes $N$ steps.
+\item If $\mathcal{I}$ is not the solution because the intersection of two sets is not empty, the resultant clusters are not the solution to the clustering problem due to the overlapped clusters.
+When $\mathcal{I}$ contains only the disjoint sets, for each mapped cluster $C$, we assign the available channels for the nodes in $C$ so that the number of common channels in $C$ equals to the weight $\omega(S)$.
+This step of transformation takes $N*|\mathcal{K}|$ steps where $\mathcal{K}$ is the set of licensed channels.
+\item The resultant clusters are not an instance for the robust clustering problem yet because the clusters don't include all the CR nodes in the CRN, just as the instance $\mathcal{I}$ doesn't include all the elements in $\mathcal{G}$.
+We add the CR nodes besides the mapped clusters, which correspond to the elements in $\mathcal{G}\backslash\mathcal{I}$.
+We can randomly assign available channels on these newly added CR nodes, which do not contribute to the sum of the numbers of the common channels $f(C)$ as defined in~\ref{def_centralized_clustering} because they actually form singleton clusters and their cluster sizes are smaller than 2.
+This steps takes at most $N$ steps.
 
 \end{itemize}
-The number of steps is dependent on $\mathcal{I}$, which is between 1 and $N^2$.
-%
-Assume we have a robust clustering black box which checks whether the clustering instance meets the requirement, \ie clusters are not overlapping and the total sum of CCs exceeds $\lambda$ or not.
-If \textit{yes} is said, then the total weight of the corresponding instance of the maximum weighted k-set packing problem is greater than $\lambda$.
-If the black box says \textit{no}, either due to overlapping clusters or the sum of CCs is smaller than $\lambda$, the corresponding instance of the packing problem is not a solution.
+In this way, we change any instance of a weighted $k$-set packing problem into an instance of robust clustering.
+%The polynomial algorithm $\sigma$ consists of three steps.
+%\begin{itemize}
+%
+%\item First, the sets in the instance $\mathcal{I}$ are mapped sequentially to the clusters of CR nodes on a two-dimensional Euclidean plane, where the CR user ID is identical with the corresponding element's index.
+%
+%\item Second, for each mapped cluster $C$, we assign the channels for the nodes in $C$ so that $|K(C)|$ equals to the $\omega(S)$.
+%We can simply assign the first $|K(C)|$ channels to each CR node in $C$, without considering the possible mismatch when the same CR node appears in different clusters and is assigned with different channels.
+%
+%\end{itemize}
+%The number of steps is dependent on $\mathcal{I}$, which is between 1 and $N^2$.
+%
+Assume we have a robust clustering black box which checks whether the clustering instance meets the requirement, \ie clusters are not overlapping, and the sum of CCs of the clusters whose size is larger than 1 exceeds $\lambda$ or not.
+\begin{itemize}
+\item If \textit{yes} is said, then the total weight of the corresponding instance of the maximum weighted k-set packing problem is greater than $\lambda$.
+\item If the black box says \textit{no}, either due to overlapping clusters or the sum of CCs is smaller than $\lambda$, the corresponding instance of the packing problem is not a solution.
+\end{itemize}
 
@@
 
-Hence, the weighted $k$-set packing can be reduced to the robust clustering problem in CRN, then the latter problem is of NP-hard.
+Hence, the weighted $k$-set packing can be reduced to the robust clustering problem in CRN, thus the latter problem is as hard as the former thus is of NP-hard.
 %An example of the reduction is shown in Table~\ref{no_hard_proof_instance}.

### 2017-04-30 journal-draft/ettdoc.tex
Modify the proof of complexity

@@
 \item the union of clusters in $\mathcal{T}$ is $\mathcal{N}$
-\item the sum of the $f(C)$ is the maximal, where $C\in \mathcal{T}$ and meanwhile the cluster sizes fall in the scope $\langle\delta_1, \delta_2\rangle$.
+\item the sum of the $f(C)$ is the maximal, where $C\in \mathcal{T}$ and meanwhile the cluster sizes fall in the scope $\big[\delta_1, \delta_2\big]$.
 $\delta_1, \delta_2\in \mathbb{Z}^+$ and $\delta_1 \leq \delta_2$.
+When the cluster size is out of $\big[\delta_1, \delta_2\big]$, $f(C)=0$.
+
 \item the size of $C$ in $\mathcal{T}$ is allowed to be 1.
@@
 
-%We assume the weights of sets are positive integers.
-We will show that any instance $\mathcal{I}$ of a weighted $k$-set packing problem, \ie a collection of sets, can be transformed into an instance of a robust clustering for a CRN within polynomial time.
-W.l.o.g. let set $\mathcal{G} = \{ 1, \ldots , N \}$, and redeem there are $N$ CR nodes in the CRN which is to form clusters.
-
-The procedure of the transformation is as follows.
-\begin{itemize}
-\item First, all the sets in the instance $\mathcal{I}$ are mapped sequentially to a group of clusters, \ie for a set $S\in\mathcal{I}$, the elements in $S$ are mapped to CR nodes which compose a cluster $C$, moreover, the resultant CR node's ID equals to the corresponding element in $\mathcal{S}$.
-This transformation takes $N$ steps.
-\item If $\mathcal{I}$ is not the solution because the intersection of two sets is not empty, the resultant clusters are not the solution to the clustering problem due to the overlapped clusters.
-When $\mathcal{I}$ contains only the disjoint sets, for each mapped cluster $C$, we assign the available channels for the nodes in $C$ so that the number of common channels in $C$ equals to the weight $\omega(S)$.
-This step of transformation takes $N*|\mathcal{K}|$ steps where $\mathcal{K}$ is the set of licensed channels.
-\item The resultant clusters are not an instance for the robust clustering problem yet because the clusters don't include all the CR nodes in the CRN, just as the instance $\mathcal{I}$ doesn't include all the elements in $\mathcal{G}$.
-We add the CR nodes besides the mapped clusters, which correspond to the elements in $\mathcal{G}\backslash\mathcal{I}$.
-We can randomly assign available channels on these newly added CR nodes, which do not contribute to the sum of the numbers of the common channels $f(C)$ as defined in~\ref{def_centralized_clustering} because they actually form singleton clusters and their cluster sizes are smaller than 2.
-This steps takes at most $N$ steps.
-
-\end{itemize}
-In this way, we change any instance of a weighted $k$-set packing problem into an instance of robust clustering.
-%The polynomial algorithm $\sigma$ consists of three steps.
+First, we argue that robust clustering problem is in NP, since given a collection of clusters, a certifier can efficiently check that such clusters are pairwise disjoint, indeed contains all the CR nodes in the CRN $\mathcal{N}$ and the sum of $f(C)$ as shown in Definition~\ref{def_centralized_clustering} is greater than a certain value.
+
+We will show that the weighted $k$-set packing problem $\leq_P$ CRN robust clustering problem.
+Given an instance of the weighted $k$-set packing problem, \ie a collection of sets of distinct integers $\mathcal{Q}=\{S_1,S_2,\cdots,S_m\}$, the integer weight $\omega(S)$ for set $S$ and a integer $\lambda$, we will construct an instance of a CRN robust clustering problem within polynomial time.
+W.l.o.g. we let set $\cup_{\forall i\in\{1, \ldots, m\}}S_i = \{ 1, \ldots , N \} = \mathcal{N}$.
+
+We will construct the CRN and the clusters as follows:
+For every set $S$ whose size is larger than 1, a corresponding cluster of CR nodes is generated.
+The CR nodes within this cluster can pair wise communicate and the IDs of these CR nodes correspond to the elements in $S$, besides, we allocate the $|\omega(S)|$ channels to all the CR nodes in this cluster, and the channels are on the spectrum band which is exclusive for this cluster.
+For every set $S$ which contains only one element, \ie $S =\{i\}$, a cluster composed with two CR nodes are created.
+One CR node's ID is $i$, the other CR node is the dummy node of the former and its ID is $N+i$.
+$|\omega(S)|$ channels from the exclusive spectrum band for this cluster are allocated to these two CR nodes.
+In the end, we construct the singleton clusters, where the IDs of the CR nodes correspond to the elements in $\mathcal{N}\backslash \cup_{S_i}$.
+Now we have completed a CRN and can claim that all the constructed clusters $C$ constitute the complete CRN network $\mathcal{N}$.
+
+Now suppose there is a set of pairwise disjoint clusters which constitute the CRN $\mathcal{N}$, and the sum of $f(C)$ is greater than $\lambda$.
+After removing the singleton clusters, we can easily find the natural association between the clusters in the CRN and the sets in $\mathcal{Q}$. 
+The clusters which contain dummy CR nodes correspond to the sets which contain only one element, and the other clusters correspond to the sets in $\mathcal{Q}$, whose elements are the node IDs of the corresponding clusters.
+Then the sum of the weights of such sets equals to the sum of $f(C)$ and thus greater than $\lambda$.
+
+We have now shown that our algorithm solves the weighted $k$-set packing problem using a black box for the robust clustering problem. 
+Since our construction takes polynomial time, and we have shown that robust clustering problem is in NP, we can conclude that Set Cover is NP-hard.
 %\begin{itemize}
-%
-%\item First, the sets in the instance $\mathcal{I}$ are mapped sequentially to the clusters of CR nodes on a two-dimensional Euclidean plane, where the CR user ID is identical with the corresponding element's index.
-%
-%\item Second, for each mapped cluster $C$, we assign the channels for the nodes in $C$ so that $|K(C)|$ equals to the $\omega(S)$.
-%We can simply assign the first $|K(C)|$ channels to each CR node in $C$, without considering the possible mismatch when the same CR node appears in different clusters and is assigned with different channels.
+%\item First, all the sets in the instance $\mathcal{I}$ are mapped sequentially to a group of clusters, \ie for a set $S\in\mathcal{I}$, the elements in $S$ are mapped to CR nodes which compose a cluster $C$, moreover, the resultant CR node's ID equals to the corresponding element in $\mathcal{S}$.
+%This transformation takes $N$ steps.
+%\item If $\mathcal{I}$ is not the solution because the intersection of two sets is not empty, the resultant clusters are not the solution to the clustering problem due to the overlapped clusters.
+%When $\mathcal{I}$ contains only the disjoint sets, for each mapped cluster $C$, we assign the available channels for the nodes in $C$ so that the number of common channels in $C$ equals to the weight $\omega(S)$.
+%This step of transformation takes $N*|\mathcal{K}|$ steps where $\mathcal{K}$ is the set of licensed channels.
+%\item The resultant clusters are not an instance for the robust clustering problem yet because the clusters don't include all the CR nodes in the CRN, just as the instance $\mathcal{I}$ doesn't include all the elements in $\mathcal{G}$.
+%We add the CR nodes besides the mapped clusters, which correspond to the elements in $\mathcal{G}\backslash\mathcal{I}$.
+%We can randomly assign available channels on these newly added CR nodes, which do not contribute to the sum of the numbers of the common channels $f(C)$ as defined in~\ref{def_centralized_clustering} because they actually form singleton clusters and their cluster sizes are smaller than 2.
+%This steps takes at most $N$ steps.
+%
 %
 %\end{itemize}
-%The number of steps is dependent on $\mathcal{I}$, which is between 1 and $N^2$.
-%
-Assume we have a robust clustering black box which checks whether the clustering instance meets the requirement, \ie clusters are not overlapping, and the sum of CCs of the clusters whose size is larger than 1 exceeds $\lambda$ or not.
-\begin{itemize}
-\item If \textit{yes} is said, then the total weight of the corresponding instance of the maximum weighted k-set packing problem is greater than $\lambda$.
-\item If the black box says \textit{no}, either due to overlapping clusters or the sum of CCs is smaller than $\lambda$, the corresponding instance of the packing problem is not a solution.
-\end{itemize}
-
-% The direction is wrong!!
-%When $\mathcal{I}$ is not an instance for weighted $k$-set packing problem due to the existence of joint sets, the corresponding clustering instance is not a successful cluster partition for the robust clustering problem, as there are overlapped clusters.
+%In this way, we change any instance of a weighted $k$-set packing problem into an instance of robust clustering.
+%%The polynomial algorithm $\sigma$ consists of three steps.
+%%\begin{itemize}
 %%
-%When the sets in an instance $\mathcal{I}$ for weighted $k$-set packing are disjoint, the sum of weights is identical to the total number of the CCs in the CRN which are mapped from $\mathcal{I'}$.
-%Thus, when a instance $\mathcal{I}$ for $k$-set packing problem is true (or false), \ie the sum of weights is greater than $\lambda$, then in the CRN which is mapped from $\mathcal{I'}$, the sum of the numbers of CCs of the clusters is greater (or smaller) than $\lambda$.
-
-Hence, the weighted $k$-set packing can be reduced to the robust clustering problem in CRN, thus the latter problem is as hard as the former thus is of NP-hard.
-%An example of the reduction is shown in Table~\ref{no_hard_proof_instance}.
+%%\item First, the sets in the instance $\mathcal{I}$ are mapped sequentially to the clusters of CR nodes on a two-dimensional Euclidean plane, where the CR user ID is identical with the corresponding element's index.
+%%
+%%\item Second, for each mapped cluster $C$, we assign the channels for the nodes in $C$ so that $|K(C)|$ equals to the $\omega(S)$.
+%%We can simply assign the first $|K(C)|$ channels to each CR node in $C$, without considering the possible mismatch when the same CR node appears in different clusters and is assigned with different channels.
+%%
+%%\end{itemize}
+%%The number of steps is dependent on $\mathcal{I}$, which is between 1 and $N^2$.
+%%
+%Assume we have a robust clustering black box which checks whether the clustering instance meets the requirement, \ie clusters are not overlapping, and the sum of CCs of the clusters whose size is larger than 1 exceeds $\lambda$ or not.
+%\begin{itemize}
+%\item If \textit{yes} is said, then the total weight of the corresponding instance of the maximum weighted k-set packing problem is greater than $\lambda$.
+%\item If the black box says \textit{no}, either due to overlapping clusters or the sum of CCs is smaller than $\lambda$, the corresponding instance of the packing problem is not a solution.
+%\end{itemize}
+%
+%
+%
+%% The direction is wrong!!
+%%When $\mathcal{I}$ is not an instance for weighted $k$-set packing problem due to the existence of joint sets, the corresponding clustering instance is not a successful cluster partition for the robust clustering problem, as there are overlapped clusters.
+%%%
+%%When the sets in an instance $\mathcal{I}$ for weighted $k$-set packing are disjoint, the sum of weights is identical to the total number of the CCs in the CRN which are mapped from $\mathcal{I'}$.
+%%Thus, when a instance $\mathcal{I}$ for $k$-set packing problem is true (or false), \ie the sum of weights is greater than $\lambda$, then in the CRN which is mapped from $\mathcal{I'}$, the sum of the numbers of CCs of the clusters is greater (or smaller) than $\lambda$.
+%
+%Hence, the weighted $k$-set packing can be reduced to the robust clustering problem in CRN, thus the latter problem is as hard as the former thus is of NP-hard.
+%%An example of the reduction is shown in Table~\ref{no_hard_proof_instance}.
 

### 2017-04-30 journal-draft/ettdoc.tex
Modify the expressions pointed by Erwin

@@
 %As to the coexistence of CR users, they can be notified by cluster head (CH) or other cluster members about the possible collision, the possibility for them to interfere neighbouring clusters is reduced~\cite{centralizedSharing80222}.
-Except for benefiting the dynamic spectrum sharing in CRN, clustering contributes to the other wireless networks in many aspects, which has already been discussed in many works. [CITATION MISSING]
+Except for benefiting the dynamic spectrum sharing in CRN, clustering contributes to the other wireless networks in many aspects, which has already been discussed in many works~\cite{Kawadia03, clustering_mesh_globecom2010, Abbasi_survey_07}.
 
@@
 The metric adopted by every secondary user in all the phases is the product of the number of CCs and cluster size.
-The drawbacks of this scheme are as follows, although the adopted metric considers both cluster size and the number of CCs, cluster formation can be easily dominated by only one factor, e.g.
-a node which can access many channels may exclude its neighbor and form a cluster by itself.
-(THIS SENTENCE IS TOO COMPLICATED.
-BREAK IT DOWN TO 2 OR 3 PLEASE.)
+The drawbacks of this scheme are as follows, although the adopted metric considers both the cluster size and the number of CCs, cluster formation can be easily dominated by only one factor.
+For example, a node which accesses abundant channels may form a cluster by itself and doesn't have motivation to unite neighboring nodes to form a cluster.
 In addition, this scheme leads to the high variance of the cluster sizes, which is not desired in certain applications as discussed in~\cite{clustering_globecom11, cluster_EW10}.
@@
 This paper extends~\cite{Li11_ROSS} in two dimensions.
-First, this paper renews the definition of robustness of clusters in a CRN, which is no longer the average number of CCs of clusters, but the ability of the clusters to sustain when the primary users' activity becomes more dynamic.
-(BAD FORMULATION TO SAY "renew".
-Changing definitions itself does not impose any benefit.
-Is there any an improval?)
-Second, this paper proposes size control mechanism, which solves the problem of devergence of clusters sizes in~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
-Besides, this paper provides a comprehensive analysis of the robust clustering problem and proposes a centralized solution. 
+First, this paper considers the correlation between the cluster robustness and the cluster size.
+As a result the cluster robustness is no longer indicated merely by the average number of CCs of clusters, but the ability of the CR nodes to get benefit from collective decision and of the clusters to sustain when the primary users' activity becomes more dynamic.
+Besides, this involment of cluster size enable us to solve the problem of clusters size devergence, which appears in~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
+Second, this paper provides a comprehensive analysis of the robust clustering problem, proposes both centralized and distributed solutions, and conducts extensive simulations. 
 %We stick to the motivation of forming robust clusters in CRN \ie let more CR users benefited from the cooperative decision making which is due to the clusters. 

### 2017-05-06 journal-draft/ettdoc.tex
polish the proof

@@
 %\usepackage{authblk}
+
+\usepackage{color}
 
@@
 \item the union of clusters in $\mathcal{T}$ is $\mathcal{N}$
-\item the sum of the $f(C)$ is the maximal, where $C\in \mathcal{T}$ and meanwhile the cluster sizes fall in the scope $\big[\delta_1, \delta_2\big]$.
+\item the sum of the $f(C)$, the number of common channels, is the maximal, where $C\in \mathcal{T}$ and meanwhile the cluster sizes fall in the scope $\big[\delta_1, \delta_2\big]$.
 $\delta_1, \delta_2\in \mathbb{Z}^+$ and $\delta_1 \leq \delta_2$.
@@
 
-The decision version of this problem is to determine whether there is a set of clusters, say $\mathcal{X}$, so that $\sum_{\forall C\in \mathcal{X}} f(C) \geqslant \lambda$ where $\lambda$ is a real number.
+The decision version of this problem is to determine whether there exists a set of clusters, say $\mathcal{X}$, so that $\cup C_{C\in\mathcal{X}} = \mathcal{N}$, and $\sum_{C\in \mathcal{X}} f(C) \geqslant \lambda$ where $\lambda$ is a real number.
 We have the following theorem on the problem's complexity.
@@
 We will show that the weighted $k$-set packing problem $\leq_P$ CRN robust clustering problem.
-Given an instance of the weighted $k$-set packing problem, \ie a collection of sets of distinct integers $\mathcal{Q}=\{S_1,S_2,\cdots,S_m\}$, the integer weight $\omega(S)$ for set $S$ and a integer $\lambda$, we will construct an instance of a CRN robust clustering problem within polynomial time.
-W.l.o.g. we let set $\cup_{\forall i\in\{1, \ldots, m\}}S_i = \{ 1, \ldots , N \} = \mathcal{N}$.
+Given an instance of the weighted $k$-set packing problem, \ie \textcolor{blue}{a collection of sets $\mathcal{Q}=\{S_1,S_2,\cdots,S_m\}$, where the set $S_i, i\in \{1,2,\ldots,m\}$ consists of positive integers.
+There is an integer weight $\omega(S_i)$ for $S_i$, in the end an integer $\lambda$ completes the description of this instance.}
+We will construct an instance of a CRN robust clustering problem within polynomial time.
+W.l.o.g. we let set $\cup_{i\in\{1, 2,\ldots, m\}}S_i = \{ 1, 2,\ldots , N \} = \mathcal{P}$.
 
 We will construct the CRN and the clusters as follows:
-For every set $S$ whose size is larger than 1, a corresponding cluster of CR nodes is generated.
-The CR nodes within this cluster can pair wise communicate and the IDs of these CR nodes correspond to the elements in $S$, besides, we allocate the $|\omega(S)|$ channels to all the CR nodes in this cluster, and the channels are on the spectrum band which is exclusive for this cluster.
-For every set $S$ which contains only one element, \ie $S =\{i\}$, a cluster composed with two CR nodes are created.
-One CR node's ID is $i$, the other CR node is the dummy node of the former and its ID is $N+i$.
-$|\omega(S)|$ channels from the exclusive spectrum band for this cluster are allocated to these two CR nodes.
-In the end, we construct the singleton clusters, where the IDs of the CR nodes correspond to the elements in $\mathcal{N}\backslash \cup_{S_i}$.
+For every set $S\in \mathcal{Q}$, there will be a corresponding cluster composed with CR nodes constructed.
+For the set whose size is larger than 1, the IDs of the constructed CR nodes are identical with the elements in it, and we locate the CR nodes so that any two of them can communicate directly when common channels are available on them.
+Besides, a set of channels with cardinality of $|\omega(S)|$ is allocated to all the CR nodes in this cluster, and the channels are on the spectrum band which is exclusive for this cluster.
+For the set $S$ which contains only one element, \ie $S =\{t\}$ where $t\in\mathcal{P}$, a cluster composed with two CR nodes will be created.
+In this case, one CR node's ID is $t$, the other CR node is the dummy node of the former and its ID is $t+N$.
+A number of $|\omega(S)|$ channels from the exclusive spectrum band for this cluster are allocated to these two CR nodes.
+In the end, we construct the singleton clusters, where the IDs of the CR nodes are from the difference of sets $\cup{S_i}$ and $\mathcal{P}$, and the number of CCs in these singleton clusters are the same as the weights for the corresponding sets.
+Actually, all the constructed CR nodes can be assumed to be put in a very small area so that each CR node is within the transmission scope of every other CR node.
+Note that in each constructed cluster, the CR nodes occupy the common channels which are exclusive to this cluster.
 Now we have completed a CRN and can claim that all the constructed clusters $C$ constitute the complete CRN network $\mathcal{N}$.
@@
 Now suppose there is a set of pairwise disjoint clusters which constitute the CRN $\mathcal{N}$, and the sum of $f(C)$ is greater than $\lambda$.
-After removing the singleton clusters, we can easily find the natural association between the clusters in the CRN and the sets in $\mathcal{Q}$. 
-The clusters which contain dummy CR nodes correspond to the sets which contain only one element, and the other clusters correspond to the sets in $\mathcal{Q}$, whose elements are the node IDs of the corresponding clusters.
-Then the sum of the weights of such sets equals to the sum of $f(C)$ and thus greater than $\lambda$.
+After removing the singleton clusters (whose common channels don't contribute to the sum of $f(C)$), we can easily find the natural association between the remaining clusters in the CRN and the sets in $\mathcal{Q}$.
+The clusters in the CRN correspond to the sets in $\mathcal{Q}$ according to the mapping between the node IDs in the clusters and the elements in the sets.
+In particular, the clusters which contain dummy CR nodes correspond to the sets which contain only one element.
+Then the sum of the weights of the corresponding sets equals to the sum of $f(C)$ and thus greater than $\lambda$.
 

### 2017-05-07 journal-draft/ettdoc.tex
modify the proof

@@
 \item the union of clusters in $\mathcal{T}$ is $\mathcal{N}$
-\item the sum of the $f(C)$, the number of common channels, is the maximal, where $C\in \mathcal{T}$ and meanwhile the cluster sizes fall in the scope $\big[\delta_1, \delta_2\big]$.
+\item when the number of common channels for cluster $C$ is denoted as $f(C)$, the sum of the $f(C)$ is the maximal, where $C\in \mathcal{T}$ and meanwhile the cluster sizes fall in the scope $\big[\delta_1, \delta_2\big]$.
 $\delta_1, \delta_2\in \mathbb{Z}^+$ and $\delta_1 \leq \delta_2$.
-When the cluster size is out of $\big[\delta_1, \delta_2\big]$, $f(C)=0$.
+When the cluster size is out of $\big[\delta_1, \delta_2\big]$, $f(C)$ is defined as 0.
 
@@
 
-First, we argue that robust clustering problem is in NP, since given a collection of clusters, a certifier can efficiently check that such clusters are pairwise disjoint, indeed contains all the CR nodes in the CRN $\mathcal{N}$ and the sum of $f(C)$ as shown in Definition~\ref{def_centralized_clustering} is greater than a certain value.
+%First, we argue that robust clustering problem is in NP, since given a collection of clusters, a certifier can efficiently check that such clusters are pairwise disjoint, indeed contains all the CR nodes in the CRN $\mathcal{N}$ and the sum of $f(C)$ as shown in Definition~\ref{def_centralized_clustering} is greater than a certain value.
 
 We will show that the weighted $k$-set packing problem $\leq_P$ CRN robust clustering problem.
-Given an instance of the weighted $k$-set packing problem, \ie \textcolor{blue}{a collection of sets $\mathcal{Q}=\{S_1,S_2,\cdots,S_m\}$, where the set $S_i, i\in \{1,2,\ldots,m\}$ consists of positive integers.
-There is an integer weight $\omega(S_i)$ for $S_i$, in the end an integer $\lambda$ completes the description of this instance.}
+Given an instance of the weighted $k$-set packing problem, \ie a collection of sets $\mathcal{Q}=\{S_1,S_2,\cdots,S_m\}$, where the set $S_i, i\in \{1,2,\ldots,m\}$ consists of positive integers.
+There is an integer weight $\omega(S_i)$ for $S_i$, in the end an integer $\lambda$ completes the description of this instance.
 We will construct an instance of a CRN robust clustering problem within polynomial time.
@@
 A number of $|\omega(S)|$ channels from the exclusive spectrum band for this cluster are allocated to these two CR nodes.
-In the end, we construct the singleton clusters, where the IDs of the CR nodes are from the difference of sets $\cup{S_i}$ and $\mathcal{P}$, and the number of CCs in these singleton clusters are the same as the weights for the corresponding sets.
-Actually, all the constructed CR nodes can be assumed to be put in a very small area so that each CR node is within the transmission scope of every other CR node.
-Note that in each constructed cluster, the CR nodes occupy the common channels which are exclusive to this cluster.
-Now we have completed a CRN and can claim that all the constructed clusters $C$ constitute the complete CRN network $\mathcal{N}$.
+Now we have constructed the clusters which correspond to all the sets in $\mathcal{Q}$.
+Note that every CR node is allowed to form a singleton cluster by itself, although its common channels don't contribute to the sum of $f(C)$.
+%In the end, we construct the singleton clusters, \ie for each element in $\mathcal{P}$, a corresponding singleton cluster is constructed.
+%In particular, if the CR node has been constructed and has been in certain clusters already through the previous steps, the CR node with all the channels assigned to it constitute a singleton cluster.
+%If there is an element in $\mathcal{P}$, which doesn't has a corresponding CR node yet, we simply construct this singleton cluster by adding that CR node, and assign it with a random number of channels from a exclusive spectrum band.
+%We call the latter kind of clusters the \textit{auxiliary singleton clusters}.
+
+Actually, all the constructed CR nodes can be assumed to locate in a very small area so that each CR node is within the transmission scope of every other CR node.
+Note that in each constructed cluster, the CR nodes occupy the common channels which are exclusive to this cluster, this design of transformation eliminates the formation of the cluster which doesn't have a corresponding set in $\mathcal{Q}$.
+The existence of the singleton clusters ensures that it is always possible to find out a group of clusters, which together constitute the whole CRN.
+%Now we have completed a CRN and can claim that all the constructed clusters $C$ constitute the complete CRN network $\mathcal{N}$.
 
 Now suppose there is a set of pairwise disjoint clusters which constitute the CRN $\mathcal{N}$, and the sum of $f(C)$ is greater than $\lambda$.
-After removing the singleton clusters (whose common channels don't contribute to the sum of $f(C)$), we can easily find the natural association between the remaining clusters in the CRN and the sets in $\mathcal{Q}$.
+After removing the singleton clusters, we can easily find the natural association between the remaining clusters and the sets in $\mathcal{Q}$. 
 The clusters in the CRN correspond to the sets in $\mathcal{Q}$ according to the mapping between the node IDs in the clusters and the elements in the sets.
@@
 We have now shown that our algorithm solves the weighted $k$-set packing problem using a black box for the robust clustering problem. 
-Since our construction takes polynomial time, and we have shown that robust clustering problem is in NP, we can conclude that Set Cover is NP-hard.
+Since our construction takes polynomial time, we can conclude that the robust clustering problem is NP-hard.
 %\begin{itemize}

### 2017-08-13 journal-draft/ettdoc_baseline.tex
modified till the comment C1-6

--- 2017-05-07 journal-draft/ettdoc.tex
@@
 %\author[3]{James Gross}
-\author{Di Li\textsuperscript{1}, Erwin Fang\textsuperscript{2}, James Gross\textsuperscript{3}\corrauth}
+\author{Di Li\textsuperscript{1}\corrauth, Erwin Fang\textsuperscript{2}, James Gross\textsuperscript{3}}
 %\affil[1]{RWTH Aachen University}
@@
 %\renewcommand\Authands{ and }
-\corraddr{Communication Theory Lab
-School of Electrical Engineering, 
-KTH Royal Institute of Technology
-SE - 100 44 Stockholm\\Email: james.gross@ee.kth.se}
+%\corraddr{Communication Theory Lab
+%School of Electrical Engineering, 
+%KTH Royal Institute of Technology
+%SE - 100 44 Stockholm\\Email: james.gross@ee.kth.se}
+\corraddr{Chair of Communication and Distributed Systems
+Ahornstraße 55 - building E3
+52074 Aachen
+Germany
+\\Email: li@umic.rwth-aachen.de}
 
@@
 \begin{itemize}
-\item ROSS without size control, \ie ROSS-DGA, ROSS-DFA.
+\item ROSS without size control: ROSS-DGA, ROSS-DFA.
 \item ROSS with size control, \ie ROSS-$\delta$-DGA and ROSS-$\delta$-DFA where $\delta$ is the desired cluster size.
@@
 %This means that the sizes of the clusters generated by ROSS-DGA are limited by the network density, and the size control feature further restricts the appearances of the big clusters, thus when the variants of ROSS are implemented, most of the CR nodes are in the clusters which are slightly smaller than the desired size.
+The limitation of distributed scheme ROSS is it doesn't generate clusters whose sizes exceed the cluster head's neighborhood.
+The reason is with ROSS, cluster heads form clusters on the basis of their neighborhood, and don't involve the nodes which are outside the neighborhood.
 
@@
 
-The limitation of distributed scheme ROSS is it doesn't generate clusters whose sizes exceed the cluster head's neighborhood.
-The reason is with ROSS, cluster heads form clusters on the basis of their neighborhood, and don't involve the nodes which are outside the neighborhood.
 %In the other way around, forming big cluster which extends a cluster head's neighborhood has limited application scenarios, as multiple hop communication and coordination are required within these clusters.

### 2017-08-14 journal-draft/ettdoc.tex
C1-4 to C1-10 are done

@@
 %
-A distributed clustering scheme ROSS is proposed in~\cite{Li11_ROSS} under the game theoretic framework. 
+A distributed clustering scheme ROSS (Robust Spectrum Sharing) is proposed in~\cite{Li11_ROSS} under the game theoretic framework. 
 Compared with the clustering schemes introduced above, the clusters are formed faster and the clusters possess more CCs than SOC.
@@
 In particular, a cluster consists of a cluster head $h(C)$ and a number of cluster members, and the cluster head is able to communicate with any cluster member directly.
-A cluster can be formed only by the cluster head.
+Our scheme enables the cluster heads are selected in a distributed manner, and a cluster can only be formed only by these selected cluster head.
+%C1-4
 %$\text{Nb}(i)$ denotes node $i$'s neighborhood which consists of all its one hop neighbors.
@@
 Figure~\ref{fig1} illustrates an example CRN where every node's connectivity vector is shown.	
+In Figure~\ref{fig1}, some primary users are randomly deployed in the network, and they are free to choose one channel out of the set of licensed channels $\mathcal{K}$ to operate.
+As to the secondary users, the channels they are allowed to use are those which are not ruled out by the primary users in their vicinities. 
+The sets of the indices of the available channels sensed by each node are: $K_A=\{1,2,3,4,5,6,10\}, K_B=\{1,2,3,5,7\}, \\K_C=\{1,3,4,10\}, K_D=\{1,2,3,5\}, \\K_E=\{2,3,5,7\}, K_F=\{2,4,5,6,7\}, \\K_G=\{1,2,3,4,8\}, K_H=\{1,2,5,8\}$.
+%C1-5
 \begin{figure}[ht!]
@@
 	\caption{Connectivity graph of the example CRN and the connectivity vector $(d_i, g_i)$ for each node.
+Primary users are not shown.
 The desired cluster size $\delta =3$.
-The sets of the indices of the available channels sensed by each node are: $K_A=\{1,2,3,4,5,6,10\}, K_B=\{1,2,3,5,7\}, K_C=\{1,3,4,10\}, K_D=\{1,2,3,5\}, K_E=\{2,3,5,7\}, K_F=\{2,4,5,6,7\}, K_G=\{1,2,3,4,8\}, K_H=\{1,2,5,8\}$.
 Dashed edge indicates the end nodes are within each other's transmission range.}
@@
 \label{clustering:theorem}
-Given a CRN, it takes at most $N$ steps that every secondary user either becomes cluster head, or gets included into at least one cluster.
+Given a CRN, it takes at most $N$ steps before every secondary user either becomes cluster head, or gets included into at least one cluster.
 \end{theorem}
-Here, by \textit{step} we mean one secondary user executing Algorithm~\ref{clustering:theorem} for one time.
-The Proof is in Appendix~\ref{proof_clustering:theorem}.
-%
-The procedure of the proof also illustrates the maximal time needed to conduct Algorithm~\ref{clustering:theorem}. 
-Consider an extreme scenario, where all the secondary nodes sequentially execute Algorithm~\ref{alg0}, \ie they constitute a list as discussed in the example in the proof.
-%
+Here, by \textit{step} we mean Algorithm~\ref{clustering:theorem} is executed by a secondary user for one time.
+Note that the minimum number of steps is 1, \eg when a cluster head is elected and all the other nodes are within its neighborhood.
+The Proof on the upper bound of the steps is given in Appendix~\ref{proof_clustering:theorem}.
+%The proof also illustrates the maximal time needed to conduct Algorithm~\ref{clustering:theorem}. 
+Consider an extreme scenario, where all the secondary nodes sequentially execute Algorithm~\ref{alg0}, \ie they constitute a chain as discussed in the example in the proof.
+%
+Assuming there is a token in the CRN, one node is allowed to execute Algorithm~\ref{alg0} only when it holds the token, and it then transfers the token to the neighboring node on the chain.
 If one step can be finished within a certain time span $T$, then the total time needed for the network to conduct Algorithm~\ref{clustering:theorem} is $N*T$.
+%C1-6
 As Algorithm~\ref{alg0} can be executed concurrently by different secondary users, the needed time can be considerably reduced.
@@
 %This judgement is conducted periodically, and phase I ends after every node ascertains it is cluster head or not.
-If we apply Algorithm~\ref{alg0} to the example shown in Figure~\ref{fig1}, then the outcome is shown in Figure~\ref{fig2}.
+If we apply Algorithm~\ref{alg0} to the example shown in Figure~\ref{fig1}, the outcome is shown in Figure~\ref{fig2}.
 Node $B$ and $H$ have the same individual connectivity degree, i.e., $d_B=d_H$. As $g_H=2>g_B=1$, node $H$ becomes the cluster head and cluster $C(H)$ is $\{H, B, A, G\}$.
@@
 As there are overlaps between neighboring clusters, the sizes of the clusters formed in this phase are larger than that of the finally formed clusters.
-Hence, a cluster head excludes some cluster members when the cluster size exceeds $t\cdot \delta$, where constant parameter $t$ is dependent on the network density and CR nodes' transmission range and $t>1$.
+Hence, a cluster head excludes some cluster members when the cluster size exceeds a certain threshold.
+We set the threshold as $t\cdot \delta$, where $\delta$ is the desired cluster size.
+The constant parameter $t$ is usually larger than 1 and is dependent on the network density and CR nodes' transmission range, in particular, $t$ is between 1 and the ratio between the average number of neighbors and the desired size.
+A smaller or bigger $t$ may lead to more clusters with smaller or larger size than $\delta$.
+Because of $t$, the threshold is larger than the desired size, then there will be some nodes choosing to affiliate with other clusters in the following phases.
+%C1-7
 In particular, the cluster head removes the cluster members sequentially according to the following principle, the absence of one cluster member leads to the maximum increase of the CCs within the cluster.
@@
 This procedure is similar with that in Section~\ref{ross_p1_guarantee_ccc}, thus Algorithm~\ref{alg_size_control_available_CCC} can be reused.
-The $t$ is set to 1.3.
+%The $t$ is set to 1.3. 	
+%C1-7
 
@@
 
-Now we apply both ROSS-DGA and ROSS-DFA to the toy network in Figure~\ref{fig2} which has been applied the phase I of ROSS.
+Now we apply both ROSS-DGA and ROSS-DFA to the network in Figure~\ref{fig2} which has been applied the phase I of ROSS.
+%C1-8
 In the network, node $A$'s claiming clusters are cluster $C(C), C(H)\in S_A$, their members are $\{A,B,C,D\}$ and $\{A,B,H,G\}$ respectively. 
@@
 The number of licensed channels is 10, each PU is operating on each channel with probability of 50\%.
+The other parameters \ie the number of CR and PU, and their transmission ranges are given in the beginning of the respective simulation sections.
+%C1-10
 The constant $t$ which is used to control cluster size for ROSS (discussed in Section~\ref{ross_p2_cluster_pruning}) is 1.3.
@@
 \subsection{Centralized Schemes vs. Decentralized Schemes}
-There are 10 primary users and 20 CR users dropped randomly (with uniform distribution) within a square area of size $A^{2}$, where we set the transmission ranges of primary and CR users to $A/3$.
+In this part of simulation, there are 10 primary users and 20 CR users dropped randomly (with uniform distribution) within a square area of size $A^{2}$, where $A$ is a positive value and we set the transmission ranges of primary and CR users to $A/3$.
+%C1-10, C1-9
 %There are 10 available channels. 
@@
 \SetAlgoLined
-\KwIn{$d_j, g_j, j\in \text{Nb}(i)\setminus \Lambda$, $\Lambda$ means cluster heads. Empty sets $\tau_1,\tau_2$}
-\KwResult{Returning 1 means $i$ is cluster head, then $d_j$ is set to 0, $j\in \text{Nb}(i)\setminus \Lambda$. returning 0 means $i$ is not cluster head.}
-
+\KwIn{$d_j, g_j, j\in \text{Nb}(i)\setminus \Lambda$, $\Lambda$ denotes the set of cluster heads among $\text{Nb}(i)$. Empty sets $\tau_1,\tau_2$}
+\KwResult{Returning 1 means $i$ is cluster head, and $d_j$ is set to 0, $j\in \text{Nb}(i)\setminus \Lambda$. Returning 0 means $i$ is not cluster head.}
+%C1-6-wording
 \If{$\nexists j\in \text{Nb}(i)\setminus \Lambda$, such that $d_i \geq d_j$}{

### 2017-08-18 journal-draft/ettdoc.tex
modified section 1

@@
 % ... decreases considerably the negative probability due to the random channel effects like fading and shadowing.
-Clustering is a process of grouping certain users in geographic proximity into a collective.
-In the context of cognitive radio netowrks, a formed cluster helps the participants not only to improve the spectrum sensing accuracy, but also to coordinate the channel switch operation when the primary users are detected by at least one secondary user in that cluster.
+
+Clustering is the process of grouping certain users in geographic proximity into a collective, and as an effective technique, it is proposed with the emergence of mobile wireless networks~\cite{gerla_97} and there has been a plethora of clustering schemes.
+As to the wireless networks where no restriction is imposed on the nodes to access the spectrum, \ie 
+%Different clustering strategies have been proposed for wireless networks of different types.
+wireless ad-hoc, mesh networks and sensor networks, the objective of clustering can be to decrease the transmission power consumption~\cite{Kawadia03}, to improve the routing performance~\cite{clustering_mesh_globecom2010}, or to imrove the network lifetime and coverage~\cite{Abbasi_survey_07}.
+%In CRN, clusters are formed in the very beginning of the network operation, and re-formed periodically according to the dynamics of the CRN.
+In the context of cognitive radio netowrks, a formed cluster helps the participants not only improve the spectrum sensing accuracy, but also coordinate the channel switch operation when the primary users are detected by at least one secondary user in that cluster.
 Then all the cluster menmbers can stop payload transmission swiftly and vacate the operating channel ~\cite{willkomm08}.
@@
 %As to the coexistence of CR users, they can be notified by cluster head (CH) or other cluster members about the possible collision, the possibility for them to interfere neighbouring clusters is reduced~\cite{centralizedSharing80222}.
-Except for benefiting the dynamic spectrum sharing in CRN, clustering contributes to the other wireless networks in many aspects, which has already been discussed in many works~\cite{Kawadia03, clustering_mesh_globecom2010, Abbasi_survey_07}.
-
-%%[crn for clustering] 
-%%due to attenuation of signal propagation, primary users can only be detected by CR users when they locate closely to CR users.
-%In cognitive radio networks, secondary users which locate closely with each other are possibly affected by the same group of primary users, so that the availability of licensed spectrum is similar to them, \ie certain channels are available on each of them.
-%The similarity of available spectrum on a group of neighbouring CR nodes, along with the benefit of collaborative decision among multiple nodes, leads to clustering as an effective approach for many applications.
-%[robustness issue for clustering]
-
-In CRN, clusters are formed in the very beginning of the network operation, and re-formed periodically according to the dynamics of the CRN.
-Each formed cluster has one or multiple unlicensed channels which are available for every CR node in the cluster.
+%Except for benefiting the dynamic spectrum sharing in CRN, clustering contributes to the other wireless networks in many aspects~\cite{Kawadia03, clustering_mesh_globecom2010, Abbasi_survey_07}.
+
+In CRN, a formed cluster seizes one or multiple unlicensed channels which are available for every CR node in the cluster.
 In this paper available unlicensed channels are called \textit{common licensed channels} (or common channels for short, which is abbreviated as CC).
+The availability of CCs within a cluster decides the existence of that cluster, \ie if no CCs are available then the corresponding cluster does not exist.
 Both payload and control overheads can be transmitted on the CCs.
@@
 In particular, if that channel is being used for payload communication, the communication pair will stop and resume the transmission on another available CC.
-The availability of CCs within a cluster defines the existence of that cluster, \ie if no CCs are available then the corresponding cluster does not exist.
 %As long as there is a CC available, the corresponding cluster can continue to exchange payload data.
-In the context of CRN, the activity of primary users is usually unknown to the secondary users. In such cases the primary users' activity is deemed as random.
-Consequently, a cluster which secures more CCs will anticipate a longer life expectancy. In other words, such clusters are more robust.
-It is obvious that fewer secondary users in one cluster yield more CCs.
+In the context of CRN, the activity of primary users is usually unknown to the secondary users, and the primary users' activity is deemed as random.
+Consequently, a cluster which secures more CCs will anticipate a longer life expectancy. 
+In other words, such clusters are more robust.
+
+Cluster size is inherently correlated with the cluster robustness.
+Given a CRN, it is obvious that getting rid of certain secondary users from a cluster may yield more CCs.
 However, this contradicts to one of the motivations of clustering, \ie the cooperative decision making, where more users result in more accurate sensing result~\cite{Consensus_based_clustering12}.
 Thus the number of small clusters, especially the \textit{singleton clusters}, \ie the cluster which has only one CR node, should be minimized.
-As to the cluster which consists of many nodes, although the spectrum sensing is benefited, it usually leads to less common channels. This undermines the robustness of the cluster.
+In the other hand, as to the cluster which consists of many nodes, although the spectrum sensing is benefited, it usually leads to less common channels. This undermines the robustness of the cluster.
 Thus, the cluster robustness discussed in terms of number of CCs carries little meaning when the sizes of formed clusters are not considered.
@@
 
+Here we give a brief review on the clustering in CRN, with emphasis on the theme of robust clustering.
+%%[crn for clustering] 
+%%due to attenuation of signal propagation, primary users can only be detected by CR users when they locate closely to CR users.
+%In cognitive radio networks, secondary users which locate closely with each other are possibly affected by the same group of primary users, so that the availability of licensed spectrum is similar to them, \ie certain channels are available on each of them.
+%The similarity of available spectrum on a group of neighbouring CR nodes, along with the benefit of collaborative decision among multiple nodes, leads to clustering as an effective approach for many applications.
+%[robustness issue for clustering]
+%%%%%%%%%%%
 %On the other hand, large clusters are not preferred in some scenarios neither, \eg for the CRN composed with resource limited users, managing the cluster members in a large cluster is a substantial burden.
 %Hence, the cluster size should fall in a desired range according to different application scenarios~\cite{Chen04clusteringalgorithms, capacity_cluster_06}.
-
+%%%%%%%%%%%%
 %with the intention to provide a robust infrastructure for the applications which may be conducted above that in CRN.
@@
 %When the cluster size is not deliberately discussed, it is also decided alongside the optimization of the network, \eg the opimal selection of the aggregation points in a wireless sensor network results in the clusters~\cite{data_aggr_algorithm_04}.
-
-Different clustering strategies have been proposed for wireless networks of different types.
-As there is no restriction on the nodes to access the spectrum in wireless ad-hoc, mesh networks and sensor networks, the objective of clustering is to decrease the transmission power consumption~\cite{Kawadia03}, to improve the routing performance~\cite{clustering_mesh_globecom2010}, or to imrove the network lifetime and coverage~\cite{Abbasi_survey_07}.
+%%%%%%%%%%%%%
 %Various clustering schemes are proposed to target different aspects in cognitive radio networks.

### 2017-08-18 journal-draft/ettdoc.tex
polish the simulation part - robustness

@@
 
+\item \textbf{Robustness of the clusters against newly added PUs.}
+Robustness is illustrated by the number of the unclustered CR nodes in the CRN, after the CRN being challenged by the increasing number of PUs.
+This metric indicates the robustness of the clusters, \ie as to the clusters formed for a given CRN and spectrum availability, how many CR nodes can still be benefited from the clusters when the spectrum availability decreases.
+
 \item \textbf{Cluster sizes.}
@@
 We investigate the distribution of CRs residing in the formed clusters with different sizes.
-
-\item \textbf{Robustness of the clusters against newly added PUs.}
-We increase the number of PUs to challenge the non-singleton clusters, and count the number of the unclustered CR nodes.
-This metric indicates the robustness of the clusters, \ie as to the clusters formed for a given CRN and spectrum availability, how many CR nodes can still be benefited from the clusters when the spectrum availability decreases.
 
@@
 \subsubsection{Robustness of the formed clusters}
+Here we see how vulnerable the clusters are when they are exposed to the increasing influence of the PUs.
 We increase the primary users' activity by importing 20 batches of PUs sequentially in the CRN, where each batch includes 10 PUs. 
 %
-Figure~\ref{singleton_clusters_100} and \ref{singleton_clusters_200} show that when $N=100$ and 200, compared with the variants of ROSS, more unclustered CR nodes are generated by SOC.
+Figure~\ref{singleton_clusters_100} and \ref{singleton_clusters_200} show that when $N=100$ and 200, compared with the variants of ROSS, more unclustered CR nodes are caused by SOC with the same intensity of PUs' activities.
 When $N=300$ as shown in Figure~\ref{singleton_clusters_300} and the new PUs are not many, ROSS-DGA/DFA generate slightly more unclustered CR nodes than SOC, but SOC's performance deteriorates quickly when the PUs continue increasing.

### 2017-09-06 journal-draft/ettdoc.tex
add new picturs, but pictures need improvment

@@
 Regarding the operation of CRN, efficient spectrum sensing is identified to be critical for a smooth operation of a cognitive radio network~\cite{Sahai_FundamentalDesignTradeoffs2006}.
-Efficient spectrum sensing can be achieved by cooperative spectrum sensing of multiple secondary users, which has been shown to cope effectively with noise uncertainty and channel fading, thus remarkably improving the sensing accuracy~\cite{coorperativeSensing_Akyildiz11}.
+The rate of false negative, \ie misdetecting the active primary users, can be decreased by cooperative spectrum sensing of multiple secondary users, which has been shown to cope effectively with noise uncertainty and channel fading, thus remarkably improving the sensing accuracy~\cite{Jacob2012, coorperativeSensing_Akyildiz11}.
+%C3
 Collaborative sensing relies on the consensus of CR users\footnote{The terms user and node appear interchangeably in this paper.
@@
 Thus the number of small clusters, especially the \textit{singleton clusters}, \ie the cluster which has only one CR node, should be minimized.
-In the other hand, as to the cluster which consists of many nodes, although the spectrum sensing is benefited, it usually leads to less common channels. This undermines the robustness of the cluster.
+On the other hand, as to the cluster which consists of many nodes, although the spectrum sensing is benefited, it usually leads to less common channels. This undermines the robustness of the cluster.
 Thus, the cluster robustness discussed in terms of number of CCs carries little meaning when the sizes of formed clusters are not considered.
@@
 The percentage of debatable nodes in the network is shown in Figure~\ref{percentage_overlapping_node}, which is between 10\% to 60\% of the total CR nodes in the network.
-In the other hand, the number of clusters heads is dependent on the network density and the CR node's transmission range as mentioned in Section~\ref{phaseI}.
+On the other hand, the number of clusters heads is dependent on the network density and the CR node's transmission range as mentioned in Section~\ref{phaseI}.
 The simulation in \cite{robust_clustering_arxiv} shows the cluster heads are only 3.4\% to 20\% of the total CR nodes.
@@
 
-We investigate the schemes with respect to four metrics.
+We investigate the schemes in the following aspects.
 
@@
 
+\item \textbf{Influence from inaccurate spectrum sensing.}
+The above simulations are conducted with the assumption of perfect spectrum sensing.
+As the errors in spectrum sensing is inevitable, we are interested to see the performance of the distributed schemes when the spectrum sensing is not perfect.
+%The errors in spectrum sensing is inevitable, and the decision is made by the secondary users and based on the sensing results, without considering the difference between the sensing result and the ground truth.
+The false negative in spectrum sensing, which misdetects the presence of the active primary users, is harmful to the primary users and should be avoided as much as possible.
+On the contrary, false positive \ie which reports the presence of active primary users when there are actually not, only decreases the available spectrum for the secondary users.
+In this regard, we assume only the false negative exists in the spectrum sensing.
+
+We assume when a secondary user is within the transmission range of an active primary user, the probability that it misdetects and thus regards a channel is available equals to the rate of false negative.
+The secondary users make clustering decisions based on the imperfect spectrum sensing.
+After the clustering process is completed, we correct the spectrum availability with the ground truth.
+Then certain formed clusters may be affected as their CCCs which are obtained due to false negative will be revoked.
+%When the clustering process is completed, we will examine the performances on robustness and cluster size control with the group truth spectrum availability.
+%C3
 \end{itemize}
 
-Simulation consists of two parts, first we investigate the performance of centralized scheme and the distributed schemes in a small network, as there is no polynomial time solution available to solve the centralized problem.
+The simulation consists of two parts, first we investigate the performance of centralized scheme and the distributed schemes in a small network, as there is no polynomial time solution available to solve the centralized problem.
 In the second part, we investigate the performance of the proposed distributed schemes in the CRN with different scales and densities.
@@
   \centering
-  \includegraphics[width=.7\linewidth]{ccc_large_scale_color.pdf}
+  \includegraphics[width=.7\linewidth]{ccc_large_scale_color_082017_newdata_no_texture.pdf}
   \caption{Average number of CCs of non-singleton clusters}
@@
 The reason is with ROSS, cluster heads form clusters on the basis of their neighborhood, and don't involve the nodes which are outside the neighborhood.
+
+\subsubsection{The Performance with False Negative in Spectrum Sensing}
+
+Figure~\ref{false_negative} shows the average number of CCCs are decreased slightly.
+The reason is that in the process of 
+A channel on a CR, which is due to false negative, is very likely ruled out during the interaction in the neighborhood.
+Figure~\ref{false_negative_ccc} is shows the size distribution of the ROSS-DGA, ROSS-$\delta$-DGA and SOC with the existence of spectrum sensing false negative.
+\begin{figure}[!h]
+  \centering
+   \includegraphics[width=0.7\linewidth]{false_negative.pdf}
+  \caption{The number of CCCs per non-singleton cluster with the presence of spectrum sensing false negative}
+  %, there are $x=6$ when $N=100$, $x=12$ when $N=200$, $x=21$ when $N=300$, which is around $2/3$ of the number of average neighbours.
+  \label{false_negative_ccc}
+\end{figure}
+
+The influence of the false negative on the sustainability of the clusters can be seen from Figure~\ref{false_negative_CDF}.
+When false negative exists and increases, the number of singleton clusters increases accordingly.
+Actually as to the ROSS variants, the changes of the CDF curves are due to the increasing singleton clusters.
+In contrast to the ROSS variants, the clusters resulted from SOC are affected by the sensing errors greatly, \ie when false negative rate is 30\%, a lot more small clusters are generated than that when other false negative rates present.
+ROSS variants are resilient to the false negative through the negotiation within the neighborhoods, whereas SOC demonstrates obvious divergence when certain rate of false negative exists.
+
+\begin{figure}[!h]
+  \centering
+   \includegraphics[width=0.7\linewidth]{draw_cdf_clusterSize_with_false_negative.pdf}
+  \caption{100 CRs with false negative in spectrum sensing, 30 PUs in network}
+  \label{false_negative_CDF}
+\end{figure}
 

### 2017-09-09 journal-draft/ettdoc.tex
modify the text about false negative, change figure

@@
 
-Figure~\ref{false_negative} shows the average number of CCCs are decreased slightly.
-The reason is that in the process of 
-A channel on a CR, which is due to false negative, is very likely ruled out during the interaction in the neighborhood.
-Figure~\ref{false_negative_ccc} is shows the size distribution of the ROSS-DGA, ROSS-$\delta$-DGA and SOC with the existence of spectrum sensing false negative.
+Figure~\ref{false_negative_ccc} shows the average number of CCCs decrease slightly when the false negative rate increases.
+The size distribution of the ROSS-DGA, ROSS-$\delta$-DGA and SOC is shown in Figure~\ref{false_negative_ccc}.
 \begin{figure}[!h]
@@
 \end{figure}
-
-The influence of the false negative on the sustainability of the clusters can be seen from Figure~\ref{false_negative_CDF}.
-When false negative exists and increases, the number of singleton clusters increases accordingly.
-Actually as to the ROSS variants, the changes of the CDF curves are due to the increasing singleton clusters.
-In contrast to the ROSS variants, the clusters resulted from SOC are affected by the sensing errors greatly, \ie when false negative rate is 30\%, a lot more small clusters are generated than that when other false negative rates present.
-ROSS variants are resilient to the false negative through the negotiation within the neighborhoods, whereas SOC demonstrates obvious divergence when certain rate of false negative exists.
+%The influence of the false negative on the sustainability of the clusters can be seen from Figure~\ref{false_negative_CDF}.
+For all the schemes, when false negative increases, the number of singleton clusters increases accordingly.
+%As to the ROSS variants, the changes of the CDF curves are resulted from the increasing singleton clusters.
+The clusters from SOC are affected by the sensing errors greatly, \ie when false negative rate is 30\%, a lot more small clusters are generated than that when other false negative rates present.
+SOC demonstrates obvious divergence when certain rate of false negative exists, in contrary, ROSS variants are resilient to the false negative in terms of cluster sizes.
+The negotiation within the neighborhoods adopted by ROSS variants rules out the channel which is due to false negative successfully, which doesn't work well in SOC.
 
@@
 \subsection{Insights Obtained from the Simulation}
-The simulation made with the large CRN network confirms that made with the small CRN network, which is that the average number of CCs along doesn't tell the robustness of the clusters, because the cluster size and the constitution of the cluster also affect the robustness.
-
-The centralized clustering scheme is able to form the clusters which satisfy the requirement on cluster size strictly, and the clusters are robust against the PUs' activity, besides, it involves the smallest control overhead in the process of clustering.
-As distributed schemes, the variants of ROSS outperform SOC considerably on three metrics.
-First, the variants of ROSS generate less unclustered nodes than SOC for a given CRN, and the resulted clusters are more robust than SOC when PUs become more active.
-Second, the signaling overhead involved in ROSS is about half of that needed for SOC, and the signaling messages are much shorter that the latter.
-Third, the sizes of the clusters generated by ROSS demonstrate smaller discrepancy than that of SOC.
+The simulation with large CRN network confirms the conclusion drawn from the small CRN network.
+First, different from the assumption adopted in all the previous works, the average number of CCCs per cluster can tell the robustness against the increasing influence of the primary users.
+Second, the centralized clustering scheme is able to form the clusters which satisfy the requirement on cluster size strictly, and the clusters are robust against PUs' increasing activity, besides, it involves the smallest control overhead in the process of clustering.
+Third, as distributed schemes, the variants of ROSS outperform SOC considerably in four aspects.
+\begin{itemize}
+\item The variants of ROSS generate less unclustered nodes than SOC for a given CRN, and the resulted clusters are more robust than SOC when PUs become more active.
+\item The signaling overhead involved in ROSS is about half of that needed for SOC, and the signaling messages are much shorter that the latter.
+\item The sizes of the clusters generated by ROSS demonstrate smaller discrepancy than that of SOC.
+\item The variants of ROSS are more resilient against the imperfect spectrum sensing.
+\end{itemize}
+
 Moreover, the ROSS variants with size control features achieve similar performance to the centralized scheme in terms of cluster size, and the cluster robustness is similar when applying the variants of ROSS and the centralized scheme respectively.
 %
-As to the variants of ROSS, the greedy mechanism in ROSS-DGA helps to improve the performance on cluster size and cluster robustness at the cost of increased signaling overhead.
+Among the variants of ROSS, the greedy mechanism in ROSS-DGA helps to improve the performance on cluster size and cluster robustness at the cost of increased signaling overhead.
 %We also notice that as a metric, the number of CCs per non-singleton cluster doesn't indicate the robustness of clusters as shown in Figure~\ref{singleton_clusters} and \ref{unclustered_100_200_300}, although it is adopted as the metric in the formation of clusters.

### 2017-09-10 journal-draft/ettdoc.tex
add the definition of robustness

@@
 The availability of CCs within a cluster decides the existence of that cluster, \ie if no CCs are available then the corresponding cluster does not exist.
-Both payload and control overheads can be transmitted on the CCs.
+As the activity of primary users is usually unknown to the secondary users, it is deemed as random as to secondary users.
+Consequently, a cluster which secures more CCs will anticipate a longer life expectancy. 
+In other words, such clusters are more robust.
+In this paper, the robustness of a cluster is the ability to sustain with the existence of primary users.
+%
+Within in a cluster, both payload and control overheads can be transmitted on the CCs.
 %Out of the available CCs, there are always one or multiple channels which are used for the payload communication.
@@
 %As long as there is a CC available, the corresponding cluster can continue to exchange payload data.
-In the context of CRN, the activity of primary users is usually unknown to the secondary users, and the primary users' activity is deemed as random.
-Consequently, a cluster which secures more CCs will anticipate a longer life expectancy. 
-In other words, such clusters are more robust.
 

### 2017-09-10 journal-draft/ettdoc.tex
change ccc to cc

@@
 After the clustering process is completed, we correct the spectrum availability with the ground truth.
-Then certain formed clusters may be affected as their CCCs which are obtained due to false negative will be revoked.
+Then certain formed clusters may be affected as their CCs which are obtained due to false negative will be revoked.
 %When the clustering process is completed, we will examine the performances on robustness and cluster size control with the group truth spectrum availability.
@@
 
-Figure~\ref{false_negative_ccc} shows the average number of CCCs decrease slightly when the false negative rate increases.
+Figure~\ref{false_negative_ccc} shows the average number of CCs decrease slightly when the false negative rate increases.
 The size distribution of the ROSS-DGA, ROSS-$\delta$-DGA and SOC is shown in Figure~\ref{false_negative_ccc}.
@@
    \includegraphics[width=0.7\linewidth]{false_negative.pdf}
-  \caption{The number of CCCs per non-singleton cluster with the presence of spectrum sensing false negative}
+  \caption{The number of CCs per non-singleton cluster with the presence of spectrum sensing false negative}
   %, there are $x=6$ when $N=100$, $x=12$ when $N=200$, $x=21$ when $N=300$, which is around $2/3$ of the number of average neighbours.
@@
 The simulation with large CRN network confirms the conclusion drawn from the small CRN network.
-First, different from the assumption adopted in all the previous works, the average number of CCCs per cluster can tell the robustness against the increasing influence of the primary users.
+First, different from the assumption adopted in all the previous works, the average number of CCs per cluster can tell the robustness against the increasing influence of the primary users.
 Second, the centralized clustering scheme is able to form the clusters which satisfy the requirement on cluster size strictly, and the clusters are robust against PUs' increasing activity, besides, it involves the smallest control overhead in the process of clustering.

### 2017-09-10 journal-draft/ettdoc.tex
minor changes in the related work

@@
 In other words, such clusters are more robust.
-In this paper, the robustness of a cluster is the ability to sustain with the existence of primary users.
+In this paper, the robustness of the clusters is their ability to sustain with the existence of primary users.
 %
@@
 
-Here we give a brief review on the clustering in CRN, with emphasis on the theme of robust clustering.
+In the following we will give a brief review on the clustering in CRN, with emphasis on the theme of robust clustering.
 %%[crn for clustering] 
@@
 However, as all the other clustering schemes, this scheme does not have control over the formation of the very small or very large clusters which are not desirable.
-Furthermore, this work doesn't consider the robustness of clusters against the increasing activity of primary users, which leaves their claim of robustness unverified.
+Furthermore, both this work and SOC define robustness just to be the number of CCs per cluster, and don't consider the sustainability of clusters against the increasing activity of primary users, which leaves their claim on robustness unverified.
 %

### 2017-09-16 journal-draft/response_to_editors.tex
add .gitignore

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{cite}
\author{Di Li}
\title{Response to editors}
\begin{document}

We thank all the reviewers and editors for their feedback and suggestions.
In the following we will address the questions and comments from the viewers.

Reviewer 1:

 1)  First of all, clustering technique is not new and it is one of the well-researched areas in ad hoc network, cognitive radio, HetNet etc. The article does not review the latest publications in this area. The references are not adequate due to the fact that no recent works have been investigated. Therefore, it makes it insufficient (or unsatisfactory) work in present context.
A lot of works on clustering in ad hoc networks or sensor networks, which address routing, power consumption and communication quality.
Compared with the wireless networks where spectrum availability is not opportunistic, the clustering in CRN facilitated the better usage of the available spectrum, and meanwhile the conduction of clustering is restricted by the spectrum availability.
This fact makes clustering in CRN a difficult topic.
Up to now, only \cite{LIU_TMC11_2, Li11_ROSS, mansoor_15_cluster_robust} and \cite{Mansoor2015} xxxxxxxxxxxxxxxx

    2)  The presentation of the paper is not good enough and needs a lot of improvements. For instance, ROSS scheme has been mentioned in the paper in many places, but it is not properly defined (though reference has been given). I had to check the reference paper to know it is Robust Spectrum Sharing. The journal article must be self-contained.
    This explanation of the scheme name is added in the introduction section.

    3)  The paragraphs are too long in the Introduction. As a result, the paragraph contains too many information which are not related each other. This makes readers difficult to understand the concept.
    xxxxxxx

    4)   In page 3, it is mentioned that “A cluster can be formed only by the cluster head”. As a matter of fact, the cluster head formation is itself a very challenging task in any cluster based approach. There are many previous works which describe the cluster head selection techniques. Please justify your statement with proper assumption or previous works that how the cluster heads are selected. I can see the description is in the few pages later but some information must be provided where it is described first time. By the way, the CH formation technique described in 4.1.1 is not novel.
	    As the reviewer has pointed out, this statement is somehow misleading. 
	    We put this line in the paper and wanted to say that after the clusters are decided, it is the cluster head's job to form a cluster out of the neighboring nodes.
In the revised version, we have changed the statement as "Our scheme enables the cluster heads are selected in a distributed manner, and a cluster can only be formed only by these selected cluster head. "

    5)  In my understanding, the values of connectivity degree in Fig. 1 came from the assumption of $K_A$, $K_B$ …..$K_H$. Each node has number of available channels and I assume that they have been randomly chosen as mentioned in Fig. 1 Caption. It would be good to mention how to obtain such information in ad hoc cognitive radio network?
    As stated in the system model, both primary and second users are able to work on the same set of channels. 
    We assume the primary users are randomly located and work on each channel with a certain probability.
    Then the secondary users can only use the channel which is not being used by the primary users, and the secondary user locates out of the transmission range of that primary user.

    6)  Theorem 4.1 is too obvious, authors need to discuss in terms of convergence and complexity of the proposed method. In fact, Theorem 4.1 and description immediately are so confusing and misleading. If step is defined as executing Algorithm 4.1 for one time which again takes at most N steps. A further clarification is needed.
    We give the definition of 'step' in the revised version.
    Immediately below the theorem 4.1, "Here, by step we mean Algorithm 4.1 is executed by a secondary user for one time."
    7)  In 4.1.3, parameter t depends on density of the network. Please clarify what is the impact of selecting value of t in system design, such as selecting t to be higher than 1.3.

    8)  In page 7, what does “the toy network in Figure 2” mean? I hope it’s a typo. Otherwise, the Sections 4.2.1, 4.2.2, 4.2.3 are nicely written.

    9)  In simulation, have authors considered the spectrum sensing parameters on each secondary nodes? Are the channels randomly made available to users? Please clarify. What value of A is chosen in simulation?

    10) It is mentioned in the article that “The number of licensed channels is 10, each PU is operating on each channel with probability of 50\%”. It means there will be only 5 channels available (maximum) to each secondary users. In section 5.1, 7 channels are available for each CR node. It means there is chance of interference in two nodes. Please clarify those conflicts.

    11) Further comparison is needed against the previous works to justify the robustness of the proposed method.

Reviewer: 2

Comments to the Author
In this paper, authors investigate the optimization algorithms for node clustering strategy in ad hoc based cognitive radio networks, where both the centralized solution and distributed solution are considered.

In Section 2, that the definition of channel $k\in K$, i.e. fading channel or noisy channel? Does the channel contain pathloss and shadowing and/or fast fading? Does the value of k indicate the channel gain in either time or frequency domain? Does the channel invariant or variant (how fast) during the clustering for how long windows range? In practical, the channel changes along with the transmission, the performance clustering may be impacted by the varying channel. What's the impact of insufficient channel knowledge?

The work emphasize on the robustness of clustering. However, such an evaluation in terms of robustness metric is not clear. The definition of robustness and relative discussions as well as the results should be further elaborated. The definition appears in Section 5 but my suggestion is to clearly state it in the system model and describe why choose this robustness metric according its relation with system design.

In Section 4, algorithm flow charts should be included.

In Section 5, Fig. 10 is missing. Fig. 14-16 can be subfigures, similar to Fig. 17-19.

Reviewer: 3

Comments to the Author
In this paper, the authors consider the robust clustering problem in the ad-hoc Cognitive Radio Networks (CRNs). The paper is well fromalized. The research background and motivation are well described. The research problem is well addressed. The simulation based experiment is conducted to show the performance of the suggested solution approach to the addressed problem.

Overall, the considered topic is very interesting. The authors well presented the considerations and assumptions on several key research issues, which inherently exist in the ad-hoc networks, for instance, decentralized spectrum sensing, synchronization on the sensing results and congestion control. To solve the addressed problem, the authors jointly use different research methods such as graphic theory and game theory, which have been widely reported in recent studies on CRNs. The experiment is well conducted with the thorough performance analysis and comparison on different experimental scenarios.

However, it seems that the authors totally miss a very important research issue, which is referred to as spectrum sensing errors in terms of overlook and misidentification on the channel availability by Secondary Users (SUs). Because the sensing errors may highly affect the effectiveness and performance of the suggested solution approach, the authors need to complement the paper by accordingly either advancing the feasible solutions to alleviate sensing errors or analysing the effect of sensing errors on the suggested solution approach.

%\bibliographystyle{IEEEtran}
\bibliography{../backmatter/myrefs}
\bibliographystyle{plain}
\end{document}

### 2017-09-16 journal-draft/ettdoc.tex
minor changes on proof B

@@
 Here, by \textit{step} we mean Algorithm~\ref{clustering:theorem} is executed by a secondary user for one time.
-Note that the minimum number of steps is 1, \eg when a cluster head is elected and all the other nodes are within its neighborhood.
+In one special scenario, \eg when a cluster head is elected and all the other nodes are within its neighborhood, the number of steps is 1.
 The Proof on the upper bound of the steps is given in Appendix~\ref{proof_clustering:theorem}.
@@
 For the sake of contradiction, let us assume there exist a secondary user $\alpha$ which is not included into any cluster.
-Then there is at least one node $\beta\in \text{Nb}(\alpha)$ such that $d_{\alpha} > d_{\beta}$ (otherwise $\alpha$ becomes cluster head). 
+Then there exists a node $\beta\in \text{Nb}(\alpha)$ such that $d_{\alpha} > d_{\beta}$ (otherwise $\alpha$ becomes cluster head). 
 In this case, according to Algorithm~\ref{alg0}, $\beta$ is not included in any clusters, because otherwise $d_{\beta} = M$, a large positive integer, which contradicts to $d_{\alpha} > d_{\beta}$.
@@
 If $\beta$ becomes cluster head, node $\alpha$ is included, the assumption is not true.
-If $\beta$ is not a cluster head, then $\beta$ is not in any cluster, we can repeat the previous analysis made on node $\alpha$, and deduce that node $\beta$ has at least one neighboring node $\gamma$ with $d_{\gamma} < d_{\beta}$.
+If $\beta$ is not a cluster head, then $\beta$ is not in any cluster, we can repeat the previous analysis made on node $\alpha$, and deduce that node $\beta$ has a neighboring node $\gamma$ with $d_{\gamma} < d_{\beta}$.
 % (COMMENT: $\beta$ not being a cluster head and $\beta$ not belonging to any cluster is not the same statement!!! ANSWER(Di): I add some more words)

### 2017-09-17 journal-draft/response_to_editors.tex
add lemmas in ROSS phase I

@@
 A further clarification is needed.
-    We give the definition of 'step' in the revised version.
-    Immediately below the theorem 4.1, "Here, by step we mean Algorithm 4.1 is executed by a secondary user for one time."
+    We agree that 'step' is not well defined.
+	In the revised version, we use 'time' to measure the length of phase I.
+	Besides, we propose the theorem after three new lemmas.
+
 	7)  In 4.1.3, parameter t depends on density of the network. Please clarify what is the impact of selecting value of t in system design, such as selecting t to be higher than 1.3.
+	$\delta$ is the desired cluster size and $t\delta$ is the cluster size
 

### 2017-09-17 journal-draft/ettdoc.tex
add lemmas in ROSS phase I

@@
 %all secondary users' individual connectivity degrees are greater than zero, then every secondary user will eventually be either integrated into a certain cluster, or becomes a cluster head.
-We have the following theorem to show that every secondary user will eventually be either integrated into a certain cluster or becomes a cluster head.
+We have the following lemma to show that every secondary user will eventually be either integrated into a certain cluster or becomes a cluster head.
+
+\begin{lemma}
+\label{clustering:lemma1}
+Given a CRN where any secondary user is able to communicate with any other secondary user through the other nodes, then after the phase of cluster head selection and initial cluster formation, every secondary user either becomes cluster head, or gets included into at least one cluster.
+\end{lemma}
+
+%Here, by \textit{step} we mean Algorithm~\ref{clustering:theorem} is executed by a secondary user for one time.
+%In one special scenario, \eg when a cluster head is elected and all the other nodes are within its neighborhood, the number of steps is 1.
+The Proof is given in Appendix~\ref{proof_clustering:lemma1}.
+%The proof also illustrates the maximal time needed to conduct Algorithm~\ref{clustering:theorem}. 
+%Consider an extreme scenario, where all the secondary nodes sequentially execute Algorithm~\ref{alg0}, \ie they constitute a chain as discussed in the example in the proof.
+%
+%Assuming there is a token in the CRN, one node is allowed to execute Algorithm~\ref{alg0} only when it holds the token, and it then transfers the token to the neighboring node on the chain.
+%If one step can be finished within a certain time span $T$, then the total time needed for the network to conduct Algorithm~\ref{clustering:theorem} is $N*T$.
+%C1-6
+
+\begin{lemma}
+\label{clustering:lemma2}
+When a secondary user becomes cluster head, it will not become cluster member again.
+\end{lemma}
+\begin{proof}
+A secondary node becomes cluster head when its \textit{Individual connectivity degree} is smaller than all its neighbors.
+Afterwards, the \textit{Individual connectivity degree} becomes $M$ and has no means to decrease, thus the cluster head will remain to be cluster head.
+\end{proof}
+
+%According to Theorem~\ref{clustering:theorem}, Phase I completes within a reasonable amount of time.
+%
+%This judgement is conducted periodically, and phase I ends after every node ascertains it is cluster head or not.
+
+\begin{lemma}
+\label{clustering:lemma3}
+In the process of cluster head selection and initial cluster formation, the maximum number of times that a secondary node becomes cluster head is $N$.
+\end{lemma}
+This lemma can be easily gotten from~\ref{clustering:lemma2} considering the $N$ is the number of all the secondary users in the CRN.
+Based on these Lemmas, we can easily obtain Theorem~\ref{clustering:lemma1},
 \begin{theorem}
 \label{clustering:theorem}
-Given a CRN, it takes at most $N$ steps before every secondary user either becomes cluster head, or gets included into at least one cluster.
+Assuming the time for a secondary user to update the information about cluster heads in its neighborhood is $T$, then it takes at most $N*T $ time to finish the process of cluster head selection and initial cluster formation.
 \end{theorem}
-Here, by \textit{step} we mean Algorithm~\ref{clustering:theorem} is executed by a secondary user for one time.
-In one special scenario, \eg when a cluster head is elected and all the other nodes are within its neighborhood, the number of steps is 1.
-The Proof on the upper bound of the steps is given in Appendix~\ref{proof_clustering:theorem}.
-%The proof also illustrates the maximal time needed to conduct Algorithm~\ref{clustering:theorem}. 
-Consider an extreme scenario, where all the secondary nodes sequentially execute Algorithm~\ref{alg0}, \ie they constitute a chain as discussed in the example in the proof.
-%
-Assuming there is a token in the CRN, one node is allowed to execute Algorithm~\ref{alg0} only when it holds the token, and it then transfers the token to the neighboring node on the chain.
-If one step can be finished within a certain time span $T$, then the total time needed for the network to conduct Algorithm~\ref{clustering:theorem} is $N*T$.
-%C1-6
+Phase I ends when no more secondary users becoming cluster head.
+based on~\ref{clustering:lemma1} and~\ref{clustering:lemma3}, the theorem is proved.
+
 As Algorithm~\ref{alg0} can be executed concurrently by different secondary users, the needed time can be considerably reduced.
-%According to Theorem~\ref{clustering:theorem}, Phase I completes within a reasonable amount of time.
-%
-%This judgement is conducted periodically, and phase I ends after every node ascertains it is cluster head or not.
 If we apply Algorithm~\ref{alg0} to the example shown in Figure~\ref{fig1}, the outcome is shown in Figure~\ref{fig2}.
@@
 \begin{proof}
-\label{proof_clustering:theorem}
+\label{proof_clustering:lemma1}
 %Note that the formed cluster can be a singleton cluster, \ie cluster size is 1.
@@
 So far, when there is no cluster head identified, the unclustered nodes, \ie $\alpha$, $\beta$ form a linked list, where their connectivity degrees monotonically decrease.
-But this list will not continue to grow, because the minimum individual connectivity degree is zero, and the length of this list is upper bounded by the total number of nodes in the CRN.
+But this list will not continue growing, because the minimum individual connectivity degree is zero, and the length of this list is upper bounded by the total number of nodes in the CRN.
 An example of the formed node series is shown as Figure~\ref{lemma1}.
@@
 
-If we see a secondary user \textit{becoming a cluster head}, or \textit{becoming a cluster member} as one step, as the length of the list of secondary users is not larger than $N$, there are $N$ steps for this scenario to form the initial clusters.
+%If we see a secondary user \textit{becoming a cluster head}, or \textit{becoming a cluster member} as one step, as the length of the list of secondary users is not larger than $N$, there are $N$ steps for this scenario to form the initial clusters.
 

### 2017-09-17 journal-draft/response_to_editors.tex
have answered all the questions from the reviewers, modified the paper

--- 2017-09-16 journal-draft/response_to_editors.tex
@@
 \author{Di Li}
+\usepackage{color}
+
 \title{Response to editors}
@@
 We thank all the reviewers and editors for their feedback and suggestions.
-In the following we will address the questions and comments from the viewers.
+In the following we will address the each questions and comment from the viewers.
 
-Reviewer 1:
+\section{Reviewer 1:}
 
- 1)  First of all, clustering technique is not new and it is one of the well-researched areas in ad hoc network, cognitive radio, HetNet etc.
+\begin{itemize}
+
+\item \textcolor{blue}{  First of all, clustering technique is not new and it is one of the well-researched areas in ad hoc network, cognitive radio, HetNet etc.
 The article does not review the latest publications in this area.
 The references are not adequate due to the fact that no recent works have been investigated.
-Therefore, it makes it insufficient (or unsatisfactory) work in present context.
-A lot of works on clustering in ad hoc networks or sensor networks, which address routing, power consumption and communication quality.
-Compared with the wireless networks where spectrum availability is not opportunistic, the clustering in CRN facilitated the better usage of the available spectrum, and meanwhile the conduction of clustering is restricted by the spectrum availability.
+Therefore, it makes it insufficient (or unsatisfactory) work in present context.}
+
+\textbf{Answer:} As mentioned in the introduction section, a lot of works on clustering in ad hoc networks or sensor networks, which address routing, power consumption and communication quality.
+Compared with the wireless networks where spectrum availability is not opportunistic, the clustering in CRN facilitated the better usage of the available spectrum, meanwhile clustering itself is restricted by the spectrum availability.
 This fact makes clustering in CRN a difficult topic.
-Up to now, only \cite{LIU_TMC11_2, Li11_ROSS, mansoor_15_cluster_robust} and \cite{Mansoor2015} xxxxxxxxxxxxxxxx
+Up to now, only \cite{LIU_TMC11_2, Li11_ROSS, mansoor_15_cluster_robust} have tried to address the robustness issue of the formed clusters in CRN.
+After searching, we find a paper \cite{Mansoor2015} from 2015 IEEE Crowncom, which proposes a clustering algorithm which aims to speed up the process of re-clustering in case a cluster doesn't uphold in from of active primary users.
+But this work doesn't consider to improve the ability of the formed clusters to maintain, and the messaging cost which is involved in this process is not considered.
+We have included this citation in the related work part.
 
-    2)  The presentation of the paper is not good enough and needs a lot of improvements.
+\item \textcolor{blue}{  The presentation of the paper is not good enough and needs a lot of improvements.
 For instance, ROSS scheme has been mentioned in the paper in many places, but it is not properly defined (though reference has been given).
 I had to check the reference paper to know it is Robust Spectrum Sharing.
-The journal article must be self-contained.
-    This explanation of the scheme name is added in the introduction section.
+The journal article must be self-contained.}
 
-    3)  The paragraphs are too long in the Introduction.
+    \textbf{Answer:} This explanation of the scheme name is added in the introduction section.
+    The paper has been thoroughly proofread.
+
+\item \textcolor{blue}{  The paragraphs are too long in the Introduction.
 As a result, the paragraph contains too many information which are not related each other.
-This makes readers difficult to understand the concept.
-    xxxxxxx
+This makes readers difficult to understand the concept.}
 
-    4)   In page 3, it is mentioned that “A cluster can be formed only by the cluster head”.
+    \textbf{Answer:} Now the section of introduction consists of 4 paragraphs: introduction of CRN with mentioning of spectrum sensing $\rightarrow$ clustering in CRN $\rightarrow$ robustness of clustering $\rightarrow$ the role of cluster size in robust clustering in CRN.
+    The related works are put in a separate section.
+
+\item \textcolor{blue}{   In page 3, it is mentioned that “A cluster can be formed only by the cluster head”.
 As a matter of fact, the cluster head formation is itself a very challenging task in any cluster based approach.
@@
 I can see the description is in the few pages later but some information must be provided where it is described first time.
-By the way, the CH formation technique described in 4.1.1 is not novel.
-	    As the reviewer has pointed out, this statement is somehow misleading. 
-	    We put this line in the paper and wanted to say that after the clusters are decided, it is the cluster head's job to form a cluster out of the neighboring nodes.
+By the way, the CH formation technique described in 4.1.1 is not novel.}
+
+\textbf{Answer:} We agree with the reviewer that this statement is not well explained.
+	    Initially, we put this line in the paper and wanted to say that after the clusters are decided, it is the cluster head's job to form a cluster out of the neighboring nodes.
 In the revised version, we have changed the statement as "Our scheme enables the cluster heads are selected in a distributed manner, and a cluster can only be formed only by these selected cluster head.
@@
 
-    5)  In my understanding, the values of connectivity degree in Fig.
+\item \textcolor{blue}{  In my understanding, the values of connectivity degree in Fig.
 1 came from the assumption of $K_A$, $K_B$ …..$K_H$.
@@
 1 Caption.
-It would be good to mention how to obtain such information in ad hoc cognitive radio network?
-    As stated in the system model, both primary and second users are able to work on the same set of channels. 
+It would be good to mention how to obtain such information in ad hoc cognitive radio network?}
+
+\textbf{Answer:} As stated in the system model, both primary and second users work on the same set of channels, i.e., the former use the channel whenever it is needed, and the later can only use it opportunistically.
     We assume the primary users are randomly located and work on each channel with a certain probability.
@@
 
-    6)  Theorem 4.1 is too obvious, authors need to discuss in terms of convergence and complexity of the proposed method.
+\item \textcolor{blue}{  Theorem 4.1 is too obvious, authors need to discuss in terms of convergence and complexity of the proposed method.
 In fact, Theorem 4.1 and description immediately are so confusing and misleading.
 If step is defined as executing Algorithm 4.1 for one time which again takes at most N steps.
-A further clarification is needed.
-    We give the definition of 'step' in the revised version.
-    Immediately below the theorem 4.1, "Here, by step we mean Algorithm 4.1 is executed by a secondary user for one time."
-    7)  In 4.1.3, parameter t depends on density of the network. Please clarify what is the impact of selecting value of t in system design, such as selecting t to be higher than 1.3.
+A further clarification is needed.}
 
-    8)  In page 7, what does “the toy network in Figure 2” mean? I hope it’s a typo. Otherwise, the Sections 4.2.1, 4.2.2, 4.2.3 are nicely written.
+\textbf{Answer:} We agree that 'step' is not fully explained.
+	We have represented this theorem in the revised version, which will be made after three lemmas.
+	Besides, we use 'time' in stead of 'step' to quantify the process of the phase of cluster head selection and initial cluster formation.
 
-    9)  In simulation, have authors considered the spectrum sensing parameters on each secondary nodes?
+\item \textcolor{blue}{  In 4.1.3, parameter t depends on density of the network.
+Please clarify what is the impact of selecting value of t in system design, such as selecting t to be higher than 1.3.}
+
+\textbf{Answer:}	$t$ is between 1 and the ratio between the average size of the every secondary user's neighborhood and the desired size.
+	When $t$ is smaller, for example, $t=1$, the formed cluster in the phase I will be $\delta$.
+	Then when the nodes which belong to multiple clusters decide on their clusters, they will be excluded from the other cluster whose size will be smaller than $\delta$.
+	A large $t$, for example, the $t$ which makes $t\cdot\delta$ the size of neighborhood, then the mechanism of adjusting the cluster size will not work any more.
+
+\item \textcolor{blue}{  In page 7, what does “the toy network in Figure 2” mean? I hope it’s a typo. Otherwise, the Sections 4.2.1, 4.2.2, 4.2.3 are nicely written.}
+
+\textbf{Answer:} It is a typo and we have changed the sentence to "Now we apply both ROSS-DGA and ROSS-DFA to the network in Figure 2 which has been applied the phase I of ROSS."
+
+\item \textcolor{blue}{  In simulation, have authors considered the spectrum sensing parameters on each secondary nodes?
 Are the channels randomly made available to users?
 Please clarify.
-What value of A is chosen in simulation?
+What value of A is chosen in simulation?}
 
-    10) It is mentioned in the article that “The number of licensed channels is 10, each PU is operating on each channel with probability of 50\%”.
+\textbf{Answer:} In the simulation, CRs and PUs are deployed on a two-dimensional Euclidean plane. 
+Each PU is operating on each channel with probability of 50\%.
+Then the channel availability on the secondary users are decided as follows.
+As to a secondary user, if none of the primary users whose transmission range include the secondary user works on a channel, the channel will be available for that secondary user.
+
+ 'A' represents the length the simulation square.
+    And the radius of transmission of both primary and secondary users is a fraction of A.
+    By doing this, we separate our scheme with concrete physical layer communication standards, and A can be given a concrete value after the physical layer protocol is decided.
+
+\item \textcolor{blue}{ It is mentioned in the article that “The number of licensed channels is 10, each PU is operating on each channel with probability of 50\%”.
 It means there will be only 5 channels available (maximum) to each secondary users.
@@
 It means there is chance of interference in two nodes.
-Please clarify those conflicts.
+Please clarify those conflicts.}
 
-    11) Further comparison is needed against the previous works to justify the robustness of the proposed method.
+\textbf{Answer:} 
+The simulation consists of two parts, the comparison between the centralized and distributed schemes, and the comparison between the distributed schemes.
+Some parameters are identical for both parts, (stated in the second paragraph in Section 6) but there are some parameters are different (as stated in the beginning of Section 6.1 and 6.2 respectively).
+The difference lies in the scale of the CRN and the primary users, and the transmission ranges.
+The reason is that there doesn't exist efficient method to solve the centralized scheme, then we have to do simulation in a smaller network.
 
-Reviewer: 2
+The parameter setting questioned by the reviewer is for the simulation involving centralized schemes in Section 6.1.
+According to the description, here will be "only 5 channels available", not "to each secondary users", but to the nodes within the primary user's transmission range.
+    The transmission radius of primary user is A/3, which means some nodes are not affected by all the primary users.
+    Other than that, from the simulation we conclude that averagely 7.1 channels are available for each secondary user.
+
+\item \textcolor{blue}{ Further comparison is needed against the previous works to justify the robustness of the proposed method.}
+\textbf{Answer:} 	We add the definition of robustness in both the introduction section (3rd paragraph) and system model section (Section 3.1).
+The robustness is illustrated by the number of the unclustered CR nodes in the CRN, which is investigated both in Section 6.1 and 6.2.
+We have modified the analysis of the simulation result in Section 6.1.3 and 6.2.2.
+We have also added additional simulations about the effects of sensing errors on the distributed schemes in Section 6.2.4.
+
+\end{itemize}
+
+\section{Reviewer 2:}
 
@@
 In this paper, authors investigate the optimization algorithms for node clustering strategy in ad hoc based cognitive radio networks, where both the centralized solution and distributed solution are considered.
+\begin{itemize}
 
-In Section 2, that the definition of channel $k\in K$, i.e.
+\item \textcolor{blue}{ In Section 2, that the definition of channel $k\in K$, i.e.
 fading channel or noisy channel?
@@
 Does the value of k indicate the channel gain in either time or frequency domain?
-Does the channel invariant or variant (how fast) during the clustering for how long windows range?
+}
+
+\textbf{Answer:} As shown in the section of system model, "We adopt the unit disk model for both primary and CR users’ transmission."
+In the other words, we don't make any assumption on the concrete propagation model, but just assume the communication is successful when the two ends locate within each other's transmission range.
+We adopt this simple communication model so as to focus on secondary users' behavior to pursue the robust cluster structure.
+
+\item \textcolor{blue}{ Does the channel invariant or variant (how fast) during the clustering for how long windows range?
 In practical, the channel changes along with the transmission, the performance clustering may be impacted by the varying channel.
-What's the impact of insufficient channel knowledge?
+What's the impact of insufficient channel knowledge?}
 
-The work emphasize on the robustness of clustering.
+\textbf{Answer:} We assume the channel availability doesn't change during the clustering process.
+We agree with the reviewer that the channel variance affects the clustering by disrupting the communication.
+In reality, when the communication during the clustering process doesn't succeed when the channel quality deteriorates, the involved nodes can still make decisions based on the available knowledge of neighbors according to our algorithm.
+
+\item \textcolor{blue}{ The work emphasize on the robustness of clustering.
 However, such an evaluation in terms of robustness metric is not clear.
 The definition of robustness and relative discussions as well as the results should be further elaborated.
-The definition appears in Section 5 but my suggestion is to clearly state it in the system model and describe why choose this robustness metric according its relation with system design.
+The definition appears in Section 5 but my suggestion is to clearly state it in the system model and describe why choose this robustness metric according its relation with system design.}
+\textbf{Answer:} We take the advice and have done the modifications in two places.
+1. We mention the definition of robustness of clusters in the 3rd paragraph of the introduction section.
+2. In Section 3.1, the robustness is associated with the number of secondary users which are not included in any cluster.
+with these modifications, readers will understand the robustness metric in Section 6 (Section 5 in the previous version) easily.
 
-In Section 4, algorithm flow charts should be included.
+\item \textcolor{blue}{ In Section 4, algorithm flow charts should be included.}
+\textbf{Answer:} a flow chart as Figure 1 is added in Section 5 (which is Section 4 before this major revision)
 
-In Section 5, Fig. 10 is missing. Fig. 14-16 can be subfigures, similar to Fig. 17-19.
+\item \textcolor{blue}{ In Section 5, Fig. 10 is missing. Fig. 14-16 can be subfigures, similar to Fig. 17-19.}
+\textbf{Answer:} Figure 10 in Section 5 in the previous version is deleted.
 
-Reviewer: 3
+\end{itemize}
+
+\section{Reviewer 3:}
 
@@
 In this paper, the authors consider the robust clustering problem in the ad-hoc Cognitive Radio Networks (CRNs).
-The paper is well fromalized.
+The paper is well formalized.
 The research background and motivation are well described.
@@
 The experiment is well conducted with the thorough performance analysis and comparison on different experimental scenarios.
+\begin{itemize}
+\item \textcolor{blue}{ However, it seems that the authors totally miss a very important research issue, which is referred to as spectrum sensing errors in terms of overlook and misidentification on the channel availability by Secondary Users (SUs).
+Because the sensing errors may highly affect the effectiveness and performance of the suggested solution approach, the authors need to complement the paper by accordingly either advancing the feasible solutions to alleviate sensing errors or analyzing the effect of sensing errors on the suggested solution approach.}
 
-However, it seems that the authors totally miss a very important research issue, which is referred to as spectrum sensing errors in terms of overlook and misidentification on the channel availability by Secondary Users (SUs).
-Because the sensing errors may highly affect the effectiveness and performance of the suggested solution approach, the authors need to complement the paper by accordingly either advancing the feasible solutions to alleviate sensing errors or analysing the effect of sensing errors on the suggested solution approach.
+ \textbf{Answer:} we admit that the sensing error was not considered in the paper.
+We agree with the reviewer that this is an important issue, as sensing error is inevitable in practical applications.
+We have done additional simulations about the effects of sensing errors on the distributed schemes in Section 6.2.4.
+\end{itemize}
 

### 2017-09-17 journal-draft/ettdoc.tex
have answered all the questions from the reviewers, modified the paper

@@
 In other words, such clusters are more robust.
-In this paper, the robustness of the clusters is their ability to sustain with the existence of primary users.
+In this paper, the robustness of the clusters is their ability to uphold with the influence of the active primary users.
+The robust clustering enables more secondary users to reside in the resulted clusters when the available spectrum becomes scarcer.
 %
@@
 
+\section{Related Works and the Relation with This Paper}
 In the following we will give a brief review on the clustering in CRN, with emphasis on the theme of robust clustering.
@@
 
+The authors of~\cite{Mansoor2015} propose a clustering algorithm which aims to speed up the process of re-clustering in case a cluster doesn't uphold in from of active primary users.
+But this work doesn't consider to improve the ability of the formed clusters to maintain, and the messaging cost which is involved in this process is not considered.
 Robustness of clusters is discussed in~\cite{LIU_TMC11_2}. A distributed clustering scheme (denoted as SOC) which is designed to generate robust clusters against primary users is proposed.
@@
 %
-This paper extends~\cite{Li11_ROSS} in two dimensions.
+This paper fundamentally extends~\cite{Li11_ROSS} in two dimensions.
 First, this paper considers the correlation between the cluster robustness and the cluster size.
@@
 
-As introduced in Section~\ref{intro}, in order to be robust against primary users' activity, the formed clusters should have more CCs.
-On the other hand, the sizes of the formed clusters should be regulated, \ie they don't diverge from a given value greatly.
+As introduced in Section~\ref{intro}, robustness of the clusters is their ability to uphold with the influence of the active primary users, and it is represented by the number of secondary users which are not included in any cluster.
+To achieve better robustness, the formed clusters should have more CCs.
+Meanwhile, the sizes of the formed clusters should be regulated, \ie they don't diverge from a given value greatly.adv
 %Considering the above mentioned requirements, we present the definition of robust clustering problem as follows.
@@
 With ROSS, CR nodes form clusters based on the proximity of the available spectrum in their neighborhood after a series of interactions with their neighbors.
-ROSS consists of two cascaded phases: \textit{cluster formation} and \textit{membership clarification}.
+ROSS consists of two cascaded phases: \textit{cluster formation} and \textit{membership clarification} as shown in Figure~\ref{flowChartROSS}.
+\begin{figure}[ht!]
+  \centering
+\includegraphics[width=0.8\linewidth]{flow_chart.pdf}
+	\caption{Processors of ROSS}
+	\label{flowChartROSS}
+\end{figure}
+
 In the first phase, clusters are formed quickly and every CR user becomes either a cluster head or a cluster member, besides, cluster size control is implemented in this phase.
@@
 %
-The node which is identified as a cluster head broadcasts a message to notify its neighbors of this change, and its neighbors which are not cluster heads become cluster members
-\footnote{The reason for the occurrence of the cluster heads in the neighborhood of a new cluster head will be explained in Section~\ref{ross_p1_guarantee_ccc} and \ref{ross_p2_cluster_pruning})}.
+The node which is identified as a cluster head broadcasts a message to notify its neighbors of this change, then its neighbors which are not cluster heads become cluster members.
+\footnote{The reason for the occurrence of the cluster heads in the neighborhood of a new cluster head will be explained in Section~\ref{ross_p1_guarantee_ccc} and \ref{ross_p2_cluster_pruning})}
+Actually during the whole phase I, whenever a CR node is decided to be a cluster head thus accordingly forms a cluster, or its cluster's composition is changed, the cluster head will broadcast the new information about its cluster, which includes the sets of available channels on all its cluster members.
 The pseudo code for the cluster head decision and the initial cluster formation is shown in Algorithm~\ref{alg0} in the appendix.
@@
 A secondary node becomes cluster head when its \textit{Individual connectivity degree} is smaller than all its neighbors.
-Afterwards, the \textit{Individual connectivity degree} becomes $M$ and has no means to decrease, thus the cluster head will remain to be cluster head.
+Afterwards, the \textit{Individual connectivity degree} of its neighbors becomes $M$ and has no means to decrease, thus the cluster head will remain to be cluster head.
 \end{proof}
@@
 As to the nodes which are eliminated from the previous clusters, they restore their original individual connectivity degrees, then execute Algorithm~\ref{alg0} and become either cluster heads or get included into other clusters afterwards according to Theorem~\ref{clustering:theorem}.
-
-During Phase I, whenever a CR node is decided to be a cluster head and accordingly forms a cluster, or its cluster's composition is changed, the cluster head will broadcast the updated information about its cluster, which includes the sets of available channels on all its cluster members.
 
@@
 We set the threshold as $t\cdot \delta$, where $\delta$ is the desired cluster size.
-The constant parameter $t$ is usually larger than 1 and is dependent on the network density and CR nodes' transmission range, in particular, $t$ is between 1 and the ratio between the average number of neighbors and the desired size.
+The constant parameter $t$ is usually larger than 1 and is dependent on the network density and CR nodes' transmission range, in particular, $t$ is between 1 and the ratio between the average neighborhood size and the desired size.
 A smaller or bigger $t$ may lead to more clusters with smaller or larger size than $\delta$.
@@
 \subsection{Centralized Schemes vs. Decentralized Schemes}
-In this part of simulation, there are 10 primary users and 20 CR users dropped randomly (with uniform distribution) within a square area of size $A^{2}$, where $A$ is a positive value and we set the transmission ranges of primary and CR users to $A/3$.
+In this part of simulation, there are 10 primary users and 20 CR users dropped randomly (with uniform distribution) in a square area where side length is $A$.
+$A$ is a positive value and the transmission ranges of both primary and CR users are set to $A/3$.
 %C1-10, C1-9
@@
 \end{multicols}
-\caption{Comparison between the distributed and centralized clustering schemes ($N$ = 20)}
+%\caption{Comparison between the distributed and centralized clustering schemes ($N$ = 20)}
 \label{compare_dis_centralized}
@@
 
+If we use the number of secondary users residing in a cluster as the numerical representation of cluster robustness, then the variants of ROSS is from 5\%,  30\% and 230\% more robust than SOC with the number of newly added PR is 10, 40 and 80 respectively.
 The above observation shows that the average number of CCs of non-singleton clusters doesn't necessarily illustrate the robustness  of cluster, \ie SOC obtains the most CCs for the clusters which are meanwhile the most vulnerable.
@@
   \centering
-   \includegraphics[width=0.7\linewidth]{nClusters_largeNetwork.pdf}
+   \includegraphics[width=0.7\linewidth]{nClusters_largeNetwork_no_texture.pdf}
   \caption{The number of formed clusters.}

### 2017-09-17 journal-draft/ettdoc.tex
modify the simulation section

@@
 The average number of CCs of the non-singleton clusters is shown in Figure~\ref{ccc_large_scale}.
-SOC achieves the most CCs per non-singleton cluster, but the lead over the variants of ROSS decreases significantly when $N$ increases.
-%\ie when $N=300$, the number of CCs achieved by ROSS variants (except for ROSS-$\delta$-DFA) is almost the same as that resulted from SOC.
+Here we don't see the obvious difference between different schemes on the number of CCs.
+%SOC achieves the most CCs per non-singleton cluster, but the lead over the variants of ROSS decreases significantly when $N$ increases.
 %This means SOC out performs in terms of the average number of CCs per non-singleton cluster when network is sparse.
@@
 Figure~\ref{false_negative_ccc} shows the average number of CCs decrease slightly when the false negative rate increases.
-The size distribution of the ROSS-DGA, ROSS-$\delta$-DGA and SOC is shown in Figure~\ref{false_negative_ccc}.
+The size distribution of the ROSS-DGA, ROSS-$\delta$-DGA and SOC is shown in Figure~\ref{false_negative_CDF}.
 \begin{figure}[!h]
@@
 %As to the ROSS variants, the changes of the CDF curves are resulted from the increasing singleton clusters.
-The clusters from SOC are affected by the sensing errors greatly, \ie when false negative rate is 30\%, a lot more small clusters are generated than that when other false negative rates present.
-SOC demonstrates obvious divergence when certain rate of false negative exists, in contrary, ROSS variants are resilient to the false negative in terms of cluster sizes.
-The negotiation within the neighborhoods adopted by ROSS variants rules out the channel which is due to false negative successfully, which doesn't work well in SOC.
-
+The clusters from SOC are affected by the sensing errors the greatly.
+More unclustered nodes are generated, and a lot of small clusters are formed, \eg when false negative rate is 30\%.
+In contrary, ROSS variants are resilient in terms of unclusterd nodes and cluster sizes.
+We can conclude that through negotiation within the neighborhoods, ROSS variants successfully rules out the channel from false negative sensing.
 \begin{figure}[!h]

### 2017-09-17 journal-draft/ettdoc.tex
minor change

@@
 
-\subsubsection{Robustness of the formed clusters}
+\subsubsection{Robustness of the Formed Clusters}
 Here we see how vulnerable the clusters are when they are exposed to the increasing influence of the PUs.

### 2017-09-18 journal-draft/response_to_editors.tex
response.tex, diff.tex
response.tex

@@
 
-\begin{itemize}
+\begin{enumerate}
 
@@
 
-\textbf{Answer:} As mentioned in the introduction section, a lot of works on clustering in ad hoc networks or sensor networks, which address routing, power consumption and communication quality.
+\textbf{Answer:} As mentioned in the introduction section, there has been a lot of works on clustering in ad hoc networks or sensor networks.
+They address problems such like routing, power consumption and communication quality.
 Compared with the wireless networks where spectrum availability is not opportunistic, the clustering in CRN facilitated the better usage of the available spectrum, meanwhile clustering itself is restricted by the spectrum availability.
@@
 Up to now, only \cite{LIU_TMC11_2, Li11_ROSS, mansoor_15_cluster_robust} have tried to address the robustness issue of the formed clusters in CRN.
-After searching, we find a paper \cite{Mansoor2015} from 2015 IEEE Crowncom, which proposes a clustering algorithm which aims to speed up the process of re-clustering in case a cluster doesn't uphold in from of active primary users.
-But this work doesn't consider to improve the ability of the formed clusters to maintain, and the messaging cost which is involved in this process is not considered.
-We have included this citation in the related work part.
+After searching, we find one relavent paper \cite{Mansoor2015} from 2015 IEEE Crowncom.
+It proposes a clustering algorithm which aims to speed up the process of re-clustering in case a cluster doesn't uphold in from of active primary users.
+But this work doesn't consider to improve the ability of the formed clusters to maintain, besides, the messaging cost which is involved in this process is not considered.
+We have included this citation in the related work section in the revised version.
 
@@
 
-    \textbf{Answer:} This explanation of the scheme name is added in the introduction section.
+    \textbf{Answer:} The explanation of the scheme name is provided in the introduction section.
     The paper has been thoroughly proofread.
@@
 
-    \textbf{Answer:} Now the section of introduction consists of 4 paragraphs: introduction of CRN with mentioning of spectrum sensing $\rightarrow$ clustering in CRN $\rightarrow$ robustness of clustering $\rightarrow$ the role of cluster size in robust clustering in CRN.
-    The related works are put in a separate section.
+    \textbf{Answer:} We polish the paper and now the section of introduction consists of 4 paragraphs: introduction of CRN with mentioning of spectrum sensing $\rightarrow$ clustering in CRN $\rightarrow$ robustness of clustering $\rightarrow$ the role of cluster size in robust clustering in CRN.
+    The part of related works becomes one separate section.
 
@@
 \textbf{Answer:} We agree with the reviewer that this statement is not well explained.
-	    Initially, we put this line in the paper and wanted to say that after the clusters are decided, it is the cluster head's job to form a cluster out of the neighboring nodes.
+	    At first, we put this line in the first submission and wanted to say that after the clusters are decided, it is the cluster head's job to form a cluster out of the neighboring nodes.
 In the revised version, we have changed the statement as "Our scheme enables the cluster heads are selected in a distributed manner, and a cluster can only be formed only by these selected cluster head.
@@
 
-\textbf{Answer:} As stated in the system model, both primary and second users work on the same set of channels, i.e., the former use the channel whenever it is needed, and the later can only use it opportunistically.
+\textbf{Answer:} 
+The available channels on the nodes in Fig. 1 is randomly chosen, which is only used to explain our scheme.
+But in the simulation, the available channels on the secondary users are decided by the primary users.
+As stated in the system model, both primary and second users work on the same set of channels, i.e., the former use the channel whenever it is needed, and the later can only use it opportunistically.
     We assume the primary users are randomly located and work on each channel with a certain probability.
-    Then the secondary users can only use the channel which is not being used by the primary users, and the secondary user locates out of the transmission range of that primary user.
+    With spectrum sensing, the secondary users can detect the presence of active primary users, and thus obtain the available channels.
 
@@
 
-\textbf{Answer:} In the simulation, CRs and PUs are deployed on a two-dimensional Euclidean plane. 
-Each PU is operating on each channel with probability of 50\%.
-Then the channel availability on the secondary users are decided as follows.
-As to a secondary user, if none of the primary users whose transmission range include the secondary user works on a channel, the channel will be available for that secondary user.
+\textbf{Answer:} In the most part of the simulation, we assume the secondary users have accurate spectrum sensing ability.
+They are able to detect the active primary users in their vicinity.
+We can say the channel availability on the secondary users is decided by the primary users.
+As to a secondary user, if none of the primary users whose transmission range include the secondary user works on a channel, that channel will be available for that secondary user. 
+We also consider the existence of sensing error, in Section 6.2.4 in new version, we investigate the influence caused by false negative sensing error.
 
@@
     And the radius of transmission of both primary and secondary users is a fraction of A.
-    By doing this, we separate our scheme with concrete physical layer communication standards, and A can be given a concrete value after the physical layer protocol is decided.
+    By doing this, we separate our scheme with concrete physical layer communication technologies, and A can be given a concrete value in practice when the physical layer technology is decided.
 
@@
 The simulation consists of two parts, the comparison between the centralized and distributed schemes, and the comparison between the distributed schemes.
-Some parameters are identical for both parts, (stated in the second paragraph in Section 6) but there are some parameters are different (as stated in the beginning of Section 6.1 and 6.2 respectively).
-The difference lies in the scale of the CRN and the primary users, and the transmission ranges.
-The reason is that there doesn't exist efficient method to solve the centralized scheme, then we have to do simulation in a smaller network.
+Some parameters are identical for both parts (stated in the second paragraph in Section 6), but there are some parameters are different (as stated in the beginning of Section 6.1 and 6.2 respectively).
+The difference lies in the number of the CRN and the primary users, and the transmission ranges.
+The reason is because there doesn't exist an efficient method to solve the centralized scheme, thus we have to do simulation in a smaller network.
 
 The parameter setting questioned by the reviewer is for the simulation involving centralized schemes in Section 6.1.
-According to the description, here will be "only 5 channels available", not "to each secondary users", but to the nodes within the primary user's transmission range.
-    The transmission radius of primary user is A/3, which means some nodes are not affected by all the primary users.
-    Other than that, from the simulation we conclude that averagely 7.1 channels are available for each secondary user.
+%According to the description, here will be "only 5 channels available", not "to each secondary users", but to the nodes within the primary user's transmission range.
+    Please note that the transmission radius of primary user is A/3, which means some nodes are not affected by all the primary users.
+    Other than that, from the simulation we know averagely 7.1 channels are available for each secondary user.
 
@@
 
-\end{itemize}
+\end{enumerate}
 
@@
 In this paper, authors investigate the optimization algorithms for node clustering strategy in ad hoc based cognitive radio networks, where both the centralized solution and distributed solution are considered.
-\begin{itemize}
+\begin{enumerate}
 
@@
 \textbf{Answer:} As shown in the section of system model, "We adopt the unit disk model for both primary and CR users’ transmission."
-In the other words, we don't make any assumption on the concrete propagation model, but just assume the communication is successful when the two ends locate within each other's transmission range.
+In other words, we don't make any assumption on the concrete propagation model, but just assume the communication is successful when the two ends locate within each other's transmission range.
 We adopt this simple communication model so as to focus on secondary users' behavior to pursue the robust cluster structure.
@@
 We agree with the reviewer that the channel variance affects the clustering by disrupting the communication.
-In reality, when the communication during the clustering process doesn't succeed when the channel quality deteriorates, the involved nodes can still make decisions based on the available knowledge of neighbors according to our algorithm.
+In reality, if the communication during the clustering process doesn't succeed as the channel quality deteriorates, the involved nodes can still make decisions based on the available knowledge of neighbors according to our algorithm.
 
@@
 The definition appears in Section 5 but my suggestion is to clearly state it in the system model and describe why choose this robustness metric according its relation with system design.}
+
 \textbf{Answer:} We take the advice and have done the modifications in two places.
@@
 \item \textcolor{blue}{ In Section 4, algorithm flow charts should be included.}
+
 \textbf{Answer:} a flow chart as Figure 1 is added in Section 5 (which is Section 4 before this major revision)
@@
 \item \textcolor{blue}{ In Section 5, Fig. 10 is missing. Fig. 14-16 can be subfigures, similar to Fig. 17-19.}
-\textbf{Answer:} Figure 10 in Section 5 in the previous version is deleted.
 
-\end{itemize}
+\textbf{Answer:} Advice is taken and change is made. Please refer Fig 8 - 9.
+
+\end{enumerate}
 
@@
 The experiment is well conducted with the thorough performance analysis and comparison on different experimental scenarios.
-\begin{itemize}
+\begin{enumerate}
 \item \textcolor{blue}{ However, it seems that the authors totally miss a very important research issue, which is referred to as spectrum sensing errors in terms of overlook and misidentification on the channel availability by Secondary Users (SUs).
@@
 
- \textbf{Answer:} we admit that the sensing error was not considered in the paper.
+ \textbf{Answer:} It is true that the sensing error was not considered in the first submission.
 We agree with the reviewer that this is an important issue, as sensing error is inevitable in practical applications.
 We have done additional simulations about the effects of sensing errors on the distributed schemes in Section 6.2.4.
-\end{itemize}
+\end{enumerate}
 

### 2017-09-23 journal-draft/response_to_editors.tex
moving some text from section 2 to 1

@@
 \textbf{Answer:} As mentioned in the introduction section, there has been a lot of works on clustering in ad hoc networks or sensor networks.
-They address problems such like routing, power consumption and communication quality.
+They address problems such as routing, power consumption and communication quality.
 Compared with the wireless networks where spectrum availability is not opportunistic, the clustering in CRN facilitated the better usage of the available spectrum, meanwhile clustering itself is restricted by the spectrum availability.
@@
 Up to now, only \cite{LIU_TMC11_2, Li11_ROSS, mansoor_15_cluster_robust} have tried to address the robustness issue of the formed clusters in CRN.
-After searching, we find one relavent paper \cite{Mansoor2015} from 2015 IEEE Crowncom.
+After searching, we find one additional relevant paper \cite{Mansoor2015} from 2015 IEEE Crowncom.
 It proposes a clustering algorithm which aims to speed up the process of re-clustering in case a cluster doesn't uphold in from of active primary users.
-But this work doesn't consider to improve the ability of the formed clusters to maintain, besides, the messaging cost which is involved in this process is not considered.
+But this work doesn't consider to improve the ability of the formed clusters to be maintained, besides, the messaging cost which is involved in this process is not considered.
 We have included this citation in the related work section in the revised version.
+We will appreciate if the reviewer could provide more specific references that we have not mentioned yet.
 
@@
 
-    \textbf{Answer:} The explanation of the scheme name is provided in the introduction section.
-    The paper has been thoroughly proofread.
+    \textbf{Answer:} In the revised version, we explain the name ROSS in the fifth paragraph when we introduce our scheme.
+%    The paper has been thoroughly proofread.
 

### 2017-09-23 journal-draft/ettdoc.tex
moving some text from section 2 to 1

@@
 Cluster sizes also play a role in transmission power consumption, \ie cluster size affects the transmission power consumption when routing is conducted~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
-In this paper we will analyze the robust clustering problem and propose efficient solutions.
-Our schemes generate the clusters which demonstrate both the robustness against the increasing primary activity and the compliance with the desired cluster sizes.
-Hence our schemes provide the network designers with more freedom when the power consumption is involved in the design of network applications.
-%In this paper we will introduce a robust cluster structure for CRN, where the robustness means the ability of the clusters to sustain under the influence of the increasing activity of primary users, and the direct metric is the number of CCs in the clusters.
+
+In this paper robust clustering in CRN is analyzed and both centralized and distributed schemes are proposed.
+This paper is based on our previous work ROSS (Robust Spectrum Sharing)~\cite{Li11_ROSS}, but fundamental extensions are made in several aspects.
+This paper provides a comprehensive analysis of the robust clustering problem, analyze and investigate the influence of cluster size and the number of CCs on cluster robustness.
+We claim that the cluster robustness against the primary users is no longer indicated merely by the average number of CCs of clusters, but by the ability of the clusters to uphold when the primary users' activity becomes more active.
+The involment of cluster size enables us to solve the problem of clusters size devergence, which appears in~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
+These new extensions are made on the basis of ROSS and its light weight version, the latter involves less overheads thus is more suitable for the scenario where fast deployment is desired.
+Throughout this paper, we refer to the clustering schemes on the basis of ROSS as the \textit{variants of ROSS}.
+
+%Our schemes generate the clusters which demonstrate both the robustness against the increasing primary activity and the compliance with the desired cluster sizes.
+
+The rest of paper is organized as follows. 
+In section~\ref{related_work}, we will introduce the clustering techniques in CRN and those focusing on robustness.
+The relation between this paper and work~\cite{Li11_ROSS} is elaborated.
+She system model and the robust clustering problem formulation are presented in Section~\ref{sec:model}. 
+The centralized and distributed solutions are introduced in Section~\ref{centralized_solution} and~\ref{ross} respectively.
+%The clustering problem is given through analysis and a centralized scheme is proposed in section~\ref{centralized_scheme}.
+Extensive performance evaluation is given in Section~\ref{performance}.
+Our work is concluded in Section~\ref{conclusion}.
 
 \section{Related Works and the Relation with This Paper}
+\label{related_work}
 In the following we will give a brief review on the clustering in CRN, with emphasis on the theme of robust clustering.
@@
 %
-This paper fundamentally extends~\cite{Li11_ROSS} in two dimensions.
-First, this paper considers the correlation between the cluster robustness and the cluster size.
-As a result the cluster robustness is no longer indicated merely by the average number of CCs of clusters, but the ability of the CR nodes to get benefit from collective decision and of the clusters to sustain when the primary users' activity becomes more dynamic.
-Besides, this involment of cluster size enable us to solve the problem of clusters size devergence, which appears in~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
-Second, this paper provides a comprehensive analysis of the robust clustering problem, proposes both centralized and distributed solutions, and conducts extensive simulations. 
-%We stick to the motivation of forming robust clusters in CRN \ie let more CR users benefited from the cooperative decision making which is due to the clusters. 
-%We propose both centralized and distributed clustering schemes, which result in more CR users in the clusters composed with multiple CR users, not only when the clusters are just formed, but also afterwards when the primary users' activity changes.
-%Besides, both centralized and distributed schemes take the cluster size into consideration, and both can control the sizes of the formed clusters to certain extent.
-%In particular, the decentralized clustering approach ROSS (RObust Spectrum Sharing) is able to form clusters with desired sizes.
-%When compared with other distributed works, ROSS involves smaller signaling overhead and the generated clusters are significantly more robust against the primary users which appear after the clusters are formed.
-%thesis
-%and the generated clusters are more robust than the other clustering scheme which has claims on cluster robustness, \ie more secondary users residing in clusters against increasing influence from primary users.
-%
-%ROSS selects cluster head through coordination within its neighborhood, and then cluster membership is decided locally and its fast convergence is proved under game theoretic framework. 
-%For our scheme we can prove convergence in cluster formation phase and resolve ambiguities with respect to cluster membership in a game-theoretic setting. 
-The new extensions are made on basis of ROSS and its light weight version, the latter involves less overheads thus is more suitable for the scenario where fast deployment is desired.
-Throughout this paper, we refer to the clustering schemes on the basis of ROSS as the \textit{variants of ROSS}.
-
-The rest of paper is organized as follows. 
-We present the system model and the robust clustering problem in Section~\ref{sec:model}. 
-The centralized and distributed solutions are introduced in Section~\ref{centralized_solution} and~\ref{ross} respectively.
-%The clustering problem is given through analysis and a centralized scheme is proposed in section~\ref{centralized_scheme}.
-Some Extensive performance evaluation is presented in Section~\ref{performance}.
-Finally, we conclude our work and point out the direction for future research in Section~\ref{conclusion}.
 

### 2017-09-24 journal-draft/response_to_editors.tex
finish the modificaiton of response_to_reviewers

@@
 
-    \textbf{Answer:} We polish the paper and now the section of introduction consists of 4 paragraphs: introduction of CRN with mentioning of spectrum sensing $\rightarrow$ clustering in CRN $\rightarrow$ robustness of clustering $\rightarrow$ the role of cluster size in robust clustering in CRN.
+    \textbf{Answer:} We polished the paper according to the reviewers request. 
+    Now the introduction consists of 5 paragraphs: introduction of CRN with mentioning of spectrum sensing $\rightarrow$ clustering in CRN $\rightarrow$ robustness of clustering $\rightarrow$ the role of cluster size in robust clustering in CRN $\rightarrow$ introduction of our work.
     The part of related works becomes one separate section.
@@
 	    At first, we put this line in the first submission and wanted to say that after the clusters are decided, it is the cluster head's job to form a cluster out of the neighboring nodes.
-In the revised version, we have changed the statement as "Our scheme enables the cluster heads are selected in a distributed manner, and a cluster can only be formed only by these selected cluster head.
+In the revised version, we have changed the statement as "Our scheme enables that the cluster heads are selected in a distributed manner, and a cluster can only be formed only by these selected cluster head.
 "
@@
 As stated in the system model, both primary and second users work on the same set of channels, i.e., the former use the channel whenever it is needed, and the later can only use it opportunistically.
-    We assume the primary users are randomly located and work on each channel with a certain probability.
-    With spectrum sensing, the secondary users can detect the presence of active primary users, and thus obtain the available channels.
+%    We assume the primary users are randomly located and work on each channel with a certain probability.
+ %   With spectrum sensing, the secondary users can detect the presence of active primary users, and thus obtain the available channels.
+
+  In Section 5.1 in the revised version, we describe the generation of connectivity vectors, and reformulate the paragraph as follows,
+
+  "Individual connectivity degree $d_i$ and neighborhood connectivity degree $g_i$ together form the \textit{connectivity vector}.
+Connectivity vector is calculated by every secondary user after channel availability is obtained, and is then broadcasted.
+Figure 2 illustrates an CRN where every node's channel availability and connectivity vector is shown.
+This CRN is used as an example in the rest of this section to illustrate the proposed distributed schemes."
 
@@
 
-\textbf{Answer:} We agree that 'step' is not fully explained.
-	We have represented this theorem in the revised version, which will be made after three lemmas.
+\textbf{Answer:} We agree with the reviewer that 'step' is not fully explained.
+	We have represented this theorem thoroughly in Section 5.1.1 in the revised version.
 	Besides, we use 'time' in stead of 'step' to quantify the process of the phase of cluster head selection and initial cluster formation.
+
+	In the phase I of ROSS, the biggest concern is when will this process end.
+	Considering the fact that the secondary users keep receiving the latest information from neighbors, it is not easy to say whether a secondary user will change its role between cluster head and remember for multiple times or even infinitely.
+	Thus we represented the theorem in the revised version, which will be made after three lemmas.
+
+	Lemma 5.1 shows all the secondary users will be involved in the process, and decide on their roles decisively in the end.
+
+	Lemma 5.2 looks obvious or even trivial but it is critical to decide the time needed for phase I of ROSS to complete.
+	According to our regulation on the \textit{Individual connectivity degree} of a secondary user (it becomes a large positive integer $M$ after being included in a cluster, and being the same when it is included in a second cluster, besides it never decreases), the cluster head will remain to be cluster head once it becomes a cluster head.
+	This excludes the possibility for a secondary user to frequently or even infinitely switch between the two different roles in clusters.
+
+	Lemma 3 is the natural outcome from Lemma 5.2.
+
+	Theorem 5.1  is the takeaway which gives the decisive maximum time to complete this process.
 
@@
 
-\textbf{Answer:}	$t$ is between 1 and the ratio between the average size of the every secondary user's neighborhood and the desired size.
-	When $t$ is smaller, for example, $t=1$, the formed cluster in the phase I will be $\delta$.
-	Then when the nodes which belong to multiple clusters decide on their clusters, they will be excluded from the other cluster whose size will be smaller than $\delta$.
-	A large $t$, for example, the $t$ which makes $t\cdot\delta$ the size of neighborhood, then the mechanism of adjusting the cluster size will not work any more.
+\textbf{Answer:}	
+The impact of $t$ in the system design is elaborated in Section 5.1.3 in the revised version.
+The added text are as follows,
+
+"$t$ is between 1 and the ratio between the average size of each secondary user's neighborhood and the desired size.
+	When $t$ is smaller, for example $t=1$, the formed cluster in the phase I will be $\delta$.
+	For the cluster whose members are included by other clusters, the size of this cluster will be smaller than $\delta$ after the membership clarification phase.
+%	Then when the nodes which belong to multiple clusters decide on their clusters, their leave will some of they will be excluded from other cluster whose size will be smaller than $\delta$.
+	If $t$ is chosen large, for example, $t\cdot\delta$ equals to the size of neighborhood, then the mechanism of adjusting the cluster size will not work any more."
 
@@
 
-\textbf{Answer:} It is a typo and we have changed the sentence to "Now we apply both ROSS-DGA and ROSS-DFA to the network in Figure 2 which has been applied the phase I of ROSS."
+\textbf{Answer:} It is a typo and we have changed the sentence as "Now we apply both ROSS-DGA and ROSS-DFA to the network in Figure 2 after phase I of ROSS is applied."
 
@@
 
-\textbf{Answer:} In the most part of the simulation, we assume the secondary users have accurate spectrum sensing ability.
+\textbf{Answer:}
+
+The way the available channels are decided complies with the our system model in Section 3.
+We would like to answer the question here again.
+
+In the most part of the simulation, we assume the secondary users have the ability to sense the spectrum accurately.
 They are able to detect the active primary users in their vicinity.
 We can say the channel availability on the secondary users is decided by the primary users.
-As to a secondary user, if none of the primary users whose transmission range include the secondary user works on a channel, that channel will be available for that secondary user. 
-We also consider the existence of sensing error, in Section 6.2.4 in new version, we investigate the influence caused by false negative sensing error.
+As for a secondary user, if it is not in any primary user's transmission range, which are working a certain channel, then the channel will be available for that secondary user. 
+Based on a comment of reviewer 3, we also considered the existence of sensing error in Section 6.2.4 of the new version, where we investigate the influence caused by false negative sensing error.
 
- 'A' represents the length the simulation square.
-    And the radius of transmission of both primary and secondary users is a fraction of A.
-    By doing this, we separate our scheme with concrete physical layer communication technologies, and A can be given a concrete value in practice when the physical layer technology is decided.
+As mentioned in Section 6.1, 'A' represents the length of one side of the simulation square.
+    Note that the radius of transmission of both primary and secondary users is a fraction of A.
+    By doing this, we try to abstract from the influence of any given physical layer technology, and A can be given a concrete value in practice when the physical layer technology is decided.
+    We have added the motivation to use 'A' in Section 6.1 in the revised version.
 
@@
 The simulation consists of two parts, the comparison between the centralized and distributed schemes, and the comparison between the distributed schemes.
-Some parameters are identical for both parts (stated in the second paragraph in Section 6), but there are some parameters are different (as stated in the beginning of Section 6.1 and 6.2 respectively).
-The difference lies in the number of the CRN and the primary users, and the transmission ranges.
+Some parameters are identical for both parts (stated in the second paragraph in Section 6), but there are some parameters which are different (as stated in the beginning of Section 6.1 and 6.2 respectively).
+The difference lies in the number of secondary and primary users, and the transmission ranges in CRN.
 The reason is because there doesn't exist an efficient method to solve the centralized scheme, thus we have to do simulation in a smaller network.
@@
     Please note that the transmission radius of primary user is A/3, which means some nodes are not affected by all the primary users.
-    Other than that, from the simulation we know averagely 7.1 channels are available for each secondary user.
+    Other than that, from the simulation we know that on average 7.1 channels are available for each secondary user.
 
@@
 \textbf{Answer:} As shown in the section of system model, "We adopt the unit disk model for both primary and CR users’ transmission."
-In other words, we don't make any assumption on the concrete propagation model, but just assume the communication is successful when the two ends locate within each other's transmission range.
-We adopt this simple communication model so as to focus on secondary users' behavior to pursue the robust cluster structure.
+In other words, we don't make any assumption on the concrete propagation model, but just assume that nodes are generally in communication range if their physical distance is lower than some threshold value.
+One can argue that such a model resembles the impact of path loss and the average impact from shadowing and fading.
+We adopt this simple communication model in order to focus on secondary users' behavior to pursue the robust cluster structure.
 
@@
 We agree with the reviewer that the channel variance affects the clustering by disrupting the communication.
-In reality, if the communication during the clustering process doesn't succeed as the channel quality deteriorates, the involved nodes can still make decisions based on the available knowledge of neighbors according to our algorithm.
+In reality, if the communication during the clustering process doesn't succeed while the channel quality deteriorates, the involved nodes can still make decisions based on the available knowledge of neighbors which is already obtained.
+In this case, many smaller clusters or even singleton clusters may be generated.
+%
+In the other hand, the chosen model would fit a slowly varying scenario, where for instance most primary and secondary users are stationary.
+Thus, single messages might be lost, but statistically the proposed schemes could still determine a stable clustering (by retransmissions etc.).
 
@@
 
-\textbf{Answer:} We take the advice and have done the modifications in two places.
-1. We mention the definition of robustness of clusters in the 3rd paragraph of the introduction section.
-2. In Section 3.1, the robustness is associated with the number of secondary users which are not included in any cluster.
-with these modifications, readers will understand the robustness metric in Section 6 (Section 5 in the previous version) easily.
+\textbf{Answer:} We took the advice and have done the modifications in two places.
+\begin{enumerate}
+\item We mention the definition of robustness of clusters in the 3rd paragraph of the introduction section.
+\item In Section 3.1, the robustness is associated with the number of secondary users which are not included in any cluster.
+With these modifications, we hope that the readers will understand the robustness metric in Section 6 (Section 5 in the previous version) easily.
+\end{enumerate}
 
@@
 
-\textbf{Answer:} a flow chart as Figure 1 is added in Section 5 (which is Section 4 before this major revision)
+\textbf{Answer:} According to the comments of the reviewer, we added a flow chart as Figure 1 in Section 5 (which is Section 4 before this major revision)
 
@@
 
-\textbf{Answer:} Advice is taken and change is made. Please refer Fig 8 - 9.
+\textbf{Answer:} We took the advice and made changes accordingly. 
+Please refer Fig 8 - 9.
 

### 2017-09-24 journal-draft/ettdoc.tex
finish the modificaiton of response_to_reviewers

@@
 The availability of CCs within a cluster decides the existence of that cluster, \ie if no CCs are available then the corresponding cluster does not exist.
-As the activity of primary users is usually unknown to the secondary users, it is deemed as random as to secondary users.
+The activity of primary users is usually unknown to the secondary users thus deemed as random to secondary users.
 Consequently, a cluster which secures more CCs will anticipate a longer life expectancy. 
 In other words, such clusters are more robust.
-In this paper, the robustness of the clusters is their ability to uphold with the influence of the active primary users.
+In this paper, the robustness of the clusters is their ability to uphold with the influence of active primary users.
 The robust clustering enables more secondary users to reside in the resulted clusters when the available spectrum becomes scarcer.
@@
 Within in a cluster, both payload and control overheads can be transmitted on the CCs.
-%Out of the available CCs, there are always one or multiple channels which are used for the payload communication.
-When one or several cluster members can not access one certain CC on which primary some user activity is detected, the channel will be excluded from the set of CCs.
-In particular, if that channel is being used for payload communication, the communication pair will stop and resume the transmission on another available CC.
+When one or several cluster members can not access a certain CC on which primary user's activity is detected, the channel will be excluded from the set of CCs.
+In particular, if that channel is being used for payload communication, the communication pair will stop and resume transmission on another available CC.
 %As long as there is a CC available, the corresponding cluster can continue to exchange payload data.
@@
 This paper is based on our previous work ROSS (Robust Spectrum Sharing)~\cite{Li11_ROSS}, but fundamental extensions are made in several aspects.
-This paper provides a comprehensive analysis of the robust clustering problem, analyze and investigate the influence of cluster size and the number of CCs on cluster robustness.
-We claim that the cluster robustness against the primary users is no longer indicated merely by the average number of CCs of clusters, but by the ability of the clusters to uphold when the primary users' activity becomes more active.
-The involment of cluster size enables us to solve the problem of clusters size devergence, which appears in~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
-These new extensions are made on the basis of ROSS and its light weight version, the latter involves less overheads thus is more suitable for the scenario where fast deployment is desired.
+This paper gives a comprehensive analysis of robust clustering problem, analyze and investigate the influence of cluster size and the number of CCs on cluster robustness.
+We claim that the cluster robustness is no longer indicated merely by the average number of CCs of clusters, but by the ability of the clusters to uphold when the primary users' activity becomes more active.
+The involment of cluster size enables us to solve the size devergence problem in clusters, which appears in~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
+Based on ROSS, our proposed distributed schemes are still suitable for the scenario where fast deployment is desired.
 Throughout this paper, we refer to the clustering schemes on the basis of ROSS as the \textit{variants of ROSS}.
-
-%Our schemes generate the clusters which demonstrate both the robustness against the increasing primary activity and the compliance with the desired cluster sizes.
-
+%
+%
 The rest of paper is organized as follows. 
@@
 $d_i$ is the total number of the CCs between node $i$ and each of its neighbors.
-%It is an indicator of node $i$'s adhesion to the CRN.
 
@@
 Individual connectivity degree $d_i$ and neighborhood connectivity degree $g_i$ together form the \textit{connectivity vector}.
-Figure~\ref{fig1} illustrates an example CRN where every node's connectivity vector is shown.	
-In Figure~\ref{fig1}, some primary users are randomly deployed in the network, and they are free to choose one channel out of the set of licensed channels $\mathcal{K}$ to operate.
-As to the secondary users, the channels they are allowed to use are those which are not ruled out by the primary users in their vicinities. 
-The sets of the indices of the available channels sensed by each node are: $K_A=\{1,2,3,4,5,6,10\}, K_B=\{1,2,3,5,7\}, \\K_C=\{1,3,4,10\}, K_D=\{1,2,3,5\}, \\K_E=\{2,3,5,7\}, K_F=\{2,4,5,6,7\}, \\K_G=\{1,2,3,4,8\}, K_H=\{1,2,5,8\}$.
+Connectivity vector is calculated by every secondary user after channel availability is obtained, and is then broadcasted.
+Figure~\ref{fig1} illustrates an CRN where every node's channel availability and connectivity vector is shown.
+This CRN is used as an example in the rest of this section to illustrate the proposed distributed schemes.
+%In Figure~\ref{fig1}, some primary users are randomly deployed in the network, and they are free to choose one channel out of the set of licensed channels $\mathcal{K}$ to operate.
+%As to the secondary users, the channels they are allowed to use are those which are not ruled out by the primary users in their vicinities. 
+In the example the sets of the indices of the available channels sensed by each node are: $K_A=\{1,2,3,4,5,6,10\}, K_B=\{1,2,3,5,7\}, \\K_C=\{1,3,4,10\}, K_D=\{1,2,3,5\}, \\K_E=\{2,3,5,7\}, K_F=\{2,4,5,6,7\}, \\K_G=\{1,2,3,4,8\}, K_H=\{1,2,5,8\}$.
 %C1-5
@@
 The constant parameter $t$ is usually larger than 1 and is dependent on the network density and CR nodes' transmission range, in particular, $t$ is between 1 and the ratio between the average neighborhood size and the desired size.
-A smaller or bigger $t$ may lead to more clusters with smaller or larger size than $\delta$.
-Because of $t$, the threshold is larger than the desired size, then there will be some nodes choosing to affiliate with other clusters in the following phases.
+%A smaller or bigger $t$ may lead to more clusters with smaller or larger size than $\delta$.
+	When $t$ is smaller, \eg $t=1$, the formed cluster in the phase I will be $\delta$.
+	For the cluster whose members are included by other clusters, the size of this cluster will be smaller than $\delta$ after the membership clarification phase.
+	If $t$ is chosen large, \eg $t\cdot\delta$ equals to the size of neighborhood, the mechanism of adjusting the cluster size will not work any more.
+
+Because of $t$, the threshold to prune is larger than the desired size, then there will be some nodes choosing to affiliate with other clusters in the following phases.
 %C1-7
@@
 $A$ is a positive value and the transmission ranges of both primary and CR users are set to $A/3$.
+By doing this, we try to abstract from the influence of any given physical layer technology, and A can be given a concrete value in practice when the physical layer technology is decided.
 %C1-10, C1-9
@@
 
-\section{Proof of Theorem~\ref{clustering:theorem}}
+\section{Proof of Lemma~\ref{clustering:theorem}}
 \begin{proof}

### 2017-09-26 journal-draft/response_to_editors.tex
before final review

@@
 
-    \textbf{Answer:} In the revised version, we explain the name ROSS in the fifth paragraph when we introduce our scheme.
+    \textbf{Answer:} In the revised version, we explain the name ROSS in the fifth paragraph when we introduce our scheme for the first time.
 %    The paper has been thoroughly proofread.
@@
 	    At first, we put this line in the first submission and wanted to say that after the clusters are decided, it is the cluster head's job to form a cluster out of the neighboring nodes.
-In the revised version, we have changed the statement as "Our scheme enables that the cluster heads are selected in a distributed manner, and a cluster can only be formed only by these selected cluster head.
+In the revised version, we have changed the statement as "Our scheme enables that the cluster heads are selected in a distributed manner, and a cluster can only be formed only by these selected cluster heads.
 "
@@
 \item \textcolor{blue}{ Further comparison is needed against the previous works to justify the robustness of the proposed method.}
+
 \textbf{Answer:} 	We add the definition of robustness in both the introduction section (3rd paragraph) and system model section (Section 3.1).
@@
  \textbf{Answer:} It is true that the sensing error was not considered in the first submission.
-We agree with the reviewer that this is an important issue, as sensing error is inevitable in practical applications.
+We agree with the reviewer that this is an important issue, as sensing errors are inevitable in practical applications.
 We have done additional simulations about the effects of sensing errors on the distributed schemes in Section 6.2.4.
+With the false negative rate increases by from 0 to 50\%, the percentage of nodes in singleton clusters generated by the variants of ROSS is increased by from 0 to 10\%, as comparison, the percentage by SOC increases from 9\% to 25\%.
+Besides, the variance of sizes of the formed clusters by the variants of ROSS is much smaller than that by SOC.
 \end{enumerate}

### 2017-09-28 journal-draft/ettdoc.tex
before final review
modifed abstract

@@
 Cluster structure in cognitive radio networks facilitates cooperative spectrum sensing, routing and other functionalities.
-Unlicensed channels, which are available for a group of cognitive radio users, consolidate the group into a cluster and the number of the available unlicensed channels decides that cluster's robustness against the licensed users' influence.
-This paper analyses the problem of how to form robust clusters in a cognitive radio network so that more cognitive radio users can get the benefits from cluster structure when the primary users' operations becomes more intense.
+Unlicensed channels, which are temporally available for a group of cognitive radio users in one area, consolidate the group into a cluster.
+More available unlicensed channels in a cluster make the cluster more likely to uphold against the licensed users' influence than only one available channel, which make that cluster to be more robust.
+This paper analyses the problem of how to form robust clusters in a cognitive radio network so that more cognitive radio users can still be benefited from cluster structure when the primary users' operations becomes more intense.
 %In the process of forming clusters, every secondary user decides with whom to form a cluster, or which cluster to join.
@@
 Through simulation, the distributed schemes demonstrate similar performance with the centralized scheme in terms of cluster robustness, signaling overhead and cluster sizes, and outperform the comparison distributed scheme on all metrics.
+Besides, spectrum sensing errors affect the performance of the variants of ROSS much less than SOC.
 

### 2017-09-28 journal-draft/ettdoc.tex
modifed introduction

@@
 
-In this paper robust clustering in CRN is analyzed and both centralized and distributed schemes are proposed.
-This paper is based on our previous work ROSS (Robust Spectrum Sharing)~\cite{Li11_ROSS}, but fundamental extensions are made in several aspects.
-This paper gives a comprehensive analysis of robust clustering problem, analyze and investigate the influence of cluster size and the number of CCs on cluster robustness.
-We claim that the cluster robustness is no longer indicated merely by the average number of CCs of clusters, but by the ability of the clusters to uphold when the primary users' activity becomes more active.
-The involment of cluster size enables us to solve the size devergence problem in clusters, which appears in~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
-Based on ROSS, our proposed distributed schemes are still suitable for the scenario where fast deployment is desired.
-Throughout this paper, we refer to the clustering schemes on the basis of ROSS as the \textit{variants of ROSS}.
+In this paper robust clustering in CRN is analyzed as a mathematical problem and proved to be NP-hard, then both centralized and distributed schemes are proposed.
+We rethink the metric used to measure the cluster robustness in the previous works~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}, and we claim cluster robustness can not be indicated merely by the average number of CCs of clusters, but by the ability of the clusters to uphold when the primary users' activity becomes more active.
+In this paper, we identify the robustness by the number of unclustered CR nodes.
+We also consider the necessity of cluster size control and its influence on cluster robustness.
+The propsoed distributed schemes extend our previous work ROSS (Robust Spectrum Sharing)~\cite{Li11_ROSS} by involving cluster size control.
+Our distributed schemes solve the size devergence problem in clusters as appears in~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
+Besides, our proposed distributed schemes are still suitable for the scenario where fast deployment is desired.
+Throughout this paper, we call the proposed distributed schemes the \textit{variants of ROSS}.
+
 %

### 2017-09-28 journal-draft/ettdoc.tex
modifed introduction
modifed related work
modifed Sec 4
polish the sec 5

@@
 
-\section{Related Works and the Relation with This Paper}
+\section{Related Work}
 \label{related_work}
@@
 As introduced in Section~\ref{intro}, robustness of the clusters is their ability to uphold with the influence of the active primary users, and it is represented by the number of secondary users which are not included in any cluster.
-To achieve better robustness, the formed clusters should have more CCs.
+To achieve better robustness, we form the clusters so that they have more CCs.
 Meanwhile, the sizes of the formed clusters should be regulated, \ie they don't diverge from a given value greatly.adv
@@
 
-\section{Distributed Clustering Algorithm: ROSS}
+\section{Distributed Clustering Algorithm: Variants of ROSS}
 \label{ross}
 
-In this section we introduce the distributed clustering scheme ROSS.
-With ROSS, CR nodes form clusters based on the proximity of the available spectrum in their neighborhood after a series of interactions with their neighbors.
-ROSS consists of two cascaded phases: \textit{cluster formation} and \textit{membership clarification} as shown in Figure~\ref{flowChartROSS}.
+In this section we introduce our distributed clustering schemes.
+With the variants of ROSS, CR nodes form clusters based on the proximity of the available spectrum in their neighborhood after a series of interactions with their neighbors.
+The variants of ROSS consist of two cascaded phases: \textit{cluster formation} and \textit{membership clarification} as shown in Figure~\ref{flowChartROSS}.
 \begin{figure}[ht!]
@@
 
-In the first phase, clusters are formed quickly and every CR user becomes either a cluster head or a cluster member, besides, cluster size control is implemented in this phase.
+In the first phase, clusters are formed quickly and every CR user becomes either cluster head or cluster member, besides, cluster size control is implemented in this phase.
 In the second phase, non-overlapping clusters are formed in a way that the CCs of relevant clusters are mostly increased.
@@
 \end{itemize}
-Individual connectivity degree $d_i$ and neighborhood connectivity degree $g_i$ together form the \textit{connectivity vector}.
+Individual connectivity degree $d_i$ and neighborhood connectivity degree $g_i$ together form the \textit{connectivity vector} $(d_i, g_i)$.
 Connectivity vector is calculated by every secondary user after channel availability is obtained, and is then broadcasted.
@@
 \subsubsection{Determining Cluster Heads and Forming Clusters}
-The procedure of determining the cluster heads is as follows.
+The procedure of determining cluster heads is as follows.
 Each CR node decides whether it is a cluster head by comparing its connectivity vector with its neighbors.
 When CR node $i$ has lower individual connectivity degree than all of its neighbors except for those which have already identified to be cluster heads, node $i$ becomes a cluster head.
-If there is another CR node $j$ in its neighborhood, which has the same individual connectivity degree as $i$, \ie $d_j = d_i$ and $d_j < d_{k}, \forall k\in \text{Nb}(j)\setminus \{\Lambda\cup i\}$ where $\Lambda$ denotes the cluster heads, then the node between $i$ and $j$, which has higher neighborhood connectivity degree will become the cluster head.
+If there is another CR node $j$ in its neighborhood, which has the same individual connectivity degree as $i$, \ie $d_j = d_i$ and $d_j < d_{k}, \forall k\in \text{Nb}(j)\setminus \{\Lambda\cup i\}$ where $\Lambda$ denotes cluster heads, then the node with higher neighborhood connectivity degree will become cluster head.
 If $g_i = g_j$ as well, the node ID is used to break the tie, \ie the one with smaller node ID becomes the cluster head.
@@
 \footnote{The reason for the occurrence of the cluster heads in the neighborhood of a new cluster head will be explained in Section~\ref{ross_p1_guarantee_ccc} and \ref{ross_p2_cluster_pruning})}
-Actually during the whole phase I, whenever a CR node is decided to be a cluster head thus accordingly forms a cluster, or its cluster's composition is changed, the cluster head will broadcast the new information about its cluster, which includes the sets of available channels on all its cluster members.
-The pseudo code for the cluster head decision and the initial cluster formation is shown in Algorithm~\ref{alg0} in the appendix.
+Actually during the whole phase I, whenever a CR node is decided to be a cluster head thus accordingly forms a cluster, or its cluster's composition is changed, the cluster head broadcasts the new information about its cluster, which includes the sets of available channels on all its cluster members.
+The pseudo code for the cluster head decision and the initial cluster formation is shown in Algorithm~\ref{alg0} in appendix.
 
@@
 
-As Algorithm~\ref{alg0} can be executed concurrently by different secondary users, the needed time can be considerably reduced.
+As Algorithm~\ref{alg0} is executed concurrently by different secondary users, the needed time can be considerably reduced.
 If we apply Algorithm~\ref{alg0} to the example shown in Figure~\ref{fig1}, the outcome is shown in Figure~\ref{fig2}.
@@
 The pseudo code for this procedure is shown in Algorithm~\ref{alg_size_control_available_CCC}.
-As to the nodes which are eliminated from the previous clusters, they restore their original individual connectivity degrees, then execute Algorithm~\ref{alg0} and become either cluster heads or get included into other clusters afterwards according to Theorem~\ref{clustering:theorem}.
+As for the nodes which are eliminated from a cluster, they restore their original individual connectivity degrees, then execute Algorithm~\ref{alg0} and become either cluster heads or get included into other clusters afterwards according to Theorem~\ref{clustering:theorem}.
 

### 2017-09-28 journal-draft/ettdoc.tex
move the proofs to the end of section 5.1
polish conclusion

@@
 %all secondary users' individual connectivity degrees are greater than zero, then every secondary user will eventually be either integrated into a certain cluster, or becomes a cluster head.
-We have the following lemma to show that every secondary user will eventually be either integrated into a certain cluster or becomes a cluster head.
-
-\begin{lemma}
-\label{clustering:lemma1}
-Given a CRN where any secondary user is able to communicate with any other secondary user through the other nodes, then after the phase of cluster head selection and initial cluster formation, every secondary user either becomes cluster head, or gets included into at least one cluster.
-\end{lemma}
-
-%Here, by \textit{step} we mean Algorithm~\ref{clustering:theorem} is executed by a secondary user for one time.
-%In one special scenario, \eg when a cluster head is elected and all the other nodes are within its neighborhood, the number of steps is 1.
-The Proof is given in Appendix~\ref{proof_clustering:lemma1}.
-%The proof also illustrates the maximal time needed to conduct Algorithm~\ref{clustering:theorem}. 
-%Consider an extreme scenario, where all the secondary nodes sequentially execute Algorithm~\ref{alg0}, \ie they constitute a chain as discussed in the example in the proof.
-%
-%Assuming there is a token in the CRN, one node is allowed to execute Algorithm~\ref{alg0} only when it holds the token, and it then transfers the token to the neighboring node on the chain.
-%If one step can be finished within a certain time span $T$, then the total time needed for the network to conduct Algorithm~\ref{clustering:theorem} is $N*T$.
-%C1-6
-
-\begin{lemma}
-\label{clustering:lemma2}
-When a secondary user becomes cluster head, it will not become cluster member again.
-\end{lemma}
-\begin{proof}
-A secondary node becomes cluster head when its \textit{Individual connectivity degree} is smaller than all its neighbors.
-Afterwards, the \textit{Individual connectivity degree} of its neighbors becomes $M$ and has no means to decrease, thus the cluster head will remain to be cluster head.
-\end{proof}
-
-%According to Theorem~\ref{clustering:theorem}, Phase I completes within a reasonable amount of time.
-%
-%This judgement is conducted periodically, and phase I ends after every node ascertains it is cluster head or not.
-
-\begin{lemma}
-\label{clustering:lemma3}
-In the process of cluster head selection and initial cluster formation, the maximum number of times that a secondary node becomes cluster head is $N$.
-\end{lemma}
-This lemma can be easily gotten from~\ref{clustering:lemma2} considering the $N$ is the number of all the secondary users in the CRN.
-Based on these Lemmas, we can easily obtain Theorem~\ref{clustering:lemma1},
-\begin{theorem}
-\label{clustering:theorem}
-Assuming the time for a secondary user to update the information about cluster heads in its neighborhood is $T$, then it takes at most $N*T $ time to finish the process of cluster head selection and initial cluster formation.
-\end{theorem}
-Phase I ends when no more secondary users becoming cluster head.
-based on~\ref{clustering:lemma1} and~\ref{clustering:lemma3}, the theorem is proved.
-
-As Algorithm~\ref{alg0} is executed concurrently by different secondary users, the needed time can be considerably reduced.
-If we apply Algorithm~\ref{alg0} to the example shown in Figure~\ref{fig1}, the outcome is shown in Figure~\ref{fig2}.
-Node $B$ and $H$ have the same individual connectivity degree, i.e., $d_B=d_H$. As $g_H=2>g_B=1$, node $H$ becomes the cluster head and cluster $C(H)$ is $\{H, B, A, G\}$.
 
@@
 
+%%%%%%%%%%%%%%%
+We have the following lemma to show that every secondary user will eventually be either integrated into a certain cluster or becomes a cluster head.
+
+\begin{lemma}
+\label{clustering:lemma1}
+Given a CRN where any secondary user is able to communicate with any other secondary user through the other nodes, then after the phase of cluster head selection and initial cluster formation, every secondary user either becomes cluster head, or gets included into at least one cluster.
+\end{lemma}
+
+%Here, by \textit{step} we mean Algorithm~\ref{clustering:theorem} is executed by a secondary user for one time.
+%In one special scenario, \eg when a cluster head is elected and all the other nodes are within its neighborhood, the number of steps is 1.
+The Proof is given in Appendix~\ref{proof_clustering:lemma1}.
+%The proof also illustrates the maximal time needed to conduct Algorithm~\ref{clustering:theorem}. 
+%Consider an extreme scenario, where all the secondary nodes sequentially execute Algorithm~\ref{alg0}, \ie they constitute a chain as discussed in the example in the proof.
+%
+%Assuming there is a token in the CRN, one node is allowed to execute Algorithm~\ref{alg0} only when it holds the token, and it then transfers the token to the neighboring node on the chain.
+%If one step can be finished within a certain time span $T$, then the total time needed for the network to conduct Algorithm~\ref{clustering:theorem} is $N*T$.
+%C1-6
+
+\begin{lemma}
+\label{clustering:lemma2}
+When a secondary user becomes cluster head, it will not become cluster member again.
+\end{lemma}
+\begin{proof}
+A secondary node becomes cluster head when its \textit{Individual connectivity degree} is smaller than all its neighbors.
+Afterwards, the \textit{Individual connectivity degree} of its neighbors becomes $M$ and has no means to decrease, thus the cluster head will remain to be cluster head.
+\end{proof}
+
+%According to Theorem~\ref{clustering:theorem}, Phase I completes within a reasonable amount of time.
+%
+%This judgement is conducted periodically, and phase I ends after every node ascertains it is cluster head or not.
+
+\begin{lemma}
+\label{clustering:lemma3}
+In the process of cluster head selection and initial cluster formation, the maximum number of times that a secondary node becomes cluster head is $N$.
+\end{lemma}
+This lemma can be easily gotten from~\ref{clustering:lemma2} considering the $N$ is the number of all the secondary users in the CRN.
+Based on these Lemmas, we can easily obtain Theorem~\ref{clustering:lemma1},
+\begin{theorem}
+\label{clustering:theorem}
+Assuming the time for a secondary user to update the information about cluster heads in its neighborhood is $T$, then it takes at most $N*T $ time to finish the process of cluster head selection and initial cluster formation.
+\end{theorem}
+Phase I ends when no more secondary users becoming cluster head.
+based on~\ref{clustering:lemma1} and~\ref{clustering:lemma3}, the theorem is proved.
+
+As Algorithm~\ref{alg0} is executed concurrently by different secondary users, the needed time can be considerably reduced.
+If we apply Algorithm~\ref{alg0} to the example shown in Figure~\ref{fig1}, the outcome is shown in Figure~\ref{fig2}.
+Node $B$ and $H$ have the same individual connectivity degree, i.e., $d_B=d_H$. As $g_H=2>g_B=1$, node $H$ becomes the cluster head and cluster $C(H)$ is $\{H, B, A, G\}$.
+
 \subsection{Phase II - Membership Clarification}
@@
 \label{conclusion}
-In this paper we investigate the robust clustering problem in CRN extensively and propose both centralized and distributed clustering solutions.
+In this paper we investigate the robust clustering problem in CRN thoroughly and propose both centralized and distributed clustering solutions.
 We give the mathematical description of the problem and prove the NP hardness of it.

### 2017-10-03 journal-draft/ettdoc.tex
the version sent to James before the reversion submission
modified changes per James' comments

@@
 Unlicensed channels, which are temporally available for a group of cognitive radio users in one area, consolidate the group into a cluster.
-More available unlicensed channels in a cluster make the cluster more likely to uphold against the licensed users' influence than only one available channel, which make that cluster to be more robust.
-This paper analyses the problem of how to form robust clusters in a cognitive radio network so that more cognitive radio users can still be benefited from cluster structure when the primary users' operations becomes more intense.
+More available unlicensed channels in a cluster make the cluster more likely to uphold against the licensed users' influence, making clusters more robust.
+This paper analyses the problem of how to form robust clusters in a cognitive radio network such that cognitive radio systems benefit from collaboration within clusters despite intense primary user activity.
 %In the process of forming clusters, every secondary user decides with whom to form a cluster, or which cluster to join.
 We give a formal description of the robust clustering problem, prove it to be NP-hard and propose both centralized and distributed solutions.
-The congestion game model is adopted to analyze the process of cluster formation, which not only contributes to the design of the distributed clustering scheme, but also provides the guarantee on the convergence into Nash Equilibrium and the convergence speed.
+The congestion game model is adopted to analyze the process of cluster formation, which not only contributes to the design of the distributed clustering scheme, but also provides a guarantee on the convergence to a Nash equilibrium and the convergence speed.
 %Our proposed clustering solution is versatile to fulfill some other requirements such as faster convergence and cluster size control.
@@
 %Besides, we prove the clustering problem is NP-hard, and also propose the centralized solution.
-Extensive simulations have been conducted which clearly support our claims.
+Extensive simulations are presented supporting the theoretical claims.
 \end{abstract}
@@
 
-Clustering is the process of grouping certain users in geographic proximity into a collective, and as an effective technique, it is proposed with the emergence of mobile wireless networks~\cite{gerla_97} and there has been a plethora of clustering schemes.
+Clustering is the process of grouping certain users in geographic proximity into a collective,.
+% and as an effective technique, it is proposed with the emergence of mobile wireless networks~\cite{gerla_97} and there has been a plethora of clustering schemes.
 As to the wireless networks where no restriction is imposed on the nodes to access the spectrum, \ie 
@@
 The activity of primary users is usually unknown to the secondary users thus deemed as random to secondary users.
-Consequently, a cluster which secures more CCs will anticipate a longer life expectancy. 
-In other words, such clusters are more robust.
+Consequently, a cluster which secures more CCs will be more robust to random primary user activity and anticipate a longer life expectancy. 
 In this paper, the robustness of the clusters is their ability to uphold with the influence of active primary users.
-The robust clustering enables more secondary users to reside in the resulted clusters when the available spectrum becomes scarcer.
-%
-Within in a cluster, both payload and control overheads can be transmitted on the CCs.
+The robust clustering enables more secondary users to reside in the resulting clusters when the available spectrum becomes scarcer.
+%
+In a cluster, both payload and control overheads can be transmitted on the CCs.
 When one or several cluster members can not access a certain CC on which primary user's activity is detected, the channel will be excluded from the set of CCs.
@@
 In this paper robust clustering in CRN is analyzed as a mathematical problem and proved to be NP-hard, then both centralized and distributed schemes are proposed.
-We rethink the metric used to measure the cluster robustness in the previous works~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}, and we claim cluster robustness can not be indicated merely by the average number of CCs of clusters, but by the ability of the clusters to uphold when the primary users' activity becomes more active.
+We propose an alternate metric to measure cluster robustness in contrast to previous works~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
+We claim cluster robustness can not be indicated merely by the average number of CCs of clusters, but by the ability of the clusters to uphold when the primary users' activity becomes more active.
 In this paper, we identify the robustness by the number of unclustered CR nodes.
@@
 The propsoed distributed schemes extend our previous work ROSS (Robust Spectrum Sharing)~\cite{Li11_ROSS} by involving cluster size control.
-Our distributed schemes solve the size devergence problem in clusters as appears in~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
+Our distributed schemes solve the size divergence problem in clusters as discussed in~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
 Besides, our proposed distributed schemes are still suitable for the scenario where fast deployment is desired.
@@
 %
-The rest of paper is organized as follows. 
-In section~\ref{related_work}, we will introduce the clustering techniques in CRN and those focusing on robustness.
+The rest of the paper is organized as follows. 
+In section~\ref{related_work}, we introduce the clustering techniques in CRN and those focusing on robustness.
 The relation between this paper and work~\cite{Li11_ROSS} is elaborated.
-She system model and the robust clustering problem formulation are presented in Section~\ref{sec:model}. 
+The system model and the robust clustering problem formulation are presented in Section~\ref{sec:model}. 
 The centralized and distributed solutions are introduced in Section~\ref{centralized_solution} and~\ref{ross} respectively.
@@
 \label{related_work}
-In the following we will give a brief review on the clustering in CRN, with emphasis on the theme of robust clustering.
+In the following we give a brief review on the clustering in CRN, with emphasis on the theme of robust clustering.
 %%[crn for clustering] 
@@
 
-The authors of~\cite{Mansoor2015} propose a clustering algorithm which aims to speed up the process of re-clustering in case a cluster doesn't uphold in from of active primary users.
-But this work doesn't consider to improve the ability of the formed clusters to maintain, and the messaging cost which is involved in this process is not considered.
+The authors of~\cite{Mansoor2015} propose a clustering algorithm which aims to speed up the process of re-clustering in case a cluster doesn't uphold in front of active primary users.
+%But this work doesn't consider to improve the ability of the formed clusters to maintain, and the messaging cost which is involved in this process is not considered.
+However, this work does not consider robustness improvement of clusters, while also ignoring messaging overhead.
 Robustness of clusters is discussed in~\cite{LIU_TMC11_2}. A distributed clustering scheme (denoted as SOC) which is designed to generate robust clusters against primary users is proposed.
@@
 %
-A distributed clustering scheme ROSS (Robust Spectrum Sharing) is proposed in~\cite{Li11_ROSS} under the game theoretic framework. 
+We propose a distributed clustering scheme ROSS (Robust Spectrum Sharing) in~\cite{Li11_ROSS} under the game theoretic framework. 
 Compared with the clustering schemes introduced above, the clusters are formed faster and the clusters possess more CCs than SOC.
 However, as all the other clustering schemes, this scheme does not have control over the formation of the very small or very large clusters which are not desirable.
-Furthermore, both this work and SOC define robustness just to be the number of CCs per cluster, and don't consider the sustainability of clusters against the increasing activity of primary users, which leaves their claim on robustness unverified.
+Furthermore, both this work and SOC define robustness just to be the number of CCs per cluster, and don't consider the sustainability of clusters against increasing activity of primary users, leaving the issue of cluster robustness open..
 %
@@
 As introduced in Section~\ref{intro}, robustness of the clusters is their ability to uphold with the influence of the active primary users, and it is represented by the number of secondary users which are not included in any cluster.
-To achieve better robustness, we form the clusters so that they have more CCs.
-Meanwhile, the sizes of the formed clusters should be regulated, \ie they don't diverge from a given value greatly.adv
+To achieve better robustness, we propose that cluster should be formed by increasing the  number of CCs.
+Meanwhile, the sizes of the formed clusters should be regulated, \ie they don't diverge from a given value greatly.
 %Considering the above mentioned requirements, we present the definition of robust clustering problem as follows.
@@
 \includegraphics[width=0.8\linewidth]{flow_chart.pdf}
-	\caption{Processors of ROSS}
+	\caption{Processing steps of ROSS}
 	\label{flowChartROSS}
@@
 \footnote{The reason for the occurrence of the cluster heads in the neighborhood of a new cluster head will be explained in Section~\ref{ross_p1_guarantee_ccc} and \ref{ross_p2_cluster_pruning})}
-Actually during the whole phase I, whenever a CR node is decided to be a cluster head thus accordingly forms a cluster, or its cluster's composition is changed, the cluster head broadcasts the new information about its cluster, which includes the sets of available channels on all its cluster members.
+Actually during the whole phase I, whenever a CR node is decided to be a cluster head (thus accordingly forms a cluster), or its cluster's composition is changed, the cluster head broadcasts the new information about its cluster, which includes the sets of available channels on all its cluster members.
 The pseudo code for the cluster head decision and the initial cluster formation is shown in Algorithm~\ref{alg0} in appendix.
@@
 \begin{proof}
-A secondary node becomes cluster head when its \textit{Individual connectivity degree} is smaller than all its neighbors.
-Afterwards, the \textit{Individual connectivity degree} of its neighbors becomes $M$ and has no means to decrease, thus the cluster head will remain to be cluster head.
+A secondary node becomes cluster head when its \textit{individual connectivity degree} is smaller than all its neighbors.
+Afterwards, the \textit{individual connectivity degree} of its neighbors becomes $M$ and has no means to decrease, thus the cluster head will remain to be cluster head.
+As to the node which is excluded form a cluster due to guaranteeing CC or size control, its \textit{individual connectivity degree} is restored, but it will not include its former cluster head, even if it becomes cluster head as regulated in~\ref{alg0}.
 \end{proof}
@@
 \end{lemma}
-This lemma can be easily gotten from~\ref{clustering:lemma2} considering the $N$ is the number of all the secondary users in the CRN.
+This lemma can be easily obtained from~\ref{clustering:lemma2} considering the $N$ is the number of all the secondary users in the CRN.
 Based on these Lemmas, we can easily obtain Theorem~\ref{clustering:lemma1},
@@
 \end{theorem}
-Phase I ends when no more secondary users becoming cluster head.
-based on~\ref{clustering:lemma1} and~\ref{clustering:lemma3}, the theorem is proved.
-
-As Algorithm~\ref{alg0} is executed concurrently by different secondary users, the needed time can be considerably reduced.
+Phase I ends when no more secondary users are becoming cluster head.
+Based on~\ref{clustering:lemma1} and~\ref{clustering:lemma3}, the theorem is proved.
+
+As Algorithm~\ref{alg0} is executed concurrently by different secondary users, the required time can be considerably reduced.
 If we apply Algorithm~\ref{alg0} to the example shown in Figure~\ref{fig1}, the outcome is shown in Figure~\ref{fig2}.
@@
 \item \textbf{Influence from inaccurate spectrum sensing.}
-The above simulations are conducted with the assumption of perfect spectrum sensing.
-As the errors in spectrum sensing is inevitable, we are interested to see the performance of the distributed schemes when the spectrum sensing is not perfect.
+The above simulations are conducted under the assumption of perfect spectrum sensing.
+As spectrum sensing in practise is subject to errors, we are interested to see the performance of the distributed schemes when the spectrum sensing is not perfect.
 %The errors in spectrum sensing is inevitable, and the decision is made by the secondary users and based on the sensing results, without considering the difference between the sensing result and the ground truth.
 The false negative in spectrum sensing, which misdetects the presence of the active primary users, is harmful to the primary users and should be avoided as much as possible.
-On the contrary, false positive \ie which reports the presence of active primary users when there are actually not, only decreases the available spectrum for the secondary users.
+On the contrary, a false positive \ie which reports the presence of active primary users when there are actually none, only decreases the available spectrum for the secondary users.
 In this regard, we assume only the false negative exists in the spectrum sensing.
 
-We assume when a secondary user is within the transmission range of an active primary user, the probability that it misdetects and thus regards a channel is available equals to the rate of false negative.
+We assume when a secondary user is within the transmission range of an active primary user, the probability that it misdetects and thus regards a channel as being available equals to the rate of false negative.
 The secondary users make clustering decisions based on the imperfect spectrum sensing.
@@
 
-If we use the number of secondary users residing in a cluster as the numerical representation of cluster robustness, then the variants of ROSS is from 5\%,  30\% and 230\% more robust than SOC with the number of newly added PR is 10, 40 and 80 respectively.
+If we use the number of secondary users residing in a cluster as the numerical representation of cluster robustness, then the ROSS based schemes are 5\%,  30\% and 230\% more robust than SOC, where the numbers of newly added PR are 10, 40 and 80 respectively.
 The above observation shows that the average number of CCs of non-singleton clusters doesn't necessarily illustrate the robustness  of cluster, \ie SOC obtains the most CCs for the clusters which are meanwhile the most vulnerable.
@@
 %The influence of the false negative on the sustainability of the clusters can be seen from Figure~\ref{false_negative_CDF}.
-For all the schemes, when false negative increases, the number of singleton clusters increases accordingly.
+For all the schemes, when false negatives increase, the number of singleton clusters increases accordingly.
 %As to the ROSS variants, the changes of the CDF curves are resulted from the increasing singleton clusters.
-The clusters from SOC are affected by the sensing errors the greatly.
+The clusters from SOC are affected by the sensing errors greatly.
 More unclustered nodes are generated, and a lot of small clusters are formed, \eg when false negative rate is 30\%.
@@
 \item The sizes of the clusters generated by ROSS demonstrate smaller discrepancy than that of SOC.
-\item The variants of ROSS are more resilient against the imperfect spectrum sensing.
+\item The variants of ROSS are more resilient against the erroneous spectrum sensing.
 \end{itemize}

### 2017-10-03 journal-draft/ettdoc.tex
modified changes per James' comments

@@
 
-Clustering is the process of grouping certain users in geographic proximity into a collective,.
+Clustering is the process of grouping certain users in geographic proximity into a collective.
 % and as an effective technique, it is proposed with the emergence of mobile wireless networks~\cite{gerla_97} and there has been a plethora of clustering schemes.
@@
 %
-We propose a distributed clustering scheme ROSS (Robust Spectrum Sharing) in~\cite{Li11_ROSS} under the game theoretic framework. 
+In~\cite{Li11_ROSS} we propose a distributed clustering scheme ROSS (Robust Spectrum Sharing) under the game theoretic framework. 
 Compared with the clustering schemes introduced above, the clusters are formed faster and the clusters possess more CCs than SOC.

### 2017-11-15 journal-draft/ettdoc.tex
modified 4 figures
proofreading Simulation Section + conclusion

@@
 % and as an effective technique, it is proposed with the emergence of mobile wireless networks~\cite{gerla_97} and there has been a plethora of clustering schemes.
-As to the wireless networks where no restriction is imposed on the nodes to access the spectrum, \ie 
-%Different clustering strategies have been proposed for wireless networks of different types.
+As to wireless networks where no restriction is imposed on nodes to access the spectrum, \ie 
 wireless ad-hoc, mesh networks and sensor networks, the objective of clustering can be to decrease the transmission power consumption~\cite{Kawadia03}, to improve the routing performance~\cite{clustering_mesh_globecom2010}, or to imrove the network lifetime and coverage~\cite{Abbasi_survey_07}.
 %In CRN, clusters are formed in the very beginning of the network operation, and re-formed periodically according to the dynamics of the CRN.
-In the context of cognitive radio netowrks, a formed cluster helps the participants not only improve the spectrum sensing accuracy, but also coordinate the channel switch operation when the primary users are detected by at least one secondary user in that cluster.
-Then all the cluster menmbers can stop payload transmission swiftly and vacate the operating channel ~\cite{willkomm08}.
+In the context of cognitive radio netowrks, a formed cluster helps the participants not only improve spectrum sensing accuracy, but also coordinate channel switch operation when primary users are detected by at least one secondary user in that cluster.
+Then all the cluster members can stop payload transmission swiftly and vacate the operating channel ~\cite{willkomm08}.
 Clustering also benefits the operation of a CRN by reducing the interference between cognitive clusters~\cite{centralizedSharing80222}, and supporting routing~\cite{Abbasi_survey_07}.
@@
 The authors of~\cite{Mansoor2015} propose a clustering algorithm which aims to speed up the process of re-clustering in case a cluster doesn't uphold in front of active primary users.
-%But this work doesn't consider to improve the ability of the formed clusters to maintain, and the messaging cost which is involved in this process is not considered.
-However, this work does not consider robustness improvement of clusters, while also ignoring messaging overhead.
-Robustness of clusters is discussed in~\cite{LIU_TMC11_2}. A distributed clustering scheme (denoted as SOC) which is designed to generate robust clusters against primary users is proposed.
-The robustness of the clusters comes from the fact that there are multiple CCs available for the clusters.
-SOC involves three phases of distributed executions.
-In the first phase, every secondary user forms clusters with some one-hop neighbors. In the second and third phase, each secondary user seeks to either merge other clusters or join one of them.
-The metric adopted by every secondary user in all the phases is the product of the number of CCs and cluster size.
+However, this work does not consider cluster robustness and messaging overhead during frequent re-clustering processes.
+A distributed clustering scheme~\cite{LIU_TMC11_2} (denoted as SOC) is proposed, which is designed to generate clusters which  have multiple CCs.
+The authors compared SOC with other schemes in terms of the average number of CCs of the formed cluster, where SOC outperforms other schemes by 50\%-100\%. 
+Note that SOC's comparison schemes are designed either for ad hoc network without consideration of channel availability~\cite{Basagni99}, or for CRN but just considering connection among CR nodes~\cite{Zhao07}.
+%The robustness of the clusters comes from the multiple CCs available for the clusters.
+%SOC involves three phases of distributed executions.
+In the first phase of SOC, every secondary user forms clusters with some one-hop neighbors. 
+In the second and final phase, each secondary user seeks to either merge other clusters or join one of them.
+The product of the number of CCs and cluster size is adopted as the metric by each secondary user in every phase. 
 The drawbacks of this scheme are as follows, although the adopted metric considers both the cluster size and the number of CCs, cluster formation can be easily dominated by only one factor.
@@
   \centering
-  \includegraphics[width=0.25\linewidth]{singletongame_png.png}
+  \includegraphics[width=0.37\linewidth]{singletongame_matching.pdf}
   \caption{Debatable nodes and claiming clusters}
@@
 
-The ROSS without size control mechanism is similar with the schemes proposed in \cite{Li11_ROSS}.
-The authors of~\cite{LIU_TMC11_2} compared SOC with other schemes in terms of the average number of CCs of the formed cluster, on which SOC outperforms other schemes by 50\%-100\%. 
-SOC's comparison schemes are designed either for ad hoc network without consideration of channel availability~\cite{Basagni99}, or for CRN but just considering connection among CR nodes~\cite{Zhao07}.
-Thus SOC is the only distributed scheme as comparison.
-As to the CRN shown in Figure~\ref{fig1}, the resulting clusters by the centralized scheme and SOC are shown in Figure~\ref{fig:final_clustering}.
+%The ROSS without size control mechanism is similar with the schemes proposed in \cite{Li11_ROSS}.
 
@@
 
-We investigate the schemes in the following aspects.
+As to the CRN shown in Figure~\ref{fig1}, the resulting clusters by the centralized scheme and SOC are shown in Figure~\ref{fig:final_clustering}.
+We now investigate the performances of the schemes in the following aspects.
 
@@
 \label{ccc_20}
-%We first have a look at the average number of common channels per non-singleton cluster.
-% shows the average number of the CCs of non-singleton clusters,
-%as the singleton clusters (in other words unclustered nodes) don't execute any functionalities of clusters, which are has be discussed in Section~\ref{intro}.
-From Figure~\ref{ccc_per_nonsingleton}, we can see the centralized schemes outperform the distributed schemes.
-Among the distributed schemes, SOC achieves the most CCs.
-The reason is, SOC is liable to group the neighboring CRs which share the most abundant spectrum together, no matter how many of them are there, thus the number of CC of the formed clusters is higher.
+Figure~\ref{ccc_per_nonsingleton} shows the centralized schemes outperform the distributed schemes.
+SOC achieves the most CCs among the distributed schemes, because SOC groups the neighboring CRs which share the most abundant spectrum together, without considering the number of them.
 %We have discussed the flaw of this metric as it doesn't convey the number of unclustered CR nodes, in fact, 
-On the other hand, SOC generates the most unclustered CRs.
+As a result, SOC also generates the most unclustered CRs.
 As to the variants of ROSS, we notice that the greedy mechanism increases CCs in non-singleton clusters significantly.
@@
 %, which can also be observed in the large scale CRN in Section~\ref{largeScaleCRN}.
-
-%This is because the desired cluster size happens to be the average size of clusters generated by ROSS-DGA and ROSS-DFA, then the size control functionality doesn't play effect to increase the number of CCs.
 
@@
 \end{multicols}
-%\caption{Comparison between the distributed and centralized clustering schemes ($N$ = 20)}
 \label{compare_dis_centralized}
@@
 \label{cluster_size}
-%\begin{figure}[h]
-%  \centering
-%  \includegraphics[width=0.8\linewidth]{cdf_clusterSize_20.pdf}
-%  \caption{Cumulative distribution of CRs residing in clusters with different sizes.}
-%  \label{size_control}
-%\end{figure}
-
-Figure~\ref{size_control} depicts the empirical cumulative distribution of the CRs in clusters of different sizes, from which we have two conclusions.
-First, given the channel availability in the CRN, SOC generates more unclustered CR nodes than other schemes.
-The centralized schemes don't produce unclustered CR nodes in the simulation, the unclustered nodes generated by ROSS-DGA/DFA account for 3\% of the total CR nodes, as comparison, 10\% of nodes are unclustered when applying SOC.
-ROSS-DGA and ROSS-DFA with size control feature generate 5\%-8\% unclustered CR nodes, which is due to the cluster pruning procedure (discussed in section~\ref{ross_p1_guarantee_ccc} and section~\ref{ross_p2_cluster_pruning}).
-Second, the centralized schemes and cluster size control mechanism of ROSS generate clusters with the desired cluster size.
-%When the desired size is 2, each generated cluster has two members, whereas when the desired size is 3, about 15\% CRs are formed into 2 node clusters.
-As to ROSS-DFG and ROSS-DFA with size control feature, CR nodes reside averagely in clusters whose sizes are 2, 3 and 4.
-%When ROSS-3-DFA is applied, most number of CRs are in 3 node clusters, nevertheless, slightly less nodes are found in 2 node and 4 node clusters, there are also considerable number of singleton clusters.
-%ROSS-3-DGA decreases the clusters sizes and results in more 2 node clusters, the second most CRs are found in 3 node clusters.
-The sizes of clusters resulted from ROSS-DGA and ROSS-DFA are disperse, but appear to be better than SOC, i.e., the 50\% percentiles for ROSS-DGA, ROSS-DFA and SOC are 4.5, 5, and 5.5, and the 90\% percentiles for the three schemes are 8, 8, and 9, the corresponding sizes of ROSS are closer to the desired size.
-%Figure~\ref{size_control} shows distributed clustering schemes are not able to control cluster sizes perfectly, but ROSS-DGA and ROSS-DFA eliminate the clusters whose size diverges largely with the desired one, \ie single node clusters and clusters with size of 13 and 14.
+
+Figure~\ref{size_control} depicts the empirical cumulative distribution of the CRs in clusters of different sizes.
+%First, given the channel availability in the CRN, SOC generates more unclustered CR nodes than other schemes.
+The centralized schemes don't produce unclustered CR nodes in the simulation.
+The unclustered nodes generated by ROSS-DGA/DFA account for 3\% of the total CR nodes, as comparison, 10\% of nodes are unclustered when applying SOC.
+ROSS-DGA and ROSS-DFA with size control feature generate 5\%-8\% unclustered CR nodes, which is due to the cluster pruning procedure (discussed in Section~\ref{ross_p1_guarantee_ccc} and Section~\ref{ross_p2_cluster_pruning}).
+
+In terms of cluster size, the clusters resulted from centralized schemes and ROSS with cluster size control mechanism have little deviation from the desired cluster size.
+%As to ROSS-DFG and ROSS-DFA with size control feature, CR nodes reside averagely in clusters whose sizes are 2, 3 and 4.
+The sizes of clusters resulted from ROSS-DGA and ROSS-DFA are disperse, but appear to be better than SOC, i.e., the 50\% percentiles for ROSS-DGA, ROSS-DFA and SOC are 4.5, 5, and 5.5, and the 90\% percentiles for the three schemes are 8, 8, and 9, the corresponding sizes resulted by ROSS are closer to the desired size.
 
@@
 In this part of simulation, we put PUs sequentially into CRN to decrease the available spectrum.
-10 PUs are in the network in the beginning, then extra 19 batches of PUs are added sequentially, where each batch includes 5 PUs. 
-%
-Figure~\ref{singleton_clusters} shows certain clusters can not maintain and the number of unclustered CR nodes grows when the number of PUs increases.
+10 PUs are in the network at start, extra 19 batches of PUs are added sequentially and each batch includes 5 PUs. 
+Figure~\ref{singleton_clusters} shows certain clusters can not maintain and the number of unclustered CR nodes increases when the number of PUs increases.
 The centralized scheme with desired size of 2 generates the most robust clusters, meanwhile, SOC results in the most vulnerable clusters.
@@
 
-If we use the number of secondary users residing in a cluster as the numerical representation of cluster robustness, then the ROSS based schemes are 5\%, 30\% and 230\% more robust than SOC, where the numbers of newly added PR are 10, 40 and 80 respectively.
-The above observation shows that the average number of CCs of non-singleton clusters doesn't necessarily illustrate the robustness  of cluster, \ie SOC obtains the most CCs for the clusters which are meanwhile the most vulnerable.
-Besides, with similar distribution of sizes, the clusters generated by ROSS-DGA and ROSS-DFA are more robust than that by SOC.
+Considering the number of secondary users residing in a cluster, ROSS based schemes benefit 5\%, 30\% and 230\% more secondary users from neighborhood cooperation than SOC, when the numbers of newly added PR are 10, 40 and 80 respectively.
+The above observation also shows the average number of CCs of non-singleton clusters doesn't necessarily illustrate the robustness  of cluster, \ie SOC obtains the most CCs among the distributed schemes, but the resulted clusters are vulnerable.
 
@@
 In this section we compare the overhead of signaling involved in different clustering schemes.
-We count the number of \textit{transmissions of control messages} as message complexity~\cite{complexity_aggregation_2011}, and without distinguishing broadcast or uni-cast control messages.
+We count the number of \textit{transmissions of control messages} as message complexity~\cite{complexity_aggregation_2011}, without distinguishing broadcast or uni-cast control messages.
 In Section~\ref{ross}, this metric is synonymous with the \textit{the number of updates}.
@@
 %According to~\cite{complexity_aggregation_2011}, the message complexity is defined as the number of messages used by all nodes.
-%To have the same metric to compare,
 
@@
 The centralized scheme is conducted at the centralized control device, which involves information aggregation and clustering decision dissemination.
-We adopt the backbone structure proposed in~\cite{Efficient_broadcasting_gathering_adhoc} to analyze the centralized scheme's message complexity.
-We apply ROSS to generate cluster heads which serve as the backbone.
-In the process of information aggregation, all the nodes transmit information to the cluster heads which forward the messages to the controller, then in the process of dissemination, all the cluster heads and the debatable nodes broadcast the clustering result, thus the upper bound for the number of broadcast is $N+m+n$.
-
-%
+To analyze the centralized scheme's message complexity, we adopt the backbone structure proposed in~\cite{Efficient_broadcasting_gathering_adhoc}, and apply ROSS to generate cluster heads which serve as the backbone.
+In the process of information aggregation, all the nodes transmit information to the cluster heads which forward the messages to the controller. 
+In the process of dissemination, all the cluster heads and the debatable nodes broadcast the clustering result, thus the upper bound for the number of broadcast is $N+m+n$.
+
 %, when a CR node decides itself to be the cluster head, it broadcasts a message containing its ID, cluster members and the set of CCs in its cluster.
@@
 %The complexity parameters are the number of nodes $n$ in network, number of clusters $h$.
-Table \ref{tab_overhead} shows the message complexity, quantitative amount of the control messages, and the size of control messages.
+Table \ref{tab_overhead} shows message complexity, quantitative amount of control messages, and size of control messages.
 Figure~\ref{control_msg} shows the analytical result of the amount of transmissions involved in different schemes.
 %the upper bound of the number of transmissions of ROSS, and the analytic number of transmissions of the centralized scheme.
-
-%\begin{table}[hc]
-%\centering
-%\caption{Singalling overhead. Notations: $n$-number of CR nodes in CRN, $h$-number of cluster heads, $m$-number of debatable nodes, $c$-number of demanding clusters.}\label{tab_overhead}
-%\begin{tabular}{|p{2.2 cm}|p{1.5 cm}|p{3.7 cm}|}
-%\hline
-% Scheme 					&   Number of transmissions 					& Content of message \\ \hline
-% ROSS-DGA, ROSS-$\delta$-DGA 		&   $h+2*m^2c$ (upper bound)
-%				& $ID_{H_C}$ and $K_C$ for $h+m^2c$ times, notification to join one cluster for $m^2c$ times					\\ \hline
-% ROSS-DFA, ROSS-$\delta$-DFA 		&   $h+ 2m$	 (upper bound) 						& $ID_{H_C}$ and $K_C$ for $h+m$ times, notification to join one cluster for $m$ times	 					\\ \hline
-% SOC 						&   $3*n$					& $\{K_i\}, i\in M\subseteq \texttt{Nb}_i$						\\ \hline
-% Centralized				&	$n$						& $\{C\}$         	\\ 
-% \hline
-%\end{tabular}
-%\end{table}
 
@@
 \label{largeScaleCRN}
-In this section we investigate the performances of the proposed distributed clustering schemes in CRN with different network scales and densities.
+In this section we investigate the performances of the proposed distributed clustering schemes with different network scales and densities.
 The transmission range of CR is $A/5$, PU's transmission range is $2A/5$.
@@
 \subsubsection{Robustness of the Formed Clusters}
-Here we see how vulnerable the clusters are when they are exposed to the increasing influence of the PUs.
-We increase the primary users' activity by importing 20 batches of PUs sequentially in the CRN, where each batch includes 10 PUs. 
-%
-Figure~\ref{singleton_clusters_100} and \ref{singleton_clusters_200} show that when $N=100$ and 200, compared with the variants of ROSS, more unclustered CR nodes are caused by SOC with the same intensity of PUs' activities.
-When $N=300$ as shown in Figure~\ref{singleton_clusters_300} and the new PUs are not many, ROSS-DGA/DFA generate slightly more unclustered CR nodes than SOC, but SOC's performance deteriorates quickly when the PUs continue increasing.
-%
-From Figure~\ref{singleton_clusters_100} to~\ref{singleton_clusters_300}, we can see that significantly less unclustered CR nodes are generated by the variants of ROSS which have size control mechanism.
+Here we see how robust clusters are when exposed to the increasing influence of PUs.
+We increase primary users' activity by importing 20 batches of PUs sequentially in CRN, where each batch includes 10 PUs. 
+%
+Figure~\ref{singleton_clusters_100} and \ref{singleton_clusters_200} show when $N=100$ and 200, with the same intensity of PUs' activities, more unclustered CR nodes are resulted from SOC than the variants of ROSS,
+When $N=300$ as shown in Figure~\ref{singleton_clusters_300} and new PUs are not many, ROSS-DGA/DFA generate slightly more unclustered CR nodes than SOC, but SOC's performance deteriorates quickly when the number of PUs continue increasing.
+%
+From Figure~\ref{singleton_clusters_100} to~\ref{singleton_clusters_300}, we can see that significantly less unclustered CR nodes are generated by ROSS with size control mechanism.
 Besides, the greedy mechanism moderately strengthens the robustness of the clusters.
-We only show the average values of the variants of ROSS as their confidence intervals overlap.
+%We only show the average values of the variants of ROSS as their confidence intervals overlap.
 
@@
 \subsubsection{Cluster Size Control}
-Figure~\ref{nClusters_largeNetwork} shows when the network density increases, \ie $N$ changes from 100 to 300, the number of generated clusters by SOC increases linearly, whereas that by ROSS increases by a smaller margin.
+Figure~\ref{nClusters_largeNetwork} shows when network density increases, \ie $N$ changes from 100 to 300 in the same area, the number of clusters resulted from SOC increases linearly, whereas that by ROSS increases by a smaller margin.
 This result coincides with the analysis in Section~\ref{ross_p2_cluster_pruning}.
 %When the network becomes denser, more clusters are generated by SOC compared with ROSS variants.
-To better understand the distribution of the sizes of formed clusters, for each network density, we depict the empirical cumulative distribution of CR nodes which are in clusters with different sizes in Figures~\ref{cdf_clusterSize_100}~\ref{cdf_clusterSize_200}~\ref{cdf_clusterSize_300} respectively.
+To see the distribution of the sizes of formed clusters, for each network density, we depict empirical cumulative distribution of CR nodes which are in clusters with different sizes in Figures~\ref{cdf_clusterSize_100}~\ref{cdf_clusterSize_200}~\ref{cdf_clusterSize_300} respectively.
 \begin{figure}[!h]
@@
 
-The variants of ROSS generate more clusters whose sizes are closer to the desired size, \ie when $N=100$ and desired cluster size is 6 as shown in Figures~\ref{cdf_clusterSize_100}, 90\% of CR nodes are in the clusters whose sizes are from 3 to 9, while as to SOC, only 17\% of nodes are in the clusters with these sizes.
-Similarly, when $N=200$ and the desired size is 12 as shown in Figure~\ref{cdf_clusterSize_200}, 80\% of nodes are in the clusters whose sizes are from 6 to 18, meanwhile only 30\% of nodes constitute clusters of these sizes when SOC is executed.
+The cluster sizes resulted from the variants of ROSS are in proximity to the desired size, \ie as shown in Figures~\ref{cdf_clusterSize_100}, 90\% of CR nodes are in the clusters whose sizes are between 3 and 9, while for SOC, only 17\% of nodes are in the clusters with these sizes.
+Similarly, when $N=200$ and desired size is 12 as shown in Figure~\ref{cdf_clusterSize_200}, 80\% of nodes are in the clusters whose sizes are between 6 and 18, meanwhile only 30\% of nodes are in the clusters with these sizes when SOC is executed.
 %Now we check how many CR nodes are in the clusters whose sizes deviate not much from the desired size, where we put the deviation limit at $\pm 50\%$ of the desired size.
-The clusters sizes from ROSS-$\delta$-DGA and ROSS-$\delta$-DFA concentrates more than that from ROSS-DGA and ROSS-DFA.
+The clusters sizes from ROSS-$\delta$-DGA and ROSS-$\delta$-DFA concentrates more around the desired size than that from ROSS-DGA and ROSS-DFA.
 In contrary, the clusters from SOC demonstrates obvious divergence on cluster sizes.
-
-%As to ROSS-DGA, the 95\% percentiles of the ROSS-DGA curves are 8, 18 and 20.
-%When the size control feature is implemented, the 95\% percentiles of ROSS-$\delta$-DGA is 5,12,13. 
-%Meanwhile, the 50\% percentiles of the ROSS-DGA curves are 6, 10 and 14 respectively, and the 50\% percentiles of the ROSS-$\delta$-DGA are 4,7,9.
-%As comparison, the 95\% percentiles of SOC are 36, 30, and 40 in the respective networks.
 
@@
 The limitation of distributed scheme ROSS is it doesn't generate clusters whose sizes exceed the cluster head's neighborhood.
-The reason is with ROSS, cluster heads form clusters on the basis of their neighborhood, and don't involve the nodes which are outside the neighborhood.
+The reason is with ROSS, cluster heads form clusters on the basis of their neighborhood, thus don't involve the nodes out of the neighborhood.
 
@@
   \caption{The number of CCs per non-singleton cluster with the presence of spectrum sensing false negative}
-  %, there are $x=6$ when $N=100$, $x=12$ when $N=200$, $x=21$ when $N=300$, which is around $2/3$ of the number of average neighbours.
   \label{false_negative_ccc}
 \end{figure}
-%The influence of the false negative on the sustainability of the clusters can be seen from Figure~\ref{false_negative_CDF}.
-For all the schemes, when false negatives increase, the number of singleton clusters increases accordingly.
-%As to the ROSS variants, the changes of the CDF curves are resulted from the increasing singleton clusters.
-The clusters from SOC are affected by the sensing errors greatly.
+For all the schemes, when false negatives increase, the number of singleton clusters and smaller clusters increases accordingly.
+The clusters resulted from SOC are affected by the sensing errors heavily.
 More unclustered nodes are generated, and a lot of small clusters are formed, \eg when false negative rate is 30\%.
 In contrary, ROSS variants are resilient in terms of unclusterd nodes and cluster sizes.
-We can conclude that through negotiation within the neighborhoods, ROSS variants successfully rules out the channel from false negative sensing.
+We can conclude that due to the negotiation within neighborhoods, ROSS variants successfully rules out the channels obtained due to false negative sensing.
 \begin{figure}[!h]
@@
 The simulation with large CRN network confirms the conclusion drawn from the small CRN network.
-First, different from the assumption adopted in all the previous works, the average number of CCs per cluster can tell the robustness against the increasing influence of the primary users.
-Second, the centralized clustering scheme is able to form the clusters which satisfy the requirement on cluster size strictly, and the clusters are robust against PUs' increasing activity, besides, it involves the smallest control overhead in the process of clustering.
-Third, as distributed schemes, the variants of ROSS outperform SOC considerably in four aspects.
-\begin{itemize}
+First, the average number of CCs per cluster, which is adopted as metric for cluster robustness, is not able to tell the robustness against the increasing influence of the primary users.
+Second, the centralized clustering scheme forms the clusters which satisfy the requirement on cluster size, and the resulted clusters are robust against PUs' increasing activity, besides, it involves the smallest control overhead in the process of clustering.
+Third, as distributed schemes, the variants of ROSS outperform SOC considerably in the following four aspects.
+\begin{itemize}[noitemsep,topsep=0pt]
 \item The variants of ROSS generate less unclustered nodes than SOC for a given CRN, and the resulted clusters are more robust than SOC when PUs become more active.
-\item The signaling overhead involved in ROSS is about half of that needed for SOC, and the signaling messages are much shorter that the latter.
-\item The sizes of the clusters generated by ROSS demonstrate smaller discrepancy than that of SOC.
+\item The amount of signaling overhead involved in ROSS is about half of that needed for SOC, and the signaling messages are much shorter that the latter.
+\item Compared with SOC, the clusters generated by ROSS don't appear with a wide span of sizes.
+ROSS with size control mechanism result in the clusters whose sizes are in proximity to the desired size.
 \item The variants of ROSS are more resilient against the erroneous spectrum sensing.
@@
 \label{conclusion}
-In this paper we investigate the robust clustering problem in CRN thoroughly and propose both centralized and distributed clustering solutions.
-We give the mathematical description of the problem and prove the NP hardness of it.
-The proposed clustering schemes generate clusters which have long life expectancy against the primary users' activity, and the generated clusters have similar sizes with the desired one.
+In this paper we investigate robust clustering problem in CRN thoroughly and propose both centralized and distributed clustering solutions.
+We give mathematical description of the problem and prove NP hardness of it.
+The proposed centralized scheme generate clusters which have long life expectancy against primary users, and the cluster sizes are close to the desired cluster size.
+%The distributed scheme not only results in more robust clusters, but the cluster sizes are in a smaller range than the comparison scheme.
 %The congestion game model in game theory is used to design the distributed schemes.
 %A Light weighted clustering scheme ROSS is also proposed.
-Through simulation, the distributed schemes demonstrate similar performance with the centralized scheme in terms of cluster robustness, signaling overhead and cluster sizes, and outperform the comparison distributed scheme on all metrics.
-Besides, spectrum sensing errors affect the performance of the variants of ROSS much less than SOC.
-
-%In the other way around, forming big cluster which extends a cluster head's neighborhood has limited application scenarios, as multiple hop communication and coordination are required within these clusters.
+Through simulation, the distributed schemes demonstrate similar performance with the centralized scheme in terms of cluster robustness, signaling overhead and cluster sizes.
+The distributed scheme outperforms the comparison distributed scheme by generating more robust clusters,  generating clusters whose sizes are in a smaller range, and being more resilient against the erroneous spectrum sensing.
 
@@
 
+\vspace{50mm} %xx mm vertical space
+
 \appendices
-\section{Peudo Code for the Algorithm~\ref{alg0}, \ref{alg_size_control_available_CCC} and~\ref{alg4}}
+\section{Peudo Code for Algorithm~\ref{alg0}, \ref{alg_size_control_available_CCC}, \ref{alg4}}
 \begin{algorithm}              % enter the algorithm environment
@@
 \label{proof_clustering:lemma1}
-%Note that the formed cluster can be a singleton cluster, \ie cluster size is 1.
 We consider a CRN which can be represented as a connected graph.

### 2017-11-20 journal-draft/ettdoc.tex
proofreading the introduction

@@
 In contrast, as one way, unlicensed users can access the spectrum via opportunistic spectrum access, \ie they access the licensed spectrum only after validating the channel is unoccupied by licensed users, where spectrum sensing~\cite{sensing_survey_2009} plays an important role in this process.
-%
 In this hierarchical spectrum access model~\cite{zhao_survey_DSA_2007}, the licensed users are also called primary users (PU), while the unlicensed users are referred to as secondary users and constitute a so called cognitive radio network (CRN).
-%
 %cluster
-Regarding the operation of CRN, efficient spectrum sensing is identified to be critical for a smooth operation of a cognitive radio network~\cite{Sahai_FundamentalDesignTradeoffs2006}.
-The rate of false negative, \ie misdetecting the active primary users, can be decreased by cooperative spectrum sensing of multiple secondary users, which has been shown to cope effectively with noise uncertainty and channel fading, thus remarkably improving the sensing accuracy~\cite{Jacob2012, coorperativeSensing_Akyildiz11}.
+For CRN, accurate spectrum sensing is critical, and the rate of false negative \ie misdetecting the active primary users, should be minimized~\cite{Sahai_FundamentalDesignTradeoffs2006}.
+Cooperative spectrum sensing, which relies on the consensus of CR users within a certain area\footnote{The terms user and node appear interchangeably in this paper.
+In particular, user is adopted when its networking or cognitive ability are discussed or stressed, while we refer to nodes typicallly in the context of the network topology.}, has been shown to improve spectrum sensing accuracy with the presence of noise uncertainty and channel fading~\cite{Jacob2012, coorperativeSensing_Akyildiz11}.
 %C3
-Collaborative sensing relies on the consensus of CR users\footnote{The terms user and node appear interchangeably in this paper.
-In particular, user is adopted when its networking or cognitive ability are discussed or stressed, while we refer to nodes typicallly in the context of the network topology.} within a certain area, in this regard, clustering is regarded as an effective method to realize cooperative spectrum sensing~\cite{Sun07_clustering_spectrum_secsing}.
+In this regard, clustering is regarded as an effective method to realize cooperative spectrum sensing~\cite{Sun07_clustering_spectrum_secsing}.
 % ... decreases considerably the negative probability due to the random channel effects like fading and shadowing.
@@
 As to wireless networks where no restriction is imposed on nodes to access the spectrum, \ie 
-wireless ad-hoc, mesh networks and sensor networks, the objective of clustering can be to decrease the transmission power consumption~\cite{Kawadia03}, to improve the routing performance~\cite{clustering_mesh_globecom2010}, or to imrove the network lifetime and coverage~\cite{Abbasi_survey_07}.
+wireless ad-hoc, mesh networks and sensor networks, clustering the network helps to decrease the transmission power consumption~\cite{Kawadia03},  improve the routing performance~\cite{clustering_mesh_globecom2010}, or imrove the network lifetime and coverage~\cite{Abbasi_survey_07}.
 %In CRN, clusters are formed in the very beginning of the network operation, and re-formed periodically according to the dynamics of the CRN.
-In the context of cognitive radio netowrks, a formed cluster helps the participants not only improve spectrum sensing accuracy, but also coordinate channel switch operation when primary users are detected by at least one secondary user in that cluster.
-Then all the cluster members can stop payload transmission swiftly and vacate the operating channel ~\cite{willkomm08}.
+For cognitive radio netowrks, the formed clusters help the participating nodes improve spectrum sensing accuracy.
+Besides, clusters benefit channel switching when primary users are detected by at least one secondary user in that cluster, then all the cluster members can stop payload transmission swiftly and vacate the operating channel ~\cite{willkomm08}.
 Clustering also benefits the operation of a CRN by reducing the interference between cognitive clusters~\cite{centralizedSharing80222}, and supporting routing~\cite{Abbasi_survey_07}.
@@
 
-In CRN, a formed cluster seizes one or multiple unlicensed channels which are available for every CR node in the cluster.
+In CRN, a formed cluster seizes one or multiple unlicensed channels which are available for every CR node in that cluster.
 In this paper available unlicensed channels are called \textit{common licensed channels} (or common channels for short, which is abbreviated as CC).
 The availability of CCs within a cluster decides the existence of that cluster, \ie if no CCs are available then the corresponding cluster does not exist.
+In a cluster, both payload and control overheads can be transmitted on the CCs.
+When one or several cluster members can not access a certain CC because primary user's activity is detected on that channel, the channel will be excluded from the set of CCs.
+In particular, if that channel is being used for payload communication, the communication pair will stop and resume transmission on another available CC.
 The activity of primary users is usually unknown to the secondary users thus deemed as random to secondary users.
@@
 %
-In a cluster, both payload and control overheads can be transmitted on the CCs.
-When one or several cluster members can not access a certain CC on which primary user's activity is detected, the channel will be excluded from the set of CCs.
-In particular, if that channel is being used for payload communication, the communication pair will stop and resume transmission on another available CC.
+
 %As long as there is a CC available, the corresponding cluster can continue to exchange payload data.
@@
 Thus the number of small clusters, especially the \textit{singleton clusters}, \ie the cluster which has only one CR node, should be minimized.
-On the other hand, as to the cluster which consists of many nodes, although the spectrum sensing is benefited, it usually leads to less common channels. This undermines the robustness of the cluster.
+On the other hand, as to the cluster which consists of many nodes, although the spectrum sensing is benefited, there is usually only a small number of CCs.
+Thus big cluster undermines the robustness of the cluster against primary users' activity.
 Thus, the cluster robustness discussed in terms of number of CCs carries little meaning when the sizes of formed clusters are not considered.
-Cluster sizes also play a role in transmission power consumption, \ie cluster size affects the transmission power consumption when routing is conducted~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
+Cluster size also plays a role in transmission power consumption, \ie cluster size affects the transmission power consumption when routing is conducted~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
 
@@
 We claim cluster robustness can not be indicated merely by the average number of CCs of clusters, but by the ability of the clusters to uphold when the primary users' activity becomes more active.
-In this paper, we identify the robustness by the number of unclustered CR nodes.
+In this paper, we identify the robustness of clusters by the number of unclustered CR nodes.
 We also consider the necessity of cluster size control and its influence on cluster robustness.
 The propsoed distributed schemes extend our previous work ROSS (Robust Spectrum Sharing)~\cite{Li11_ROSS} by involving cluster size control.
-Our distributed schemes solve the size divergence problem in clusters as discussed in~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
-Besides, our proposed distributed schemes are still suitable for the scenario where fast deployment is desired.
+%Our distributed schemes solve the size divergence problem in clusters as discussed in~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
+%Besides, our proposed distributed schemes are still suitable for the scenario where fast deployment is desired.
 Throughout this paper, we call the proposed distributed schemes the \textit{variants of ROSS}.

### 2017-11-20 journal-draft/ettdoc.tex
Erwin's proofreading to Section 3

@@
 \corraddr{Chair of Communication and Distributed Systems
-Ahornstraße 55 - building E3
+Ahornstrasse 55 - building E3
 52074 Aachen
@@
 For cognitive radio netowrks, the formed clusters help the participating nodes improve spectrum sensing accuracy.
-Besides, clusters benefit channel switching when primary users are detected by at least one secondary user in that cluster, then all the cluster members can stop payload transmission swiftly and vacate the operating channel ~\cite{willkomm08}.
+Besides, clusters benefit channel switching when primary users are detected by at least one secondary user in that cluster, then all the cluster members can stop payload transmissions swiftly and vacate the operating channel ~\cite{willkomm08}.
 Clustering also benefits the operation of a CRN by reducing the interference between cognitive clusters~\cite{centralizedSharing80222}, and supporting routing~\cite{Abbasi_survey_07}.
@@
 In particular, if that channel is being used for payload communication, the communication pair will stop and resume transmission on another available CC.
-The activity of primary users is usually unknown to the secondary users thus deemed as random to secondary users.
-Consequently, a cluster which secures more CCs will be more robust to random primary user activity and anticipate a longer life expectancy. 
-In this paper, the robustness of the clusters is their ability to uphold with the influence of active primary users.
+The activity of primary users is usually unknown to the secondary users, thus deemed as random to secondary users.
+Consequently, a cluster which secures more CCs will be more robust to random primary user activities and anticipate a longer life expectancy. 
+In this paper, the robustness of clusters is their ability to uphold with the influence of active primary users.
 The robust clustering enables more secondary users to reside in the resulting clusters when the available spectrum becomes scarcer.
@@
 Given a CRN, it is obvious that getting rid of certain secondary users from a cluster may yield more CCs.
-However, this contradicts to one of the motivations of clustering, \ie the cooperative decision making, where more users result in more accurate sensing result~\cite{Consensus_based_clustering12}.
+However, this contradicts to one of the motivations of clustering, \ie the cooperative decision making, where in general more users result in more accurate sensing results~\cite{Consensus_based_clustering12}.
 Thus the number of small clusters, especially the \textit{singleton clusters}, \ie the cluster which has only one CR node, should be minimized.
@@
 In section~\ref{related_work}, we introduce the clustering techniques in CRN and those focusing on robustness.
-The relation between this paper and work~\cite{Li11_ROSS} is elaborated.
+The relation between this paper and work in~\cite{Li11_ROSS} is elaborated.
 The system model and the robust clustering problem formulation are presented in Section~\ref{sec:model}. 
@@
 The product of the number of CCs and cluster size is adopted as the metric by each secondary user in every phase. 
-The drawbacks of this scheme are as follows, although the adopted metric considers both the cluster size and the number of CCs, cluster formation can be easily dominated by only one factor.
+The drawbacks of this scheme are as follows: although the adopted metric considers both the cluster size and the number of CCs, cluster formation can be easily dominated by only one factor.
 For example, a node which accesses abundant channels may form a cluster by itself and doesn't have motivation to unite neighboring nodes to form a cluster.
@@
 %
-In~\cite{Li11_ROSS} we propose a distributed clustering scheme ROSS (Robust Spectrum Sharing) under the game theoretic framework. 
+In~\cite{Li11_ROSS} we propose a distributed clustering scheme ROSS (Robust Spectrum Sharing) under a game theoretic framework. 
 Compared with the clustering schemes introduced above, the clusters are formed faster and the clusters possess more CCs than SOC.
-However, as all the other clustering schemes, this scheme does not have control over the formation of the very small or very large clusters which are not desirable.
-Furthermore, both this work and SOC define robustness just to be the number of CCs per cluster, and don't consider the sustainability of clusters against increasing activity of primary users, leaving the issue of cluster robustness open..
+However, as all the other clustering schemes, this scheme does not have control over formation of the very small or very large clusters which are not desirable.
+Furthermore, both this work and SOC define robustness just to be the number of CCs per cluster, and don't consider the sustainability of clusters against increasing activity of primary users, leaving the issue of cluster robustness open.
 %
@@
 %On the other hand, if $i$ is not in the transmission range of primary user $p$, $i$ can certainly not detect the presence of $p$.
-We assume the primary users change their operation channels slowly, thus we consider the clustering problem at some point in time given some degree of information of the availability of the control channels.
-Due to the same reason, we omit the time index for the spectrum availability. 
+We assume the primary users change their operation channels slowly, thus we omit the time index when denoting spectrum availability. 
+%Thus we consider the clustering problem at some point in time given some degree of information of the availability of the control channels.
+%Due to the same reason, we omit the time index for the spectrum availability. 
 As the result of spectrum sensing, $K_i \subseteq \mathcal{K}$ denotes the set of available licensed channels for CR user $i$.
@@
 Over the control channel, a secondary user $i$ can exchange its spectrum sensing result $K_i$ with all its one hop neighbors $\text{Nb}(i)$.
-In the following, we refer to the licensed channels as channels in general, and will explicitly mention the dedicated control channel if necessary.
+In the following, we refer to licensed channels as channels in general, and will explicitly mention the dedicated control channel if necessary.
 
@@
 A cluster $C$ is a set of secondary nodes, and there is one set of common channels which are available for each node.
-In particular, a cluster consists of a cluster head $h(C)$ and a number of cluster members, and the cluster head is able to communicate with any cluster member directly.
-Our scheme enables the cluster heads are selected in a distributed manner, and a cluster can only be formed only by these selected cluster head.
+In particular, a cluster consists of a cluster head $h(C)$ and a number of cluster members.
+The cluster head is able to communicate with any cluster member directly.
+Our scheme enables the cluster heads to be selected in a distributed manner, and a cluster can only be formed only by these selected cluster head.
 %C1-4

### 2017-11-21 journal-draft/ettdoc.tex
proofreading section 4 and 5.1

@@
 A set of licensed channels $\mathcal{K}$ is available for the primary users. 
-The CR users are allowed to transmit on channel $k \in \mathcal{K}$ only if no primary user is detected on channel $k$. 
+The CR users are allowed to transmit on channel $k \in \mathcal{K}$ only if no primary user is detected to be working at their locations on channel $k$. 
 CR users conduct spectrum sensing independently and sequentially on all licensed channels.\footnote{We assume that every node can detect the presence of an active primary user on each channel with certain accuracy.
@@
 If a CR node $i$ locates within the transmission range of an active primary user $p$, $i$ is not allowed to use the channel which is being used by $p$.
-%On the other hand, if $i$ is not in the transmission range of primary user $p$, $i$ can certainly not detect the presence of $p$.
 We assume the primary users change their operation channels slowly, thus we omit the time index when denoting spectrum availability. 
-%Thus we consider the clustering problem at some point in time given some degree of information of the availability of the control channels.
-%Due to the same reason, we omit the time index for the spectrum availability. 
 As the result of spectrum sensing, $K_i \subseteq \mathcal{K}$ denotes the set of available licensed channels for CR user $i$.
-As the transmission range of primary users is limited and CR users have different locations, different CR users have different views of the spectrum availability, i.e., for any $i, j \in \mathcal{N}$, $K_i = K_{j}$ does not necessarily hold.
+As the transmission range of primary users is limited and CR users have different locations, different CR users have different views of the spectrum availability, i.e., for any $i, j \in \mathcal{N}$, $K_i$ equals $K_{j}$ does not necessarily hold.
 We therefore represent the network of CR nodes by a graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{i, j\} \in E$ if and only if $K_{i} \cap K_{j}\neq \emptyset$ and $d_{i,j} < r$, where $d_{i,j}$ is the distance between $i, j$ and $r$ is the radius of CR user's transmission range.
@@
 
-We give the definition of cluster in CRN as follows. 
-A cluster $C$ is a set of secondary nodes, and there is one set of common channels which are available for each node.
-In particular, a cluster consists of a cluster head $h(C)$ and a number of cluster members.
+Here we give the description of cluster in CRN. 
+A cluster $C$ is a set of secondary nodes in an area, and there is a set of common channels which are available for each node.
+Besides, a cluster consists of a cluster head $h(C)$ and a number of cluster members.
 The cluster head is able to communicate with any cluster member directly.
@@
 \toprule
-%\multicolumn{2}{c}{Item} \\
-%\cmidrule(r){1-2}
 Symbol & Description \\
@@
 $C(i)$ & a cluster whose cluster head is $i$  \\
-%$k_i$   & set of available channels at CR node $i$  \\
 $K_i$   & the set of available channels at CR node $i$  \\
@@
 To achieve better robustness, we propose that cluster should be formed by increasing the number of CCs.
-Meanwhile, the sizes of the formed clusters should be regulated, \ie they don't diverge from a given value greatly.
-%Considering the above mentioned requirements, we present the definition of robust clustering problem as follows.
+Meanwhile, the sizes of the formed clusters should be regulated, \ie they don't diverge from the desired cluster size greatly.
 
@@
 
-%To formulate the problem, we propose a new definition for the number of CCs in a cluster.
-%We use $f(C_i)$ to denote the number of CCs of a cluster $C_i\in \mathcal{S}$, which is,
-%%and the number of common licensed channels is $f(C_i) = |K(C_i)|$ if $|C_i|>1$, and $f(C_i)=0$ when $|C_i|=1$.
-%$$
-%f(C_i) = \left\{ \begin{array}{rl}
-%|K(C_i)| 	&\mbox{$|C_i|>1$} \\
-%0 				&\mbox{$|C_i|=1$} \\
-%\end{array} \right.
-%$$
-%According to the new definition of the number of CCs in a cluster, the singleton clusters in $\mathcal{S'}$ don't contribute to the value to be maximized.
-
-%The decision version of \textit{weighted exact cover problem}: 
-%Given an universe $U$, and collection $S=\{s_1, s_2, \ldots, s_m\}$ where each subset $s_i\subseteq U$ and is given a weight $w_i$, whether there exists a collection of subsets $\mathcal{C}$ and constant number $\lambda$, so that the union of $\mathcal{C}$ equals to $U$, $s_j\cap s_{j'} = \emptyset$ for different $j$ and $j'\in \{1,2,\ldots, m\}$, and $\sum_{i\in J} w_i \geq \lambda$.
-
 \section{Centralized Solution for Robust Clustering}
 \label{centralized_solution}
-When the global knowledge of the CRN is available to us, we can propose a centralized scheme as comparison.
+When the global knowledge of the CRN \ie the locations of primary users and their working channels, and the locations of secondary users and available channels on them, we can propose a centralized scheme.
 We obtain the set of $\mathcal{S}$ which contains all the clusters in $\mathcal{N}$, \ie $\mathcal{S}=\{C_1, C_2,\ldots,C_i, \ldots, C_{|\mathcal{S}|}\}$ \footnote{The subscript $i$ means the $i$-th cluster in $\mathcal{S}$.} and there is $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = \mathcal{N}$.
 The proposed centralized solution formulates the problem in Definition~\ref{def_centralized_clustering} as an optimization problem which is solved with standard software packages.
-The optimization decides on the clusters according to the following optimization formulation,
-%
-%which constitute the whole CRN without overlapping between any two of them, besides, the sum of CCs of the chosen clusters is maximized.
-%Then, a central node (or controller) with the knowledge of all CR nodes (and also the possible clusters) can solve the problem based on the following formulation. 
-%
-%Second, we assign a cluster size related weight to each cluster, which is positively correlated with the difference between the cluster size and the desired cluster size.
-
-%Exact cover problem can be solved with Knuth's Algorithm X~\cite{dancingLinks_Knuth} as it finds out all the instances of exact cover, then we can choose the one with the biggest sum of weights. 
-%To make the formulation possible, we adopt heuristics in both the objective function and the constraints, besides, the objective is not totally aligned with the object in the Definition~\ref{def_centralized_clustering}.
-%The problem by the Definition~\ref{def_centralized_clustering} is formulate
-
-%Meanwhile, it provide a chance to constrain the cluster size by putting groups with desired sizes into $\mathcal{C}$.
-
-%the maximum size of $S$ is the \textit{Bell number} of $N$, and $S$ contains the conditions cluster .
-
-%We thus list all possible clusters whose sizes are from 2 to one certain number \footnote{this number of decided by the density of CR network, along with the occupation of PUs.
-We set this number as cluster size of the biggest cluster ever appears when conducting distributed schemes.}, and check each combination of clusters to find the best covering of network on the aspect of number of ICCs per cluster.
-%The complexity of computation is thus \bigO$(N^\delta)$, $\delta$ is the preferred cluster size.
-
-%We apply this centralized scheme on a network with network size $N$ and cluster size $\delta$.
-%There is $N\mod \delta=0$, and the expected number of clusters is $C = N/\delta$.
-%These tailored parameters don't harm the validity of the performance gap between the two schemes.
+The optimization decides on the clusters according to the following optimization formulation, which is a binary linear programming problem and can be solved by many available solvers.
 
@@
 \end{equation}
-This problem is a binary linear programming problem, which can be solved by many available solvers.
 $y_i$ and $x_{ij}$ are two binary variables.
@@
 %$|K(C_i)|$ is the number of CCs of cluster $C_i$, and $|C_i|$ is the size of cluster $C_i$.
-$p(C_i)$ is the size-related weight, which reflects the deviation of $C_i$'s size from the desired size.
-Assuming $\delta$ is the desired size, then the weight $p$ is decided according to the different cluster sizes, \ie 1,2, $\cdots$, $\sigma$.  
+$p(C_i)$ is the size-related weight, which is positively related with the difference between $C_i$'s size and the desired size.
+Assuming $\delta$ is the desired size, then weight $p$ is decided with respect to cluster sizes 1,2, $\cdots$, $\sigma$ as follows,
 $$
@@
 $$
-where $\rho_1, \rho_2, \cdots, \rho_\sigma$ are positive values and these is $\sigma > \rho_2> \rho_1>0$.
+where $ 0 < \rho_1< \rho_2 < \cdots < \rho_\sigma$.
 
@@
 
-%$$
-%w_i = \left\{ \begin{array}{rl}
-%0 &\mbox{if $i$th possible cluster $C_i$ is chosen} \\
-%1 &\mbox{if $i$th possible cluster $C_i$ is not chosen} \\
-%\end{array} \right.
-%$$
-%When $w_i$ is zero, it means $C_i$ is chosen by the optimization algorithm, in this case, the second item in the objective function becomes $p$, which is defined as follows,
-
-%Because of $w_i$, any cluster which appears in the clustering solution ($w=0$) will compromise the first component.
-%Only when that cluster's size is exactly the preferred size $\delta$, the punishment is zero.
-%In contrary, when the chosen cluster's size diverges from $\delta$, the objective function suffers \textit{loss}.
-%Then it is easy to notice that when the optimization algorithm adopts singleton clusters, the first xx.
-%With such design, the solution is encouraged not to generate singleton clusters.
-%doesn't follow the definition of $f(C)$ in Definition~\ref{def_centralized_clustering} strictly, where $f(C_i)=0$ when $|C_i|=1$, but our design echoes the definition by exerting the most severe punishment on the singleton clusters in the clustering solution.
-%Choice of $\rho_i$ affects the resultant clusters.
-
-%\begin{figure}[ht!]
-%\centering
-%\includegraphics[width=0.45\linewidth]{example.JPG}
-%\caption{Example of Matrix Q in a 6-node network, cluster size is set as 2}
-%\label{xx}
-%\end{figure}
-
-%\begin{figure}[ht!]
-%  \centering
-%  \includegraphics[width=0.5\linewidth]{figure5final.pdf}
-%  \caption{Final cluster formation.}
-%  \label{fig4}
-%\end{figure}
-
-%Note that the proposed centralized solution is heuristic.
-%We reiterate the reasons for pursuing the heuristic scheme, 
-%Note the collection of potential clusters is dependant on the network topology and spectrum availability in the network, thus to each specific CRN, the space of solution is different.
-
 The difficulty of using this method lies in obtaining the set $\mathcal{S}$.
-In the worst case, \ie the CRN forms a full connected graph, the size of $\mathcal{S}$ is $\Sigma_{r=1}^{N}\ {N \choose r} = 2^N-1$.
-%To levitate this problem, a smaller set, \ie $\mathcal{G} \subset \mathcal{S}$ can be used.
-%In this case, the global optimal may not be found.
-%$\mathcal{G}$ can be prepared based on the cluster size, and it is recommended to include all the singleton clusters to make sure the availability of feasible solutions.
-Another obstacle comes from the fact that the centralized controller needs to be reliable at anytime, which is a challenge for CRN as the spectrum on the controller can not be guaranteed.
-%In order to apply this scheme in practice, a large over head needs to be factored in in collecting the channel usage as seen by the R nodes, as well as the connectivity between the CR nodes.
-%After computing the clustering solution, the centralized node needs to distribute it across the whole network.
-
-%In CRN, it is necessary to do clustering again on some occasions.
-%For example, when a certain amount of CR users move away from their clusters, \ie they loose the direction connection with any member in their previous clusters, or a certain amount of clusters can not be maintained as the CCs in these clusters don't exist any longer due to primary users' activity.
-%Hence, when the spectrum availability and the CR users' location change frequently, the centralized robust clustering scheme is not suitable for CRN.
-
-%We thus list all possible clusters whose sizes are from 2 to one certain number \footnote{this number of decided by the density of CR network, along with the occupation of PUs.
-We set this number as cluster size of the biggest cluster ever appears when conducting distributed schemes.}, and check each combination of clusters to find the best covering of network on the aspect of number of ICCs per cluster.
-%The complexity of computation is thus \bigO$(N^\delta)$, $\delta$ is the preferred cluster size.
+In the worst case, \ie every CR node communicates directly with any other node and the CRN forms a full connected graph, the size of $\mathcal{S}$ is $\Sigma_{r=1}^{N}\ {N \choose r} = 2^N-1$.
 
@@
   \centering
-\includegraphics[width=0.8\linewidth]{flow_chart.pdf}
+\includegraphics[width=0.9\linewidth]{flow_chart.pdf}
 	\caption{Processing steps of ROSS}
@@
 
-In the first phase, clusters are formed quickly and every CR user becomes either cluster head or cluster member, besides, cluster size control is implemented in this phase.
+In the first phase, clusters are formed quickly and every CR user becomes either cluster head or cluster member, cluster size control is also implemented.
 In the second phase, non-overlapping clusters are formed in a way that the CCs of relevant clusters are mostly increased.

### 2017-11-21 journal-draft/ettdoc.tex
proofread Section 5

@@
 
-In the first phase, clusters are formed quickly and every CR user becomes either cluster head or cluster member, cluster size control is also implemented.
+In the first phase, clusters are formed quickly and every CR user becomes either cluster head or cluster member, cluster size control is also implemented	.
 In the second phase, non-overlapping clusters are formed in a way that the CCs of relevant clusters are mostly increased.
@@
 \label{phaseI}
-We assume that before conducting clustering, spectrum sensing, neighbor discovery and exchange of spectrum availability have been completed, so that every CR node is aware of the available channels for themselves and their neighbors.
+Before conducting clustering, we assume spectrum sensing and neighbor discovery are completed, and neighboring nodes exchange their channel availabilities via the dedicated control channel. 
+As a result, every CR node is aware of the available channels for themselves and their neighbors.
 In this phase, cluster heads are determined after a series of comparisons with their neighbors. 
-Two metrics are proposed to characterize the proximity in terms of available spectrum between CR node $i$ and its neighborhood, which are used in the comparisons to decide on the cluster heads.
-
-%After introducing the connectivity vector, we can proceed to introduce the first phase of algorithm ROSS.
-
-%When a CR user is identified as cluster head, its neighborhood becomes a cluster.
+Two metrics are proposed to characterize the proximity in terms of available spectrum between CR node $i$ and its neighborhood, which will be used to decide on cluster heads.
 
@@
 Connectivity vector is calculated by every secondary user after channel availability is obtained, and is then broadcasted.
-Figure~\ref{fig1} illustrates an CRN where every node's channel availability and connectivity vector is shown.
-This CRN is used as an example in the rest of this section to illustrate the proposed distributed schemes.
-%In Figure~\ref{fig1}, some primary users are randomly deployed in the network, and they are free to choose one channel out of the set of licensed channels $\mathcal{K}$ to operate.
-%As to the secondary users, the channels they are allowed to use are those which are not ruled out by the primary users in their vicinities. 
-In the example the sets of the indices of the available channels sensed by each node are: $K_A=\{1,2,3,4,5,6,10\}, K_B=\{1,2,3,5,7\}, \\K_C=\{1,3,4,10\}, K_D=\{1,2,3,5\}, \\K_E=\{2,3,5,7\}, K_F=\{2,4,5,6,7\}, \\K_G=\{1,2,3,4,8\}, K_H=\{1,2,5,8\}$.
-%C1-5
+Figure~\ref{fig1} shows a CRN, where dashed edge indicates the end nodes are within each other's transmission range, the number along the dashed line is the number of common channels between the two ends.
+The sets of the indices of the available channels sensed by each node are: $K_A=\{1,2,3,4,5,6,10\}, K_B=\{1,2,3,5,7\}, \\K_C=\{1,3,4,10\}, K_D=\{1,2,3,5\}, \\K_E=\{2,3,5,7\}, K_F=\{2,4,5,6,7\}, \\K_G=\{1,2,3,4,8\}, K_H=\{1,2,5,8\}$.
+Each node's connectivity vector is calculated and shown.
 \begin{figure}[ht!]
@@
 % \includegraphics{figure1.pdf}
-	\caption{Connectivity graph of the example CRN and the connectivity vector $(d_i, g_i)$ for each node.
-Primary users are not shown.
-The desired cluster size $\delta =3$.
-Dashed edge indicates the end nodes are within each other's transmission range.}
+	\caption{Connectivity graph of a CRN and the connectivity vector $(d_i, g_i)$ for each node. Primary users are not shown.}
 	\label{fig1}
@@
 The procedure of determining cluster heads is as follows.
-Each CR node decides whether it is a cluster head by comparing its connectivity vector with its neighbors.
-When CR node $i$ has lower individual connectivity degree than all of its neighbors except for those which have already identified to be cluster heads, node $i$ becomes a cluster head.
-If there is another CR node $j$ in its neighborhood, which has the same individual connectivity degree as $i$, \ie $d_j = d_i$ and $d_j < d_{k}, \forall k\in \text{Nb}(j)\setminus \{\Lambda\cup i\}$ where $\Lambda$ denotes cluster heads, then the node with higher neighborhood connectivity degree will become cluster head.
+Each CR node decides whether it is a cluster head by comparing its connectivity vector with neighbors.
+When CR node $i$ has lower individual connectivity degree than any of its neighbors except for those which have already been identified as cluster heads, node $i$ becomes a cluster head.
+If there is a CR node $j$ in $i$'s neighborhood, and has the same individual connectivity degree as $i$, \ie $d_j = d_i$ and $d_j < d_{k}, \forall k\in \text{Nb}(j)\setminus \{\Lambda\cup i\}$ where $\Lambda$ denotes cluster heads, then out of $i$ and $j$, the node with higher neighborhood connectivity degree will become cluster head.
 If $g_i = g_j$ as well, the node ID is used to break the tie, \ie the one with smaller node ID becomes the cluster head.
 %
-The node which is identified as a cluster head broadcasts a message to notify its neighbors of this change, then its neighbors which are not cluster heads become cluster members.
-\footnote{The reason for the occurrence of the cluster heads in the neighborhood of a new cluster head will be explained in Section~\ref{ross_p1_guarantee_ccc} and \ref{ross_p2_cluster_pruning})}
-Actually during the whole phase I, whenever a CR node is decided to be a cluster head (thus accordingly forms a cluster), or its cluster's composition is changed, the cluster head broadcasts the new information about its cluster, which includes the sets of available channels on all its cluster members.
+The node which is identified as cluster head broadcasts a message to notify its neighbors of this news, then its neighbors which are not cluster heads become its cluster members.
+\footnote{The presence of cluster heads in the neighborhood of a newly formed cluster head will be explained in Section~\ref{ross_p1_guarantee_ccc} and \ref{ross_p2_cluster_pruning})}
+During the whole phase I, whenever a CR node becomes cluster head (thus accordingly forms a cluster), or its cluster's composition is changed, the cluster head broadcasts the new information about its cluster, which includes the sets of available channels on itself and all its cluster members.
 The pseudo code for the cluster head decision and the initial cluster formation is shown in Algorithm~\ref{alg0} in appendix.
 
-After receiving the notification from a cluster head, a CR node $i$ is aware that it becomes a member of a cluster. 
-Consequently, $i$ sets its individual connectivity degree to a positive number $M > |\mathcal{K}| \cdot N$, and broadcasts the new individual connectivity degree to all of its neighbors. 
-%wrong:
-%Note that there is no cluster head which receives the notification on cluster head eligibility, and there is a Lemma on this.
-%\begin{theorem}{lemma}
-%There is no cluster head receiving the notification message on cluster head eligibility, which is sent from a node which newly becomes a cluster head.
-%\end{theorem}
-%\begin{proof}
-%We use contradiction to prove. 
-%Assume a CR node $j$ is cluster head, and receives a notification on cluster head eligibility form CR node $i$. 
-%According to the assumption on the reciprocal communication link, $i$ should have received the notification message from $j$ when $j$ becomes cluster head.
-%Then CR node $i$ will set its individual connectivity degree to zero, and has no possibility to become a cluster head.
-%\end{proof}
-When a CR node $i$ is associated to multiple clusters, \ie $i$ has received multiple notifications from different cluster heads, $d_i$ is still set to be $M$. 
-%In other words, with this manipulation on its individual connectivity degree, every CR node in the network will be involved in the clustering process, the proof will be given later.
+After a CR node, say $i$, receives notification that there is a new cluster head in its neighborhood, $i$ sets its individual connectivity degree to a positive number $M > |\mathcal{K}| \cdot N$, and broadcasts the new individual connectivity degree.
+When node $i$ is associated with multiple clusters, \ie $i$ has received multiple notifications from different cluster heads, $d_i$ is still set to be $M$. 
 The manipulation of the individual connectivity degree of the cluster members accelerates the decision on the cluster heads.
-%, which enables the nodes which are outside of the cluster can possibly become cluster heads or can also be included into other clusters.
-%We have the following theorem to show that when there is no one secondary which shares no CC with any other secondary users, \ie
-%all secondary users' individual connectivity degrees are greater than zero, then every secondary user will eventually be either integrated into a certain cluster, or becomes a cluster head.
 
@@
 \label{ross_p1_guarantee_ccc}
-%After deciding itself being cluster head, CR node broadcasts to notify its neighbours on the dedicated control channel, meanwhile, $i$'s initial cluster is formed immediately, which is $i$'s neighbourhood except for those nodes which have become cluster heads, \ie $C_i=(\text{Nb}_i\setminus \text{CHs})\cup i$.
 After executing Algorithm~\ref{alg0}, certain formed clusters may not possess any CCs.
-As decreasing cluster size increases the CCs within a cluster, for those clusters having no CCs, certain nodes need to be eliminated to obtain at least one CC.
-The sequence of elimination is performed according to an ascending list of nodes which are sorted by the number of common channels between the nodes and the cluster head. 
-In other words, the cluster member which has the least common channels with the cluster head is excluded first.
-If there are multiple nodes having the same number of common channels with the cluster head, the node whose elimination brings in more common channels will be excluded.
-If this criterion meets a tie, the tie will be broken by deleting the node with smaller node ID.
-It is possible that the cluster head excludes all of its neighbors, resulting in a singleton cluster which is composed by itself.
-%At the end of this procedure every formed cluster has at least one common channel.
-%The pseudo code for cluster head to obtain at least one common channel is shown in Algorithm~\ref{alg_size_control_available_CCC}.
+As decreasing cluster size increases CCs within a cluster, for those clusters without CCs, certain nodes need to be excluded to obtain at least one CC.
+The sequence of removing is performed according to an ascending list of nodes, which are sorted according to the number of common channels between the nodes and the cluster head. 
+In other words, the cluster member which has the least common channels with the cluster head will be removed first.
+When there are multiple nodes having the same amount of common channels with the cluster head, the node whose absence brings in more common channels will be removed.
+If this criterion meets a tie, the tie can be broken by removing the node with smaller node ID.
+It is possible that the cluster head removes all its neighbors before obtaining CCs, which results in a singleton cluster which is composed by itself.
 The pseudo code for this procedure is shown in Algorithm~\ref{alg_size_control_available_CCC}.
-As for the nodes which are eliminated from a cluster, they restore their original individual connectivity degrees, then execute Algorithm~\ref{alg0} and become either cluster heads or get included into other clusters afterwards according to Theorem~\ref{clustering:theorem}.
+As for the nodes which are removed from a cluster, they restore their original individual connectivity degrees, then execute Algorithm~\ref{alg0} and become either cluster heads or get included into other clusters afterwards according to Theorem~\ref{clustering:theorem}.
 
@@
 
-%In this subsection, we illustrate the pressing necessity to control the cluster size when CRN becomes denser.
-%
-%We consider a cluster $C(i)$ where $i$ is the cluster head in a dense CRN. 
-%To make the analysis easier, we assume there is no cluster heads which are generated within $i$'s neighborhood during the procedure of guaranteeing CCs.
-%Assuming the CR users and PUs are evenly distributed and PUs occupy the licensed channels randomly, then both CR nodes density and channel availability in the CRN can be seen to be spatially homogeneous.
-%In this case the formed clusters are decided by the transmission range and network density.
-%According to Algorithm~\ref{alg0}, the nearest cluster heads could locate just outside node $i$'s transmission range.
-%%
-%An instance of this situation is shown in Figure~\ref{clusters_denseNetwork}.
-%In the figure, black dots represent cluster heads, the circles denote the transmission ranges of cluster heads.
-%Cluster members are not shown in the figure.
-%%Circles represent the transmission range of cluster head, within which CR nodes are absorbed in cluster.
-%\begin{figure}[h!]
-%  \centering
-%  \includegraphics[width=0.3\linewidth]{clusters_denseNetwork_2.pdf}
-%  \caption{Clusters formation in extremely dense CRN. Black dots are cluster heads, cluster members are not drawn.}
-%  \label{clusters_denseNetwork}
-%\end{figure}
-%Let $l$ be the length of side of simulation plan square, and $r$ be CR's transmission radius.
-%Based on the aforementioned analysis and geometry illustration as shown in Figure~\ref{clusters_denseNetwork}, we give an estimate on the maximum number of generated clusters, which is the product of the number of cluster heads in one row and that number in one line, $l/r * l/r = l^2/r^2$.
-%%Now we verify the estimation with simulation.
-%%We distribute CR and primary users randomly on a square plain, $r$=10 and $l$=50.
-%%Network density is increased by adding more CR users.
-%%We now have a look at how does the network density affect the cluster size when the transmission range is constant.
-%%This implicates when the cluster size is decided by the density of the network.
-%%As to SOC, the membership of one cluster is decided after a complex process, and the cluster size is roughly the same with one neighborhood.xxxx
-%%We can see from the example that although two neighbouring clusters can overlap greatly with each other, no cluster head will be covered by other clusters.
-%Given $r$=10 and $l$=50, the maximum number of clusters is 25.
-%The number of clusters in the simulation is shown in Figure~\ref{number_clusters_scale}.
-%Simulation is run for 50 times and the confidence interval is 95\%.
-%With the increase of CR users, network density (the average number of neighbours) increases linearly, and the number of clusters approaches to 25 which complies with the estimation.
-%
-%\begin{figure}[h]
-%  \centering
-%  \includegraphics[width=0.7\linewidth]{number_clusters_upperBound.pdf}
-%  \caption{The correlation between the number of formed clusters and network density.}
-%  \label{number_clusters_scale}
-%\end{figure}
-It is necessary to control the cluster size when CRN becomes denser.
-Both analysis and simulation~\cite{2017arXiv170404828L} show that when applying ROSS, after the clusters are saturated with the increase of network density, the cluster size increases linearly with the network density, thus certain measures are needed to curb this problem.
-This task falls upon the cluster heads.
-To control the cluster size, cluster heads prune their cluster members to reach the desired cluster size.
+Both analysis and simulation~\cite{2017arXiv170404828L} show that with ROSS, when network density increases to a certain level, the number of formed clusters becomes constant.
+This means if the network density keeps on increasing, the cluster size increases linearly with the network density.
+Thus It is necessary to control the cluster size when CRN becomes denser, and this task falls upon the cluster heads.
+
+To control the cluster size, cluster heads remove their cluster members when cluster sizes are larger than a threshold.
+The threshold should be larger than the desired size $\delta$, because there are overlaps between neighboring clusters.
 The desired size $\delta$ is decided based on the capability of the CR users and the tasks to be conveyed.
-As there are overlaps between neighboring clusters, the sizes of the clusters formed in this phase are larger than that of the finally formed clusters.
-Hence, a cluster head excludes some cluster members when the cluster size exceeds a certain threshold.
-We set the threshold as $t\cdot \delta$, where $\delta$ is the desired cluster size.
-The constant parameter $t$ is usually larger than 1 and is dependent on the network density and CR nodes' transmission range, in particular, $t$ is between 1 and the ratio between the average neighborhood size and the desired size.
-%A smaller or bigger $t$ may lead to more clusters with smaller or larger size than $\delta$.
+%Hence, a cluster head excludes some cluster members when the cluster size exceeds a certain threshold.
+We set the threshold as $t\cdot \delta$, where the constant parameter $t$ is dependent on the network density and CR nodes' transmission range.
+We adopt $t$ to be between 1 and the ratio of the average neighborhood size and desired size.
 	When $t$ is smaller, \eg $t=1$, the formed cluster in the phase I will be $\delta$.
-	For the cluster whose members are included by other clusters, the size of this cluster will be smaller than $\delta$ after the membership clarification phase.
+	For the cluster whose members are included by other clusters, the size of this cluster will be smaller than $\delta$ after the following membership clarification phase.
 	If $t$ is chosen large, \eg $t\cdot\delta$ equals to the size of neighborhood, the mechanism of adjusting the cluster size will not work any more.
 
-Because of $t$, the threshold to prune is larger than the desired size, then there will be some nodes choosing to affiliate with other clusters in the following phases.
+%Because of $t$, the threshold to prune is larger than the desired size, then there will be some nodes choosing to affiliate with other clusters in the following phases.
 %C1-7
-In particular, the cluster head removes the cluster members sequentially according to the following principle, the absence of one cluster member leads to the maximum increase of the CCs within the cluster.
+The cluster head removes the cluster members sequentially according to the following principle, the absence of one cluster member leads to the maximum increase of CCs in the cluster.
+The removed nodes restore their original individual connectivity degrees.
 This process ends when each cluster's size is smaller or equal to $t \cdot\delta$.
@@
 %%%%%%%%%%%%%%%
-We have the following lemma to show that every secondary user will eventually be either integrated into a certain cluster or becomes a cluster head.
+We have the following lemma to show every secondary user will eventually be either integrated into a cluster or becomes a cluster head.
 
@@
 
-%Here, by \textit{step} we mean Algorithm~\ref{clustering:theorem} is executed by a secondary user for one time.
-%In one special scenario, \eg when a cluster head is elected and all the other nodes are within its neighborhood, the number of steps is 1.
 The Proof is given in Appendix~\ref{proof_clustering:lemma1}.
-%The proof also illustrates the maximal time needed to conduct Algorithm~\ref{clustering:theorem}. 
-%Consider an extreme scenario, where all the secondary nodes sequentially execute Algorithm~\ref{alg0}, \ie they constitute a chain as discussed in the example in the proof.
-%
-%Assuming there is a token in the CRN, one node is allowed to execute Algorithm~\ref{alg0} only when it holds the token, and it then transfers the token to the neighboring node on the chain.
-%If one step can be finished within a certain time span $T$, then the total time needed for the network to conduct Algorithm~\ref{clustering:theorem} is $N*T$.
 %C1-6
@@
 \begin{proof}
-A secondary node becomes cluster head when its \textit{individual connectivity degree} is smaller than all its neighbors.
-Afterwards, the \textit{individual connectivity degree} of its neighbors becomes $M$ and has no means to decrease, thus the cluster head will remain to be cluster head.
-As to the node which is excluded form a cluster due to guaranteeing CC or size control, its \textit{individual connectivity degree} is restored, but it will not include its former cluster head, even if it becomes cluster head as regulated in~\ref{alg0}.
+A secondary node, say $i$, becomes cluster head when its \textit{individual connectivity degree} is smaller than any of its neighbors.
+Afterwards, the \textit{individual connectivity degrees} of its neighbors becomes $M$.
+%If all the neighbors stay in the cluster, the cluster head will remain to be cluster head.
+If certain nodes are removed from the cluster due to guaranteeing CC or size control, these nodes may become either cluster members of another cluster head, or cluster heads themselves.
+In both cases, $i$'s \textit{individual connectivity degrees} is still smaller than these nodes.
+Note that when the removed node becomes cluster head, it will not include its former cluster head $i$, so that $i$ doesn't become cluster member and its \textit{individual connectivity degrees} doesn't change.
 \end{proof}
-
-%According to Theorem~\ref{clustering:theorem}, Phase I completes within a reasonable amount of time.
-%
-%This judgement is conducted periodically, and phase I ends after every node ascertains it is cluster head or not.
 
@@
 \label{clustering:theorem}
-Assuming the time for a secondary user to update the information about cluster heads in its neighborhood is $T$, then it takes at most $N*T $ time to finish the process of cluster head selection and initial cluster formation.
+Assuming the time for a secondary user to update the information about cluster heads in its neighborhood is $T$, then it takes at most $N*T $ to finish the process of cluster head selection and initial cluster formation.
 \end{theorem}
-Phase I ends when no more secondary users are becoming cluster head.
-Based on~\ref{clustering:lemma1} and~\ref{clustering:lemma3}, the theorem is proved.
+Phase I ends when no more secondary users become cluster heads.
+Based on Lemma~\ref{clustering:lemma1} and Lemma~\ref{clustering:lemma3}, the theorem is proved.
 
 As Algorithm~\ref{alg0} is executed concurrently by different secondary users, the required time can be considerably reduced.
-If we apply Algorithm~\ref{alg0} to the example shown in Figure~\ref{fig1}, the outcome is shown in Figure~\ref{fig2}.
+If we apply Algorithm~\ref{alg0} to the CRN in Figure~\ref{fig1}, the outcome can be found in Figure~\ref{fig2}.
 Node $B$ and $H$ have the same individual connectivity degree, i.e., $d_B=d_H$. As $g_H=2>g_B=1$, node $H$ becomes the cluster head and cluster $C(H)$ is $\{H, B, A, G\}$.
@@
 %\subsubsection*{Problem Description}
-As to the example CRN shown in Figure~\ref{fig1}, the resulted clusters are shown in Figure~\ref{fig2} after running phase I of ROSS.
-We notice that nodes $A, B, D$ are included in more than one cluster. 
+As to the resulted clusters shown in Figure~\ref{fig2} after running phase I of ROSS, we notice that nodes $A, B, D$ are included in more than one cluster. 
 We refer to these nodes as \textit{debatable nodes} as their cluster affiliations are not decided.
 The clusters which include the debatable node $i$ are called \textit{claiming clusters} of node $i$, and the set of these clusters is denoted as $S_i$.  
-%Actually, debatable nodes extensively exist in CRN with larger scale.
-The debatable nodes which are generated from the first phase of ROSS should be exclusively associated with only one cluster and be removed from the other claiming clusters, this procedure is called \textit{cluster membership clarification}.
-
-%In particular, the un-affiliation of one debatable nodes from a cluster increasing the set $K_C$ of ICCs of cluster $C$ (at the cost of potentially decreasing $R_C$, the set of OCCs).
-
-%\newtheorem{observation}{Observation}
-%\label{observation}
-%\begin{observation}
-%If the number of nodes within a cluster decreases, the number of common channels will increase or keep constant.
-%\end{observation}
-%
-%\begin{proof}
-%Contradiction, To be continued
-%\end{proof}
-%From observation 1 we know that the procedure of membership clarification will increase the set of common channels for some clusters and accordingly strengthen the robustness of intra connectivity.
-
-% % % % %	dependancy!
-%An debatable node belongs to multiple clusters, and in the same time, it is possible that several debatable CR nodes locate within one same cluster.
-%Each debatable node tries to increase the sum of ICC of the clusters which it belong to.
-More specifically,
-%For a debatable node $i\in S_i$ after phase I, as to clarify its membership, it will choose one cluster $C\in S_i$ to stay and withdraw from the other clusters in $S_i$ with the consideration of increasing ICCs within $S_i$ by the largest margin.
+The debatable nodes should be exclusively associated with only one cluster and be removed from the other claiming clusters, this procedure is called \textit{cluster membership clarification}.
 
 \subsubsection{Distributed Greedy Algorithm (DGA)}
-%Debatable node $i$ is aware of all its claiming clusters in $S_i$. 
-Assuming a debatable node $i$ which needs to decide one cluster $C\in S_i$ to stay and leaves the other clusters in $S_i$, then the principle for $i$ is its decision should result in the greatest increase of CCs in all its claiming clusters.
-As node $i$ has been notified of the spectrum availability on all the nodes in each claiming cluster, node $i$ is able to calculate how many more CCs will be produced in a claiming cluster if $i$ leaves that cluster.
-%Based on this calculation, $i$ decides on one claiming cluster to stay and leaves the other claiming clusters.
+When a debatable node $i$ decides one cluster $C\in S_i$ to stay and leaves the other its claiming clusters, the principle for $i$ is that its move should result in the greatest increase of CCs in all its claiming clusters.
+As node $i$ has been notified of the spectrum availability on all the nodes in each claiming cluster, node $i$ is able to calculate how many more CCs can be produced in a claiming cluster if $i$ leaves that cluster.
 Then node $i$ decides on the cluster $C\in S_i$, if $i$ leaving cluster $C$ results in less increased CCs than leaving any other claiming clusters in $S_i$.
@@
 When there comes a tie between two claiming clusters, $i$ chooses to stay in the cluster whose cluster head shares the most CCs with $i$.
-When the tie still exists, node $i$ chooses to stay in the claiming cluster which has the smallest size.
-Node IDs of cluster heads will be used to break tie if all the previous metrics could not decide on the unique claiming cluster for $i$ to stay.
+When a tie still exists, node $i$ chooses to stay in the claiming cluster which has the smallest size.
+Node IDs of cluster heads will be used to break tie in the end if necessary.
 The pseudo code of this algorithm is given in Algorithm~\ref{alg4}.
-%To conduct Algorithm~\ref{alg4}, debatable node $i$ needs to know the necessary information about its claiming clusters, \ie $K(C)$ (the set of available channels in cluster $C$), $K(h_C)$ (the set of available channels on $C$'s cluster head $h_C$) and $|C|, C\in S_i$ (sizes of $i$'s claiming clusters).
 After deciding its membership, debatable node $i$ notifies all its claiming clusters of its choice, and the claiming clusters from which node $i$ leaves also broadcast their new cluster composition and the spectrum availability on all their cluster members.
@@
 The autonomous decisions made by the debatable CR nodes raise the concern on the endless chain effect in the membership clarification phase.
-A debatable node's choice is dependent on the compositions of its claiming clusters, which can be changed by other debatable nodes' decisions.
-As a result, the debatable node which makes decision first may change its original choice, and this process may go on forever.
+A debatable node's choice is dependent on the compositions of its claiming clusters, and the members of these claiming clusters can be changed by other debatable nodes' moves.
+As a result, the debatable node which have made decision may not be content with its original move.
+There is concern that this process may go on forever.
 To erase this concern, we formulate the process of membership clarification into a game, where a equilibrium is reached after a finite number of best response updates made by the debatable nodes.
-
-%%  update their choices based on other debatable nodes' choices, and this process 
-%%%thesis needs1
-%For example, assuming one debatable node $i$ locates in cluster $C\in S_i$, and $C$ has more than one debatable node except for $i$.
-%Assuming node $i$ decides to stay in cluster $C$, then one another debatable nodes $j$ decides its affiliation, and there is $j\in C\in S_i$.
-%$j$'s move decreases cluster $C$'s size, and could possibly trigger node $i$ to alter its previous decision to leave $C$, as $C$'s size is smaller now and leaving it may result in more increase of CCs in $S_i$.
-%At this point of time, debatable node $j$ may rejoin cluster $C$ due to the changes in $S_j$, then both node $i$ and $j$ face the \textit{same} situation again.
-%%\footnote{Actually it is not totally same as before, as there are some new changes within $S_j$.}
-%%To maximize the increase of common channel in clusters in $S_j$, $j$ either stays in $C$, or leaves cluster $C$ and stay another cluster in $S_j$.
-%%$j$'s decision changes $C$'s membership, which will affect $i$'s decision.
-%%Assume $i$ makes decision before $j$ and chooses to stay in $C$, as which brings the most common channels in $i$' claiming clusters, and then it is $j$' turn to choose cluster.
-%%If $j$ leaves $C$, the smaller cluster $C$ will possibly make $i$ to leave it and join another cluster.
-%%and the choice of $j$ to stay in $C$ or not possibly changes $C$'s membership and  which potentially further triggers node $i$ to alter its previous decision. 
-%Thence, we need to answer this concern before implementing ROSS-DGA.
-%%, and if it converges, how good such a distributed scheme performs.
 
@@
 The relation between the debatable nodes and the claiming clusters is shown in Figure~\ref{debatable_nodes_claiming_cluster}.
-%The concern on convergence appears again as we have discussed in the previous subsubsection.
-%We give proof on convergence under game theoretic framework.
+
 \begin{figure}[ht!]
@@
 
-%In the following we will introduce an \textit{server matching}~\cite{kothari:congestion_serverMatching} problem to illustrate congestion game's application in communication systems.
-
 In the following, we show that the decision of debatable nodes to clarify their membership can be mapped to the behaviour of the players in a \textit{player-specific singleton congestion game} when proper cost function is given.
 The game to be constructed is represented with a 4-tuple $\Gamma=(\mathcal{P},\mathcal{R},\sum_{i, i \in \mathcal{P}}, f)$ with the following elements:
-%To make the model of this game more clear, we make some change to our original problem.
-Previously, the nodes in overlapping areas belong to more than one cluster, and our scheme is to remove them out of some clusters to increase the set of common channels within the cluster form which the mode leave.
-In the new model, we assume all the nodes in overlapping nodes don't belong any cluster and the problem become into how do these nodes decide which cluster to join.
-
-%The components of the game are listed as follows,
 
 \begin{itemize}
-%	\item $\mathcal{D}=\left\{1,\ldots,n\right\}$, the set of players (debatable nodes).
 	\item $\mathcal{P}$, the set of players in the game, which are the debatable nodes in our problem.
-%	\item $\mathcal{R}=\left\{1,\ldots,m\right\}$, the set of resources which player can choose, which are all the clusters in our model.
 	\item $\mathcal{R} = \cup S_i, i\in \mathcal{P}$, the set of the resources for players to choose.
@@
 	As debatable node $i$ is supposed to choose only one claiming cluster, then only one piece of resource will be allocated to $i$.%, accordingly this congestion game is a singleton game.
-	%when $i$ makes decision, only one resource (one claiming cluster) from the allowed resources is allocated.
-
-	%\item We denote by $\mathcal{S}=\left(\mathcal{S}_1,\ldots,\mathcal{S}_n\right)\in \sum_1\times \cdots\times\sum_n$ the state of game where player $i$ plays strategy $\mathcal{S}_i\in \Sigma_i$.
-
-	\item %For the clusters which are possible destination of debatable nodes, the decrease of common channels caused by different debatable node' join can be different because of the heterogeneity of channel availability within itself and on the debatable nodes.
-%furthermore, the sequence of debatable node's join can also alter the decrease.
-	The utility (cost) function $f(C)$ as to a resource $C$. 
+	\item 	The cost function $f(C)$ as to a resource $C$. 
 	$f(C) = \Delta\vert K^i(C)|, C\in S_i$, which represents the decreased number of CCs in cluster $C$ when debatable node $i$ joins $C$.
-	As to cluster $C\in S_i$, the decrease of CCs caused by including the debatable nodes is $\sum_{i:C\in S_i, i\rightarrow C} \Delta\vert K^i(C) \vert$. 
+	As to cluster $C\in S_i$, the decrease of CCs caused by accepting the debatable nodes is $\sum_{i:C\in S_i, i\rightarrow C} \Delta\vert K^i(C) \vert$. 
 $i\rightarrow C$ means $i$ joins cluster $C$.
@@
 
-The utility function $f$ is not purely decided by the number of players accessing the resource (debatable nodes join claiming clusters), which happens in a canonical congestion game.
-The reason is in this game the channel availability on debatable nodes is different.
-Given two same groups of debatable nodes and their sizes are the same, when the nodes are not completely the same (neither are the channel availabilities on these nodes), the cost happened on one claiming cluster could be different if the two groups of debatable nodes join that cluster respectively.
-%In a canonical congestion game, the cost (or pay off) is function of only the number of players occupying the resource, and is mono-
-%In this new game, the cost function 
+When the utility function is decided purely by the amount of players accessing the resource, the game is a canonical congestion game~\cite{Ackermann06purenash}.
+In our game, as the channel availability on debatable nodes (players) is different, the loss of CCs (cost) caused by a debatable node could also be different.
+%For example, given two same groups of debatable nodes and their sizes are the same, when the nodes are not completely the same (neither are the channel availabilities on these nodes), the cost happened on one claiming cluster could be different if the two groups of debatable nodes join that cluster respectively.
 Hence, this congestion game is player specific~\cite{Ackermann06purenash}.
@@
 In fact, the upper bound for the number of steps which are involved in this process is much smaller than $N^3$.
-The percentage of debatable nodes in the network is shown in Figure~\ref{percentage_overlapping_node}, which is between 10\% to 60\% of the total CR nodes in the network.
+The percentage of debatable nodes in the network is shown in Figure~\ref{percentage_overlapping_node}, which is between 10\% to 60\%.
 On the other hand, the number of clusters heads is dependent on the network density and the CR node's transmission range as mentioned in Section~\ref{phaseI}.
-The simulation in \cite{robust_clustering_arxiv} shows the cluster heads are only 3.4\% to 20\% of the total CR nodes.
-
-%and the number of steps towards \textit{Nash Equilibrium} is upper-bounded\footnote{Here we present this with modifying the original conclusion in \cite{Ackermann06purenash} according to our model.} by $ n^2\cdot m $.
-In our context, $n$ is the number of debatable nodes, $m$ is number of clusters in CRN, %$rk(\Gamma)$ of the matroid  is the cardinality of the maximal independent sets, which is 1 in the case of singleton game,
-%so the total time complexity to achieve the \textit{Nash Equilibrium} using greedy approach is 	.
-%%(XXX Just mention after this complexity result the relationship to the system mdeol XX)
-%This is upper-bounded (in the worst case) by $O(\vert I\vert^3)$. 
-%Based on above model and analysis, phase II converges is Algorithm~\ref{alg4} is run by debatable nodes. 
-%Although the game version of DGA can achieve \textit{Nash Equilibrium}, the whole scheme can possibly obtain sub-optimal result.
-%, furthermore,this stable state is a local minimum of the global decrease function.
-%\todo[inline]{The number of steps, or the upper bound of steps in convergence needs a formal proof}
+The simulation in \cite{robust_clustering_arxiv} shows the cluster heads account for from 3.4\% to 20\% of the total CR nodes with the increase of network density.
+Furthermore, as the game played locally and in parallel \ie a debatable node can only interact with a few claiming clusters, which greatly accelerates the execution speed.
 
 \subsubsection{Distributed Fast Algorithm (DFA)}
-%The convergence speed of DGA is large recalling that the number of steps is of $\mathcal{O}(N^3)$.
 On the basis of ROSS-DGA, we propose a faster version ROSS-DFA which differs from ROSS-DGA in the second phase.
@@
 \end{figure}
-
-\begin{comment}
-As an example, when node A comes to decide which cluster to stay, the memberships of relevant clusters, like $C_C$ and $C_H$, are $\{C,B,D,A\}$ and $\{H,B,G,A\}$ respectively.
-Before the other two debatable nodes B and D making their belonging clear, cluster $C_C$ and $C_H$ have them in the same time.
-So node A can decide which cluster to belong to without considering other debatable nodes' action.
-There are two strategies for node A, which is illustrated in Figure \ref{fig3}.
-Because staying in cluster $C_C$ brings in more common channels within relevant clusters, node A finally choose cluster $C_C$ to stay and caveat from cluster $C_H$.
-The membership of $C_H$ is updated in the same time.
-Node B and D undertake the same process and the clusters are formed finally as Figure \ref{fig4} shows.
-
-Because debatable nodes can conduct membership clarification abased on static membership information of relevant clusters, thus no iteration happens in this process.
-The time complexity of this algorithm is only decided by the number of debatable nodes, which is maximal $O(\vert I\vert)$.
-
-As an example, when node A comes to decide which cluster to stay, the memberships of relevant clusters, like $C_C$ and $C_H$, are $\{C,B,D,A\}$ and $\{H,B,G,A\}$ respectively.
-Before the other two debatable nodes B and D making their belonging clear, cluster $C_C$ and $C_H$ have them in the same time.
-So node A can decide which cluster to belong to without considering other debatable nodes' action.
-Figure \ref{AinC}.
-Because staying in cluster $C_C$ brings in more common channels within relevant clusters, node A finally choose cluster $C_C$ to stay and retreat from cluster $C_H$.
-The membership of $C_H$ is updated in the same time.
-Node B and D undertake the same process and the clusters are formed finally as Figure \ref{final_clustering_ross} shows.
-\end{comment}
 

### 2017-11-25 journal-draft/ettdoc_JG.tex
add ettdoc_JG

--- 2017-11-21 journal-draft/ettdoc.tex
@@
 \begin{abstract}
-Cluster structure in cognitive radio networks facilitates cooperative spectrum sensing, routing and other functionalities.
-Unlicensed channels, which are temporally available for a group of cognitive radio users in one area, consolidate the group into a cluster.
-More available unlicensed channels in a cluster make the cluster more likely to uphold against the licensed users' influence, making clusters more robust.
-This paper analyses the problem of how to form robust clusters in a cognitive radio network such that cognitive radio systems benefit from collaboration within clusters despite intense primary user activity.
-%In the process of forming clusters, every secondary user decides with whom to form a cluster, or which cluster to join.
-We give a formal description of the robust clustering problem, prove it to be NP-hard and propose both centralized and distributed solutions.
-The congestion game model is adopted to analyze the process of cluster formation, which not only contributes to the design of the distributed clustering scheme, but also provides a guarantee on the convergence to a Nash equilibrium and the convergence speed.
-%Our proposed clustering solution is versatile to fulfill some other requirements such as faster convergence and cluster size control.
-The proposed distributed clustering scheme outperforms state-of-the-art related works in terms of cluster robustness, convergence speed and overhead.
-%Besides, we prove the clustering problem is NP-hard, and also propose the centralized solution.
-Extensive simulations are presented supporting the theoretical claims.
+%Cluster structure in cognitive radio networks facilitates cooperative spectrum sensing, routing and other functionalities.
+%Unlicensed channels, which are temporally available for a group of cognitive radio users in one area, consolidate the group into a cluster.
+%More available unlicensed channels in a cluster make the cluster more likely to uphold against the licensed users' influence, making clusters more robust.
+%This paper analyses the problem of how to form robust clusters in a cognitive radio network such that cognitive radio systems benefit from collaboration within clusters despite intense primary user activity.
+%%In the process of forming clusters, every secondary user decides with whom to form a cluster, or which cluster to join.
+%We give a formal description of the robust clustering problem, prove it to be NP-hard and propose both centralized and distributed solutions.
+%The congestion game model is adopted to analyze the process of cluster formation, which not only contributes to the design of the distributed clustering scheme, but also provides a guarantee on the convergence to a Nash equilibrium and the convergence speed.
+%%Our proposed clustering solution is versatile to fulfill some other requirements such as faster convergence and cluster size control.
+%The proposed distributed clustering scheme outperforms state-of-the-art related works in terms of cluster robustness, convergence speed and overhead.
+%%Besides, we prove the clustering problem is NP-hard, and also propose the centralized solution.
+%Extensive simulations are presented supporting the theoretical claims.
 \end{abstract}
@@
 \label{intro}
-%CR concept
-Cognitive radio (CR) is a promising technology to solve the spectrum scarcity problem for the upcomging era of internet of things~\cite{Mitola, Rawat20161}.
-Licensed users access the spectrum allocated to them whenever there is information to be transmitted.
-In contrast, as one way, unlicensed users can access the spectrum via opportunistic spectrum access, \ie they access the licensed spectrum only after validating the channel is unoccupied by licensed users, where spectrum sensing~\cite{sensing_survey_2009} plays an important role in this process.
-In this hierarchical spectrum access model~\cite{zhao_survey_DSA_2007}, the licensed users are also called primary users (PU), while the unlicensed users are referred to as secondary users and constitute a so called cognitive radio network (CRN).
-%cluster
-For CRN, accurate spectrum sensing is critical, and the rate of false negative \ie misdetecting the active primary users, should be minimized~\cite{Sahai_FundamentalDesignTradeoffs2006}.
-Cooperative spectrum sensing, which relies on the consensus of CR users within a certain area\footnote{The terms user and node appear interchangeably in this paper.
-In particular, user is adopted when its networking or cognitive ability are discussed or stressed, while we refer to nodes typicallly in the context of the network topology.}, has been shown to improve spectrum sensing accuracy with the presence of noise uncertainty and channel fading~\cite{Jacob2012, coorperativeSensing_Akyildiz11}.
-%C3
-In this regard, clustering is regarded as an effective method to realize cooperative spectrum sensing~\cite{Sun07_clustering_spectrum_secsing}.
-% ... decreases considerably the negative probability due to the random channel effects like fading and shadowing.
-
-Clustering is the process of grouping certain users in geographic proximity into a collective.
-% and as an effective technique, it is proposed with the emergence of mobile wireless networks~\cite{gerla_97} and there has been a plethora of clustering schemes.
-As to wireless networks where no restriction is imposed on nodes to access the spectrum, \ie 
-wireless ad-hoc, mesh networks and sensor networks, clustering the network helps to decrease the transmission power consumption~\cite{Kawadia03},  improve the routing performance~\cite{clustering_mesh_globecom2010}, or imrove the network lifetime and coverage~\cite{Abbasi_survey_07}.
-%In CRN, clusters are formed in the very beginning of the network operation, and re-formed periodically according to the dynamics of the CRN.
-For cognitive radio netowrks, the formed clusters help the participating nodes improve spectrum sensing accuracy.
-Besides, clusters benefit channel switching when primary users are detected by at least one secondary user in that cluster, then all the cluster members can stop payload transmissions swiftly and vacate the operating channel ~\cite{willkomm08}.
-Clustering also benefits the operation of a CRN by reducing the interference between cognitive clusters~\cite{centralizedSharing80222}, and supporting routing~\cite{Abbasi_survey_07}.
-%As to the coexistence of CR users, they can be notified by cluster head (CH) or other cluster members about the possible collision, the possibility for them to interfere neighbouring clusters is reduced~\cite{centralizedSharing80222}.
-%Except for benefiting the dynamic spectrum sharing in CRN, clustering contributes to the other wireless networks in many aspects~\cite{Kawadia03, clustering_mesh_globecom2010, Abbasi_survey_07}.
-
-In CRN, a formed cluster seizes one or multiple unlicensed channels which are available for every CR node in that cluster.
-In this paper available unlicensed channels are called \textit{common licensed channels} (or common channels for short, which is abbreviated as CC).
-The availability of CCs within a cluster decides the existence of that cluster, \ie if no CCs are available then the corresponding cluster does not exist.
-In a cluster, both payload and control overheads can be transmitted on the CCs.
-When one or several cluster members can not access a certain CC because primary user's activity is detected on that channel, the channel will be excluded from the set of CCs.
-In particular, if that channel is being used for payload communication, the communication pair will stop and resume transmission on another available CC.
-The activity of primary users is usually unknown to the secondary users, thus deemed as random to secondary users.
-Consequently, a cluster which secures more CCs will be more robust to random primary user activities and anticipate a longer life expectancy. 
-In this paper, the robustness of clusters is their ability to uphold with the influence of active primary users.
-The robust clustering enables more secondary users to reside in the resulting clusters when the available spectrum becomes scarcer.
-%
-
-%As long as there is a CC available, the corresponding cluster can continue to exchange payload data.
-
-Cluster size is inherently correlated with the cluster robustness.
-Given a CRN, it is obvious that getting rid of certain secondary users from a cluster may yield more CCs.
-However, this contradicts to one of the motivations of clustering, \ie the cooperative decision making, where in general more users result in more accurate sensing results~\cite{Consensus_based_clustering12}.
-Thus the number of small clusters, especially the \textit{singleton clusters}, \ie the cluster which has only one CR node, should be minimized.
-On the other hand, as to the cluster which consists of many nodes, although the spectrum sensing is benefited, there is usually only a small number of CCs.
-Thus big cluster undermines the robustness of the cluster against primary users' activity.
-Thus, the cluster robustness discussed in terms of number of CCs carries little meaning when the sizes of formed clusters are not considered.
-Cluster size also plays a role in transmission power consumption, \ie cluster size affects the transmission power consumption when routing is conducted~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
-
-In this paper robust clustering in CRN is analyzed as a mathematical problem and proved to be NP-hard, then both centralized and distributed schemes are proposed.
+Cognitive radio (CR) is a promising approach to mitigate the increasing scarcity of radio spectrum~\cite{Mitola} arising from the common practice to license radio frequencies in a de-facto exclusive manner.
+In CR, licensed users can access the spectrum allocated to them at any point in time, while unlicensed users may access the spectrum when it is not utilized. 
+This can be realized by so-called opportunistic spectrum access, \ie unlicensed users access the spectrum only after validating that the channel is currently unoccupied.
+In the context of cognitive radio, licensed users are also called primary users (PU), while unlicensed users are often referred to as secondary users and constitute a cognitive radio network (CRN)\footnote{The terms user and node appear interchangeably in this paper.
+In particular, user is adopted when its networking or cognitive ability are discussed or stressed, while we refer to nodes typically in the context of the network topology.}.
+For CRN, accurate spectrum sensing is critical, and the rate of false negatives, \ie the likelihood of misdetecting active primary users, needs to be minimized~\cite{Sahai_FundamentalDesignTradeoffs2006}.
+It has been shown that cooperative spectrum sensing, which relies on the consensus of CR users within a certain area, can significantly decrease the rate of false negatives despite the presence of receiver noise and wireless channel fading~\cite{Jacob2012, coorperativeSensing_Akyildiz11}.
+Thus, clustering of secondary nodes is regarded as a necessary condition to realize cooperative spectrum sensing~\cite{Sun07_clustering_spectrum_secsing} for opportunistic spectrum access.
+
+Clustering is the process of logically grouping certain users in geographic proximity.
+As to wireless networking in general, and in particular with respect to wireless ad-hoc, mesh or sensor networks, clustering is known to decrease the power consumption~\cite{Kawadia03},  improve routing performance~\cite{clustering_mesh_globecom2010}, and improve the network lifetime and coverage~\cite{Abbasi_survey_07}.
+For cognitive radio networks, apart from improving the sensing accuracy, clustering also improves spectrum utilization among several cognitive radio networks by allowing for coordination in particular when CRNs have to vacate channels~\cite{willkomm08}, while also been known for reducing the interference between cognitive clusters~\cite{centralizedSharing80222}, and improving routing~\cite{Abbasi_survey_07}.
+
+In CRNs, formed clusters maintain a set of unlicensed channels which are validated by every CR node in that cluster, meaning that the channel is perceived as not been occupied by a primary user.
+In the following we refer to these maintained unlicensed channels as \textit{common channels} (CC).
+The availability of CCs within a cluster is elementary for the cluster, \ie if no CCs are available then the corresponding cluster can not operate any longer as CCs ascertain both control and payload data transmission within the cluster.
+However, due to primary user activity, over time the list of maintained CCs of a cluster varies randomly as it is generally unknown to secondary nodes when primary users appear on different licensed channels.
+Being able to maintain a sufficiently large list of CCs ensures the \textit{robustness} of the cluster despite primary user activity, i.e. it provides a longer uninterrupted operation of the cluster.
+
+On the other hand, the larger the cluster size is, the lower is in general the set of CCs that all nodes of a cluster observe as unoccupied by primary users.
+This is due to the fact that in general, secondary nodes at different spatial locations will be able to sense the activity of different primary users due to different channel characteristics. 
+Thus, a trade-off arises for the formation of robust cognitive radio clusters:
+On the one hand, a low number of nodes in a cluster is desirable, as it generally provides more nodes with a common observation of primary user activity on different channels, and thus leads to a larger set of CCs, ultimately increasing the robustness.
+On the other hand, a too low number of nodes in a cluster compromises the sensing accuracy, in particular if only one or two nodes are members of a cluster~\cite{Consensus_based_clustering12}.
+One therefore needs to strike a balance between the \textit{size} of a cluster and the \textit{number} of common channels per cluster, to balance robustness and sensing accuracy.
+Cluster size plays furthermore a role in transmit power consumption, \ie the cluster size affects the transmit power consumption under certain routing schemes~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
+
+In this paper, we analytically study the above mentioned trade-off which we term in the following the \textit{CRN robust clustering problem}.
+We show it to be an NP-hard problem under certain assumptions, and furthermore study centralized as well as distributed algorithms.
 We propose an alternate metric to measure cluster robustness in contrast to previous works~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
-We claim cluster robustness can not be indicated merely by the average number of CCs of clusters, but by the ability of the clusters to uphold when the primary users' activity becomes more active.
-In this paper, we identify the robustness of clusters by the number of unclustered CR nodes.
-We also consider the necessity of cluster size control and its influence on cluster robustness.
-The propsoed distributed schemes extend our previous work ROSS (Robust Spectrum Sharing)~\cite{Li11_ROSS} by involving cluster size control.
-%Our distributed schemes solve the size divergence problem in clusters as discussed in~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
-%Besides, our proposed distributed schemes are still suitable for the scenario where fast deployment is desired.
-Throughout this paper, we call the proposed distributed schemes the \textit{variants of ROSS}.
-
-%
-%
-The rest of the paper is organized as follows. 
-In section~\ref{related_work}, we introduce the clustering techniques in CRN and those focusing on robustness.
-The relation between this paper and work in~\cite{Li11_ROSS} is elaborated.
-The system model and the robust clustering problem formulation are presented in Section~\ref{sec:model}. 
-The centralized and distributed solutions are introduced in Section~\ref{centralized_solution} and~\ref{ross} respectively.
+We claim that cluster robustness can not be indicated merely by the average number of CCs of a cluster, but by the ability of the cluster to uphold over time despite random primary user activity.
+Our proposed distributed scheme extends our previous work ROSS (Robust Spectrum Sharing)~\cite{Li11_ROSS} by additionally incorporating control over the size of a cluster.
+Throughout this paper, we call the newly proposed distributed schemes \textit{variants of ROSS}.
+%
+%
+The rest of the paper is organized as follows:
+In Section~\ref{related_work}, we review related work in particular with respect to clustering techniques in CRN.
+We also discuss in more detail the relation between the contribution in this paper and our previous work in~\cite{Li11_ROSS}.
+Our system model as well as the problem statement with respect to the robust clustering problem are presented in Section~\ref{sec:model}. 
+The main contribution, the centralized and distributed solutions are introduced in Section~\ref{centralized_solution} and~\ref{ross} respectively.
 %The clustering problem is given through analysis and a centralized scheme is proposed in section~\ref{centralized_scheme}.
-Extensive performance evaluation is given in Section~\ref{performance}.
-Our work is concluded in Section~\ref{conclusion}.
+Extensive performance evaluation is given in Section~\ref{performance} before we conclude our work in Section~\ref{conclusion}.
 
@@
 \label{related_work}
-In the following we give a brief review on the clustering in CRN, with emphasis on the theme of robust clustering.
-%%[crn for clustering] 
-%%due to attenuation of signal propagation, primary users can only be detected by CR users when they locate closely to CR users.
-%In cognitive radio networks, secondary users which locate closely with each other are possibly affected by the same group of primary users, so that the availability of licensed spectrum is similar to them, \ie certain channels are available on each of them.
-%The similarity of available spectrum on a group of neighbouring CR nodes, along with the benefit of collaborative decision among multiple nodes, leads to clustering as an effective approach for many applications.
-%[robustness issue for clustering]
-%%%%%%%%%%%
-%On the other hand, large clusters are not preferred in some scenarios neither, \eg for the CRN composed with resource limited users, managing the cluster members in a large cluster is a substantial burden.
-%Hence, the cluster size should fall in a desired range according to different application scenarios~\cite{Chen04clusteringalgorithms, capacity_cluster_06}.
-%%%%%%%%%%%%
-%with the intention to provide a robust infrastructure for the applications which may be conducted above that in CRN.
-%that being said, when we design this clustering scheme in CRN, we do consider the services to be delivered by the network.
-%Cluster sizes affect the power consumption directly in wirelss sensor networks~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
-%When the cluster size is not deliberately discussed, it is also decided alongside the optimization of the network, \eg the opimal selection of the aggregation points in a wireless sensor network results in the clusters~\cite{data_aggr_algorithm_04}.
-%%%%%%%%%%%%%
-%Various clustering schemes are proposed to target different aspects in cognitive radio networks.
-%Work~\cite{Consensus_based_clustering12} improves spectrum sensing ability by grouping the CR users with potentially best detection performance into the same cluster.
+In the following we review briefly state-of-the-art regarding clustering in CRN, with an emphasis on robust clustering.
+
+With regard to forming clusters in CRN, deciding on the common channel within each cluster is the foremost question to answer.
+\cite{Zhao07, Chen07,Affinity_clustering_09icccn} propose different clustering schemes and enforce that every cluster possesses at least one CC.
+The clustering scheme in~\cite{Consensus_based_clustering12} looks for a network partition which improves the accuracy of spectrum sensing without considering robustness.
 %Clustering scheme~\cite{clustering_globecom11} obtains the best cluster size which minimizes power consumption caused by communication within and among clusters.
-%\cite{clustering_globecom11} proposes clustering strategy in cognitive radio network, which looks into the relationship between cluster size and power consumption and accordingly controlling the cluster size to decrease power consumption.
-With regard to forming clusters in CRN, deciding on the common channel within each cluster is the foremost question to answer.
-\cite{Zhao07, Chen07,Affinity_clustering_09icccn} propose the clustering schemes and enforce that every cluster possesses at least one CC.
-Clustering scheme~\cite{Consensus_based_clustering12} looks for a network partition which improves the accuracy of spectrum sensing with the cluster structure.
-%Clustering scheme~\cite{clustering_globecom11} obtains the best cluster size which minimizes power consumption caused by communication within and among clusters.
-\cite{TWC2012_cooperative_communication} forms the clusters by deciding on the cluster heads, where the transmit power for the long-haul transmission between the cluster heads is minimized.
-\cite{clustering_globecom11} proposes a cluster structure which promises energy efficiency.
-\cite{cluster_EW10} proposes strategy on how to decide on the CCs and access the multiple CCs within clusters.
+In \cite{TWC2012_cooperative_communication} clusters are formed by deciding on the cluster heads, where the transmit power for the long-haul transmission between the cluster heads is minimized.
+\cite{clustering_globecom11} proposes a cluster structure which imprroves energy efficiency.
+Furthermore, \cite{cluster_EW10} proposes a strategy on how to decide on the CCs and access multiple CCs within clusters.
 An event-driven clustering scheme is proposed for cognitive radio sensor networks in \cite{Ozger_cluster_crsn_13}.
-None of the above mentioned schemes provides a certain robustness to formed clusters against primary users.
-
-The authors of~\cite{Mansoor2015} propose a clustering algorithm which aims to speed up the process of re-clustering in case a cluster doesn't uphold in front of active primary users.
-However, this work does not consider cluster robustness and messaging overhead during frequent re-clustering processes.
-A distributed clustering scheme~\cite{LIU_TMC11_2} (denoted as SOC) is proposed, which is designed to generate clusters which  have multiple CCs.
-The authors compared SOC with other schemes in terms of the average number of CCs of the formed cluster, where SOC outperforms other schemes by 50\%-100\%. 
-Note that SOC's comparison schemes are designed either for ad hoc network without consideration of channel availability~\cite{Basagni99}, or for CRN but just considering connection among CR nodes~\cite{Zhao07}.
-%The robustness of the clusters comes from the multiple CCs available for the clusters.
-%SOC involves three phases of distributed executions.
-In the first phase of SOC, every secondary user forms clusters with some one-hop neighbors. 
+However, none of the above mentioned schemes provide robustness of the clusters against random primary user activity.
+
+The authors of~\cite{Mansoor2015} propose a clustering algorithm which aims at speeding up the process of re-clustering in case that primary user activity eliminates all CCs.
+However, this work does not consider cluster robustness in the first place, but rather focuses on reactive measures.
+\cite{mansoor_15_cluster_robust} presents a heuristic method to form clusters. 
+Although the authors claim that robustness is one goal to achieve, only the minimization of the number of formed clusters is studied.
+A distributed clustering scheme referred to as SOC is proposed in~\cite{LIU_TMC11_2}, targeting at cluster generation with multiple CCs per cluster.
+In the first phase of SOC, every secondary user forms clusters with some one-hop neighbor. 
 In the second and final phase, each secondary user seeks to either merge other clusters or join one of them.
 The product of the number of CCs and cluster size is adopted as the metric by each secondary user in every phase. 
-The drawbacks of this scheme are as follows: although the adopted metric considers both the cluster size and the number of CCs, cluster formation can be easily dominated by only one factor.
-For example, a node which accesses abundant channels may form a cluster by itself and doesn't have motivation to unite neighboring nodes to form a cluster.
-In addition, this scheme leads to the high variance of the cluster sizes, which is not desired in certain applications as discussed in~\cite{clustering_globecom11, cluster_EW10}.
-\cite{mansoor_15_cluster_robust} presents a heuristic method to form clusters. Although the authors claim that robustness is one goal to achieve, the minimum number of clusters is finally pursued.
-%
+The authors compare SOC with other schemes in terms of the average number of CCs of the formed clusters, where SOC outperforms other schemes by 50\%-100\%. 
+Nevertheless, the drawbacks of this scheme are as follows: Although the adopted metric considers both the cluster size and the number of CCs, cluster formation can be easily dominated by only one factor.
+For example, a node which accesses abundant channels may form a cluster solely by itself, a so called singleton cluster.
+In addition, this scheme leads to a high variance of the cluster sizes, which is not desirable in certain applications as discussed in~\cite{clustering_globecom11, cluster_EW10}.
 In~\cite{Li11_ROSS} we propose a distributed clustering scheme ROSS (Robust Spectrum Sharing) under a game theoretic framework. 
-Compared with the clustering schemes introduced above, the clusters are formed faster and the clusters possess more CCs than SOC.
-However, as all the other clustering schemes, this scheme does not have control over formation of the very small or very large clusters which are not desirable.
-Furthermore, both this work and SOC define robustness just to be the number of CCs per cluster, and don't consider the sustainability of clusters against increasing activity of primary users, leaving the issue of cluster robustness open.
-%
+Compared with the clustering schemes introduced above, the clusters are formed faster and the clusters possess more CCs than in case of being formed by SOC.
+However, as all the other clustering schemes, this scheme does not have control over formation of very small or very large clusters, being not desirable as discussed above.
+Summarizing, this work and SOC deem cluster robustness just to be the number of CCs per cluster, and don't consider the sustainability of clusters against increasing activity of primary users, leaving the issue of cluster robustness open.
+
+% XXX Not happy with this last sentence.
+In my view, robustness is provided by the number of CCs and therefore both works address robustness.
+However, they do not address the issue of the size of the cluster, where we have been saying further up in the introduction that a small cluster looses sensing accuracy, so what these two works do not address is the balance between sensing accuracy and robustness (which we have been discussing much in the introduction).
+Is that maybe what is meant here?
+
+% XXXX 
+%Their biggest problem is, that they stick to the 'the number of CCs' metric and claim they achieve the robustness by obtaining the 'large number of CCs'.
+%It is fair to say robustness is provided by the number of CCs, but only the amount of CCs doesn't decide how robust the clusters are.
+It is possible that the cluster with more CCs can be destroied earlier than the other clusters under the intensity of PRs' activity.
+This situation is illustrated in Fig 8 and 10.
+%Except for the amount of CCs, robustness is also decided by cluster sizes and the compositiomn of the clusters.
+%In the simulation section, one of the conclusion is the number of CCs is not an accurate metric to measure robustness (consider Fig 8 and 10).
+Nevertheless, in our schemes, we still consider to increase 'the number of CCs' to improve robustness.
+% XXXX
 
@@
 A set of licensed channels $\mathcal{K}$ is available for the primary users. 
-The CR users are allowed to transmit on channel $k \in \mathcal{K}$ only if no primary user is detected to be working at their locations on channel $k$. 
+The CR users are allowed to transmit on channel $k \in \mathcal{K}$ only if no primary user is detected to be occupying channel $k$. 
 CR users conduct spectrum sensing independently and sequentially on all licensed channels.\footnote{We assume that every node can detect the presence of an active primary user on each channel with certain accuracy.
 The spectrum availability can be validated with a certain probability of detection.
-Spectrum sensing/validation is out of the scope of this paper.}
+While we do argue that too small cluster sizes lead in general to a loss of sensing accuracy, a study of the detailed spectrum sensing/validation accuracy is out of the scope of this paper.}
 We adopt the unit disk model~\cite{unitDiskModel} for both primary and CR users' transmission.
-If a CR node $i$ locates within the transmission range of an active primary user $p$, $i$ is not allowed to use the channel which is being used by $p$.
-We assume the primary users change their operation channels slowly, thus we omit the time index when denoting spectrum availability. 
+Thus, if a CR node $i$ locates within the transmission range of an active primary user $p$, $i$ is not allowed to use the channel which is being used by $p$.
+We assume the primary users to change their operation channels slowly, thus we omit the time index when denoting spectrum availability. 
 As the result of spectrum sensing, $K_i \subseteq \mathcal{K}$ denotes the set of available licensed channels for CR user $i$.
-As the transmission range of primary users is limited and CR users have different locations, different CR users have different views of the spectrum availability, i.e., for any $i, j \in \mathcal{N}$, $K_i$ equals $K_{j}$ does not necessarily hold.
-We therefore represent the network of CR nodes by a graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{i, j\} \in E$ if and only if $K_{i} \cap K_{j}\neq \emptyset$ and $d_{i,j} < r$, where $d_{i,j}$ is the distance between $i, j$ and $r$ is the radius of CR user's transmission range.
+As the transmission range of primary users is limited and CR users have different locations, different CR users have different views of the spectrum availability, i.e., for any $i, j \in \mathcal{N}$, $K_{i} = K_{j}$ typically does not hold.
+The resulting network of CR nodes is represented by a graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{i, j\} \in E$ if and only if $K_{i} \cap K_{j}\neq \emptyset$ and $d_{i,j} < r$, where $d_{i,j}$ is the spatial distance between $i, j$ and $r$ is the radius of CR user's transmission range.
 %
@@
 
-Here we give the description of cluster in CRN. 
-A cluster $C$ is a set of secondary nodes in an area, and there is a set of common channels which are available for each node.
-Besides, a cluster consists of a cluster head $h(C)$ and a number of cluster members.
+We next focus on a single CR cluster. 
+A cluster $C$ is a set of secondary nodes in an area, and there is a set of common channels which are available to each node belonging to the cluster.
+One of the nodes belonging to the cluster is furthermore the cluster head $h(C)$.
 The cluster head is able to communicate with any cluster member directly.
-Our scheme enables the cluster heads to be selected in a distributed manner, and a cluster can only be formed only by these selected cluster head.
+%Our scheme enables the cluster heads to be selected in a distributed manner, and a cluster can only be formed only by these selected cluster head.
 %C1-4
@@
 %For any cluster member $i \in C$, $i \in \text{Nb} (h_C) $ holds.
-The size of $C$ is denoted by $|C|$.
+The number of nodes belonging to $C$ is denoted by $|C|$.
 When the cluster head of a cluster is $i$, we denote that cluster by $C(i)$.
-$K(C)$ denotes the set of CCs in cluster $C$, $ K(C) = \bigcap_{i\in C} K_i$.
+$K(C)$ denotes the set of CCs of all nodes in cluster $C$, i.e. $ K(C) = \bigcap_{i\in C} K_i$.
 %Clustering is performed periodically, because the secondary users are mobile and the primary users change their operation channels, thus the channel availability on secondary users changes accordingly.
-The notations used in the system model are listed in Table~\ref{tab1}.
+We also summarize all used notation in Table~\ref{tab1}.
 \begin{table}[h!]
@@
  $C_i$  & the $i$-th cluster in $\mathcal{S}$ \\
- $|C_i|$ & size of the cluster $C_i$\\
+ $|C_i|$ & the size of the cluster $C_i$\\
  $|K(C_i)|$ & the number of CCs of cluster $C_i$\\
@@
 
-As introduced in Section~\ref{intro}, robustness of the clusters is their ability to uphold with the influence of the active primary users, and it is represented by the number of secondary users which are not included in any cluster.
-To achieve better robustness, we propose that cluster should be formed by increasing the number of CCs.
-Meanwhile, the sizes of the formed clusters should be regulated, \ie they don't diverge from the desired cluster size greatly.
+%As introduced in Section~\ref{intro}, robustness of the clusters is the ability to uphold with the influence of the active primary users, and it is represented by the number of secondary users which are not included in any cluster.
+%In our scheme, we still 
+%To achieve better robustness, we propose that cluster should be formed by increasing the number of CCs.
+%Meanwhile, the sizes of the formed clusters should be regulated, \ie they don't diverge from the desired cluster size greatly.
+
+% XXX Di, these previous three sentences do not make sense: Robustness is actually really only the number of CCs.
+If you want to add the fact  that the size should be controlled, in particular that not too small clusters are formed, you need to motivate this differently, for example by the sensing accuracy, as I did in the introduction.
+Please try to reformulate these three sentences accordingly
+% XXXX I changed the three sentences, see below.
+Robustness of the clusters is the ability to uphold with the influence of the active primary users, \ie how many secondary users are not included in any cluster.
+To achieve better robustness, we use the amount of CCs as metric and try to increase it. 
+Meanwhile, the sizes of the formed clusters should be regulated, so that the clusters can not only benefited from the spectrum sensing accuracy from cooperative sensing, but achieve a large set of CCs.
 
@@
 
-As to a cognitive radio network where the set of CR nodes is $\mathcal{N}$, the robust clustering problem is to decide the set of clusters $\mathcal{T}$, where 
+As to a cognitive radio network where the set of CR nodes is $\mathcal{N}$, the robust clustering problem is to determine a set of clusters $\mathcal{T}$, where 
 \begin{enumerate}
@@
 \item the intersection of any two clusters in $\mathcal{T}$ is an empty set
-\item the union of clusters in $\mathcal{T}$ is $\mathcal{N}$
-\item when the number of common channels for cluster $C$ is denoted as $f(C)$, the sum of the $f(C)$ is the maximal, where $C\in \mathcal{T}$ and meanwhile the cluster sizes fall in the scope $\big[\delta_1, \delta_2\big]$.
-$\delta_1, \delta_2\in \mathbb{Z}^+$ and $\delta_1 \leq \delta_2$.
-When the cluster size is out of $\big[\delta_1, \delta_2\big]$, $f(C)$ is defined as 0.
-
+\item the union of all nodes in all clusters in $\mathcal{T}$ is $\mathcal{N}$
+\item the sum over $f(C)$ for all clusters $C$ is maximized, where the number of common channels for cluster $C$ is denoted as $f(C)$ 
+\item all cluster sizes are within the range $\big[\delta_1, \delta_2\big]$, with $\delta_1, \delta_2\in \mathbb{Z}^+$ and $\delta_1 \leq \delta_2$.
+When the cluster size is larger or smaller than the range $\big[\delta_1, \delta_2\big]$, $f(C)$ is defined as 0.
 \item the size of $C$ in $\mathcal{T}$ is allowed to be 1.
@@
 \end{mydef}
-
-The decision version of this problem is to determine whether there exists a set of clusters, say $\mathcal{X}$, so that $\cup C_{C\in\mathcal{X}} = \mathcal{N}$, and $\sum_{C\in \mathcal{X}} f(C) \geqslant \lambda$ where $\lambda$ is a real number.
+% XXX Di: What does the last statement mean with respect to the size of C being allowed to be 1.
+Does that mean for all C in T, the size is allowed to be 1?
+Doesn't that contradict what you have been saying in the definition before, where you come up with the range ?
+% XXXX 
+%1. we have a function f(C) to denote the number of CCs, if cluster size in the scope, fine; if not, f(C) equals zero.
+%2. it is OK for every CR node to form their own cluster. Then according to rule 3, f(C) is zero and we obtain a 'bad' clustering result.
+% XXXX
+
+The decision version of this problem is to determine whether there exists a set of clusters, say $\mathcal{X}$, so that $\cup_{C\in\mathcal{X}} C = \mathcal{N}$, and $\sum_{C\in \mathcal{X}} f(C) \geqslant \lambda$ where $\lambda$ is a positive integer number.
 We have the following theorem on the problem's complexity.
@@
 \end{theorem}
-The proof is in Appendix~\ref{proof_theorem1}.
+The proof is given in Appendix~\ref{proof_theorem1}.
 
@@
 %$|K(C_i)|$ is the number of CCs of cluster $C_i$, and $|C_i|$ is the size of cluster $C_i$.
-$p(C_i)$ is the size-related weight, which is positively related with the difference between $C_i$'s size and the desired size.
-Assuming $\delta$ is the desired size, then weight $p$ is decided with respect to cluster sizes 1,2, $\cdots$, $\sigma$ as follows,
+$p(C_i)$ is the size-related weight, which is positively related with the difference between $C_i$'s size and the desired size $\delta$.
+The desired size $\delta$ is decided based on the capability of the CR users and the tasks to be conveyed.
+The weight $p$ is decided with respect to cluster sizes 1,2, $\cdots$, $\sigma$ as follows,
 $$
@@
 The threshold should be larger than the desired size $\delta$, because there are overlaps between neighboring clusters.
-The desired size $\delta$ is decided based on the capability of the CR users and the tasks to be conveyed.
 %Hence, a cluster head excludes some cluster members when the cluster size exceeds a certain threshold.

### 2017-11-26 journal-draft/ettdoc_JG.tex
in ettdoc_JG, on system model

@@
 When the cluster size is larger or smaller than the range $\big[\delta_1, \delta_2\big]$, $f(C)$ is defined as 0.
+In particular, the range can be expressed as $[\delta-u, \delta+u]$, where $\delta$ is the desired cluster size, $u$ is a constant and $\delta-u > 0$.
 \item the size of $C$ in $\mathcal{T}$ is allowed to be 1.
@@
 % XXXX 
-%1. we have a function f(C) to denote the number of CCs, if cluster size in the scope, fine; if not, f(C) equals zero.
+%1. we have a function f(C) to denote the number of CCs, if cluster size is in the scope, fine; if not, f(C) equals zero.
 %2. it is OK for every CR node to form their own cluster. Then according to rule 3, f(C) is zero and we obtain a 'bad' clustering result.
@@
 When the global knowledge of the CRN \ie the locations of primary users and their working channels, and the locations of secondary users and available channels on them, we can propose a centralized scheme.
-We obtain the set of $\mathcal{S}$ which contains all the clusters in $\mathcal{N}$, \ie $\mathcal{S}=\{C_1, C_2,\ldots,C_i, \ldots, C_{|\mathcal{S}|}\}$ \footnote{The subscript $i$ means the $i$-th cluster in $\mathcal{S}$.} and there is $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = \mathcal{N}$.
+We obtain the set of $\mathcal{S}$ which contains all the clusters.
+These clusters satisfy the definition of cluster in Section~\ref{sec:model}, and they basically form a powerset of $\mathcal{N}$, which nevertheless are restricted by connectivity and spectrum availability.
+There are $\mathcal{S}=\{C_1, C_2, \ldots, C_{|\mathcal{S}|}\}$ \footnote{The subscript $i$ means the $i$-th cluster in $\mathcal{S}$.} and $|\mathcal{S}| = M$.
 The proposed centralized solution formulates the problem in Definition~\ref{def_centralized_clustering} as an optimization problem which is solved with standard software packages.
@@
 \begin{aligned}
-     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot t_{ij}) \\
+     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p(C_i)) \\
      &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, for\,\,\forall j=1, \ldots, N \\
@@
 \end{equation}
-$y_i$ and $x_{ij}$ are two binary variables.
-% where $j\in \{1,2,\cdots,N-1, N\}$ and $i\in \{1,2,\cdots,M-1, M\}$.
-%$G = |\mathcal{G}|$ and there is $\mathcal{G} \subseteq \mathcal{S}$.
+$N$ is the total number of CR users in network $\mathcal{N}$.
+$y_i$ and $x_{ij}$ are binary variables.
 Being either 1 or 0, $y_i$ denotes whether the $i$-th cluster $C_i$ in $\mathcal{S}$ is chosen or not.
 $x_{ij}$ indicates whether the CR node $j$ resides in the cluster $C_i$, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$.
-%Node index $j$ is identical to the node ID.
-$N$ is the total number of CR users in network $\mathcal{N}$, $M$ is the number of clusters in $\mathcal{S}$.
 
@@
 %The optimization is a binary linear programming problem.
-The objective is to maximize the sum of the numbers of CCs in the clusters which constitute the CRN.
-$t_{ij}$ is a constant and there is
-%In practice, we can solve the problem with $\mathcal{G} = \mathcal{S}$ when $|\mathcal{S}|$ is not large. 
-%
-%
-%Given a CRN $\mathcal{N}$ and desired cluster size $\delta$, we obtain a collection of clusters $\mathcal{G}$ which contains all the \textit{potential} clusters, and the sizes of these clusters are $1,2,\ldots,\delta$.
-%Potential clusters are the clusters which satisfy the conditions introduced in Section~\ref{sec:model}. 
-%Note that the potential clusters include the singleton ones.
-%By permitting the existence of the singleton clusters, we can ensure that the $\mathcal{S}'$ in Definition~\ref{def_centralized_clustering} is always be feasible.
-
-\begin{equation}
-t_{ij} = \frac{q_{ij}}{|C_i|} - p_i(C_i)
-\end{equation}
-where constant $q_{ij}= |K(C_i)|$ when node $j\in C_i$, and $q_{ij}= 0$ when node $j\notin C_i$.
-%$|K(C_i)|$ is the number of CCs of cluster $C_i$, and $|C_i|$ is the size of cluster $C_i$.
-$p(C_i)$ is the size-related weight, which is positively related with the difference between $C_i$'s size and the desired size $\delta$.
-The desired size $\delta$ is decided based on the capability of the CR users and the tasks to be conveyed.
-The weight $p$ is decided with respect to cluster sizes 1,2, $\cdots$, $\sigma$ as follows,
+As to the objective function, the sum of the first items is the sum of CCs of the clusters which constitute the CRN.
+In the second item, we propose $p(C_i)$ which is a size-related weight for cluster $C_i, i\in{1,\cdots, M}$.
+$p(C_i)$ is positively related with the difference between $C_i$'s size and the desired size $\delta$.
+The desired size $\delta$ is pre-decided based on the capability of the CR users and the tasks to be conveyed.
+When $y_i$ is 1 ($C_i$ is chosen) but $|C_i|$ doesn't equal to the desired cluster size $\delta$, it will be negative, which contradicts the direction of the optimization.
+Thus the second item discourages the appearance the clusters whose sizes deviate from $\delta$.
+The weight $p(C_i)$ with respect to different cluster sizes is as follows,
+%$$
+%p(C_i) = \left\{ \begin{array}{rl}
+%0 &\mbox{ if $|C_i|=\delta$} \\
+%\rho_1 &\mbox{if $||C_i|-1|=\delta$} \\
+%\rho_2 &\mbox{if $||C_i|-2|=\delta$} \\
+%\vdots\\
+%\rho_\sigma &\mbox{if $||C_i|-\sigma|=\delta$} \\
+%\end{array} \right.
+%$$
+
 $$
@@
 0 &\mbox{ if $|C_i|=\delta$} \\
-\rho_1 &\mbox{if $||C_i|-1|=\delta$} \\
-\rho_2 &\mbox{if $||C_i|-2|=\delta$} \\
+\rho_1 &\mbox{if $|C_i|=\delta \pm 1$ } \\
+\rho_2 &\mbox{if $|C_i|=\delta \pm 2$} \\
 \vdots\\
-\rho_\sigma &\mbox{if $||C_i|-\sigma|=\delta$} \\
+\rho_\sigma &\mbox{if $|C_i|=\delta \pm \sigma$} \\
 \end{array} \right.
@@
 where $ 0 < \rho_1< \rho_2 < \cdots < \rho_\sigma$.
-
-%%Based on the knowledge on $\mathcal{S}$, we construct a $M\times N$ matrix $Q_{M\text{x}N}$ which is shown in Figure~\ref{costant_matrix_Q}. 
-%%Constant $q_{ij}$ is the element of $Q_{M\text{x}N}$, and its subscripts correspond to the $i$th cluster and CR node $j$ respectively.
-%$q_{ij}= |K(C_i)|/|C_i|$ when there is $j\in C_i$, and $q_{ij}= 0$ when there is $j\notin C_i$.
-%In other words, each non-zero element $q_{ij}$ means the number of CCs of the cluster $i$ where node $j$ resides.
-
-%\begin{figure}[ht!]
-%\centering
-%\bordermatrix{~ 		& 1 	& 2 	& 3 	& \cdots & j & \cdots	& N-1 	& N	\cr
-%                  1 	& |K(C_1)| 	& |K(C_1)| 	& 0 	& \cdots & \cdots &\cdots	& 0 	& 0	\cr
-%                  2 	& |K(C_2)| 	& 0 	& |K(C_2)| 	& \cdots & \cdots & \cdots 	& 0 	& 0	\cr
-%				\vdots  	&\vdots & 	 	& 		&  \vdots		& 		& \vdots \cr
-%				i 	& 0 	& |K(C_i)| 	& 0 	& \cdots  & \cdots & \cdots 	& |K(C_i)| 	& 0	\cr
-%				\vdots  	&\vdots & 	 	& 		&  \vdots & \cdots & \vdots 		& 		& \vdots \cr
-%				\vdots 	& 0  	& 0 	& 0 	& \cdots & \cdots & \cdots 	& |K(C_i')| 	& 0	\cr
-%				G  	& |K(C_G)| & \cdots	 	& 		&  \vdots	& \cdots & \vdots& 		& \vdots \cr}	
-%\caption{An example of Matrix $Q$, its rows correspond to all possible clusters, and columns correspond to the CR nodes in the CRN. }
-%\label{costant_matrix_Q}
-%\end{figure}
-
-%Now we examine the objective function to see whether it in line with the goal to maximize the total number of CCs meanwhile consider the restriction on the cluster size.
-When $t_{ij}$ is replaced by $\frac{q_{ij}}{|C_i|} - p(C_i)$, the objective function becomes,
-\begin{equation}
-\begin{aligned}
-     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p(C_i)) \\
-\notag
-\end{aligned}
-\label{centralized_opt}
-\end{equation}
-The sum of the first items is the sum of CCs of all the chosen clusters.
-As to the second item, when $w_i$ is 1 ($C_i$ is chosen) and $|C_i|\neq\delta$, it will be negative, which contradicts the direction of the optimization.
-Thus the second item discourages the appearance the clusters whose sizes deviate from $\delta$.
+Please note that here we adopt the desired cluster size in stead of the range for cluster sizes which is described in Definition~\ref{problem}.
+Because in implementation, we usually need a large range to guarantee a feasible result for the optimization problem.
+By adopting the desired size and the punishment for deviating from it, we actually set a large range of cluster sizes and meanwhile a better control of the resulted sizes.
 

### 2017-11-26 journal-draft/ettdoc_JG.tex
in ettdoc_JG, change the font of words as normal

@@
      &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p(C_i)) \\
-     &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, for\,\,\forall j=1, \ldots, N \\
-   &&& \Sigma_{j=1}^N x_{ij} = |C_i|\cdot y_i,\, for\,\,\forall i=1, \ldots, M \\
+     &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, \text{for}\,\,\forall j=1, \ldots, N \\
+   &&& \Sigma_{j=1}^N x_{ij} = |C_i|\cdot y_i,\, \text{for}\,\,\forall i=1, \ldots, M \\
   % &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\

### 2017-12-02 journal-draft/ettdoc_JG.tex
update ettdoc_JG.tex with the changes from James.

@@
 
-In CRNs, formed clusters maintain a set of unlicensed channels which are validated by every CR node in that cluster, meaning that the channel is perceived as not been occupied by a primary user.
+In CRNs, formed clusters maintain a set of unlicensed channels which are validated by every CR node in that cluster, meaning that the channel is perceived as not being occupied by a primary user.
 In the following we refer to these maintained unlicensed channels as \textit{common channels} (CC).
@@
 Our proposed distributed scheme extends our previous work ROSS (Robust Spectrum Sharing)~\cite{Li11_ROSS} by additionally incorporating control over the size of a cluster.
-Throughout this paper, we call the newly proposed distributed schemes \textit{variants of ROSS}.
+Throughout this paper, we call these newly proposed distributed schemes \textit{variants of ROSS}.
 %
@@
 \label{related_work}
-In the following we review briefly state-of-the-art regarding clustering in CRN, with an emphasis on robust clustering.
-
+In the following we first review briefly state-of-the-art regarding clustering in CRN in general, and then focus on robust clustering in particular.
 With regard to forming clusters in CRN, deciding on the common channel within each cluster is the foremost question to answer.
@@
 However, as all the other clustering schemes, this scheme does not have control over formation of very small or very large clusters, being not desirable as discussed above.
-Summarizing, this work and SOC deem cluster robustness just to be the number of CCs per cluster, and don't consider the sustainability of clusters against increasing activity of primary users, leaving the issue of cluster robustness open.
-
-% XXX Not happy with this last sentence.
-In my view, robustness is provided by the number of CCs and therefore both works address robustness.
-However, they do not address the issue of the size of the cluster, where we have been saying further up in the introduction that a small cluster looses sensing accuracy, so what these two works do not address is the balance between sensing accuracy and robustness (which we have been discussing much in the introduction).
-Is that maybe what is meant here?
-
-% XXXX 
-%Their biggest problem is, that they stick to the 'the number of CCs' metric and claim they achieve the robustness by obtaining the 'large number of CCs'.
-%It is fair to say robustness is provided by the number of CCs, but only the amount of CCs doesn't decide how robust the clusters are.
-It is possible that the cluster with more CCs can be destroied earlier than the other clusters under the intensity of PRs' activity.
-This situation is illustrated in Fig 8 and 10.
-%Except for the amount of CCs, robustness is also decided by cluster sizes and the compositiomn of the clusters.
-%In the simulation section, one of the conclusion is the number of CCs is not an accurate metric to measure robustness (consider Fig 8 and 10).
-Nevertheless, in our schemes, we still consider to increase 'the number of CCs' to improve robustness.
-% XXXX
+Summarizing, our own previous work and SOC deem cluster robustness just to be the number of CCs per cluster. 
+However, this potentially can lead to a significant number of singleton clusters being formed, which leads to lower sensing accuracy and has also other downsides as for example an increased routing overhead.
+In the following we focus on striking the balance between cluster size and cluster robustness.
 
@@
 As the transmission range of primary users is limited and CR users have different locations, different CR users have different views of the spectrum availability, i.e., for any $i, j \in \mathcal{N}$, $K_{i} = K_{j}$ typically does not hold.
-The resulting network of CR nodes is represented by a graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{i, j\} \in E$ if and only if $K_{i} \cap K_{j}\neq \emptyset$ and $d_{i,j} < r$, where $d_{i,j}$ is the spatial distance between $i, j$ and $r$ is the radius of CR user's transmission range.
+The resulting network of CR nodes is represented by a graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{i, j\} \in E$ if and only if $K_{i} \cap K_{j}\neq \emptyset$ and $d_{i,j} < r$, where $d_{i,j}$ is the spatial distance between nodes $i$ and $j$, and $r$ is the radius of CR user's transmission range.
 %
@@
 This control channel could be one of the ISM bands or other reserved spectrum which is exclusively used for transmitting control messages.\footnote{Actually, the control messages involved in the clustering process can also be transmitted on the available licensed channels through a rendezvous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}, i.e., two neighboring nodes establish communication on the same channel.}
-Over the control channel, a secondary user $i$ can exchange its spectrum sensing result $K_i$ with all its one hop neighbors $\text{Nb}(i)$.
-In the following, we refer to licensed channels as channels in general, and will explicitly mention the dedicated control channel if necessary.
+Over the control channel, a secondary user $i$ can exchange its spectrum sensing result $K_i$ with all its one-hop neighbors $\text{Nb}(i)$.
+%In the following, we refer to licensed channels as channels in general, and will explicitly mention the dedicated control channel if necessary.
 
@@
 %Clustering is performed periodically, because the secondary users are mobile and the primary users change their operation channels, thus the channel availability on secondary users changes accordingly.
-We also summarize all used notation in Table~\ref{tab1}.
+Table~\ref{tab1} summarizes all parameters and their assumed relevance in our system model.
 \begin{table}[h!]
@@
 % XXXX I changed the three sentences, see below.
-Robustness of the clusters is the ability to uphold with the influence of the active primary users, \ie how many secondary users are not included in any cluster.
-To achieve better robustness, we use the amount of CCs as metric and try to increase it. 
-Meanwhile, the sizes of the formed clusters should be regulated, so that the clusters can not only benefited from the spectrum sensing accuracy from cooperative sensing, but achieve a large set of CCs.
+Robustness of a cluster is its ability to uphold communication among the cluster members despite the influence of the active primary users.
+Thus, to achieve better robustness, a clear component of an optimization metric needs to be the amount of CCs among each formed cluster. 
+However, this can lead in an extreme situation to a large amount of singleton clusters, if the size of the clusters is not controlled simultaneously. 
+A large amount of singleton clusters, as discussed reduced spectrum sensing accuracy through cooperative sensing, as well as being not desirable from different other perspectives.
+Thus, we essentially propose to include this trade-off in the optimization process of building clusters, captured in the following definition:
 
@@
 \label{def_centralized_clustering}
-\textit{Robust clustering problem in CRN.}
-
-As to a cognitive radio network where the set of CR nodes is $\mathcal{N}$, the robust clustering problem is to determine a set of clusters $\mathcal{T}$, where 
+For a set of CR nodes $\mathcal{N}$, the \textbf{CRN robust clustering problem} is to determine a set of clusters $\mathcal{T}$, where
 \begin{enumerate}
 \setlength{\itemindent}{.05in}
-\item the intersection of any two clusters in $\mathcal{T}$ is an empty set
-\item the union of all nodes in all clusters in $\mathcal{T}$ is $\mathcal{N}$
-\item the sum over $f(C)$ for all clusters $C$ is maximized, where the number of common channels for cluster $C$ is denoted as $f(C)$ 
-\item all cluster sizes are within the range $\big[\delta_1, \delta_2\big]$, with $\delta_1, \delta_2\in \mathbb{Z}^+$ and $\delta_1 \leq \delta_2$.
-When the cluster size is larger or smaller than the range $\big[\delta_1, \delta_2\big]$, $f(C)$ is defined as 0.
+\item the intersection of any two clusters in $\mathcal{T}$ results in the empty set;
+\item the union of all clusters in $\mathcal{T}$ results in$\mathcal{N}$;
+\item the sum over $f(C)$ for all clusters $C$ is maximized, where the number of common channels for cluster $C$ is denoted as $f(C)$;
+
+\item all cluster sizes are within the range $\big[\delta_1, \delta_2\big]$, with $\delta_1, \delta_2\in \mathbb{Z}^+$ and $\delta_1 \leq \delta_2$;
+\item When the cluster size is larger or smaller than the range $\big[\delta_1, \delta_2\big]$, $f(C)$ is defined as 0, i.e.
+singleton clusters may be formed but do mot contribute to the objective function.
 In particular, the range can be expressed as $[\delta-u, \delta+u]$, where $\delta$ is the desired cluster size, $u$ is a constant and $\delta-u > 0$.
-\item the size of $C$ in $\mathcal{T}$ is allowed to be 1.
-%, and $\delta$ is decided according to the application to be implemented in the CRN.
+
 \end{enumerate}
@@
 \label{centralized_solution}
-When the global knowledge of the CRN \ie the locations of primary users and their working channels, and the locations of secondary users and available channels on them, we can propose a centralized scheme.
-We obtain the set of $\mathcal{S}$ which contains all the clusters.
-These clusters satisfy the definition of cluster in Section~\ref{sec:model}, and they basically form a powerset of $\mathcal{N}$, which nevertheless are restricted by connectivity and spectrum availability.
-There are $\mathcal{S}=\{C_1, C_2, \ldots, C_{|\mathcal{S}|}\}$ \footnote{The subscript $i$ means the $i$-th cluster in $\mathcal{S}$.} and $|\mathcal{S}| = M$.
+Given the fact that the complexity of the CRN clustering problem is determined, we consider in this section a centralized solution for the problem.
+The motivation is mainly to have later on a comparison scheme for distributed algorithms, that we present in the next section.
+Assuming some global knowledge of the CRN to be given at some point in the network, a centralized solution \ie the locations of primary users and their working channels, and the locations of secondary users and available channels on them, we can propose a centralized scheme.
+We obtain the set of $\mathcal{S}$ which contains all the clusters in $\mathcal{N}$, \ie $\mathcal{S}=\{C_1, C_2,\ldots,C_i, \ldots, C_{|\mathcal{S}|}\}$ \footnote{The subscript $i$ means the $i$-th cluster in $\mathcal{S}$.} and there is $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = \mathcal{N}$.
 The proposed centralized solution formulates the problem in Definition~\ref{def_centralized_clustering} as an optimization problem which is solved with standard software packages.
@@
 $N$ is the total number of CR users in network $\mathcal{N}$.
-$y_i$ and $x_{ij}$ are binary variables.
+$y_i$ and $x_{ij}$ are two binary variables.
 Being either 1 or 0, $y_i$ denotes whether the $i$-th cluster $C_i$ in $\mathcal{S}$ is chosen or not.
@@
 In this section we introduce our distributed clustering schemes.
-With the variants of ROSS, CR nodes form clusters based on the proximity of the available spectrum in their neighborhood after a series of interactions with their neighbors.
-The variants of ROSS consist of two cascaded phases: \textit{cluster formation} and \textit{membership clarification} as shown in Figure~\ref{flowChartROSS}.
+With the variants of ROSS, CR nodes form clusters based on their own available channels, as well as the available channels of the nodes in their neighborhood.
+This clarified and conducted through a series of interactions on the control channel.
+All variants of ROSS consist of two cascaded phases: \textit{Cluster formation} and \textit{Membership clarification}, as shown in Figure~\ref{flowChartROSS}.
 \begin{figure}[ht!]
@@
 \end{figure}
-
-In the first phase, clusters are formed quickly and every CR user becomes either cluster head or cluster member, cluster size control is also implemented	.
-In the second phase, non-overlapping clusters are formed in a way that the CCs of relevant clusters are mostly increased.
-
-%is based on the spectrum sensing results in its neighbours , then
+In the first phase, clusters are initially formed such that every CR user becomes either cluster head or cluster member.
+During this phase, size control is already realized, however, memberships might not be efficient with respect to robustness while also not being necessarily unique.
+This is addressed in the second phase, where non-overlapping clusters are formed in a way that the CCs of the involved clusters are predominantly increased.
 
@@
 \label{phaseI}
-Before conducting clustering, we assume spectrum sensing and neighbor discovery are completed, and neighboring nodes exchange their channel availabilities via the dedicated control channel. 
-As a result, every CR node is aware of the available channels for themselves and their neighbors.
-In this phase, cluster heads are determined after a series of comparisons with their neighbors. 
-Two metrics are proposed to characterize the proximity in terms of available spectrum between CR node $i$ and its neighborhood, which will be used to decide on cluster heads.
-
+Before conducting clustering, we assume spectrum sensing and neighborhood discovery have been completed.
+Furthermore, neighboring nodes have exchanged already their channel availabilities via the dedicated control channel. 
+As a result, every CR node is aware of the available channels of themselves and their one-hop neighbors.
+Next, cluster heads are determined after a comparison series among neighbors.
+Two metrics are proposed to characterize the channel availability in the proximity of each terminal, which subsequently are used to decide the cluster heads.
 \begin{itemize}
@@
 \item \textit{Individual connectivity degree} $d_i$: $d_i=\sum_{j\in \text{Nb}(i)}\vert K_i\cap K_j\vert$. 
-$d_i$ is the total number of the CCs between node $i$ and each of its neighbors.
-
-\item \textit{Neighborhood connectivity degree} $g_i$: the number of CCs which are available for $i$ and all of its neighbors.
-$g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$, which represents the ability of $i$ to form a robust cluster with its neighbors.
+$d_i$ is the total number of the CCs between node $i$ and each of its neighbors, it does not reflect the amount of jointly common channels among all neighbors of $i$.
+\item \textit{Neighborhood connectivity degree} $g_i$: In contrast, $g_i$ is the number of CCs which are available for $i$ and all of its neighbors, thus
+$g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$. It therefore represents the ability of $i$ to form a robust cluster with its neighbors.
 \end{itemize}
 Individual connectivity degree $d_i$ and neighborhood connectivity degree $g_i$ together form the \textit{connectivity vector} $(d_i, g_i)$.
-Connectivity vector is calculated by every secondary user after channel availability is obtained, and is then broadcasted.
-Figure~\ref{fig1} shows a CRN, where dashed edge indicates the end nodes are within each other's transmission range, the number along the dashed line is the number of common channels between the two ends.
-The sets of the indices of the available channels sensed by each node are: $K_A=\{1,2,3,4,5,6,10\}, K_B=\{1,2,3,5,7\}, \\K_C=\{1,3,4,10\}, K_D=\{1,2,3,5\}, \\K_E=\{2,3,5,7\}, K_F=\{2,4,5,6,7\}, \\K_G=\{1,2,3,4,8\}, K_H=\{1,2,5,8\}$.
-Each node's connectivity vector is calculated and shown.
+The connectivity vector is determined by every secondary user and is then broadcasted.
+Figure~\ref{fig1} illustrates the computation of the connectivity vectors for a CRN, where dashed edges indicate that the nodes are within each other's transmission range, while the number along the dashed line is the number of common channels between the two ends.
+In this example, the set of available channels per terminals are given by: $K_A=\{1,2,3,4,5,6,10\}, K_B=\{1,2,3,5,7\}, \\K_C=\{1,3,4,10\}, K_D=\{1,2,3,5\}, \\K_E=\{2,3,5,7\}, K_F=\{2,4,5,6,7\}, \\K_G=\{1,2,3,4,8\}, K_H=\{1,2,5,8\}$.
+The figure shows in particular the resulting connectivity vector per node.
 \begin{figure}[ht!]
@@
 % \includegraphics{figure1.pdf}
-	\caption{Connectivity graph of a CRN and the connectivity vector $(d_i, g_i)$ for each node. Primary users are not shown.}
+	\caption{Illustration of the resulting connectivity vector $(d_i, g_i)$ for each node of an example CRN.}
 	\label{fig1}
@@
 \subsubsection{Determining Cluster Heads and Forming Clusters}
-The procedure of determining cluster heads is as follows.
-Each CR node decides whether it is a cluster head by comparing its connectivity vector with neighbors.
+Given the connectivity vector per node, the procedure of determining cluster heads is as follows.
+Each CR node decides whether it is a cluster head by comparing its connectivity vector with all neighboring connectivity vectors.
 When CR node $i$ has lower individual connectivity degree than any of its neighbors except for those which have already been identified as cluster heads, node $i$ becomes a cluster head.
-If there is a CR node $j$ in $i$'s neighborhood, and has the same individual connectivity degree as $i$, \ie $d_j = d_i$ and $d_j < d_{k}, \forall k\in \text{Nb}(j)\setminus \{\Lambda\cup i\}$ where $\Lambda$ denotes cluster heads, then out of $i$ and $j$, the node with higher neighborhood connectivity degree will become cluster head.
+If there is a CR node $j$ in $i$'s neighborhood, which has the same individual connectivity degree as $i$, \ie $d_j = d_i$ while the connectivity degree of $j$ is lower than for all other nodes in its neighborhood (except for nodes that already declared themselves as heads) then out of $i$ and $j$ the node with higher neighborhood connectivity degree will become cluster head.
 If $g_i = g_j$ as well, the node ID is used to break the tie, \ie the one with smaller node ID becomes the cluster head.
 %
-The node which is identified as cluster head broadcasts a message to notify its neighbors of this news, then its neighbors which are not cluster heads become its cluster members.
-\footnote{The presence of cluster heads in the neighborhood of a newly formed cluster head will be explained in Section~\ref{ross_p1_guarantee_ccc} and \ref{ross_p2_cluster_pruning})}
-During the whole phase I, whenever a CR node becomes cluster head (thus accordingly forms a cluster), or its cluster's composition is changed, the cluster head broadcasts the new information about its cluster, which includes the sets of available channels on itself and all its cluster members.
-The pseudo code for the cluster head decision and the initial cluster formation is shown in Algorithm~\ref{alg0} in appendix.
+The node which is identified as cluster head broadcasts a message to notify its neighbors of this status update. 
+As a consequence, all neighbors - which have not become cluster head themselves -  become cluster members of this cluster head.
+In this step, nodes can become member of multiple clusters, depending on how many neighbors declare themselves as cluster heads.
+\footnote{The issues arising out of cluster heads in the neighborhood of a newly formed cluster head are addressed in Section~\ref{ross_p1_guarantee_ccc} and \ref{ross_p2_cluster_pruning}}
+During the whole phase I, whenever a CR node becomes cluster head, or the cluster composition changes, the cluster head broadcasts new/updated information about the cluster structure, in particular the new/ update sets of available channels regarding itself and all its cluster members.
+Pseudo code regarding this process, i.e. the cluster head decision and the initial cluster formation, is also provided as Algorithm~\ref{alg0} in the appendix.
 
@@
 \label{ross_p1_guarantee_ccc}
-After executing Algorithm~\ref{alg0}, certain formed clusters may not possess any CCs.
-As decreasing cluster size increases CCs within a cluster, for those clusters without CCs, certain nodes need to be excluded to obtain at least one CC.
-The sequence of removing is performed according to an ascending list of nodes, which are sorted according to the number of common channels between the nodes and the cluster head. 
+After executing Algorithm~\ref{alg0}, several formed clusters may not possess any CCs.
+As decreasing the cluster size usually increases CCs within a cluster, the next step is to decrease the the cluster size accordingly.
+This is done by following sequence of removing nodes according to an ascending list of nodes regarding their number of common channels between them and the cluster head. 
 In other words, the cluster member which has the least common channels with the cluster head will be removed first.
-When there are multiple nodes having the same amount of common channels with the cluster head, the node whose absence brings in more common channels will be removed.
-If this criterion meets a tie, the tie can be broken by removing the node with smaller node ID.
-It is possible that the cluster head removes all its neighbors before obtaining CCs, which results in a singleton cluster which is composed by itself.
-The pseudo code for this procedure is shown in Algorithm~\ref{alg_size_control_available_CCC}.
-As for the nodes which are removed from a cluster, they restore their original individual connectivity degrees, then execute Algorithm~\ref{alg0} and become either cluster heads or get included into other clusters afterwards according to Theorem~\ref{clustering:theorem}.
+When there are multiple nodes having the same amount of common channels with the cluster head, the node whose elimination results in more common channels will be removed.
+In case of a tie, it can be broken by removing the node with smaller node ID.
+It is possible that cluster heads remove all their neighbors to obtain CCs, which results in a singleton cluster.
+The pseudo code for this procedure is given as Algorithm~\ref{alg_size_control_available_CCC}.
+As for the nodes which are removed from a cluster, they restore their original individual connectivity degrees, then execute Algorithm~\ref{alg0} and become either cluster heads or get included into other clusters, see also Theorem~\ref{clustering:theorem}.
 
@@
 This means if the network density keeps on increasing, the cluster size increases linearly with the network density.
-Thus It is necessary to control the cluster size when CRN becomes denser, and this task falls upon the cluster heads.
+Thus, it is necessary to control the cluster size when CRN becomes denser, and this task falls upon the cluster heads.
 
@@
 We adopt $t$ to be between 1 and the ratio of the average neighborhood size and desired size.
-	When $t$ is smaller, \eg $t=1$, the formed cluster in the phase I will be $\delta$.
+When $t$ is smaller, \eg $t=1$, the formed cluster in phase I will be $\delta$.
 For the cluster whose members are included by other clusters, the size of this cluster will be smaller than $\delta$ after the following membership clarification phase.
-	If $t$ is chosen large, \eg $t\cdot\delta$ equals to the size of neighborhood, the mechanism of adjusting the cluster size will not work any more.
+If $t$ is chosen large, \eg $t\cdot\delta$ equals the size of the neighborhood, the mechanism of adjusting the cluster size will not work any more.
 
@@
 %C1-7
-The cluster head removes the cluster members sequentially according to the following principle, the absence of one cluster member leads to the maximum increase of CCs in the cluster.
+The cluster head removes the cluster members sequentially according to the above explained principle.
 The removed nodes restore their original individual connectivity degrees.
 This process ends when each cluster's size is smaller or equal to $t \cdot\delta$.
-This procedure is similar with that in Section~\ref{ross_p1_guarantee_ccc}, thus Algorithm~\ref{alg_size_control_available_CCC} can be reused.
+As this procedure is similar with that in Section~\ref{ross_p1_guarantee_ccc}, Algorithm~\ref{alg_size_control_available_CCC} can also be applied.
 %The $t$ is set to 1.3. 	
@@
   \includegraphics[width=0.5\linewidth]{figure2.pdf}
-  \caption{Clusters formation after the phase I of ROSS. Nodes $A, B, D$ are debatable nodes as they belong to multiple clusters.}
+  \caption{Cluster formation after phase I of ROSS. Nodes $A, B, D$ are debatable nodes as they belong to multiple clusters.}
   \label{fig2}
@@
 %%%%%%%%%%%%%%%
-We have the following lemma to show every secondary user will eventually be either integrated into a cluster or becomes a cluster head.
+We have the following lemma to show every secondary user will eventually be either integrated into a cluster or become a cluster head.
 
@@
 \end{lemma}
-
 The Proof is given in Appendix~\ref{proof_clustering:lemma1}.
@@
 If certain nodes are removed from the cluster due to guaranteeing CC or size control, these nodes may become either cluster members of another cluster head, or cluster heads themselves.
-In both cases, $i$'s \textit{individual connectivity degrees} is still smaller than these nodes.
-Note that when the removed node becomes cluster head, it will not include its former cluster head $i$, so that $i$ doesn't become cluster member and its \textit{individual connectivity degrees} doesn't change.
+In both cases, $i$'s \textit{individual connectivity degree} is still smaller than the one of the respective other nodes.
+Note that when the removed node becomes cluster head, it will not include its former cluster head $i$, so that $i$ doesn't become cluster member and so its \textit{individual connectivity degree} doesn't change.
 \end{proof}
@@
 \end{lemma}
-This lemma can be easily obtained from~\ref{clustering:lemma2} considering the $N$ is the number of all the secondary users in the CRN.
-Based on these Lemmas, we can easily obtain Theorem~\ref{clustering:lemma1},
+This lemma follows from Lemma~\ref{clustering:lemma2} considering that $N$ is the number of all the secondary users in the CRN.
+Based on the above lemmas, we have:
 \begin{theorem}
@@
 Phase I ends when no more secondary users become cluster heads.
-Based on Lemma~\ref{clustering:lemma1} and Lemma~\ref{clustering:lemma3}, the theorem is proved.
-
-As Algorithm~\ref{alg0} is executed concurrently by different secondary users, the required time can be considerably reduced.
-If we apply Algorithm~\ref{alg0} to the CRN in Figure~\ref{fig1}, the outcome can be found in Figure~\ref{fig2}.
+Based on Lemma~\ref{clustering:lemma1} and Lemma~\ref{clustering:lemma3}, Theorem~\ref{clustering:theorem} follows directly.
+Note that as Algorithm~\ref{alg0} is executed concurrently by different secondary users, the required time is typically considerably lower.
+
+If we apply Algorithm~\ref{alg0} to the example CRN in Figure~\ref{fig1}, the outcome results to the representation in Figure~\ref{fig2}.
 Node $B$ and $H$ have the same individual connectivity degree, i.e., $d_B=d_H$. As $g_H=2>g_B=1$, node $H$ becomes the cluster head and cluster $C(H)$ is $\{H, B, A, G\}$.
@@
 %\subsubsection*{Problem Description}
-As to the resulted clusters shown in Figure~\ref{fig2} after running phase I of ROSS, we notice that nodes $A, B, D$ are included in more than one cluster. 
-We refer to these nodes as \textit{debatable nodes} as their cluster affiliations are not decided.
-The clusters which include the debatable node $i$ are called \textit{claiming clusters} of node $i$, and the set of these clusters is denoted as $S_i$.  
-The debatable nodes should be exclusively associated with only one cluster and be removed from the other claiming clusters, this procedure is called \textit{cluster membership clarification}.
+After running phase I of ROSS, we notice that nodes $A, B, D$ are included in more than one cluster as shown in Figure~\ref{fig2}. 
+We refer to these nodes as \textit{debatable nodes} as their cluster affiliations are not uniquely decided.
+All clusters which include debatable node $i$ are called \textit{claiming clusters} of node $i$, and the set of these clusters is denoted as $S_i$.  
+Nevertheless, debatable nodes need to be exclusively associated with only one cluster and be removed from the other claiming clusters.
+We refer to this procedure as \textit{cluster membership clarification}.
 
 \subsubsection{Distributed Greedy Algorithm (DGA)}
-When a debatable node $i$ decides one cluster $C\in S_i$ to stay and leaves the other its claiming clusters, the principle for $i$ is that its move should result in the greatest increase of CCs in all its claiming clusters.
-As node $i$ has been notified of the spectrum availability on all the nodes in each claiming cluster, node $i$ is able to calculate how many more CCs can be produced in a claiming cluster if $i$ leaves that cluster.
-Then node $i$ decides on the cluster $C\in S_i$, if $i$ leaving cluster $C$ results in less increased CCs than leaving any other claiming clusters in $S_i$.
+When a debatable node $i$ decides to join cluster $C\in S_i$, the guiding idea is that its decision should result in the greatest increase of CCs in all its claiming clusters.
+As node $i$ has been notified of the spectrum availability on all the nodes in each claiming cluster, node $i$ is able to calculate how many more CCs will result in a claiming cluster if $i$ leaves that cluster.
+Then node $i$ decides on the cluster $C\in S_i$, if $i$ leaving cluster $C$ results in a lower increase in terms of CCs than leaving any other claiming clusters in $S_i$.
 %As to a cluster $C\in S_i$, if $i$ leaves cluster $C$ and results in less increased CCs than leaving any other claiming clusters, then $i$ chooses to stay in cluster $C$.
-When there comes a tie between two claiming clusters, $i$ chooses to stay in the cluster whose cluster head shares the most CCs with $i$.
+In case of a tie between two claiming clusters, $i$ chooses to stay in the cluster whose cluster head shares the most CCs with $i$.
 When a tie still exists, node $i$ chooses to stay in the claiming cluster which has the smallest size.
 Node IDs of cluster heads will be used to break tie in the end if necessary.
-The pseudo code of this algorithm is given in Algorithm~\ref{alg4}.
-After deciding its membership, debatable node $i$ notifies all its claiming clusters of its choice, and the claiming clusters from which node $i$ leaves also broadcast their new cluster composition and the spectrum availability on all their cluster members.
-
-The autonomous decisions made by the debatable CR nodes raise the concern on the endless chain effect in the membership clarification phase.
-A debatable node's choice is dependent on the compositions of its claiming clusters, and the members of these claiming clusters can be changed by other debatable nodes' moves.
-As a result, the debatable node which have made decision may not be content with its original move.
-There is concern that this process may go on forever.
-To erase this concern, we formulate the process of membership clarification into a game, where a equilibrium is reached after a finite number of best response updates made by the debatable nodes.
+The pseudo code of this algorithm is given by Algorithm~\ref{alg4}.
+After deciding its membership, debatable node $i$ notifies all its claiming clusters.
+%xxxxxxxxxxxxxxxxxxx
+
+The autonomous decisions made by the debatable CR nodes raises the possibility of an endless chain effect during the membership clarification phase.
+A debatable node's choice is dependent on the composition of its claiming clusters, and the members of these claiming clusters can be changed by other debatable nodes' moves.
+There is the possibility that this process may go on forever.
+However, by formulating the process of membership clarification into a game, we can show that an equilibrium is reached after a finite number of best response updates made by the debatable nodes.
+Thus, the membership clarification phase is guaranteed to terminate.
 
@@
 A game consists of three elements: a set of players, a selfish utility for each player, and a feasible strategy space for each player. 
-In a game, the players are rational and intelligent decision makers, which are related with one explicit formalized incentive expression (the utility or cost).
-Game theory provides standard procedures to study its equilibriums~\cite{game_for_communication_01}.
-In the past few years, game theory has been extensively applied to problems in communication and networking~\cite{Neel06analysisand, Wang_gtc_crn_survey_2010}.
-Congestion game is an attractive game model which describes the problem where participants compete for limited resources in a non-cooperative manner, it has the good property that Nash equilibrium can be achieved after finite steps of best response dynamic, \ie each player chooses the strategy to maximize/minimize its utility/cost with respect to the other players' strategies.
-The framework of the congestion game has been used to model certain problems in internet-centric applications or cloud computing, where self-interested clients compete for the centralized resources and meanwhile interact with each other.
-For example, server selection is involved in distributed computing platforms~\cite{Cloud_Computing_2010}, or users downloading files from cloud, etc.
-
-To formulate the debatable nodes' membership clarification into the desired congestion game, we reexamine this process from a different/opposite perspective. 
-From the new perspective, the debatable nodes are not included in any cluster and they need to decide on one cluster to join.
-When a debatable node $i$ join one cluster $C$, the decrease of CCs in cluster $C$ is $\sum_{C\in S_i}\Delta\vert K(C) \vert=\sum_{C\in S_i}({\vert K(C) \vert-\vert K(C\cup i) \vert})$.
+In a game, the players are modeled as rational and intelligent decision makers, which are related through one explicit formalized incentive expression (the utility or cost).
+Game theory provides standard procedures to study potential equilibria~\cite{game_for_communication_01}.
+Over the last decade, game theory has been extensively applied to problems in communication and networking~\cite{Neel06analysisand, Wang_gtc_crn_survey_2010}.
+Congestion game is an interesting game model which describes the problem where participants compete for limited resources in a non-cooperative manner.
+It has the good property that a Nash equilibrium can be achieved after finite steps of best response dynamic, \ie each player chooses the strategy to maximize/minimize its utility/cost with respect to the other players' strategies.
+The framework of the congestion game has been used to model server selection in distributed computing platforms~\cite{Cloud_Computing_2010}, or users downloading files from cloud, etc.
+
+To formulate the debatable nodes' membership clarification into a congestion game, we reexamine this process from a different perspective. 
+Thus, debatable nodes are not included in any cluster and they need to decide on one cluster to join.
+When a debatable node $i$ joins one cluster $C$, the decrease of CCs in cluster $C$ is $\sum_{C\in S_i}\Delta\vert K(C) \vert=\sum_{C\in S_i}({\vert K(C) \vert-\vert K(C\cup i) \vert})$.
 Then, node $i$ chooses the cluster $C$, where the decrease of CCs in cluster $C$ is smaller than the decrease if $i$ would have joined any other claiming cluster in $S_i$.
@@
   \includegraphics[width=0.37\linewidth]{singletongame_matching.pdf}
-  \caption{Debatable nodes and claiming clusters}
+  \caption{Illustration of debatable nodes and claiming clusters}
   \label{debatable_nodes_claiming_cluster}
@@
 	\item Strategy space $\sum_i, i \in \mathcal{P}$, $\sum_i$ is the set of the claiming clusters $S_i$.
-	As debatable node $i$ is supposed to choose only one claiming cluster, then only one piece of resource will be allocated to $i$.%, accordingly this congestion game is a singleton game.
-	\item 	The cost function $f(C)$ as to a resource $C$. 
+	As debatable node $i$ is supposed to choose only one claiming cluster, only a single resource will be allocated to $i$.%, accordingly this congestion game is a singleton game.
+	\item 	The cost function $f(C)$ regarding resource $C$. 
 	$f(C) = \Delta\vert K^i(C)|, C\in S_i$, which represents the decreased number of CCs in cluster $C$ when debatable node $i$ joins $C$.
@@
 
-As to singleton congestion game, there exists a pure equilibria which can be reached with the best response update, and the upper bound for the number of steps before convergence is $n^2*m$~\cite{Ackermann06purenash}, where $n$ is the number of players, and $m$ is the number of resources.
+As to singleton congestion game, there exists a pure equilibrium which can be reached with the best response update, while the upper bound for the number of steps before convergence is $n^2*m$~\cite{Ackermann06purenash}, where $n$ is the number of players, and $m$ is the number of resources.
 In our problem, the players are the debatable nodes, and the resources are the claiming clusters.
-Thus the number of steps can be expressed as $\mathcal{O}(N^3)$.
+Thus, the number of steps can be expressed as $\mathcal{O}(N^3)$.
 %
@@
 The percentage of debatable nodes in the network is shown in Figure~\ref{percentage_overlapping_node}, which is between 10\% to 60\%.
-On the other hand, the number of clusters heads is dependent on the network density and the CR node's transmission range as mentioned in Section~\ref{phaseI}.
-The simulation in \cite{robust_clustering_arxiv} shows the cluster heads account for from 3.4\% to 20\% of the total CR nodes with the increase of network density.
-Furthermore, as the game played locally and in parallel \ie a debatable node can only interact with a few claiming clusters, which greatly accelerates the execution speed.
+On the other hand, the number of cluster heads is dependent on the network density and the CR node's transmission range, as mentioned in Section~\ref{phaseI}.
+The simulation in \cite{robust_clustering_arxiv} shows that the cluster heads account for from 3.4\% to 20\% of the total CR nodes with increasing network density.
+Furthermore, as the game is played locally and in parallel \ie a debatable node can only interact with a few claiming clusters, the execution speed is significantly reduced.
 
@@
 The debatable nodes consider their claiming clusters to include all their debatable nodes, thus the membership of claiming clusters is static and all the debatable nodes can make decisions simultaneously without considering the change of membership of their claiming clusters.
-As ROSS-DFA is quicker than ROSS-DGA, the former is especially suitable for the CRN where the channel availability changes frequently.
-To run ROSS-DFA, debatable nodes execute only one loop in Algorithm~\ref{alg4}.
-
-Now we apply both ROSS-DGA and ROSS-DFA to the network in Figure~\ref{fig2} which has been applied the phase I of ROSS.
+As ROSS-DFA is quicker than ROSS-DGA, it is more suitable for CRN where the channel availability changes frequently.
+To run ROSS-DFA, debatable nodes execute only one loop of Algorithm~\ref{alg4}.
+
+Now we apply both ROSS-DGA and ROSS-DFA to the network in Figure~\ref{fig2} after phase I of ROSS is complete.
 %C1-8
-In the network, node $A$'s claiming clusters are cluster $C(C), C(H)\in S_A$, their members are $\{A,B,C,D\}$ and $\{A,B,H,G\}$ respectively. 
-The two possible strategies of node $A$ is illustrated in Figure \ref{fig3}.
-In Figure \ref{AinC}, node $A$ staying in $C(C)$ and leaving $C(H)$ brings 2 more CCs to $S_A$, which is more than that brought by another strategy shown in \ref{AinH}.
-After the decisions made similarly by the other debatable nodes $B$ and $D$, the final clusters are formed as shown in Figure~\ref{final_clustering_ross}.
+In the network, node $A$'s claiming clusters are cluster $C(C), C(H)\in S_A$, while the respective members are $\{A,B,C,D\}$ and $\{A,B,H,G\}$. 
+The two possible strategies of node $A$ are illustrated in Figure \ref{fig3}.
+In Figure \ref{AinC}, node $A$ stays in $C(C)$ and leaves $C(H)$ which brings 2 more CCs to $S_A$, which is more than that brought by another strategy, as shown in \ref{AinH}.
+After similar decisions are made by the other debatable nodes $B$ and $D$, the final clusters are formed as shown in Figure~\ref{final_clustering_ross}.
 
@@
   \includegraphics[width=0.5\linewidth]{final_clustering_ross.pdf}
-  \caption{Final formation of clusters. Common channels are shown beside corresponding clusters.}
+  \caption{Final formation of clusters. Common channels are shown as well as the corresponding clusters.}
   \label{final_clustering_ross}
@@
 \label{performance}
-%In this section, we evaluate the performances of ROSS.
-The schemes involved in the simulation are as follows,
-\begin{itemize}
-\item ROSS without size control: ROSS-DGA, ROSS-DFA.
-\item ROSS with size control, \ie ROSS-$\delta$-DGA and ROSS-$\delta$-DFA where $\delta$ is the desired cluster size.
-In the following, we refer to the above mentioned four schemes as the variants of ROSS.
-\item SOC~\cite{LIU_TMC11_2}, a distributed clustering scheme pursuing cluster robustness.
-\item Centralized robust clustering scheme. 
-As shown in Section~\ref{centralized_solution}, the centralized robust clustering scheme is formulated as an integer linear optimization problem and is solved by MATLAB with the function $bintprog$.
-\end{itemize}
-
-%The ROSS without size control mechanism is similar with the schemes proposed in \cite{Li11_ROSS}.
-
-%Before we investigating the performance of the clustering schemes with simulation, we apply the two comparison clustering schemes in the example CRN in Figure~\ref{fig1}, and make an initial comparison in terms of the amount of CCs.
-%As to the centralized robust clustering scheme, we set the desired cluster size $\delta$ as 3, as a result, according to the network topology, the collection of all the possible clusters
-%$\mathcal{S}=\{\{A\}, \{B\},\dots,\{B,C\},\{B,A\},\{B,H\},\cdots,\{B,A,C\},$\\$\{B,H,C\}, \{A,D,C\},\cdots\}$, and $|\mathcal{S}|=38$.
-%We set $\rho_1$ and $\rho_1$ as 0.2 and 0.8 respectively.
-%The formed clusters by the centralized clustering scheme are shown in Fig.~\ref{fig:final_clustering_LP}.
-%%$\{\{D,E,F\},\{A,C,G\},\{H,G\}\}$, the numbers of CCs are 2, 3, 3.
-%The resulted clustering solutions from SOC is shown in Fig.~\ref{fig:final_clustering_soc}.
-%%
-%We compare the average number of CCs achieved by different schemes, the results of ROSS\footnote{In this example network, both ROSS-DGA and ROSS-DFA and their size control variants form the same clusters)}, centralized and SOC are 2.66, 2.66, and 3 respectively.
-%Note there is one singleton cluster $C(H)$ generated by SOC, which is not preferred.
-%When we only consider the clusters which are not singleton, the average number of CCs of SOC drops to 2.5. 
+Taking the final clustering result of ROSS into account for our toy example shown in Figure~\ref{final_clustering_ross}, we can compare the outcome with our centralized scheme proposed in Equation~\ref{centralized_opt} as well as the state-of-the-art algorithm SOC~\cite{LIU_TMC11_2}.
+Those corresponding results of the later two schemes are shown in Figure~\ref{fig:final_clustering}.
+We observe for this example case that ROSS and the centralized scheme achieve cluster sizes that are more balanced, while SOC leads to a larger variance in terms of the cluster size.
+Regarding the amount of CCs, the same observation holds. 
 \begin{figure}[ht]
@@
 \end{center}
-\caption{Final clusters formed by the centralized clustering scheme and SOC.}
+\caption{Final clusters formed by SOC as well as the centralized clustering scheme.}
 \label{fig:final_clustering}
@@
 
-As to the CRN shown in Figure~\ref{fig1}, the resulting clusters by the centralized scheme and SOC are shown in Figure~\ref{fig:final_clustering}.
-We now investigate the performances of the schemes in the following aspects.
-
+In the following, we are interested in a more general performance comparison regarding clustering in CRNs.
+We therefore present in the following an extensive evaluation study.
+We base our evaluations on simulations, and consider the following comparison schemes:
+\begin{itemize}
+\item ROSS without size control: ROSS-DGA, ROSS-DFA;
+\item ROSS with size control, \ie ROSS-$\delta$-DGA and ROSS-$\delta$-DFA where $\delta$ is the desired cluster size;
+\item SOC~\cite{LIU_TMC11_2}, a distributed clustering scheme pursuing cluster robustness;
+\item Centralized robust clustering scheme; in our evaluations we use the built-in function $bintprog$ of MATLAB to solve the corresponding integer optimization problem given in Equation~\ref{centralized_opt}
+\end{itemize}
+
+Given these comparison schemes, we are interested in the following performance metrics regarding clustering:
 \begin{itemize}
 \item \textbf{The average number of CCs per non-singleton cluster.}
-Non-singleton cluster refers to the cluster whose cluster size is larger than one.
-Previous work \cite{LIU_TMC11_2} and \cite{Li11_ROSS} claim that the larger average number of CCs over all the clusters indicates robustness , from which we see two flaws.
-First, the unclustered CR nodes (synonym of singleton clusters) should not be considered when calculating the average number of CCs, as singleton clusters don't contribute to the collaborative computing or sensing.
-Second, the average number of CCs doesn't necessarily indicate the robustness of individual clusters, because the ability for a cluster to sustain also depends on cluster size and the locations of the cluster members, but these information can not be illustrated in the average number of CCs.
-In the performance evaluation, we will examine the metric of average number of CCs per non-singleton cluster, which excludes the bias brought in by the unclustered CR nodes.
-Moreover, we will examine whether this metric reflects the robustness of the clusters.
-
+Previous work \cite{LIU_TMC11_2} and \cite{Li11_ROSS} claim that the larger average number of CCs over all the clusters indicates robustness.
+As mentioned, this interpretation has several shortcomings:
+First, singleton clusters should not be considered when calculating the average number of CCs, as singleton clusters don't contribute to the collaborative computing or sensing.
+Second, the average number of CCs doesn't necessarily indicate the robustness of a cluster, because the ability of a cluster to sustain primary user activity also depends on the size and the location of the cluster members.
+This information, however, is not reflected by the average number of CCs.
+Thus, in the following we will consider the average number of CCs per cluster, excluding singleton clusters from this averaging, as our first performance metric.
 \item \textbf{Robustness of the clusters against newly added PUs.}
-Robustness is illustrated by the number of the unclustered CR nodes in the CRN, after the CRN being challenged by the increasing number of PUs.
-This metric indicates the robustness of the clusters, \ie as to the clusters formed for a given CRN and spectrum availability, how many CR nodes can still be benefited from the clusters when the spectrum availability decreases.
-
+If clusters are less robust, this leads to an increasing number of unclustered CR nodes if clusters are exposed to random primary user activity.
+We thus are interested in this effect as a second measure for robustness. 
+In particular, we are interested in the number of CR nodes which are still part of a cluster after exposing the clusters to primary user activity.
 \item \textbf{Cluster sizes.}
-%Specific clusters size is pursued in many applications due to energy preservation and the system design ~\cite{clustering_globecom11}.
-We investigate the distribution of CRs residing in the formed clusters with different sizes.
-
-\item \textbf{Amount of control messages involved.}
-We investigate the number of control messages involved in the clustering process.
-
+We investigate the distribution of the size the formed clusters.
+This metric reflects that above mentioned size constraints, i.e. clusters are supposed to be neither too big nor too small.
+\item \textbf{Control message overhead.}
+We investigate the number of control messages involved until the final clustering result is established .
 \item \textbf{Influence from inaccurate spectrum sensing.}
-The above simulations are conducted under the assumption of perfect spectrum sensing.
-As spectrum sensing in practise is subject to errors, we are interested to see the performance of the distributed schemes when the spectrum sensing is not perfect.
-%The errors in spectrum sensing is inevitable, and the decision is made by the secondary users and based on the sensing results, without considering the difference between the sensing result and the ground truth.
-The false negative in spectrum sensing, which misdetects the presence of the active primary users, is harmful to the primary users and should be avoided as much as possible.
-On the contrary, a false positive \ie which reports the presence of active primary users when there are actually none, only decreases the available spectrum for the secondary users.
-In this regard, we assume only the false negative exists in the spectrum sensing.
-
-We assume when a secondary user is within the transmission range of an active primary user, the probability that it misdetects and thus regards a channel as being available equals to the rate of false negative.
-The secondary users make clustering decisions based on the imperfect spectrum sensing.
-After the clustering process is completed, we correct the spectrum availability with the ground truth.
-Then certain formed clusters may be affected as their CCs which are obtained due to false negative will be revoked.
-%When the clustering process is completed, we will examine the performances on robustness and cluster size control with the group truth spectrum availability.
-%C3
+While most of our evaluations are conducted under the assumption of perfect channel sensing by the individual CR nodes, an important question relates to the fact how the clustering performs under imperfect sensing accuracy.
+In case of erroneous channel sensing, false negatives harm primary users while false positives harm the CR nodes.
+Both effects obviously impact the clustering process. 
+However, in the following we only consider the impact from false negatives. 
+In particular, we assume that primary user activity is only correcly detected by a CR node in transmission range with a certain probability, i.e. there is a certain probability for misdetections.
+Given this erroneous sensing result, the secondary users nevertheless make their clustering decisions.
+As we are interested in the distorting impact of the erroneous channel sensing results on the clustering process, after the clustering is complete, we provide ground truth and reevaluate the discrepancy between the assumed channel utilization and its effect on clustering, and the de-facto channel utilization and how this affects the CCs of formed clusters.
 \end{itemize}
 
-The simulation consists of two parts, first we investigate the performance of centralized scheme and the distributed schemes in a small network, as there is no polynomial time solution available to solve the centralized problem.
-In the second part, we investigate the performance of the proposed distributed schemes in the CRN with different scales and densities.
-The following simulation setting is the same for both simulation parts.
+Our performance evaluation is split into two parts:
+First we investigate the performance of the centralized scheme and the distributed schemes for a small network, as the run-time for the centralized solution quickly grows out of hand as a function of the network size .
+In the second part, we investigate the performance only of the distributed schemes for larger settings.
+The following simulation settings are identical for both evalutions:
 CRs and PUs are deployed on a two-dimensional Euclidean plane.
@@
 The number of licensed channels is 10, each PU is operating on each channel with probability of 50\%.
-The other parameters \ie the number of CR and PU, and their transmission ranges are given in the beginning of the respective simulation sections.
 %C1-10
 The constant $t$ which is used to control cluster size for ROSS (discussed in Section~\ref{ross_p2_cluster_pruning}) is 1.3.
-CR users are assumed to be able to sense the existence of primary users and identify available channels.
+CR users are assumed to sense the existence of primary users and identify available channels perfectly, unless we investigate the impact from erroneous channel sensing.
 All primary and CR users are assumed to be static during the process of clustering.
-The simulation is written in C++, and the performance results are averaged over 50 randomly generated topologies, and the confidence interval corresponds to 95\% confidence level.
+All other parameters \ie the number of CR and PU, and their transmission ranges are given at the beginning of the respective subsections.
+The simulation is written in C++, and the performance results are averaged over 50 randomly generated topologies.
+We provide confidence interval corresponding to a 95\% confidence level.
 
 \subsection{Centralized Schemes vs. Decentralized Schemes}
-In this part of simulation, there are 10 primary users and 20 CR users dropped randomly (with uniform distribution) in a square area where side length is $A$.
-$A$ is a positive value and the transmission ranges of both primary and CR users are set to $A/3$.
-By doing this, we try to abstract from the influence of any given physical layer technology, and A can be given a concrete value in practice when the physical layer technology is decided.
-%C1-10, C1-9
-%There are 10 available channels. 
-%With this setting, the average number of neighbours of one CR user is 4.8.
-%Each primary user randomly occupies one channel, and 
-When clustering scheme is executed, around 7 channels are available on each CR node.
-The desired cluster size $\delta$ is 3.
-As for the centralized scheme, the parameters used in the \textit{punishment} for choosing the clusters with undesired sizes are set as follows, $\rho_1 =  0.4$, $\rho_2 =  0.6$.
-
-\subsubsection{CCs in Non-singleton Clusters}
-\label{ccc_20}
-Figure~\ref{ccc_per_nonsingleton} shows the centralized schemes outperform the distributed schemes.
-SOC achieves the most CCs among the distributed schemes, because SOC groups the neighboring CRs which share the most abundant spectrum together, without considering the number of them.
+We start with the comparison of the centralized scheme versus various distributed ones.
+For this, we consider 10 primary users and 20 CR users are dropped randomly (with uniform distribution) in a square area where side length is $A$.
+Transmission ranges of both primary and CR users are set to $A/3$.
+By doing this, we abstract from the influence of any given physical layer technology and propagation environment parameters.
+Due to the parameterization, on average 7 channels are available per CR node when the clustering process is started.
+We set the desired cluster size $\delta$ as 3.
+As for the centralized scheme, we set the following parameters numerically: $\rho_1 =  0.4$, $\rho_2 =  0.6$.
+
+We start with the consideration of the CCs in all non-singleton clusters.
+Figure~\ref{ccc_per_nonsingleton} shows that basically the centralized schemes outperforms all distributed schemes in terms of the average number of CCs per cluster.
+SOC achieves the most CCs among the distributed schemes, because SOC groups the neighboring CRs which share the most abundant spectrum together, without considering the size of them.
 %We have discussed the flaw of this metric as it doesn't convey the number of unclustered CR nodes, in fact, 
-As a result, SOC also generates the most unclustered CRs.
-As to the variants of ROSS, we notice that the greedy mechanism increases CCs in non-singleton clusters significantly.
-%, this is due to the procedure that debatable nodes greedily look for better affiliation to improve the number of CCs.
-%We also notice that the size control feature doesn't affect the number of CCs for both ROSS-DGA and ROSS-DFA.
-%Size control mechanism converts the large clusters into small ones, but meanwhile clusters with the desired sizes have to be made when forming smaller clusters is possible.
-%, which can also be observed in the large scale CRN in Section~\ref{largeScaleCRN}.
-
+However, as a consequence, SOC also generates the most singleton clusters.
+As to the variants of ROSS, we notice that the greedy mechanism (i.e. the ROSS-DGA variants) maximize the CCs in non-singleton clusters significantly.
 \begin{figure*}[th]
@@
 
-\subsubsection{Cluster Size}
-\label{cluster_size}
-
-Figure~\ref{size_control} depicts the empirical cumulative distribution of the CRs in clusters of different sizes.
+Figure~\ref{size_control} provides further insights into the performance comparison.
+Here, we depict the empirical cumulative distribution function of the size of the clusters.
 %First, given the channel availability in the CRN, SOC generates more unclustered CR nodes than other schemes.
-The centralized schemes don't produce unclustered CR nodes in the simulation.
-The unclustered nodes generated by ROSS-DGA/DFA account for 3\% of the total CR nodes, as comparison, 10\% of nodes are unclustered when applying SOC.
+The centralized schemes don't result in any singleton clusters in the the considered evaluation scenarios.
+In contrast, ROSS-DGA/DFA account for 3\% singleton clusters of the total CR nodes, as compared to 10\% of nodes being unclustered when applying SOC.
 ROSS-DGA and ROSS-DFA with size control feature generate 5\%-8\% unclustered CR nodes, which is due to the cluster pruning procedure (discussed in Section~\ref{ross_p1_guarantee_ccc} and Section~\ref{ross_p2_cluster_pruning}).
-
-In terms of cluster size, the clusters resulted from centralized schemes and ROSS with cluster size control mechanism have little deviation from the desired cluster size.
-%As to ROSS-DFG and ROSS-DFA with size control feature, CR nodes reside averagely in clusters whose sizes are 2, 3 and 4.
-The sizes of clusters resulted from ROSS-DGA and ROSS-DFA are disperse, but appear to be better than SOC, i.e., the 50\% percentiles for ROSS-DGA, ROSS-DFA and SOC are 4.5, 5, and 5.5, and the 90\% percentiles for the three schemes are 8, 8, and 9, the corresponding sizes resulted by ROSS are closer to the desired size.
-
-\subsubsection{Robustness of the formed clusters}
-%When the number of PUs in CRN increases, or their operation becomes more intensive, some clusters don't seize any CCs any more, so that the cluster members and the cluster heads become unclustered, or singleton clusters.
-%If there is no common channels available any more because of the new added PUs, the cluster is regarded as destroyed and the former cluster member CRs become unclustered CRs or in other words singleton clusters.
-%We investigate the number of singleton clusters with primary users whose intensity of activities are varying.
-%We will obtain two observations by examining this metric.
-%First, we will know how many CR nodes are unclusterred by applying the robust clustering schemes in a given CRN.
-In this part of simulation, we put PUs sequentially into CRN to decrease the available spectrum.
-10 PUs are in the network at start, extra 19 batches of PUs are added sequentially and each batch includes 5 PUs. 
-Figure~\ref{singleton_clusters} shows certain clusters can not maintain and the number of unclustered CR nodes increases when the number of PUs increases.
-The centralized scheme with desired size of 2 generates the most robust clusters, meanwhile, SOC results in the most vulnerable clusters.
-The centralized scheme with desired size of 3 doesn't outperform the variants of ROSS, because pursuing cluster size prevents forming the the clusters with more CCs.
-In contrary, the variants of ROSS generate some smaller clusters which are more likely to maintain when there are more PUs.
-
-Considering the number of secondary users residing in a cluster, ROSS based schemes benefit 5\%, 30\% and 230\% more secondary users from neighborhood cooperation than SOC, when the numbers of newly added PR are 10, 40 and 80 respectively.
-The above observation also shows the average number of CCs of non-singleton clusters doesn't necessarily illustrate the robustness  of cluster, \ie SOC obtains the most CCs among the distributed schemes, but the resulted clusters are vulnerable.
-
-\subsubsection{Control Signaling Overhead}
-
-In this section we compare the overhead of signaling involved in different clustering schemes.
-We count the number of \textit{transmissions of control messages} as message complexity~\cite{complexity_aggregation_2011}, without distinguishing broadcast or uni-cast control messages.
-In Section~\ref{ross}, this metric is synonymous with the \textit{the number of updates}.
+In terms of cluster size, the clusters resulting from the centralized schemes and ROSS with cluster size control mechanism have little deviation from the desired cluster size.
+In contrast, the size of clusters resulting from ROSS-DGA and ROSS-DFA have a higher variance, but appear to be better than SOC, i.e., the 50\% percentiles for ROSS-DGA, ROSS-DFA and SOC are 4.5, 5, and 5.5, and the 90\% percentiles for the three schemes are 8, 8, and 9.
+Thus, the corresponding sizes resulting from ROSS are closer to the desired size.
+
+Next, we consider the robustness of clusters if facing random primary user activity.
+We thus extend the simulation by adding more primary users sequentially into CRN, leading to a decreasing spectrum availability.
+While 10 primary users are in the network at start, some extra19 batches of primary users are added sequentially, each batch including 5 primary users that are placed randomly in the area.
+These added primary users choose then an active channel also at random. 
+Figure~\ref{singleton_clusters} shows the corresponding average number of unclustered CR nodes as a result of this significant increase in primary user activity. 
+The figure reveals that the centralized scheme with a desired size of 2 leads to the best robustness, while SOC leads to the worst one.
+Surprisingly, the centralized scheme with desired size of 3 doesn't outperform the variants of ROSS, because pursuing larger cluster sizes generally leads to clusters with a lower amount of CCs. 
+In contrary, the variants of ROSS generate some smaller clusters which are more likely to be maintain despite the increasing primary user activity.
+
+Alternatively, we can consider the total share of users (still) residing in a cluster after the addition of the primary users as performance metric for robustness.
+If we do so, the ROSS-based schemes maintain 5\%, 30\% and 230\% more secondary users within clusters than SOC, when the numbers of newly added PR are 10, 40 and 80 respectively (no figure is provided for this data).
+%XXXXX
+The above observation illustrates clearly that the average number of CCs of non-singleton clusters doesn't necessarily reflect the robustness of clusters, \ie SOC obtains the most CCs among the distributed schemes, but the resulting clusters are vulnerable to primary user activity.
+
+We finally turn to a comparison of the involved signaling overhead for the different clustering schemes.
+For this, we count the number of \textit{transmissions of control messages} as metric~\cite{complexity_aggregation_2011}, without distinguishing broadcast or uni-cast control messages.
+%In Section~\ref{ross}, this metric is synonymous with the \textit{the number of updates}.
 %We don't consider the the control messages which are involved in neighborhood discovery, which is the premise and deemed to be the same for all clustering schemes.
@@
 As to ROSS, in the first phase the maximal number of broadcast is $N$ according to~\ref{clustering:theorem}.
-The upper bounds for the transmissions are $n^2m$ and $n$ for ROSS-DGA and ROSS-DFA respectively.
-Scheme SOC consists of three rounds, and in each round every node needs to broadcast to do comparisons and cluster mergers.
-The centralized scheme is conducted at the centralized control device, which involves information aggregation and clustering decision dissemination.
-To analyze the centralized scheme's message complexity, we adopt the backbone structure proposed in~\cite{Efficient_broadcasting_gathering_adhoc}, and apply ROSS to generate cluster heads which serve as the backbone.
-In the process of information aggregation, all the nodes transmit information to the cluster heads which forward the messages to the controller. 
-In the process of dissemination, all the cluster heads and the debatable nodes broadcast the clustering result, thus the upper bound for the number of broadcast is $N+m+n$.
-
-%, when a CR node decides itself to be the cluster head, it broadcasts a message containing its ID, cluster members and the set of CCs in its cluster.
-%In the second phase, a debatable node broadcasts its affiliation to inform its claiming clusters, then the cluster heads of the claiming clusters broadcast message about the new cluster members if they are changed due to the debatable node's decision.
-%The upper bound of the total number of the control messages involved in cluster formation is analyzed in Theorem~\ref{clustering:theorem} and Section~\ref{clustering:phaseII:game}.
-%
-%The comparison scheme SOC consists of three rounds of execution. 
-%In the first two rounds, every CR node maintains its own cluster and seeks either to integrate neighboring clusters or to join one neighboring cluster.
-%The final clusters are obtained in the third round. 
-%In each round, every CR node is involved in comparisons and cluster mergers.
-%%Comparing with the second phase of ROSS, only debatable nodes to communicate with cluster heads to clarify their membership.
-%%The signalling overhead for centralized scheme comes from two processes, the the process of collecting information to the centralized controller, and the process that the controller spreads the clustering result to all the CR nodes.
-%
-%The centralized scheme is conducted at the centralized control device, but it involves two phases of control message transmission.
-%The first phase is information aggregation, in which every CR node's channel availability and neighborhood is transmitted to the centralized controller.
-%iIn the second phase, the control broadcasts the clustering solution, which is disseminated to every CR node.
-%%
-%We adopt the algorithm proposed in~\cite{Efficient_broadcasting_gathering_adhoc} to broadcast and gather information as the algorithm is simple and self-stabilizing.
-%This scheme needs building a backbone structure to support the communication. 
-%We apply ROSS to generate cluster heads which serve as the backbone, and the debatable nodes are used as the gateway nodes between the backbone nodes.
-%As the backbone is built for one time and supports the transmission of control messages later on, we don't take account the messages involved in building the backbone.
-%As to the process of information gathering, we assume that every cluster member sends the spectrum availability and its ID to its cluster head, which further forwards the message to the controller, then the number of transmissions is $N$.
-%As to the process of dissemination, in an extreme situation where all the gateway and the backbone nodes broadcast, the number of transmissions is $m + n$, where $m$ is the number of cluster heads and $n$ is number of debatable nodes.
-
-The number of control messages which are involved in ROSS variants and the centralized scheme is related with the number of debatable nodes.
+The upper limits for the message exchanges are $n^2m$ and $n$ for ROSS-DGA and ROSS-DFA, respectively.
+SOC consists of three rounds, and in each round every node needs to perform a broadcast to do comparisons and cluster merging.
+The centralized scheme is conducted at some control device, which involves information aggregation and subsequent dissemination of clustering decisions.
+To analyze the centralized scheme's message overhead, we adopt a backbone structure proposed in~\cite{Efficient_broadcasting_gathering_adhoc}, and apply ROSS to generate cluster heads which serve as the backbone.
+In the stage of information aggregation, all the nodes transmit information to the cluster heads which forward the messages to the controller. 
+In the dissemination stage, all the cluster heads and the debatable nodes broadcast the clustering result, thus the upper limit for the number of broadcast is $N+m+n$.
+
+The number of control messages which are involved in ROSS variants and the centralized scheme is related to the number of debatable nodes.
 Figure~\ref{percentage_overlapping_node} shows the percentage of debatable nodes with different network densities.
@@
   \includegraphics[width=0.6\linewidth]{percentage_overlapping_node.pdf}
-  \caption{The percentage of debatable nodes after phase I of ROSS.}\label{percentage_overlapping_node}
+  \caption{Percentage of debatable nodes after phase I of ROSS.}
+  \label{percentage_overlapping_node}
 \end{figure}
@@
 %The complexity parameters are the number of nodes $n$ in network, number of clusters $h$.
-Table \ref{tab_overhead} shows message complexity, quantitative amount of control messages, and size of control messages.
+Table \ref{tab_overhead} shows the messaging overhead , quantitative amount of control messages, and size of control messages for the different schemes under consideration.
 Figure~\ref{control_msg} shows the analytical result of the amount of transmissions involved in different schemes.
@@
 \hline
- Scheme 				&Message Complexity 	&   Quantitative number of messages 		& Content and size of the message 									\\ \hline
+ Scheme 				&Message Overhead 	&   Quantitative number of messages 		& Content and size of the message 									\\ \hline
  ROSS-DGA, ROSS-$\delta$-DGA 	&$\mathcal{O}(N^3)$ (worst case)		&   $N+n^2m$ (upper bound)  				&   \multirow{2}{*}{\parbox{7.7cm}{PhaseI: ID, $d_i$,$g_i$, which are 3 bytes;\\ PhaseII: Cluster head $i$ broadcasts channel availability to all \\ members, where are $|C(i)| |\mathcal{K}|$ bytes}}								\\ \cline{1-3}
@@
   \includegraphics[width=0.6\linewidth]{number_controlMsg.pdf}
-  \caption{Quantitative amount of control messages.}
+  \caption{Absolute amount of control messages required for clustering.}
+%XXXXXX Quantitative, or Absolute
   \label{control_msg}
@@
 \label{largeScaleCRN}
-In this section we investigate the performances of the proposed distributed clustering schemes with different network scales and densities.
-The transmission range of CR is $A/5$, PU's transmission range is $2A/5$.
-The initial number of PU is 30.
+We now switch to a more fine-grained investigation only of the distributed schemes. 
+We are here most important interested in their properties when the network size and density scales.
+In our scenario, we set now the transmission range of CR to $A/5$ while the primary user transmission range is set to $2A/5$.
+The initial number of primary users is set to 30.
 %The number of CR is 100, 200 and 300, and the average number of neighbours of each CR is 9.5, 20, and 31.
-The desired sizes adopted are listed in the Table~\ref{Simulation_para}, which is about 60\% of the average number of neighbors.
+As we scale now the number CR nodes in the scenario, we adjust the desired size in the clustering process.
+Our adopted values are listed in the Table~\ref{Simulation_para}, which represent about 60\% of the average number of neighbors.
 %When run ROSS, the parameter $t$ which is used to control cluster size in phase I is 1.3.
@@
   \includegraphics[width=.7\linewidth]{ccc_large_scale_color_082017_newdata_no_texture.pdf}
-  \caption{Average number of CCs of non-singleton clusters}
+  \caption{Average number of CCs of non-singleton clusters in case of increasing the number of CR nodes.}
   \label{ccc_large_scale}
 \end{figure}
-
-The average number of CCs of the non-singleton clusters is shown in Figure~\ref{ccc_large_scale}.
-Here we don't see the obvious difference between different schemes on the number of CCs.
-%SOC achieves the most CCs per non-singleton cluster, but the lead over the variants of ROSS decreases significantly when $N$ increases.
-%This means SOC out performs in terms of the average number of CCs per non-singleton cluster when network is sparse.
-%This is also observed in the evaluation in Section \ref{ccc_20} where $N=20$.
-%When the network becomes denser, even this metric favours SOC as discussed in the beginning of Section~\ref{performance}, ROSS-DGA achieves even more CCs than SOC, and ROSS-DFA and ROSS-$\delta$-DGA increase the number of CCs visibly.
-
-\subsubsection{Robustness of the Formed Clusters}
-Here we see how robust clusters are when exposed to the increasing influence of PUs.
-We increase primary users' activity by importing 20 batches of PUs sequentially in CRN, where each batch includes 10 PUs. 
-%
-Figure~\ref{singleton_clusters_100} and \ref{singleton_clusters_200} show when $N=100$ and 200, with the same intensity of PUs' activities, more unclustered CR nodes are resulted from SOC than the variants of ROSS,
-When $N=300$ as shown in Figure~\ref{singleton_clusters_300} and new PUs are not many, ROSS-DGA/DFA generate slightly more unclustered CR nodes than SOC, but SOC's performance deteriorates quickly when the number of PUs continue increasing.
-%
-From Figure~\ref{singleton_clusters_100} to~\ref{singleton_clusters_300}, we can see that significantly less unclustered CR nodes are generated by ROSS with size control mechanism.
-Besides, the greedy mechanism moderately strengthens the robustness of the clusters.
-%We only show the average values of the variants of ROSS as their confidence intervals overlap.
-
+We start again with considering the average number of CCS over all non-singleton clusters, shown in Figure~\ref{ccc_large_scale}.
+Note that in this case we increase the number of CR nodes in the scenario.
+The result does not reveal, as in the previous section, a significant performance advantage of either of the distributed schemes.
+
+We next consider the robustness of the formed clusters in case that more and more primary users are added to the scenario.
+In this case, we increase primary users' activity by adding 20 batches of primary users sequentially in CRN, each batch including 10 primary users which are placed randomly and select a channel at random.
+Figure~\ref{singleton_clusters_100} and \ref{singleton_clusters_200} show the corresponding results for $N=100$ and 200 CR nodes in the scenario.
+We basically see that as the primary user activity increases, more unclustered CR nodes result from SOC than the variants of ROSS.
+This correlates a somewhat similar observation in the previous section.
+When $N=300$, as shown in Figure~\ref{singleton_clusters_300}, and the amount of newly added primary users is moderate, ROSS-DGA/DFA results in slightly more unclustered CR nodes than SOC, while SOC's performance deteriorates quickly when the number of primary users continue increasing.
+Also, Figures~\ref{singleton_clusters_100} to~\ref{singleton_clusters_300} reveal that ROSS with size control mechanism results in significantly less singleton clusters.
 \begin{figure*}[t]
@@
 
-\subsubsection{Cluster Size Control}
-Figure~\ref{nClusters_largeNetwork} shows when network density increases, \ie $N$ changes from 100 to 300 in the same area, the number of clusters resulted from SOC increases linearly, whereas that by ROSS increases by a smaller margin.
+We next turn to the size of the formed clusters under the different distributed schemes.
+For this we study in Figure~\ref{nClusters_largeNetwork} the average number of total clusters formed under the different schemes for the different parameter combinations considered.
+The figure shows that the number of clusters resulting from SOC increases linearly, whereas the number of formed clusters increases sub-linearly in case of the variants of ROSS.
 This result coincides with the analysis in Section~\ref{ross_p2_cluster_pruning}.
 %When the network becomes denser, more clusters are generated by SOC compared with ROSS variants.
-To see the distribution of the sizes of formed clusters, for each network density, we depict empirical cumulative distribution of CR nodes which are in clusters with different sizes in Figures~\ref{cdf_clusterSize_100}~\ref{cdf_clusterSize_200}~\ref{cdf_clusterSize_300} respectively.
+We furthermore consider the empirical distribution function of the size of the formed clusters, for each considered network density, in Figures~\ref{cdf_clusterSize_100}~\ref{cdf_clusterSize_200}~\ref{cdf_clusterSize_300} respectively.
 \begin{figure}[!h]
@@
 
-The cluster sizes resulted from the variants of ROSS are in proximity to the desired size, \ie as shown in Figures~\ref{cdf_clusterSize_100}, 90\% of CR nodes are in the clusters whose sizes are between 3 and 9, while for SOC, only 17\% of nodes are in the clusters with these sizes.
-Similarly, when $N=200$ and desired size is 12 as shown in Figure~\ref{cdf_clusterSize_200}, 80\% of nodes are in the clusters whose sizes are between 6 and 18, meanwhile only 30\% of nodes are in the clusters with these sizes when SOC is executed.
+The ECDF results show that the cluster sizes resulting from the variants of ROSS are clearly governed by the the desired size, \ie as shown in Figures~\ref{cdf_clusterSize_100}, 90\% of CR nodes are in clusters whose sizes are between 3 and 9, while for SOC, only 17\% of nodes are in the clusters with these sizes.
+Similarly, when $N=200$ and the desired size is 12 (as shown in Figure~\ref{cdf_clusterSize_200}), 80\% of nodes are in clusters whose sizes are between 6 and 18, while only 30\% of nodes are in clusters of similar sizes when SOC is executed.
 %Now we check how many CR nodes are in the clusters whose sizes deviate not much from the desired size, where we put the deviation limit at $\pm 50\%$ of the desired size.
-The clusters sizes from ROSS-$\delta$-DGA and ROSS-$\delta$-DFA concentrates more around the desired size than that from ROSS-DGA and ROSS-DFA.
-In contrary, the clusters from SOC demonstrates obvious divergence on cluster sizes.
-
-%This means that the sizes of the clusters generated by ROSS-DGA are limited by the network density, and the size control feature further restricts the appearances of the big clusters, thus when the variants of ROSS are implemented, most of the CR nodes are in the clusters which are slightly smaller than the desired size.
-The limitation of distributed scheme ROSS is it doesn't generate clusters whose sizes exceed the cluster head's neighborhood.
-The reason is with ROSS, cluster heads form clusters on the basis of their neighborhood, thus don't involve the nodes out of the neighborhood.
-
-\subsubsection{The Performance with False Negative in Spectrum Sensing}
-
-Figure~\ref{false_negative_ccc} shows the average number of CCs decrease slightly when the false negative rate increases.
-The size distribution of the ROSS-DGA, ROSS-$\delta$-DGA and SOC is shown in Figure~\ref{false_negative_CDF}.
+The cluster sizes from ROSS-$\delta$-DGA and ROSS-$\delta$-DFA concentrate more around the desired size than that of ROSS-DGA and ROSS-DFA.
+
+We finally turn to the results of clustering under erroneous spectrum sensing.
+In Figure~\ref{false_negative_ccc} we first study the impact of erroneous spectrum sensing and subsequent clustering on the number of CCs per cluster.
+The figure shows that the average number of CCs decreases slightly when the false negative rate increases.
+Nevertheless, as with the previous investigated scenarios, the results do not show large differences between the distributed variants.
 \begin{figure}[!h]
@@
 \end{figure}
-For all the schemes, when false negatives increase, the number of singleton clusters and smaller clusters increases accordingly.
-The clusters resulted from SOC are affected by the sensing errors heavily.
-More unclustered nodes are generated, and a lot of small clusters are formed, \eg when false negative rate is 30\%.
-In contrary, ROSS variants are resilient in terms of unclusterd nodes and cluster sizes.
-We can conclude that due to the negotiation within neighborhoods, ROSS variants successfully rules out the channels obtained due to false negative sensing.
+We furthermore consider the ECDF of the size of the formed clusters under erroneous spectrum sensing in Figure~\ref{false_negative_CDF}.
+For all the schemes, when the rate of false negatives increases, the number of singleton clusters and smaller clusters increases accordingly.
+Clusters formed by SOC are furthermore affected by the sensing errors significantly.
+More unclustered nodes are generated, and a lot of small clusters are formed, \eg when the false negative rate is 30\%.
+In contrary, the ROSS variants are resilient in terms of unclustered nodes and cluster sizes.
+We can conclude that due to the negotiation step within neighborhoods, ROSS variants successfully rule out the false negative channels resulting from erroneous spectrum sensing. 
+This is an interesting and remarkabl advantage of ROSS in comparison to SOC.
 \begin{figure}[!h]
@@
 
-\subsection{Insights Obtained from the Simulation}
-The simulation with large CRN network confirms the conclusion drawn from the small CRN network.
-First, the average number of CCs per cluster, which is adopted as metric for cluster robustness, is not able to tell the robustness against the increasing influence of the primary users.
-Second, the centralized clustering scheme forms the clusters which satisfy the requirement on cluster size, and the resulted clusters are robust against PUs' increasing activity, besides, it involves the smallest control overhead in the process of clustering.
-Third, as distributed schemes, the variants of ROSS outperform SOC considerably in the following four aspects.
-\begin{itemize}[noitemsep,topsep=0pt]
-\item The variants of ROSS generate less unclustered nodes than SOC for a given CRN, and the resulted clusters are more robust than SOC when PUs become more active.
-\item The amount of signaling overhead involved in ROSS is about half of that needed for SOC, and the signaling messages are much shorter that the latter.
-\item Compared with SOC, the clusters generated by ROSS don't appear with a wide span of sizes.
+%\subsection{Discussion}
+%Evaluating the small and the large scenarios lead to consistent insights.
+%Firstly, our observations strengthen the claim that the average number of CCs per cluster is not necessarily a good metric to represent the robustness of a cluster.
+%While ROSS and SOC have somewhat comparable results regarding the average size of the formed clusters, their robustness in case of additional primary user activity is strongly different.
+%In contrast, for the centralized clustering scheme the claim is true that the number of CCs per cluster is a good measure for robustness.
+%Furthermore, regarding the distributed schemes, the variants of ROSS outperform SOC considerably in the following four aspects.
+%\begin{itemize}[noitemsep,topsep=0pt]
+%\item The variants of ROSS result in less unclustered nodes than SOC for a given CRN, and the resulting clusters are more robust than the clusters formed by SOC.
+%\item The amount of signaling overhead involved in ROSS is about half of that needed for SOC, and the signaling messages are much shorter that the latter.
+%\item Compared with SOC, the clusters generated by ROSS don't appear with a wide span of sizes.
 ROSS with size control mechanism result in the clusters whose sizes are in proximity to the desired size.
-\item The variants of ROSS are more resilient against the erroneous spectrum sensing.
-\end{itemize}
-
-Moreover, the ROSS variants with size control features achieve similar performance to the centralized scheme in terms of cluster size, and the cluster robustness is similar when applying the variants of ROSS and the centralized scheme respectively.
-%
-Among the variants of ROSS, the greedy mechanism in ROSS-DGA helps to improve the performance on cluster size and cluster robustness at the cost of increased signaling overhead.
-%We also notice that as a metric, the number of CCs per non-singleton cluster doesn't indicate the robustness of clusters as shown in Figure~\ref{singleton_clusters} and \ref{unclustered_100_200_300}, although it is adopted as the metric in the formation of clusters.
+%\item The variants of ROSS are more resilient against the erroneous spectrum sensing.
+%\end{itemize}
+%
+%Moreover, the ROSS variants with size control features achieve similar performance to the centralized scheme in terms of cluster size, and the cluster robustness is similar when applying the variants of ROSS and the centralized scheme respectively.
+%%
+%Among the variants of ROSS, the greedy mechanism in ROSS-DGA helps to improve the performance on cluster size and cluster robustness at the cost of increased signaling overhead.
+%%We also notice that as a metric, the number of CCs per non-singleton cluster doesn't indicate the robustness of clusters as shown in Figure~\ref{singleton_clusters} and \ref{unclustered_100_200_300}, although it is adopted as the metric in the formation of clusters.
 
@@
 \label{proof_clustering:lemma1}
-We consider a CRN which can be represented as a connected graph.
+We consider a CRN which is represented by a connected graph.
 % (COMMENT: Why is it necessarily connected?
@@
 My point it, when theorem works in one component, it works in the complete graph.)
-To simplify the discussion, we assume the secondary users have unique individual connectivity degrees. 
+To simplify the discussion, we assume that secondary users have unique individual connectivity degrees. 
 Each user has an identical ID and a neighborhood connectivity degree.
-This assumption is fair as the neighborhood connectivity degrees and node ID are used to break ties in Algorithm~\ref{alg0}, when the individual connectivity degrees are unique, it is not necessary to use the former two metrics.
+This assumption is justified as the neighborhood connectivity degrees and node IDs are used to break ties in Algorithm~\ref{alg0}, when the individual connectivity degrees are unique, it is not necessary to use the former two metrics.
 %(COMMENT: What do you mean by breaking ties??
@@
 Then there exists a node $\beta\in \text{Nb}(\alpha)$ such that $d_{\alpha} > d_{\beta}$ (otherwise $\alpha$ becomes cluster head). 
-In this case, according to Algorithm~\ref{alg0}, $\beta$ is not included in any clusters, because otherwise $d_{\beta} = M$, a large positive integer, which contradicts to $d_{\alpha} > d_{\beta}$.
+In this case, according to Algorithm~\ref{alg0}, $\beta$ is not included into any cluster, because otherwise $d_{\beta} = M$, a large positive integer, which contradicts to $d_{\alpha} > d_{\beta}$.
 Now, we distinguish between two cases: 
@@
 So far, when there is no cluster head identified, the unclustered nodes, \ie $\alpha$, $\beta$ form a linked list, where their connectivity degrees monotonically decrease.
-But this list will not continue growing, because the minimum individual connectivity degree is zero, and the length of this list is upper bounded by the total number of nodes in the CRN.
+But this list will not continue growing, because the minimum individual connectivity degree is zero, and the length of this list is upper-bounded by the total number of nodes in the CRN.
 An example of the formed node series is shown as Figure~\ref{lemma1}.
@@
 
-%we know that within at most $N$ steps, all the nodes belong to certain clusters. (COMMENT: No, we don't! Where was that shown?)
+%we know that within at most $N$ steps, all the nodes belong to certain clusters. (XXXXXXX COMMENT: No, we don't! Where was that shown?)
 \end{proof}

### 2017-12-02 journal-draft/ettdoc_JG_section6.tex
update ettdoc_JG.tex with the changes from James.

--- 2017-12-02 journal-draft/ettdoc_JG.tex
@@
 \label{def_centralized_clustering}
-For a set of CR nodes $\mathcal{N}$, the \textbf{CRN robust clustering problem} is to determine a set of clusters $\mathcal{T}$, where
+For a set of CR nodes $\mathcal{N}$, the \texbf{CRN robust clustering problem} is to determine a set of clusters $\mathcal{T}$, where 
 \begin{enumerate}
@@
 singleton clusters may be formed but do mot contribute to the objective function.
-In particular, the range can be expressed as $[\delta-u, \delta+u]$, where $\delta$ is the desired cluster size, $u$ is a constant and $\delta-u > 0$.
 
@@
 \end{mydef}
-% XXX Di: What does the last statement mean with respect to the size of C being allowed to be 1.
-Does that mean for all C in T, the size is allowed to be 1?
-Doesn't that contradict what you have been saying in the definition before, where you come up with the range ?
-% XXXX 
-%1. we have a function f(C) to denote the number of CCs, if cluster size is in the scope, fine; if not, f(C) equals zero.
-%2. it is OK for every CR node to form their own cluster. Then according to rule 3, f(C) is zero and we obtain a 'bad' clustering result.
-% XXXX
 
@@
 \begin{aligned}
-     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p(C_i)) \\
-     &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, \text{for}\,\,\forall j=1, \ldots, N \\
-   &&& \Sigma_{j=1}^N x_{ij} = |C_i|\cdot y_i,\, \text{for}\,\,\forall i=1, \ldots, M \\
+     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot t_{ij}) \\
+     &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, for\,\,\forall j=1, \ldots, N \\
+   &&& \Sigma_{j=1}^N x_{ij} = |C_i|\cdot y_i,\, for\,\,\forall i=1, \ldots, M \\
   % &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
@@
 \end{equation}
-$N$ is the total number of CR users in network $\mathcal{N}$.
 $y_i$ and $x_{ij}$ are two binary variables.
+% where $j\in \{1,2,\cdots,N-1, N\}$ and $i\in \{1,2,\cdots,M-1, M\}$.
+%$G = |\mathcal{G}|$ and there is $\mathcal{G} \subseteq \mathcal{S}$.
 Being either 1 or 0, $y_i$ denotes whether the $i$-th cluster $C_i$ in $\mathcal{S}$ is chosen or not.
 $x_{ij}$ indicates whether the CR node $j$ resides in the cluster $C_i$, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$. 
+%Node index $j$ is identical to the node ID.
+$N$ is the total number of CR users in network $\mathcal{N}$, $M$ is the number of clusters in $\mathcal{S}$.
 
@@
 %The optimization is a binary linear programming problem.
-As to the objective function, the sum of the first items is the sum of CCs of the clusters which constitute the CRN.
-In the second item, we propose $p(C_i)$ which is a size-related weight for cluster $C_i, i\in{1,\cdots, M}$.
-$p(C_i)$ is positively related with the difference between $C_i$'s size and the desired size $\delta$.
-The desired size $\delta$ is pre-decided based on the capability of the CR users and the tasks to be conveyed.
-When $y_i$ is 1 ($C_i$ is chosen) but $|C_i|$ doesn't equal to the desired cluster size $\delta$, it will be negative, which contradicts the direction of the optimization.
-Thus the second item discourages the appearance the clusters whose sizes deviate from $\delta$.
-The weight $p(C_i)$ with respect to different cluster sizes is as follows,
-%$$
-%p(C_i) = \left\{ \begin{array}{rl}
-%0 &\mbox{ if $|C_i|=\delta$} \\
-%\rho_1 &\mbox{if $||C_i|-1|=\delta$} \\
-%\rho_2 &\mbox{if $||C_i|-2|=\delta$} \\
-%\vdots\\
-%\rho_\sigma &\mbox{if $||C_i|-\sigma|=\delta$} \\
-%\end{array} \right.
-%$$
-
+The objective is to maximize the sum of the numbers of CCs in the clusters which constitute the CRN.
+$t_{ij}$ is a constant and there is
+%In practice, we can solve the problem with $\mathcal{G} = \mathcal{S}$ when $|\mathcal{S}|$ is not large. 
+%
+%
+%Given a CRN $\mathcal{N}$ and desired cluster size $\delta$, we obtain a collection of clusters $\mathcal{G}$ which contains all the \textit{potential} clusters, and the sizes of these clusters are $1,2,\ldots,\delta$.
+%Potential clusters are the clusters which satisfy the conditions introduced in Section~\ref{sec:model}. 
+%Note that the potential clusters include the singleton ones.
+%By permitting the existence of the singleton clusters, we can ensure that the $\mathcal{S}'$ in Definition~\ref{def_centralized_clustering} is always be feasible.
+
+\begin{equation}
+t_{ij} = \frac{q_{ij}}{|C_i|} - p_i(C_i)
+\end{equation}
+where constant $q_{ij}= |K(C_i)|$ when node $j\in C_i$, and $q_{ij}= 0$ when node $j\notin C_i$.
+%$|K(C_i)|$ is the number of CCs of cluster $C_i$, and $|C_i|$ is the size of cluster $C_i$.
+$p(C_i)$ is the size-related weight, which is positively related with the difference between $C_i$'s size and the desired size $\delta$.
+The desired size $\delta$ is decided based on the capability of the CR users and the tasks to be conveyed.
+The weight $p$ is decided with respect to cluster sizes 1,2, $\cdots$, $\sigma$ as follows,
 $$
@@
 0 &\mbox{ if $|C_i|=\delta$} \\
-\rho_1 &\mbox{if $|C_i|=\delta \pm 1$ } \\
-\rho_2 &\mbox{if $|C_i|=\delta \pm 2$} \\
+\rho_1 &\mbox{if $||C_i|-1|=\delta$} \\
+\rho_2 &\mbox{if $||C_i|-2|=\delta$} \\
 \vdots\\
-\rho_\sigma &\mbox{if $|C_i|=\delta \pm \sigma$} \\
+\rho_\sigma &\mbox{if $||C_i|-\sigma|=\delta$} \\
 \end{array} \right.
@@
 where $ 0 < \rho_1< \rho_2 < \cdots < \rho_\sigma$.
-Please note that here we adopt the desired cluster size in stead of the range for cluster sizes which is described in Definition~\ref{problem}.
-Because in implementation, we usually need a large range to guarantee a feasible result for the optimization problem.
-By adopting the desired size and the punishment for deviating from it, we actually set a large range of cluster sizes and meanwhile a better control of the resulted sizes.
+
+%%Based on the knowledge on $\mathcal{S}$, we construct a $M\times N$ matrix $Q_{M\text{x}N}$ which is shown in Figure~\ref{costant_matrix_Q}. 
+%%Constant $q_{ij}$ is the element of $Q_{M\text{x}N}$, and its subscripts correspond to the $i$th cluster and CR node $j$ respectively.
+%$q_{ij}= |K(C_i)|/|C_i|$ when there is $j\in C_i$, and $q_{ij}= 0$ when there is $j\notin C_i$.
+%In other words, each non-zero element $q_{ij}$ means the number of CCs of the cluster $i$ where node $j$ resides.
+
+%\begin{figure}[ht!]
+%\centering
+%\bordermatrix{~ 		& 1 	& 2 	& 3 	& \cdots & j & \cdots	& N-1 	& N	\cr
+%                  1 	& |K(C_1)| 	& |K(C_1)| 	& 0 	& \cdots & \cdots &\cdots	& 0 	& 0	\cr
+%                  2 	& |K(C_2)| 	& 0 	& |K(C_2)| 	& \cdots & \cdots & \cdots 	& 0 	& 0	\cr
+%				\vdots  	&\vdots & 	 	& 		&  \vdots		& 		& \vdots \cr
+%				i 	& 0 	& |K(C_i)| 	& 0 	& \cdots  & \cdots & \cdots 	& |K(C_i)| 	& 0	\cr
+%				\vdots  	&\vdots & 	 	& 		&  \vdots & \cdots & \vdots 		& 		& \vdots \cr
+%				\vdots 	& 0  	& 0 	& 0 	& \cdots & \cdots & \cdots 	& |K(C_i')| 	& 0	\cr
+%				G  	& |K(C_G)| & \cdots	 	& 		&  \vdots	& \cdots & \vdots& 		& \vdots \cr}	
+%\caption{An example of Matrix $Q$, its rows correspond to all possible clusters, and columns correspond to the CR nodes in the CRN. }
+%\label{costant_matrix_Q}
+%\end{figure}
+
+%Now we examine the objective function to see whether it in line with the goal to maximize the total number of CCs meanwhile consider the restriction on the cluster size.
+When $t_{ij}$ is replaced by $\frac{q_{ij}}{|C_i|} - p(C_i)$, the objective function becomes,
+\begin{equation}
+\begin{aligned}
+     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p(C_i)) \\
+\notag
+\end{aligned}
+\label{centralized_opt}
+\end{equation}
+The sum of the first items is the sum of CCs of all the chosen clusters.
+As to the second item, when $w_i$ is 1 ($C_i$ is chosen) and $|C_i|\neq\delta$, it will be negative, which contradicts the direction of the optimization.
+Thus the second item discourages the appearance the clusters whose sizes deviate from $\delta$.
 
@@
 This clarified and conducted through a series of interactions on the control channel.
-All variants of ROSS consist of two cascaded phases: \textit{Cluster formation} and \textit{Membership clarification}, as shown in Figure~\ref{flowChartROSS}.
+All variants of ROSS consist of two cascaded phases: \textit{Cluster formation} and \textit{membership clarification}, as shown in Figure~\ref{flowChartROSS}.
 \begin{figure}[ht!]
@@
 \begin{itemize}
-
 \item \textit{Individual connectivity degree} $d_i$: $d_i=\sum_{j\in \text{Nb}(i)}\vert K_i\cap K_j\vert$. 
@@
 To control the cluster size, cluster heads remove their cluster members when cluster sizes are larger than a threshold.
-The threshold should be larger than the desired size $\delta$, because there are overlaps between neighboring clusters.
+The threshold should be larger than the desired size $\delta_1$, because there are overlaps between neighboring clusters.
 %Hence, a cluster head excludes some cluster members when the cluster size exceeds a certain threshold.
@@
 After deciding its membership, debatable node $i$ notifies all its claiming clusters.
-%xxxxxxxxxxxxxxxxxxx
 
@@
 The relation between the debatable nodes and the claiming clusters is shown in Figure~\ref{debatable_nodes_claiming_cluster}.
-
 \begin{figure}[ht!]
@@
 \end{figure}
-
 In the following, we show that the decision of debatable nodes to clarify their membership can be mapped to the behaviour of the players in a \textit{player-specific singleton congestion game} when proper cost function is given.
@@
 If we do so, the ROSS-based schemes maintain 5\%, 30\% and 230\% more secondary users within clusters than SOC, when the numbers of newly added PR are 10, 40 and 80 respectively (no figure is provided for this data).
-%XXXXX
 The above observation illustrates clearly that the average number of CCs of non-singleton clusters doesn't necessarily reflect the robustness of clusters, \ie SOC obtains the most CCs among the distributed schemes, but the resulting clusters are vulnerable to primary user activity.
@@
 %According to~\cite{complexity_aggregation_2011}, the message complexity is defined as the number of messages used by all nodes.
-
 As to ROSS, in the first phase the maximal number of broadcast is $N$ according to~\ref{clustering:theorem}.
@@
   \caption{Absolute amount of control messages required for clustering.}
-%XXXXXX Quantitative, or Absolute
   \label{control_msg}
@@
 %When run ROSS, the parameter $t$ which is used to control cluster size in phase I is 1.3.
-
 \begin{table}[ht]
@@
 \end{table}
-
-\subsubsection{Number of CCs per Non-singleton Clusters}
 
@@
 An example of the formed node series is shown as Figure~\ref{lemma1}.
-
 \begin{figure}[ht!]
@@
 \end{figure}
-
 In this example, node $\omega$ is at the tail of a list.
@@
 In this way, cluster heads are generated from the tail to the head in the list, and every node in the list is in at least one cluster, which contradicts the assumption that $\alpha$ is not included in any cluster.
-
-%If we see a secondary user \textit{becoming a cluster head}, or \textit{becoming a cluster member} as one step, as the length of the list of secondary users is not larger than $N$, there are $N$ steps for this scenario to form the initial clusters.
-
-%we know that within at most $N$ steps, all the nodes belong to certain clusters. (XXXXXXX COMMENT: No, we don't! Where was that shown?)
 \end{proof}

### 2017-12-03 journal-draft/ettdoc_JG.tex
changes from James on Sction 5 and 6

@@
 %$\text{CH}$ & cluster head\\
-$\delta$ & the cluster size which is preferred\\
+$\delta$ & the desired cluster size\\
 $S_i$ & a set of claiming clusters, each of which includes \\
@@
 \item the sum over $f(C)$ for all clusters $C$ is maximized, where the number of common channels for cluster $C$ is denoted as $f(C)$;
-
-\item all cluster sizes are within the range $\big[\delta_1, \delta_2\big]$, with $\delta_1, \delta_2\in \mathbb{Z}^+$ and $\delta_1 \leq \delta_2$;
+\item all cluster sizes are within the range $\big[\delta_1, \delta_2\big]$, with $\delta_1, \delta_2\in \mathbb{Z}^+$ and $\delta_1 \leq \delta_2$.
+The range can also be expressed as $[\delta-u, \delta+u]$, where $\delta$ is the desired cluster size, $u$ is a constant and $\delta-u > 0$.
 \item When the cluster size is larger or smaller than the range $\big[\delta_1, \delta_2\big]$, $f(C)$ is defined as 0, i.e.
 singleton clusters may be formed but do mot contribute to the objective function.
-In particular, the range can be expressed as $[\delta-u, \delta+u]$, where $\delta$ is the desired cluster size, $u$ is a constant and $\delta-u > 0$.
 
@@
 The desired size $\delta$ is pre-decided based on the capability of the CR users and the tasks to be conveyed.
-When $y_i$ is 1 ($C_i$ is chosen) but $|C_i|$ doesn't equal to the desired cluster size $\delta$, it will be negative, which contradicts the direction of the optimization.
-Thus the second item discourages the appearance the clusters whose sizes deviate from $\delta$.
+When $y_i$ is 1 ($C_i$ is chosen) but $|C_i|$ doesn't equal to the desired cluster size $\delta$, the second item is negative, which contradicts the direction of the optimization.
+Thus the second item discourages the appearance the clusters whose sizes deviate from the desired cluster size $\delta$.
 The weight $p(C_i)$ with respect to different cluster sizes is as follows,
@@
 The connectivity vector is determined by every secondary user and is then broadcasted.
-Figure~\ref{fig1} illustrates the computation of the connectivity vectors for a CRN, where dashed edges indicate that the nodes are within each other's transmission range, while the number along the dashed line is the number of common channels between the two ends.
-In this example, the set of available channels per terminals are given by: $K_A=\{1,2,3,4,5,6,10\}, K_B=\{1,2,3,5,7\}, \\K_C=\{1,3,4,10\}, K_D=\{1,2,3,5\}, \\K_E=\{2,3,5,7\}, K_F=\{2,4,5,6,7\}, \\K_G=\{1,2,3,4,8\}, K_H=\{1,2,5,8\}$.
-The figure shows in particular the resulting connectivity vector per node.
+Figure~\ref{fig1} illustrates the computation of the connectivity vectors for a CRN, where a dashed edge indicates one end node is within the other's transmission range, while the number along the dashed line is the number of common channels between the two end nodes.
+In this example, the sets of available channels on the nodes are: $K_A=\{1,2,3,4,5,6,10\}, K_B=\{1,2,3,5,7\}, \\K_C=\{1,3,4,10\}, K_D=\{1,2,3,5\}, \\K_E=\{2,3,5,7\}, K_F=\{2,4,5,6,7\}, \\K_G=\{1,2,3,4,8\}, K_H=\{1,2,5,8\}$.
+Figure~\ref{fig1} shows in particular the resulting connectivity vector per node.
 \begin{figure}[ht!]
@@
 %Hence, a cluster head excludes some cluster members when the cluster size exceeds a certain threshold.
-We set the threshold as $t\cdot \delta$, where the constant parameter $t$ is dependent on the network density and CR nodes' transmission range.
-We adopt $t$ to be between 1 and the ratio of the average neighborhood size and desired size.
-When $t$ is smaller, \eg $t=1$, the formed cluster in phase I will be $\delta$.
-For the cluster whose members are included by other clusters, the size of this cluster will be smaller than $\delta$ after the following membership clarification phase.
-If $t$ is chosen large, \eg $t\cdot\delta$ equals the size of the neighborhood, the mechanism of adjusting the cluster size will not work any more.
+We set the threshold as $t\cdot \delta$, where the constant parameter $t$ is dependent on network density and CR nodes' transmission range.
+We adopt $t$ to be between 1 and the ratio of the average neighborhood size and the desired size.
+When $t$ is smaller, \eg $t=1$, the formed cluster in phase I is $\delta$.
+For a cluster which has members included by other clusters, the size of that cluster will be smaller than $\delta$ after the membership clarification phase.
+If $t$ is chosen large, \eg $t\cdot\delta$ equals the size of the neighborhood, cluster size control will not work any more.
 
@@
 
-We finally turn to a comparison of the involved signaling overhead for the different clustering schemes.
+We finally turn to a comparison of the amount of the involved control messages for the different clustering schemes.
 For this, we count the number of \textit{transmissions of control messages} as metric~\cite{complexity_aggregation_2011}, without distinguishing broadcast or uni-cast control messages.
@@
 As to ROSS, in the first phase the maximal number of broadcast is $N$ according to~\ref{clustering:theorem}.
-The upper limits for the message exchanges are $n^2m$ and $n$ for ROSS-DGA and ROSS-DFA, respectively.
+In the second phase, the upper bound for the number of message exchanges is $n^2m$ and $n$ for ROSS-DGA and ROSS-DFA respectively, where $n$ is the number of debatable nodes and $m$ is the number of claiming clusters.
 SOC consists of three rounds, and in each round every node needs to perform a broadcast to do comparisons and cluster merging.
@@
 %
-%As we adopt a simplified communication model, node's transmission is not influenced by collision or interference, 
-%Our simulation doesn't consider the behaviour in the physical layer, 
-%
-%
-%Assume we use OSPF~\cite{BCJ10} to aggregate and disseminate information, then the best and worst complexity for is $\mathcal{O}(E)$, where $E$ is the number of edges in the graph which corresponds to the network.
-%The minimum number of edges is $n-1$ when the nodes form a line and each node has at more two neighbours, and the maximum number is $N*(N-1)/2$ when the nodes form a complete graph.
-%Thus the best message complexity of the centralized scheme is $\mathcal{O}{(N)}$ and the worst is $\mathcal{O}{(N^2)}$.
-%
-%1. update membership to form X1, 
-%2. broadcast new X1, form new X2
-%3. broadcast X3
-%The complexity parameters are the number of nodes $n$ in network, number of clusters $h$.
-Table \ref{tab_overhead} shows the messaging overhead , quantitative amount of control messages, and size of control messages for the different schemes under consideration.
-Figure~\ref{control_msg} shows the analytical result of the amount of transmissions involved in different schemes.
-%the upper bound of the number of transmissions of ROSS, and the analytic number of transmissions of the centralized scheme.
+Table \ref{tab_overhead} shows the amount of control messages using big O notation , the number (or upper bound) of control messages (illustrated in Figure~\ref{control_msg}), and the size of control messages for the different schemes under consideration.
+From Figure~\ref{control_msg} we can see the upper bound on the number of control messages, which are involved in the variants of ROSS, is still smaller than that involved in SOC.
+Meanwhile, the length of the control messages involved in the variants of ROSS is shorter than that involved in the centralized scheme.
 
@@
 \begin{table*}[!htb]
-\caption{Signalling overhead}\label{tab_overhead}
+\caption{Quantity of control messages}\label{tab_overhead}
 {\renewcommand{\arraystretch}{1.15} %<- modify value to suit your needs
@@
 \hline
- Scheme 				&Message Overhead 	&   Quantitative number of messages 		& Content and size of the message 									\\ \hline
- ROSS-DGA, ROSS-$\delta$-DGA 	&$\mathcal{O}(N^3)$ (worst case)		&   $N+n^2m$ (upper bound)  				&   \multirow{2}{*}{\parbox{7.7cm}{PhaseI: ID, $d_i$,$g_i$, which are 3 bytes;\\ PhaseII: Cluster head $i$ broadcasts channel availability to all \\ members, where are $|C(i)| |\mathcal{K}|$ bytes}}								\\ \cline{1-3}
- ROSS-DFA, ROSS-$\delta$-DFA 	&$\mathcal{O}(N)$ (worst case)		&   $N + n$	 (upper bound) 					& 	      												\\ \hline
+ Scheme 				&Message Overhead 	&   Number of messages 		& Content and size of the message 									\\ \hline
+ ROSS-DGA, ROSS-$\delta$-DGA 	&$\mathcal{O}(N^3)$ (\tnotex{tnote:robots-r0} 	)		&   $N+n^2m$ (upper bound)  				&   \multirow{2}{*}{\parbox{7.7cm}{PhaseI: ID, $d_i$,$g_i$, which are 3 bytes;\\ PhaseII: Cluster head $i$ broadcasts channel availability to all \\ members, where are $|C(i)| |\mathcal{K}|$ bytes}}								\\ \cline{1-3}
+ ROSS-DFA, ROSS-$\delta$-DFA 	&$\mathcal{O}(N)$ (\tnotex{tnote:robots-r3} 	)		&   $N + n$	 (upper bound) 					& 	      												\\ \hline
  SOC 					&$\mathcal{O}(N)$		&   $3N$									& Every CR node $i$ broadcasts channel availability on all cluster members, which is $|C(i)| |\mathcal{K}|$ bytes
@@
     \begin{tablenotes}
+    \item \label{tnote:robots-r0}For the upper bound on the number of messages. 
+    \item \label{tnote:robots-r3}For the upper bound on the number of messages.
       \item\label{tnote:robots-r1}Assuming the data structure of the clustering result is in the form of $\{i, C\}, i\in C, i\in \mathcal{N}$.
@@
   \centering
-  \includegraphics[width=0.6\linewidth]{number_controlMsg.pdf}
-  \caption{Absolute amount of control messages required for clustering.}
-%XXXXXX Quantitative, or Absolute
+  \includegraphics[width=0.7\linewidth]{number_controlMsg_debug.pdf}
+  \caption{The number of control messages required for clustering, which is based on the second column of Table~\ref{tab_overhead} }
   \label{control_msg}
@@
 We now switch to a more fine-grained investigation only of the distributed schemes. 
-We are here most important interested in their properties when the network size and density scales.
-In our scenario, we set now the transmission range of CR to $A/5$ while the primary user transmission range is set to $2A/5$.
+We are here most interested in their properties when the network size and density scales.
+%The number of CR is 100, 200 and 300, and the average number of neighbours of each CR is 9.5, 20, and 31.
+In particular, we set the desired size based on the density of the network.
+As shown in the Table~\ref{Simulation_para}, the desired size equals to 60\% of the average number of neighbors.
+The transmission range of CR to $A/5$ while the primary user transmission range is set to $2A/5$.
 The initial number of primary users is set to 30.
-%The number of CR is 100, 200 and 300, and the average number of neighbours of each CR is 9.5, 20, and 31.
-As we scale now the number CR nodes in the scenario, we adjust the desired size in the clustering process.
-Our adopted values are listed in the Table~\ref{Simulation_para}, which represent about 60\% of the average number of neighbors.
-%When run ROSS, the parameter $t$ which is used to control cluster size in phase I is 1.3.
-
 \begin{table}[ht]
@@
 \end{figure}
-We start again with considering the average number of CCS over all non-singleton clusters, shown in Figure~\ref{ccc_large_scale}.
+We start again with considering the average number of CCs over all non-singleton clusters, shown in Figure~\ref{ccc_large_scale}.
 Note that in this case we increase the number of CR nodes in the scenario.
@@
 
-The ECDF results show that the cluster sizes resulting from the variants of ROSS are clearly governed by the the desired size, \ie as shown in Figures~\ref{cdf_clusterSize_100}, 90\% of CR nodes are in clusters whose sizes are between 3 and 9, while for SOC, only 17\% of nodes are in the clusters with these sizes.
+The ECDF results show that the cluster sizes resulting from the variants of ROSS are clearly governed by the the desired size, \ie as shown in Figures~\ref{cdf_clusterSize_100}, where the number of CR nodes is 100 and the desired cluster size is 6, 90\% of CR nodes are in clusters whose sizes are between 3 and 9, while for SOC, only 17\% of nodes are in the clusters with these sizes.
 Similarly, when $N=200$ and the desired size is 12 (as shown in Figure~\ref{cdf_clusterSize_200}), 80\% of nodes are in clusters whose sizes are between 6 and 18, while only 30\% of nodes are in clusters of similar sizes when SOC is executed.
@@
 \label{conclusion}
-In this paper we investigate robust clustering problem in CRN thoroughly and propose both centralized and distributed clustering solutions.
-We give mathematical description of the problem and prove NP hardness of it.
-The proposed centralized scheme generate clusters which have long life expectancy against primary users, and the cluster sizes are close to the desired cluster size.
+In this paper we investigate the robust clustering problem in CRN, give mathematical description of the problem and prove NP hardness of it.
+Both centralized and distributed clustering solutions are proposed.
+With the increasing tensity of the primary users' activity, our proposed schemes generates clusters which make more secondary users to be in the clusters composed with multiple users, so that more secondary users can benefit from cooperative spectrum sensing.
+Besides, the resulted cluster sizes lie in a smaller range centered around the desired cluster size and involve less control messages than the comparison scheme.
+In particular, the proposed centralized scheme outperforms the proposed distributed schemes in all aspects, although it requires a centralized device and the involved control message packet is large.
+Our proposed distributed scheme is also more robust against the erroneous spectrum sensing compared with the comparison scheme.
+The simulation confirms that the metric of average number of CCs of clusters alone is not an accurate indicator for the cluster robustness against the primary users' activity.
 %The distributed scheme not only results in more robust clusters, but the cluster sizes are in a smaller range than the comparison scheme.
@@
 %A Light weighted clustering scheme ROSS is also proposed.
-Through simulation, the distributed schemes demonstrate similar performance with the centralized scheme in terms of cluster robustness, signaling overhead and cluster sizes.
-The distributed scheme outperforms the comparison distributed scheme by generating more robust clusters,  generating clusters whose sizes are in a smaller range, and being more resilient against the erroneous spectrum sensing.
+%Through simulation, the distributed schemes demonstrate similar performance with the centralized scheme in terms of cluster robustness, amount of involved control messages and cluster sizes.
+%The distributed scheme outperforms the comparison distributed scheme by generating more robust clusters,  generating clusters whose sizes are in a smaller range, and being more resilient against the erroneous spectrum sensing.
 

### 2017-12-10 journal-draft/ettdoc.tex
revison based on james' comments on 5th Dec

@@
 
-The decision version of this problem is to determine whether there exists a set of clusters, say $\mathcal{X}$, so that $\cup C_{C\in\mathcal{X}} = \mathcal{N}$, and $\sum_{C\in \mathcal{X}} f(C) \geqslant \lambda$ where $\lambda$ is a real number.
+The decision version of this problem is to determine whether there exists a set of clusters, say $\mathcal{T}$, so that $\cup C_{C\in\mathcal{X}} = \mathcal{N}$, and $\sum_{C\in \mathcal{X}} f(C) \geqslant \lambda$ where $\lambda$ is a real number.
 We have the following theorem on the problem's complexity.

### 2017-12-10 journal-draft/ettdoc_JG.tex
revison based on james' comments on 5th Dec

@@
 %
-%
+
 The rest of the paper is organized as follows:
@@
 However, this can lead in an extreme situation to a large amount of singleton clusters, if the size of the clusters is not controlled simultaneously. 
-A large amount of singleton clusters, as discussed reduced spectrum sensing accuracy through cooperative sensing, as well as being not desirable from different other perspectives.
+As discussed, a large amount of singleton clusters reduces spectrum sensing accuracy through cooperative sensing, as well as being not desirable from different other perspectives (routing, coordination with respect to channel vacation).
 Thus, we essentially propose to include this trade-off in the optimization process of building clusters, captured in the following definition:
@@
 \label{def_centralized_clustering}
-For a set of CR nodes $\mathcal{N}$, the \textbf{CRN robust clustering problem} is to determine a set of clusters $\mathcal{T}$, where
+For a set of CR nodes $\mathcal{N}$, the \textbf{CRN robust clustering problem} is to determine a set of clusters $\mathcal{T}$, where:
 \begin{enumerate}
 \setlength{\itemindent}{.05in}
-\item the intersection of any two clusters in $\mathcal{T}$ results in the empty set;
-\item the union of all clusters in $\mathcal{T}$ results in$\mathcal{N}$;
-\item the sum over $f(C)$ for all clusters $C$ is maximized, where the number of common channels for cluster $C$ is denoted as $f(C)$;
-\item all cluster sizes are within the range $\big[\delta_1, \delta_2\big]$, with $\delta_1, \delta_2\in \mathbb{Z}^+$ and $\delta_1 \leq \delta_2$.
-The range can also be expressed as $[\delta-u, \delta+u]$, where $\delta$ is the desired cluster size, $u$ is a constant and $\delta-u > 0$.
+\item The intersection of any two clusters in $\mathcal{T}$ results in the empty set.
+\item The union of all clusters in $\mathcal{T}$ results in $\mathcal{N}$.
+\item For all clusters with size within the range $\big[\delta_1, \delta_2\big]$, with $\delta_1, \delta_2\in \mathbb{Z}^+$ and $\delta_1 \leq \delta_2$, the number of CCs per cluster is $f(C) = K(C)$, i.e.
+it is given as the number of jointly available CCs for all nodes of that cluster.
+The desired size $\delta$ is within $\big[\delta_1, \delta_2\big]$, which is pre-decided based on the capability of the CR users and the tasks to be conveyed.
+%In particular, the range can be expressed as $[\delta-u, \delta+u]$, where $\delta_1= \delta -u, \delta_2=\delta+u$, $\delta$ is referred to as \textbf{desired cluster size}, $u$ is a constant and $\delta-u > 0$.
 \item When the cluster size is larger or smaller than the range $\big[\delta_1, \delta_2\big]$, $f(C)$ is defined as 0, i.e.
-singleton clusters may be formed but do mot contribute to the objective function.
-
+singleton clusters may be formed but does not contribute to the objective function.
+\item The sum over $f(C)$ for all clusters $C \in \mathcal{T}$ is maximal.
 \end{enumerate}
 \end{mydef}
+Note that in the above definition, we distinguish between the real number of CCs per cluster, which is given as $K(C)$, and the contribution of each formed cluster towards the objective function, which is given by function $f(C)$.
+If the cluster size is within range, the two parameters are the same, but otherwise the distinction is enforce a cost for building clusters that are out of range.
 % XXX Di: What does the last statement mean with respect to the size of C being allowed to be 1.
@@
 
-The decision version of this problem is to determine whether there exists a set of clusters, say $\mathcal{X}$, so that $\cup_{C\in\mathcal{X}} C = \mathcal{N}$, and $\sum_{C\in \mathcal{X}} f(C) \geqslant \lambda$ where $\lambda$ is a positive integer number.
+The decision version of this problem is to determine whether there exists a set of clusters, say $\mathcal{T}$, so that $\cup_{C\in\mathcal{T}} C = \mathcal{N}$, and $\sum_{C\in \mathcal{T}} f(C) \geqslant \lambda$ where $\lambda$ is a positive integer number.
 We have the following theorem on the problem's complexity.
@@
 \label{centralized_solution}
-Given the fact that the complexity of the CRN clustering problem is determined, we consider in this section a centralized solution for the problem.
-The motivation is mainly to have later on a comparison scheme for distributed algorithms, that we present in the next section.
-Assuming some global knowledge of the CRN to be given at some point in the network, a centralized solution \ie the locations of primary users and their working channels, and the locations of secondary users and available channels on them, we can propose a centralized scheme.
-We obtain the set of $\mathcal{S}$ which contains all the clusters in $\mathcal{N}$, \ie $\mathcal{S}=\{C_1, C_2,\ldots,C_i, \ldots, C_{|\mathcal{S}|}\}$ \footnote{The subscript $i$ means the $i$-th cluster in $\mathcal{S}$.} and there is $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = \mathcal{N}$.
-The proposed centralized solution formulates the problem in Definition~\ref{def_centralized_clustering} as an optimization problem which is solved with standard software packages.
-The optimization decides on the clusters according to the following optimization formulation, which is a binary linear programming problem and can be solved by many available solvers.
-
+%XXXXXX
+%Di: The first paragraph has been revised based on the first batch of comments for the camera-ready version, but somehow get lost in the last version.
+I take some parts from your revision and keep some from my revision.
+We now turn to algorithms that can solve the CRN robust clustering problem, despite its complexity. 
+We initially consider a centralized solution for this problem.
+Assuming some global knowledge of the CRN to be given at some point in the network, \ie the locations of primary users and their working channels, and the locations of secondary users and available channels on them, we can propose a centralized scheme.
+We obtain the set of $\mathcal{S}$ which contains all the clusters which satisfy the definition of cluster in Section~\ref{sec:model}.
+$\mathcal{S}$ is basically a powerset of $\mathcal{N}$, which nevertheless is restricted by connectivity and spectrum availability in the network.
+There are $\mathcal{S}=\{C_1, C_2, \ldots, C_{|\mathcal{S}|}\}$ \footnote{The subscript $i$ means the $i$-th cluster in $\mathcal{S}$.} and $|\mathcal{S}| = M$.
+Then the problem as defined in Definition~\ref{def_centralized_clustering} can be formulated as a binary linear programming problem and can be solved by many available solvers:
 \begin{equation}
@@
 \end{equation}
-$N$ is the total number of CR users in network $\mathcal{N}$.
-$y_i$ and $x_{ij}$ are two binary variables.
+$y_i$ and $x_{ij}$ are the two sets of binary optimization variables.
 Being either 1 or 0, $y_i$ denotes whether the $i$-th cluster $C_i$ in $\mathcal{S}$ is chosen or not.
@@
 $p(C_i)$ is positively related with the difference between $C_i$'s size and the desired size $\delta$.
-The desired size $\delta$ is pre-decided based on the capability of the CR users and the tasks to be conveyed.
 When $y_i$ is 1 ($C_i$ is chosen) but $|C_i|$ doesn't equal to the desired cluster size $\delta$, the second item is negative, which contradicts the direction of the optimization.
@@
 where $ 0 < \rho_1< \rho_2 < \cdots < \rho_\sigma$.
-Please note that here we adopt the desired cluster size in stead of the range for cluster sizes which is described in Definition~\ref{problem}.
+Note that here we adopt the desired cluster size in stead of the range for cluster sizes which is described in Definition~\ref{problem}.
 Because in implementation, we usually need a large range to guarantee a feasible result for the optimization problem.
@@
 The difficulty of using this method lies in obtaining the set $\mathcal{S}$.
-In the worst case, \ie every CR node communicates directly with any other node and the CRN forms a full connected graph, the size of $\mathcal{S}$ is $\Sigma_{r=1}^{N}\ {N \choose r} = 2^N-1$.
+In the worst case, \ie if every CR node can communicate directly with any other node, then the CRN forms a full connected graph and therefore the size of the powerset $\mathcal{S}$ is $\Sigma_{r=1}^{N}\ {N \choose r} = 2^N-1$.
 
@@
 With the variants of ROSS, CR nodes form clusters based on their own available channels, as well as the available channels of the nodes in their neighborhood.
-This clarified and conducted through a series of interactions on the control channel.
+This is clarified and conducted through a series of interactions on the control channel.
 All variants of ROSS consist of two cascaded phases: \textit{Cluster formation} and \textit{Membership clarification}, as shown in Figure~\ref{flowChartROSS}.
@@
 \item \textit{Individual connectivity degree} $d_i$: $d_i=\sum_{j\in \text{Nb}(i)}\vert K_i\cap K_j\vert$. 
-$d_i$ is the total number of the CCs between node $i$ and each of its neighbors, it does not reflect the amount of jointly common channels among all neighbors of $i$.
-\item \textit{Neighborhood connectivity degree} $g_i$: In contrast, $g_i$ is the number of CCs which are available for $i$ and all of its neighbors, thus
+$d_i$ is the total number of \textit{pairwise} CCs between node $i$ and each of its neighbors.
+Be aware that it does not reflect the amount of \textit{jointly} common channels among all neighbors of $i$.
+\item \textit{Neighborhood connectivity degree} $g_i$: In contrast, $g_i$ is the number of CCs which are \textit{jointly} available for $i$ and all of its neighbors, thus
 $g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$. It therefore represents the ability of $i$ to form a robust cluster with its neighbors.
@@
 \footnote{The issues arising out of cluster heads in the neighborhood of a newly formed cluster head are addressed in Section~\ref{ross_p1_guarantee_ccc} and \ref{ross_p2_cluster_pruning}}
-During the whole phase I, whenever a CR node becomes cluster head, or the cluster composition changes, the cluster head broadcasts new/updated information about the cluster structure, in particular the new/ update sets of available channels regarding itself and all its cluster members.
-Pseudo code regarding this process, i.e. the cluster head decision and the initial cluster formation, is also provided as Algorithm~\ref{alg0} in the appendix.
+During the whole phase I, whenever a CR node becomes cluster head, or the cluster composition changes, the cluster head broadcasts new/updated information about the cluster structure, in particular the new/updated sets of available channels regarding itself and all its cluster members.
+Pseudo code regarding this process, i.e. the cluster head decision and the initial cluster formation, is provided as Algorithm~\ref{alg0} in the appendix.
 
@@
 After executing Algorithm~\ref{alg0}, several formed clusters may not possess any CCs.
-As decreasing the cluster size usually increases CCs within a cluster, the next step is to decrease the the cluster size accordingly.
-This is done by following sequence of removing nodes according to an ascending list of nodes regarding their number of common channels between them and the cluster head. 
+As decreasing the cluster size usually increases CCs within a cluster, the next step is to decrease the cluster size accordingly.
+This is done by the following sequence of removing nodes according to an ascending list of nodes regarding their number of common channels between them and the cluster head. 
 In other words, the cluster member which has the least common channels with the cluster head will be removed first.
@@
 Obviously this function is non-decreasing with respect to the number of nodes joining cluster $C$.
+\end{itemize}
 
@@
 %This is the global objective we want to minimize.
-\end{itemize}
 
@@
 Taking the final clustering result of ROSS into account for our toy example shown in Figure~\ref{final_clustering_ross}, we can compare the outcome with our centralized scheme proposed in Equation~\ref{centralized_opt} as well as the state-of-the-art algorithm SOC~\cite{LIU_TMC11_2}.
-Those corresponding results of the later two schemes are shown in Figure~\ref{fig:final_clustering}.
+Those corresponding results of the latter two schemes are shown in Figure~\ref{fig:final_clustering}.
 We observe for this example case that ROSS and the centralized scheme achieve cluster sizes that are more balanced, while SOC leads to a larger variance in terms of the cluster size.
@@
 In the following, we are interested in a more general performance comparison regarding clustering in CRNs.
-We therefore present in the following an extensive evaluation study.
+We therefore present an extensive evaluation study.
 We base our evaluations on simulations, and consider the following comparison schemes:
@@
 \item \textbf{Cluster sizes.}
-We investigate the distribution of the size the formed clusters.
-This metric reflects that above mentioned size constraints, i.e. clusters are supposed to be neither too big nor too small.
+We investigate the distribution of the sizes of the formed clusters.
+This metric reflects the above mentioned size constraints, i.e. clusters are supposed to be neither too big nor too small.
 \item \textbf{Control message overhead.}
@@
 Our performance evaluation is split into two parts:
-First we investigate the performance of the centralized scheme and the distributed schemes for a small network, as the run-time for the centralized solution quickly grows out of hand as a function of the network size .
+First we investigate the performance of the centralized scheme and the distributed schemes for a small network, as the run-time for the centralized solution quickly grows out of hand as a function of the network size.
 In the second part, we investigate the performance only of the distributed schemes for larger settings.
@@
 The simulation is written in C++, and the performance results are averaged over 50 randomly generated topologies.
-We provide confidence interval corresponding to a 95\% confidence level.
-
-\subsection{Centralized Schemes vs. Decentralized Schemes}
+We provide confidence intervals corresponding to a 95\% confidence level.
+
+\subsection{Centralized Scheme vs. Decentralized Schemes}
 We start with the comparison of the centralized scheme versus various distributed ones.
@@
 We set the desired cluster size $\delta$ as 3.
-As for the centralized scheme, we set the following parameters numerically: $\rho_1 =  0.4$, $\rho_2 =  0.6$.
+As for the centralized schemes, we set the following parameters numerically: $\rho_1 =  0.4$, $\rho_2 =  0.6$.
 
 We start with the consideration of the CCs in all non-singleton clusters.
-Figure~\ref{ccc_per_nonsingleton} shows that basically the centralized schemes outperforms all distributed schemes in terms of the average number of CCs per cluster.
+Figure~\ref{ccc_per_nonsingleton} shows that basically the centralized schemes outperform all distributed schemes in terms of the average number of CCs per cluster.
 SOC achieves the most CCs among the distributed schemes, because SOC groups the neighboring CRs which share the most abundant spectrum together, without considering the size of them.
@@
 Next, we consider the robustness of clusters if facing random primary user activity.
-We thus extend the simulation by adding more primary users sequentially into CRN, leading to a decreasing spectrum availability.
+We thus extend the simulation by adding more primary users sequentially into the area of the CRN, leading to a decreasing spectrum availability.
 While 10 primary users are in the network at start, some extra19 batches of primary users are added sequentially, each batch including 5 primary users that are placed randomly in the area.
@@
 Surprisingly, the centralized scheme with desired size of 3 doesn't outperform the variants of ROSS, because pursuing larger cluster sizes generally leads to clusters with a lower amount of CCs. 
-In contrary, the variants of ROSS generate some smaller clusters which are more likely to be maintain despite the increasing primary user activity.
+In contrary, the variants of ROSS generate some smaller clusters which are more likely to be maintained despite the increasing primary user activity.
 
@@
 If we do so, the ROSS-based schemes maintain 5\%, 30\% and 230\% more secondary users within clusters than SOC, when the numbers of newly added PR are 10, 40 and 80 respectively (no figure is provided for this data).
-%XXXXX
-The above observation illustrates clearly that the average number of CCs of non-singleton clusters doesn't necessarily reflect the robustness of clusters, \ie SOC obtains the most CCs among the distributed schemes, but the resulting clusters are vulnerable to primary user activity.
+This observation illustrates clearly that the average number of CCs of non-singleton clusters doesn't necessarily reflect the robustness of clusters, \ie SOC obtains the most CCs among the distributed schemes, but the resulting clusters are vulnerable to primary user activity.
 
@@
 
-As to ROSS, in the first phase the maximal number of broadcast is $N$ according to~\ref{clustering:theorem}.
+As to ROSS, in the first phase the maximal number of broadcasts is $N$ according to~\ref{clustering:theorem}.
 In the second phase, the upper bound for the number of message exchanges is $n^2m$ and $n$ for ROSS-DGA and ROSS-DFA respectively, where $n$ is the number of debatable nodes and $m$ is the number of claiming clusters.
@@
 %
-Table \ref{tab_overhead} shows the amount of control messages using big O notation , the number (or upper bound) of control messages (illustrated in Figure~\ref{control_msg}), and the size of control messages for the different schemes under consideration.
-From Figure~\ref{control_msg} we can see the upper bound on the number of control messages, which are involved in the variants of ROSS, is still smaller than that involved in SOC.
+Table \ref{tab_overhead} shows the amount of control messages using big O notation, the number (or upper bound) of control messages (illustrated in Figure~\ref{control_msg}), and the size of control messages for the different schemes under consideration.
+From Figure~\ref{control_msg} we can see that the upper bound on the number of control messages which are involved in the variants of ROSS is still smaller than the one involved in SOC.
 Meanwhile, the length of the control messages involved in the variants of ROSS is shorter than that involved in the centralized scheme.
@@
 In particular, we set the desired size based on the density of the network.
-As shown in the Table~\ref{Simulation_para}, the desired size equals to 60\% of the average number of neighbors.
-The transmission range of CR to $A/5$ while the primary user transmission range is set to $2A/5$.
+As shown in Table~\ref{Simulation_para}, the desired size equals to 60\% of the average number of neighbors.
+The transmission range of CR is now set to $A/5$ while the primary user transmission range is set to $2A/5$.
 The initial number of primary users is set to 30.
@@
 
-\subsubsection{Number of CCs per Non-singleton Clusters}
-
 \begin{figure}[ht!]
@@
 Note that in this case we increase the number of CR nodes in the scenario.
-The result does not reveal, as in the previous section, a significant performance advantage of either of the distributed schemes.
+As in the previous section, the result does not reveal a significant performance advantage of either of the distributed schemes.
 
@@
 We basically see that as the primary user activity increases, more unclustered CR nodes result from SOC than the variants of ROSS.
-This correlates a somewhat similar observation in the previous section.
-When $N=300$, as shown in Figure~\ref{singleton_clusters_300}, and the amount of newly added primary users is moderate, ROSS-DGA/DFA results in slightly more unclustered CR nodes than SOC, while SOC's performance deteriorates quickly when the number of primary users continue increasing.
+This corrobates a somewhat similar observation of the previous section.
+When $N=300$, as shown in Figure~\ref{singleton_clusters_300}, and the amount of newly added primary users is moderate, ROSS-DGA/DFA results in slightly more unclustered CR nodes than SOC, while SOC's performance deteriorates quickly when the number of primary users continues to increase.
 Also, Figures~\ref{singleton_clusters_100} to~\ref{singleton_clusters_300} reveal that ROSS with size control mechanism results in significantly less singleton clusters.
@@
 %When the network becomes denser, more clusters are generated by SOC compared with ROSS variants.
-We furthermore consider the empirical distribution function of the size of the formed clusters, for each considered network density, in Figures~\ref{cdf_clusterSize_100}~\ref{cdf_clusterSize_200}~\ref{cdf_clusterSize_300} respectively.
+We furthermore consider the empirical distribution function of the size of the formed clusters, for each considered network density, in Figures~\ref{cdf_clusterSize_100}, ~\ref{cdf_clusterSize_200} and~\ref{cdf_clusterSize_300} respectively.
 \begin{figure}[!h]
@@
 
-The ECDF results show that the cluster sizes resulting from the variants of ROSS are clearly governed by the the desired size, \ie as shown in Figures~\ref{cdf_clusterSize_100}, where the number of CR nodes is 100 and the desired cluster size is 6, 90\% of CR nodes are in clusters whose sizes are between 3 and 9, while for SOC, only 17\% of nodes are in the clusters with these sizes.
+The ECDF results show that the cluster sizes resulting from the variants of ROSS are clearly governed by the desired size, \ie as shown in Figures~\ref{cdf_clusterSize_100}, where the number of CR nodes is 100 and the desired cluster size is 6, 90\% of CR nodes are in clusters whose sizes are between 3 and 9, while for SOC, only 17\% of nodes are in the clusters with these sizes.
 Similarly, when $N=200$ and the desired size is 12 (as shown in Figure~\ref{cdf_clusterSize_200}), 80\% of nodes are in clusters whose sizes are between 6 and 18, while only 30\% of nodes are in clusters of similar sizes when SOC is executed.
@@
 We can conclude that due to the negotiation step within neighborhoods, ROSS variants successfully rule out the false negative channels resulting from erroneous spectrum sensing. 
-This is an interesting and remarkabl advantage of ROSS in comparison to SOC.
+This is an interesting and remarkable advantage of ROSS in comparison to SOC.
 \begin{figure}[!h]

### 2017-12-10 journal-draft/ettdoc_JG_0512.tex
revison based on james' comments on 5th Dec

--- 2017-12-10 journal-draft/ettdoc_JG.tex
@@
 it is given as the number of jointly available CCs for all nodes of that cluster.
-The desired size $\delta$ is within $\big[\delta_1, \delta_2\big]$, which is pre-decided based on the capability of the CR users and the tasks to be conveyed.
-%In particular, the range can be expressed as $[\delta-u, \delta+u]$, where $\delta_1= \delta -u, \delta_2=\delta+u$, $\delta$ is referred to as \textbf{desired cluster size}, $u$ is a constant and $\delta-u > 0$.
+The range can also be expressed as $[\delta-u, \delta+u]$, where $\delta$ is referred to as \textbf{desired cluster size}, $u$ is a constant and $\delta-u > 0$.
 \item When the cluster size is larger or smaller than the range $\big[\delta_1, \delta_2\big]$, $f(C)$ is defined as 0, i.e.
@@
 
-The decision version of this problem is to determine whether there exists a set of clusters, say $\mathcal{T}$, so that $\cup_{C\in\mathcal{T}} C = \mathcal{N}$, and $\sum_{C\in \mathcal{T}} f(C) \geqslant \lambda$ where $\lambda$ is a positive integer number.
+The decision version of this problem is to determine whether there exists a set of clusters, say $\mathcal{X}$, so that $\cup_{C\in\mathcal{X}} C = \mathcal{N}$, and $\sum_{C\in \mathcal{X}} f(C) \geqslant \lambda$ where $\lambda$ is a positive integer number.
 We have the following theorem on the problem's complexity.
@@
 \label{centralized_solution}
-%XXXXXX
-%Di: The first paragraph has been revised based on the first batch of comments for the camera-ready version, but somehow get lost in the last version.
-I take some parts from your revision and keep some from my revision.
 We now turn to algorithms that can solve the CRN robust clustering problem, despite its complexity. 
 We initially consider a centralized solution for this problem.
+The motivation is mainly to have later on a comparison scheme for distributed algorithms, that we present in the next section.
 Assuming some global knowledge of the CRN to be given at some point in the network, \ie the locations of primary users and their working channels, and the locations of secondary users and available channels on them, we can propose a centralized scheme.
-We obtain the set of $\mathcal{S}$ which contains all the clusters which satisfy the definition of cluster in Section~\ref{sec:model}.
-$\mathcal{S}$ is basically a powerset of $\mathcal{N}$, which nevertheless is restricted by connectivity and spectrum availability in the network.
-There are $\mathcal{S}=\{C_1, C_2, \ldots, C_{|\mathcal{S}|}\}$ \footnote{The subscript $i$ means the $i$-th cluster in $\mathcal{S}$.} and $|\mathcal{S}| = M$.
+Define the set $\mathcal{S}$ as the powerset of $\mathcal{S}$, i.e.
+it contains all possible clustering possibilities that can be formed of $\mathcal{N}$, with $\mathcal{S}=\{C_1, C_2,\ldots,C_i, \ldots, C_{|\mathcal{S}|}\}$ where subscript $i$ refers to the $i$-th cluster in the powers $\mathcal{S}$.
 Then the problem as defined in Definition~\ref{def_centralized_clustering} can be formulated as a binary linear programming problem and can be solved by many available solvers:
@@
 $p(C_i)$ is positively related with the difference between $C_i$'s size and the desired size $\delta$.
+The desired size $\delta$ is pre-decided based on the capability of the CR users and the tasks to be conveyed.
 When $y_i$ is 1 ($C_i$ is chosen) but $|C_i|$ doesn't equal to the desired cluster size $\delta$, the second item is negative, which contradicts the direction of the optimization.
@@
 By adopting the desired size and the punishment for deviating from it, we actually set a large range of cluster sizes and meanwhile a better control of the resulted sizes. 
+% XXX I have no clue what you trying to express with these three lines.
 
@@
 \label{ross}
-
 In this section we introduce our distributed clustering schemes.

### 2017-12-10 journal-draft/ettdoc_JG.tex
revison based on james' comments on 5th Dec

@@
 \label{centralized_solution}
-%XXXXXX
+%XXXXXX%
 %Di: The first paragraph has been revised based on the first batch of comments for the camera-ready version, but somehow get lost in the last version.
@@
 $x_{ij}$ indicates whether the CR node $j$ resides in the cluster $C_i$, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$.
+$q_{ij}$ is a constant and it equals $|K(C_i)|$ when node $j\in C_i$.
+$q_{ij}$ equals zero when node $j\notin C_i$.
 
@@
 %The optimization is a binary linear programming problem.
-As to the objective function, the sum of the first items is the sum of CCs of the clusters which constitute the CRN.
-In the second item, we propose $p(C_i)$ which is a size-related weight for cluster $C_i, i\in{1,\cdots, M}$.
+As to the objective function, the sum of the first term in the bracket over all clusters in $\mathcal{S}$ and all CR node in $\mathcal{N}$ is the sum of CCs of the clusters which constitute the CRN.
+In the second term in the bracket, we propose $p(C_i)$ which is a size-related weight for cluster $C_i, i\in{1,\cdots, M}$.
 $p(C_i)$ is positively related with the difference between $C_i$'s size and the desired size $\delta$.

### 2017-12-10 journal-draft/ettdoc_JG.tex
revise section 4

@@
 $\mathcal{S}$ is basically a powerset of $\mathcal{N}$, which nevertheless is restricted by connectivity and spectrum availability in the network.
-There are $\mathcal{S}=\{C_1, C_2, \ldots, C_{|\mathcal{S}|}\}$ \footnote{The subscript $i$ means the $i$-th cluster in $\mathcal{S}$.} and $|\mathcal{S}| = M$.
+With $|\mathcal{S}| = M$, there is $\mathcal{S}=\{C_1, C_2, \ldots, C_M\}$ \footnote{The subscript $i$ means the $i$-th cluster in $\mathcal{S}$.}.
 Then the problem as defined in Definition~\ref{def_centralized_clustering} can be formulated as a binary linear programming problem and can be solved by many available solvers:
 \begin{equation}
+%\begin{aligned}
+%     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p(C_i)) \\
+%     &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, \text{for}\,\,\forall j=1, \ldots, N \\
+%   &&& \Sigma_{j=1}^N x_{ij} = |C_i|\cdot y_i,\, \text{for}\,\,\forall i=1, \ldots, M \\
+%  % &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
+%   &&& i\in \{1,2, \cdots M\}, \hspace{0.3cm} j\in \{1,2,\cdots N\}
+%%\notag
+%\end{aligned}
 \begin{aligned}
-     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p(C_i)) \\
-     &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, \text{for}\,\,\forall j=1, \ldots, N \\
-   &&& \Sigma_{j=1}^N x_{ij} = |C_i|\cdot y_i,\, \text{for}\,\,\forall i=1, \ldots, M \\
-  % &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
-   &&& i\in \{1,2, \cdots M\}, \hspace{0.3cm} j\in \{1,2,\cdots N\}
+     &\max\limits_{x_i} && \Sigma_{i=1}^M (x_i\cdot |K(C_i)| - x_i\cdot p(C_i)) \\
+     &\text{subject to}   && \Sigma_{i=1}^M (x_i\cdot e_{ij}) = 1  \quad\text{for}\,\,\forall j\in\{1, \ldots, N\} \\
 %\notag
@@
 \end{equation}
-$y_i$ and $x_{ij}$ are the two sets of binary optimization variables.
-Being either 1 or 0, $y_i$ denotes whether the $i$-th cluster $C_i$ in $\mathcal{S}$ is chosen or not.
-$x_{ij}$ indicates whether the CR node $j$ resides in the cluster $C_i$, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$.
-$q_{ij}$ is a constant and it equals $|K(C_i)|$ when node $j\in C_i$.
-$q_{ij}$ equals zero when node $j\notin C_i$.
-
-The constraints guarantee to obtain the clusters which together include all the CR users and don't overlap.
-The first constraint regulates that a CR node should reside in exactly one cluster.
-The second constraint regulates that when the $i$-th cluster $C_i$ is chosen, there will be exactly $|C_i|$ CR nodes residing in $C_i$.
-
-%The optimization is a binary linear programming problem.
-As to the objective function, the sum of the first term in the bracket over all clusters in $\mathcal{S}$ and all CR node in $\mathcal{N}$ is the sum of CCs of the clusters which constitute the CRN.
+$x_i, i\in \{1,2, \cdots M\}$ is a set of binary optimization variables.
+Being either 1 or 0, $x_i$ denotes whether the $i$-th cluster $C_i$ in $\mathcal{S}$ is chosen or not.
+$e_{ij}, i\in \{1,2, \cdots M\}$ and $j=\{1, \ldots, N\}$ is a set of constants which indicate whether the CR node $j$ resides in the cluster $C_i$, \ie $e_{ij}=1$ means node $j$ resides in the cluster $C_i$, $e_{ij}=0$ indicates $j$ doesn't belong to that cluster .
+
+The constraint regulates that for any node $j$, the sum of $x_i\cdot e_{ij}$ over all the clusters in $\mathcal{S}$ is 1.
+This constraint has two implications.
+First, the sum being larger than zero indicates that every node should be involved.
+Second, the sum equals 1 means a node can only appear in one cluster, which prevents the chosen clusters from overlapping.
+
+As to the objective function, the sum of the first term in the bracket over all clusters in $\mathcal{S}$ is the sum of CCs of the clusters which constitute the CRN.
 In the second term in the bracket, we propose $p(C_i)$ which is a size-related weight for cluster $C_i, i\in{1,\cdots, M}$.
 $p(C_i)$ is positively related with the difference between $C_i$'s size and the desired size $\delta$.
-When $y_i$ is 1 ($C_i$ is chosen) but $|C_i|$ doesn't equal to the desired cluster size $\delta$, the second item is negative, which contradicts the direction of the optimization.
+When $x_i$ is 1 ($C_i$ is chosen) but $|C_i|$ doesn't equal to the desired cluster size $\delta$, the second item is negative, which contradicts the direction of the optimization.
 Thus the second item discourages the appearance the clusters whose sizes deviate from the desired cluster size $\delta$.
 The weight $p(C_i)$ with respect to different cluster sizes is as follows,
-%$$
-%p(C_i) = \left\{ \begin{array}{rl}
-%0 &\mbox{ if $|C_i|=\delta$} \\
-%\rho_1 &\mbox{if $||C_i|-1|=\delta$} \\
-%\rho_2 &\mbox{if $||C_i|-2|=\delta$} \\
-%\vdots\\
-%\rho_\sigma &\mbox{if $||C_i|-\sigma|=\delta$} \\
-%\end{array} \right.
-%$$
 
@@
 0 &\mbox{ if $|C_i|=\delta$} \\
-\rho_1 &\mbox{if $|C_i|=\delta \pm 1$ } \\
-\rho_2 &\mbox{if $|C_i|=\delta \pm 2$} \\
+\rho(1) &\mbox{if $|C_i|=\delta \pm 1$ } \\
+\rho(2) &\mbox{if $|C_i|=\delta \pm 2$} \\
 \vdots\\
-\rho_\sigma &\mbox{if $|C_i|=\delta \pm \sigma$} \\
+\rho(\sigma) &\mbox{if $|C_i|=\delta \pm \sigma$} \\
 \end{array} \right.
 $$
-where $ 0 < \rho_1< \rho_2 < \cdots < \rho_\sigma$.
+where $\rho$ is an increasing function and there is $ 0 < \rho(1)< \rho(2) < \cdots < \rho_(\sigma)$.
 Note that here we adopt the desired cluster size in stead of the range for cluster sizes which is described in Definition~\ref{problem}.
 Because in implementation, we usually need a large range to guarantee a feasible result for the optimization problem.
-By adopting the desired size and the punishment for deviating from it, we actually set a large range of cluster sizes and meanwhile a better control of the resulted sizes.
+By adopting the desired size and the cost for deviating from it, we actually set a large range of cluster sizes and meanwhile a better control of the resulted sizes. 
+Still to guarantee the feasibility of the problem, we allow the singleton cluster to contribute the objective function.
 

### 2017-12-22 journal-draft/ettdoc_JG.tex
changed according to comments on 3.12

@@
 \usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\argmax}{arg\,max}
+\DeclareMathOperator*{\argmin}{\textbf{\upshape arg\,min}}
+\DeclareMathOperator*{\argmax}{\textbf{\upshape arg\,max}}
 
@@
 $\delta$ & the desired cluster size\\
-$S_i$ & a set of claiming clusters, each of which includes \\
-& debatable node $i$ after phase I\\
-$d_i$  & individual connectivity degree of CR node $i$\\
-$g_i$  & neighborhood connectivity degree of CR node $i$\\
-$f(C)$ & the number of CCs of a cluster $C$, which is used \\
-& in the problem description\\
+$S_i$ & a set of claiming clusters, each of which \\
+& includes debatable node $i$ after phase I\\
+$f(C)$ & the number of CCs of a cluster $C$ in the\\ 
+& problem description\\
 % $\mathcal{G}$ & a collection of some possible clusters in $\mathcal{N}$\\
@@
  $|K(C_i)|$ & the number of CCs of cluster $C_i$\\
+ $M$ & the cardinality of set $\mathcal{S}$ which contains all\\ 
+ & the possible clusters (Sec.~\ref{centralized_solution})\\
+ $p(C_i)$ & the weight with respect to cluster $C_i$ (Sec.~\ref{centralized_solution}) \\
+ $d_i$  & individual connectivity degree of CR node $i$\\
+$g_i$  & neighborhood connectivity degree of CR node $i$\\
   $n$ & the number of debatable nodes\\
  $m$ & the number of claiming cluster heads\\
+ $J$ & the new value of $d_i$ for the CR node after it\\
+ & becomes a cluster member (Sec.~\ref{ross})\\
+ $e$ & cost function in the formulated game (Sec.~\ref{clustering:phaseII:game})\\
 \bottomrule
@@
 %XXXXXX%
-%Di: The first paragraph has been revised based on the first batch of comments for the camera-ready version, but somehow get lost in the last version.
+%Di writes: The first paragraph has been revised based on the first batch of comments for the camera-ready version, but somehow get lost in the last version.
 I take some parts from your revision and keep some from my revision.
@@
 By adopting the desired size and the cost for deviating from it, we actually set a large range of cluster sizes and meanwhile a better control of the resulted sizes. 
-Still to guarantee the feasibility of the problem, we allow the singleton cluster to contribute the objective function.
+Also to guarantee the feasibility of the problem, we allow the singleton cluster to contribute the objective function.
 
@@
 
-After a CR node, say $i$, receives notification that there is a new cluster head in its neighborhood, $i$ sets its individual connectivity degree to a positive number $M > |\mathcal{K}| \cdot N$, and broadcasts the new individual connectivity degree.
-When node $i$ is associated with multiple clusters, \ie $i$ has received multiple notifications from different cluster heads, $d_i$ is still set to be $M$. 
+After a CR node, say $i$, receives notification that there is a new cluster head in its neighborhood, $i$ sets its individual connectivity degree to a positive number $J > |\mathcal{K}| \cdot N$, and broadcasts the new individual connectivity degree.
+When node $i$ is associated with multiple clusters, \ie $i$ has received multiple notifications from different cluster heads, $d_i$ is still set to be $J$. 
 The manipulation of the individual connectivity degree of the cluster members accelerates the decision on the cluster heads.
@@
 A secondary node, say $i$, becomes cluster head when its \textit{individual connectivity degree} is smaller than any of its neighbors.
-Afterwards, the \textit{individual connectivity degrees} of its neighbors becomes $M$.
+Afterwards, the \textit{individual connectivity degrees} of its neighbors becomes $J$.
 %If all the neighbors stay in the cluster, the cluster head will remain to be cluster head.
@@
 \subsubsection{Distributed Greedy Algorithm (DGA)}
-When a debatable node $i$ decides to join cluster $C\in S_i$, the guiding idea is that its decision should result in the greatest increase of CCs in all its claiming clusters.
-As node $i$ has been notified of the spectrum availability on all the nodes in each claiming cluster, node $i$ is able to calculate how many more CCs will result in a claiming cluster if $i$ leaves that cluster.
-Then node $i$ decides on the cluster $C\in S_i$, if $i$ leaving cluster $C$ results in a lower increase in terms of CCs than leaving any other claiming clusters in $S_i$.
+When a debatable node $i$ decides to join the cluster $C\in S_i$, the guiding idea is that its decision should result in the greatest increase of CCs in all its claiming clusters.
+As the node $i$ has been notified of the spectrum availability on all the nodes in each claiming cluster, node $i$ can calculate how many more CCs will be generated in $\mathcal{S}_i$ if it chooses a claiming cluster and leaves the other claiming clusters.
+%Then node $i$ decides on the cluster $C\in S_i$, if $i$ leaving cluster $C$ results in a lower increase in terms of CCs than leaving any other claiming clusters in $S_i$.
 %As to a cluster $C\in S_i$, if $i$ leaves cluster $C$ and results in less increased CCs than leaving any other claiming clusters, then $i$ chooses to stay in cluster $C$.
@@
 
-\subsubsection{Bridging ROSS-DGA with Congestion Game}
+\subsubsection{Formulation of ROSS-DGA to Congestion Game}
 \label{clustering:phaseII:game}
@@
 In the following, we show that the decision of debatable nodes to clarify their membership can be mapped to the behaviour of the players in a \textit{player-specific singleton congestion game} when proper cost function is given.
-The game to be constructed is represented with a 4-tuple $\Gamma=(\mathcal{P},\mathcal{R},\sum_{i, i \in \mathcal{P}}, f)$ with the following elements:
+The game to be constructed is represented with a 4-tuple $\Gamma=(\mathcal{P},\mathcal{R},\sum_{i, i \in \mathcal{P}}, e)$ with the following elements:
 
@@
 	As debatable node $i$ is supposed to choose only one claiming cluster, only a single resource will be allocated to $i$.%, accordingly this congestion game is a singleton game.
-	\item 	The cost function $f(C)$ regarding resource $C$. 
-	$f(C) = \Delta\vert K^i(C)|, C\in S_i$, which represents the decreased number of CCs in cluster $C$ when debatable node $i$ joins $C$.
+	\item 	The cost function $e(C)$ regarding resource $C$. 
+	$e(C) = \Delta\vert K^i(C)|, C\in S_i$, which represents the decreased number of CCs in cluster $C$ when debatable node $i$ joins $C$.
 	As to cluster $C\in S_i$, the decrease of CCs caused by accepting the debatable nodes is $\sum_{i:C\in S_i, i\rightarrow C} \Delta\vert K^i(C) \vert$. 
@@
   \includegraphics[width=0.6\linewidth]{percentage_overlapping_node.pdf}
-  \caption{Percentage of debatable nodes after phase I of ROSS.}
+  \caption{Percentage of debatable nodes after ROSS phase I}
   \label{percentage_overlapping_node}
@@
  Scheme 				&Message Overhead 	&   Number of messages 		& Content and size of the message 									\\ \hline
- ROSS-DGA, ROSS-$\delta$-DGA 	&$\mathcal{O}(N^3)$ (\tnotex{tnote:robots-r0} 	)		&   $N+n^2m$ (upper bound)  				&   \multirow{2}{*}{\parbox{7.7cm}{PhaseI: ID, $d_i$,$g_i$, which are 3 bytes;\\ PhaseII: Cluster head $i$ broadcasts channel availability to all \\ members, where are $|C(i)| |\mathcal{K}|$ bytes}}								\\ \cline{1-3}
- ROSS-DFA, ROSS-$\delta$-DFA 	&$\mathcal{O}(N)$ (\tnotex{tnote:robots-r3} 	)		&   $N + n$	 (upper bound) 					& 	      												\\ \hline
+ ROSS-DGA, ROSS-$\delta$-DGA 	&$\mathcal{O}(N^3)$ \tnotex{tnote:robots-r0}		&   $N+n^2m$ (upper bound)  				&   \multirow{2}{*}{\parbox{7.7cm}{PhaseI: ID, $d_i$,$g_i$, which are 3 bytes;\\ PhaseII: Cluster head $i$ broadcasts channel availability to all \\ members, where are $|C(i)| |\mathcal{K}|$ bytes}}								\\ \cline{1-3}
+ ROSS-DFA, ROSS-$\delta$-DFA 	&$\mathcal{O}(N)$  \tnotex{tnote:robots-r3}   	&   $N + n$	 (upper bound) 					& 	      												\\ \hline
  SOC 					&$\mathcal{O}(N)$		&   $3N$									& Every CR node $i$ broadcasts channel availability on all cluster members, which is $|C(i)| |\mathcal{K}|$ bytes
@@
 \begin{table}[ht]
-\caption{}
+\caption{The average numbers of neighbors and the chosen desired sizes with respect to different network scales}
 \label{Simulation_para}
@@
 \begin{multicols}{3}
-    \includegraphics[width=\linewidth]{survival_rate_100_edge50.pdf}\par\caption{100 CRs}\label{singleton_clusters_100}
-    \includegraphics[width=\linewidth]{survival_rate_200_edge50.pdf}\par\caption{200 CRs}\label{singleton_clusters_200}
-    \includegraphics[width=\linewidth]{survival_rate_300_edge50.pdf}\par\caption{300 CRs}\label{singleton_clusters_300}
+    \includegraphics[width=\linewidth]{survival_rate_100_edge50.pdf}\par\caption{Percentage of Unclustered CR nodes when $N=100$}\label{singleton_clusters_100}
+    \includegraphics[width=\linewidth]{survival_rate_200_edge50.pdf}\par\caption{Percentage of Unclustered CR nodes when $N=200$}\label{singleton_clusters_200}
+    \includegraphics[width=\linewidth]{survival_rate_300_edge50.pdf}\par\caption{Percentage of Unclustered CR nodes when $N=300$}\label{singleton_clusters_300}
 \end{multicols}
@@
 \begin{multicols}{3}
-    \includegraphics[width=\linewidth]{cdf_clusterSize_100.pdf}\par\caption{100 CRs, 30 PUs in network}\label{cdf_clusterSize_100}
-    \includegraphics[width=\linewidth]{cdf_clusterSize_200.pdf}\par\caption{200 CRs, 30 PUs in network}\label{cdf_clusterSize_200}
-    \includegraphics[width=\linewidth]{cdf_clusterSize_300.pdf}\par\caption{300 CRs, 30 PUs in network}\label{cdf_clusterSize_300}
+    \includegraphics[width=\linewidth]{cdf_clusterSize_100.pdf}\par\caption{Empirical distribution function associated with cluster sizes when there are 100 CRs and 30 PUs in network}\label{cdf_clusterSize_100}
+    \includegraphics[width=\linewidth]{cdf_clusterSize_200.pdf}\par\caption{Empirical distribution function associated with cluster sizes when there are 200 CRs and 30 PUs in network}\label{cdf_clusterSize_200}
+    \includegraphics[width=\linewidth]{cdf_clusterSize_300.pdf}\par\caption{Empirical distribution function associated with cluster sizes when there are 300 CRs  and 30 PUs in network}\label{cdf_clusterSize_300}
 \end{multicols}
@@
 
-The ECDF results show that the cluster sizes resulting from the variants of ROSS are clearly governed by the desired size, \ie as shown in Figures~\ref{cdf_clusterSize_100}, where the number of CR nodes is 100 and the desired cluster size is 6, 90\% of CR nodes are in clusters whose sizes are between 3 and 9, while for SOC, only 17\% of nodes are in the clusters with these sizes.
+The empirical distribution functions (ECDF) associated with the cluster sizes show that the cluster sizes resulting from the variants of ROSS are clearly influenced by the chosen desired size, \ie as shown in Figures~\ref{cdf_clusterSize_100}, where the number of CR nodes is 100 and the desired cluster size is 6, 90\% of CR nodes are in clusters whose sizes are between 3 and 9, while for SOC, only 17\% of nodes are in the clusters with these sizes.
 Similarly, when $N=200$ and the desired size is 12 (as shown in Figure~\ref{cdf_clusterSize_200}), 80\% of nodes are in clusters whose sizes are between 6 and 18, while only 30\% of nodes are in clusters of similar sizes when SOC is executed.
@@
    \includegraphics[width=0.7\linewidth]{draw_cdf_clusterSize_with_false_negative.pdf}
-  \caption{100 CRs with false negative in spectrum sensing, 30 PUs in network}
+  \caption{Empirical distribution function associated with cluster sizes, where there are 30 PUs and 100 CRs with false negative in spectrum sensing}
   \label{false_negative_CDF}
@@
 \appendices
-\section{Peudo Code for Algorithm~\ref{alg0}, \ref{alg_size_control_available_CCC}, \ref{alg4}}
+\section{Peudo Code for Alg.~\ref{alg0}, \ref{alg_size_control_available_CCC}, \ref{alg4}}
 \begin{algorithm}              % enter the algorithm environment
@@
 \SetAlgoLined
-\KwIn{$d_j, g_j, j\in \text{Nb}(i)\setminus \Lambda$, $\Lambda$ denotes the set of cluster heads among $\text{Nb}(i)$. Empty sets $\tau_1,\tau_2$}
+\KwIn{$d_j, g_j, j\in \text{Nb}(i)\setminus \Lambda$, $\Lambda$ denotes the set of cluster heads among $\text{Nb}(i)$. Empty sets $\tau_1,\tau_2$.}
 \KwResult{Returning 1 means $i$ is cluster head, and $d_j$ is set to 0, $j\in \text{Nb}(i)\setminus \Lambda$. Returning 0 means $i$ is not cluster head.}
 %C1-6-wording
-\If{$\nexists j\in \text{Nb}(i)\setminus \Lambda$, such that $d_i \geq d_j$}{
+\If{$\nexists j\in \text{\upshape Nb}(i)\setminus \Lambda$, \text{\upshape such that} $d_i \geq d_j$}{
 	return 1;
 	}
-\eIf{$\exists j\in \text{Nb}(i)\setminus \Lambda$, such that $d_i > d_j$}{
+\eIf{$\exists j\in \text{\upshape Nb}(i)\setminus \Lambda$, \text{\upshape such that} $d_i > d_j$}{
 	return 0;}{
-	\If{$\nexists j\in \text{Nb}(i)\setminus \Lambda$, such that $d_j == d_i$}{
+	\If{$\nexists j\in \text{\upshape Nb}(i)\setminus \Lambda$, \text{\upshape such that} $d_j == d_i$}{
 	$\tau_1 \leftarrow j$
@@
 }
-\If{$\nexists j\in \tau_1$, such that $g_i \leq g_j$}{
+\If{$\nexists j\in \tau_1$, \text{\upshape such that} $g_i \leq g_j$}{
 	return 1;
 	}
-\eIf{$\exists j\in \tau_1$, such that $g_i < g_j$}{
+\eIf{$\exists j\in \tau_1$, \text{\upshape such that} $g_i < g_j$}{
 	return 0;
 	}
-	{\If{$\nexists j\in \tau_1$, such that $g_j == g_i$}{
+	{\If{$\nexists j\in \tau_1$, \text{\upshape such that} $g_j == g_i$}{
 		$\tau_2\leftarrow j$
@@
 	}
-\If{$\texttt{ID}_i$ is smaller than any $\texttt{ID}_j$, $j\in \tau_2\setminus i$}{
+\If{$\text{\upshape ID}_i$ \text{\upshape is smaller than any} $\text{\upshape ID}_j$, $j\in \tau_2\setminus i$}{
 	return 1;
@@
 	%calculate $\lambda = \min_{i\in C, i\neq H_C}(|K_{H_C}\cap K_i|)$;\\
-	\eIf{$\exists$ only one $i\in C\setminus h(C)$, $i = \argmin(|K_{h(C)}\cap K_i|)$}{
+	\eIf{$\exists$ \text{\upshape only one} $i\in C\setminus h(C)$, $i = \argmin(|K_{h(C)}\cap K_i|)$}{
 			$C=C\setminus i$;
@@
 
-	\eIf{$\exists$ only one $i\in \tau_1$, $i = \argmax(|\cap_{j\in C\setminus i} K_j|-|\cap_{j\in C} K_j|)$}{
+	\eIf{$\exists$ \text{\upshape only one} $i\in \tau_1$, $i = \argmax(|\cap_{j\in C\setminus i} K_j|-|\cap_{j\in C} K_j|)$}{
 		$C=C\setminus i$;
@@
 			%$\exists$ multiple $i$ which satisfies $i = \argmax(|\cap_{j\in C\setminus i} K_j|-|\cap_{j\in C} K_j|)$;\\
-			$C=C\setminus i$, where $i = \argmin_{i\in \tau_1} \texttt{ID}_i $
+			$C=C\setminus i$, where $i = \argmin\limits_{i\in \tau_1} \texttt{ID}_i $
 			%$\texttt{ID}_i$ is smaller than any $\texttt{ID}_j$, $j\in \tau_2\setminus i$;
@@
 }
-\While{$i$ has not chosen the cluster, or $i$ has joined cluster $\tilde{C}$, but $\exists C'\in S_i, C'\neq \tilde{C}$, which has $|K(C'\setminus i)|-|K(C')|<|K(C\setminus i)|-|K(C)|$}{
-	\eIf{$\exists$ only one $C\in S_i$, $C = \argmin(|K(C\setminus i)| - |K(C)|)$}{
+\While{$i$ \text{\upshape has not chosen the cluster, or} $i$ \text{\upshape has joined} \text{\upshape cluster} $\tilde{C}$, \text{\upshape but} $\exists C'\in S_i (C'\neq \tilde{C})$, \text{\upshape which has} $|K(C'\setminus i)|-|K(C')|<|K(\tilde{C}\setminus i)|-|K(\tilde{C})|$}{
+	\eIf{$\exists$ \text{\upshape only one} $C\in S_i$, $C = \argmax\limits_{C'\in \mathcal{S}_i\backslash C} \Sigma (|K(C'\setminus i)| - |K(C')|)$}{
 			return $C$;
 		}{
-				$\exists$ multiple $C\in S_i$ which satisfies $C = \argmin(|K(C\setminus i)| - |K(C)|)$;\\ 
+				%$\exists$ multiple $C\in S_i$ which satisfies $C = \argmax \Sigma_{C'\in \mathcal{S}_i\backslash C}(|K(C'\setminus i)| - |K(C')|)$;\\ 
+				$\exists$ \text{\upshape multiple} $C$ satisfying the above condition, then
 				$\tau_1\leftarrow C$;		
 		}
-	\eIf{$\exists$ only one $C\in \tau_1$, $C = \argmax(K_{h(C)}\cap K_i)$}{
+	\eIf{$\exists$ \text{\upshape only one} $C\in \tau_1$, $C = \argmax(K_{h(C)}\cap K_i)$}{
 			return $C$;
 		}{
-				$\exists$ multiple $C\in S_i$ which satisfies $C = \argmax(K_{h(C)}\cap K_i)$;\\ 
+				%$\exists$ multiple $C\in S_i$ which satisfies $C = \argmax(K_{h(C)}\cap K_i)$;\\ 
+				$\exists$ \text{\upshape multiple} $C$ satisfying the above condition, then
 				$\tau_2\leftarrow C$;		
 		}
-	\eIf{$\exists$ only one $C\in \tau_2$, $C = \argmin|C|)$}{
+	\eIf{$\exists$ \text{\upshape only one} $C\in \tau_2$, $C = \argmin|C|$}{
 			return $C$;
 		}{
-				return $\argmin_{C\in \tau_2}h(C)$;\\
+				return $\argmin\limits_{C\in \tau_2}h(C)$;\\
 		}
@@
 To simplify the discussion, we assume that secondary users have unique individual connectivity degrees.
-Each user has an identical ID and a neighborhood connectivity degree.
-This assumption is justified as the neighborhood connectivity degrees and node IDs are used to break ties in Algorithm~\ref{alg0}, when the individual connectivity degrees are unique, it is not necessary to use the former two metrics.
+%Each user has an identical ID and a neighborhood connectivity degree.
+%This assumption is justified as the neighborhood connectivity degrees and node IDs are used to break ties in Algorithm~\ref{alg0}, when the individual connectivity degrees are unique, it is not necessary to use the former two metrics.
 %(COMMENT: What do you mean by breaking ties??
@@
 %Otherwise, node $\alpha$ is eligible to form a cluster. COMMENT: unnecessary sentence!
-If $\beta$ becomes cluster head, node $\alpha$ is included, the assumption is not true.
+If $\beta$ becomes cluster head, node $\alpha$ is included, the assumption that $\alpha$ is not included in any cluster is not true.
 If $\beta$ is not a cluster head, then $\beta$ is not in any cluster, we can repeat the previous analysis made on node $\alpha$, and deduce that node $\beta$ has a neighboring node $\gamma$ with $d_{\gamma} < d_{\beta}$.
 % (COMMENT: $\beta$ not being a cluster head and $\beta$ not belonging to any cluster is not the same statement!!! ANSWER(Di): I add some more words)
-So far, when there is no cluster head identified, the unclustered nodes, \ie $\alpha$, $\beta$ form a linked list, where their connectivity degrees monotonically decrease.
+So far, when no cluster head is identified, the unclustered nodes, \ie $\alpha$, $\beta$ form a linked list, where their individual connectivity degrees monotonically decrease.
 But this list will not continue growing, because the minimum individual connectivity degree is zero, and the length of this list is upper-bounded by the total number of nodes in the CRN.
@@
 Then $\omega$ incorporates all its one-hop neighbors (here we assume that every newly formed cluster has common channels), including the nodes which precede $\omega$ in the list.
-The nodes which join a cluster set their individual connection degrees to $M$, which makes the node immediately precede in the list to become a cluster head.
+The nodes which join a cluster set their individual connection degrees to $J$, which makes the node immediately precede in the list to become a cluster head.
 In this way, cluster heads are generated from the tail to the head in the list, and every node in the list is in at least one cluster, which contradicts the assumption that $\alpha$ is not included in any cluster.

### 2017-12-22 journal-draft/ettdoc_JG.tex
changed according to comments on 3.12

@@
  & becomes a cluster member (Sec.~\ref{ross})\\
- $e$ & cost function in the formulated game (Sec.~\ref{clustering:phaseII:game})\\
+% $e$ & cost function in the formulated game (Sec.~\ref{clustering:phaseII:game})\\
 \bottomrule
@@
 
-To formulate the debatable nodes' membership clarification into a congestion game, we reexamine this process from a different perspective. 
-Thus, debatable nodes are not included in any cluster and they need to decide on one cluster to join.
+To formulate the debatable nodes' membership clarification into a congestion game, we see this process from a different perspective. 
+In particular, for a debatable node, instead being in all its claiming clusters, now it is not included in any claiming cluster and it needs to decide on one cluster to join.
 When a debatable node $i$ joins one cluster $C$, the decrease of CCs in cluster $C$ is $\sum_{C\in S_i}\Delta\vert K(C) \vert=\sum_{C\in S_i}({\vert K(C) \vert-\vert K(C\cup i) \vert})$.
@@
   \includegraphics[width=0.7\linewidth]{number_controlMsg_debug.pdf}
-  \caption{The number of control messages required for clustering, which is based on the second column of Table~\ref{tab_overhead} }
+  \caption{The number of transmitted control messages required for clustering (based on the third column in Table~\ref{tab_overhead})}
   \label{control_msg}
@@
 Besides, a set of channels with cardinality of $|\omega(S)|$ is allocated to all the CR nodes in this cluster, and the channels are on the spectrum band which is exclusive for this cluster.
-For the set $S$ which contains only one element, \ie $S =\{t\}$ where $t\in\mathcal{P}$, a cluster composed with two CR nodes will be created.
-In this case, one CR node's ID is $t$, the other CR node is the dummy node of the former and its ID is $t+N$.
+For the set $S$ which contains only one element, \ie $S =\{t\}$ where $t\in\mathcal{P}$, a cluster composed with two CR nodes will be created, \ie one CR node's ID is $t$, the other CR node is the dummy node of the former and its ID is $t+N$.
 A number of $|\omega(S)|$ channels from the exclusive spectrum band for this cluster are allocated to these two CR nodes.
@@
 Actually, all the constructed CR nodes can be assumed to locate in a very small area so that each CR node is within the transmission scope of every other CR node.
-Note that in each constructed cluster, the CR nodes occupy the common channels which are exclusive to this cluster, this design of transformation eliminates the formation of the cluster which doesn't have a corresponding set in $\mathcal{Q}$.
+Note that each constructed cluster maintains the common channels which are exclusive to that cluster.
+This rule in transformation makes the formation for every set in $\mathcal{Q}$ to be feasible.
 The existence of the singleton clusters ensures that it is always possible to find out a group of clusters, which together constitute the whole CRN.

### 2017-12-24 journal-draft/ettdoc_JG.tex
change figure captioins and figure

@@
 \begin{multicols}{3}
-    \includegraphics[width=\linewidth]{survival_rate_100_edge50.pdf}\par\caption{Percentage of Unclustered CR nodes when $N=100$}\label{singleton_clusters_100}
-    \includegraphics[width=\linewidth]{survival_rate_200_edge50.pdf}\par\caption{Percentage of Unclustered CR nodes when $N=200$}\label{singleton_clusters_200}
-    \includegraphics[width=\linewidth]{survival_rate_300_edge50.pdf}\par\caption{Percentage of Unclustered CR nodes when $N=300$}\label{singleton_clusters_300}
+    \includegraphics[width=\linewidth]{survival_rate_100_edge50.pdf}\par\caption{Percentage of Unclustered CR nodes with increasing number of PUs, where $N=100$}\label{singleton_clusters_100}
+    \includegraphics[width=\linewidth]{survival_rate_200_edge50.pdf}\par\caption{Percentage of Unclustered CR nodes with increasing number of PUs, where $N=200$}\label{singleton_clusters_200}
+    \includegraphics[width=\linewidth]{survival_rate_300_edge50.pdf}\par\caption{Percentage of Unclustered CR nodes with increasing number of PUs, where $N=300$}\label{singleton_clusters_300}
 \end{multicols}
@@
    \includegraphics[width=0.7\linewidth]{nClusters_largeNetwork_no_texture.pdf}
-  \caption{The number of formed clusters.}
+  \caption{The number of formed clusters in CRN with different densities.}
   %, there are $x=6$ when $N=100$, $x=12$ when $N=200$, $x=21$ when $N=300$, which is around $2/3$ of the number of average neighbours.

### 2017-12-24 journal-draft/ettdoc_JG.tex
minor change

@@
 
-To formulate the debatable nodes' membership clarification into a congestion game, we see this process from a different perspective. 
-In particular, for a debatable node, instead being in all its claiming clusters, now it is not included in any claiming cluster and it needs to decide on one cluster to join.
+To formulate the debatable nodes' membership clarification into a congestion game, we see the process from a different perspective. 
+In particular, for a debatable node, instead being in all its claiming clusters, we see it is not included in any claiming cluster and it needs to decide on one cluster to join.
 When a debatable node $i$ joins one cluster $C$, the decrease of CCs in cluster $C$ is $\sum_{C\in S_i}\Delta\vert K(C) \vert=\sum_{C\in S_i}({\vert K(C) \vert-\vert K(C\cup i) \vert})$.

### 2017-12-24 journal-draft/ettdoc_JG.tex
polish the tabel of notations, polish the introduction of \delta

--- 2017-12-24 journal-draft/ettdoc_JG.tex
@@
 Table~\ref{tab1} summarizes all parameters and their assumed relevance in our system model. 
+The usage scope is also provided when they are not used throughout the paper.
 \begin{table}[h!]
@@
 $\mathcal{K}$	& set of licensed channels\\
-$k(i)$ & the working channel of user $i$\\
+%$k(i)$ & the working channel of user $i$\\
 $\text{Nb}(i)$ & the neighborhood of CR node $i$    \\
@@
 $f(C)$ & the number of CCs of a cluster $C$ in the\\ 
-& problem description\\
+& problem description (Sec.~\ref{problem})\\
 % $\mathcal{G}$ & a collection of some possible clusters in $\mathcal{N}$\\
- $\mathcal{S}$ & the collection of all the possible clusters in $\mathcal{N}$\\
- $C_i$  & the $i$-th cluster in $\mathcal{S}$ \\
- $|C_i|$ & the size of the cluster $C_i$\\
- $|K(C_i)|$ & the number of CCs of cluster $C_i$\\
- $M$ & the cardinality of set $\mathcal{S}$ which contains all\\ 
- & the possible clusters (Sec.~\ref{centralized_solution})\\
+ $\mathcal{S}$ & the collection of all the possible clusters \\
+ & in $\mathcal{N}$ (Sec.~\ref{centralized_solution})\\
+ $M$ & the cardinality of $\mathcal{S}$ (Sec.~\ref{centralized_solution})\\
+ $C_i$  & the $i$-th cluster in $\mathcal{S}$ (Sec.~\ref{centralized_solution})\\
+ %$|C_i|$ & the size of the cluster $C_i$\\
+ %$|K(C_i)|$ & the number of CCs of cluster $C_i$\\
  $p(C_i)$ & the weight with respect to cluster $C_i$ (Sec.~\ref{centralized_solution}) \\
@@
 As to the objective function, the sum of the first term in the bracket over all clusters in $\mathcal{S}$ is the sum of CCs of the clusters which constitute the CRN.
-In the second term in the bracket, we propose $p(C_i)$ which is a size-related weight for cluster $C_i, i\in{1,\cdots, M}$.
+For the second term in the bracket, we propose $p(C_i)$ which is a size-related weight for cluster $C_i, i\in{1,\cdots, M}$.
 $p(C_i)$ is positively related with the difference between $C_i$'s size and the desired size $\delta$.
@@
 where $\rho$ is an increasing function and there is $ 0 < \rho(1)< \rho(2) < \cdots < \rho_(\sigma)$.
-Note that here we adopt the desired cluster size in stead of the range for cluster sizes which is described in Definition~\ref{problem}.
-Because in implementation, we usually need a large range to guarantee a feasible result for the optimization problem.
-By adopting the desired size and the cost for deviating from it, we actually set a large range of cluster sizes and meanwhile a better control of the resulted sizes. 
-Also to guarantee the feasibility of the problem, we allow the singleton cluster to contribute the objective function.
+Note that here we adopt the desired cluster size in stead of the upper and lower bounds for cluster sizes which is described in Definition~\ref{problem}.
+%Because in implementation, we usually need a large range to guarantee a feasible result for the optimization problem.
+With $\delta$ and the deviation from it, we actually set a large range of cluster sizes, which guarantees the feasibility of the problem as we allow the singleton cluster to appear, meanwhile a better control of the resulted sizes by setting weights for the formed clusters based on their deviations from the desired size.
+%Also to guarantee the feasibility of the problem, we allow the singleton cluster to contribute the objective function.
 

### 2017-12-24 journal-draft/ettdoc_JG.tex
change the proof 3.1, modify section 4 by deleding \rho

@@
  %$|K(C_i)|$ & the number of CCs of cluster $C_i$\\
- $p(C_i)$ & the weight with respect to cluster $C_i$ (Sec.~\ref{centralized_solution}) \\
+ %$p(C_i)$ & the weight with respect to cluster $C_i$ (Sec.~\ref{centralized_solution}) \\
  $d_i$  & individual connectivity degree of CR node $i$\\
@@
 For the second term in the bracket, we propose $p(C_i)$ which is a size-related weight for cluster $C_i, i\in{1,\cdots, M}$.
-$p(C_i)$ is positively related with the difference between $C_i$'s size and the desired size $\delta$.
+There is, 
+$$
+p(C_i) = \rho(||C_i|-\delta|)
+$$
+where $\rho$ is a positive increasing function with respect to the the difference between $C_i$'s size and the desired size $\delta$.
 When $x_i$ is 1 ($C_i$ is chosen) but $|C_i|$ doesn't equal to the desired cluster size $\delta$, the second item is negative, which contradicts the direction of the optimization.
 Thus the second item discourages the appearance the clusters whose sizes deviate from the desired cluster size $\delta$.
-The weight $p(C_i)$ with respect to different cluster sizes is as follows,
-
-$$
-p(C_i) = \left\{ \begin{array}{rl}
-0 &\mbox{ if $|C_i|=\delta$} \\
-\rho(1) &\mbox{if $|C_i|=\delta \pm 1$ } \\
-\rho(2) &\mbox{if $|C_i|=\delta \pm 2$} \\
-\vdots\\
-\rho(\sigma) &\mbox{if $|C_i|=\delta \pm \sigma$} \\
-\end{array} \right.
-$$
-where $\rho$ is an increasing function and there is $ 0 < \rho(1)< \rho(2) < \cdots < \rho_(\sigma)$.
-Note that here we adopt the desired cluster size in stead of the upper and lower bounds for cluster sizes which is described in Definition~\ref{problem}.
+%The weight $p(C_i)$ with respect to different cluster sizes is as follows,
+
+%$$
+%p(C_i) = \left\{ \begin{array}{rl}
+%0 &\mbox{ if $|C_i|=\delta$} \\
+%\rho(1) &\mbox{if $|C_i|=\delta \pm 1$ } \\
+%\rho(2) &\mbox{if $|C_i|=\delta \pm 2$} \\
+%\vdots\\
+%%\rho(\sigma) &\mbox{if $|C_i|=\delta \pm \sigma$} \\
+%\end{array} \right.
+%$$
+%where $\rho$ is an increasing function and there is $ 0 < \rho(1)< \rho(2) < \cdots $.
+Note here we adopt the desired cluster size in stead of the upper and lower bounds for cluster sizes which is described in Definition~\ref{problem}.
 %Because in implementation, we usually need a large range to guarantee a feasible result for the optimization problem.
-With $\delta$ and the deviation from it, we actually set a large range of cluster sizes, which guarantees the feasibility of the problem as we allow the singleton cluster to appear, meanwhile a better control of the resulted sizes by setting weights for the formed clusters based on their deviations from the desired size.
+With $\delta$ and the deviation from it, we actually have a large range of cluster sizes, which guarantees the feasibility of the problem as we allow the singleton cluster to exist, meanwhile a better control of the resulted sizes by setting weights for the formed clusters based on their deviations from the desired size.
 %Also to guarantee the feasibility of the problem, we allow the singleton cluster to contribute the objective function.
 
-The difficulty of using this method lies in obtaining the set $\mathcal{S}$.
+The difficulty of implementing this method is obtaining the set $\mathcal{S}$.
 In the worst case, \ie if every CR node can communicate directly with any other node, then the CRN forms a full connected graph and therefore the size of the powerset $\mathcal{S}$ is $\Sigma_{r=1}^{N}\ {N \choose r} = 2^N-1$.
@@
 	return 0;}{
-	\If{$\nexists j\in \text{\upshape Nb}(i)\setminus \Lambda$, \text{\upshape such that} $d_j == d_i$}{
+	\If{$\nexists j\in \text{\upshape Nb}(i)\setminus \Lambda$, \text{\upshape such that} $d_j$ \text{\upshape equals}  $ d_i$}{
 	$\tau_1 \leftarrow j$
@@
 	}
-	{\If{$\nexists j\in \tau_1$, \text{\upshape such that} $g_j == g_i$}{
+	{\If{$\nexists j\in \tau_1$, \text{\upshape such that} $g_j$ \text{\upshape equals} $g_i$}{
 		$\tau_2\leftarrow j$
@@
 \KwIn{all claiming clusters $C\in S_i$}
-\KwOut{one cluster $C\in S_i$, node $i$ notifies all its claiming clusters in $S_i$ about its affiliation decision.
-}
-\While{$i$ \text{\upshape has not chosen the cluster, or} $i$ \text{\upshape has joined} \text{\upshape cluster} $\tilde{C}$, \text{\upshape but} $\exists C'\in S_i (C'\neq \tilde{C})$, \text{\upshape which has} $|K(C'\setminus i)|-|K(C')|<|K(\tilde{C}\setminus i)|-|K(\tilde{C})|$}{
-	\eIf{$\exists$ \text{\upshape only one} $C\in S_i$, $C = \argmax\limits_{C'\in \mathcal{S}_i\backslash C} \Sigma (|K(C'\setminus i)| - |K(C')|)$}{
+\KwOut{one cluster $C\in S_i$, afterwards node $i$ notifies all its claiming clusters in $S_i$ about its affiliation decision.
+}
+\While{$i$ \text{\upshape has not chosen a cluster, or} $i$ \text{\upshape has chosen cluster} $\tilde{C}$, \text{\upshape but} $\exists C'\in S_i (C'\neq \tilde{C})$, \text{\upshape which has} $|K(C'\setminus i)|-|K(C')|<|K(\tilde{C}\setminus i)|-|K(\tilde{C})|$}{
+	\eIf{$\exists$ \text{\upshape only one} $C\in S_i$, $C = \argmax \sum\limits_{C'\in \mathcal{S}_i\backslash C} (|K(C'\setminus i)| - |K(C')|)$}{
 			return $C$;
@@
 We will show that the weighted $k$-set packing problem $\leq_P$ CRN robust clustering problem.
-Given an instance of the weighted $k$-set packing problem, \ie a collection of sets $\mathcal{Q}=\{S_1,S_2,\cdots,S_m\}$, where the set $S_i, i\in \{1,2,\ldots,m\}$ consists of positive integers.
+Given an instance of the weighted $k$-set packing problem, \ie a collection of sets $\mathcal{Q}=\{S_1,S_2,\cdots,S_m\}$, where each set $S_i, i\in \{1,2,\ldots,m\}$ consists of positive integers.
 There is an integer weight $\omega(S_i)$ for $S_i$, in the end an integer $\lambda$ completes the description of this instance.
@@
 For the set $S$ which contains only one element, \ie $S =\{t\}$ where $t\in\mathcal{P}$, a cluster composed with two CR nodes will be created, \ie one CR node's ID is $t$, the other CR node is the dummy node of the former and its ID is $t+N$.
-A number of $|\omega(S)|$ channels from the exclusive spectrum band for this cluster are allocated to these two CR nodes.
-Now we have constructed the clusters which correspond to all the sets in $\mathcal{Q}$.
-Note that every CR node is allowed to form a singleton cluster by itself, although its common channels don't contribute to the sum of $f(C)$.
-%In the end, we construct the singleton clusters, \ie for each element in $\mathcal{P}$, a corresponding singleton cluster is constructed.
-%In particular, if the CR node has been constructed and has been in certain clusters already through the previous steps, the CR node with all the channels assigned to it constitute a singleton cluster.
-%If there is an element in $\mathcal{P}$, which doesn't has a corresponding CR node yet, we simply construct this singleton cluster by adding that CR node, and assign it with a random number of channels from a exclusive spectrum band.
-%We call the latter kind of clusters the \textit{auxiliary singleton clusters}.
+Afterwards, $|\omega(S)|$ channels which are exclusively allocated to this cluster are assigned to these two CR nodes.
+Now we have constructed the clusters which correspond to every set in $\mathcal{Q}$.
+In the end, singleton clusters are formed with respect to every element in $\mathcal{P}$.
+Note that the common channels in these singleton clusters don't contribute to the sum of $f(C)$.
+The existence of the singleton clusters ensures that it is always possible to find out a group of clusters, which together constitute the whole CRN.
 
 Actually, all the constructed CR nodes can be assumed to locate in a very small area so that each CR node is within the transmission scope of every other CR node.
-Note that each constructed cluster maintains the common channels which are exclusive to that cluster.
-This rule in transformation makes the formation for every set in $\mathcal{Q}$ to be feasible.
-The existence of the singleton clusters ensures that it is always possible to find out a group of clusters, which together constitute the whole CRN.
-%Now we have completed a CRN and can claim that all the constructed clusters $C$ constitute the complete CRN network $\mathcal{N}$.
-
-Now suppose there is a set of pairwise disjoint clusters which constitute the CRN $\mathcal{N}$, and the sum of $f(C)$ is greater than $\lambda$.
-After removing the singleton clusters, we can easily find the natural association between the remaining clusters and the sets in $\mathcal{Q}$. 
-The clusters in the CRN correspond to the sets in $\mathcal{Q}$ according to the mapping between the node IDs in the clusters and the elements in the sets.
-In particular, the clusters which contain dummy CR nodes correspond to the sets which contain only one element.
+Note that each constructed cluster maintains certain common channels which are exclusive to other clusters.
+This rule in transformation makes the transformation for every set in $\mathcal{Q}$ to be feasible.
+
+Given any instance $\mathcal{I}$ of the maximum weighted k-set packing problem, we can now formulate it to an instance $\mathcal{T}$ of the robust clustering problem.
+For each set in $\mathcal{I}$, we find out the corresponding clusters, as well as the singleton clusters, whose IDs are from $\mathcal{P}\setminus(\cup S_i), S_i\in \mathcal{I}$.
+%Given any clusters formation with respect to the instance of the maximum weighted k-set packing problem, after removing the singleton clusters, we can easily find the direct association between the remaining clusters and the sets in the instance $\mathcal{I}\subseteq \mathcal{Q}$.
+%The clusters in the CRN correspond to the sets in $\mathcal{I}$ according to the mapping between the node IDs in the clusters and the elements in the sets.
+%In particular, the clusters which contain dummy CR nodes correspond to the sets which contain only one element.
 Then the sum of the weights of the corresponding sets equals to the sum of $f(C)$ and thus greater than $\lambda$.
 
-We have now shown that our algorithm solves the weighted $k$-set packing problem using a black box for the robust clustering problem. 
-Since our construction takes polynomial time, we can conclude that the robust clustering problem is NP-hard.
+%Now suppose there is a set of pairwise disjoint clusters which constitute the CRN $\mathcal{N}$, and the sum of $f(C)$ is greater than $\lambda$, the robust clustering black box will say yes, then the instance $\mathcal{I}$ is the answer to the maximum weighted k-set packing problem.
+Based on the above construction and transformation, if robust clustering black box says yes to a clusters formation $\mathcal{T}$, then the corresponding $\mathcal{I}$ is an instance for the maximum weighted k-set packing problem.
+If the clusters formation $\mathcal{T}$ is not a solution for the robust clustering problem, then $\mathcal{I}$ is an instance for the maximum weighted k-set packing problem.
+
+Since the construction and transformation from instance to clusters formation take polynomial time, we can conclude that the robust clustering problem is NP-hard.
 %\begin{itemize}

### 2017-12-24 journal-draft/ettdoc_JG.tex
modify section 4 and others

@@
 \begin{abstract}
-%Cluster structure in cognitive radio networks facilitates cooperative spectrum sensing, routing and other functionalities.
-%Unlicensed channels, which are temporally available for a group of cognitive radio users in one area, consolidate the group into a cluster.
-%More available unlicensed channels in a cluster make the cluster more likely to uphold against the licensed users' influence, making clusters more robust.
-%This paper analyses the problem of how to form robust clusters in a cognitive radio network such that cognitive radio systems benefit from collaboration within clusters despite intense primary user activity.
-%%In the process of forming clusters, every secondary user decides with whom to form a cluster, or which cluster to join.
-%We give a formal description of the robust clustering problem, prove it to be NP-hard and propose both centralized and distributed solutions.
-%The congestion game model is adopted to analyze the process of cluster formation, which not only contributes to the design of the distributed clustering scheme, but also provides a guarantee on the convergence to a Nash equilibrium and the convergence speed.
-%%Our proposed clustering solution is versatile to fulfill some other requirements such as faster convergence and cluster size control.
-%The proposed distributed clustering scheme outperforms state-of-the-art related works in terms of cluster robustness, convergence speed and overhead.
-%%Besides, we prove the clustering problem is NP-hard, and also propose the centralized solution.
-%Extensive simulations are presented supporting the theoretical claims.
+Cluster structure in cognitive radio networks facilitates cooperative spectrum sensing, routing and other functionalities.
+Unlicensed channels, which are temporally available for a group of cognitive radio users in one area, consolidate the group into a cluster.
+More available unlicensed channels in a cluster make the cluster more likely to uphold against the licensed users' influence, making clusters more robust.
+This paper analyses the problem of how to form robust clusters in a cognitive radio network such that cognitive radio systems benefit from collaboration within clusters despite intense primary user activity.
+%In the process of forming clusters, every secondary user decides with whom to form a cluster, or which cluster to join.
+We give a formal description of the robust clustering problem, prove it to be NP-hard and propose both centralized and distributed solutions.
+The congestion game model is adopted to analyze the process of cluster formation, which not only contributes to the design of the distributed clustering scheme, but also provides a guarantee on the convergence to a Nash equilibrium and the convergence speed.
+%Our proposed clustering solution is versatile to fulfill some other requirements such as faster convergence and cluster size control.
+The proposed distributed clustering scheme outperforms state-of-the-art related works in terms of cluster robustness, convergence speed and overhead.
+%Besides, we prove the clustering problem is NP-hard, and also propose the centralized solution.
+Extensive simulations are presented supporting the theoretical claims.
 \end{abstract}
@@
  %$|K(C_i)|$ & the number of CCs of cluster $C_i$\\
- %$p(C_i)$ & the weight with respect to cluster $C_i$ (Sec.~\ref{centralized_solution}) \\
+ $p$ & the weight with respect to cluster's size (Sec.~\ref{centralized_solution}) \\
  $d_i$  & individual connectivity degree of CR node $i$\\
@@
 \begin{aligned}
-     &\max\limits_{x_i} && \Sigma_{i=1}^M (x_i\cdot |K(C_i)| - x_i\cdot p(C_i)) \\
+     &\max\limits_{x_i} && \Sigma_{i=1}^M (x_i\cdot |K(C_i)| - x_i\cdot p(||C_i|-\delta|)) \\
      &\text{subject to}   && \Sigma_{i=1}^M (x_i\cdot e_{ij}) = 1  \quad\text{for}\,\,\forall j\in\{1, \ldots, N\} \\
@@
 As to the objective function, the sum of the first term in the bracket over all clusters in $\mathcal{S}$ is the sum of CCs of the clusters which constitute the CRN.
-For the second term in the bracket, we propose $p(C_i)$ which is a size-related weight for cluster $C_i, i\in{1,\cdots, M}$.
-There is, 
-$$
-p(C_i) = \rho(||C_i|-\delta|)
-$$
-where $\rho$ is a positive increasing function with respect to the the difference between $C_i$'s size and the desired size $\delta$.
+For the second term in the bracket, $p$ is a positive increasing function with respect to the the difference between $C_i$'s size and the desired size $\delta$.
 When $x_i$ is 1 ($C_i$ is chosen) but $|C_i|$ doesn't equal to the desired cluster size $\delta$, the second item is negative, which contradicts the direction of the optimization.
@@
 During the whole phase I, whenever a CR node becomes cluster head, or the cluster composition changes, the cluster head broadcasts new/updated information about the cluster structure, in particular the new/updated sets of available channels regarding itself and all its cluster members.
-Pseudo code regarding this process, i.e. the cluster head decision and the initial cluster formation, is provided as Algorithm~\ref{alg0} in the appendix.
+Pseudo code regarding this process, i.e. the cluster head decision and the initial cluster formation, is in Algorithm~\ref{alg0} in appendix.
 
@@
 In the following, we show that the decision of debatable nodes to clarify their membership can be mapped to the behaviour of the players in a \textit{player-specific singleton congestion game} when proper cost function is given.
-The game to be constructed is represented with a 4-tuple $\Gamma=(\mathcal{P},\mathcal{R},\sum_{i, i \in \mathcal{P}}, e)$ with the following elements:
+The game to be constructed is represented with a 4-tuple $\Gamma=(\mathcal{P},\mathcal{R},\sum_{i, i \in \mathcal{P}}, \rho)$ with the following elements:
 
@@
 	As debatable node $i$ is supposed to choose only one claiming cluster, only a single resource will be allocated to $i$.%, accordingly this congestion game is a singleton game.
-	\item 	The cost function $e(C)$ regarding resource $C$. 
-	$e(C) = \Delta\vert K^i(C)|, C\in S_i$, which represents the decreased number of CCs in cluster $C$ when debatable node $i$ joins $C$.
+	\item 	The cost function $\rho(C)$ regarding resource $C$. 
+	$\rho(C) = \Delta\vert K^i(C)|, C\in S_i$, which represents the decreased number of CCs in cluster $C$ when debatable node $i$ joins $C$.
 	As to cluster $C\in S_i$, the decrease of CCs caused by accepting the debatable nodes is $\sum_{i:C\in S_i, i\rightarrow C} \Delta\vert K^i(C) \vert$. 
@@
 We set the desired cluster size $\delta$ as 3.
-As for the centralized schemes, we set the following parameters numerically: $\rho_1 =  0.4$, $\rho_2 =  0.6$.
+As for the centralized schemes, we set the following parameters numerically: $p(1) =  0.4$, $p(2) =  0.6$.
 
@@
 Figure~\ref{size_control} provides further insights into the performance comparison.
-Here, we depict the empirical cumulative distribution function of the size of the clusters.
+Here, we depict the empirical cumulative distribution function (ECDF) of the size of the clusters.
 %First, given the channel availability in the CRN, SOC generates more unclustered CR nodes than other schemes.
@@
 
-The empirical distribution functions (ECDF) associated with the cluster sizes show that the cluster sizes resulting from the variants of ROSS are clearly influenced by the chosen desired size, \ie as shown in Figures~\ref{cdf_clusterSize_100}, where the number of CR nodes is 100 and the desired cluster size is 6, 90\% of CR nodes are in clusters whose sizes are between 3 and 9, while for SOC, only 17\% of nodes are in the clusters with these sizes.
+The ECDF associated with the cluster sizes show that the cluster sizes resulting from the variants of ROSS are clearly influenced by the chosen desired size, \ie as shown in Figures~\ref{cdf_clusterSize_100}, where the number of CR nodes is 100 and the desired cluster size is 6, 90\% of CR nodes are in clusters whose sizes are between 3 and 9, while for SOC, only 17\% of nodes are in the clusters with these sizes.
 Similarly, when $N=200$ and the desired size is 12 (as shown in Figure~\ref{cdf_clusterSize_200}), 80\% of nodes are in clusters whose sizes are between 6 and 18, while only 30\% of nodes are in clusters of similar sizes when SOC is executed.

### 2017-12-28 journal-draft/ettdoc_JG.tex
minor changes
delete the line about solvers

@@
 Table~\ref{tab1} summarizes all parameters and their assumed relevance in our system model. 
-The usage scope is also provided when they are not used throughout the paper.
+The locations of the first appearances are provided for some notations.
 \begin{table}[h!]
@@
 With $|\mathcal{S}| = M$, there is $\mathcal{S}=\{C_1, C_2, \ldots, C_M\}$ \footnote{The subscript $i$ means the $i$-th cluster in $\mathcal{S}$.}.
-Then the problem as defined in Definition~\ref{def_centralized_clustering} can be formulated as a binary linear programming problem and can be solved by many available solvers:
+Then the problem as defined in Definition~\ref{def_centralized_clustering} can be formulated as a binary linear programming problem.
+% and can be solved by many available solvers:
 \begin{equation}

### 2018-02-21 journal-draft/ettdoc_JG.tex
modify the bibtex entry of the arxiv file. minor change in ettdoc_JG.tex

@@
 
-\def\volumeyear{2017}
+\def\volumeyear{2018}
 
@@
 This paper analyses the problem of how to form robust clusters in a cognitive radio network such that cognitive radio systems benefit from collaboration within clusters despite intense primary user activity.
-%In the process of forming clusters, every secondary user decides with whom to form a cluster, or which cluster to join.
 We give a formal description of the robust clustering problem, prove it to be NP-hard and propose both centralized and distributed solutions.
 The congestion game model is adopted to analyze the process of cluster formation, which not only contributes to the design of the distributed clustering scheme, but also provides a guarantee on the convergence to a Nash equilibrium and the convergence speed.
-%Our proposed clustering solution is versatile to fulfill some other requirements such as faster convergence and cluster size control.
 The proposed distributed clustering scheme outperforms state-of-the-art related works in terms of cluster robustness, convergence speed and overhead.
-%Besides, we prove the clustering problem is NP-hard, and also propose the centralized solution.
 Extensive simulations are presented supporting the theoretical claims.
@@
 \label{related_work}
-In the following we first review briefly state-of-the-art regarding clustering in CRN in general, and then focus on robust clustering in particular.
+In the following we first review the state-of-the-art regarding clustering in CRN in general, and then focus on robust clustering in particular.
 With regard to forming clusters in CRN, deciding on the common channel within each cluster is the foremost question to answer.
@@
 \label{theorem1}
-The robust clustering problem in CRN is NP-hard, when $\delta_1=2$ and $\delta_2 > 3$.
+The robust clustering problem in CRN is NP-hard, when $\delta_1=2$ and $\delta_2 $ is $\infty$.
 %when the maximum size of clusters is larger than 3
